### 2017-03-20 formalization/others/syntax.tex
paper init

\documentclass{article}
\usepackage{amsmath,amsfonts,amsthm,amssymb,algorithm,algpseudocode}
\usepackage{color,chngpage}
\usepackage{extramarks,epsfig}
\usepackage{fancyhdr,float}
\usepackage{graphicx}
\usepackage{indentfirst}
\usepackage{lastpage,listings}
\usepackage{soul,setspace}
\usepackage{wrapfig}
\usepackage[T1]{fontenc}
\usepackage[scaled=0.85]{beramono}

% Homework Specific Information. Change it to your own

\newcommand{\thistitle}{Syntax: Object Algebras}

% In case you need to adjust margins:
\topmargin=-0.45in      %
\evensidemargin=0in     %
\oddsidemargin=0in      %
\textwidth=6.5in        %
\textheight=9.0in       %
\headsep=0.25in         %

\lstset{ %
language=Java,                % choose the language of the code
columns=flexible,
lineskip=-1pt,
basicstyle=\ttfamily\small,       % the size of the fonts that are used for the code
numbers=none,                   % where to put the line-numbers
numberstyle=\ttfamily\tiny,      % the size of the fonts that are used for the line-numbers
stepnumber=1,                   % the step between two line-numbers. If it's 1 each line will be numbered
numbersep=5pt,                  % how far the line-numbers are from the code
backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
frame=single,                   % adds a frame around the code
morekeywords={sig,where,type,algebra,data,from,let,build,in},
tabsize=2,                  % sets default tabsize to 2 spaces
captionpos=none,                   % sets the caption-position to bottom
breaklines=true,                % sets automatic line breaking
breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
title=\lstname,                 % show the filename of files included with \lstinputlisting; also try caption instead of title
escapeinside={(*}{*)},          % if you want to add a comment within your code
keywordstyle=\ttfamily\bfseries,
% commentstyle=\color{Gray},
% stringstyle=\color{Green}
}

% Setup the header and footer
\pagestyle{fancy}
\lhead{} \chead{\thistitle} \rhead{}
\lfoot{} \cfoot{}
\rfoot{Page\ \thepage\ of\ \protect\pageref{LastPage}}
\renewcommand\headrulewidth{0.4pt}                                      %
\renewcommand\footrulewidth{0.4pt}                                      %

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Some tools

\newcommand{\Answer}{\ \\\textbf{Answer:} }
\newcommand{\todo}{\textbf{Proposition. } }
\newcommand{\lemma}{\textbf{Lemma. } }
\newcommand{\tab}{\ \ }
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\nb}{\textit{NB. }}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Make title
\title{\huge\textmd{\bf\thistitle}}
\date{}
\author{\today}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\begin{spacing}{1.1}
\maketitle \thispagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Begin edit from here

\section*{Notation}

\begin{align*}
N,\ T,\ \overline{N},\ \overline{T},\ E:&\textrm{ name, type, list of names, list of types, expression.}\\
\red{\&}(\overline{T}):&\textrm{ intersecting a list of types.}\\
\red{(,,)}(\overline{E}):&\textrm{ merging a list of expressions.}\\
\red{[}\blue{A}\red{\ \mapsto B]}\ E:&\textrm{ substituting }A\textrm{ for }B\textrm{ in expression }E.\\
\red{\Sigma}(...):&\textrm{ collect all fields of records, using copy and paste instead of intersection.}
\end{align*}

\section{Object Algebra Interface}

\subsection{Inheritance $\times$}

\subsubsection{Template}

\begin{lstlisting}[numbers=none]
BEFORE:     (*$\Gamma\ \vdash$*) sig (*$N_{AI}[\overline{T_{AI}}]$*) where (*$\overline{N_{CS}:T_{CS}}$*) in E
\end{lstlisting}
\begin{lstlisting}[numbers=none]
THEN:       (*$\Gamma\ \vdash$*) type (*$N_{AI}[\overline{T_{AI}}]$*) = {(*$\overline{N_{CS}:T_{CS}}$*)} in E
\end{lstlisting}
\begin{lstlisting}[numbers=none]
AFTER:      (*$\Gamma,\ N_{AI}[\overline{T_{AI}}]$*) = (*$\{\overline{N_{CS}:T_{CS}}\}\ \vdash$*)
            (*$\red{[}\blue{N_{AI}[\overline{T}]}\red{\ \mapsto[\blue{\overline{T}}\red{\ \mapsto\overline{T_{AI}}}]\ \{\overline{N_{CS}:T_{CS}}\}]}$*)
            ((*$\lambda$*)(merge(*$N_{AI}$*) : forall (*$\overline{T_{AI}^{(1)}}.$*) forall (*$\overline{T_{AI}^{(2)}}.\ N_{AI}[\overline{T_{AI}^{(1)}}]$*) -> (*$N_{AI}[\overline{T_{AI}^{(2)}}]$*) -> (*$N_{AI}[\overline{T_{AI}^{(1)\&(2)}}]$*)). E)
                (*$\Lambda\overline{T_{AI}^{(1)}}$*). (*$\Lambda\overline{T_{AI}^{(2)}}$*). (*$\lambda$*)(alg1 : (*$\overline{T_{AI}^{(1)}}$*)). (*$\lambda$*)(alg2 : (*$\overline{T_{AI}^{(2)}}$*)).
                    (*$\left\{\overline{N_{CS}\ =\ \lambda(\overline{x}:\overline{T_{CS}^{(1)\&(2)}}).\ alg1.N_{CS}\ \overline{x}\ ,,\ alg2.N_{CS}\ \overline{x}}\right\}$*)
\end{lstlisting}

\subsubsection{Example: \lstinline{ExpAlg[E]}}

\begin{lstlisting}[numbers=none]
BEFORE:     sig ExpAlg[E] where
                lit : Int -> E,
                add : E -> E -> E;
            ...
\end{lstlisting}
\begin{lstlisting}[numbers=none]
THEN:       type ExpAlg[E] = {
                lit : Int -> E,
                add : E -> E -> E
            };
            let mergeExpAlg [E1, E2] (alg1 : ExpAlg[E1]) (alg2 : ExpAlg[E2]) = {
                lit = \(x1 : Int) -> alg1.lit x1 ,, alg2.lit x1,
                add = \(x1 : E1 & E2) -> \(x2 : E1 & E2) -> alg1.add x1 x2 ,, alg2.add x1 x2
            };
            ...
\end{lstlisting}

\newpage

\subsection{Inheritance $\surd$}

\subsubsection{Template}

\begin{lstlisting}[numbers=none]
BEFORE:     (*$\Gamma\ \vdash$*) (*$N_{AI}[\overline{T_{AI}}]$*) extends (*$\overline{N_{AI_2}[\overline{T_{AI_2}}]}$*) where (*$\overline{N_{CS}:T_{CS}}$*) in E
\end{lstlisting}
\begin{lstlisting}[numbers=none]
THEN:       (*$\Gamma\ \vdash$*) type (*$N_{AI}[\overline{T_{AI}}]$*) = (*$\red{\Sigma}(\overline{N_{AI_2}[\overline{T_{AI_2}}]},\overline{N_{CS}:T_{CS}})$*) in E
\end{lstlisting}
\begin{lstlisting}[numbers=none]
AFTER:      (*$\Gamma,\ N_{AI}[\overline{T_{AI}}]$*) = (*$\red{\Sigma}(\overline{N_{AI_2}[\overline{T_{AI_2}}]},\overline{N_{CS}:T_{CS}})\ \vdash$*)
            (*$\red{[}\blue{N_{AI}[\overline{T}]}\red{\ \mapsto[\blue{\overline{T}}\red{\ \mapsto\overline{T_{AI}}}]\ \red{\Sigma}(\overline{N_{AI_2}[\overline{T_{AI_2}}]},\overline{N_{CS}:T_{CS}})]}$*) E
\end{lstlisting}

\nb Need to be updated.

\subsubsection{Example: \lstinline{StatAlg[E, S]}}

\begin{lstlisting}[numbers=none]
BEFORE:     sig StatAlg[E, S] extends ExpAlg[E] where
                seq : S -> S -> S,
                asn : String -> E -> S;
            ...
\end{lstlisting}
\begin{lstlisting}[numbers=none]
THEN:       type StatAlg[E, S] = {
                lit : Int -> E,
                add : E -> E -> E,
                seq : S -> S -> S,
                asn : String -> E -> S
            };
            ...
\end{lstlisting}

\section{Object Algebra}

\subsection{Inheritance $\times$}

\subsubsection{Template}

\begin{lstlisting}[numbers=none]
BEFORE:     algebra (*$N_A$*) implements (*$\overline{N_{AI}[\overline{T_A}]}$*) where (*$\overline{t@(N_{CS}\ \overline{x})=E}$*) in F
\end{lstlisting}
\begin{lstlisting}[numbers=none]
THEN:       let (*$N_A$*) = (*$\red{[}\blue{\overline{T_A}}\red{\ \mapsto\overline{T_{AI}}]}$*) (*$\{\overline{N_{CS}=\lambda(\overline{x}:\overline{T_{CS}}).\ \{t=E\}}\}$*) in F
\end{lstlisting}
\begin{lstlisting}[numbers=none]
AFTER:      ((*$\lambda$*)((*$N_A$*) : ???). F) (*$\red{[}\blue{\overline{T_A}}\red{\ \mapsto\overline{T_{AI}}]}$*) (*$\{\overline{N_{CS}=\lambda(\overline{x}:\overline{T_{CS}}).\ \{t=E\}}\}$*)
\end{lstlisting}

\nb ???

\subsubsection{Example: \lstinline{EvalExpAlg}}

\begin{lstlisting}[numbers=none]
BEFORE:     type IEval = { eval : Int };
            algebra EvalExpAlg implements ExpAlg[IEval] where
                eval@(lit x)(*$\ \ \ $*)= x,
                eval@(add x y) = x.eval + y.eval;
\end{lstlisting}
\begin{lstlisting}[numbers=none]
AFTER:      type IEval = { eval : Int };
            let EvalExpAlg = {
                lit = \(x : Int) -> { eval = x },
                add = \(x : IEval) -> \(y : IEval) -> { eval = x.eval + y.eval }
            };
\end{lstlisting}

\nb Note that in F2J, it should be \lstinline{evalExpAlg}.

\subsection{Inheritance $\surd$}

\subsubsection{Template}

\begin{lstlisting}[numbers=none]
BEFORE:     algebra (*$N_A$*) extends (*$\overline{N_{A_2}}$*) implements (*$\overline{N_{AI}[\overline{T_A}]}$*) where (*$\overline{t@(N_{CS}\ \overline{x})=E}$*);
\end{lstlisting}
\begin{lstlisting}[numbers=none]
AFTER:      let (*$N_A$*) =  (*$\left((\red{,,})\left(\overline{N_{A_2}}\right)\right)$*) ,, (*$\red{[}\blue{\overline{T_A}}\red{/\overline{T_{AI}}]}$*)(*$\{\overline{N_{CS}=\lambda(\overline{x}:\overline{T_{CS}}).\ \{t=E\}}\}$*);
\end{lstlisting}

\nb Need to be updated.

\subsubsection{Example: \lstinline{PrintStatAlg}}

\begin{lstlisting}[numbers=none]
BEFORE:     type IPrint = { print : String };
            algebra PrintExpAlg implements ExpAlg[IPrint] where
                print@(lit x)(*$\ \ \ $*)= "\{x}",
                print@(add x y) = "\{x.print} + \{y.print}";
            algebra PrintStatAlg extends PrintExpAlg implements StatAlg[IPrint, IPrint] where
                print@(seq x y) = "\{x.print} || \{y.print}",
                print@(asn x y) = "\{x} = \{y.print}";
\end{lstlisting}
\begin{lstlisting}[numbers=none]
AFTER:      type IPrint = { print : String };
            let PrintExpAlg = {
                lit = \(x : Int) -> { print = "\{x}" },
                add = \(x : IPrint) -> \(y : IPrint) -> { print = "\{x.print} + \{y.print}" }
            };
            let PrintStatAlg = PrintExpAlg ,, {
                seq = \(x : IPrint) -> \(y : IPrint) -> { print = "\{x.print} || \{y.print}" },
                asn = \(x : String) -> \(y : IPrint) -> { print = "\{x} = \{y.print}" }
            };
\end{lstlisting}

\section{Datatype}

\subsection{Template}

\begin{lstlisting}[numbers=none]
BEFORE:     data (*$N_D[\overline{T_D}]$*) from (*$N_{AI}[\overline{T_{AI}}].S$*);
\end{lstlisting}
\begin{lstlisting}[numbers=none]
AFTER:      type (*$N_D[\overline{T_D}]$*) = { accept : forall ((*$\overline{T_{AI}}\backslash\overline{T_D}$*)). (*$N_{AI}[\overline{T_{AI}}]$*) -> (*$S$*) };
\end{lstlisting}

\nb Usually $\overline{T_{AI}}\backslash\overline{T_D}=S$.

\subsection{Example: \lstinline{List[A]}}

\begin{lstlisting}[numbers=none]
BEFORE:     sig ListAlg[A, L] where
                nil(*$\ \ $*): L,
                cons : A -> L -> L;
            data List[A] from ListAlg[A, L].L;
\end{lstlisting}
\begin{lstlisting}[numbers=none]
AFTER:      type ListAlg[A, L] = {
                nil(*$\ \ $*): L,
                cons : A -> L -> L
            };
            type List[A] = { accept : forall L. ListAlg[A, L] -> L };
\end{lstlisting}

\section{Creating a Structure}

\subsection{Simple Structures}

\subsubsection{Template}

\begin{lstlisting}[numbers=none]
BEFORE:     build (*$N_S$*) : (*$N_D[\overline{T}]$*) = E;
\end{lstlisting}
\begin{lstlisting}[numbers=none]
AFTER:      let (*$N_S$*) = { accept = (*$\Lambda$*)((*$\overline{T_{AI}}\backslash\overline{T_D}$*)). (*$\lambda$*)(alg : (*$N_{AI}[\red{[}\blue{\overline{T}}\red{/\overline{T_D}]}\overline{T_{AI}}]$*)). (*$\red{[}\blue{\overline{alg.N_{CS}}}\red{/\overline{N_{CS}}]}$*)E };
\end{lstlisting}

\nb Potentially there could be name conflicts with \lstinline{alg}. Also names of functions and constructors could probably overlap.

\subsubsection{Example: \lstinline{Exp} and \lstinline{List[Int]}}

\begin{lstlisting}[numbers=none]
BEFORE:     data Exp from ExpAlg[E].E;
            data List[A] from ListAlg[A, L].L;
            build exp : Exp = add (lit 3) (lit 5);
            build lst : List[Int] = cons 3 (cons 5 nil);
\end{lstlisting}
\begin{lstlisting}[numbers=none]
AFTER:      type Exp = { accept : forall E. ExpAlg[E] -> E };
            type List[A] = { accept : forall L. ListAlg[A, L] -> L };
            let exp = { accept = /\E -> \(alg : ExpAlg[E]) -> alg.add (alg.lit 3) (alg.lit 5) };
            let lst = { accept = /\L -> \(alg : ListAlg[Int, L]) -> alg.cons 3 (alg.cons 5 alg.nil) };
\end{lstlisting}

\subsection{Complicated Structures Created by Functions}

\subsubsection{Template}

\begin{lstlisting}[numbers=none]
BEFORE:     build (*$N_S$*) (*$(\overline{x}$*) : (*$\overline{T_1\ne N_D[\overline{T}]})\ (\overline{y}$*) : (*$\overline{T_2=N_D[\overline{T}]})$*) : (*$N_D[\overline{T}]$*) = E;
\end{lstlisting}
\begin{lstlisting}[numbers=none]
AFTER:      let (*$N_S$*) = (*$\lambda$*)((*$\overline{x}$*) : (*$\overline{T_1}$*)). (*$\lambda$*)((*$\overline{y}$*) : (*$\overline{T_2}$*)). {
                accept = (*$\Lambda$*)((*$\overline{T_{AI}}\backslash\overline{T_D}$*)). (*$\lambda$*)(alg : (*$N_{AI}[\red{[}\blue{\overline{T}}\red{/\overline{T_D}]}\overline{T_{AI}}]$*)). (*$\red{[}\blue{\overline{alg.N_{CS}}}\red{/\overline{N_{CS}}]}\red{[}\blue{(\overline{y.accept[\overline{T_{AI}}\backslash\overline{T_D}]\ alg})}\red{/\overline{y}]}$*)E
            };
\end{lstlisting}

\subsubsection{Example: \lstinline{myAdd} and \lstinline{myCons}}

\begin{lstlisting}[numbers=none]
BEFORE:     build myAdd (e1 : Exp) (e2 : Exp) : Exp = add e1 e2;
            build myCons (x : Int) (xs : List[Int]) : List[Int] = cons x xs;
\end{lstlisting}
\begin{lstlisting}[numbers=none]
AFTER:      let myAdd = \(e1 : Exp) -> \(e2 : Exp) -> {
                accept = /\E -> \(alg : ExpAlg[E]) -> alg.add (e1.accept[E] alg) (e2.accept[E] alg)
            };
            let myCons = \(x : Int) -> \(xs : List[Int]) -> {
                accept = /\L -> \(alg : ListAlg[Int, L]) -> alg.cons x (xs.accept[L] alg)
            };
\end{lstlisting}

\nb Extension 1: What if there are BigLambdas in those functions?\\

\nb Extension 2: Does it make sense if there are two different instantiations from one datatype in a function? Namely $N_D[\overline{T_1}]$ and $N_D[\overline{T_2}]$?\\

\nb Extension 3: Recursive ones?\\

\nb IMPORTANT: Why don't we generate \lstinline{"add : Exp -> Exp -> Exp"} and \lstinline{"cons : A -> List[A] -> List[A]"} automatically for global use? My intuition is that for these two examples it's easy; however there could be non-trivial ones. For instance, a new constructor for \lstinline{ListAlg} can be \lstinline{"f : L -> A"}, in which case some structures like \lstinline{"cons (f nil)}\lstinline{ nil"} also make sense, but how to design a template for \lstinline{"f : List[Int] -> Int"}? Instead it's easier to have \lstinline{"alg.cons (alg.f alg.nil)}\lstinline{ alg.nil"}.

\section{Instantiation}

\subsection{Template}

\begin{lstlisting}[numbers=none]
BEFORE:     (*$N_S$*)[(*$\overline{[\overline{T}]}$*)]<(*$\overline{N_A}$*)>
\end{lstlisting}
\begin{lstlisting}[numbers=none]
AFTER:      (*$\red{(,,)}(\overline{N_S.accept[\overline{T}]\ N_A})$*)
\end{lstlisting}

\nb Furthermore, the types $[\overline{[\overline{T}]}]$ could potentially be omitted. But since $N_A$ could implement multiple interfaces, it's not easy to infer the types from context.

Another approach is something like \lstinline{"let result : IEval & IPrint = exp<EvalExpAlg, PrintExpAlg>"}.

\subsection{Example: \lstinline{ListAlg[A, L]} and \lstinline{List[A]}}

\begin{lstlisting}[numbers=none]
BEFORE:     type IEval = { eval : Int };
            type IPrint = { print : String };
            sig ListAlg[A, L] where
                nil(*$\ \ $*): L,
                cons : A -> L -> L;
            algebra SumListAlg implements ListAlg[IEval, IEval] where
                eval@(nil)(*$\ \ \ \ \ \ $*)= 0,
                eval@(cons x y) = x.eval + y.eval;
            algebra PrintListAlg implements ListAlg[IPrint, IPrint] where
                print@(nil)(*$\ \ \ \ \ \ $*)= "",
                print@(cons x y) = "\{x.print} \{y.print}";
            data List[A] from ListAlg[A, L].L;
            build lst : List[Int] = cons 1 (cons 2 (cons 3 nil));
            lst[[IEval, IEval], [IPrint, IPrint]]<EvalListAlg, PrintListAlg>
\end{lstlisting}
\begin{lstlisting}[numbers=none]
AFTER:      type IEval = { eval : Int };
            type IPrint = { print : String };
            type ListAlg[A, L] = {
                nil(*$\ \ $*): L,
                cons : A -> L -> L
            };
            let SumListAlg = {
                nil(*$\ \ $*)= { eval = 0 },
                cons = \(x : IEval) -> \(y : IEval) -> { eval = x.eval + y.eval }
            };
            let PrintListAlg = {
                nil(*$\ \ $*)= { print = "" },
                cons = \(x : IPrint) -> \(y : IPrint) -> { print = "\{x.print} \{y.print}" }
            };
            type List[A] = { accept : forall L. ListAlg[A, L] -> L };
            let lst = {
                accept = /\L -> \(alg : ListAlg[Int, L]) -> alg.cons 1 (alg.cons 2 (alg.cons 3 alg.nil))
            };
            (lst.accept[IEval, IEval] SumListAlg) ,, (lst.accept[IPrint, IPrint] PrintListAlg)
\end{lstlisting}

% Transformation?

% End edit to here
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{spacing}
\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-03-20 paper/computePositions.rb

@@ -1,0 +1,71 @@
+#require 'tempfile'
+require 'fileutils'
+
+# Example 1 - Read File and close
+def scan(fileName, beginpos, endpos, fileloc)
+  file = File.new(fileName, "r")
+  counter = 1
+  while (line = file.gets)
+    if line =~ /BEGIN_(\w+)/
+      throw "Symbol '#{$1}' already defined" if fileloc[$1]
+      fileloc[$1] = fileName
+      beginpos[$1] = counter+1
+      puts "BEGIN #{$1}: #{beginpos[$1]}"
+    end
+    if line =~ /END_(\w+)/
+      endpos[$1] = counter-1
+      puts "END #{$1}: #{endpos[$1]}"
+    end
+    counter = counter + 1
+  end
+  file.close
+end
+
+def process(file, out, beginpos, endpos, fileloc)
+  while (line = file.gets)
+    if line =~ /APPLY:(\w+)=(\w+)/
+      var = $1
+      label = $2
+      line = line.sub( /#{var}=([0-9-]*)/, "#{var}=#{beginpos[label]}-#{endpos[label]}" )
+      line = line.sub( /\{[^{]*\}/, "{#{fileloc[label]}}" )
+    end
+    out.write(line)
+  end
+  file.close
+  out.close
+end
+
+fileloc = {}
+beginpos = {}
+endpos = {}
+
+Dir['../UseMixinLombok/src/*/*.java'].each do |file| 
+  scan(file, beginpos, endpos, fileloc)
+end
+
+Dir['../UseMixinLombok/src/*/*/*.java'].each do |file| 
+  scan(file, beginpos, endpos, fileloc)
+end
+
+Dir['../UseMixinLombok/src/*/*/*/*.java'].each do |file| 
+  scan(file, beginpos, endpos, fileloc)
+end
+
+Dir['*.tex'].each do |file| 
+  #temp = Tempfile.new('compute_positions')
+  tempname = "footempfile.txt"
+  temp = File.new(tempname, "w")
+  process(File.new(file, "r"), temp, beginpos, endpos, fileloc)
+  FileUtils.cp(file, "#{file}-old")
+  FileUtils.cp(tempname, file)
+end
+
+Dir['*/*.tex'].each do |file| 
+  #temp = Tempfile.new('compute_positions')
+  tempname = "footempfile.txt"
+  temp = File.new(tempname, "w")
[…]

### 2017-03-20 paper/sections/Formalization.tex
Tex.

\section{Formalization}

\begin{itemize}
	\item Syntax + typing rules + Semantics + Auxiliary definitions
	\item Implementation: a simple type checker + interpreter in Scala
\end{itemize}

\subsection{Syntax}
See Figure~\ref{fig:syntax}.

\begin{figure*}[htbp]
\begin{displaymath}
\begin{array}{l}
\begin{array}{llrl}
\text{Interfaces}   & IL & \Coloneqq & \interface{I}{I}{M} \\
\text{Methods}      & M  & \Coloneqq & \method{I}{m}{I}{x}{J}{e} \\
\text{Expressions}  & e  & \Coloneqq & x \mid
e.m(\overline{e}) \mid
\new{I} \mid
e.I::m(\overline{e}) \mid
\kwsuper.I::m(e) \\
\text{Context}      & \Gamma & \Coloneqq & x_1:I_1 ... x_n:I_n \\
\text{\red{Values}}       & v & \Coloneqq & <I>\new{C}
\end{array}
\end{array}
\end{displaymath}
\caption{Syntax.}\label{fig:syntax}
\end{figure*}

\subsection{Subtyping}
See Figure~\ref{fig:subtyping}.

\begin{figure*}[htbp]
\begin{mathpar}
	\subid \\
	\subtrans \\
	\subextends
\end{mathpar}
\caption{Subtyping.}\label{fig:subtyping}
\end{figure*}

\subsection{Typing Rules}
See Figure~\ref{fig:typingrules}.

\begin{figure*}[htbp]
\begin{mathpar}
	\tvar \\
	\tinvk \\
	\tpathinvk \\
	\tsuperinvk \\
	\tnew \\
	\tmethod \\
	\tintf
\end{mathpar}
\caption{Typing rules.}\label{fig:typingrules}
\end{figure*}

\subsection{Small-step Semantics}
See Figure~\ref{fig:smallstep}.

\begin{figure*}[htbp]
\begin{mathpar}
	\sinvk \\
	\spathinvk \\
	\ssuperinvk
\end{mathpar}
\caption{Small-step semantics.}\label{fig:smallstep}
\end{figure*}

\subsection{Congruence}
See Figure~\ref{fig:congruence}.

\begin{figure*}[htbp]
\deff
\begin{mathpar}
	\creceiver \\
	\red{\cpathreceiver} \\
	\red{\cargs} \\
	\red{\cpathargs} \\
	\red{\csuperargs} \\
	\cstatictype \\
	\cfreduce \\
	\cannoreduce
\end{mathpar}
\caption{Congruence.}\label{fig:congruence}
\end{figure*}

\subsection{Auxilary Definitions}

\subsubsection{\mbody}
\begin{mathpar}
	\inferrule* [left=]
	{C \{ m() \; \kwoverride \; C ... \} }
	{\mbody(m, C, A) = (\overline{X} \; \overline{x}, E \; e_0) \text{ IN } C}

	\inferrule* [left=]
	{C \{ m() \; \kwoverride \; A ... \} }
	{\mbody(m, C, A) = (\overline{X} \; \overline{x}, E \; e_0) \text{ IN } C}

	\inferrule* [left=]
	{   \mbody(m, C) = \{ A.m(), B.m(), ...\}
		\\ \nexists \; C.m()}
	{\mbody(m, C, A) = (\overline{X} \; \overline{x}, E \; e_0) \text{ IN } A}
\end{mathpar}

$$\interface{I}{I}{M}$$

$mbody(m, I)$ algorithm:
\begin{itemize}
	\item If m is defined in I directly, then return I.m()
	\item Else, let $\overline{I'} = mdefined(fathers(I))$, all ancestors of $I$ that has directly defined $m()$.
	\item $\overline{I''} = needed(\overline{I'})$, keep only interfaces that are needed, which are not super-interface of others.
	\item If $\overline{I''}$ is unique, then return this unique one. Else if any two I1,I2 in $\overline{I''}$ share a parent in $\overline{I'}$, then diamond conflict is detected, report error. Else return multiple $m()$s.
\end{itemize}

\subsubsection{\mtype}
$\mtype(m, C)$ algorithm:
\begin{itemize}
	\item If the result of $\mbody(m, C, A)$ is a unique method,\\
	$\method{I_0}{m}{I}{x}{J}{e_0}$,\\
	then $\mtype(m, C) = \overline{I} \to I_0$
	\item Else ($\Undefined$ or multiple methods returned), $\mtype(m, C) = \Error$
\end{itemize}

\subsubsection{\ext}
\ext(I,J) means interface $I$ (directly) extends $J$.
\begin{mathpar}
	\inferrule* [left=]
	{   \interface{I}{I}{M}
		\\ J \in \overline{I} }
	{\ext(I, J) = \kwtrue}      \\

	\inferrule* [left=]
	{}
	{\ext(I, J) = \kwfalse}
\end{mathpar}

\subsubsection{\collectMethods}
\[ \collectMethods(I) = \left( \bigcup_{I_i \in \overline{I}} \methods(I_i) \right) \bigcup \methods(I) \]
\[ \methods(I) = \overline{M}, \text{where } IT(I) = \interface{I}{I}{M} \]

\subsubsection{\needed}

\subsubsection{\only}
$\only(m, I)$ is true iff inside $I$ there is only one (direct) methoed $m$ definition.

### 2017-03-20 paper/sections/Overview.tex
Tex.

\section{Overview}

\begin{itemize}
	\item Code for the problem (Draw example)
	\item Potential fixes (renaming, traits, ....)
	\item How it is solved with our language (client code, simple explanation) + show update
\end{itemize}

### 2017-03-20 paper/sections/RelatedWork.tex
Tex.

\section{Related Work}

\begin{itemize}
	\item Multiple inheritance models
		\begin{itemize}
			\item Mixin
			\item Scala Mixins
			\item trait
			\item C++ model
			\item Java 8
			\item CZ
		\end{itemize}
	\item Resolve unintended method confliction
		\begin{itemize}
			\item Parents are Shared Parts of Objects: Inheritance and Encapsulation in SELF* (tiebreaker rule)
			\item ???
		\end{itemize}
	\item Static+Dynamic type method lookup (any existing language that supports this?)
	\item Formalization based on FJ (novelty: keep static types <I> in formalization)
		\begin{itemize}
			\item Existing formalizations based on FJ proposed new features and added rules in syntax and semantics. But we not only add rules, but also piggyback static types on almost all semantic rules to model method lookup. 
			\item Featherweight defenders, ...
		\end{itemize}
\end{itemize}

### 2017-03-28 paper/sections/Overview.tex
changes..

@@
 \end{itemize}
+
+\begin{lstlisting}
+interface Deck {
+   draw();  // draws a card from the Deck
+}
+
+interface Drawable {
+   draw();  // draws something on the screen
+}
+
+interface DrawableDeck extends Deck, Drawable {
+   ...
+} 
+\end{lstlisting}
+
+\subsection{Potential fixes}
+
+\begin{itemize}
+    \item Explicit override m() in C.
+    \item Choose one (such as Mixin model).
+    \item With Traits: method exclusion.
+    \item With Traits: method rename.
+\end{itemize}
+In previous solutions, only renaming can preserve the two different methods m(), 
+but it’s cumbersome to do in practice: new names have to be introduced, and (probably) need to prefer one over another. 
+Other solutions only preserve one method. Can we keep both methods without renaming?
+
+\subsection{Solution in our language}
+\begin{lstlisting}
+
+\end{lstlisting}
+
+\subsection{Method refinement}

### 2017-04-01 paper/sections/Formalization.tex
changes..
A bit.
minor changes
Fix.

@@
 \text{Context}      & \Gamma & \Coloneqq & x_1:I_1 ... x_n:I_n \\
-\text{\red{Values}}       & v & \Coloneqq & <I>\new{C}
+\text{\red{Values}}       & v & \Coloneqq & <J>\new{I}
 \end{array}
@@
 	\inferrule* [left=]
-	{C \{ m() \; \kwoverride \; C ... \} }
-	{\mbody(m, C, A) = (\overline{X} \; \overline{x}, E \; e_0) \text{ IN } C}
-
-	\inferrule* [left=]
-	{C \{ m() \; \kwoverride \; A ... \} }
-	{\mbody(m, C, A) = (\overline{X} \; \overline{x}, E \; e_0) \text{ IN } C}
-
-	\inferrule* [left=]
-	{   \mbody(m, C) = \{ A.m(), B.m(), ...\}
-		\\ \nexists \; C.m()}
-	{\mbody(m, C, A) = (\overline{X} \; \overline{x}, E \; e_0) \text{ IN } A}
+	{  \mostSpecific(m, I_d, I_s) = \{I\} \\
+		\mostSpecific_3(m, I_d, I) = \{J\} \\
+		\kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{E}{m}{X}{x}{I}{e_0}...\}}
+	{\mbody(m, I_d, I_s) = (\overline{X} \; \overline{x}, E \; e_0)}
 \end{mathpar}
 
-$$\interface{I}{I}{M}$$
-
+\begin{comment}
 $mbody(m, I)$ algorithm:
@@
 \end{itemize}
+\end{comment}
+
+\subsubsection{\mostSpecific}
+\begin{mathpar}	
+	\inferrule* [left=]
+	{ set = \; $\{$ K <: J \; $and$ \; K >: I \; | \; m \in dom(K) \} }
+	{\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
+				$prune(set)$ & if $set$ is not empty \\ $\mostSpecific_2(m, J)$ & otherwise
+			\end{tabular}}\right.}
+
+	\inferrule* [left=]
+	{ set = \; $\{$ K >: I \; | \; m \in dom(K) \} }
+	{\mostSpecific_2(m, I) = prune(set)}
+
+	\inferrule* [left=]
+	{ set = \; $\{$ K <: J \; $and$ \; K \neq J \; $and$ \; K >: I \; | \\
+		\kwinterface \; K \; \kwextends \; \overline{K} \; \{ E \; m(\overline{X} \; \overline{x}) \;
+		\kwoverride \; J ... \}  $\}$ }
+	{\mostSpecific_3(m, I, J) = prune(set)}
+\end{mathpar}
+
+$$ prune(set) = \{I \in set \; | \; \nexists J \in set, J <: I, J \neq I \} $$
 
@@
 $\only(m, I)$ is true iff inside $I$ there is only one (direct) methoed $m$ definition.
+
+\subsection{\pathcheck}
+$$\forall P \in getSupTypes(I)$$
+
+\begin{align*}
+ set = \{ class | class \in getSupTypes(I) 
+		\\ class.m \text{ defined in its body }
+		\\ class <: P \}
+\end{align*}
+
+$$ prune(set) = \{x \in set | \nexists y \in set, y <: x, y \neq x \} $$
+$$ |prune(set)| <= 1 $$

### 2017-04-01 paper/sections/Formalization.tex
Done rule fixes.
More.

@@
 
-\begin{itemize}
-	\item Syntax + typing rules + Semantics + Auxiliary definitions
-	\item Implementation: a simple type checker + interpreter in Scala
-\end{itemize}
+In this section, we present a formalization of our MIM calculus, based on
+a minimal subset of Java 8 interfaces. The syntax, typing rules and small-step
+semantics are included below.
 
 \subsection{Syntax}
-See Figure~\ref{fig:syntax}.
+Figure~\ref{fig:syntax} shows the syntax of MIM. The multiple inheritance feature
+of MIM has a basis on Java interfaces. To demonstrate how unintentional method conflicts
+are untangled in MIM, we present the calculus in a straightforward way, hence we only
+focus on a small subset of the interface model. For example, all the methods declared in an
+interface are default methods, that is to say, they always provide default implementations.
+From this point we can view that we are actually modelling a class model that supports multiple
+inheritance. Then it is straightforward to do object creation like ``\new I''. Fields and
+primitive types are not modelled as well.
+
+We use uppercase letters like $I, J, K$ to represent identifiers for interfaces. By multiple inheritance,
+an interface can have a set of super interfaces, where such a set can be empty. Inside an interface are a
+set of method declarations. Each method body holds a return statement. As seen in Figure~\ref{fig:syntax},
+we have introduced the \kwoverride keyword to override an old implementation of the method. If the interface
+that it overrides is exactly the enclosing interface, then such a method is seen as ``originally defined''.
+Again for simplicity, overloading is not modelled for methods, which implies we can uniquely identify a method
+by its name.
+
+An expression can be a variable, a method invocation, an object creation, furthermore, a path-invocation like
+``$e.I::m(\overline{e})$'', meaning that the dynamically binded implementation for method $m$ should be along
+the path $I$. Another case is the super-invocation, enabling a method to access an old implementation from the
+specified super type. Hence a super-invocation can only be used inside an interface definition. Finally an expression
+can also be a value ``$<I> \new J$''. It is exactly an object instance of $J$ with annotated static type $I$.
+Note that values are only intended for the small-step semantics of MIM, hence they are not supposed to appear in the source program.
 
@@
 e.I::m(\overline{e}) \mid
-\kwsuper.I::m(e) \\
+\kwsuper.I::m(e) \; \red{\mid} \; \red{v^*} \\
 \text{Context}      & \Gamma & \Coloneqq & x_1:I_1 ... x_n:I_n \\
-\text{\red{Values}}       & v & \Coloneqq & <J>\new{I}
+\text{\red{Values}}       & v & \Coloneqq & <I>\new{J} \\
+\\
+\text{Interface names} & I, J, K & & \\
+\text{Method names} & m & & \\
+\text{Variable names} & x & &
 \end{array}
@@
 \end{displaymath}
-\caption{Syntax.}\label{fig:syntax}
+\caption{Syntax. \red{*: only intended for semantic rules.}}\label{fig:syntax}
 \end{figure*}
@@
 \begin{mathpar}
-	\subid \\
-	\subtrans \\
-	\subextends
+	\framebox{$ I <: J $} \hspace{.5in} \subid \\
+	\subtrans \hspace{.5in} \subextends
 \end{mathpar}
@@
 \begin{mathpar}
+	\framebox{$ \judgeewf \Gamma {e:I} $} \hspace{.5in}
 	\tvar \\
@@
 \begin{mathpar}
+	\framebox{$ e \rightarrow v $} \hspace{.5in}
 	\sinvk \\
@@
 \begin{figure*}[htbp]
-\deff
 \begin{mathpar}
-	\creceiver \\
+	\creceiver \hspace{.5in}
 	\red{\cpathreceiver} \\
@@
 \end{mathpar}
-\caption{Congruence.}\label{fig:congruence}
+\caption{Congruence. \haoyuan{How are the last two rules used?}}\label{fig:congruence}
 \end{figure*}
@@
 
-\subsubsection{\mbody}
+\begin{figure*}[htbp]
 	\begin{mathpar}
@@
 			\mostSpecific_3(m, I_d, I) = \{J\} \\
-		\kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{E}{m}{X}{x}{I}{e_0}...\}}
-	{\mbody(m, I_d, I_s) = (\overline{X} \; \overline{x}, E \; e_0)}
+			\kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_E}{m}{I_X}{x}{I}{e_0}\ldots\}}
+		{\mbody(m, I_d, I_s) = (\overline{I_X} \; \overline{x}, I_E \; e_0)}
+
+	\inferrule* [left=]
+	{ set = \; $\{$ K <: J \; $and$ \; K >: I \; | \; m \in dom(K) \} }
+	{\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
+				$prune(set)$ & if $set$ is not empty \\ $\mostSpecific_2(m, J)$ & otherwise
+			\end{tabular}}\right.}
+	\inferrule* [left=]
+		{ set = \; $\{$ K >: I \; | \; m \in dom(K) \} }
+		{\mostSpecific_2(m, I) = prune(set)}
+
+	\inferrule* [left=]
+		{ set = \; $\{$ K <: J \; $and$ \; K >: I \; | \;
+			\kwinterface \; K \; \kwextends \; \overline{K} \; \{ I_E \; m(\overline{I_X} \; \overline{x}) \;
+			\kwoverride \; J \ldots \}  $\}$ }
+		{\mostSpecific_3(m, I, J) = prune(set)}
+
+	prune(set) = \{I \in set \; | \; \nexists J \in set, J <: I, J \neq I \}
+
+	\inferrule* [left=]
+	{   \interface{I}{I}{M}
+		\\ J \in \overline{I} }
+	{\ext(I, J)}
 	\end{mathpar}
+	\caption{Auxiliary functions.}\label{fig:auxfunc}
+\end{figure*}
+
+\subsubsection{\mbody}
+
+$\mbody(m, I_d, I_s)$, as defined in Figure~\ref{fig:auxfunc}, denotes a method lookup function.
+We use $I_d, I_s$, since $\mbody$ is usually invoked by a receiver of a method $m$, with its dynamic
+type $I_d$ and static type $I_s$. Such a function returns the most specific method implementation, more
+accurately, its parameters, returned expression and the types.
+
+To calculate $\mbody(m, I_d, I_s)$:
+\begin{itemize}
+	\item First, an auxiliary function $\mostSpecific(m, I_d, I_s)$ returns the set of interfaces that
+	originally defines the most specific implementations of method $m$. We use another helper function $prune$ to ensure that none of those implementations overrides one another.
+	\item If $\mostSpecific$ returns a singleton set $\{I\}$, then it is good, otherwise $\mbody$ is undefined in
+	this case.
+The set $\{I\}$ implies that we will use the $m$ from $I$ without ambiguity.
+But moreover, we have to invoke $\mostSpecific_3(m, I_d, I)$, to check if there are updated versions of $m$ between $I_d$ and $I$.
+Again we forbid ambiguity, so the expected set after pruning is also a singleton set $\{J\}$.
+	\item Finally, we fetch the implementation of $m$ in interface $J$ and return.
+\end{itemize}
 
@@
 \subsubsection{\mostSpecific}
-\begin{mathpar}	
-	\inferrule* [left=]
-	{ set = \; $\{$ K <: J \; $and$ \; K >: I \; | \; m \in dom(K) \} }
-	{\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
-				$prune(set)$ & if $set$ is not empty \\ $\mostSpecific_2(m, J)$ & otherwise
-			\end{tabular}}\right.}
 
-	\inferrule* [left=]
-	{ set = \; $\{$ K >: I \; | \; m \in dom(K) \} }
-	{\mostSpecific_2(m, I) = prune(set)}
-
-	\inferrule* [left=]
-	{ set = \; $\{$ K <: J \; $and$ \; K \neq J \; $and$ \; K >: I \; | \\
-		\kwinterface \; K \; \kwextends \; \overline{K} \; \{ E \; m(\overline{X} \; \overline{x}) \;
-		\kwoverride \; J ... \}  $\}$ }
-	{\mostSpecific_3(m, I, J) = prune(set)}
-\end{mathpar}
-
-$$ prune(set) = \{I \in set \; | \; \nexists J \in set, J <: I, J \neq I \} $$
+\haoyuan{TODO}
 
@@
 \ext(I,J) means interface $I$ (directly) extends $J$.
-\begin{mathpar}
-	\inferrule* [left=]
-	{   \interface{I}{I}{M}
-		\\ J \in \overline{I} }
-	{\ext(I, J) = \kwtrue}      \\
-
-	\inferrule* [left=]
-	{}
-	{\ext(I, J) = \kwfalse}
-\end{mathpar}
 
@@
 
-\subsection{\pathcheck}
-$$\forall P \in getSupTypes(I)$$
-
-\begin{align*}
- set = \{ class | class \in getSupTypes(I) 
-		\\ class.m \text{ defined in its body }
-		\\ class <: P \}
-\end{align*}
-
-$$ prune(set) = \{x \in set | \nexists y \in set, y <: x, y \neq x \} $$
-$$ |prune(set)| <= 1 $$
+\begin{itemize}
+	\item Syntax + typing rules + Semantics + Auxiliary definitions
+	\item Implementation: a simple type checker + interpreter in Scala
+\end{itemize}

### 2017-04-02 paper/sections/Formalization.tex
Small fix.
More.

@@
 \begin{mathpar}
-	\framebox{$ e \rightarrow v $} \hspace{.5in}
 	\sinvk \\
@@
 \end{mathpar}
-\caption{Congruence. \haoyuan{How are the last two rules used?}}\label{fig:congruence}
+\caption{Congruence.}\label{fig:congruence}
 \end{figure*}
@@
 \subsection{Auxilary Definitions}
+
+To make our formalization concise and expressive, we have defined a list of
+auxiliary functions, collected by Figure~\ref{fig:auxfunc}. To begin with, we
+introduce the basic functions: $\ext, \updateSet$ and $\prune$. $\ext(I, J)$
+simply indicates that interface $I$ directly extends interface $J$. Corresponding
+to this is a more general case $I <: J$, meaning that $I$ is a subtype of $J$.
+$\updateSet(I, J)$ returns a set of methods defined in $I$ that have ``$\kwoverride \; J$''
+in their signatures. Notice that $\updateSet(I, I)$ is a special representative of
+the ``originally-defined'' method set from $I$. The $\prune$ function takes a set of
+types, and filters out those that have subtypes in the same set. Finally in the returned set,
+none of them has a subtyping to one another, since all super types have been removed.
 
@@
 	\inferrule* [left=]
-	{ set = \; $\{$ K <: J \; $and$ \; K >: I \; | \; m \in dom(K) \} }
+	{ set = \; \{ K <: J \; $and$ \; K >: I \; | \; m \in \updateSet(K, K) \} }
 	{\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
@@
 	\inferrule* [left=]
-		{ set = \; $\{$ K >: I \; | \; m \in dom(K) \} }
+		{ set = \; \{ K >: I \; | \; m \in \updateSet(K, K) \} }
 		{\mostSpecific_2(m, I) = prune(set)}
@@
 	\inferrule* [left=]
-		{ set = \; $\{$ K <: J \; $and$ \; K >: I \; | \;
-			\kwinterface \; K \; \kwextends \; \overline{K} \; \{ I_E \; m(\overline{I_X} \; \overline{x}) \;
-			\kwoverride \; J \ldots \}  $\}$ }
+		{ set = \; \{ K <: J \; $and$ \; K >: I \; | \;
+			m \in \updateSet(K, J)  \} }
 		{\mostSpecific_3(m, I, J) = prune(set)}
@@
 	{\ext(I, J)}
+
+	\inferrule* [left=]
+	{   \kwinterface \; I \; \kwextends \; \overline{I} \; \{ I_E \; m(\overline{I_X} \; \overline{x}) \;
+		\kwoverride \; J \ldots \} }
+	{m \in \updateSet(I, J)}
 	\end{mathpar}
@@
 
-$\mbody(m, I_d, I_s)$, as defined in Figure~\ref{fig:auxfunc}, denotes a method lookup function.
+$\mbody(m, I_d, I_s)$, as defined in Figure~\ref{fig:auxfunc}, denotes a method body lookup function.
 We use $I_d, I_s$, since $\mbody$ is usually invoked by a receiver of a method $m$, with its dynamic

### 2017-04-02 paper/sections/Formalization.tex
more.
Added an example.

@@
 \subsection{Subtyping}
-See Figure~\ref{fig:subtyping}.
+See Figure~\ref{fig:subtyping}. \haoyuan{TODO}
 
@@
 \subsection{Typing Rules}
-See Figure~\ref{fig:typingrules}.
+See Figure~\ref{fig:typingrules}. \haoyuan{TODO}
 
@@
 \subsection{Small-step Semantics}
-See Figure~\ref{fig:smallstep}.
+See Figure~\ref{fig:smallstep}. \haoyuan{TODO}
 
@@
 \subsection{Congruence}
-See Figure~\ref{fig:congruence}.
+See Figure~\ref{fig:congruence}. \haoyuan{TODO}
 
@@
 \subsubsection{\mtype}
-$\mtype(m, C)$ algorithm:
-\begin{itemize}
-	\item If the result of $\mbody(m, C, A)$ is a unique method,\\
-	$\method{I_0}{m}{I}{x}{J}{e_0}$,\\
-	then $\mtype(m, C) = \overline{I} \to I_0$
-	\item Else ($\Undefined$ or multiple methods returned), $\mtype(m, C) = \Error$
-\end{itemize}
 
-\subsubsection{\ext}
-\ext(I,J) means interface $I$ (directly) extends $J$.
+\haoyuan{TODO. mtype(m, I) from mbody(I, I).}
 
+\begin{comment}
 \subsubsection{\collectMethods}
@@
 \[ \methods(I) = \overline{M}, \text{where } IT(I) = \interface{I}{I}{M} \]
-
-\subsubsection{\needed}
-
-\subsubsection{\only}
-$\only(m, I)$ is true iff inside $I$ there is only one (direct) methoed $m$ definition.
+\end{comment}
 
@@
 \end{itemize}
+
+\subsubsection{A Non-Trivial Example}
+
+\[
+\begin{array}{l}
+\kwinterface \; A \; \kwextends \; \{ \\
+\; \; \; \; A \; m() \; \kwoverride \; A \; \{\kwreturn \; \new A;\} \\
+\} \\
+\\
+\kwinterface \; B \; \kwextends \; A \; \{ \\
+\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new B;\} \\
+\} \\
+\\
+\kwinterface \; C \; \kwextends \; A \; \{ \\
+\; \; \; \; A \; m() \; \kwoverride \; C \; \{\kwreturn \; \new C;\} \\
+\} \\
+\\
+\kwinterface \; D \; \kwextends \; B, \; C \; \{ \\
+\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new D;\} \\
+\} \\
+\\
+\kwinterface \; E \; \kwextends \; B \; \{ \\
+\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new E;\} \\
+\} \\
+\\
+\kwinterface \; F \; \kwextends \; D, \; E \; \{ \\
+\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new F;\} \\
+\; \; \; \; A \; n(B \; b) \; \kwoverride \; F \; \{\kwreturn \; b.m();\} \\
+\} \\
+\\
+\new F.n(\new F)
+\end{array}
+\]
+
+~\haoyuan{Unfortunately I think this example shows that it is hard to reuse
+	$D.m$ on path $B$ and $E.m$ on path $B$ in $F$?}
+
+\haoyuan{We can use the $\kwsuper$ keyword to access the originally defined methods
+	in super types, but we cannot access the old updating methods.}
+
+\haoyuan{Just like $\kwsuper.I::m()$ is equivalent to $\new I.m()$, maybe we can add
+a degree of freedom to $\kwsuper$, for example, $\kwsuper.D::B::m()$ is equivalent to
+$\new D.B::m()$, so we can use $\kwsuper.D::B::m()$ and $\kwsuper.E::B::m()$ inside interface $F$ for code reuse?}
+
+Interfaces $A,B,C,D,E,F$ OK in type checking.
+
+To type-check $\new F.n(\new F)$:
+\begin{itemize}
+	\item By (T-INVK), we need to calculate $\mtype(n, F)$.
+	\item $\mtype(n, F) = B \to A$. And $\new F : B$.
+	\item $\new F.n(\new F) : A$.
+\end{itemize}
+
+~
+
+To compute \red{$\new F.n(\new F)$}:
+\begin{itemize}
+	\item By (C-RECEIVER), we compute \red{$\new F$}:
+		\begin{itemize}
+			\item By (C-STATICTYPE): \red{$<F> \new F$}.
+		\end{itemize}
+	\item By (C-ARGS), we compute \red{$\new F$}:
+		\begin{itemize}
+			\item By (C-STATICTYPE): \red{$<F> \new F$}.
+		\end{itemize}
+	\item Now we get \red{$(<F> \new F).n(<F> \new F)$}. By (S-INVK):
+		\begin{itemize}
+			\item Compute $\mbody(n, F, F) = \red{(B \; b, A \; b.m())}$.
+			\item Replace \red{$b$} with \red{$<B> \new F$} in \red{$b.m()$}.
+			\item Replace \red{$\kwthis$} with \red{$<F> \new F$} in \red{$b.m()$}.
+		\end{itemize}
+	\item Finally we get \red{$<A>((<B> \new F).m())$}.
+	\item By (C-FREDUCE), we first compute \red{$(<B> \new F).m()$}:
+		\begin{itemize}
+			\item By (S-INVK), we compute \red{$\mbody(m, F, B)$}.
+			\item In $\mbody$, we invoke \red{$\mostSpecific(m, F, B)$}.
+			\item In $\mostSpecific$, \red{$set = \{B\}$, $\prune(set) = \{B\}$}.
+			\item Back to $\mbody$, we invoke \red{$\mostSpecific_3(m, F, B)$}.
+			\item In $\mostSpecific_3$, \red{$set = \{B,D,E,F\}$, $\prune(set) = \{F\}$}.
+			\item Back to $\mbody$, we check \red{$F.m$} and return \red{$(-,A \; (\new F))$}.
+			\item Back to (S-INVK).
+			\item Replace \red{$\kwthis$} with \red{$<B> \new F$} in \red{$\new F$}.
+			\item Finally we get \red{$<A> \new F$}.
+		\end{itemize}
+	\item Now we have \red{$<A>(<A> \new F)$}.
+	\item By (C-ANNOREDUCE): \red{$<A> \new F$}.
+\end{itemize}

### 2017-04-03 paper/sections/Formalization.tex
Fix.

@@
 		{  \mostSpecific(m, I_d, I_s) = \{I\} \\
-			\mostSpecific_3(m, I_d, I) = \{J\} \\
+			\mostSpecific_2(m, I_d, I) = \{J\} \\
 			\kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_E}{m}{I_X}{x}{I}{e_0}\ldots\}}
@@
 	\inferrule* [left=]
-	{ set = \; \{ K <: J \; $and$ \; K >: I \; | \; m \in \updateSet(K, K) \} }
+	{ set1 = \; \{ K <: J \; $and$ \; K >: I \; | \; m \in \updateSet(K, K) \} \\
+		set2 = \; \{ K >: J \; | \; m \in \updateSet(K, K) \} }
 	{\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
-				$prune(set)$ & if $set$ is not empty \\ $\mostSpecific_2(m, J)$ & otherwise
+				$prune(set1)$ & if $set1$ is not empty \\ $prune(set2)$ & otherwise
 			\end{tabular}}\right.}
-	\inferrule* [left=]
-		{ set = \; \{ K >: I \; | \; m \in \updateSet(K, K) \} }
-		{\mostSpecific_2(m, I) = prune(set)}
 
@@
 			m \in \updateSet(K, J)  \} }
-		{\mostSpecific_3(m, I, J) = prune(set)}
+		{\mostSpecific_2(m, I, J) = prune(set)}
 

### 2017-05-05 paper/sections/Formalization.tex
TODO.
fix
formalization text

@@
 \text{Interfaces}   & IL & \Coloneqq & \interface{I}{I}{M} \\
-\text{Methods}      & M  & \Coloneqq & \method{I}{m}{I}{x}{J}{e} \\
+\text{Methods}      & M  & \Coloneqq & \method{I}{m}{I_x}{x}{J}{e} \\
 \text{Expressions}  & e  & \Coloneqq & x \mid
@@
 \kwsuper.I::m(e) \; \red{\mid} \; \red{v^*} \\
-\text{Context}      & \Gamma & \Coloneqq & x_1:I_1 ... x_n:I_n \\
+\text{Context}      & \Gamma & \Coloneqq & \overline{x:I} \\
 \text{\red{Values}}       & v & \Coloneqq & <I>\new{J} \\
@@
 
-\subsection{Subtyping}
-See Figure~\ref{fig:subtyping}. \haoyuan{TODO}
+\subsection{Subtyping and Typing Rules}
+See Figure~\ref{fig:subtyping}. 
+The subtyping of MIM consists of only a few rules shown in Figure ?.
+In short, subtyping relations are built from the inheritance in interface
+declarations. They hold both reflexivity and transitivity.
+
+Details of type-checking rules are displayed in Figure ?, including expression
+typing, well-formedness of methods and interfaces. As a convention, an environment
+$\Gamma$ is maintained to store the types of variables, together with ``this'' type, namely
+the enclosing type. The three rules for method invocation, (T-INVK), (T-PATHINVK) and (T-SUPERINVK)
+are very similar, in the sense that they all check the type of the specific method, by using
+an auxiliary function \mtype. \mtype is the function for looking up method types, which we will
+illustrate later. After the method type is obtained, they all check that arguments and the receiver
+have compatible types. Additionally, (T-PATHINVK) requires the receiver to be the subtype of the specified
+path type, and (T-SUPERINVK) checks if the enclosing type directly extends the specified super type.
+
+The method typing rule (T-METHOD) is more interesting, since the method update is taken into consideration.
+Besides that the static type of the return expression should be the subtype of the declared return type,
+we use another helper function \mostSpecific to ensure that the method update is legal. Briefly, $\mostSpecific(m, I, J)$
+returns a set of interfaces, and an interface is included if and only if: (1) it originally defines method $m$; (2) it is
+a supertype of $I$; (3) it is along path $J$, meaning that it is either a supertype or a subtype of $J$ (including $J$ itself);
+(4) it does not have a subtype in the same set, namely we filter out all super types.
+Hence by $\mostSpecific(m, I, J) = \{J\}$ we define the legality of method updating: the updated method must be an original method (not another method update), and method updating cannot cross over method overriding.
+
+Finally, (T-INTF) defines interface type-checking in a straightforward way.
 
@@
 \end{figure*}
-
-\subsection{Typing Rules}
-See Figure~\ref{fig:typingrules}. \haoyuan{TODO}
 
@@
 
-\subsection{Small-step Semantics}
-See Figure~\ref{fig:smallstep}. \haoyuan{TODO}
+\subsection{Small-step Semantics and Congruence}
+Figure ? and Figure ? define small-step semantic rules and congruence rules,
+respectively. When evaluating an expression, they are invoked recursively and
+alternately to produce a single value in the end. The small-step semantics (S-INVK), (S-PATHINVK) and (S-SUPERINVK) behave similarly, each corresponds to
+one kind of method invocation.
+They all invoke \mbody for method body lookup.
+Generally, one can understand $\mbody(m, I, J)$ in a way that it finds the most specific body of method $m$, when the receiver has dynamic type $I$ and static type $J$.
+The three rules require that the receiver and the arguments have been evaluated into values, before substitution is applied.
 
@@
 \end{figure*}
-
-\subsection{Congruence}
-See Figure~\ref{fig:congruence}. \haoyuan{TODO}
 
@@
 
-\haoyuan{TODO}
-
 \subsubsection{\mtype}
 
-\haoyuan{TODO. mtype(m, I) from mbody(I, I).}
+\red{TODO. mtype(m, I) from mbody(I, I).}
 
@@
 
-~\haoyuan{Unfortunately I think this example shows that it is hard to reuse
+~\red{Unfortunately I think this example shows that it is hard to reuse
 	$D.m$ on path $B$ and $E.m$ on path $B$ in $F$?}
 
-\haoyuan{We can use the $\kwsuper$ keyword to access the originally defined methods
+\red{We can use the $\kwsuper$ keyword to access the originally defined methods
 	in super types, but we cannot access the old updating methods.}
 
-\haoyuan{Just like $\kwsuper.I::m()$ is equivalent to $\new I.m()$, maybe we can add
+\red{Just like $\kwsuper.I::m()$ is equivalent to $\new I.m()$, maybe we can add
 a degree of freedom to $\kwsuper$, for example, $\kwsuper.D::B::m()$ is equivalent to
@@
 \end{itemize}
+
+\red{TODO: class encapsulation problem: interface A: m; interface B: m update A; interface C: m update B.}

### 2017-05-05 paper/sections/Formalization.tex
More formalization.

@@
 \subsection{Subtyping and Typing Rules}
-See Figure~\ref{fig:subtyping}. 
 The subtyping of MIM consists of only a few rules shown in Figure ?.
@@
 
-The method typing rule (T-METHOD) is more interesting, since the method update is taken into consideration.
-Besides that the static type of the return expression should be the subtype of the declared return type,
-we use another helper function \mostSpecific to ensure that the method update is legal. Briefly, $\mostSpecific(m, I, J)$
-returns a set of interfaces, and an interface is included if and only if: (1) it originally defines method $m$; (2) it is
-a supertype of $I$; (3) it is along path $J$, meaning that it is either a supertype or a subtype of $J$ (including $J$ itself);
-(4) it does not have a subtype in the same set, namely we filter out all super types.
-Hence by $\mostSpecific(m, I, J) = \{J\}$ we define the legality of method updating: the updated method must be an original method (not another method update), and method updating cannot cross over method overriding.
+The method typing rule (T-METHOD) is more interesting, since the method can either be an original implementation or a update.
+Besides static type-checking for the return expression,
+we further use the helper function $\mostSpecific$ to ensure that the method update is legal. The formal definition is available in Section ?
+By that we define the legality of method updating: the updated method must be an original method (not another method update), and method updating cannot cross over method overriding (a method overriding cannot appear between the method update and the updated original method in inheritance hierarchy).
 
@@
 
-\subsubsection{\mbody}
+\subsubsection{$\mostSpecific$ and $\mostSpecific_2$}
+
+$\mostSpecific$ is an auxiliary function that finds the most specific original implementations of a method.
+Let us consider $\mostSpecific(m, I, J)$, what it returns is a set of interfaces, each including its own $m$ as a most specific implementation.
+Such a set may contain several elements, but that implies ambiguity; what we expect is actually a singleton set.
+By the definition of $\mostSpecific$ shown in Figure ?, an interface belongs to the return set if and only if:
+\begin{itemize}
+	\item It has an original definition of $m$;
+	\item It is a supertype of $I$;
+	\item It is along path $J$, meaning that it is either a supertype or a subtype of $J$ (including $J$ itself);
+	\item It does not have a subtype in the same set, because we have used $prune$ to filter out all super types, as the most specific one is always in the sub-most type.
+\end{itemize}
+We could have put $set1$ and $set2$ together, but the current definition leads a clearer illustration.
+
+The $\mostSpecific$ function only focuses on original method implementations, all the method updates are omitted during that time.
+On the other hand, another auxiliary function $\mostSpecific_2(m, I, J)$ has the assumption that $J$ defines an original $m$, and this function tries to find the most specific implementations that update such an $m$.
+Just as $\mostSpecific$, $\mostSpecific_2$ also returns the set of interfaces after pruning.
+An interface belongs to the return set if and only if:
+\begin{itemize}
+	\item It is between $I$ and $J$;
+	\item It defines a method update for $J.m$;
+	\item It does not have a subtype in the same set.
+\end{itemize}
+The algorithm for finding the most specific method update is quite similar to that for most specific original method.
+A method update is not allowed to work on another method update, and one can hide another if their interfaces has subtyping relations.
+If they do not hide each other, the result implies ambiguity.
+
+\subsubsection{$\mbody$ and $\mtype$}
 
@@
 type $I_d$ and static type $I_s$. Such a function returns the most specific method implementation, more
-accurately, its parameters, returned expression and the types.
+accurately, its parameters, returned expression and the types. It considers both originally defined methods and method updates, so $\mostSpecific$ and $\mostSpecific_2$ are invoked.
 
@@
 \begin{itemize}
-	\item First, an auxiliary function $\mostSpecific(m, I_d, I_s)$ returns the set of interfaces that
-	originally defines the most specific implementations of method $m$. We use another helper function $prune$ to ensure that none of those implementations overrides one another.
+	\item First, it invokes $\mostSpecific(m, I_d, I_s)$ and returns a set.
 	\item If $\mostSpecific$ returns a singleton set $\{I\}$, then it is good, otherwise $\mbody$ is undefined in
@@
 The set $\{I\}$ implies that we will use the $m$ from $I$ without ambiguity.
-But moreover, we have to invoke $\mostSpecific_3(m, I_d, I)$, to check if there are updated versions of $m$ between $I_d$ and $I$.
+But moreover, we have to invoke $\mostSpecific_2(m, I_d, I)$, to check if there are updated versions of $m$ between $I_d$ and $I$.
 Again we forbid ambiguity, so the expected set after pruning is also a singleton set $\{J\}$.
-	\item Finally, we fetch the implementation of $m$ in interface $J$ and return.
+	\item Finally, we fetch the implementation of $m$ in interface $J$ and return its related information.
 \end{itemize}
+The definition of $\mtype$ simply relies on $\mbody$. In short,
+$$\mbody(m, I, I) = (\overline{I_x}\ \overline{x}, I_E\ e) \ \Longrightarrow\ \mtype(m, I) = \overline{I_x}\rightarrow I_E$$
 
@@
 \end{comment}
-
-\subsubsection{\mostSpecific}
-
-\subsubsection{\mtype}
-
-\red{TODO. mtype(m, I) from mbody(I, I).}
 

### 2017-05-19 paper/sections/Formalization.tex
fix
before format change

@@
 e.I::m(\overline{e}) \mid
-\kwsuper.I::m(e) \; \red{\mid} \; \red{v^*} \\
+\kwsuper.I::m(e) \; \mid \; v^* \\
 \text{Context}      & \Gamma & \Coloneqq & \overline{x:I} \\
-\text{\red{Values}}       & v & \Coloneqq & <I>\new{J} \\
+\text{Values}       & v & \Coloneqq & <I>\new{J} \\
 \\
@@
 \end{displaymath}
-\caption{Syntax. \red{*: only intended for semantic rules.}}\label{fig:syntax}
+\caption{Syntax. *: only intended for semantic rules.}\label{fig:syntax}
 \end{figure*}
@@
 	\creceiver \hspace{.5in}
-	\red{\cpathreceiver} \\
-	\red{\cargs} \\
-	\red{\cpathargs} \\
-	\red{\csuperargs} \\
+	\cpathreceiver \\
+	\cargs \\
+	\cpathargs \\
+	\csuperargs \\
 	\cstatictype \\
@@
 
+\newpage
+
 \subsubsection{A Non-Trivial Example}
 
+\begin{lstlisting}
+interface A extends {
+	A m() override A {return new A(); }
+}
+interface B extends A {
+	A m() override B {return new B(); }
+}
+interface C extends A {
+	A m() override C {return new C(); }
+}
+interface D extends B, C {
+	A m() override B {return new D(); }
+}
+interface E extends B {
+	A m() override B {return new E(); }
+}
+interface F extends D, E {
+	A m() override B {return new F(); } 
+	A n(B b) override F {return b.m(); }
+}
+new F().n(new F())
+\end{lstlisting}
+
+\begin{comment}
 \[
@@
 \]
+\end{comment}
 
@@
 \red{TODO: class encapsulation problem: interface A: m; interface B: m update A; interface C: m update B.}
+
+\subsection{Type Safety}
+
+\begin{theorem}[Subject Reduction]
+$\textit{If } \ \judgeewf \Gamma {e : I} \; \textit{ and } \ e \rightarrow e',\ 
+\textit{then } \judgeewf \Gamma {e' : I'} \ \textit{ for some } \ I' <: I.$
+\end{theorem}
+
+\begin{theorem}[Progress]
+$\textit{If } \ \judgeewf {} {e : I}, \textit{ then either } \ e 
+\textit{ is a value or there is an } e' \textit{ with } e \rightarrow e'.$
+\end{theorem}

### 2017-05-19 paper/sections/RelatedWork.tex
changes..
A bit.
before format change

@@
 \begin{itemize}
-	\item Multiple inheritance models
-		\begin{itemize}
-			\item Mixin
-			\item Scala Mixins
-			\item trait
-			\item C++ model
-			\item Java 8
-			\item CZ
-		\end{itemize}
-	\item Resolve unintended method confliction
-		\begin{itemize}
-			\item Parents are Shared Parts of Objects: Inheritance and Encapsulation in SELF* (tiebreaker rule)
-			\item ???
-		\end{itemize}
 	\item Static+Dynamic type method lookup (any existing language that supports this?)
@@
 \end{itemize}
+
+\subsection{Mainstream Multiple Inheritance Models}
+Multiple inheritance is a useful feature in object-oriented programming world although it's difficult to model and can 
+cause various problems (e.g. the diamond problem).  There are many existing languages/models that support multiple 
+inheritance, either coming with multiple inheritance capability or added through evolution. The Mixin model allows naming components 
+that can be applied to various classes as reusable functionality units. However, the linearization (total ordering) of mixin 
+inheritance cannot provide a satisfactory resolution in some cases and restricts the flexibility of mixin composition.
+
+Simplifying the mixins approach, traits~\cite{scharli03traits} draw a strong line between units of reuse and object factories. 
+Traits act as units of reuse, containing functionality code; while classes, assembled from traits, act as object factories.
+
+Java 8 interfaces are closely related to traits: concrete method implementations are allowed (via the default keyword) inside interfaces. 
+The introduction of default methods opens the gate for various flavors of multiple inheritance in Java.
+
+Malayeri and Aldrich proposed a model CZ~\cite{malayeri2009cz} which aims to do multiple inheritance without the diamond problem. 
+Inheritance is divided into two concepts: inheritance dependency and implementation inheritance. 
+Using a combination of requires and extends, a program with diamond inheritance is transformed to one without diamonds. 
+Moreover, fields and multiple inheritance can coexist. However untangling inheritance also untangles the class structure. 
+In CZ, not only the number of classes, but also the class hierarchy complexity increases.
+
+The above mentioned models/languages support multiple inheritance, and they handle method confliction in the same way: requiring 
+programmers to explicitly resolve ambiguity and disallowing two methods with the same signature from two different libraries 
+to co-exit.
+
+\subsection{Resolving Unintended Method Confliction}
+There are still a few languages that already realized the problem and explored a bit. We discuss them one by one.
+
+\noindent {\bf C++ model.}
+As discussed in Section~\ref{}, C++ supports very flexible inheritance mode and allows programmers to choose different 
+confliction resolution approaches via normal or virtual inheritance. Generally speaking, C++ model is much more complex 
+and flexible than our approach. For example, given the following code
+\begin{lstlisting}[language=Java]
+class A { public: void m() {cout << "MA" << endl;}};
+class B { public: void m() {cout << "MB" << endl;}};
+class C : public A, public B { 
+	void m() {cout << "MC" << endl;}
+};
+void func(A* a) { a->m(); }
+int main() {
+	C* c = new C();
+	c->B::m();
+	func(c); 
+	return 0; //Running result: MB MA
+}
+\end{lstlisting}
+The running result is $MB \; MA$, meaning that it looks at the static type when doing method lookup. However, we can alter the code 
+a little bit with virtual method and the result will be totally different:
+\begin{lstlisting}
+class A { 
+	public: virtual void m() {cout << "MA" << endl;}
+};
+class B { 
+	public: virtual void m() {cout << "MB" << endl;}
+};
+class C : public A, public B { 
+    public: virtual void m() {cout << "MC" << endl;}
+};
+void func(A* a) { a->m(); }
+int main() {
+	C* c = new C();
+	c->B::m();
+	func(c); 
+	return 0; //Running result: MB MC
+}
+\end{lstlisting}
+Now the running result will be $MB \; MC$. With virtual method, method lookup algorithm will find the most specific 
+method definition of $m$, which is the definition in class $C$. Although C++ support this flexibility, it does not 
+support updating both $A.m$ and $B.m$ in class $C$.
+
+\begin{lstlisting}
+\end{lstlisting}
+
+\noindent  {\bf C\# Explicit method implementation.}
+Explicit method implementation is a special feature supported by \csharp. As described in \csharp
+tutorial~\cite{}, a class that implements an interface can explicitly implement a member of that
+interface. When a member is explicitly implemented, it can only be accessed through an instance
+of the interface. Explicit interface implementation allows the programmer to inherit two interfaces 
+that share the same member names and give each interface member a separate implementation. 
+Explicit interface member implementations have two advantages:
+Explicit interface member implementations allow interface implementations to be excluded 
+from the public interface of a class. This is particularly useful when a class implements an internal 
+interface that is of no interest to a consumer of that class or struct.
+Explicit interface member implementations allow disambiguation of interface members with the 
+same signature. This is the the advantage that is similar to ours' model. However, there are two 
+diffirencies: firstly, method (default) implementations are not allowed in \csharp interfaces; 
+secondly, when handling unintended method confliction, multi-way method updating is not supported 
+in \csharp.
+
+\begin{lstlisting}
+\end{lstlisting}
+
+\noindent {\bf Self.} In the prototype-based language \self~\cite{Chambers1991}, inheritance is a basic feature.
+It does not include classes but instead allow individual objects to inherit from (or delegate to) other objects. 
+Although it is different than class-based languages, the multiple inheritance model is somehow similar. The \self 
+language support multiple (object) inheritance in a clever way. Not only the new inheritance
+relation \emph{prioritized parents} is developed, but also the method lookup rule called 
+\emph{sender path tiebreaker rule}, which is similar with our approach, using hirarchical 
+information in method resolution, but in a prototype-based language setting.
+
+\subsection{Static+Dynamic Type Method Lookup}
+
+\subsection{Formalization Based on FeatherweightJava}
+FeatherweightJava~\cite{Igarashi01FJ} is a minimal core calculus of Java language, proposed by Igarashi et. al. Many models are based on 
+FeatherweightJava, for example FeatherTrait~\cite{Liquori08ftj}, Featherweight defenders~\cite{goetz12fdefenders}, Jx~\cite{Nystrom2004}, as well as our model.
+It provides the standard model of formalizing a Java-like object-oriented language and 
+people can easily extends it to form a new language. In terms of formalization, they key novelty of our model is the use of 
+static types as annotations along with various terms. As far as we know, this technique has not appear in literature before.

### 2017-05-19 SpringerLNCS/paper.tex
change format to Springer LNCS

\documentclass{llncs}

\usepackage{listings}

\usepackage{xspace}
\usepackage{multicol}
\usepackage{microtype}%if unwanted, comment out or use option "draft"
%\usepackage[table,xcdraw]{xcolor} -- clash with preamble.tex
\usepackage{color}
% \usepackage{amsthm}
% \usepackage{amsmath}
\usepackage{stmaryrd}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{url}
%\usepackage{pstricks,pst-node,pst-tree} -- clash with preamble.tex
\usepackage{bbm}
%\usepackage{pgf} -- clash with preamble.tex
\usepackage{multirow}
\usepackage{enumitem}

\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[normalem]{ulem}

\usepackage[T1]{fontenc}
\usepackage[scaled=0.85]{beramono}
% \usepackage{mathpartir}
\usepackage[utf8]{inputenc}
\usepackage{flushend}

\let\proof\relax
\let\endproof\relax
\let\mathpar\relax

\input{predef/names.tex}
\input{predef/mim/syntax.tex}
\input{predef/others/preamble.tex}
\input{predef/macros/common_pl_macros.tex}
\input{predef/algebra/syntax.tex}
\input{predef/f-and/base.tex}
\input{predef/f-and/orthogonality.tex}
\input{predef/f-and/wellformedness.tex}
\input{predef/f-and/subtyping.tex}
\input{predef/f-and/select.tex}
\input{predef/f-and/restrict.tex}
\input{predef/f-and/typing.tex}

\begin{document}

\title{NoTitle}
%\subtitle{\InterfaceBased Programming for the Masses}

% \authorinfo{NoAuthor}
%            {The University of Hong Kong, China}
% %           {\{ylwang,hyzhang,bruno\}@cs.hku.hk}
% %\authorinfo{Marco Servetto}
% %          {Victoria University of Wellington, New Zealand}
% %          {marco.servetto@ecs.vuw.ac.nz}
\author{Author 1, Author 2}

\institute{Lab, University, Address}

\maketitle

\begin{abstract}
  Text.
\end{abstract}

\input{sections/Introduction.tex}

\input{sections/Overview.tex}

\input{sections/Formalization.tex}

\input{sections/Implementation.tex}

\input{sections/Discussion.tex}

\input{sections/CaseStudy.tex}

\input{sections/RelatedWork.tex}

\input{sections/Conclusion.tex}

\section*{Acknowledgments}\label{sec:Acknowledgments}

Authors would like to thank YYYYY.

% \newpage
% \clearpage
% \bibliographystyle{abbrvnat}
\bibliographystyle{splncs03}
\bibliography{paper}

% \appendix
% \input{sections/Appendix_Formalization.tex}
% \input{sections/Translation.tex}
% \input{sections/Appendix_Translation.tex}
% \input{sections/Appendix.tex}

\end{document}

### 2017-05-19 SpringerLNCS/sections/Introduction.tex
change format to Springer LNCS

\section{Introduction}

\begin{itemize}
	\item problem: Unintended method confliction in Multiple inheritance
	\item Existing approaches or models and Their drawbacks
	\item New features (update)
	\item Our contributions
\end{itemize}

In multiple inheritance, naming conflicts often occurs. Among these conflicts, some are real conflicts which needs 
explicit resolve by programmers, however, there are cases where accidental naming conflicts occurs, where the conflicting
methods have completely different meaning/domain which just share the same name.

Existing OOP models have taken care of the first case intensively. However, few of them supports 
unintended method confliction well. Trait and other 
mainstream OO models do not allow unintended methods confliction to co-exist. 
SELF~\cite{} uses \emph{sender path tiebreaker rule} to automatically resolve 
ambiguities that are almost certainly caused by accidental naming conflicts. C++ allows methods with the same signature 
co-exist in a class via inheritance and programmers can use $::$ operator to select the method wanted. 
However none of them allows refining these unintended conflicting methods in subclasses. We propose a calculus that 
deals with unintended method confliction and meanwhile allows refining these methods.

Contributions:
\begin{itemize}
    \item A multiple inheritance model formalized as \MIM.
    \item Novel notion \updates for method path updating.
    \item Implementation of a simple typechecker and evaluator in Scala.
\end{itemize}

### 2017-05-19 sigplan conf format paper/sections/Overview.tex
change format to Springer LNCS

--- 2017-03-28 paper/sections/Overview.tex
@@
 \begin{lstlisting}
-
+interface Deck {
+   void draw() { // draws a card from the Deck }
+}
+interface Drawable {
+   void draw() { // draws something on the screen }
+}
+interface DrawableDeck extends Deck, Drawable {
+  //both draw() methods are kept automaticlaly in our language
+} 
+new DrawableDeck().Deck::draw()
 \end{lstlisting}
@@
 \subsection{Method refinement}
+\begin{lstlisting}
+interface DrawableDeck2 extends DrawableDeck {
+   void draw() override Deck {
+      // new implementation of draw a card from deck
+   }
+   void draw() override Drawable {
+      // new implementation of drawing something
+   } 
+} 
+new DrawableDeck2().Deck::draw()
+\end{lstlisting}

### 2017-05-21 SpringerLNCS/paper.tex
Remove unnecessary files.
Overview.

@@
 \usepackage{flushend}
+\usepackage{lmodern}
 
@@
 \input{predef/macros/common_pl_macros.tex}
-\input{predef/algebra/syntax.tex}
 \input{predef/f-and/base.tex}
@@
 \input{predef/f-and/typing.tex}
+
+\lstset{ %
+	language=Java,                % choose the language of the code
+	columns=flexible,
+	lineskip=-1pt,
+	basicstyle=\ttfamily\small,       % the size of the fonts that are used for the code
+	numbers=none,                   % where to put the line-numbers
+	numberstyle=\ttfamily\tiny,      % the size of the fonts that are used for the line-numbers
+	stepnumber=1,                   % the step between two line-numbers. If it's 1 each line will be numbered
+	numbersep=5pt,                  % how far the line-numbers are from the code
+	backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
+	showspaces=false,               % show spaces adding particular underscores
+	showstringspaces=false,         % underline spaces within strings
+	showtabs=false,                 % show tabs within strings adding particular underscores
+	morekeywords={var},
+	%  frame=single,                   % adds a frame around the code
+	tabsize=2,                  % sets default tabsize to 2 spaces
+	captionpos=none,                   % sets the caption-position to bottom
+	breaklines=true,                % sets automatic line breaking
+	breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
+	title=\lstname,                 % show the filename of files included with \lstinputlisting; also try caption instead of title
+	escapeinside={(*}{*)},          % if you want to add a comment within your code
+	keywordstyle=\ttfamily\bfseries,
+	aboveskip=0pt,
+	belowskip=0pt
+	% commentstyle=\color{Gray},
+	% stringstyle=\color{Green}
+}
 

### 2017-05-21 SpringerLNCS/sections/Overview.tex
Overview.

\section{A Running Example: \lstinline{DrawableDeck}}

This section illustrates the features of our \MIM{} model for resolving unintentional method
conflicts. As mentioned before, such a case arises when two inherited methods happen to have the
same signature, but with different semantics and functionalities. This could be quite troublesome
to programmers that use multiple inheritance. Below we illustrate with a running example called \lstinline|DrawableDeck|.
Note that we use Java-like syntax throughout the paper, and all types are defined with the keyword ``\lstinline|interface|'', which
supports multiple inheritance. Since \MIM{} is designed to be simple, we do not allow abstract methods, that is every method
is required to have a body for its implementation. In that case, interfaces can be directly instantiated by the keyword ``\lstinline|new|''
to create an object.

\subsection{Problem: Unintentional Method Conflicts}

Suppose that two components \lstinline|Drawable| and \lstinline|Deck| have been developed in a system.
\lstinline|Drawable| defines an interface for graphics that can be drawn, which includes a method called \lstinline|draw()|
for visual display. While interface \lstinline|Deck| represents a deck of cards, and supports several operations, like
\lstinline|draw()| for drawing a card from the deck.

\begin{lstlisting}
interface Deck {
  void draw() { // draws a card from the Deck
    Stack<Card> cards = this.getStack();
    Card card = cards.pop();
    ...
  }
}

interface Drawable {
  void draw() { // draws something on the screen
    JFrame frame = new JFrame("Canvas");
    frame.setVisible(true);
    ...
  }
}
\end{lstlisting}
Note that both methods have \lstinline|void| return type (we will not formalize
\lstinline|void| in our calculus afterwards; here is only for illustration). In \lstinline|Deck|, \lstinline|draw()| tries to get the cards as a stack, pops
out the top card, and so on. While in \lstinline|Drawable|, \lstinline|draw()|
creates a blank canvas using \lstinline|JFrame|. Now, a programmer is designing a
card game with GUI. He may want to draw a deck on the screen, so he defines a drawable
deck using multiple inheritance:

\begin{lstlisting}
interface DrawableDeck extends Deck, Drawable {
  ...
} 
\end{lstlisting}
The point of using multiple inheritance is surely for composing the features of
components, achieving great code reuse. It is supported by many mainstream OO
languages. Nevertheless at this point, \lstinline|DrawableDeck| has to throw a compile
error, for the two \lstinline|draw()| methods cause a conflict, though accidentally.

\subsection{More}
\begin{itemize}
	\item Code for the problem (Draw example)
	\item Potential fixes (delegation, renaming, traits, ....)
	\item How it is solved with our language (client code, simple explanation) + show update
\end{itemize}

\subsection{Potential fixes}

For that problem, there are several workarounds that quickly come to our mind:

\paragraph{I. Delegation.}

\paragraph{II. Creating a \lstinline|draw()| method in \lstinline|DrawableDeck|, which explicitly overrides the old ones.}

\paragraph{III. Choosing one of them as the default method, like Mixins.}

\paragraph{IV. Method exclusion like traits.}

\paragraph{V. Method renaming.}
In previous solutions, only renaming can preserve the two different methods m(), 
but it’s cumbersome to do in practice: new names have to be introduced, and (probably) need to prefer one over another. 
Other solutions only preserve one method. Can we keep both methods without renaming?

\subsection{Solution in our language}
\begin{lstlisting}

\end{lstlisting}

\subsection{Method refinement}

### 2017-05-21 SpringerLNCS/sections/Overview.tex
A little bit.

@@
-\section{A Running Example: \lstinline{DrawableDeck}}
+\section{A Running Example: DrawableDeck}
 
@@
 
-\subsection{More}
-\begin{itemize}
-	\item Code for the problem (Draw example)
-	\item Potential fixes (delegation, renaming, traits, ....)
-	\item How it is solved with our language (client code, simple explanation) + show update
-\end{itemize}
-
 \subsection{Potential fixes}
@@
 
-\paragraph{I. Delegation.}
+\paragraph{I. Delegation.} As an alternative to multiple inheritance, delegation can be used by
+introducing two fields with \lstinline|Drawable| type and \lstinline|Deck| type, respectively. This avoids
+method conflicts, nevertheless, delegation itself is too restricted in modularity, and meanwhile
+introduces a lot of boilerplate.
 
 \paragraph{II. Creating a \lstinline|draw()| method in \lstinline|DrawableDeck|, which explicitly overrides the old ones.}
+This is a non-solution. It does not make any sense to override both methods with totally different functionalities, as old
+methods have to be hidden.
 
-\paragraph{III. Choosing one of them as the default method, like Mixins.}
+\paragraph{III. Choosing one of them as the default method, like Mixins.} The mixin model can be applied to choose a
+default one based on linearisation. Similarly, we want to preserve both features, rather than keeping only one of them.
 
-\paragraph{IV. Method exclusion like traits.}
+\paragraph{IV. Method exclusion like traits.} Same reason as above.
 
-\paragraph{V. Method renaming.}
-In previous solutions, only renaming can preserve the two different methods m(), 
-but it’s cumbersome to do in practice: new names have to be introduced, and (probably) need to prefer one over another. 
-Other solutions only preserve one method. Can we keep both methods without renaming?
+\paragraph{V. Method renaming like traits.} This is probably what people do in most cases, by simply renaming one to avoid conflicts.
+It can indeed preserve both features, however, it is cumbersome in practice, as introducing new names can affect other code blocks.
+Certainly this is a workaround, not a solution.
 
-\subsection{Solution in our language}
-\begin{lstlisting}
-
-\end{lstlisting}
+\subsection{Solution in \MIM: \dispatchnamecaptical}
+It uses dynamic dispatch.
 

### 2017-05-22 SpringerLNCS/sections/Overview.tex
Overview more.

@@
     Stack<Card> cards = this.getStack();
+    if (!cards.isEmpty()) {
       Card card = cards.pop();
       ...
+    }
   }
@@
 \begin{lstlisting}
-interface DrawableDeck extends Deck, Drawable {
+interface DrawableDeck extends Drawable, Deck {
   ...
@@
 It can indeed preserve both features, however, it is cumbersome in practice, as introducing new names can affect other code blocks.
-Certainly this is a workaround, not a solution.
+Certainly this is a workaround, not a solution.\\
+
+What we really expect from the language is we keep both methods without renaming, and the type checker does not complain on the
+inheritance. But we need to find an approach to disambiguate on method calls statically.
+
+Certainly the compiler can ignore the conflict when \lstinline|DrawableDeck| is declared, but once an object of \lstinline|DrawableDeck| is created, a method call for \lstinline|draw()| on that object is ambiguous, due to dynamic dispatch.
+Nonetheless, we can adopt static dispatch for disambiguating.
+Some languages like C++ use qualified names in that way:
+
+\begin{lstlisting}
+void func(Drawable obj) {
+  obj.draw();
+}
+
+DrawableDeck d = new DrawableDeck();
+d.Drawable::draw();       // calling draw() in Drawable
+((Drawable) d).draw(); // calling draw() in Drawable
+func(d);                 // calling draw() in Drawable
+\end{lstlisting}
+Thus we have: \paragraph{VI. Static dispatch.} Static dispatch finds out and invokes the most specific method ``by need''.
+
+On the other hand, we also need dynamic dispatch as it is essential and widely used in object-oriented programming.
+C++ has the flexibility for choosing either way of dispatch by the ``virtual'' keyword.
+Unfortunately, this approach is still unsatisfactory regarding code reuse. For instance, here we redefine \lstinline|Deck| to support
+both \lstinline|draw()| and another operation called \lstinline|shuffleAndDraw()|:
+\begin{lstlisting}
+interface Deck {
+  void draw() {...}
+  void shuffleAndDraw() {
+    shuffle();
+    draw();
+  }
+  ...
+}
+\end{lstlisting}
+\lstinline|shuffleAndDraw()| is a designed method that invokes \lstinline|draw()| in its definition. In principle, we want
+that invocation to use dynamic dispatch, because a programmer may define a subtype of \lstinline|Deck|, and override \lstinline|draw()|:
+\begin{lstlisting}
+interface LoggingDeck {
+  void draw() { // overriding
+    Stack<Card> cards = this.getStack();
+    if (!cards.isEmpty()) {
+      Card card = cards.pop();
+      println("The card is: " + card.toString());
+      ...
+    } else {
+      println("Empty deck.");
+    }
+  }
+}
+\end{lstlisting}
+Usually we want to reuse the code of \lstinline|shuffleAndDraw()| during inheritance, hence dynamic dispatch is necessary, otherwise
+programmers have to override all the other methods that invoke \lstinline|draw()|. However, as seen before, dynamic dispatch can cause
+ambiguity if we have:
+\begin{lstlisting}
+interface DrawableLoggingDeck extends Drawable, LoggingDeck {
+  ...
+}
+
+DrawableLoggingDeck d = new DrawableLoggingDeck();
+d.shuffleAndDraw(); // ambiguous draw()
+\end{lstlisting}
+Since the dynamic type of the receiver is \lstinline|DrawableLoggingDeck|, calling \lstinline|shuffleAndDraw()| triggers the ambiguity.
 
 \subsection{Solution in \MIM: \dispatchnamecaptical}
-It uses dynamic dispatch.
 

### 2017-05-22 SpringerLNCS/sections/Formalization.tex
change format to Springer LNCS
proof

--- 2017-05-19 paper/sections/Formalization.tex
@@
 From this point we can view that we are actually modelling a class model that supports multiple
-inheritance. Then it is straightforward to do object creation like ``\new I''. Fields and
+inheritance. Then it is straightforward to do object creation like $\new I$. Fields and
 primitive types are not modelled as well.
@@
 
-\newpage
-
 \subsubsection{A Non-Trivial Example}
@@
 
+\begin{lemma}~\label{lamma0}
+$\textit{If } \mtype(m, I, J) = \overline{D} \rightarrow D, \textit{ and } \mbody(m, I, J) = \overline{x}.e, 
+ \textit{ then for some } J_0 \textit{ with } I <: J_0, \  \exists C <: D, \textit{ such that }  
+ \judgeewf {\overline{x}:\overline{D}, \kwthis:J_0} {e:C} $.
+\end{lemma}
+
+\begin{lemma}[Term Substitution Preserves Typing]~\label{lamma1}
+$\textit{If } \ \judgeewf {\Gamma, \ \overline{x}:\overline{I_X}} { e : I } \textit{ , and }
+\judgeewf {\Gamma} {\overline{y}:\overline{I_Y}} \textit{ where } \overline{I_Y} \subtype \overline{I_X}
+\textit{, then } \judgeewf {\Gamma} {[\overline{y}/\overline{x}]e : I'} \textit{ for some } I' \subtype I.
+$
+\end{lemma}
+
 \begin{theorem}[Subject Reduction]
@@
 
+\begin{proof} ~\\
+\noindent \textbf{Case Invk.} 
+let \[ e = <J>\new I.m(<\overline{I_E}>\overline{e}) \]	
+Suppose \[ \mbody(m, I, J) = (\overline{I_X} \; \overline{x}, I_{E_0} \; e_0) \] 
+then \[ e' =  [<\overline{I_X}>\overline{e}/\overline{x}, \; <J>\new I/\kwthis ] e_0 \] 
+By rules (T-NEW) and (T-INVK), 
+  \[ \judgeewf \Gamma {\new I:I} \quad 
+	 \mtype(m, I, J) = \overline{I_X} \rightarrow I_{E_0} \quad 
+	 \judgeewf \Gamma {\overline{e} : \overline{Y_E}} \quad
+	 \overline{Y_E} \subtype \overline{X} \quad
+	 \textit{, for some } \; \overline{Y_E}
+  \]
+By Lemma~\ref{lamma0},
+	\[
+	\judgeewf {\Gamma, \overline{x}:\overline{I_X}, \kwthis:J_0} {e_0:I_F} \textit{, for some } J \subtype J_0 \textit{ and } I_F \subtype I_{E_0}
+	\]
+By Lemma~\ref{lamma1},
+	\[
+	\judgeewf {\Gamma} {[<\overline{I_X}>\overline{e}/\overline{x}, \; <J>\new I/\kwthis ] e_0  :  I_G} \textit{, for some } I_G \subtype I_F 
+	\]
+So $I_G <: I_{E_0}$, finally just let $I' = I_G$.
+
+\noindent \textbf{Case PathInvk.}
+let \[ e = <J>\new I.K::m(<\overline{I_E}>\overline{e}) \]	
+Suppose \[ \mbody(m, I, K) = (\overline{I_X} \; \overline{x}, I_{E_0} \; e_0) \] 
+then \[ e' =  [<\overline{I_X}>\overline{e}/\overline{x}, \; <K>\new I/\kwthis ] e_0 \] 
+By rules (T-NEW) and (T-INVK), 
+  \[ \judgeewf \Gamma {\new I:I} \quad 
+	 \mtype(m, I, K) = \overline{I_X} \rightarrow I_{E_0} \quad 
+	 \judgeewf \Gamma {\overline{e} : \overline{Y_E}} \quad
+	 \overline{Y_E} \subtype \overline{X} \quad
+	 \textit{, for some } \; \overline{Y_E}
+  \]
+By Lemma~\ref{lamma0},
+	\[
+	\judgeewf {\Gamma, \overline{x}:\overline{I_X}, \kwthis:J_0} {e_0:I_F} \textit{, for some } K \subtype J_0 \textit{ and } I_F \subtype I_{E_0}
+	\]
+By Lemma~\ref{lamma1},
+	\[
+	\judgeewf {\Gamma} {[<\overline{I_X}>\overline{e}/\overline{x}, \; <K>\new I/\kwthis ] e_0  :  I_G} \textit{, for some } I_G \subtype I_F 
+	\]
+So $I_G <: I_{E_0}$, finally just let $I' = I_G$.
+
+\noindent \textbf{Case Super-Invk.}
+let \[ e = \kwsuper.K::m(<\overline{I_E}>\overline{e}) \]	
+Suppose \[ \mbody(m, K, K) = (\overline{I_X} \; \overline{x}, I_{E_0} \; e_0) \] 
+then \[ e' =  [<\overline{I_X}>\overline{e}/\overline{x}] e_0 \] 
+By rules (T-NEW) and (T-INVK), 
+  \[ 
+	 \mtype(m, K, K) = \overline{I_X} \rightarrow I_{E_0} \quad 
+	 \judgeewf \Gamma {\overline{e} : \overline{Y_E}} \quad
+	 \overline{Y_E} \subtype \overline{X} \quad
+	 \textit{, for some } \; \overline{Y_E}
+  \]
+By Lemma~\ref{lamma0},
+	\[
+	\judgeewf {\Gamma, \overline{x}:\overline{I_X}, \kwthis:J_0} {e_0:I_F} \textit{, for some } K \subtype J_0 \textit{ and } I_F \subtype I_{E_0}
+	\]
+By Lemma~\ref{lamma1},
+	\[
+	\judgeewf {\Gamma} {[<\overline{I_X}>\overline{e}/\overline{x} ] e_0  :  I_G} \textit{, for some } I_G \subtype I_F 
+	\]
+So $I_G <: I_{E_0}$, finally just let $I' = I_G$.
+
+\end{proof}
+
 \begin{theorem}[Progress]

### 2017-05-22 SpringerLNCS/sections/Overview.tex
More overview text.

@@
 
-\begin{lstlisting}
+\vspace{3pt}\begin{lstlisting}
 interface Deck {
@@
 }
-\end{lstlisting}
+\end{lstlisting}\vspace{3pt}
 Note that both methods have \lstinline|void| return type (we will not formalize
@@
 
-\begin{lstlisting}
+\vspace{3pt}\begin{lstlisting}
 interface DrawableDeck extends Drawable, Deck {
@@
 } 
-\end{lstlisting}
+\end{lstlisting}\vspace{3pt}
 The point of using multiple inheritance is surely for composing the features of
@@
 
-\begin{lstlisting}
+\vspace{3pt}\begin{lstlisting}
 void func(Drawable obj) {
@@
 func(d);                 // calling draw() in Drawable
-\end{lstlisting}
+\end{lstlisting}\vspace{3pt}
 Thus we have: \paragraph{VI. Static dispatch.} Static dispatch finds out and invokes the most specific method ``by need''.
@@
 both \lstinline|draw()| and another operation called \lstinline|shuffleAndDraw()|:
-\begin{lstlisting}
+\vspace{3pt}\begin{lstlisting}
 interface Deck {
@@
 }
-\end{lstlisting}
-\lstinline|shuffleAndDraw()| is a designed method that invokes \lstinline|draw()| in its definition. In principle, we want
+\end{lstlisting}\vspace{3pt}
+\lstinline|shuffleAndDraw()| is a representative method that invokes \lstinline|draw()| in its definition. In principle, we want
 that invocation to use dynamic dispatch, because a programmer may define a subtype of \lstinline|Deck|, and override \lstinline|draw()|:
-\begin{lstlisting}
+\vspace{3pt}\begin{lstlisting}
 interface LoggingDeck {
@@
 }
-\end{lstlisting}
+\end{lstlisting}\vspace{3pt}
 Usually we want to reuse the code of \lstinline|shuffleAndDraw()| during inheritance, hence dynamic dispatch is necessary, otherwise
@@
 ambiguity if we have:
-\begin{lstlisting}
+\vspace{3pt}\begin{lstlisting}
 interface DrawableLoggingDeck extends Drawable, LoggingDeck {
@@
 d.shuffleAndDraw(); // ambiguous draw()
-\end{lstlisting}
-Since the dynamic type of the receiver is \lstinline|DrawableLoggingDeck|, calling \lstinline|shuffleAndDraw()| triggers the ambiguity.
+\end{lstlisting}\vspace{3pt}
+Since the dynamic type of the receiver is \lstinline|DrawableLoggingDeck|, calling \lstinline|shuffleAndDraw()| triggers the ambiguity. Therefore, we need to find another algorithm for method binding.
 
 \subsection{Solution in \MIM: \dispatchnamecaptical}
+Our \MIM{} model uses \dispatchnameit{} for method lookup.
+A qualified method invocation, for instance, \lstinline|e.I::m()|, is read as ``finding the most specific \lstinline|m()| along path \lstinline|I|''.
+The meaning of ``along path \lstinline|I|'' is that, if the result of \dispatch{} is \lstinline|J.m()| for some \lstinline|J|, then such a \lstinline|J| must be a super type of \lstinline|e|'s dynamic type, and \lstinline|J| has a subtyping relation with \lstinline|I| (either \lstinline|J <: I| or \lstinline|J >: I|).
+Intuitively, the most specific \lstinline|m()| must be from branch \lstinline|I|, but it can be an overridden version after \lstinline|I| like dynamic dispatch.
+The formal definition will be introduced later.
+
+In the above example, when
+
+Now we can actually redefine \lstinline|Deck| as follows:
+\vspace{3pt}\begin{lstlisting}
+interface Deck {
+  void draw() {...}
+  void shuffleAndDraw() {
+    this.Deck::shuffle();
+    this.Deck::draw();
+  }
+  ...
+}
+\end{lstlisting}\vspace{3pt}
+It guarantees that \lstinline|shuffleAndDraw()| are calling \lstinline|shuffle()| and \lstinline|draw()| from its own branch, so that the namesakes
+from other branches will not cause conflicts. Now \lstinline|d.shuffleAndDraw()| is no longer ambiguous.
+
+The above example reflects the general case, that is, all method calls with receiver ``\lstinline|this|'' need to be qualified with its enclosing interface name, so as to avoid potential conflicts.
+Actually in \MIM{}, we can still write ``\lstinline|shuffle();|'' and ``\lstinline|draw();|''
+in \lstinline|Deck|, because \MIM{} automatically desugars those method calls to qualified ones, by its implicit semantic rules.
+\textcolor{red}{Haoyuan: More. super call. update.}
 

### 2017-05-25 SpringerLNCS/sections/Formalization.tex
more proof

@@
 
-\begin{lemma}~\label{lamma0}
+\begin{lemma}~\label{lemma0}
 $\textit{If } \mtype(m, I, J) = \overline{D} \rightarrow D, \textit{ and } \mbody(m, I, J) = \overline{x}.e, 
@@
 
-\begin{lemma}[Term Substitution Preserves Typing]~\label{lamma1}
+\begin{lemma}[Term Substitution Preserves Typing]~\label{lemma1}
 $\textit{If } \ \judgeewf {\Gamma, \ \overline{x}:\overline{I_X}} { e : I } \textit{ , and }
@@
 \end{lemma}
+
+\begin{proof}~\\
+\noindent \textbf{Case Var.}
+$ e = x \quad I = \Gamma(x) $. \\
+If $x \notin \overline{x}$, then the conclusion is immediate, since $[\overline{y}/\overline{x}]x = x$.
+On the other hand, if $x = x_i$ and $I = {I_X}_i$, then since $[\overline{y}/\overline{x}]x = [\overline{y}/\overline{x}]x_i = y_i$,
+letting $I' = {I_Y}_i$ finishes the case.
+
+\noindent \textbf{Case New.}
+$e = \new I$ and there are no term for substitution, the conclusion is obvious.
+
+\noindent \textbf{Case Invk.}
+
+\noindent \textbf{Case PathInvk.}
+
+\noindent \textbf{Case SuperInvk.}
+
+\end{proof}
 
@@
   \]
-By Lemma~\ref{lamma0},
+By Lemma~\ref{lemma0},
 	\[
@@
 	\]
-By Lemma~\ref{lamma1},
+By Lemma~\ref{lemma1},
 	\[

### 2017-05-25 SpringerLNCS/sections/Overview.tex
Small fix.

@@
 \end{lstlisting}\vspace{3pt}
-Since the dynamic type of the receiver is \lstinline|DrawableLoggingDeck|, calling \lstinline|shuffleAndDraw()| triggers the ambiguity. Therefore, we need to find another algorithm for method binding.
+Since the dynamic type of the receiver is \lstinline|DrawableLoggingDeck|, calling \lstinline|shuffleAndDraw()| triggers the ambiguity.
+When \lstinline|shuffleAndDraw()| invokes \lstinline|draw()|, what we really want is \lstinline|LoggingDeck.draw()|, yet
+neither static dispatch nor dynamic dispatch in languages like C++ does so.
+ Therefore, we need to find another algorithm for method binding.
 
@@
 
-In the above example, when
+On the other hand, \lstinline|((I) e).m()| behaves the same as \lstinline|e.I::m()| in our model.
+Such a dispatch make uses of both the static type and the dynamic type of the receiver.
+Intuitively, the static type specifies one branch of the method to avoid ambiguity, and the dynamic type finds the latest version on that branch.
+It may still introduce ambiguity when there are multiple paths from the static type to the dynamic type, and those paths cause conflicts.
+To prevent this, we disallow this kind of diamond inheritance to ensure unambiguity.
+That is to say, we do not allow two conflicted methods to override a same base method.
+This is natural as it is no longer an ``unintended'' conflict in that way.
 
-Now we can actually redefine \lstinline|Deck| as follows:
+With the old example, below code meets our expectation:
 \vspace{3pt}\begin{lstlisting}
@@
 
-The above example reflects the general case, that is, all method calls with receiver ``\lstinline|this|'' need to be qualified with its enclosing interface name, so as to avoid potential conflicts.
-Actually in \MIM{}, we can still write ``\lstinline|shuffle();|'' and ``\lstinline|draw();|''
-in \lstinline|Deck|, because \MIM{} automatically desugars those method calls to qualified ones, by its implicit semantic rules.
+Actually in \MIM{}, we can still write ``\lstinline|shuffle();|'' and ``\lstinline|draw();|'',
+because the compiler is able to know that the receiver ``\lstinline|this|'' exactly has static type \lstinline|Deck|, hence hierarchical dispatch eliminates ambiguity.
 \textcolor{red}{Haoyuan: More. super call. update.}

### 2017-06-05 SpringerLNCS/paper.tex
more proof
Overview.

@@
 	showtabs=false,                 % show tabs within strings adding particular underscores
-	morekeywords={var},
+	morekeywords={var,updates},
 	%  frame=single,                   % adds a frame around the code
@@
 
+\begin{comment}
 \section*{Acknowledgments}\label{sec:Acknowledgments}
@@
 Authors would like to thank YYYYY.
+\end{comment}
 
@@
 
-% \appendix
+\newpage
+\appendix
+\input{sections/Appendix.tex}
 % \input{sections/Appendix_Formalization.tex}
@@
 % \input{sections/Appendix_Translation.tex}
-% \input{sections/Appendix.tex}
 

### 2017-06-05 SpringerLNCS/sections/Overview.tex
Overview.

@@
 
-\subsection{Potential fixes}
+\subsection{Potential Fixes}
 
@@
 
-On the other hand, \lstinline|((I) e).m()| behaves the same as \lstinline|e.I::m()| in our model.
+On the other hand, \lstinline|((I) e).m()|, or simply \lstinline|e.m()| where \lstinline|e| has static type \lstinline|I|, behaves the same as \lstinline|e.I::m()| in our model.
 Such a dispatch make uses of both the static type and the dynamic type of the receiver.
@@
 because the compiler is able to know that the receiver ``\lstinline|this|'' exactly has static type \lstinline|Deck|, hence hierarchical dispatch eliminates ambiguity.
-\textcolor{red}{Haoyuan: More. super call. update.}
 
-\subsection{Method refinement}
+\subsection{Method Update in \MIM	}
+
+\MIM{} supports two kinds of polymorphism on methods: (1) method overriding; (2) method update.
+A method update is similar to overriding, in the sense that it provides a refined implementation of a method.
+But the difference is that an update just refines one branch, since \MIM{} can preserve several conflicted branches at the same time.
+Whereas a method overriding will hide all its inherited original methods, in which case method conflicts are unexpectedly ignored.
+
+For example, we define an interface \lstinline|DrawableLoggingDeck2|, where we refine the \lstinline|draw()| from \lstinline|Drawable()| by setting
+the canvas invisible:
+\vspace{3pt}\begin{lstlisting}
+interface DrawableLoggingDeck2 extends DrawableLoggingDeck {
+  void draw() updates Drawable {
+    JFrame frame = new JFrame("Canvas");
+    frame.setVisible(false);
+    ...
+  }
+}
+\end{lstlisting}\vspace{3pt}
+Here the update specifies \lstinline|Drawable| to be refined.
+The use of this update ensures that both branches of \lstinline|draw()| are preserved.
+At the same time, we should notice that a method update is no longer considered as an original method.
+Some client code is shown below:
+\vspace{3pt}\begin{lstlisting}
+DrawableLoggingDeck2 d2 = new DrawableLoggingDeck2();
+d2.Drawable::draw(); // calling draw() in DrawableLoggingDeck2
+d2.Deck::draw();       // calling draw() in LoggingDeck
+\end{lstlisting}\vspace{3pt}
+
+In \MIM{}, hierarchical dispatch first finds the most specific original method (with respect to method overriding), then it finds the most specific update on that method.
+A counter-example is when there are two method updates on \lstinline|Drawable| in \lstinline|DrawableLoggingDeck2|, it leads to ambiguity.
+The compiler is supposed to forbid that during compile time.
+
+Two rules for method updates in \MIM: updates can only refine \textbf{original} methods, and they cannot overlap method overriding.
+For instance, writing \lstinline|"void draw()| \lstinline|updates Deck {...}"| is disallowed in \lstinline|DrawableLoggingDeck2|, because existing two branches are \lstinline|Drawable.draw()| and \lstinline|LoggingDeck.draw()|, yet \lstinline|Deck.draw()| is already overridden.
+It does not really make sense to update the old branch.
+
+Similar to many OO languages, \MIM{} also allows \textit{super method invocation} in a method body.
+The invocation \lstinline|super.T::m()| will ignore all the subtypes of \lstinline|T|, and only look at \lstinline|T| together with its super interfaces.

### 2017-06-05 SpringerLNCS/sections/Formalization.tex
Small fix.
separate proof

--- 2017-05-19 paper/sections/Formalization.tex
@@
 \end{displaymath}
-\caption{Syntax. *: only intended for semantic rules.}\label{fig:syntax}
+\caption{Syntax. *: only intended for semantic rules. \red{Do we need "this"?}}\label{fig:syntax}
 \end{figure*}
@@
 \end{mathpar}
-\caption{Small-step semantics.}\label{fig:smallstep}
+\caption{Small-step semantics.\red{Haoyuan: TODO: <???> new I()/this}}\label{fig:smallstep}
 \end{figure*}
@@
 \red{TODO: class encapsulation problem: interface A: m; interface B: m update A; interface C: m update B.}
-
-\subsection{Type Safety}
-
-\begin{theorem}[Subject Reduction]
-$\textit{If } \ \judgeewf \Gamma {e : I} \; \textit{ and } \ e \rightarrow e',\ 
-\textit{then } \judgeewf \Gamma {e' : I'} \ \textit{ for some } \ I' <: I.$
-\end{theorem}
-
-\begin{theorem}[Progress]
-$\textit{If } \ \judgeewf {} {e : I}, \textit{ then either } \ e 
-\textit{ is a value or there is an } e' \textit{ with } e \rightarrow e'.$
-\end{theorem}

### 2017-06-05 SpringerLNCS/sections/Conclusion.tex
Conclusion.

\section{Conclusion}

This paper proposes \MIM{} as a new multiple inheritance model for unintentional method conflicts.
Existing approaches including static dispatch and dynamic dispatch have to compromise between code reuse
and type safety, whereas \MIM{} uses a different solution called hierarchical dispatch to obtain both.
Such an approach not only offers great code reuse like dynamic dispatch, but also ensures unambiguity by
our algorithm for method binding. This paper also introduces method updates for refinements on branches individually.
\MIM{} is formalized with a basis on Featherweight Java, and supported
by a few theorems.

Our model can certainly be improved at some aspects. We did not formalize fields, though it is difficult to
put state and multiple inheritance together []. For simplicity, we did not formalize other common features including
method overloading, casts, covariant return types, and so on. Moreover, we restrict method updates to target only at the
original methods. Potentially a looser condition can better support encapsulation and modularity with respect to code design.

### 2017-06-05 SpringerLNCS/sections/Formalization.tex
Conclusion.

@@
 Finally, (T-INTF) defines interface type-checking in a straightforward way.
+Note that it is responsible for checking conflicted paths with a same source.
+As we illustrated in Section ?, such a case is disallowed for unambiguity.
 
@@
 one kind of method invocation.
-They all invoke \mbody for method body lookup.
+They all invoke \mbody{} for method body lookup.
 Generally, one can understand $\mbody(m, I, J)$ in a way that it finds the most specific body of method $m$, when the receiver has dynamic type $I$ and static type $J$.
@@
 
+\red{H: mtype based on mbody?}
 $\mbody(m, I_d, I_s)$, as defined in Figure~\ref{fig:auxfunc}, denotes a method body lookup function.
@@
 \end{comment}
-
-\begin{itemize}
-	\item Syntax + typing rules + Semantics + Auxiliary definitions
-	\item Implementation: a simple type checker + interpreter in Scala
-\end{itemize}
-
-\subsubsection{A Non-Trivial Example}
-
-\begin{lstlisting}
-interface A extends {
-	A m() override A {return new A(); }
-}
-interface B extends A {
-	A m() override B {return new B(); }
-}
-interface C extends A {
-	A m() override C {return new C(); }
-}
-interface D extends B, C {
-	A m() override B {return new D(); }
-}
-interface E extends B {
-	A m() override B {return new E(); }
-}
-interface F extends D, E {
-	A m() override B {return new F(); } 
-	A n(B b) override F {return b.m(); }
-}
-new F().n(new F())
-\end{lstlisting}
-
-\begin{comment}
-\[
-\begin{array}{l}
-\kwinterface \; A \; \kwextends \; \{ \\
-\; \; \; \; A \; m() \; \kwoverride \; A \; \{\kwreturn \; \new A;\} \\
-\} \\
-\\
-\kwinterface \; B \; \kwextends \; A \; \{ \\
-\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new B;\} \\
-\} \\
-\\
-\kwinterface \; C \; \kwextends \; A \; \{ \\
-\; \; \; \; A \; m() \; \kwoverride \; C \; \{\kwreturn \; \new C;\} \\
-\} \\
-\\
-\kwinterface \; D \; \kwextends \; B, \; C \; \{ \\
-\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new D;\} \\
-\} \\
-\\
-\kwinterface \; E \; \kwextends \; B \; \{ \\
-\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new E;\} \\
-\} \\
-\\
-\kwinterface \; F \; \kwextends \; D, \; E \; \{ \\
-\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new F;\} \\
-\; \; \; \; A \; n(B \; b) \; \kwoverride \; F \; \{\kwreturn \; b.m();\} \\
-\} \\
-\\
-\new F.n(\new F)
-\end{array}
-\]
-\end{comment}
-
-~\red{Unfortunately I think this example shows that it is hard to reuse
-	$D.m$ on path $B$ and $E.m$ on path $B$ in $F$?}
-
-\red{We can use the $\kwsuper$ keyword to access the originally defined methods
-	in super types, but we cannot access the old updating methods.}
-
-\red{Just like $\kwsuper.I::m()$ is equivalent to $\new I.m()$, maybe we can add
-a degree of freedom to $\kwsuper$, for example, $\kwsuper.D::B::m()$ is equivalent to
-$\new D.B::m()$, so we can use $\kwsuper.D::B::m()$ and $\kwsuper.E::B::m()$ inside interface $F$ for code reuse?}
-
-Interfaces $A,B,C,D,E,F$ OK in type checking.
-
-To type-check $\new F.n(\new F)$:
-\begin{itemize}
-	\item By (T-INVK), we need to calculate $\mtype(n, F)$.
-	\item $\mtype(n, F) = B \to A$. And $\new F : B$.
-	\item $\new F.n(\new F) : A$.
-\end{itemize}
-
-~
-
-To compute \red{$\new F.n(\new F)$}:
-\begin{itemize}
-	\item By (C-RECEIVER), we compute \red{$\new F$}:
-		\begin{itemize}
-			\item By (C-STATICTYPE): \red{$<F> \new F$}.
-		\end{itemize}
-	\item By (C-ARGS), we compute \red{$\new F$}:
-		\begin{itemize}
-			\item By (C-STATICTYPE): \red{$<F> \new F$}.
-		\end{itemize}
-	\item Now we get \red{$(<F> \new F).n(<F> \new F)$}. By (S-INVK):
-		\begin{itemize}
-			\item Compute $\mbody(n, F, F) = \red{(B \; b, A \; b.m())}$.
-			\item Replace \red{$b$} with \red{$<B> \new F$} in \red{$b.m()$}.
-			\item Replace \red{$\kwthis$} with \red{$<F> \new F$} in \red{$b.m()$}.
-		\end{itemize}
-	\item Finally we get \red{$<A>((<B> \new F).m())$}.
-	\item By (C-FREDUCE), we first compute \red{$(<B> \new F).m()$}:
-		\begin{itemize}
-			\item By (S-INVK), we compute \red{$\mbody(m, F, B)$}.
-			\item In $\mbody$, we invoke \red{$\mostSpecific(m, F, B)$}.
-			\item In $\mostSpecific$, \red{$set = \{B\}$, $\prune(set) = \{B\}$}.
-			\item Back to $\mbody$, we invoke \red{$\mostSpecific_3(m, F, B)$}.
-			\item In $\mostSpecific_3$, \red{$set = \{B,D,E,F\}$, $\prune(set) = \{F\}$}.
-			\item Back to $\mbody$, we check \red{$F.m$} and return \red{$(-,A \; (\new F))$}.
-			\item Back to (S-INVK).
-			\item Replace \red{$\kwthis$} with \red{$<B> \new F$} in \red{$\new F$}.
-			\item Finally we get \red{$<A> \new F$}.
-		\end{itemize}
-	\item Now we have \red{$<A>(<A> \new F)$}.
-	\item By (C-ANNOREDUCE): \red{$<A> \new F$}.
-\end{itemize}
-
-\red{TODO: class encapsulation problem: interface A: m; interface B: m update A; interface C: m update B.}

### 2017-06-08 Aplas17/predef/java.tex

--- 2017-05-21 SpringerLNCS/paper.tex
@@
-\documentclass{llncs}
-
-\usepackage{listings}
-
-\usepackage{xspace}
-\usepackage{multicol}
-\usepackage{microtype}%if unwanted, comment out or use option "draft"
-%\usepackage[table,xcdraw]{xcolor} -- clash with preamble.tex
-\usepackage{color}
-% \usepackage{amsthm}
-% \usepackage{amsmath}
-\usepackage{stmaryrd}
-\usepackage{graphicx}
-\usepackage{amssymb}
-\usepackage{fancyvrb}
-\usepackage{url}
-%\usepackage{pstricks,pst-node,pst-tree} -- clash with preamble.tex
-\usepackage{bbm}
-%\usepackage{pgf} -- clash with preamble.tex
-\usepackage{multirow}
-\usepackage{enumitem}
-
-\usepackage{verbatim}
-\usepackage{graphicx}
-\usepackage{wrapfig}
-\usepackage[normalem]{ulem}
-
-\usepackage[T1]{fontenc}
-\usepackage[scaled=0.85]{beramono}
-% \usepackage{mathpartir}
-\usepackage[utf8]{inputenc}
-\usepackage{flushend}
-\usepackage{lmodern}
-
-\let\proof\relax
-\let\endproof\relax
-\let\mathpar\relax
-
-\input{predef/names.tex}
-\input{predef/mim/syntax.tex}
-\input{predef/others/preamble.tex}
-\input{predef/macros/common_pl_macros.tex}
-\input{predef/f-and/base.tex}
-\input{predef/f-and/orthogonality.tex}
-\input{predef/f-and/wellformedness.tex}
-\input{predef/f-and/subtyping.tex}
-\input{predef/f-and/select.tex}
-\input{predef/f-and/restrict.tex}
-\input{predef/f-and/typing.tex}
+\lstdefinelanguage{JavaScala}{
+  morekeywords={public,int,interface,implements,default,
+    abstract,case,void,catch,class,def,static,%
+    do,else,extends,false,final,finally,%
+    for,if,implicit,import,match,mixin,%
+    new,null,object,override,package,%
+    private,protected,requires,return,sealed,%
+    super,this,throw,trait,true,try,%
+    type,var,while,yield,obj,updater},
+  otherkeywords={=>,<-,<\%,<:,>:,\#,@},
+  sensitive=true,
+  morecomment=[l]{//},
+  morecomment=[n]{/*}{*/},
+  morestring=[b]",
+  morestring=[b]',
+  morestring=[b]"""
+}
 
@@
 }
-
-\begin{document}
-
-\title{NoTitle}
-%\subtitle{\InterfaceBased Programming for the Masses}
-
-% \authorinfo{NoAuthor}
-%            {The University of Hong Kong, China}
-% %           {\{ylwang,hyzhang,bruno\}@cs.hku.hk}
-% %\authorinfo{Marco Servetto}
-% %          {Victoria University of Wellington, New Zealand}
-% %          {marco.servetto@ecs.vuw.ac.nz}
-\author{Author 1, Author 2}
-
-\institute{Lab, University, Address}
-
-\maketitle
-
-\begin{abstract}
-  Text.
-\end{abstract}
-
-\input{sections/Introduction.tex}
-
-\input{sections/Overview.tex}
-
-\input{sections/Formalization.tex}
-
-\input{sections/Implementation.tex}
-
-\input{sections/Discussion.tex}
-
-\input{sections/CaseStudy.tex}
-
-\input{sections/RelatedWork.tex}
-
-\input{sections/Conclusion.tex}
-
-\section*{Acknowledgments}\label{sec:Acknowledgments}
-
-Authors would like to thank YYYYY.
-
-% \newpage
-% \clearpage
-% \bibliographystyle{abbrvnat}
-\bibliographystyle{splncs03}
-\bibliography{paper}
-
-% \appendix
-% \input{sections/Appendix_Formalization.tex}
-% \input{sections/Translation.tex}
-% \input{sections/Appendix_Translation.tex}
-% \input{sections/Appendix.tex}
-
-\end{document}

### 2017-06-08 Aplas17/sections/Overview.tex

--- 2017-06-05 SpringerLNCS/sections/Overview.tex
@@
 
+\red{H: with UML graphs the illustration could be better.}
 This section illustrates the features of our \MIM{} model for resolving unintentional method
@@
 It may still introduce ambiguity when there are multiple paths from the static type to the dynamic type, and those paths cause conflicts.
-To prevent this, we disallow this kind of diamond inheritance to ensure unambiguity.
-That is to say, we do not allow two conflicted methods to override a same base method.
-This is natural as it is no longer an ``unintended'' conflict in that way.
+To prevent this, we disallow this kind of conflict to ensure unambiguity.
+That is to say, we do not allow two methods to override a same base method when they cause conflicts.
+This is natural, as they are just two versions of the same operation, hence it is no longer an ``unintentional'' conflict in that way.
 

### 2017-06-11 Aplas17/sections/Introduction.tex
Introduction in progress.

\section{Introduction}

Contributions:
\begin{itemize}
    \item A multiple inheritance model formalized as \MIM.
    \item Novel notion \updates for method path updating.
    \item Implementation of a simple typechecker and evaluator in Scala.
\end{itemize}

\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

Object-oriented programming has been adopted for years in both industry and research areas to offer great code reuse.
It allows data structures and behaviours to be represented by modules and the relationship among them. But earlier
single inheritance appeared to be less expressive and flexible to use. Since the occurrence of multiple inheritance, it
seems more practical to programmers in many mainstream languages like C++ and Java.

Nevertheless, just as Steve Cook pointed out
in [], it is good but ``there is no good way to do it''.
One of the most sensitive and critical issue is perhaps the ambiguity introduced by multiple inheritance.
One case is the famous \textit{diamond problem}. It says that such inheritance could allow one feature to be inherited from
multiple parent classes, hence conflicts arise. The variety of strategies on resolving such conflicts urges the occurrence of
different multiple inheritance models, including traits, mixins, CZ, and so on. We can observe that existing languages have taken
care of this case intensively. Other issues include how multiple inheritance
deals with state, as discussed in [C++] and [], and so on.

In contrast with the diamond inheritance, a second case of ambiguity is that conflicted methods do not actually refer to the same feature.
This issue was proposed by the trait paper, so-called \textit{unintentional method conflicts}. In a nominal system, they are designed
for different behaviours, and they just happen to have same names (and signatures),
yet an inheritance to compose them has to be rejected. Unlike the
diamond problem, the conflicted methods usually do not share a common parent, hence in this paper we also call such a case ``\textit{the triangle
inheritance}''.\haoyuan{Fine to have a graph with diamond and triangle shapes if we got space.}

Unintentional method conflicts are less common than the diamond problem, nonetheless, they have severe effects in practice. This
is unfortunately because such an issue has not been formally studied much, hence existing languages can merely provide limited support on it.
In most situations, it is only treated the same as the diamond inheritance. This is unfair and practically unacceptable, especially when it is
necessary to combine two large modules and their features, but the inheritance is simply prohibited by such a small conflict. As a workaround from the diamond inheritance side, it is possible to define a new method in the child class, to override those conflicted methods. Intuitively using one method to fuse two unrelated features is unsatisfactory, therefore we need a real solution to keep both features individually during inheritance,
so as not to break independent extensibility.

Some better workarounds include delegation, renaming/exclusion in the trait model, and so on, yet they still have various drawbacks as we will discuss in Section ?. On the other hand, there is indeed some related work [] that approaches our expectation, that is, they allow two unintentionally conflicted method to coexist in the system. Among them C++ is a representative that accepts the triangle inheritance and resolves the ambiguity by static dispatch. However, when virtual methods are defined with unintentional conflicts, C++ has to throw (linker?) errors on them.
This is again unsatisfactory because dynamic dispatch is necessary under many circumstances for code reuse and extensibility.

Having tolerance for unintentional method conflicts does not mean to sacrifice extensibility, hence in contrast with static dispatch and dynamic dispatch, we propose a third approach, which looks like a combination of both, called \textit{hierarchical dispatch}. By hierarchical dispatch,

### 2017-06-11 Aplas17/sections/Introduction.tex
Finished draft of introduction.

@@
 \section{Introduction}
-
-Contributions:
-\begin{itemize}
-    \item A multiple inheritance model formalized as \MIM.
-    \item Novel notion \updates for method path updating.
-    \item Implementation of a simple typechecker and evaluator in Scala.
-\end{itemize}
-
-\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
 
@@
 Having tolerance for unintentional method conflicts does not mean to sacrifice extensibility, hence in contrast with static dispatch and dynamic dispatch, we propose a third approach, which looks like a combination of both, called \textit{hierarchical dispatch}.
-By hierarchical dispatch,
+By hierarchical dispatch, the method binder will look at both the static type and the dynamic type of the receiver during runtime.
+When there are multiple branches that cause unintentional conflicts, the static type can specify one branch among them for unambiguity, and the dynamic type helps to find the most specific (the newest) implementation.
+In that case both unambiguity and extensibility are preserved.
+To present this idea, we introduce a formalized model in Section ?
+based on Featherweight Java, together with some theorems and proofs for type soundness.
+In the model we also propose \textit{partial overrides}, where a method refinement can be applied only to one branch.
+
+In summary, our contributions are: \haoyuan{will have prototype implementation in Scala if we still have time.}
+\begin{itemize}
+	\item \textbf{Hierarchical dispatch:} which integrates both the static type and dynamic type for method binding, and hence
+	ensures unambiguity as well as extensibility.
+	\item \textbf{Partial overrides:} a novel notion that allows method refinements on individual branches.
+	\item \textbf{MIM:} a formalized model based on Featherweight Java, supporting the above features. Some theorems and their proofs
+	are attached to confirm the type soundness (unambiguity?) of the model.
+\end{itemize}

### 2017-06-11 Aplas17/sections/RelatedWork.tex
related work

--- 2017-05-19 paper/sections/RelatedWork.tex
@@
 Multiple inheritance is a useful feature in object-oriented programming world although it's difficult to model and can 
-cause various problems (e.g. the diamond problem).  There are many existing languages/models that support multiple 
+cause various problems (e.g. the diamond problem~\cite{Sak89dis,Singh1995}).  There are many existing languages/models that support multiple 
 inheritance, either coming with multiple inheritance capability or added through evolution. The Mixin model allows naming components 
@@
 
-Java 8 interfaces are closely related to traits: concrete method implementations are allowed (via the default keyword) inside interfaces. 
+Java 8 interfaces are closely related to traits: concrete method implementations are allowed (via the \textbf{\texttt{default}} keyword) inside interfaces. 
 The introduction of default methods opens the gate for various flavors of multiple inheritance in Java.
@@
 Inheritance is divided into two concepts: inheritance dependency and implementation inheritance. 
-Using a combination of requires and extends, a program with diamond inheritance is transformed to one without diamonds. 
-Moreover, fields and multiple inheritance can coexist. However untangling inheritance also untangles the class structure. 
-In CZ, not only the number of classes, but also the class hierarchy complexity increases.
+Using a combination of \textbf{\texttt{requires}} and \textbf{\texttt{extends}}, a program with 
+diamond inheritance is transformed to one without diamonds. Moreover, fields and multiple inheritance can coexist. 
+However untangling inheritance also untangles the class structure. In CZ, not only the number of classes, but also 
+the class hierarchy complexity increases.
 
@@
 programmers to explicitly resolve ambiguity and disallowing two methods with the same signature from two different libraries 
-to co-exit.
+to co-exit. This is the common drawback of the above mentioned models versus our model.
 
@@
 \noindent {\bf C++ model.}
-As discussed in Section~\ref{}, C++ supports very flexible inheritance mode and allows programmers to choose different 
+As discussed in Section~\ref{sec:overview}, C++ supports very flexible inheritance mode and allows programmers to choose different 
 confliction resolution approaches via normal or virtual inheritance. Generally speaking, C++ model is much more complex 
@@
 \end{lstlisting}
-The running result is $MB \; MA$, meaning that it looks at the static type when doing method lookup. However, we can alter the code 
-a little bit with virtual method and the result will be totally different:
-\begin{lstlisting}
+The running result is $MB \; MA$, meaning that it uses static dispatch (looks at the static types) when doing method lookup. 
+On calling \texttt{func(c)}, no matter the dynamic type of \texttt{c} is class \texttt{C}, the method call still dispatches to 
+the method \texttt{m} in class \texttt{A} because of static dispatch.
+However, we can alter the code a little bit with \textbf{\texttt{virtual}} methods and the result will be totally different:
+\begin{lstlisting}[language=c++]
 class A { 
@@
 \end{lstlisting}
-Now the running result will be $MB \; MC$. With virtual method, method lookup algorithm will find the most specific 
-method definition of $m$, which is the definition in class $C$. Although C++ support this flexibility, it does not 
-support updating both $A.m$ and $B.m$ in class $C$.
+Now the running result will be $MB \; MC$. With virtual method, dynamic dispatch is used and 
+method lookup algorithm will find the most specific method definition of $m$, which is the definition 
+in class $C$. Although C++ support this flexibility, the drawback compared to our model is
+obvious: it does not support updating both $A.m$ and $B.m$ in class $C$.
 
@@
 
-\noindent  {\bf C\# Explicit method implementation.}
+\noindent  {\bf \csharp Explicit method implementation.}
 Explicit method implementation is a special feature supported by \csharp. As described in \csharp
-tutorial~\cite{}, a class that implements an interface can explicitly implement a member of that
+documentation~\cite{csharpdoc}, a class that implements an interface can explicitly implement a member of that
 interface. When a member is explicitly implemented, it can only be accessed through an instance

### 2017-06-12 Aplas17/sections/Formalization.tex
changes

--- 2017-06-05 SpringerLNCS/sections/Formalization.tex
@@
 In this section, we present a formalization of our MIM calculus, based on
-a minimal subset of Java 8 interfaces. The syntax, typing rules and small-step
+a minimal subset of Java 8 interfaces.\bruno{Mention that it is done 
+in a FJ style?} The syntax, typing rules and small-step
 semantics are included below.
@@
 \subsection{Syntax}
-Figure~\ref{fig:syntax} shows the syntax of MIM. The multiple inheritance feature
-of MIM has a basis on Java interfaces. To demonstrate how unintentional method conflicts
-are untangled in MIM, we present the calculus in a straightforward way, hence we only
-focus on a small subset of the interface model. For example, all the methods declared in an
-interface are default methods, that is to say, they always provide default implementations.
-From this point we can view that we are actually modelling a class model that supports multiple
-inheritance. Then it is straightforward to do object creation like $\new I$. Fields and
-primitive types are not modelled as well.
 
-We use uppercase letters like $I, J, K$ to represent identifiers for interfaces. By multiple inheritance,
-an interface can have a set of super interfaces, where such a set can be empty. Inside an interface are a
-set of method declarations. Each method body holds a return statement. As seen in Figure~\ref{fig:syntax},
-we have introduced the \kwoverride keyword to override an old implementation of the method. If the interface
-that it overrides is exactly the enclosing interface, then such a method is seen as ``originally defined''.
-Again for simplicity, overloading is not modelled for methods, which implies we can uniquely identify a method
-by its name.
+Figure~\ref{fig:syntax} shows the syntax of MIM. The multiple
+inheritance feature of MIM as a basis Java 8 interfaces, which support
+method implementations via default methods. This feature is quite
+closely related to \emph{traits}\cite{}.  To demonstrate how
+unintentional method conflicts are untangled in MIM, we present the
+calculus in a straightforward way, hence we only focus on a small
+subset of the interface model. For example, all the methods declared
+in an interface are default methods, that is to say, they always
+provide default implementations.  From this point we can view that we
+are actually modelling a class model that supports multiple
+inheritance. Then it is straightforward to do object creation like
+$\new I$. Fields and primitive types are not modelled as well.
 
-An expression can be a variable, a method invocation, an object creation, furthermore, a path-invocation like
-``$e.I::m(\overline{e})$'', meaning that the dynamically binded implementation for method $m$ should be along
-the path $I$. Another case is the super-invocation, enabling a method to access an old implementation from the
-specified super type. Hence a super-invocation can only be used inside an interface definition. Finally an expression
-can also be a value ``$<I> \new J$''. It is exactly an object instance of $J$ with annotated static type $I$.
-Note that values are only intended for the small-step semantics of MIM, hence they are not supposed to appear in the source program.
+We use uppercase letters like $I, J, K$ to represent identifiers for
+interfaces. By multiple inheritance, an interface can have a set of
+super interfaces, where such a set can be empty. Inside an interface
+is a set of method declarations. Each method body holds a return
+statement. As seen in Figure~\ref{fig:syntax}, we have introduced the
+\kwoverride keyword\bruno{use \\xspace to deal with the spacing issues
+in commands like override} to override an old implementation of the
+method. If the interface that it overrides is exactly the enclosing
+interface, then such a method is seen as ``originally defined''.
+Again for simplicity, overloading is not modelled for methods, which
+implies we can uniquely identify a method by its name.
+
+An expression can be a variable, a method invocation, an object
+creation, furthermore, a path-invocation like
+``$e.I::m(\overline{e})$'', meaning that the dynamically binded
+implementation for method $m$ should be along the path $I$. Another
+case is the super-invocation, enabling a method to access an old
+implementation from the specified super type. Hence a super-invocation
+can only be used inside an interface definition. Finally an expression
+can also be a value ``$<I> \new J$''. It is exactly an object instance
+of $J$ with annotated static type $I$.  Note that values are only
+intended for the small-step semantics of MIM, hence they are not
+supposed to appear in the source program.
 

### 2017-06-12 Aplas17/sections/Formalization.tex

@@
 \end{figure*}
+\bruno{Path invocation subsumes regular invocation. In other words:
+e0.m(e) = e0.I::m(e) when the type of e0 is I.}
+\bruno{Last time I met I told you that the typing of ``this'' is
+  wrong, and this is not yet fixed. I've also told you to make all
+figures at the top. In T-Method, \Gamma shows up out of nowhere.
+}
+\bruno{Rule for new is wrong! It says that a new expression that
+  creates a class with any name (even if the class does not exist) 
+is valid. The paper is not even following the rules of FJ.}
 

### 2017-06-12 Aplas17/sections/Formalization.tex
fix
Quick fixes on formalization.

@@
 statement. As seen in Figure~\ref{fig:syntax}, we have introduced the
-\kwoverride keyword\bruno{use \\xspace to deal with the spacing issues
-in commands like override} to override an old implementation of the
+\kwoverride{} keyword to override an old implementation of the
 method. If the interface that it overrides is exactly the enclosing
@@
 
-\begin{figure*}[htbp]
+\begin{figure*}[t]
 \begin{displaymath}
@@
 e.I::m(\overline{e}) \mid
-\kwsuper.I::m(e) \; \mid \; v^* \\
+\kwsuper.I::m(e) \; \mid \; <I> e \\
 \text{Context}      & \Gamma & \Coloneqq & \overline{x:I} \\
@@
 \end{displaymath}
-\caption{Syntax. *: only intended for semantic rules. \red{Do we need "this"?}}\label{fig:syntax}
+\caption{Syntax. \haoyuan{mention in text that annotated expressions are only intended for semantic rules?}}\label{fig:syntax}
 \end{figure*}
@@
 
-\begin{figure*}[htbp]
+\begin{figure*}[t]
 \begin{mathpar}
@@
   wrong, and this is not yet fixed. I've also told you to make all
-figures at the top. In T-Method, \Gamma shows up out of nowhere.
+figures at the top. In T-Method, $\Gamma$ shows up out of nowhere.
 }
@@
 \end{mathpar}
-\caption{Small-step semantics.\red{Haoyuan: TODO: <???> new I()/this}}\label{fig:smallstep}
+\caption{Small-step semantics.\haoyuan{fixed rules. Need to change text.}}\label{fig:smallstep}
 \end{figure*}
 
-\begin{figure*}[htbp]
+\begin{figure*}[t]
 \begin{mathpar}
@@
 
-\begin{figure*}[htbp]
+\begin{figure*}[t]
 	\begin{mathpar}
@@
 			\kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_E}{m}{I_X}{x}{I}{e_0}\ldots\}}
-		{\mbody(m, I_d, I_s) = (\overline{I_X} \; \overline{x}, I_E \; e_0)}
+		{\mbody(m, I_d, I_s) = (J, \overline{I_X} \; \overline{x}, I_E \; e_0)}
 
@@
 
-\red{H: mtype based on mbody?}
 $\mbody(m, I_d, I_s)$, as defined in Figure~\ref{fig:auxfunc}, denotes a method body lookup function.
@@
 The definition of $\mtype$ simply relies on $\mbody$. In short,
-$$\mbody(m, I, I) = (\overline{I_x}\ \overline{x}, I_E\ e) \ \Longrightarrow\ \mtype(m, I) = \overline{I_x}\rightarrow I_E$$
+$$\mbody(m, I, I) = (J, \overline{I_x}\ \overline{x}, I_E\ e) \ \Longrightarrow\ \mtype(m, I) = \overline{I_x}\rightarrow I_E$$
 

### 2017-06-12 Aplas17/sections/Introduction.tex

@@
 Some better workarounds include delegation, renaming/exclusion in the trait model, and so on, yet they still have various drawbacks as we will discuss in Section ?.
-On the other hand, there is indeed some related work [] that approaches our expectation, that is, they allow two unintentionally conflicted method to coexist in the system.
+On the other hand, there is indeed some related work [] that is approaching our expectation, that is, they allow two unintentionally conflicted method to coexist in the system.
 Among them C++ is a representative that accepts the triangle inheritance and resolves the ambiguity by static dispatch.
@@
 In the model we also propose \textit{partial overrides}, where a method refinement can be applied only to one branch.
+Briefly speaking, our model generalizes the trait model by providing support to the triangle inheritance.
 

### 2017-06-12 Aplas17/sections/Overview.tex

@@
-\section{A Running Example: DrawableDeck}
-
+\section{A Running Example: DrawableDeck}~\label{sec:overview}
+\includegraphics[height=3.3cm]{pics/DrawableLoggingDeck.pdf}
 \red{H: with UML graphs the illustration could be better.}
@@
 is required to have a body for its implementation. In that case, interfaces can be directly instantiated by the keyword ``\lstinline|new|''
-to create an object.
+to create an object. \haoyuan{TODO: mention relation to Java 8 interfaces with default methods; and traits}
 
@@
 }
-\end{lstlisting}\vspace{3pt}
+\end{lstlisting}\vspace{3pt} \haoyuan{TODO: drawObject}
 Note that both methods have \lstinline|void| return type (we will not formalize
@@
 method conflicts, nevertheless, delegation itself is too restricted in modularity, and meanwhile
-introduces a lot of boilerplate.
+introduces a lot of boilerplate.\haoyuan{TODO: drawbacks: hard to correctly maintain self-references[]}
 
@@
 
-\paragraph{IV. Method exclusion like traits.} Same reason as above.
+\paragraph{IV. Method exclusion like traits.} Same reason as above. \haoyuan{TODO: put exclusion and renaming together}
 
-\paragraph{V. Method renaming like traits.} This is probably what people do in most cases, by simply renaming one to avoid conflicts.
+\paragraph{V. Method renaming like traits.} This is probably what people do in most cases, \haoyuan{not supported by most languages; breaks subtyping} by simply renaming one to avoid conflicts.
 It can indeed preserve both features, however, it is cumbersome in practice, as introducing new names can affect other code blocks.
@@
 neither static dispatch nor dynamic dispatch in languages like C++ does so.
- Therefore, we need to find another algorithm for method binding.
+ Therefore, we need to find another algorithm for method binding\haoyuan{method resolution}.
 
@@
 
-On the other hand, \lstinline|((I) e).m()|, or simply \lstinline|e.m()| where \lstinline|e| has static type \lstinline|I|, behaves the same as \lstinline|e.I::m()| in our model.
+On the other hand, \lstinline|((I) e).m()| \haoyuan{explicit casts are not supported in our model}, or simply \lstinline|e.m()| where \lstinline|e| has static type \lstinline|I|, behaves the same as \lstinline|e.I::m()| in our model.
 Such a dispatch make uses of both the static type and the dynamic type of the receiver.

### 2017-06-12 Aplas17/sections/Overview.tex
Revising overview.

--- 2017-06-08 Aplas17/sections/Overview.tex
@@
 to programmers that use multiple inheritance. Below we illustrate with a running example called \lstinline|DrawableDeck|.
-Note that we use Java-like syntax throughout the paper, and all types are defined with the keyword ``\lstinline|interface|'', which
-supports multiple inheritance. Since \MIM{} is designed to be simple, we do not allow abstract methods, that is every method
-is required to have a body for its implementation. In that case, interfaces can be directly instantiated by the keyword ``\lstinline|new|''
-to create an object.
+Note that we use Java-like syntax throughout the paper, and all types are defined with the keyword ``\lstinline|interface|''. The concept
+is closely related to Java 8 interfaces, and traits. For simplicity, an interface in our model has the following characteristics:
+\begin{itemize}
+	\item It allows multiple inheritance.
+	\item Every method represents a behaviour and requires a body for its implementation (like Java 8 default methods). There is no abstract method.
+	\item It can be directly instantiated by the \lstinline|new| keyword.
+\end{itemize}
+Furthermore for simplicity, our formalization does not model state at this stage, but that should not block our discussions below.
 
@@
 
-Suppose that two components \lstinline|Drawable| and \lstinline|Deck| have been developed in a system.
-\lstinline|Drawable| defines an interface for graphics that can be drawn, which includes a method called \lstinline|draw()|
-for visual display. While interface \lstinline|Deck| represents a deck of cards, and supports several operations, like
-\lstinline|draw()| for drawing a card from the deck.
+Suppose that two components \lstinline|Deck| and \lstinline|Drawable| have been developed in a system.
+\lstinline|Deck| represents a deck of cards, and defines \lstinline|draw()| for drawing a card from the deck.
+While \lstinline|Drawable| is an interface for graphics that can be drawn, and also includes a method called \lstinline|draw()|
+for visual display. For illustration, the implementation of \lstinline|draw()| in \lstinline|Drawable|
+only creates a blank canvas on the screen, and later some instances (\lstinline|Circle|, \lstinline|Square|, or whatever) that extend
+\lstinline|Drawable| may define their own \lstinline|drawObject()| methods and invoke \lstinline|draw()|.
 
@@
 \vspace{3pt}\begin{lstlisting}
-interface DrawableDeck extends Drawable, Deck {
-  ...
-} 
+interface DrawableDeck extends Drawable, Deck {...} 
 \end{lstlisting}\vspace{3pt}
@@
 introducing two fields with \lstinline|Drawable| type and \lstinline|Deck| type, respectively. This avoids
-method conflicts, nevertheless, delegation itself is too restricted in modularity, and meanwhile
-introduces a lot of boilerplate.
+method conflicts. Nevertheless, it is known that using delegation makes it hard to correctly maintain self-references \haoyuan{?} in an
+extensible system [], and meanwhile introduces a lot of boilerplate.
 
@@
 
-\paragraph{IV. Method exclusion like traits.} Same reason as above.
-
-\paragraph{V. Method renaming like traits.} This is probably what people do in most cases, by simply renaming one to avoid conflicts.
-It can indeed preserve both features, however, it is cumbersome in practice, as introducing new names can affect other code blocks.
-Certainly this is a workaround, not a solution.\\
+\paragraph{IV. Method exclusion/renaming in traits.} Those features provided by the trait model can eliminate conflicts, although
+most programming languages do not support them. In a traditional OO system, they more or less break the subtyping. Moreover, in
+contrast with exclusion, renaming can indeed preserve both conflicted behaviours, however, it is cumbersome in practice, as introducing new names can affect other code blocks.
+It could be considered as a workaround, but certainly is not a good solution.\\
 
@@
 \end{lstlisting}\vspace{3pt}
-Thus we have: \paragraph{VI. Static dispatch.} Static dispatch finds out and invokes the most specific method ``by need''.
+Thus we have: \paragraph{V. Static dispatch.} Static dispatch finds out and invokes the most specific method ``by need''.
 
@@
 \vspace{3pt}\begin{lstlisting}
-interface DrawableLoggingDeck extends Drawable, LoggingDeck {
-  ...
-}
+interface DrawableLoggingDeck extends Drawable, LoggingDeck {...}
 
@@
 neither static dispatch nor dynamic dispatch in languages like C++ does so.
- Therefore, we need to find another algorithm for method binding.
+ Therefore, we need to find another algorithm for method resolution.
 
@@
 The formal definition will be introduced later.
+On the other hand, \lstinline|e.m()| where \lstinline|e| has static type \lstinline|I|, simply behaves the same as \lstinline|e.I::m()| in our model.
+It is just like the difference between implicit and explicit casts.
 
-On the other hand, \lstinline|((I) e).m()|, or simply \lstinline|e.m()| where \lstinline|e| has static type \lstinline|I|, behaves the same as \lstinline|e.I::m()| in our model.
 Such a dispatch make uses of both the static type and the dynamic type of the receiver.
@@
 
-\subsection{Method Update in \MIM	}
+\subsection{Partial Overrides in \MIM	} \haoyuan{TODO}
 

### 2017-06-12 Aplas17/sections/Formalization.tex
Revising overview.
add tex for proof and move proofs to Appendix

@@
 \end{comment}
+
+\subsection{Properties}
+Previously the definitions of our model are given, now we should proceed to prove the type soundness of 
+the model, which relates typing to computation. We want to prove such a property: if an expression is 
+well-typed, then after many reduction steps it must reduces to a value of a subtype of the original type
+of the expression. Following the FeatherweightJava paper~\cite{Igarashi01FJ}, the type-soundness theorem 
+(Theorem~\ref{theorem_soundness}) is proved by using the standard technique of subject reduction (Theorem~\ref{theorem_subject})
+and progress (Theorem~\ref{theorem_progress})~\cite{Wright1994}.
+
+\begin{theorem}[Subject Reduction]~\label{theorem_subject}
+$\textit{If } \ \judgeewf \Gamma {e : I} \; \textit{ and } \ e \rightarrow e',\ 
+\textit{then } \judgeewf \Gamma {e' : I'} \ \textit{ for some } \ I' <: I.$
+\end{theorem}
+\begin{proof}
+See Appendix~\ref{appendix_proof}.
+\end{proof}
+
+\begin{theorem}[Progress]~\label{theorem_progress}
+$\textit{Suppose } e \textit{ is a well-typed expression } $ \\
+\begin{enumerate}
+\item If $e$ includes $\left(<J>\new{I}\right).m(\overline{<I_E>} \; \overline{e})$ as a subexpression,
+    then $ \mbody(m, I, J) = (\overline{I_X} \; \overline{x}, I'_E \; e_0) $ and
+         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$
+\item If $e$ includes $\left(<J>\new{I}\right).K::m(\overline{<I_E> e})$ as a subexpression,
+    then $ \mbody(m, I, K) = (\overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
+         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$
+\item If $e$ includes $\kwsuper.K::m(\overline{<I_E> e})$ as a subexpression,
+    then $ \mbody(m, K, K) = (\overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
+         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$
+\end{enumerate}
+\end{theorem}
+\begin{proof}
+See Appendix~\ref{appendix_proof}.
+\end{proof}
+
+\begin{theorem}[Type Soundness]~\label{theorem_soundness}
+If $\judgeewf \o {e : I}$ and $e \to^* e'$ with $e'$ a normal form, then $e'$ is 
+a value $v$ with $\judgeewf \o {v:J}$ and $J \subtype I$.
+\end{theorem}
+\begin{proof}
+Immediate from Theorem~\ref{theorem_subject} and Theroem~\ref{theorem_progress}.
+\end{proof}

### 2017-06-12 Aplas17/sections/RelatedWork.tex
add tex for proof and move proofs to Appendix

@@
 
-\noindent {\bf Self.} In the prototype-based language \self~\cite{Chambers1991}, inheritance is a basic feature.
+\subsection{Hirarchical Dispatch}
+As we have discussed before, the mix of static and dynamic dispatch is needed by the literature 
+pay little attention to this. In the prototype-based language \self~\cite{Chambers1991}, inheritance is a basic feature.
 It does not include classes but instead allow individual objects to inherit from (or delegate to) other objects. 
@@
 
-\subsection{Static+Dynamic Type Method Lookup}
-
 \subsection{Formalization Based on FeatherweightJava}

### 2017-06-12 Aplas17/sections/Introduction.tex

@@
 \begin{itemize}
-	\item \textbf{Hierarchical dispatch:} which integrates both the static type and dynamic type for method binding, and hence
+	\item \textbf{Hierarchical dispatch:} which integrates both the static type and dynamic type for method dispatch, and hence
 	ensures unambiguity as well as extensibility.

### 2017-06-12 Aplas17/sections/Overview.tex
Some Text for Overview

@@
 \red{H: with UML graphs the illustration could be better.}
-This section illustrates the features of our \MIM{} model for resolving unintentional method
-conflicts. As mentioned before, such a case arises when two inherited methods happen to have the
-same signature, but with different semantics and functionalities. This could be quite troublesome
-to programmers that use multiple inheritance. Below we illustrate with a running example called \lstinline|DrawableDeck|.
-Note that we use Java-like syntax throughout the paper, and all types are defined with the keyword ``\lstinline|interface|''. The concept
-is closely related to Java 8 interfaces, and traits. For simplicity, an interface in our model has the following characteristics:
+
+This section illustrates the features of our \MIM{} model for
+resolving unintentional method conflicts. As mentioned before, such a
+case arises when two inherited methods happen to have the same
+signature, but with different semantics and functionality. This
+situation is troublesome to programmers that use multiple
+inheritance. Below we illustrate with a running example called
+\lstinline|DrawableDeck|, which models a drawable deck of cards. 
+Note that we use Java-like syntax
+throughout the paper, and all types are defined with the keyword
+``\lstinline|interface|''. The concept is closely related to Java 8
+interfaces, and traits. For simplicity, an interface in our model has
+the following characteristics:
 \begin{itemize}
 	\item It allows multiple inheritance.
-	\item Every method represents a behaviour and requires a body for its implementation (like Java 8 default methods). There is no abstract method.
+	\item Every method represents a behaviour and requires a body for its implementation (like Java 8 default methods). There are no abstract methods.
 	\item It can be directly instantiated by the \lstinline|new| keyword.
 \end{itemize}
-Furthermore for simplicity, our formalization does not model state at this stage, but that should not block our discussions below.
+Furthermore for simplicity, our formalization does not model state at
+this stage. %%, but that should not block our discussions below.
 
@@
 
-Suppose that two components \lstinline|Deck| and \lstinline|Drawable| have been developed in a system.
-\lstinline|Deck| represents a deck of cards, and defines \lstinline|draw()| for drawing a card from the deck.
-While \lstinline|Drawable| is an interface for graphics that can be drawn, and also includes a method called \lstinline|draw()|
-for visual display. For illustration, the implementation of \lstinline|draw()| in \lstinline|Drawable|
-only creates a blank canvas on the screen, and later some instances (\lstinline|Circle|, \lstinline|Square|, or whatever) that extend
-\lstinline|Drawable| may define their own \lstinline|drawObject()| methods and invoke \lstinline|draw()|.
+Suppose that two components \lstinline|Deck| and \lstinline|Drawable| 
+have been developed in a system.  \lstinline|Deck| represents a deck
+of cards, and defines \lstinline|draw()| for drawing a card from the
+deck.  While \lstinline|Drawable| is an interface for graphics that
+can be drawn, and also includes a method called \lstinline|draw()| for
+visual display. For illustration, the implementation of
+\lstinline|draw()| in \lstinline|Drawable| only creates a blank canvas
+on the screen, and later some instances (\lstinline|Circle|,
+\lstinline|Square|, or others) that extend \lstinline|Drawable| may
+define their own \lstinline|drawObject()| methods and invoke
+\lstinline|draw()|.
 
@@
 \end{lstlisting}\vspace{3pt}
+\bruno{Space is probably going to be a problem, so you may have to
+  consider putting code side-by-side to maximize space usage.}
 Note that both methods have \lstinline|void| return type (we will not formalize
@@
 \end{lstlisting}\vspace{3pt}
-The point of using multiple inheritance is surely for composing the features of
-components, achieving great code reuse. It is supported by many mainstream OO
+The point of using multiple inheritance is surely for composing the features from
+components, and to achieve code reuse. Multiple inheritance is supported by many mainstream OO
 languages. Nevertheless at this point, \lstinline|DrawableDeck| has to throw a compile
-error, for the two \lstinline|draw()| methods cause a conflict, though accidentally.
+error, since the two \lstinline|draw()| methods cause a conflict, though accidentally.
 
@@
 
-For that problem, there are several workarounds that quickly come to our mind:
+For that problem, there are several workarounds. We go over some of
+the main ones next.
 
-\paragraph{I. Delegation.} As an alternative to multiple inheritance, delegation can be used by
-introducing two fields with \lstinline|Drawable| type and \lstinline|Deck| type, respectively. This avoids
-method conflicts. Nevertheless, it is known that using delegation makes it hard to correctly maintain self-references \haoyuan{?} in an
-extensible system [], and meanwhile introduces a lot of boilerplate.
+\paragraph{I. Delegation.} As an alternative to multiple inheritance,
+delegation can be used by introducing two fields with
+\lstinline|Drawable| type and \lstinline|Deck| type,
+respectively. This avoids method conflicts. Nevertheless, it is known
+that using delegation makes it hard to correctly maintain
+self-references \haoyuan{?} in an extensible system [], and also
+introduces a lot of boilerplate code.
 
@@
 
-\paragraph{III. Choosing one of them as the default method, like Mixins.} The mixin model can be applied to choose a
-default one based on linearisation. Similarly, we want to preserve both features, rather than keeping only one of them.
+\paragraph{III. Refactor Drawable and/or Deck to rename the methods.} If
+the code for \lstinline|Drawable| or \lstinline|Deck| are available
+then it may be possible to rename one of the \lstinline|draw|
+methods. However this approach is non-modular, as it requires 
+modifying existing code, and may not be possible if code is unavailable.
 
-\paragraph{IV. Method exclusion/renaming in traits.} Those features provided by the trait model can eliminate conflicts, although
-most programming languages do not support them. In a traditional OO system, they more or less break the subtyping. Moreover, in
+%\paragraph{III. Choosing one of them as the default method, like Mixins.} The mixin model can be applied to choose a
+%default one based on linearisation. Similarly, we want to preserve both features, rather than keeping only one of them.
+
+\paragraph{IV. Method exclusion/renaming in traits.} Those features
+provided by the trait model can eliminate conflicts, although most
+programming languages do not support them. In a traditional OO system,
+they more or less break the subtyping. Moreover, in
 contrast with exclusion, renaming can indeed preserve both conflicted behaviours, however, it is cumbersome in practice, as introducing new names can affect other code blocks.

### 2017-06-12 Aplas17/sections/Overview.tex
Paper

@@
 this stage. %%, but that should not block our discussions below.
+\bruno{I think there are two important things being discussed in this
+  section:
+1) Hierarchical dispatch: which allows methods calls to be correctly 
+dispatched based on a combination of static and dynamic type
+information; and
+2) Traingle Inheritance: i.e. allowing multiple method implementations 
+to coexist in the same class based on the superclass hierarchy.
+
+The text in this section is good, but it could emphasize better those 
+two aspects. I think the text starts off with point 2) (the two draw
+methods), then in between the discussion moves to hierarchical
+dispatching. Later it returns to point 2. 
+}
 
 \subsection{Problem: Unintentional Method Conflicts}
+\bruno{maybe call this problem 1?}
 
@@
 
-\paragraph{IV. Method exclusion/renaming in traits.} Those features
-provided by the trait model can eliminate conflicts, although most
+\paragraph{IV. Method exclusion/renaming in traits.} Some trait models
+support method exclusion/renaming. Those features
+provided can eliminate conflicts, although most
 programming languages do not support them. In a traditional OO system,
 they more or less break the subtyping. Moreover, in
-contrast with exclusion, renaming can indeed preserve both conflicted behaviours, however, it is cumbersome in practice, as introducing new names can affect other code blocks.
-It could be considered as a workaround, but certainly is not a good solution.\\
+contrast with exclusion, renaming can indeed preserve both conflicted
+behaviours, however, it is cumbersome in practice, as introducing new
+names can affect other code blocks. \\
 
-What we really expect from the language is we keep both methods without renaming, and the type checker does not complain on the
-inheritance. But we need to find an approach to disambiguate on method calls statically.
+What we really expect from the language is that we keep both methods
+without renaming, and the type checker does not complain about 
+inheritance. But we need to find an approach to \emph{disambiguate on method
+calls statically}.
+\bruno{Perhaps show the solution in MIM here, and then move to problem
+2 (which is being discussed next with shuffleAndDraw)}
 
-Certainly the compiler can ignore the conflict when \lstinline|DrawableDeck| is declared, but once an object of \lstinline|DrawableDeck| is created, a method call for \lstinline|draw()| on that object is ambiguous, due to dynamic dispatch.
-Nonetheless, we can adopt static dispatch for disambiguating.
-Some languages like C++ use qualified names in that way:
+Certainly the compiler can ignore the conflict when
+\lstinline|DrawableDeck| is declared, but once an object of
+\lstinline|DrawableDeck| is created, a method call for
+\lstinline|draw()| on that object is ambiguous, due to dynamic
+dispatch. Nonetheless, we can adopt static dispatch for
+disambiguating. Some languages like C++ use qualified names in that
+way:
 
@@
 \subsection{Solution in \MIM: \dispatchnamecaptical}
-Our \MIM{} model uses \dispatchnameit{} for method lookup.
-A qualified method invocation, for instance, \lstinline|e.I::m()|, is read as ``finding the most specific \lstinline|m()| along path \lstinline|I|''.
-The meaning of ``along path \lstinline|I|'' is that, if the result of \dispatch{} is \lstinline|J.m()| for some \lstinline|J|, then such a \lstinline|J| must be a super type of \lstinline|e|'s dynamic type, and \lstinline|J| has a subtyping relation with \lstinline|I| (either \lstinline|J <: I| or \lstinline|J >: I|).
+The \MIM{} model uses \dispatchnameit{} for method lookup. A qualified
+method invocation, for instance, \lstinline|e.I::m()|, is read as
+``finding the most specific method \lstinline|m| along the path
+\lstinline|I|''. The meaning of ``along the path \lstinline|I|'' is
+that, if the result of \dispatch{} is \lstinline|J.m()| for some \lstinline|J|, then such a \lstinline|J| must be a super type of \lstinline|e|'s dynamic type, and \lstinline|J| has a subtyping relation with \lstinline|I| (either \lstinline|J <: I| or \lstinline|J >: I|).
 Intuitively, the most specific \lstinline|m()| must be from branch \lstinline|I|, but it can be an overridden version after \lstinline|I| like dynamic dispatch.

### 2017-06-12 Aplas17/sections/Formalization.tex
figures
Fixed overview. Move on to formalization.

@@
 
-\subsection{Syntax}
+\subsection{Syntax} \haoyuan{TODO: syntactic sugar; mention that path invocation subsumes
+regular invocation; add explanation for interface check; use the examples to illustrate the
+mbody algorithm in an intuitive way, and especially explain the two counter-examples that are
+important to type soundness.}
 
@@
 e0.m(e) = e0.I::m(e) when the type of e0 is I.}
-\bruno{Last time I met I told you that the typing of ``this'' is
-  wrong, and this is not yet fixed. I've also told you to make all
-figures at the top. In T-Method, $\Gamma$ shows up out of nowhere.
-}
-\bruno{Rule for new is wrong! It says that a new expression that
-  creates a class with any name (even if the class does not exist) 
-is valid. The paper is not even following the rules of FJ.}
 
@@
 \subsection{Auxilary Definitions}
+
+\begin{figure*}[t]
+\centering
+\vspace{-1ex}
+\begin{tabular}{ccccc}
+\includegraphics[width=2cm]{pics/p1.pdf}\hspace{4pt} &
+\includegraphics[width=2cm]{pics/p2.pdf}\hspace{4pt} &
+\includegraphics[width=2cm]{pics/p3.pdf}\hspace{4pt} &
+\includegraphics[height=3cm]{pics/p4.pdf}\hspace{4pt} &
+\includegraphics[height=3cm]{pics/p5.pdf}\hspace{4pt} \\
+(a) & (b) & (c) & (d) & (e)
+\end{tabular}
+\caption{Figures..}\label{fig:pegasus}
+%\saveSpaceFig
+\end{figure*}
 

### 2017-06-12 Aplas17/sections/Overview.tex
Comments on S2
Fixed overview. Move on to formalization.

@@
 calls statically}.
-\bruno{Perhaps show the solution in MIM here, and then move to problem
+\bruno{Perhaps show the solution in MIM here (i.e Section 2.4), and then move to problem
 2 (which is being discussed next with shuffleAndDraw)}
@@
 
-\subsection{Partial Overrides in \MIM	} \haoyuan{TODO}
+\subsection{Partial Overrides in \MIM	}
 
-\MIM{} supports two kinds of polymorphism on methods: (1) method overriding; (2) method update.
-A method update is similar to overriding, in the sense that it provides a refined implementation of a method.
-But the difference is that an update just refines one branch, since \MIM{} can preserve several conflicted branches at the same time.
-Whereas a method overriding will hide all its inherited original methods, in which case method conflicts are unexpectedly ignored.
+Method overriding is commonly supported by many OO languages as a kind of polymorphism.
+We have seen that \MIM{} is able to preserve several conflicted branches simultaneously and let them coexist.
+In that case, a traditional method overriding, like one in Java, will override all the inherited methods, and hence
+hide all those conflicted branches. Besides, \MIM{} also allows partial overrides to offer independent extensibility.
+A partial override will specify one of the branches, and only refine the method from that branch. It ensures that
+other branches are not affected.
 
-For example, we define an interface \lstinline|DrawableLoggingDeck2|, where we refine the \lstinline|draw()| from \lstinline|Drawable()| by setting
+For example, we define an interface \lstinline|DrawableLoggingDeck2|, and in its definition we refine the \lstinline|draw()| from \lstinline|Drawable()| by setting
 the canvas invisible:
@@
 interface DrawableLoggingDeck2 extends DrawableLoggingDeck {
-  void draw() updates Drawable {
+  void draw() override Drawable {
     JFrame frame = new JFrame("Canvas");
@@
 \end{lstlisting}\vspace{3pt}
-Here the update specifies \lstinline|Drawable| to be refined.
-The use of this update ensures that both branches of \lstinline|draw()| are preserved.
-At the same time, we should notice that a method update is no longer considered as an original method.
-Some client code is shown below:
+Here the partial override specifies \lstinline|Drawable| to be refined.
+The use of it ensures that both branches of \lstinline|draw()| are preserved.
+At the same time, we should notice that the methods we present in previous examples are called ``original methods'', and they are actually created by ``total overrides'', rather than partial overrides.
+Some client code is shown below: \haoyuan{which words should we use instead of "total overrides"?}
 \vspace{3pt}\begin{lstlisting}
@@
 
-In \MIM{}, hierarchical dispatch first finds the most specific original method (with respect to method overriding), then it finds the most specific update on that method.
-A counter-example is when there are two method updates on \lstinline|Drawable| in \lstinline|DrawableLoggingDeck2|, it leads to ambiguity.
+In \MIM{}, hierarchical dispatch first finds the most specific original method (branch), then it finds the most specific partial override on that branch.
+A quick counter-example is when there are two partial overrides on \lstinline|Drawable| in \lstinline|DrawableLoggingDeck2|, it leads to ambiguity.
 The compiler is supposed to forbid that during compile time.
 
-Two rules for method updates in \MIM: updates can only refine \textbf{original} methods, and they cannot overlap method overriding.
-For instance, writing \lstinline|"void draw()| \lstinline|updates Deck {...}"| is disallowed in \lstinline|DrawableLoggingDeck2|, because existing two branches are \lstinline|Drawable.draw()| and \lstinline|LoggingDeck.draw()|, yet \lstinline|Deck.draw()| is already overridden.
-It does not really make sense to update the old branch.
+Two rules for partial overrides in \MIM: updates can only refine \textbf{original} methods, and they cannot overlap total overrides.
+For instance, writing \lstinline|"void draw()| \lstinline|override Deck {...}"| is disallowed in \lstinline|DrawableLoggingDeck2|, because existing two branches are \lstinline|Drawable.draw()| and \lstinline|LoggingDeck.draw()|, and \lstinline|Deck.draw()| is already covered.
+It does not really make sense to refine an old branch.
 

### 2017-06-12 Aplas17/sections/Formalization.tex
proof fix according to mbody change

--- 2017-06-12 Aplas17/sections/Formalization.tex
@@
 
-\subsection{Syntax}
+\subsection{Syntax} \haoyuan{TODO: syntactic sugar}
 
@@
 
+\begin{figure*}[t]
+\centering
+\vspace{-1ex}
+\begin{tabular}{ccccc}
+\includegraphics[width=2cm]{pics/p1.pdf}\hspace{4pt} &
+\includegraphics[width=2cm]{pics/p2.pdf}\hspace{4pt} &
+\includegraphics[width=2cm]{pics/p3.pdf}\hspace{4pt} &
+\includegraphics[height=3cm]{pics/p4.pdf}\hspace{4pt} &
+\includegraphics[height=3cm]{pics/p5.pdf}\hspace{4pt} \\
+(a) & (b) & (c) & (d) & (e)
+\end{tabular}
+\caption{Figures..}\label{fig:pegasus}
+%\saveSpaceFig
+\end{figure*}
+
 To make our formalization concise and expressive, we have defined a list of
@@
 \item If $e$ includes $\left(<J>\new{I}\right).m(\overline{<I_E>} \; \overline{e})$ as a subexpression,
-    then $ \mbody(m, I, J) = (\overline{I_X} \; \overline{x}, I'_E \; e_0) $ and
+    then $ \mbody(m, I, J) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and
          $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$
 \item If $e$ includes $\left(<J>\new{I}\right).K::m(\overline{<I_E> e})$ as a subexpression,
-    then $ \mbody(m, I, K) = (\overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
+    then $ \mbody(m, I, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
          $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$
 \item If $e$ includes $\kwsuper.K::m(\overline{<I_E> e})$ as a subexpression,
-    then $ \mbody(m, K, K) = (\overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
+    then $ \mbody(m, K, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
          $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$

### 2017-06-12 Aplas17/sections/Formalization.tex

@@
 
-\subsection{Syntax} \haoyuan{TODO: syntactic sugar}
+\subsection{Syntax} \haoyuan{TODO: syntactic sugar; mention that path invocation subsumes
+regular invocation; add explanation for interface check; use the examples to illustrate the
+mbody algorithm in an intuitive way, and especially explain the two counter-examples that are
+important to type soundness.}
 

### 2017-06-13 Aplas17/sections/Introduction.tex
Introduction

@@
 \section{Introduction}
+\bruno{Please fill in the references.}
+Inheritance in Object-Oriented Programming (OOP) offers a mechanism
+for code reuse. However many OOP languages are restricted to single
+inheritance, which is less expressive and flexible than multiple
+inheritance. Nevertheless different flavours of multiple inheritance
+have been adopted in some popular OOP languages. C++ has had 
+multiple inheritance from the start. Scala adapts ideas from traits~\cite{} 
+and mixins~\cite{} to offer a disciplined form of multiple inheritance. Java 8 
+offers a variant of traits with disguised of interfaces with default methods~\cite{}.
 
-Object-oriented programming has been adopted for years in both industry and research areas to offer great code reuse.
-It allows data structures and behaviours to be represented by modules and the relationship among them. But earlier
-single inheritance appeared to be less expressive and flexible to use. Since the occurrence of multiple inheritance, it
-seems more practical to programmers in many mainstream languages like C++ and Java.
+A reason why programming languages have resisted to multiple
+inheritance in the past is that, as Cook~\cite{} puts it, 
+multiple inheritance is good but ``\emph{there is no good way to do it}''.
+One of the most sensitive and critical issues is perhaps the ambiguity
+introduced by multiple inheritance. One case is the famous
+\textit{diamond problem}~\cite{}. In the diamond problem inheritance could allow
+one feature to be inherited from multiple parent classes, hence
+conflicts arise. The variety of strategies on resolving such conflicts
+urges the occurrence of different multiple inheritance models,
+including traits, mixins, CZ~\cite{}, and many others. Existing
+languages have taken care of this case intensively. Other issues
+include how multiple inheritance deals with state, as discussed in
+which also has been discussed quite extensively~\cite{C++,...}.
 
-Nevertheless, just as Steve Cook pointed out
-in [], it is good but ``there is no good way to do it''.
-One of the most sensitive and critical issue is perhaps the ambiguity introduced by multiple inheritance.
-One case is the famous \textit{diamond problem}. It says that such inheritance could allow one feature to be inherited from
-multiple parent classes, hence conflicts arise. The variety of strategies on resolving such conflicts urges the occurrence of
-different multiple inheritance models, including traits, mixins, CZ, and so on. We can observe that existing languages have taken
-care of this case intensively. Other issues include how multiple inheritance
-deals with state, as discussed in [C++] and [], and so on.
+In contrast with the diamond inheritance, a second case of ambiguity
+is \textit{unintentional method conflicts}~\cite{traits}. That is conflicting 
+methods that do not actually refer to the same feature.
+%%This issue was proposed by the trait paper, so-called
+In a nominal system, methods can be designed for different
+functionality, but they just happen to have same names (and
+signatures). When inheritance is used to compose those methods an
+error happens due to conflicts. However, unlike the diamond problem,
+the conflicted methods usually do not share a common parent. In this
+paper we call such a case ``\textit{triangle inheritance}''.
+\haoyuan{Fine to have a graph with diamond and triangle shapes if we got space.}
 
-In contrast with the diamond inheritance, a second case of ambiguity is that conflicted methods do not actually refer to the same feature.
-This issue was proposed by the trait paper, so-called \textit{unintentional method conflicts}. In a nominal system, they are designed
-for different behaviours, and they just happen to have same names (and signatures),
-yet an inheritance to compose them has to be rejected. Unlike the
-diamond problem, the conflicted methods usually do not share a common parent, hence in this paper we also call such a case ``\textit{the triangle
-inheritance}''.\haoyuan{Fine to have a graph with diamond and triangle shapes if we got space.}
+Unintentional method conflicts are less common than the diamond
+problem, nonetheless, they have severe effects in practice. This is
+unfortunate because such an issue has not received much formal study 
+before. In practice existing languages also provide limited support for
+it. In most languages, the mechanism available to deal with this problem are the same as the diamond
+inheritance. Unfortunatelly this is often inadequate and can lead 
+to tricky problems in practice. This is especially the case
+when it is necessary to combine two large modules and their features,
+but the inheritance is simply prohibited by a small conflict. As
+a workaround from the diamond inheritance side, it is possible to
+define a new method in the child class, to override those conflicting
+methods. Intuitively using one method to fuse two unrelated features
+is unsatisfactory. Therefore we need a real solution to keep both
+features separately during inheritance, so as not to break
+\emph{independent extensibility}\cite{odersky}.
 
-Unintentional method conflicts are less common than the diamond problem, nonetheless, they have severe effects in practice. This
-is unfortunately because such an issue has not been formally studied much, hence existing languages can merely provide limited support on it.
-In most situations, it is only treated the same as the diamond inheritance. This is unfair and practically unacceptable, especially when it is
-necessary to combine two large modules and their features, but the inheritance is simply prohibited by such a small conflict.
-As a workaround from the diamond inheritance side, it is possible to define a new method in the child class, to override those conflicted methods.
-Intuitively using one method to fuse two unrelated features is unsatisfactory, therefore we need a real solution to keep both features individually during inheritance,
-so as not to break independent extensibility.
+Some other workarounds or approaches include delegation, and
+renaming/exclusion in the trait model. Yet they still have various
+drawbacks as we will discuss in Section~\ref{}. Closest to our work
+are mechanisms available in C++ and C\# that allow for two
+unintentionally conflicted method to coexist in the system. Among them
+C++ is a representative that accepts the triangle inheritance and
+resolves the ambiguity by \emph{static dispatching}. However, C++ has
+limited support for virtual methods with unintentional conflicts, and
+it will often throw errors when composing them. This is again
+unsatisfactory because virtual methods are pervasive in OOP and used 
+for code reuse and extensibility.
 
-Some better workarounds include delegation, renaming/exclusion in the trait model, and so on, yet they still have various drawbacks as we will discuss in Section ?.
-On the other hand, there is indeed some related work [] that is approaching our expectation, that is, they allow two unintentionally conflicted method to coexist in the system.
-Among them C++ is a representative that accepts the triangle inheritance and resolves the ambiguity by static dispatch.
-However, when virtual methods are defined with unintentional conflicts, C++ has to throw (linker?) errors on them.
-This is again unsatisfactory because dynamic dispatch is necessary under many circumstances for code reuse and extensibility.
-
-Having tolerance for unintentional method conflicts does not mean to sacrifice extensibility, hence in contrast with static dispatch and dynamic dispatch, we propose a third approach, which looks like a combination of both, called \textit{hierarchical dispatch}.
-By hierarchical dispatch, the method binder will look at both the static type and the dynamic type of the receiver during runtime.
-When there are multiple branches that cause unintentional conflicts, the static type can specify one branch among them for unambiguity, and the dynamic type helps to find the most specific (the newest) implementation.
-In that case both unambiguity and extensibility are preserved.
-To present this idea, we introduce a formalized model in Section ?
-based on Featherweight Java, together with some theorems and proofs for type soundness.
-In the model we also propose \textit{partial overrides}, where a method refinement can be applied only to one branch.
-Briefly speaking, our model generalizes the trait model by providing support to the triangle inheritance.
+Having tolerance for unintentional method conflicts does not mean to
+sacrifice extensibility, hence in contrast with static dispatch and
+dynamic dispatch, we propose a third approach, which looks like a
+combination of both, called \textit{hierarchical dispatch}. By
+hierarchical dispatch, the method binder will look at both the \emph{static
+type} and the \emph{dynamic type} of the receiver during runtime. When there
+are multiple branches that cause unintentional conflicts, the static
+type can specify one branch among them for unambiguity, and the
+dynamic type helps to find the most specific (the newest)
+implementation. In that case both unambiguity and extensibility are
+preserved. To present this idea, we introduce a formalized model in
+Section~\ref{} based on Featherweight Java~\cite{}, together with theorems and
+proofs for type soundness. In the model we also propose
+\textit{partial overrides}, where a method refinement can be applied
+only to one branch. Our model generalizes the trait
+model by providing additional support to the triangle inheritance.
 

### 2017-06-13 Aplas17/paper.tex
related work
changes
add tex for proof and move proofs to Appendix
abstract

--- 2017-06-05 SpringerLNCS/paper.tex
@@
 
+%%\newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
+
 \input{predef/names.tex}
@@
 \input{predef/f-and/typing.tex}
+
+\newcommand{\authornote}[3]{{\color{#2} {\sc #1}: #3}}
+\newcommand{\authorText}[2]{{\color{#1}#2}}
+\newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
+\newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
+\newcommand\marco[1]{\authornote{marco}{blue}{#1}}
+\newcommand\haoyuan[1]{\authornote{haoyuan}{cyan}{#1}}
 
@@
 \begin{abstract}
-  Text.
+Multiple inheritance is a valuable feature for Object-Oriented
+Programming. However it is also tricky to get right, as illustrated by
+the extensive literature on the topic. One of the most promising 
+approaches to multiple inheritance are traits. Traits offer a
+restricted model of multiple inheritance that is easy to reason and 
+has many elegant properties. Traits have good support for method 
+conflicts which arize from \emph{diamond inheritance}:
+conflicts that arize from method implementations sharing a common 
+ancestor. However the mechanisms of traits are inadequate to deal 
+with \emph{unintentional method conflicts}: conflicts which 
+arize from two unrelated methods that happen to share the same name
+and signature.
+
+This paper presents a new trait model that deals with unintended
+method conflicts. In our new trait model conflicting methods arizing
+from unrelated methods can coexist in the same trait. Moreover they
+can be \emph{independently overriden}. What ensures unambiguity 
+is the use of information about the class hierarchy. In turn
+hierarchical information is also employed in method dispatching, which 
+uses a combination of static and dynamic type information to chose 
+the implementation of a method at run-time. We give illustrative 
+examples of our language and features and formalize a minimal 
+Featherweight-Java style calculus.
+
 \end{abstract}
@@
 \input{sections/Formalization.tex}
+% \input{sections/TypeSafety.tex}
 
-\input{sections/Implementation.tex}
-
-\input{sections/Discussion.tex}
+% \input{sections/Implementation.tex}
 

### 2017-06-13 Aplas17/sections/Introduction.tex
add some references

@@
 have been adopted in some popular OOP languages. C++ has had 
-multiple inheritance from the start. Scala adapts ideas from traits~\cite{} 
-and mixins~\cite{} to offer a disciplined form of multiple inheritance. Java 8 
-offers a variant of traits with disguised of interfaces with default methods~\cite{}.
+multiple inheritance from the start. Scala adapts ideas from traits~\cite{scharli03traits} 
+and mixins~\cite{bracha90mixin} to offer a disciplined form of multiple inheritance. Java 8 
+offers a variant of traits with disguised of interfaces with default methods~\cite{goetz12fdefenders}.
 
 A reason why programming languages have resisted to multiple
-inheritance in the past is that, as Cook~\cite{} puts it, 
+inheritance in the past is that, as Cook~\cite{Cook1987} puts it, 
 multiple inheritance is good but ``\emph{there is no good way to do it}''.
@@
 introduced by multiple inheritance. One case is the famous
-\textit{diamond problem}~\cite{}. In the diamond problem inheritance could allow
+\textit{diamond problem}~\cite{Sak89dis,Singh1995}. In the diamond problem inheritance could allow
 one feature to be inherited from multiple parent classes, hence
@@
 urges the occurrence of different multiple inheritance models,
-including traits, mixins, CZ~\cite{}, and many others. Existing
+including traits, mixins, CZ~\cite{malayeri2009cz}, and many others. Existing
 languages have taken care of this case intensively. Other issues
 include how multiple inheritance deals with state, as discussed in
-which also has been discussed quite extensively~\cite{C++,...}.
+which also has been discussed quite extensively~\cite{classless, C++,...}.
 
 In contrast with the diamond inheritance, a second case of ambiguity
-is \textit{unintentional method conflicts}~\cite{traits}. That is conflicting 
+is \textit{unintentional method conflicts}~\cite{scharli03traits}. That is conflicting 
 methods that do not actually refer to the same feature.
@@
 features separately during inheritance, so as not to break
-\emph{independent extensibility}\cite{odersky}.
+\emph{independent extensibility}\cite{zenger05independentlyextensible}.
 
@@
 renaming/exclusion in the trait model. Yet they still have various
-drawbacks as we will discuss in Section~\ref{}. Closest to our work
+drawbacks as we will discuss in Section~\ref{sec:overview}. Closest to our work
 are mechanisms available in C++ and C\# that allow for two
@@
 preserved. To present this idea, we introduce a formalized model in
-Section~\ref{} based on Featherweight Java~\cite{}, together with theorems and
+Section~\ref{sec:formalization} based on Featherweight Java~\cite{Igarashi01FJ}, together with theorems and
 proofs for type soundness. In the model we also propose

### 2017-06-13 Aplas17/paper.tex
Abstract typos.

@@
 has many elegant properties. Traits have good support for method 
-conflicts which arize from \emph{diamond inheritance}:
-conflicts that arize from method implementations sharing a common 
+conflicts which arise from \emph{diamond inheritance}:
+conflicts that arise from method implementations sharing a common 
 ancestor. However the mechanisms of traits are inadequate to deal 
 with \emph{unintentional method conflicts}: conflicts which 
-arize from two unrelated methods that happen to share the same name
+arise from two unrelated methods that happen to share the same name
 and signature.
@@
 This paper presents a new trait model that deals with unintended
-method conflicts. In our new trait model conflicting methods arizing
+method conflicts. In our new trait model conflicting methods arising
 from unrelated methods can coexist in the same trait. Moreover they
-can be \emph{independently overriden}. What ensures unambiguity 
+can be \emph{independently overridden}. What ensures unambiguity 
 is the use of information about the class hierarchy. In turn
 hierarchical information is also employed in method dispatching, which 
-uses a combination of static and dynamic type information to chose 
+uses a combination of static and dynamic type information to choose 
 the implementation of a method at run-time. We give illustrative 

### 2017-06-13 Aplas17/sections/Introduction.tex
add a ref

@@
 include how multiple inheritance deals with state, as discussed in
-which also has been discussed quite extensively~\cite{classless, C++,...}.
+which also has been discussed quite extensively~\cite{classless,malayeri2009cz,stroustrup1995}.
 

### 2017-06-13 Aplas17/paper.tex
temp title
abstract fix

@@
 
-\title{NoTitle}
+\title{Untangling Unintended Conflicts with Hierarchical Dispatch}
 %\subtitle{\InterfaceBased Programming for the Masses}
@@
 % %          {marco.servetto@ecs.vuw.ac.nz}
-\author{Author 1, Author 2}
+\author{Authors Omitted}
 
-\institute{Lab, University, Address}
+\institute{}
 
@@
 the extensive literature on the topic. One of the most promising 
-approaches to multiple inheritance are traits. Traits offer a
+approaches to multiple inheritance is \emph{traits}. Traits offers a
 restricted model of multiple inheritance that is easy to reason and 
-has many elegant properties. Traits have good support for method 
+has many elegant properties. Traits has good support for method 
 conflicts which arise from \emph{diamond inheritance}:

### 2017-06-14 Aplas17/paper.tex
fix

--- 2017-06-13 Aplas17/paper.tex
@@
 
-\title{NoTitle}
+% \title{Untangling Unintended Conflicts with Hierarchical Dispatch}
+\title{FHJ: A Formal Model for Resolving Unintended Conflicts in Multiple Inheritance}
 %\subtitle{\InterfaceBased Programming for the Masses}
@@
 the extensive literature on the topic. One of the most promising 
-approaches to multiple inheritance are traits. Traits offer a
+approaches to multiple inheritance is \emph{traits}. Traits offer a
 restricted model of multiple inheritance that is easy to reason and 
-has many elegant properties. Traits have good support for method 
+have many elegant properties. Traits have good support for method 
 conflicts which arise from \emph{diamond inheritance}:
@@
 
-This paper presents a new trait model that deals with unintended
-method conflicts. In our new trait model conflicting methods arising
-from unrelated methods can coexist in the same trait. Moreover they
+This paper presents a new model \name{} 
+(short for \emph{\textbf{F}eatherweight \textbf{H}irarchical \textbf{J}ava}) 
+that deals with unintended
+method conflicts. In our new model conflicting methods arising
+from unrelated methods can coexist in the same component. Moreover they
 can be \emph{independently overridden}. What ensures unambiguity 

### 2017-06-14 Aplas17/sections/Formalization.tex
add some references
fix

@@
-\section{Formalization}
+\section{Formalization}~\label{sec:formalization}
 
-In this section, we present a formalization of our MIM calculus, based on
-a minimal subset of Java 8 interfaces.\bruno{Mention that it is done 
+In this section, we present a formalization of our \MIM{} calculus, based on
+a minimal subset of Java 8 interfaces following Featherweight Java style~\cite{Igarashi01FJ}.\bruno{Mention that it is done 
 in a FJ style?} The syntax, typing rules and small-step
@@
 
-Figure~\ref{fig:syntax} shows the syntax of MIM. The multiple
-inheritance feature of MIM as a basis Java 8 interfaces, which support
+Figure~\ref{fig:syntax} shows the syntax of \MIM{}. The multiple
+inheritance feature of \MIM{} as a basis Java 8 interfaces, which support
 method implementations via default methods. This feature is quite
-closely related to \emph{traits}\cite{}.  To demonstrate how
-unintentional method conflicts are untangled in MIM, we present the
+closely related to \emph{traits}\cite{scharli03traits}.  To demonstrate how
+unintentional method conflicts are untangled in \MIM{}, we present the
 calculus in a straightforward way, hence we only focus on a small
@@
 of $J$ with annotated static type $I$.  Note that values are only
-intended for the small-step semantics of MIM, hence they are not
+intended for the small-step semantics of \MIM{}, hence they are not
 supposed to appear in the source program.
@@
 \subsection{Subtyping and Typing Rules}
-The subtyping of MIM consists of only a few rules shown in Figure ?.
+The subtyping of \MIM{} consists of only a few rules shown in Figure~\ref{fig:subtyping}.
 In short, subtyping relations are built from the inheritance in interface
@@
 
-Details of type-checking rules are displayed in Figure ?, including expression
+Details of type-checking rules are displayed in Figure~\ref{fig:typingrules}, including expression
 typing, well-formedness of methods and interfaces. As a convention, an environment
@@
 
-The method typing rule (T-METHOD) is more interesting, since the method can either be an original implementation or a update.
+The method typing rule (T-METHOD) is more interesting, since the method can either be an original implementation or an update.
 Besides static type-checking for the return expression,
-we further use the helper function $\mostSpecific$ to ensure that the method update is legal. The formal definition is available in Section ?
+we further use the helper function $\mostSpecific$ to ensure that the method update is legal. The formal definition is available in Section~\ref{sec:aux}.
 By that we define the legality of method updating: the updated method must be an original method (not another method update), and method updating cannot cross over method overriding (a method overriding cannot appear between the method update and the updated original method in inheritance hierarchy).
@@
 \subsection{Small-step Semantics and Congruence}
-Figure ? and Figure ? define small-step semantic rules and congruence rules,
+Figure~\ref{fig:smallstep} and Figure~\ref{fig:congruence} define small-step semantic rules and congruence rules,
 respectively. When evaluating an expression, they are invoked recursively and
@@
 
-\subsection{Auxilary Definitions}
+\subsection{Auxilary Definitions}~\label{sec:aux}
 
@@
 Such a set may contain several elements, but that implies ambiguity; what we expect is actually a singleton set.
-By the definition of $\mostSpecific$ shown in Figure ?, an interface belongs to the return set if and only if:
+By the definition of $\mostSpecific$ shown in Figure~\ref{fig:auxfunc}, an interface belongs to the return set if and only if:
 \begin{itemize}

### 2017-06-14 Aplas17/sections/Introduction.tex
temp title
fix

@@
 \section{Introduction}
-\bruno{Please fill in the references.}
 Inheritance in Object-Oriented Programming (OOP) offers a mechanism
@@
 	\item \textbf{Partial overrides:} a novel notion that allows method refinements on individual branches.
-	\item \textbf{MIM:} a formalized model based on Featherweight Java, supporting the above features. Some theorems and their proofs
+	\item \textbf{\name:} a formalized model based on Featherweight Java, supporting the above features. Some theorems and their proofs
 	are attached to confirm the type soundness (unambiguity?) of the model.

### 2017-06-14 Aplas17/sections/Formalization.tex
Fixing formalization.

@@
 In this section, we present a formalization of our \MIM{} calculus, based on
-a minimal subset of Java 8 interfaces following Featherweight Java style~\cite{Igarashi01FJ}.\bruno{Mention that it is done 
-in a FJ style?} The syntax, typing rules and small-step
+a minimal subset of Java 8 interfaces following Featherweight Java style~\cite{Igarashi01FJ}.
+The syntax, typing rules and small-step
 semantics are included below.
 
-\subsection{Syntax} \haoyuan{TODO: syntactic sugar; mention that path invocation subsumes
-regular invocation; add explanation for interface check; use the examples to illustrate the
+\subsection{Syntax} \haoyuan{TODO: use the examples to illustrate the
 mbody algorithm in an intuitive way, and especially explain the two counter-examples that are
@@
 method. If the interface that it overrides is exactly the enclosing
-interface, then such a method is seen as ``originally defined''.
+interface, then such a method is seen as ``originally defined''; otherwise
+it is a partial override.
 Again for simplicity, overloading is not modelled for methods, which
@@
 implementation from the specified super type. Hence a super-invocation
-can only be used inside an interface definition. Finally an expression
-can also be a value ``$<I> \new J$''. It is exactly an object instance
-of $J$ with annotated static type $I$.  Note that values are only
-intended for the small-step semantics of \MIM{}, hence they are not
-supposed to appear in the source program.
+can only be used inside an interface definition.
+Finally an expression can also be annotated with its static type. But annotated expressions are only intended for the semantic rules,
+hence they are not supposed to appear in the source program. A value is the final result of semantic
+rules on evaluating an expression, which looks like ``$<I> \new J$''. It is exactly an object instance
+of $J$ with annotated static type $I$.
 
@@
 \end{displaymath}
-\caption{Syntax. \haoyuan{mention in text that annotated expressions are only intended for semantic rules?}}\label{fig:syntax}
+\caption{Syntax.}\label{fig:syntax}
 \end{figure*}
@@
 $\Gamma$ is maintained to store the types of variables, together with ``this'' type, namely
-the enclosing type. The three rules for method invocation, (T-INVK), (T-PATHINVK) and (T-SUPERINVK)
+the enclosing type. The three rules for method invocation, \textsc{(T-Invk)}, \textsc{(T-PathInvk)} and \textsc{(T-SuperInvk)}
 are very similar, in the sense that they all check the type of the specific method, by using
-an auxiliary function \mtype. \mtype is the function for looking up method types, which we will
-illustrate later. After the method type is obtained, they all check that arguments and the receiver
-have compatible types. Additionally, (T-PATHINVK) requires the receiver to be the subtype of the specified
-path type, and (T-SUPERINVK) checks if the enclosing type directly extends the specified super type.
+an auxiliary function \mtype. \mtype{} is the function for looking up method types, which we will
+illustrate later in Section~\ref{subsec:auxdefs}. After the method type is obtained, they all check that arguments and the receiver
+have compatible types. Additionally, \textsc{(T-PathInvk)} requires the receiver to be the subtype of the specified
+path type, and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.
 
-The method typing rule (T-METHOD) is more interesting, since the method can either be an original implementation or an update.
+The method typing rule \textsc{(T-Method)} is more interesting, since the method can either be an original implementation or a partial override.
 Besides static type-checking for the return expression,
-we further use the helper function $\mostSpecific$ to ensure that the method update is legal. The formal definition is available in Section~\ref{sec:aux}.
-By that we define the legality of method updating: the updated method must be an original method (not another method update), and method updating cannot cross over method overriding (a method overriding cannot appear between the method update and the updated original method in inheritance hierarchy).
+we further use the helper function $\mostSpecific$ to ensure that the method update is legal. The formal definition is again in Section~\ref{subsec:auxdefs}.
+By the equation ``$\mostSpecific(m, I, J) = \{J\}$'' we define the legality of method overrides as mentioned in Section~\ref{subsec:partialoverrides}, namely if it is a partial override, it should not overlap a total override, otherwise
+the total override would be returned instead of $J$.
 
-Finally, (T-INTF) defines interface type-checking in a straightforward way.
-Note that it is responsible for checking conflicted paths with a same source.
-As we illustrated in Section ?, such a case is disallowed for unambiguity.
+Finally, \textsc{(T-Invk)} defines interface checking. The condition helps to ensure unambiguity and type soundness of the calculus. We will
+introduce \mbody{} and some counter-examples later. But intuitively, if $\mbody(m,I,J)$ is defined, that means $\new{I}.J::m()$ is not
+ambiguous during runtime. Therefore the condition says that if an expression type checks, it should not introduce ambiguity during runtime
+in any case. The interface check is responsible to capture ambiguity during compilation.
 
@@
 \end{figure*}
-\bruno{Path invocation subsumes regular invocation. In other words:
-e0.m(e) = e0.I::m(e) when the type of e0 is I.}
 
@@
 respectively. When evaluating an expression, they are invoked recursively and
-alternately to produce a single value in the end. The small-step semantics (S-INVK), (S-PATHINVK) and (S-SUPERINVK) behave similarly, each corresponds to
+alternately to produce a single value in the end. The small-step semantics \textsc{(S-Invk)}, \textsc{(S-PathInvk)} and \textsc{(S-SuperInvk)} behave similarly, each corresponds to
 one kind of method invocation.
@@
 Generally, one can understand $\mbody(m, I, J)$ in a way that it finds the most specific body of method $m$, when the receiver has dynamic type $I$ and static type $J$.
-The three rules require that the receiver and the arguments have been evaluated into values, before substitution is applied.
+Notice, for example in \textsc{(S-Invk)}, that when ``$\new{I}$'' replaces ``\lstinline|this|'', its static type should be the interface to which $m$ is dispatched.
+Therefore we also keep the interface type in the definition of \mbody.
+This point is consistent with the last paragraph in
+Section~\ref{subsec:solutionmim}.
+
+On the other hand, there is a relationship between path invocation and the regular method invocation, and it can be observed from the similarity
+between their semantic rules in Figure~\ref{fig:smallstep}.
+For any \lstinline|e.I::m()|, the result of evaluation remains unchanged if we set the static type of \lstinline|e| to be $I$.
+This can be done by an implicit cast, that is, we can define a function with one parameter type $I$, then \lstinline|e| is passed to that function and directly returned.
+It is just equivalent if we write explicit casts like \lstinline|((I) e).m()| in languages like Java.
 
@@
 \end{mathpar}
-\caption{Small-step semantics.\haoyuan{fixed rules. Need to change text.}}\label{fig:smallstep}
+\caption{Small-step semantics.}\label{fig:smallstep}
 \end{figure*}
@@
 
-\subsection{Auxilary Definitions}~\label{sec:aux}
+\subsection{Auxiliary Definitions}\label{subsec:auxdefs}\haoyuan{to revise}
 
@@
 Such a set may contain several elements, but that implies ambiguity; what we expect is actually a singleton set.
-By the definition of $\mostSpecific$ shown in Figure~\ref{fig:auxfunc}, an interface belongs to the return set if and only if:
+By the definition of $\mostSpecific$ shown in Figure ?, an interface belongs to the return set if and only if:
 \begin{itemize}

### 2017-06-14 Aplas17/sections/RelatedWork.tex
Finished revising formalization.

@@
 \section{Related Work}
-
-\begin{itemize}
-	\item Static+Dynamic type method lookup (any existing language that supports this?)
-	\item Formalization based on FJ (novelty: keep static types <I> in formalization)
-		\begin{itemize}
-			\item Existing formalizations based on FJ proposed new features and added rules in syntax and semantics.
-But we not only add rules, but also piggyback static types on almost all semantic rules to model method lookup.
-			\item Featherweight defenders, ...
-		\end{itemize}
-\end{itemize}
 

### 2017-06-14 Aplas17/sections/Overview.tex
fix
Fixing formalization.
pic

@@
 \section{A Running Example: DrawableDeck}~\label{sec:overview}
-\includegraphics[height=3.3cm]{pics/DrawableLoggingDeck.pdf}
-\red{H: with UML graphs the illustration could be better.}
+
+\begin{figure*}[t]
+\centering
+\includegraphics[height=2cm]{pics/DrawableLoggingDeck.pdf}
+\caption{DrawableLoggingDeck UML}\label{fig:subtyping}
+\end{figure*}
 
@@
 
-\subsection{Problem: Unintentional Method Conflicts}
-\bruno{maybe call this problem 1?}
-
+\subsection{Problem 1: Unintentional Method Conflicts}
 Suppose that two components \lstinline|Deck| and \lstinline|Drawable| 
@@
 calls statically}.
-\bruno{Perhaps show the solution in MIM here (i.e Section 2.4), and then move to problem
+\bruno{Perhaps show the solution in \MIM{} here (i.e Section 2.4), and then move to problem
 2 (which is being discussed next with shuffleAndDraw)}

### 2017-06-14 Aplas17/sections/Formalization.tex

@@
 
-\subsection{Syntax} \haoyuan{TODO: use the examples to illustrate the
-mbody algorithm in an intuitive way, and especially explain the two counter-examples that are
-important to type soundness.}
+\subsection{Syntax}
 
@@
 
-\subsection{Auxiliary Definitions}\label{subsec:auxdefs}\haoyuan{to revise}
-
-\begin{figure*}[t]
-\centering
-\vspace{-1ex}
-\begin{tabular}{ccccc}
-\includegraphics[width=2cm]{pics/p1.pdf}\hspace{4pt} &
-\includegraphics[width=2cm]{pics/p2.pdf}\hspace{4pt} &
-\includegraphics[width=2cm]{pics/p3.pdf}\hspace{4pt} &
-\includegraphics[height=3cm]{pics/p4.pdf}\hspace{4pt} &
-\includegraphics[height=3cm]{pics/p5.pdf}\hspace{4pt} \\
-(a) & (b) & (c) & (d) & (e)
-\end{tabular}
-\caption{Figures..}\label{fig:pegasus}
-%\saveSpaceFig
-\end{figure*}
+\subsection{Auxiliary Definitions}\label{subsec:auxdefs}
 
@@
 auxiliary functions, collected by Figure~\ref{fig:auxfunc}. To begin with, we
-introduce the basic functions: $\ext, \updateSet$ and $\prune$. $\ext(I, J)$
-simply indicates that interface $I$ directly extends interface $J$. Corresponding
+introduce the basic functions: $\ext, \overrideSet$ and $\prune$. $\ext(I, J)$
+simply indicates that interface $I$ directly extends interface $J$. Compared to
 to this is a more general case $I <: J$, meaning that $I$ is a subtype of $J$.
-$\updateSet(I, J)$ returns a set of methods defined in $I$ that have ``$\kwoverride \; J$''
-in their signatures. Notice that $\updateSet(I, I)$ is a special representative of
+$\overrideSet(I, J)$ returns a set of methods defined in $I$ that have ``$\kwoverride \; J$''
+in their signatures. Notice that $\overrideSet(I, I)$ is a special representative of
 the ``originally-defined'' method set from $I$. The $\prune$ function takes a set of
@@
 		{  \mostSpecific(m, I_d, I_s) = \{I\} \\
-			\mostSpecific_2(m, I_d, I) = \{J\} \\
+			\mostSpecificOverride(m, I_d, I) = \{J\} \\
 			\kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_E}{m}{I_X}{x}{I}{e_0}\ldots\}}
@@
 	\inferrule* [left=]
-	{ set1 = \; \{ K <: J \; $and$ \; K >: I \; | \; m \in \updateSet(K, K) \} \\
-		set2 = \; \{ K >: J \; | \; m \in \updateSet(K, K) \} }
+	{ set1 = \; \{ K <: J \; $and$ \; K >: I \; | \; m \in \overrideSet(K, K) \} \\
+		set2 = \; \{ K >: J \; | \; m \in \overrideSet(K, K) \} }
 	{\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
@@
 		{ set = \; \{ K <: J \; $and$ \; K >: I \; | \;
-			m \in \updateSet(K, J)  \} }
-		{\mostSpecific_2(m, I, J) = prune(set)}
+			m \in \overrideSet(K, J)  \} }
+		{\mostSpecificOverride(m, I, J) = prune(set)}
 
@@
 		\kwoverride \; J \ldots \} }
-	{m \in \updateSet(I, J)}
+	{m \in \overrideSet(I, J)}
 	\end{mathpar}
@@
 
-\subsubsection{$\mostSpecific$ and $\mostSpecific_2$}
+\begin{figure*}[t]
+	\centering
+	\vspace{-1ex}
+	\begin{tabular}{ccc}
+		\includegraphics[width=2cm]{pics/p1.pdf}\hspace{4pt} &
+		\includegraphics[width=2cm]{pics/p2.pdf}\hspace{4pt} &
+		\includegraphics[width=2cm]{pics/p3.pdf}\hspace{4pt} \\
+		(a) $\mbody(m,C,A) = (A,...)$\ \ \  & (b) $\mbody(m,C,A) = (C,...)$\ \ \  & (c) $\mbody(m,C,A) = (C,...)$
+	\end{tabular} \\
+   \begin{tabular}{cc}
+   	\includegraphics[height=3cm]{pics/p4.pdf}\hspace{4pt} &
+   	\includegraphics[height=3cm]{pics/p5.pdf}\hspace{4pt} \\ 
+   	(d) $\mbody(m,D,A) = \keyword{undefined}$\ \ \  & (e) $\mbody(m,D,A) = \keyword{undefined}$
+   \end{tabular}
+	\caption{Examples on $\mbody$.}\label{fig:examplesmbody}
+	%\saveSpaceFig
+\end{figure*}
+
+\subsubsection{$\mostSpecific$ and $\mostSpecificOverride$}
 
@@
 	\item It is along path $J$, meaning that it is either a supertype or a subtype of $J$ (including $J$ itself);
-	\item It does not have a subtype in the same set, because we have used $prune$ to filter out all super types, as the most specific one is always in the sub-most type.
+	\item It does not have a subtype in the same set, because we have used $prune$ to filter out all super types.
 \end{itemize}
@@
 The $\mostSpecific$ function only focuses on original method implementations, all the method updates are omitted during that time.
-On the other hand, another auxiliary function $\mostSpecific_2(m, I, J)$ has the assumption that $J$ defines an original $m$, and this function tries to find the most specific implementations that update such an $m$.
-Just as $\mostSpecific$, $\mostSpecific_2$ also returns the set of interfaces after pruning.
+On the other hand, another auxiliary function $\mostSpecificOverride(m, I, J)$ has the assumption that $J$ defines an original $m$, and this function tries to find the most specific implementations that partially overrides such an $m$.
+Just as $\mostSpecific$, $\mostSpecificOverride$ also returns the set of interfaces after pruning.
 An interface belongs to the return set if and only if:
@@
 \end{itemize}
-The algorithm for finding the most specific method update is quite similar to that for most specific original method.
-A method update is not allowed to work on another method update, and one can hide another if their interfaces has subtyping relations.
+The algorithm for finding the most specific partial overrides is quite similar to that for most specific original method.
+A partial override is not allowed to work on another partial override, and one can hide another if their interfaces has subtyping relations.
 If they do not hide each other, the result implies ambiguity.
@@
 type $I_d$ and static type $I_s$. Such a function returns the most specific method implementation, more
-accurately, its parameters, returned expression and the types. It considers both originally defined methods and method updates, so $\mostSpecific$ and $\mostSpecific_2$ are invoked.
+accurately, its parameters, returned expression and the types. It considers both originally defined methods and method updates, so $\mostSpecific$ and $\mostSpecificOverride$ are invoked.
 
@@
 The set $\{I\}$ implies that we will use the $m$ from $I$ without ambiguity.
-But moreover, we have to invoke $\mostSpecific_2(m, I_d, I)$, to check if there are updated versions of $m$ between $I_d$ and $I$.
+But moreover, we have to invoke $\mostSpecificOverride(m, I_d, I)$, to check if there are updated versions of $m$ between $I_d$ and $I$.
 Again we forbid ambiguity, so the expected set after pruning is also a singleton set $\{J\}$.
@@
 \end{itemize}
-The definition of $\mtype$ simply relies on $\mbody$. In short,
+The definition of $\mtype$ used in typing rules simply relies on $\mbody$. In short,
 $$\mbody(m, I, I) = (J, \overline{I_x}\ \overline{x}, I_E\ e) \ \Longrightarrow\ \mtype(m, I) = \overline{I_x}\rightarrow I_E$$
@@
 
+\subsubsection{Examples}
+
+Examples on $\mbody$ are shown in Figure~\ref{fig:examplesmbody} for a better understanding. For each small example, the result
+gives the interface to which $m$ is dispatched. (a) is a basic model for unintended method conflicts; (b) and (c) demonstrate
+that hierarchical dispatch can find the most specific original method and partial override. More interesting are the two bad examples
+(d) and (e), they both fail on $\mbody$. (d) is the well-known diamond inheritance, which our model also forbids, and (e) is similar to
+(d) because the two partial overrides are working on the same operation. Both counter-examples imply that \lstinline|new D().A::m()| will
+lead to ambiguity, and in order for type soundness, both have to be denied by the type checker. It has been guaranteed by the interface check
+\textsc{(T-Intf)} in Figure~\ref{fig:typingrules}.
+
 \subsection{Properties}
 Previously the definitions of our model are given, now we should proceed to prove the type soundness of 
-the model, which relates typing to computation. We want to prove such a property: if an expression is 
-well-typed, then after many reduction steps it must reduces to a value of a subtype of the original type
-of the expression. Following the FeatherweightJava paper~\cite{Igarashi01FJ}, the type-soundness theorem 
+the model, which relates typing to computation. The type soundness states that, if an expression is 
+well-typed, then after many reduction steps it must reduce to a value, with its annotation to be subtype of the original expression type.
+Following the FeatherweightJava paper~\cite{Igarashi01FJ}, the type-soundness theorem 
 (Theorem~\ref{theorem_soundness}) is proved by using the standard technique of subject reduction (Theorem~\ref{theorem_subject})
-and progress (Theorem~\ref{theorem_progress})~\cite{Wright1994}.
+and progress (Theorem~\ref{theorem_progress})~\cite{Wright1994}. In Theorem~\ref{theorem_progress} ``$\#(\overline{x})$'' denotes the number of
+elements.
 
@@
 \begin{enumerate}
-\item If $e$ includes $\left(<J>\new{I}\right).m(\overline{<I_E>} \; \overline{e})$ as a subexpression,
-    then $ \mbody(m, I, J) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and
-         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$
-\item If $e$ includes $\left(<J>\new{I}\right).K::m(\overline{<I_E> e})$ as a subexpression,
-    then $ \mbody(m, I, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
-         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$
-\item If $e$ includes $\kwsuper.K::m(\overline{<I_E> e})$ as a subexpression,
-    then $ \mbody(m, K, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
-         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$
+\item If $e$ includes $\left(<J>\emph{\kwnew}\;I()\right).m(\overline{<I_E>} \; \overline{e})$ as a subexpression,
+    then $ \emph{\mbody}(m, I, J) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and
+         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$.
+\item If $e$ includes $\left(<J>\emph{\kwnew}\;I()\right).K::m(\overline{<I_E> e})$ as a subexpression,
+    then $ \emph{\mbody}(m, I, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
+         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$.
+\item If $e$ includes $\emph{\kwsuper}.K::m(\overline{<I_E> e})$ as a subexpression,
+    then $ \emph{\mbody}(m, K, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
+         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$.
 \end{enumerate}

### 2017-06-14 Aplas17/sections/Overview.tex

@@
 calls statically}.
-\bruno{Perhaps show the solution in \MIM{} here (i.e Section 2.4), and then move to problem
+\bruno{Perhaps show the solution in MIM here (i.e Section 2.4), and then move to problem
 2 (which is being discussed next with shuffleAndDraw)}
@@
 
-\subsection{Solution in \MIM: \dispatchnamecaptical}
+\subsection{Solution in \MIM: \dispatchnamecaptical}\label{subsec:solutionmim}
 The \MIM{} model uses \dispatchnameit{} for method lookup. A qualified
@@
 
-\subsection{Partial Overrides in \MIM	}
+\subsection{Partial Overrides in \MIM	}\label{subsec:partialoverrides}
 

### 2017-06-14 Aplas17/sections/Formalization.tex
A quick review on related work.

@@
 well-typed, then after many reduction steps it must reduce to a value, with its annotation to be subtype of the original expression type.
-Following the FeatherweightJava paper~\cite{Igarashi01FJ}, the type-soundness theorem 
+Following the Featherweight Java paper~\cite{Igarashi01FJ}, the type-soundness theorem 
 (Theorem~\ref{theorem_soundness}) is proved by using the standard technique of subject reduction (Theorem~\ref{theorem_subject})

### 2017-06-14 Aplas17/sections/RelatedWork.tex
A quick review on related work.

@@
 
-The above mentioned models/languages support multiple inheritance, and they handle method confliction in the same way: requiring 
-programmers to explicitly resolve ambiguity and disallowing two methods with the same signature from two different libraries 
-to co-exit. This is the common drawback of the above mentioned models versus our model.
+The above mentioned models/languages support multiple inheritance, and they handle method conflicts in the same way, by
+simply disallowing two methods with the same signature from two different units to coexist. The ambiguity is resolved either
+by programmers explicitly or by setting a linearised composition. This is the common drawback of the above mentioned models versus our model.
 
-\subsection{Resolving Unintended Method Confliction}
-There are still a few languages that already realized the problem and explored a bit. We discuss them one by one.
+\subsection{Resolving Unintended Method Conflicts}
+There are still a few languages that partly realize the problem. They provide limited support for unintended conflicting methods.
 
 \noindent {\bf C++ model.}
-As discussed in Section~\ref{sec:overview}, C++ supports very flexible inheritance mode and allows programmers to choose different 
-confliction resolution approaches via normal or virtual inheritance. Generally speaking, C++ model is much more complex 
-and flexible than our approach. For example, given the following code
+C++ supports very flexible inheritance models and allows programmers to choose either static dispatch or dynamic dispatch for method lookup.
+It allows unintended conflicts and uses static dispatch to resolve them, as discussed in Section~\ref{sec:overview}. For example, given the following code
 \begin{lstlisting}[language=Java]
-class A { public: void m() {cout << "MA" << endl;}};
-class B { public: void m() {cout << "MB" << endl;}};
+class A { public: void m() {cout << "MA" << endl;} };
+class B { public: void m() {cout << "MB" << endl;} };
 class C : public A, public B { 
@@
 \end{lstlisting}
-The running result is $MB \; MA$, meaning that it uses static dispatch (looks at the static types) when doing method lookup. 
-On calling \texttt{func(c)}, no matter the dynamic type of \texttt{c} is class \texttt{C}, the method call still dispatches to 
-the method \texttt{m} in class \texttt{A} because of static dispatch.
+The running result is $MB \; MA$, meaning that it uses static dispatch (looks at the static types) for method \lstinline|m()|. 
+On calling \texttt{func(c)}, in spite that the dynamic type of \texttt{c} is class \texttt{C}, the method call still dispatches to 
+\lstinline|A.m|.
 However, we can alter the code a little bit with \textbf{\texttt{virtual}} methods and the result will be totally different:
 \begin{lstlisting}[language=c++]
-class A { 
-	public: virtual void m() {cout << "MA" << endl;}
-};
-class B { 
-	public: virtual void m() {cout << "MB" << endl;}
-};
+class A { public: virtual void m() {cout << "MA" << endl;} };
+class B { public: virtual void m() {cout << "MB" << endl;} };
 class C : public A, public B { 
@@
 \end{lstlisting}
-Now the running result will be $MB \; MC$. With virtual method, dynamic dispatch is used and 
-method lookup algorithm will find the most specific method definition of $m$, which is the definition 
-in class $C$. Although C++ support this flexibility, the drawback compared to our model is
-obvious: it does not support updating both $A.m$ and $B.m$ in class $C$.
+Now the running result will be $MB \; MC$. With virtual methods, dynamic dispatch is used and 
+method lookup algorithm will find the most specific method definition of $m$, namely \lstinline|C.m| at this time.
+Although C++ support this flexibility, unfortunately, dynamic dispatch on conflicting methods will be problematic.
+Furthermore, it does not support partial overrides compared to our model.
 
@@
 
-\noindent  {\bf \csharp Explicit method implementation.}
-Explicit method implementation is a special feature supported by \csharp. As described in \csharp
+\noindent  {\bf \csharp{} Explicit method implementation.}
+Explicit method implementation is a special feature supported by \csharp{}. As described in \csharp{}
 documentation~\cite{csharpdoc}, a class that implements an interface can explicitly implement a member of that
@@
 that share the same member names and give each interface member a separate implementation.
-Explicit interface member implementations have two advantages:
-Explicit interface member implementations allow interface implementations to be excluded 
+
+Explicit interface member implementations have two advantages.
+Firstly, they allow interface implementations to be excluded 
 from the public interface of a class. This is particularly useful when a class implements an internal 
 interface that is of no interest to a consumer of that class or struct.
-Explicit interface member implementations allow disambiguation of interface members with the 
-same signature. This is the the advantage that is similar to ours' model. However, there are two 
-diffirencies: firstly, method (default) implementations are not allowed in \csharp interfaces; 
-secondly, when handling unintended method confliction, multi-way method updating is not supported 
-in \csharp.
+Secondly, they allow disambiguation of interface members with the 
+same signature. However, there are two critical differences to \MIM{}:
+(1) default implementations are not allowed in \csharp{} interfaces; 
+(2) there are only one-level partial overrides (implementations).
 
@@
 
-\subsection{Hirarchical Dispatch}
-As we have discussed before, the mix of static and dynamic dispatch is needed by the literature 
-pay little attention to this. In the prototype-based language \self~\cite{Chambers1991}, inheritance is a basic feature.
+\subsection{Hierarchical Dispatch}
+As we have discussed before, the mix of static and dynamic dispatch is particularly useful under certain circumstances,
+yet there is little attention from related work. In the prototype-based language \self~\cite{Chambers1991}, inheritance is a basic feature.
 It does not include classes but instead allow individual objects to inherit from (or delegate to) other objects. 
-Although it is different than class-based languages, the multiple inheritance model is somehow similar. The \self 
-language support multiple (object) inheritance in a clever way. Not only the new inheritance
-relation \emph{prioritized parents} is developed, but also the method lookup rule called 
-\emph{sender path tiebreaker rule}, which is similar with our approach, using hirarchical 
-information in method resolution, but in a prototype-based language setting.
+Although it is different from class-based languages, the multiple inheritance model is somehow similar. The \self{}
+language supports multiple (object) inheritance in a clever way. It not only develops the new inheritance
+relation \emph{prioritized parents}, but also adopts \emph{sender path tiebreaker rule} for method lookup, which is similar with our approach, using hierarchical information in method resolution, but in a prototype-based language setting.\haoyuan{Do they have updates?}
 
-\subsection{Formalization Based on FeatherweightJava}
-FeatherweightJava~\cite{Igarashi01FJ} is a minimal core calculus of Java language, proposed by Igarashi et. al. Many models are based on 
-FeatherweightJava, for example FeatherTrait~\cite{Liquori08ftj}, Featherweight defenders~\cite{goetz12fdefenders}, Jx~\cite{Nystrom2004}, as well as our model.
-It provides the standard model of formalizing a Java-like object-oriented language and 
-people can easily extends it to form a new language. In terms of formalization, they key novelty of our model is the use of 
+\subsection{Formalization Based on Featherweight Java}
+Featherweight Java~\cite{Igarashi01FJ} is a minimal core calculus of Java language, proposed by Igarashi et. al\haoyuan{Need cite}. There are
+many models built on
+Featherweight Java, including FeatherTrait~\cite{Liquori08ftj}, Featherweight defenders~\cite{goetz12fdefenders}, Jx~\cite{Nystrom2004}, and so on.
+It provides the standard model of formalizing a Java-like object-oriented language, and 
+is easily extensible. In terms of formalization, they key novelty of our model is the use of 
 static types as annotations along with various terms. As far as we know, this technique has not appear in literature before.

### 2017-06-15 Aplas17/paper.tex
Intro and Abstract

@@
 the extensive literature on the topic. One of the most promising 
-approaches to multiple inheritance is \emph{traits}. Traits offer a
+approaches to multiple inheritance are \emph{traits}. Traits offer a
 restricted model of multiple inheritance that is easy to reason and 
-have many elegant properties. Traits have good support for method 
+has many elegant properties. Traits have good support for method 
 conflicts which arise from \emph{diamond inheritance}:
@@
 the implementation of a method at run-time. We give illustrative 
-examples of our language and features and formalize a minimal 
+examples of our language and features and formalize \name{} as a minimal 
 Featherweight-Java style calculus.

### 2017-06-15 Aplas17/sections/Introduction.tex
Intro and Abstract

@@
 \textit{diamond problem}~\cite{Sak89dis,Singh1995}. In the diamond problem inheritance could allow
-one feature to be inherited from multiple parent classes, hence
-conflicts arise. The variety of strategies on resolving such conflicts
+one feature to be inherited from multiple parent classes that share a
+common ancestor, hence
+conflicts arise. The variety of strategies for resolving such conflicts
 urges the occurrence of different multiple inheritance models,
 including traits, mixins, CZ~\cite{malayeri2009cz}, and many others. Existing
-languages have taken care of this case intensively. Other issues
-include how multiple inheritance deals with state, as discussed in
+languages and research have taken care of this case extensively. Other issues
+include how multiple inheritance deals with state, 
 which also has been discussed quite extensively~\cite{classless,malayeri2009cz,stroustrup1995}.
@@
 methods that do not actually refer to the same feature. 
-%%This issue was proposed by the trait paper, so-called
 In a nominal system, methods can be designed for different
 functionality, but they just happen to have same names (and
-signatures). When inheritance is used to compose those methods an
+signatures).
+A simple example of this situation are two \lstinline{draw} methods that
+are inherited from a deck of cards and a drawable widget. 
+In such context the two draw methods have very different meanings, 
+but they happen to share the same name.
+%%This issue was proposed by the trait paper, so-called
+When inheritance is used to compose those methods an
 error happens due to conflicts. However, unlike the diamond problem,
-the conflicted methods usually do not share a common parent. In this
-paper we call such a case ``\textit{triangle inheritance}''.
+the conflicted methods have very different meanings and do not share a
+common parent. We call such a case ``\textit{triangle inheritance}''.
 \haoyuan{Fine to have a graph with diamond and triangle shapes if we got space.}
@@
 before. In practice existing languages also provide limited support for
-it. In most languages, the mechanism available to deal with this problem are the same as the diamond
+it. In most languages, the mechanisms available to deal with this problem are the same as the diamond
 inheritance. Unfortunatelly this is often inadequate and can lead 
@@
 methods. Intuitively using one method to fuse two unrelated features
-is unsatisfactory. Therefore we need a real solution to keep both
+is unsatisfactory. Therefore we need a better solution to keep both
 features separately during inheritance, so as not to break
-\emph{independent extensibility}\cite{zenger05independentlyextensible}.
+\emph{independent extensibility}~\cite{zenger05independentlyextensible}.
 
@@
 are mechanisms available in C++ and C\# that allow for two
-unintentionally conflicted method to coexist in the system. Among them
+unintentionally conflicted methods to coexist in a class. Among them
 C++ is a representative that accepts the triangle inheritance and
@@
 unsatisfactory because virtual methods are pervasive in OOP and used 
-for code reuse and extensibility.
+for code reuse and extensibility. A problem with the C++ approach is
+that it can only use either static or dynamic dispatching separately, but dealing
+with unintentional method conflicts seems to require a combination of both.
 
-Having tolerance for unintentional method conflicts does not mean to
-sacrifice extensibility, hence in contrast with static dispatch and
-dynamic dispatch, we propose a third approach, which looks like a
-combination of both, called \textit{hierarchical dispatch}. By
-hierarchical dispatch, the method binder will look at both the \emph{static
-type} and the \emph{dynamic type} of the receiver during runtime. When there
-are multiple branches that cause unintentional conflicts, the static
-type can specify one branch among them for unambiguity, and the
-dynamic type helps to find the most specific (the newest)
-implementation. In that case both unambiguity and extensibility are
-preserved. To present this idea, we introduce a formalized model in
-Section~\ref{sec:formalization} based on Featherweight Java~\cite{Igarashi01FJ}, together with theorems and
+%Having tolerance for unintentional method conflicts does not mean to
+%sacrifice extensibility, hence in contrast with static dispatch and
+%dynamic dispatch,
+
+This paper proposes \textit{hierarchical dispatch}: a novel approach
+to method dispatching, which combines static and dynamic
+information. Using hierarchical dispatch, the method binder will look
+at both the \emph{static type} and the \emph{dynamic type} of the
+receiver during runtime. When there are multiple branches that cause
+unintentional conflicts, the static type can specify one branch among
+them for unambiguity, and the dynamic type helps to find the most
+specific implementation. In that case both unambiguity and
+extensibility are preserved. To present this idea, we introduce a
+formalized model in Section~\ref{sec:formalization} based on
+Featherweight Java~\cite{Igarashi01FJ}, together with theorems and
 proofs for type soundness. In the model we also propose
-\textit{partial overrides}, where a method refinement can be applied
-only to one branch. Our model generalizes the trait
-model by providing additional support to the triangle inheritance.
+\textit{partial overrides}, where method overriding can be applied
+only to one branch of the class hierarchy. Our model can be viewed as
+a generalization of the trait model by providing additional support to
+the triangle inheritance.
 
@@
 	ensures unambiguity as well as extensibility.
-	\item \textbf{Partial overrides:} a novel notion that allows method refinements on individual branches.
+	\item \textbf{Partial overrides:} a novel notion that allows
+          method overrides on individual branches of the class hierarchy.
 	\item \textbf{\name:} a formalized model based on Featherweight Java, supporting the above features. Some theorems and their proofs
-	are attached to confirm the type soundness (unambiguity?) of the model.
+	are attached to confirm the type soundness (unambiguity?) of
+        the model.\bruno{Anything about unambiguity?}
 \end{itemize}

### 2017-06-15 Aplas17/sections/Overview.tex
Intro and Abstract
Section 2 some text

@@
 \end{figure*}
+\bruno{I've said this several times in the past: please use proper UML
+notation! The UML arrows are not right.}
+\bruno{This figure is never referred to in the text! You need to talk 
+about the figure in the text.}
 
@@
 ``\lstinline|interface|''. The concept is closely related to Java 8
-interfaces, and traits. For simplicity, an interface in our model has
+interfaces with default methods~\cite{}, and traits. For simplicity, an interface in our model has
 the following characteristics:
@@
 of cards, and defines \lstinline|draw()| for drawing a card from the
-deck.  While \lstinline|Drawable| is an interface for graphics that
+deck.  \lstinline|Drawable| is an interface for graphics that
 can be drawn, and also includes a method called \lstinline|draw()| for
@@
 programming languages do not support them. In a traditional OO system,
-they more or less break the subtyping. Moreover, in
+they can break the subtyping. Moreover, in
 contrast with exclusion, renaming can indeed preserve both conflicted
@@
 without renaming, and the type checker does not complain about 
-inheritance. But we need to find an approach to \emph{disambiguate on method
+conflicts. But we need to find an approach to \emph{disambiguate on method
 calls statically}.

### 2017-06-15 Aplas17/sections/Overview.tex
temp fix

--- 2017-06-14 Aplas17/sections/Overview.tex
@@
 \end{lstlisting}\vspace{3pt}
-The point of using multiple inheritance is surely for composing the features from
+The point of using multiple inheritance is surely for composing the features from various 
 components, and to achieve code reuse. Multiple inheritance is supported by many mainstream OO
@@
 behaviours, however, it is cumbersome in practice, as introducing new
-names can affect other code blocks. \\
+names can affect other code blocks.
 
-What we really expect from the language is that we keep both methods
-without renaming, and the type checker does not complain about 
-inheritance. But we need to find an approach to \emph{disambiguate on method
+\paragraph{V. Static dispatch.}
+What we really expect from the language is keeping both methods
+without renaming, and the type checker does not complain. 
+But we need to find an approach to \emph{disambiguate on method
 calls statically}.
@@
 \lstinline|DrawableDeck| is created, a method call for
-\lstinline|draw()| on that object is ambiguous, due to dynamic
-dispatch. Nonetheless, we can adopt static dispatch for
+\lstinline|draw()| on that object would be ambiguous. Nonetheless, we can adopt static dispatch for
 disambiguating. Some languages like C++ use qualified names in that
@@
 \end{lstlisting}\vspace{3pt}
-Thus we have: \paragraph{V. Static dispatch.} Static dispatch finds out and invokes the most specific method ``by need''.
+Static dispatch in C++ finds out and invokes the most specific method ``by need''.
 
+\subsection{Problem 2: Dynamic Dispatch for Code Reuse}
 On the other hand, we also need dynamic dispatch as it is essential and widely used in object-oriented programming.
-C++ has the flexibility for choosing either way of dispatch by the ``virtual'' keyword.
+C++ has the flexibility for choosing either way of dispatch by the \kwvirtual{} keyword.
 Unfortunately, this approach is still unsatisfactory regarding code reuse. For instance, here we redefine \lstinline|Deck| to support
@@
 that, if the result of \dispatch{} is \lstinline|J.m()| for some \lstinline|J|, then such a \lstinline|J| must be a super type of \lstinline|e|'s dynamic type, and \lstinline|J| has a subtyping relation with \lstinline|I| (either \lstinline|J <: I| or \lstinline|J >: I|).
-Intuitively, the most specific \lstinline|m()| must be from branch \lstinline|I|, but it can be an overridden version after \lstinline|I| like dynamic dispatch.
+Intuitively, the most specific \lstinline|m()| must be from branch \lstinline|I|, but it can be an overridden version after \lstinline|I| because of dynamic dispatch.
 The formal definition will be introduced later.
@@
 
-Such a dispatch make uses of both the static type and the dynamic type of the receiver.
+Such a dispatch algorithm make uses of both the static type and the dynamic type of the receiver.
 Intuitively, the static type specifies one branch of the method to avoid ambiguity, and the dynamic type finds the latest version on that branch.
@@
 
-With the old example, below code meets our expectation:
+With the old example, the code below meets our expectation:
 \vspace{3pt}\begin{lstlisting}
@@
 \end{lstlisting}\vspace{3pt}
-It guarantees that \lstinline|shuffleAndDraw()| are calling \lstinline|shuffle()| and \lstinline|draw()| from its own branch, so that the namesakes
+It guarantees that \lstinline|shuffleAndDraw()| calls \lstinline|shuffle()| and \lstinline|draw()| from its own branch, so that the namesakes
 from other branches will not cause conflicts. Now \lstinline|d.shuffleAndDraw()| is no longer ambiguous.

### 2017-06-15 Aplas17/sections/Formalization.tex
Notes on uparrow.
Some text

@@
 Figure~\ref{fig:syntax} shows the syntax of \MIM{}. The multiple
-inheritance feature of \MIM{} as a basis Java 8 interfaces, which support
+inheritance feature of \MIM{} is inspired by Java 8 interfaces, which support
 method implementations via default methods. This feature is quite
-closely related to \emph{traits}\cite{scharli03traits}.  To demonstrate how
+closely related to \emph{traits}~\cite{scharli03traits}.  To demonstrate how
 unintentional method conflicts are untangled in \MIM{}, we present the

### 2017-06-15 Aplas17/sections/Formalization.tex
Section 3

@@
 \subsection{Syntax}
-
 Figure~\ref{fig:syntax} shows the syntax of \MIM{}. The multiple
@@
 closely related to \emph{traits}~\cite{scharli03traits}.  To demonstrate how
-unintentional method conflicts are untangled in \MIM{}, we present the
-calculus in a straightforward way, hence we only focus on a small
+unintentional method conflicts are untangled in \MIM{}, we only focus on a small
 subset of the interface model. For example, all the methods declared
 in an interface are default methods, that is to say, they always
-provide default implementations.  From this point we can view that we
-are actually modelling a class model that supports multiple
-inheritance. Then it is straightforward to do object creation like
-$\new I$. Fields and primitive types are not modelled as well.
+provide default implementations. 
+%From this point we can view that we
+%are actually modelling a class model that supports multiple
+%inheritance. 
+Object creation is directly supported via $\new I$. 
+Fields and primitive types are not modelled as well.
 
-We use uppercase letters like $I, J, K$ to represent identifiers for
-interfaces. By multiple inheritance, an interface can have a set of
-super interfaces, where such a set can be empty. Inside an interface
-is a set of method declarations. Each method body holds a return
-statement. As seen in Figure~\ref{fig:syntax}, we have introduced the
+We use uppercase letters like $I, J, K$ for interface identifiers. 
+Due to multiple inheritance, an interface can have a set of
+super interfaces, where such a set can be empty. Each interface
+has a set of method declarations. Each method body returns
+an expression. As seen in Figure~\ref{fig:syntax}, we have introduced the
 \kwoverride{} keyword to override an old implementation of the
@@
 it is a partial override.
-Again for simplicity, overloading is not modelled for methods, which
+For simplicity, overloading is not modelled for methods, which
 implies we can uniquely identify a method by its name.
 
-An expression can be a variable, a method invocation, an object
-creation, furthermore, a path-invocation like
+Expressions can be standard constructs such as variables, method
+invocation, or object creation. A novel type of expressions are path-invocations like
 ``$e.I::m(\overline{e})$'', meaning that the dynamically binded
 implementation for method $m$ should be along the path $I$. Another
-case is the super-invocation, enabling a method to access an old
+interesting expression are super-invocations, which enable a method to access an old
 implementation from the specified super type. Hence a super-invocation
 can only be used inside an interface definition.
-Finally an expression can also be annotated with its static type. But annotated expressions are only intended for the semantic rules,
-hence they are not supposed to appear in the source program. A value is the final result of semantic
-rules on evaluating an expression, which looks like ``$<I> \new J$''. It is exactly an object instance
-of $J$ with annotated static type $I$.
+Finally an expression can also be annotated with its static type. But \emph{annotated expressions are only intended for the semantic rules},
+hence they are not supposed to appear in the source program. A value
+``$\langle I \rangle~\new J$''
+is the final result of multple reduction steps evaluating an
+expression. Such value is represents an object instance
+of $J$ with an annotated static type $I$.
 
@@
 e.I::m(\overline{e}) \mid
-\kwsuper.I::m(e) \; \mid \; <I> e \\
+\kwsuper.I::m(e) \; \mid \; \langle I \rangle~e \\
 \text{Context}      & \Gamma & \Coloneqq & \overline{x:I} \\
-\text{Values}       & v & \Coloneqq & <I>\new{J} \\
-\\
-\text{Interface names} & I, J, K & & \\
-\text{Method names} & m & & \\
-\text{Variable names} & x & &
+\text{Values}       & v & \Coloneqq & \langle I \rangle~\new{J} \\
+%%\\
+%%\text{Interface names} & I, J, K & & \\
+%%\text{Method names} & m & & \\
+%%\text{Variable names} & x & &
 \end{array}
@@
 \end{displaymath}
-\caption{Syntax.}\label{fig:syntax}
+\caption{Syntax of name{}.}\label{fig:syntax}
 \end{figure*}
@@
    \end{tabular}
-	\caption{Examples on $\mbody$.}\label{fig:examplesmbody}
+	\caption{Examples on $\mbody$. ``$\uparrow$'' stands for partial overrides.}\label{fig:examplesmbody}
 	%\saveSpaceFig
@@
 
-Examples on $\mbody$ are shown in Figure~\ref{fig:examplesmbody} for a better understanding. For each small example, the result
+Examples on $\mbody$ are shown in Figure~\ref{fig:examplesmbody} for a better understanding.
+Note that we use \lstinline|m| to denote an original method, and ``\lstinline|m|$\uparrow$\lstinline|A|'' for a partial override on \lstinline|A|.
+For each small example, the result
 gives the interface to which $m$ is dispatched. (a) is a basic model for unintended method conflicts; (b) and (c) demonstrate

### 2017-06-15 Aplas17/sections/Overview.tex
overview

@@
 
-\begin{figure*}[t]
-\centering
-\includegraphics[height=2cm]{pics/DrawableLoggingDeck.pdf}
-\caption{DrawableLoggingDeck UML}\label{fig:subtyping}
-\end{figure*}
 \bruno{I've said this several times in the past: please use proper UML
@@
 \subsection{Problem 2: Dynamic Dispatch for Code Reuse}
+\begin{figure*}[t]
+\centering
+\includegraphics[height=2cm]{pics/DrawableLoggingDeck.pdf}
+\caption{DrawableLoggingDeck UML}\label{fig:drawableloggingdeck}
+\end{figure*}
+
 On the other hand, we also need dynamic dispatch as it is essential and widely used in object-oriented programming.
 C++ has the flexibility for choosing either way of dispatch by the \kwvirtual{} keyword.
-Unfortunately, this approach is still unsatisfactory regarding code reuse. For instance, here we redefine \lstinline|Deck| to support
+Unfortunately, this approach is still unsatisfactory regarding code reuse. For instance in Figure~\ref{fig:drawableloggingdeck}, 
+we redefine \lstinline|Deck| to support
 both \lstinline|draw()| and another operation called \lstinline|shuffleAndDraw()|:

### 2017-06-15 Aplas17/sections/Formalization.tex
Section 3

@@
 \section{Formalization}~\label{sec:formalization}
+
+\bruno{There is quite a bit of teminology that we need to be careful
+  to introduce earlier in the paper. For example: ``original
+  method''. We are also still using terminology such as ``method
+  update'', which I think is now outdated.
+We need to read the paper carefully enough to spot
+  possible uses of terminology which may make sense to us, but 
+we have not introduced properly.}
 
@@
 is the final result of multple reduction steps evaluating an
-expression. Such value is represents an object instance
+expression. Such value represents an object instance
 of $J$ with an annotated static type $I$.
@@
 \end{displaymath}
-\caption{Syntax of name{}.}\label{fig:syntax}
+\caption{Syntax of \name{}.}\label{fig:syntax}
 \end{figure*}
@@
 \subsection{Subtyping and Typing Rules}
-The subtyping of \MIM{} consists of only a few rules shown in Figure~\ref{fig:subtyping}.
+The subtyping of \MIM{} consists of only a few rules shown at the top of Figure~\ref{fig:typingrules}.
 In short, subtyping relations are built from the inheritance in interface
-declarations. They hold both reflexivity and transitivity.
+declarations. Subtyping is both reflexive and transitive.
 
-Details of type-checking rules are displayed in Figure~\ref{fig:typingrules}, including expression
+Details of type-checking rules are displayed at the bottom of Figure~\ref{fig:typingrules}, including expression
 typing, well-formedness of methods and interfaces. As a convention, an environment
@@
 The method typing rule \textsc{(T-Method)} is more interesting, since the method can either be an original implementation or a partial override.
-Besides static type-checking for the return expression,
+Besides type-checking the return expression,
 we further use the helper function $\mostSpecific$ to ensure that the method update is legal. The formal definition is again in Section~\ref{subsec:auxdefs}.
@@
 	\framebox{$ I <: J $} \hspace{.5in} \subid \\
-	\subtrans \hspace{.5in} \subextends
-\end{mathpar}
-\caption{Subtyping.}\label{fig:subtyping}
-\end{figure*}
-
-\begin{figure*}[t]
-\begin{mathpar}
+	\subtrans \hspace{.5in} \subextends \\
 	\framebox{$ \judgeewf \Gamma {e:I} $} \hspace{.5in}
@@
 \end{mathpar}
-\caption{Typing rules.}\label{fig:typingrules}
-\end{figure*}
+\caption{Typing and subtyping rules.}\label{fig:typingrules}
+\end{figure*}\bruno{do not use the notation ``-'' in T-METHOD, or
+  otherwise explain it.}
 
 \subsection{Small-step Semantics and Congruence}
-Figure~\ref{fig:smallstep} and Figure~\ref{fig:congruence} define small-step semantic rules and congruence rules,
-respectively. When evaluating an expression, they are invoked recursively and
-alternately to produce a single value in the end. The small-step semantics \textsc{(S-Invk)}, \textsc{(S-PathInvk)} and \textsc{(S-SuperInvk)} behave similarly, each corresponds to
-one kind of method invocation.
-They all invoke \mbody{} for method body lookup.
-Generally, one can understand $\mbody(m, I, J)$ in a way that it finds the most specific body of method $m$, when the receiver has dynamic type $I$ and static type $J$.
-Notice, for example in \textsc{(S-Invk)}, that when ``$\new{I}$'' replaces ``\lstinline|this|'', its static type should be the interface to which $m$ is dispatched.
-Therefore we also keep the interface type in the definition of \mbody.
-This point is consistent with the last paragraph in
-Section~\ref{subsec:solutionmim}.
 
-On the other hand, there is a relationship between path invocation and the regular method invocation, and it can be observed from the similarity
-between their semantic rules in Figure~\ref{fig:smallstep}.
-For any \lstinline|e.I::m()|, the result of evaluation remains unchanged if we set the static type of \lstinline|e| to be $I$.
-This can be done by an implicit cast, that is, we can define a function with one parameter type $I$, then \lstinline|e| is passed to that function and directly returned.
-It is just equivalent if we write explicit casts like \lstinline|((I) e).m()| in languages like Java.
+Figure~\ref{fig:smallstep} defines the small-step semantic and
+congruence rules, respectively. When evaluating an expression, they
+are invoked recursively and alternately to produce a single value in
+the end. The small-step semantics rules \textsc{(S-Invk)},
+\textsc{(S-PathInvk)} and \textsc{(S-SuperInvk)} behave similarly:
+each corresponds to one kind of method invocation. They all invoke
+\mbody{} for method body lookup. Generally, one can understand
+$\mbody(m, I, J)$ in a way that it finds the most specific body of
+method $m$, when the receiver has dynamic type $I$ and static type
+$J$.  Notice, for example in \textsc{(S-Invk)}, that when
+``$\new{I}$'' replaces ``\lstinline|this|'', its static type should be
+the interface to which $m$ is dispatched. Therefore we also keep the
+interface type in the definition of \mbody. This point is consistent
+with the last paragraph in Section~\ref{subsec:solutionmim}.
+
+On the other hand, there is a relationship between path invocation and
+the regular method invocation, and it can be observed from the
+similarity between their semantic rules in
+Figure~\ref{fig:smallstep}. For any \lstinline|e.I::m()|, the result
+of evaluation remains unchanged if we set the static type of
+\lstinline|e| to be $I$. This can be done by an implicit cast, that
+is, we can define a function with one parameter type $I$, then
+\lstinline|e| is passed to that function and directly returned. This
+is equivalent to writing explicit casts like \lstinline|((I) e).m()|
+in languages like Java.
 
@@
 	\spathinvk \\
-	\ssuperinvk
-\end{mathpar}
-\caption{Small-step semantics.}\label{fig:smallstep}
-\end{figure*}
-
-\begin{figure*}[t]
-\begin{mathpar}
+	\ssuperinvk \\
 	\creceiver \hspace{.5in}
@@
 \end{mathpar}
+\caption{Small-step semantics.}\label{fig:smallstep}
+\end{figure*}
+
+\begin{comment}
+\begin{figure*}[t]
+\begin{mathpar}
+\end{mathpar}
 \caption{Congruence.}\label{fig:congruence}
 \end{figure*}
+\end{comment}
 
@@
 
-To make our formalization concise and expressive, we have defined a list of
-auxiliary functions, collected by Figure~\ref{fig:auxfunc}. To begin with, we
+The auxiliary definitions used in our formalization are presented in 
+Figure~\ref{fig:auxfunc}. To begin with, we
 introduce the basic functions: $\ext, \overrideSet$ and $\prune$. $\ext(I, J)$
-simply indicates that interface $I$ directly extends interface $J$. Compared to
-to this is a more general case $I <: J$, meaning that $I$ is a subtype of $J$.
+simply indicates that interface $I$ directly extends interface $J$. 
 $\overrideSet(I, J)$ returns a set of methods defined in $I$ that have ``$\kwoverride \; J$''
@@
 \end{itemize}
-We could have put $set1$ and $set2$ together, but the current definition leads a clearer illustration.
+We could have put $set1$ and $set2$ together, but the current
+definition is clearer.
 
@@
 The set $\{I\}$ implies that we will use the $m$ from $I$ without ambiguity.
-But moreover, we have to invoke $\mostSpecificOverride(m, I_d, I)$, to check if there are updated versions of $m$ between $I_d$ and $I$.
+Moreover, we have to invoke $\mostSpecificOverride(m, I_d, I)$, to check if there are updated versions of $m$ between $I_d$ and $I$.
 Again we forbid ambiguity, so the expected set after pruning is also a singleton set $\{J\}$.
@@
 
-Examples on $\mbody$ are shown in Figure~\ref{fig:examplesmbody} for a better understanding.
+Examples for $\mbody$ are shown in Figure~\ref{fig:examplesmbody}.
 Note that we use \lstinline|m| to denote an original method, and ``\lstinline|m|$\uparrow$\lstinline|A|'' for a partial override on \lstinline|A|.
@@
 (d) because the two partial overrides are working on the same operation. Both counter-examples imply that \lstinline|new D().A::m()| will
-lead to ambiguity, and in order for type soundness, both have to be denied by the type checker. It has been guaranteed by the interface check
+lead to ambiguity, and in order for type soundness, both have to be denied by the type checker. This is guaranteed by the interface check
 \textsc{(T-Intf)} in Figure~\ref{fig:typingrules}.

### 2017-06-15 Aplas17/sections/Introduction.tex

@@
 \begin{itemize}
-	\item \textbf{Hierarchical dispatch:} which integrates both the static type and dynamic type for method dispatch, and hence
+	\item \textbf{Hierarchical dispatch algorithm:} which integrates both the static type and dynamic type for method dispatch, and hence
 	ensures unambiguity as well as extensibility.
 	\item \textbf{Partial overrides:} a novel notion that allows
-          method overrides on individual branches of the class hierarchy.
+          methods to override on individual branches of the class hierarchy.
 	\item \textbf{\name:} a formalized model based on Featherweight Java, supporting the above features. Some theorems and their proofs
-	are attached to confirm the type soundness (unambiguity?) of
-        the model.\bruno{Anything about unambiguity?}
+	are attached to confirm the type soundness of the model.\bruno{Anything about unambiguity?}
 \end{itemize}

### 2017-06-15 Aplas17/sections/Formalization.tex
small fix

--- 2017-06-15 Aplas17/sections/Formalization.tex
@@
 \section{Formalization}~\label{sec:formalization}
-
-In this section, we present a formalization of our \MIM{} calculus, based on
+In this section, we present the formal model \MIM{}, short for 
+\emph{\textbf{F}eatherweight \textbf{H}irarchical \textbf{J}ava} , based on
 a minimal subset of Java 8 interfaces following Featherweight Java style~\cite{Igarashi01FJ}.
-The syntax, typing rules and small-step
-semantics are included below.
+The syntax, typing rules and small-step semantics are included below.
 

### 2017-06-15 Aplas17/sections/RelatedWork.tex
RW revision

@@
 \subsection{Mainstream Multiple Inheritance Models}
-Multiple inheritance is a useful feature in object-oriented programming world although it's difficult to model and can 
+Multiple inheritance is an useful feature in object-oriented
+programming, although it is difficult to model and can 
 cause various problems (e.g. the diamond problem~\cite{Sak89dis,Singh1995}).  There are many existing languages/models that support multiple 
-inheritance, either coming with multiple inheritance capability or added through evolution. The Mixin model allows naming components 
+inheritance. The Mixin model~\cite{} allows naming components 
 that can be applied to various classes as reusable functionality units. However, the linearization (total ordering) of mixin 
@@
 
-Simplifying the mixins approach, traits~\cite{scharli03traits} draw a strong line between units of reuse and object factories. 
-Traits act as units of reuse, containing functionality code; while classes, assembled from traits, act as object factories.
+Simplifying the mixins approach, traits~\cite{scharli03traits} draw a
+strong line between units of reuse and object factories.  Traits act
+as units of reuse, containing functionality code; while classes,
+assembled from traits, act as object factories.\bruno{Should talk
+  about work on traits that support renaming.}\bruno{I remember Yanlin
+  had a presentation with alot of related work on multiple
+  inheritance. Many of those seem to be missing here} Java 8
+interfaces~\cite{} are closely related to traits: concrete method
+implementations are allowed (via the \textbf{\texttt{default}}
+keyword) inside interfaces.  The introduction of default methods opens
+the gate for various flavors of multiple inheritance in Java.
 
-Java 8 interfaces are closely related to traits: concrete method implementations are allowed (via the \textbf{\texttt{default}} keyword) inside interfaces. 
-The introduction of default methods opens the gate for various flavors of multiple inheritance in Java.
+Malayeri and Aldrich proposed a model CZ~\cite{malayeri2009cz} which
+aims to do multiple inheritance without the diamond problem.
+Inheritance is divided into two concepts: inheritance dependency and
+implementation inheritance.  Using a combination of
+\textbf{\texttt{requires}} and \textbf{\texttt{extends}}, a program
+with diamond inheritance is transformed to one without
+diamonds. Moreover, fields and multiple inheritance can coexist.
+However untangling inheritance also untangles the class structure. In
+CZ, not only the number of classes, but also the class hierarchy
+complexity increases.
 
-Malayeri and Aldrich proposed a model CZ~\cite{malayeri2009cz} which aims to do multiple inheritance without the diamond problem. 
-Inheritance is divided into two concepts: inheritance dependency and implementation inheritance. 
-Using a combination of \textbf{\texttt{requires}} and \textbf{\texttt{extends}}, a program with 
-diamond inheritance is transformed to one without diamonds. Moreover, fields and multiple inheritance can coexist. 
-However untangling inheritance also untangles the class structure. In CZ, not only the number of classes, but also 
-the class hierarchy complexity increases.
-
-The above mentioned models/languages support multiple inheritance, and they handle method conflicts in the same way, by
-simply disallowing two methods with the same signature from two different units to coexist. The ambiguity is resolved either
-by programmers explicitly or by setting a linearised composition. This is the common drawback of the above mentioned models versus our model.
+The above mentioned models/languages support multiple inheritance, and
+they handle method conflicts in the same way, by simply disallowing
+two methods with the same signature from two different units to
+coexist. The ambiguity is resolved either by programmers explicitly or
+by setting a linearised composition. This is the common drawback of
+the above mentioned models versus our model.
 
 \subsection{Resolving Unintended Method Conflicts}
-There are still a few languages that partly realize the problem. They provide limited support for unintended conflicting methods.
+There are a few languages that partly realize the problem of
+unintended conflicts and provide some support for it.
 
 \noindent {\bf C++ model.}
-C++ supports very flexible inheritance models and allows programmers to choose either static dispatch or dynamic dispatch for method lookup.
+C++ supports a very flexible inheritance model and allows programmers to choose either static dispatch or dynamic dispatch for method lookup.
 It allows unintended conflicts and uses static dispatch to resolve them, as discussed in Section~\ref{sec:overview}. For example, given the following code
@@
 method lookup algorithm will find the most specific method definition of $m$, namely \lstinline|C.m| at this time.
-Although C++ support this flexibility, unfortunately, dynamic dispatch on conflicting methods will be problematic.
-Furthermore, it does not support partial overrides compared to our model.
-
-\begin{lstlisting}
-\end{lstlisting}
+Although C++ support this flexibility, dynamic dispatching on
+conflicting methods is problematic.\bruno{why? give example of
+  something that goes wrong?}
+Furthermore, C++ does not support partial overrides compared to our
+model.
 
 \noindent  {\bf \csharp{} Explicit method implementation.}
-Explicit method implementation is a special feature supported by \csharp{}. As described in \csharp{}
-documentation~\cite{csharpdoc}, a class that implements an interface can explicitly implement a member of that
-interface. When a member is explicitly implemented, it can only be accessed through an instance
-of the interface. Explicit interface implementation allows the programmer to inherit two interfaces 
-that share the same member names and give each interface member a separate implementation.
+Explicit method implementation is a special feature supported by
+\csharp{}. As described in \csharp{} documentation~\cite{csharpdoc}, a
+class that implements an interface can explicitly implement a member
+of that interface. When a member is explicitly implemented, it can
+only be accessed through an instance of the interface. Explicit
+interface implementation allows the programmer to inherit two
+interfaces that share the same member names and give each interface
+member a separate implementation.
 
@@
 (1) default implementations are not allowed in \csharp{} interfaces; 
-(2) there are only one-level partial overrides (implementations).
-
-\begin{lstlisting}
-\end{lstlisting}
+(2) there is only one level of partial overrides (implementations).
 
@@
 language supports multiple (object) inheritance in a clever way. It not only develops the new inheritance
-relation \emph{prioritized parents}, but also adopts \emph{sender path tiebreaker rule} for method lookup, which is similar with our approach, using hierarchical information in method resolution, but in a prototype-based language setting.\haoyuan{Do they have updates?}
+relation with \emph{prioritized parents}, but also adopts \emph{sender path tiebreaker rule} for method lookup, which is similar with our approach, using hierarchical information in method resolution, but in a prototype-based language setting.\haoyuan{Do they have updates?}
 
 \subsection{Formalization Based on Featherweight Java}
-Featherweight Java~\cite{Igarashi01FJ} is a minimal core calculus of Java language, proposed by Igarashi et. al\haoyuan{Need cite}. There are
+Featherweight Java (FJ)~\cite{Igarashi01FJ} is a minimal core calculus of Java language, proposed by Igarashi et. al\haoyuan{Need cite}. There are
 many models built on
 Featherweight Java, including FeatherTrait~\cite{Liquori08ftj}, Featherweight defenders~\cite{goetz12fdefenders}, Jx~\cite{Nystrom2004}, and so on.
-It provides the standard model of formalizing a Java-like object-oriented language, and 
-is easily extensible. In terms of formalization, they key novelty of our model is the use of 
-static types as annotations along with various terms. As far as we know, this technique has not appear in literature before.
+FJ provides the standard model of formalizing a Java-like object-oriented language, and 
+is easily extensible. In terms of formalization, the key novelty of our model is the use of 
+static types as annotations along with various terms. As far as we
+know, this technique has not appeared in the literature before.

### 2017-06-15 Aplas17/paper.tex
fix

@@
 \newcommand{\authorText}[2]{{\color{#1}#2}}
+
 \newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
@@
 \newcommand\haoyuan[1]{\authornote{haoyuan}{cyan}{#1}}
+
+% \newcommand\bruno[1]{}
+% \newcommand\yanlin[1]{}
+% \newcommand\marco[1]{}
+% \newcommand\haoyuan[1]{}
 
@@
 % \title{Untangling Unintended Conflicts with Hierarchical Dispatch}
-\title{FHJ: A Formal Model for Resolving Unintended Conflicts in Multiple Inheritance}
+% \title{FHJ: A Formal Model for Resolving Unintended Conflicts in Multiple Inheritance}
+\title{Hirarchical Dispatching and Overriding}
 %\subtitle{\InterfaceBased Programming for the Masses}
@@
 (short for \emph{\textbf{F}eatherweight \textbf{H}irarchical \textbf{J}ava}) 
-that deals with unintended
+that deals with unintentional
 method conflicts. In our new model conflicting methods arising

### 2017-06-15 Aplas17/sections/Formalization.tex
fix

--- 2017-06-15 Aplas17/sections/Formalization.tex
@@
 
-In this section, we present a formalization of our \MIM{} calculus, based on
+In this section, we present the formal model \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}irarchical \textbf{J}ava}) , based on
 a minimal subset of Java 8 interfaces following Featherweight Java style~\cite{Igarashi01FJ}.
-The syntax, typing rules and small-step
-semantics are included below.
+The syntax, typing rules and small-step semantics are included below.
 
@@
 Object creation is directly supported via $\new I$. 
-Fields and primitive types are not modelled as well.
+Fields and primitive types are not modelled in \MIM{}.
 
@@
 For each small example, the result
-gives the interface to which $m$ is dispatched. (a) is a basic model for unintended method conflicts; (b) and (c) demonstrate
+gives the interface to which $m$ is dispatched. (a) is a basic model for unintentional method conflicts; (b) and (c) demonstrate
 that hierarchical dispatch can find the most specific original method and partial override. More interesting are the two bad examples

### 2017-06-15 Aplas17/sections/Overview.tex
fix

@@
 \section{A Running Example: DrawableDeck}~\label{sec:overview}
-
-\bruno{I've said this several times in the past: please use proper UML
-notation! The UML arrows are not right.}
-\bruno{This figure is never referred to in the text! You need to talk 
-about the figure in the text.}
-
 This section illustrates the features of our \MIM{} model for

### 2017-06-15 Aplas17/sections/RelatedWork.tex
fix

--- 2017-06-14 Aplas17/sections/RelatedWork.tex
@@
 
-\subsection{Resolving Unintended Method Conflicts}
-There are still a few languages that partly realize the problem. They provide limited support for unintended conflicting methods.
+\subsection{Resolving Unintentional Method Conflicts}
+There are still a few languages that partly realize the problem. They provide limited support for unintentional conflicting methods.
 
@@
 C++ supports very flexible inheritance models and allows programmers to choose either static dispatch or dynamic dispatch for method lookup.
-It allows unintended conflicts and uses static dispatch to resolve them, as discussed in Section~\ref{sec:overview}. For example, given the following code
+It allows unintentional conflicts and uses static dispatch to resolve them, as discussed in Section~\ref{sec:overview}. For example, given the following code
 \begin{lstlisting}[language=Java]

### 2017-06-15 Aplas17/paper.tex

@@
 % \title{FHJ: A Formal Model for Resolving Unintended Conflicts in Multiple Inheritance}
-\title{Hirarchical Dispatching and Overriding}
+\title{Hierarchical Dispatching and Overriding}
 %\subtitle{\InterfaceBased Programming for the Masses}
@@
 This paper presents a new model \name{} 
-(short for \emph{\textbf{F}eatherweight \textbf{H}irarchical \textbf{J}ava}) 
+(short for \emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}) 
 that deals with unintentional

### 2017-06-15 Aplas17/sections/Introduction.tex

@@
 inheritance in the past is that, as Cook~\cite{Cook1987} puts it, 
-multiple inheritance is good but ``\emph{there is no good way to do it}''.
+``\emph{multiple inheritance is good but there is no good way to do it}''.
 One of the most sensitive and critical issues is perhaps the ambiguity
 introduced by multiple inheritance. One case is the famous
-\textit{diamond problem}~\cite{Sak89dis,Singh1995}. In the diamond problem inheritance could allow
+\textit{diamond problem}~\cite{Sak89dis,Singh1995} (also known as ``fork-join inheritance''~\cite{Sak89dis}). In the diamond problem inheritance could allow
 one feature to be inherited from multiple parent classes that share a

### 2017-06-15 Aplas17/sections/RelatedWork.tex

--- 2017-06-15 Aplas17/sections/RelatedWork.tex
@@
 
-\subsection{Resolving Unintended Method Conflicts}
+\subsection{Resolving Unintentional Method Conflicts}
 There are a few languages that partly realize the problem of
-unintended conflicts and provide some support for it.
+unintentional conflicts and provide some support for it.
 
@@
 C++ supports a very flexible inheritance model and allows programmers to choose either static dispatch or dynamic dispatch for method lookup.
-It allows unintended conflicts and uses static dispatch to resolve them, as discussed in Section~\ref{sec:overview}. For example, given the following code
+It allows unintentional conflicts and uses static dispatch to resolve them, as discussed in Section~\ref{sec:overview}. For example, given the following code
 \begin{lstlisting}[language=Java]

### 2017-06-15 Aplas17/sections/Introduction.tex
revise Introduction

@@
 and mixins~\cite{bracha90mixin} to offer a disciplined form of multiple inheritance. Java 8 
-offers a variant of traits with disguised of interfaces with default methods~\cite{goetz12fdefenders}.
+offers a simple variant of traits with disguised of interfaces with default methods~\cite{goetz12fdefenders}.
 
 A reason why programming languages have resisted to multiple
-inheritance in the past is that, as Cook~\cite{Cook1987} puts it, 
+inheritance in the past is that, as Cook~\cite{Cook1987} put it, 
 ``\emph{multiple inheritance is good but there is no good way to do it}''.
@@
 introduced by multiple inheritance. One case is the famous
-\textit{diamond problem}~\cite{Sak89dis,Singh1995} (also known as ``fork-join inheritance''~\cite{Sak89dis}). In the diamond problem inheritance could allow
+\textit{diamond problem}~\cite{Sak89dis,Singh1995} (also known as ``fork-join inheritance''~\cite{Sak89dis}). 
+In the diamond problem, inheritance could allow
 one feature to be inherited from multiple parent classes that share a
@@
 languages and research have taken care of this case extensively. Other issues
-include how multiple inheritance deals with state, 
-which also has been discussed quite extensively~\cite{classless,malayeri2009cz,stroustrup1995}.
+including how multiple inheritance deals with state, 
+have also been discussed quite extensively~\cite{classless,malayeri2009cz,stroustrup1995}.
 
@@
 are inherited from a deck of cards and a drawable widget. 
-In such context the two draw methods have very different meanings, 
+In such context the two \lstinline{draw} methods have very different meanings, 
 but they happen to share the same name.
 %%This issue was proposed by the trait paper, so-called
-When inheritance is used to compose those methods an
+When inheritance is used to compose these methods, a compilation 
 error happens due to conflicts. However, unlike the diamond problem,
@@
 Unintentional method conflicts are less common than the diamond
-problem, nonetheless, they have severe effects in practice. This is
-unfortunate because such an issue has not received much formal study 
-before. In practice existing languages also provide limited support for
+problem, nonetheless, they have severe effects in practice. 
+Unfortunately, such an issue has not received much formal study 
+before. In practice, existing languages also provide limited support for
 it. In most languages, the mechanisms available to deal with this problem are the same as the diamond
-inheritance. Unfortunatelly this is often inadequate and can lead 
+inheritance. However, this is often inadequate and can lead 
 to tricky problems in practice. This is especially the case
@@
 a workaround from the diamond inheritance side, it is possible to
-define a new method in the child class, to override those conflicting
+define a new method in the child class to override those conflicting
 methods. Intuitively using one method to fuse two unrelated features
@@
 for code reuse and extensibility. A problem with the C++ approach is
-that it can only use either static or dynamic dispatching separately, but dealing
+that programmers can only use either static or dynamic dispatching separately, but dealing
 with unintentional method conflicts seems to require a combination of both.
@@
 extensibility are preserved. To present this idea, we introduce a
-formalized model in Section~\ref{sec:formalization} based on
+formalized model \MIM{} in Section~\ref{sec:formalization} based on
 Featherweight Java~\cite{Igarashi01FJ}, together with theorems and
@@
 \begin{itemize}
-	\item \textbf{Hierarchical dispatch algorithm:} which integrates both the static type and dynamic type for method dispatch, and hence
+	\item \textbf{Hierarchical dispatch algorithm:} an algorithm that integrates both the static type and dynamic type for method dispatch, and hence
 	ensures unambiguity as well as extensibility.

### 2017-06-15 Calculus/src/framework/FHJ.scala
Done type checker regarding implementation.

@@ -1,0 +1,244 @@
+package framework
+
+import scala.util.parsing.combinator._
+import scala.util.parsing.combinator.syntactical._
+
+object FHJ extends StandardTokenParsers with PackratParsers {
+  
+  case class Info(table: List[String], typeMap: Map[String, List[String]],
+      methodMap: Map[String, List[MethDef]], typeDefMap: Map[String, TypeDef]) {
+    def ext(t1: String, t2: String): Boolean = {
+      if (!table.contains(t1) || !table.contains(t2)) throw new Exception("Error: ext.")
+      typeMap.get(t1).contains(t2)
+    }
+    def subType(t1: String, t2: String): Boolean = {
+      if (!table.contains(t1) || !table.contains(t2)) throw new Exception("Error: subType.")
+      if (t1 == t2) return true
+      typeMap.get(t1).get.exists(x => subType(x, t2))
+    }
+    def overrideSet(i: String, j: String): Set[String] = {
+      if (!table.contains(i) || !table.contains(j)) throw new Exception("Error: overrideSet.")
+      methodMap.get(i).get.filter(x => x.update == j).map(x => x.name).toSet
+    }
+    def prune(set: Set[String]): Set[String] = set.filter(i => !set.exists(j => j != i && subType(j, i)))
+    def collectMethods(i: String): Set[String] = {
+      if (!table.contains(i)) throw new Exception("Error: collectMethods.")
+      val start = methodMap.get(i).get.map(x => x.name).toSet
+      val op = (s: Set[String], x: String) => s ++ collectMethods(x)
+      typeMap.get(i).get.foldLeft(start)(op)
+    }
+    def mbody(m: String, id: String, is: String): Option[(String, List[(String, String)], (String, Expr))] = {
+      if (!table.contains(id) || !table.contains(is)) throw new Exception("Error: mbody.")
+      val set1 = mostSpecific(m, id, is)
+      if (set1.size != 1) return None
+      val i = set1.head
+      val set2 = mostSpecificOverride(m, id, i)
+      if (set2.size != 1) return None
+      val j = set2.head
+      val method = methodMap.get(j).get.find(x => x.name == m && x.update == i)
+      if (method.isEmpty) None else Some(j, method.get.paras, (method.get.returnType, method.get.returnExpr))
+    }
[…]

### 2017-06-15 Calculus/src/framework/Util.scala

@@ -1,383 +1,0 @@
-package framework
-
-import scala.util.parsing.combinator._
-import scala.util.parsing.combinator.syntactical._
-
-object Util extends StandardTokenParsers with PackratParsers {
-  
-  def noDuplicate[E](l : List[E]) : Boolean = l.size == l.toSet.size
-  
-  class Info(
-      ts : Set[String],
-      dMap : Map[String, Set[String]],
-      mMap : Map[String, Set[MethDef]],
-      noOL : Boolean) {
-    val traits = ts
-    val directUpMap = dMap
-    val methodMap = mMap // TO BE DEBUGGED, ALL CODE RELATED TO methodMap
-    val methodNameMap = mMap.mapValues{x => x.filter{y => y.updateTrait.isEmpty()}.map{y => y.name}}
-    val noOverloading : Boolean = noOL // TO BE DEBUGGED
-    lazy val upMapOption : Option[Map[String, Set[String]]] = {
-      def f : (String, Set[String]) => Option[Set[String]] = (x, s) => {
-        val setX : Set[String] = directUpMap.getOrElse(x, Set())
-        if (directUpMap.get(x).isEmpty || !(setX & s).isEmpty) None else {
-          val set = setX.map{x => f(x, s + x).map{y => y + x}}
-          if (!set.forall{x => x.isDefined}) None
-          else Some(set.foldLeft(Set[String]())((x, y) => x ++ y.get))
-        }
-      }
-      if (traits.isEmpty) Some(Map()) else {
-        val res : Set[Option[Map[String, Set[String]]]] =
-          traits.map{x => f(x, Set(x)).map{y => Map(x -> y)}}
-        if (!res.forall{x => x.isDefined}) None
-        else Some(res.foldLeft(Map[String, Set[String]]())((x, y) => x ++ y.get))
-      }
-    }
-    lazy val noCycle : Boolean = upMapOption.isDefined
-    lazy val infoCheck : Boolean = noCycle && noOverloading
-    lazy val upMap : Map[String, Set[String]] = upMapOption.getOrElse(Map())
-    lazy val mBody : Map[String, Map[String, Set[String]]] = {
-      upMap.toSet[(String, Set[String])]
-           .foldLeft(Map[String, Map[String, Set[String]]]())((accM, p) => accM + (p._1 -> {
-        (p._2 + p._1).map{x => methodNameMap.get(x).get}
[…]

### 2017-06-16 Calculus/src/framework/FHJ.scala
Done implementation.

@@ -93,6 +93,10 @@ object FHJ extends StandardTokenParsers with PackratParsers {
       val checkType = e.checkType(env)
       if (checkType.isEmpty) Left("Expression type-check failed") else Right(checkType.get)
     }
+    def run: Option[Value] = {
+      if (programCheck.isLeft) None
+      else Some(e.eval(new {val info = collectInfo.get; val gamma = Map[String, String]()}))
+    }
   }
   
   case class TypeDef(name: String, sups: List[String], methods: List[MethDef]) {
@@ -126,18 +130,28 @@ object FHJ extends StandardTokenParsers with PackratParsers {
   }
   
   abstract class Expr {
+    def copy: Expr
     def checkType(env: Env): Option[String]
+    def subst(map: Map[String, Expr]): Expr
+    def eval(env: Env): Value
   }
   
   case class Var(n: String) extends Expr {
+    def copy = Var(n)
     def checkType(env: Env) = env.gamma.get(n)
+    def subst(map: Map[String, Expr]) = if (map.contains(n)) map.get(n).get.copy else Var(n)
+    def eval(env: Env) = throw new Exception("Error: Var.eval.")
   }
   
   case class New(o: String) extends Expr {
+    def copy = New(o)
     def checkType(env: Env) = if (env.info.table.contains(o)) Some(o) else None
+    def subst(map: Map[String, Expr]) = New(o)
+    def eval(env: Env) = new Value(o, o)
   }
   
   case class Invk(e: Expr, m: String, args: List[Expr]) extends Expr {
+    def copy = Invk(e.copy, m, args.map(x => x.copy))
     def checkType(env: Env): Option[String] = {
       val eT = e.checkType(env)
       if (eT.isEmpty) return None
@@ -148,9 +162,20 @@ object FHJ extends StandardTokenParsers with PackratParsers {
       val argsMismatch = mtype.get._1.zip(argsT).exists(p => p._2.isEmpty || !env.info.subType(p._2.get, p._1))
       if (argsMismatch) None else Some(mtype.get._2)
     }
+    def subst(map: Map[String, Expr]) = Invk(e.subst(map), m, args.map(x => x.subst(map)))
+    def eval(env: Env) = {
+      val eValue = e.eval(env)
+      val (tempI, tempJ) = (eValue.id, eValue.is)
[…]

### 2017-06-17 Aplas17/sections/Formalization.tex
langle rangle

@@
 hence they are not supposed to appear in the source program. A value
-``$\langle I \rangle~\new J$''
+``$\angl{I}\new{J}$''
 is the final result of multple reduction steps evaluating an
@@
 e.I::m(\overline{e}) \mid
-\kwsuper.I::m(e) \; \mid \; \langle I \rangle~e \\
+\kwsuper.I::m(e) \; \mid \; \angl{I}e \\
 \text{Context}      & \Gamma & \Coloneqq & \overline{x:I} \\
-\text{Values}       & v & \Coloneqq & \langle I \rangle~\new{J} \\
+\text{Values}       & v & \Coloneqq & \angl{I} \new{J} \\
 %%\\
@@
 \begin{enumerate}
-\item If $e$ includes $\left(<J>\emph{\kwnew}\;I()\right).m(\overline{<I_E>} \; \overline{e})$ as a subexpression,
+\item If $e$ includes $\left(\angl{J}\emph{\kwnew}\;I()\right).m(\overline{\angl{I_E}} \; \overline{e})$ as a subexpression,
     then $ \emph{\mbody}(m, I, J) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and
          $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$.
-\item If $e$ includes $\left(<J>\emph{\kwnew}\;I()\right).K::m(\overline{<I_E> e})$ as a subexpression,
+\item If $e$ includes $\left(\angl{J}\emph{\kwnew}\;I()\right).K::m(\overline{\angl{I_E} e})$ as a subexpression,
     then $ \emph{\mbody}(m, I, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
          $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$.
-\item If $e$ includes $\emph{\kwsuper}.K::m(\overline{<I_E> e})$ as a subexpression,
+\item If $e$ includes $\emph{\kwsuper}.K::m(\overline{\angl{I_E} e})$ as a subexpression,
     then $ \emph{\mbody}(m, K, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 

### 2017-06-17 Aplas17/sections/Formalization.tex
separate \overline

@@
 \kwsuper.I::m(e) \; \mid \; \angl{I}e \\
-\text{Context}      & \Gamma & \Coloneqq & \overline{x:I} \\
+\text{Context}      & \Gamma & \Coloneqq & \overline{x}:\overline{I} \\
 \text{Values}       & v & \Coloneqq & \angl{I} \new{J} \\
@@
          $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$.
-\item If $e$ includes $\left(\angl{J}\emph{\kwnew}\;I()\right).K::m(\overline{\angl{I_E} e})$ as a subexpression,
+\item If $e$ includes $\left(\angl{J}\emph{\kwnew}\;I()\right).K::m(\overline{\angl{I_E}} \overline{e})$ as a subexpression,
     then $ \emph{\mbody}(m, I, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
          $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$.
-\item If $e$ includes $\emph{\kwsuper}.K::m(\overline{\angl{I_E} e})$ as a subexpression,
+\item If $e$ includes $\emph{\kwsuper}.K::m(\overline{\angl{I_E}} \overline{e})$ as a subexpression,
     then $ \emph{\mbody}(m, K, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 

### 2017-06-17 Aplas17/sections/Formalization.tex
consistant notation of I_x

@@
 			\mostSpecificOverride(m, I_d, I) = \{J\} \\
-			\kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_E}{m}{I_X}{x}{I}{e_0}\ldots\}}
-		{\mbody(m, I_d, I_s) = (J, \overline{I_X} \; \overline{x}, I_E \; e_0)}
+			\kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_e}{m}{I_x}{x}{I}{e_0}\ldots\}}
+		{\mbody(m, I_d, I_s) = (J, \overline{I_x} \; \overline{x}, I_e \; e_0)}
 
@@
 	\inferrule* [left=]
-	{   \kwinterface \; I \; \kwextends \; \overline{I} \; \{ I_E \; m(\overline{I_X} \; \overline{x}) \;
+	{   \kwinterface \; I \; \kwextends \; \overline{I} \; \{ I_e \; m(\overline{I_x} \; \overline{x}) \;
 		\kwoverride \; J \ldots \} }
@@
 The definition of $\mtype$ used in typing rules simply relies on $\mbody$. In short,
-$$\mbody(m, I, I) = (J, \overline{I_x}\ \overline{x}, I_E\ e) \ \Longrightarrow\ \mtype(m, I) = \overline{I_x}\rightarrow I_E$$
+$$\mbody(m, I, I) = (J, \overline{I_x}\ \overline{x}, I_e\ e) \ \Longrightarrow\ \mtype(m, I) = \overline{I_x}\rightarrow I_e$$
 
@@
 \begin{enumerate}
-\item If $e$ includes $\left(\angl{J}\emph{\kwnew}\;I()\right).m(\overline{\angl{I_E}} \; \overline{e})$ as a subexpression,
-    then $ \emph{\mbody}(m, I, J) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and
-         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$.
-\item If $e$ includes $\left(\angl{J}\emph{\kwnew}\;I()\right).K::m(\overline{\angl{I_E}} \overline{e})$ as a subexpression,
-    then $ \emph{\mbody}(m, I, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
-         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$.
-\item If $e$ includes $\emph{\kwsuper}.K::m(\overline{\angl{I_E}} \overline{e})$ as a subexpression,
-    then $ \emph{\mbody}(m, K, K) = (J', \overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
-         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$.
+\item If $e$ includes $\left(\angl{J}\emph{\kwnew}\;I()\right).m(\overline{\angl{I_e}} \; \overline{e})$ as a subexpression,
+    then $ \emph{\mbody}(m, I, J) = (J', \overline{I_x} \; \overline{x}, I'_E \; e_0) $ and
+         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_x}, \overline{x}, I_e'$ and $e_0$.
+\item If $e$ includes $\left(\angl{J}\emph{\kwnew}\;I()\right).K::m(\overline{\angl{I_e}} \overline{e})$ as a subexpression,
+    then $ \emph{\mbody}(m, I, K) = (J', \overline{I_x} \; \overline{x}, I'_E \; e_0) $ and 
+         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_x}, \overline{x}, I_e'$ and $e_0$.
+\item If $e$ includes $\emph{\kwsuper}.K::m(\overline{\angl{I_e}} \overline{e})$ as a subexpression,
+    then $ \emph{\mbody}(m, K, K) = (J', \overline{I_x} \; \overline{x}, I'_E \; e_0) $ and 
+         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_x}, \overline{x}, I_e'$ and $e_0$.
 \end{enumerate}

### 2017-06-17 Calculus/src/framework/FHJ.scala
Added tests to validate impl.

@@ -97,6 +97,10 @@ object FHJ extends StandardTokenParsers with PackratParsers {
       if (programCheck.isLeft) None
       else Some(e.eval(new {val info = collectInfo.get; val gamma = Map[String, String]()}))
     }
+    override def toString = {
+      val isStr = if (is.isEmpty) "" else is.map(x => x.toString).reduce((a, b) => a + "\n" + b) + "\n\n"
+      isStr + e.toString
+    }
   }
   
   case class TypeDef(name: String, sups: List[String], methods: List[MethDef]) {
@@ -107,6 +111,11 @@ object FHJ extends StandardTokenParsers with PackratParsers {
       val collectMethods = env.info.collectMethods(name)
       !(collectMethods.exists(m => env.info.table.exists(j => env.info.subType(name, j) &&
           env.info.mtype(m, j).isDefined && env.info.mbody(m, name, j).isEmpty)))
+    }
+    override def toString = {
+      val supStr = if (sups.isEmpty) "" else " extends " + sups.reduce((a, b) => a + ", " + b)
+      "interface " + name + supStr + " " +
+        (if (methods.size == 0) "{}" else "{\n" + methods.map(x => x.toString).reduce((a, b) => a + "\n" + b) + "\n}")
     }
   }
   
@@ -127,6 +136,11 @@ object FHJ extends StandardTokenParsers with PackratParsers {
       val mostSpecific = env.info.mostSpecific(name, thisType, update)
       mostSpecific.size == 1 && mostSpecific.head == update
     }
+    override def toString = {
+      val parasStr = if (paras.isEmpty) "" else paras.map(p => p._1 + " " + p._2).reduce((a, b) => a + ", " + b)
+      "  " + returnType + " " + name + "(" + parasStr + ") override " + update + " {\n    return " +
+        returnExpr.toString + ";\n  }"
+    }
   }
   
   abstract class Expr {
@@ -134,6 +148,7 @@ object FHJ extends StandardTokenParsers with PackratParsers {
     def checkType(env: Env): Option[String]
     def subst(map: Map[String, Expr]): Expr
     def eval(env: Env): Value
+    override def toString: String
   }
   
   case class Var(n: String) extends Expr {
@@ -141,6 +156,7 @@ object FHJ extends StandardTokenParsers with PackratParsers {
     def checkType(env: Env) = env.gamma.get(n)
[…]

### 2017-06-17 Aplas17/sections/Conclusion.tex
Add text for implementaion.

--- 2017-06-05 SpringerLNCS/sections/Conclusion.tex
@@
 Such an approach not only offers great code reuse like dynamic dispatch, but also ensures unambiguity by
-our algorithm for method binding. This paper also introduces method updates for refinements on branches individually.
+our algorithm for method resolution. This paper also introduces method updates for refinements on branches individually.
 \MIM{} is formalized with a basis on Featherweight Java, and supported
-by a few theorems.
+by a few theorems. The prototype is implemented in Scala as a simple interpreter.
 
-Our model can certainly be improved at some aspects. We did not formalize fields, though it is difficult to
-put state and multiple inheritance together []. For simplicity, we did not formalize other common features including
-method overloading, casts, covariant return types, and so on. Moreover, we restrict method updates to target only at the
-original methods. Potentially a looser condition can better support encapsulation and modularity with respect to code design.
+Our model can certainly be improved at some aspects. We did not formalize fields as in Featherweight Java for simplicity.
+And we did not formalize other common features including
+method overloading, casts, covariant return types, and so on, some of which are orthogonal in the design space.
+Moreover, we restrict that hierarchical overriding can only work on original methods.
+Potentially a looser condition can better support encapsulation and modularity with respect to code design.

### 2017-06-17 Aplas17/sections/Introduction.tex
Add text for implementaion.

@@
 
-In summary, our contributions are: \haoyuan{will have prototype implementation in Scala if we still have time.}
+In summary, our contributions are:
 \begin{itemize}
@@
 	are attached to confirm the type soundness of the model.\bruno{Anything about unambiguity?}
+	\item \textbf{Prototype Implementation\footnote{Available in supplementary material attached to the submission.}:} a simple interpreter implemented in Scala that follows our formalization rules, incorporating parsing, type-checking and semantic evaluation.\haoyuan{also mention in formalization.}
 \end{itemize}

### 2017-06-17 Aplas17/sections/Introduction.tex
Revising overview. Done 2.1

--- 2017-06-15 Aplas17/sections/Introduction.tex
@@
 proofs for type soundness. In the model we also propose
-\textit{partial overrides}, where method overriding can be applied
+\textit{hierarchical overriding}, where method overriding can be applied
 only to one branch of the class hierarchy. Our model can be viewed as
@@
 	ensures unambiguity as well as extensibility.
-	\item \textbf{Partial overrides:} a novel notion that allows
+	\item \textbf{Hierarchical overriding:} a novel notion that allows
           methods to override on individual branches of the class hierarchy.
@@
 	are attached to confirm the type soundness of the model.\bruno{Anything about unambiguity?}
+	\item \textbf{Prototype implementation\footnote{Available in supplementary material attached to the submission.}:} a simple interpreter implemented in Scala that follows our formalization rules, incorporating parsing, type-checking and semantic evaluation.\haoyuan{also mention in formalization.}
 \end{itemize}

### 2017-06-17 Aplas17/sections/Overview.tex
UML
Revising overview. Done 2.1

@@
 ``\lstinline|interface|''. The concept is closely related to Java 8
-interfaces with default methods~\cite{}, and traits. For simplicity, an interface in our model has
+interfaces with default methods~\cite{bono14} and traits. For simplicity, an interface in our model has
 the following characteristics:
@@
 have been developed in a system.  \lstinline|Deck| represents a deck
-of cards, and defines \lstinline|draw()| for drawing a card from the
+of cards, and defines \lstinline|draw| for drawing a card from the
 deck.  \lstinline|Drawable| is an interface for graphics that
-can be drawn, and also includes a method called \lstinline|draw()| for
+can be drawn, and also includes a method called \lstinline|draw| for
 visual display. For illustration, the implementation of
-\lstinline|draw()| in \lstinline|Drawable| only creates a blank canvas
+\lstinline|draw| in \lstinline|Drawable| only creates a blank canvas
 on the screen, and later some instances (\lstinline|Circle|,
 \lstinline|Square|, or others) that extend \lstinline|Drawable| may
-define their own \lstinline|drawObject()| methods and invoke
-\lstinline|draw()|.
+define their own \lstinline|drawObject| methods and invoke
+\lstinline|draw|.
 
@@
     Stack<Card> cards = this.getStack();
-    if (!cards.isEmpty()) {
-      Card card = cards.pop();
-      ...
-    }
+    if (!cards.isEmpty()) { Card card = cards.pop(); ... }
   }
@@
 \end{lstlisting}\vspace{3pt}
-\bruno{Space is probably going to be a problem, so you may have to
-  consider putting code side-by-side to maximize space usage.}
 Note that both methods have \lstinline|void| return type (we will not formalize
-\lstinline|void| in our calculus afterwards; here is only for illustration). In \lstinline|Deck|, \lstinline|draw()| tries to get the cards as a stack, pops
-out the top card, and so on. While in \lstinline|Drawable|, \lstinline|draw()|
+\lstinline|void| in our calculus afterwards; here is only for illustration). In \lstinline|Deck|, \lstinline|draw| tries to get the cards as a stack, pops
+out the top card, and so on. While in \lstinline|Drawable|, \lstinline|draw|
 creates a blank canvas using \lstinline|JFrame|. Now, a programmer is designing a
@@
 The point of using multiple inheritance is surely for composing the features from various 
-components, and to achieve code reuse. Multiple inheritance is supported by many mainstream OO
-languages. Nevertheless at this point, \lstinline|DrawableDeck| has to throw a compile
-error, since the two \lstinline|draw()| methods cause a conflict, though accidentally.
+components, and to achieve code reuse, as supported by many mainstream OO
+languages. Nevertheless at this point, languages like Java simply throw a compile
+error on \lstinline|DrawableDeck|, since the two \lstinline|draw| methods cause a conflict, though accidentally.
 
-\subsection{Potential Fixes}
+Now one may quickly comes up with a workaround, which is creating a new \lstinline|draw| in \lstinline|DrawableDeck| to
+explicitly overrides the old ones. However, the two conflicting methods have totally different functionalities, merging
+them into one does not make any sense. This non-solution will hide the old methods, and break independent extensibility. The
+feature we expect is called ``triangle inheritance'', that is to say, when the conflicting methods serve for different behaviours,
+we can allow them to coexist in the extending interface in a type-safe way.\\
 
-For that problem, there are several workarounds. We go over some of
-the main ones next.
-
-\paragraph{I. Delegation.} As an alternative to multiple inheritance,
+\noindent\textbf{Potential Fixes} There are several workarounds that come to our mind:
+\begin{itemize}
+	\item \textbf{I. Delegation.} As an alternative to multiple inheritance,
 	delegation can be used by introducing two fields with
@@
 	introduces a lot of boilerplate code.
-
-\paragraph{II. Creating a \lstinline|draw()| method in \lstinline|DrawableDeck|, which explicitly overrides the old ones.}
-This is a non-solution. It does not make any sense to override both methods with totally different functionalities, as old
-methods have to be hidden.
-
-\paragraph{III. Refactor Drawable and/or Deck to rename the methods.} If
+	\item \textbf{II. Refactor Drawable and/or Deck to rename the methods.} If
 	the code for \lstinline|Drawable| or \lstinline|Deck| are available
@@
 	modifying existing code, and may not be possible if code is unavailable.
-
-%\paragraph{III. Choosing one of them as the default method, like Mixins.} The mixin model can be applied to choose a
-%default one based on linearisation. Similarly, we want to preserve both features, rather than keeping only one of them.
-
-\paragraph{IV. Method exclusion/renaming in traits.} Some trait models
+	\item \textbf{III. Method exclusion/renaming in traits.} Some trait models
 	support method exclusion/renaming. Those features
@@
 	names can affect other code blocks.
+	\item \textbf{IV. Static dispatch.} Some other languages like C++ have
+	direct support for the triangle inheritance. While conflicting methods are
+	both preserved, the ambiguity of method call is resolved by static dispatch.
+	Qualified names are used to specify the branch to give the right implementation.
+\end{itemize}
 
-\paragraph{V. Static dispatch.}
-What we really expect from the language is keeping both methods
-without renaming, and the type checker does not complain. 
-But we need to find an approach to \emph{disambiguate on method
-calls statically}.
-\bruno{Perhaps show the solution in MIM here (i.e Section 2.4), and then move to problem
-2 (which is being discussed next with shuffleAndDraw)}
+\noindent\textbf{Solution in \name{}:} below is the pseudo-code that shows the triangle
+inheritance supported by \name{}.
+We can define \lstinline|DrawableDeck| by inheriting \lstinline|Drawable| and \lstinline|Deck| together while
+type safety is ensured. It is slightly different from our prototype as we do not model \lstinline|void|, though one can
+define a \lstinline|Void| interface for it.
+\vspace{3pt}\begin{lstlisting}
+interface DrawableDeck extends Drawable, Deck {}
 
-Certainly the compiler can ignore the conflict when
-\lstinline|DrawableDeck| is declared, but once an object of
-\lstinline|DrawableDeck| is created, a method call for
-\lstinline|draw()| on that object would be ambiguous. Nonetheless, we can adopt static dispatch for
-disambiguating. Some languages like C++ use qualified names in that
-way:
-
-\vspace{3pt}\begin{lstlisting}
-void func(Drawable obj) {
-  obj.draw();
+interface Foo {
+  void func(Deck obj) { obj.draw(); }
 }
 
-DrawableDeck d = new DrawableDeck();
-d.Drawable::draw();       // calling draw() in Drawable
-((Drawable) d).draw(); // calling draw() in Drawable
-func(d);                 // calling draw() in Drawable
+// main program
+new DrawableDeck().Drawable::draw()      // calling draw() in Drawable
+new Foo().func(new DrawableDeck())       // calling draw() in Deck
 \end{lstlisting}\vspace{3pt}
-Static dispatch in C++ finds out and invokes the most specific method ``by need''.
+Note that both cases in the above code are valid in C++ for disambiguation. As shown by \lstinline|func|, C++ looks at
+the static type of the receiver for static dispatching. Normally we can define such a method \lstinline|func| for ``implicit''
+casts in \name{}. C++ further allows explicit casts.
+
+In the following text we will see that C++ is still unsatisfactory, as it introduces another problem on code reuse, which motivates
+our work.
 

### 2017-06-17 Aplas17/sections/RelatedWork.tex
added references

@@
 \section{Related Work}
+Here we describe related work in four parts. We discuss from mainstream popular multiple 
+inheritance models to several specific models (C++ and \csharp) which are closest to our work. Then we 
+discuss similar techniques used in \self. Finally we discuss the foundation and related work of our formalization.
 
@@
 programming, although it is difficult to model and can 
-cause various problems (e.g. the diamond problem~\cite{Sak89dis,Singh1995}).  There are many existing languages/models that support multiple 
-inheritance. The Mixin model~\cite{} allows naming components 
+cause various problems (e.g. the diamond problem~\cite{Sak89dis,Singh1995}).  
+There are many existing languages/models that support multiple 
+inheritance~\cite{ellis1990annotated,scala-overview,bracha90mixin,scharli03traits,malayeri2009cz,csharpdoc,Moon1986,Flatt1998,Ancona2003}. 
+The Mixin model~\cite{bracha90mixin} allows naming components 
 that can be applied to various classes as reusable functionality units. However, the linearization (total ordering) of mixin 
 inheritance cannot provide a satisfactory resolution in some cases and restricts the flexibility of mixin composition. 
+Scala traits~\cite{scala-overview} are in fact linearized mixins and hence have the same problem as mixins.
 
-Simplifying the mixins approach, traits~\cite{scharli03traits} draw a
+Simplifying the mixins approach, traits~\cite{scharli03traits,Ducasse:2006:TMF:1119479.1119483} draw a
 strong line between units of reuse and object factories. Traits act
 as units of reuse, containing functionality code; while classes,
-assembled from traits, act as object factories.\bruno{Should talk
+assembled from traits, act as object factories. Java 8
+interfaces are closely related to traits: concrete method
+implementations are allowed (via the \textbf{\texttt{default}}
+keyword) inside interfaces and there are also proposals such as FeatherTrait Java~\cite{Liquori08ftj} 
+for extending Java with traits. There are extensions~\cite{reppy2006foundation,Reppy:2007:MT:2394758.2394784} to 
+the original trait model with various advanced features such as \emph{renaming}. As discussed in Section~\ref{sec:overview},
+the renaming feature helps to solve the unintentional method conflicts problem, however, it breaks structural subtyping.
+\bruno{Should talk
   about work on traits that support renaming.}\bruno{I remember Yanlin
   had a presentation with alot of related work on multiple
-  inheritance. Many of those seem to be missing here} Java 8
-interfaces~\cite{} are closely related to traits: concrete method
-implementations are allowed (via the \textbf{\texttt{default}}
-keyword) inside interfaces.  The introduction of default methods opens
-the gate for various flavors of multiple inheritance in Java.
+  inheritance. Many of those seem to be missing here}
+
+\begin{comment}
+There are also proposals for extending Java with traits. For example, 
+FeatherTrait Java (FTJ) [14] extends FJ [13] with statically-typed traits, 
+adding trait-based inheritance in Java. Except for few, mostly syntac- tic details, 
+their work can be emulated with Java 8 interfaces. There are also extensions 
+to the original trait model, with operations (e.g. renaming [18], which breaks 
+structural sub- typing) that default methods and interfaces cannot model.
+\end{comment}
 
@@
 Although C++ support this flexibility, dynamic dispatching on
-conflicting methods is problematic.\bruno{why? give example of
+unintentional conflicting methods is problematic, as discussed in Section~\ref{sec:overview}.\bruno{why? give example of
   something that goes wrong?}

### 2017-06-17 Aplas17/sections/Overview.tex
Overview up to 2.2

@@
 this stage. %%, but that should not block our discussions below.
-\bruno{I think there are two important things being discussed in this
-  section:
-1) Hierarchical dispatch: which allows methods calls to be correctly 
-dispatched based on a combination of static and dynamic type
-information; and
-2) Traingle Inheritance: i.e. allowing multiple method implementations 
-to coexist in the same class based on the superclass hierarchy.
-
-The text in this section is good, but it could emphasize better those 
-two aspects. I think the text starts off with point 2) (the two draw
-methods), then in between the discussion moves to hierarchical
-dispatching. Later it returns to point 2. 
-}
 
@@
 	that using delegation makes it hard to correctly maintain
-	self-references \haoyuan{?} in an extensible system [], and also
+	self-references \haoyuan{need to cite} in an extensible system [], and also
 	introduces a lot of boilerplate code.
@@
 // main program
-new DrawableDeck().Drawable::draw()      // calling draw() in Drawable
-new Foo().func(new DrawableDeck())       // calling draw() in Deck
+new DrawableDeck().Drawable::draw()      // calling draw in Drawable
+new Foo().func(new DrawableDeck())       // calling draw in Deck
 \end{lstlisting}\vspace{3pt}
@@
 
-\subsection{Problem 2: Dynamic Dispatch for Code Reuse}
-\begin{figure*}[t]
-\centering
-\includegraphics[height=2cm]{pics/DrawableLoggingDeck.pdf}
-\caption{DrawableLoggingDeck UML}\label{fig:drawableloggingdeck}
-\end{figure*}
+\subsection{Problem 2: Dynamic Dispatch for Code Reuse}\label{subsec:problem2}
 
@@
 C++ has the flexibility for choosing either way of dispatch by the \kwvirtual{} keyword.
-Unfortunately, this approach is still unsatisfactory regarding code reuse. For instance in Figure~\ref{fig:drawableloggingdeck}, 
+Unfortunately, this approach is still unsatisfactory regarding code reuse. For instance, 
 we redefine \lstinline|Deck| to support
-both \lstinline|draw()| and another operation called \lstinline|shuffleAndDraw()|:
+both \lstinline|draw| and another operation called \lstinline|shuffleAndDraw|:
 \vspace{3pt}\begin{lstlisting}
@@
   void draw() {...}
-  void shuffleAndDraw() {
-    shuffle();
-    draw();
-  }
+  void shuffleAndDraw() { shuffle(); draw(); }
   ...
@@
 \end{lstlisting}\vspace{3pt}
-\lstinline|shuffleAndDraw()| is a representative method that invokes \lstinline|draw()| in its definition. In principle, we want
-that invocation to use dynamic dispatch, because a programmer may define a subtype of \lstinline|Deck|, and override \lstinline|draw()|:
+\lstinline|shuffleAndDraw| is a typical method that invokes \lstinline|draw| in its definition. In principle, we want
+that invocation to use dynamic dispatch, because a programmer may define a subtype of \lstinline|Deck|, and override \lstinline|draw|:
 \vspace{3pt}\begin{lstlisting}
@@
       ...
-    } else {
-      println("Empty deck.");
-    }
+    } else println("Empty deck.");
   }
@@
 \end{lstlisting}\vspace{3pt}
-Usually we want to reuse the code of \lstinline|shuffleAndDraw()| during inheritance, hence dynamic dispatch is necessary, otherwise
-programmers have to override all the other methods that invoke \lstinline|draw()|. However, as seen before, dynamic dispatch can cause
-ambiguity if we have:
+In that case, \lstinline|shuffleAndDraw| needs to be adapted to the new \lstinline|draw|. But due to static dispatch,
+it still refers to the old \lstinline|draw| in \lstinline|Deck|. Thus programmers have to copy the \lstinline|shuffleAndDraw| code in
+\lstinline|LoggingDeck|. It requires a lot of redundant work if we have to duplicate all such methods. Hence in order for code reuse,
+we cannot just rely on static dispatch. However, as seen before, dynamic dispatch would take us back to problem 1, for instance, when we
+have the UML in Figure~\ref{fig:drawableloggingdeck} and the following code:
 \vspace{3pt}\begin{lstlisting}
@@
 DrawableLoggingDeck d = new DrawableLoggingDeck();
-d.shuffleAndDraw(); // ambiguous draw()
+d.shuffleAndDraw(); // ambiguous draw if dynamically dispatched
 \end{lstlisting}\vspace{3pt}
-Since the dynamic type of the receiver is \lstinline|DrawableLoggingDeck|, calling \lstinline|shuffleAndDraw()| triggers the ambiguity.
-When \lstinline|shuffleAndDraw()| invokes \lstinline|draw()|, what we really want is \lstinline|LoggingDeck.draw()|, yet
-neither static dispatch nor dynamic dispatch in languages like C++ does so.
- Therefore, we need to find another algorithm for method resolution.
 
-\subsection{Solution in \MIM: \dispatchnamecaptical}\label{subsec:solutionmim}
-The \MIM{} model uses \dispatchnameit{} for method lookup. A qualified
-method invocation, for instance, \lstinline|e.I::m()|, is read as
+\begin{figure*}[t]
+	\centering
+	\includegraphics[height=2cm]{pics/DrawableLoggingDeck.pdf}
+	\caption{UML graph for \lstinline|DrawableLoggingDeck|.}\label{fig:drawableloggingdeck}
+\end{figure*}
+If we try to keep the triangle inheritance, but apply dynamic dispatch, calling \lstinline|shuffleAndDraw| would trigger ambiguity. 
+In principle we want \lstinline|shuffleAndDraw| to invoke \lstinline|LoggingDeck.draw|, because they belong to the same branch, 
+nonetheless, choosing either static dispatch
+or dynamic dispatch cannot ensure both the triangle inheritance and code reuse. As far as we know, C++ does not have a solution
+to it. Therefore we need to find another algorithm for method resolution.\\
+
+\noindent\textbf{Solution in \name{}:} \name{} uses \textit{hierarchical dispatch} for method lookup. A qualified
+method invocation in \name{}, for instance, \lstinline|e.I::m()|, is read as
 ``finding the most specific method \lstinline|m| along the path
@@
 that, if the result of \dispatch{} is \lstinline|J.m()| for some \lstinline|J|, then such a \lstinline|J| must be a super type of \lstinline|e|'s dynamic type, and \lstinline|J| has a subtyping relation with \lstinline|I| (either \lstinline|J <: I| or \lstinline|J >: I|).
-Intuitively, the most specific \lstinline|m()| must be from branch \lstinline|I|, but it can be an overridden version after \lstinline|I| because of dynamic dispatch.
+Intuitively, the most specific \lstinline|m()| must be from branch \lstinline|I|, but it can be an updated version after \lstinline|I| because of dynamic dispatch.
 The formal definition will be introduced later.
+
 On the other hand, \lstinline|e.m()| where \lstinline|e| has static type \lstinline|I|, simply behaves the same as \lstinline|e.I::m()| in our model.
-It is just like the difference between implicit and explicit casts.
+Such a dispatch algorithm makes use of both the static type and the dynamic type of the receiver, so it is like a combination of static and dynamic dispatch.
+Intuitively, the static type specifies one branch to avoid ambiguity, and the dynamic type finds the latest version on that branch.
+It may still introduce ambiguity when there are multiple paths from the static type to the dynamic type, and those paths cause conflicts.
+\name{} disallows this kind of conflict to ensure unambiguity.
+That is to say, we do not allow two methods to override a same base method when they cause conflicts.
+This is natural, as they are just two versions of the same operation, hence it is no longer an ``unintentional'' conflict, but the diamond problem.
 
-Such a dispatch algorithm make uses of both the static type and the dynamic type of the receiver.
-Intuitively, the static type specifies one branch of the method to avoid ambiguity, and the dynamic type finds the latest version on that branch.
-It may still introduce ambiguity when there are multiple paths from the static type to the dynamic type, and those paths cause conflicts.
-To prevent this, we disallow this kind of conflict to ensure unambiguity.
-That is to say, we do not allow two methods to override a same base method when they cause conflicts.
-This is natural, as they are just two versions of the same operation, hence it is no longer an ``unintentional'' conflict in that way.
-
-With the old example, the code below meets our expectation:
+Back to the example, we can write \lstinline|"this.Deck::draw()"| inside the implementation of \lstinline|shuffleAndDraw|, and on \lstinline|d.shuffleAndDraw()| it automatically dispatches to \lstinline|LoggingDeck.draw()|.
+Furthermore, the following code in \name{}
+also behaves as expected:
 \vspace{3pt}\begin{lstlisting}
@@
   void draw() {...}
-  void shuffleAndDraw() {
-    this.Deck::shuffle();
-    this.Deck::draw();
-  }
+  void shuffleAndDraw() { shuffle(); draw(); }
   ...
@@
 \end{lstlisting}\vspace{3pt}
-It guarantees that \lstinline|shuffleAndDraw()| calls \lstinline|shuffle()| and \lstinline|draw()| from its own branch, so that the namesakes
-from other branches will not cause conflicts. Now \lstinline|d.shuffleAndDraw()| is no longer ambiguous.
-
-Actually in \MIM{}, we can still write ``\lstinline|shuffle();|'' and ``\lstinline|draw();|'',
-because the compiler is able to know that the receiver ``\lstinline|this|'' exactly has static type \lstinline|Deck|, hence hierarchical dispatch eliminates ambiguity.
+It is because the compiler is able to know that the receiver ``\lstinline|this|'' exactly has static type \lstinline|Deck|. Hence hierarchical dispatch eliminates ambiguity.
 

### 2017-06-17 Aplas17/sections/Formalization.tex
Overview up to 2.2
separate Aux defs out to a section

@@
 \caption{Typing and subtyping rules.}\label{fig:typingrules}
-\end{figure*}\bruno{do not use the notation ``-'' in T-METHOD, or
-  otherwise explain it.}
+\end{figure*}
 
 \subsection{Small-step Semantics and Congruence}
-
 Figure~\ref{fig:smallstep} defines the small-step semantic and
@@
 interface type in the definition of \mbody. This point is consistent
-with the last paragraph in Section~\ref{subsec:solutionmim}.
+with the last paragraph in Section~\ref{subsec:problem2}.
 
@@
 \end{comment}
-
-\subsection{Auxiliary Definitions}\label{subsec:auxdefs}
-
-The auxiliary definitions used in our formalization are presented in 
-Figure~\ref{fig:auxfunc}. To begin with, we
-introduce the basic functions: $\ext, \overrideSet$ and $\prune$. $\ext(I, J)$
-simply indicates that interface $I$ directly extends interface $J$. 
-$\overrideSet(I, J)$ returns a set of methods defined in $I$ that have ``$\kwoverride \; J$''
-in their signatures. Notice that $\overrideSet(I, I)$ is a special representative of
-the ``originally-defined'' method set from $I$. The $\prune$ function takes a set of
-types, and filters out those that have subtypes in the same set. Finally in the returned set,
-none of them has a subtyping to one another, since all super types have been removed.
-
-\begin{figure*}[t]
-	\begin{mathpar}
-	\inferrule* [left=]
-		{  \mostSpecific(m, I_d, I_s) = \{I\} \\
-			\mostSpecificOverride(m, I_d, I) = \{J\} \\
-			\kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_e}{m}{I_x}{x}{I}{e_0}\ldots\}}
-		{\mbody(m, I_d, I_s) = (J, \overline{I_x} \; \overline{x}, I_e \; e_0)}
-
-	\inferrule* [left=]
-	{ set1 = \; \{ K <: J \; $and$ \; K >: I \; | \; m \in \overrideSet(K, K) \} \\
-		set2 = \; \{ K >: J \; | \; m \in \overrideSet(K, K) \} }
-	{\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
-				$prune(set1)$ & if $set1$ is not empty \\ $prune(set2)$ & otherwise
-			\end{tabular}}\right.}
-
-	\inferrule* [left=]
-		{ set = \; \{ K <: J \; $and$ \; K >: I \; | \;
-			m \in \overrideSet(K, J)  \} }
-		{\mostSpecificOverride(m, I, J) = prune(set)}
-
-	prune(set) = \{I \in set \; | \; \nexists J \in set, J <: I, J \neq I \}
-
-	\inferrule* [left=]
-	{   \interface{I}{I}{M}
-		\\ J \in \overline{I} }
-	{\ext(I, J)}
-
-	\inferrule* [left=]
-	{   \kwinterface \; I \; \kwextends \; \overline{I} \; \{ I_e \; m(\overline{I_x} \; \overline{x}) \;
-		\kwoverride \; J \ldots \} }
-	{m \in \overrideSet(I, J)}
-	\end{mathpar}
-	\caption{Auxiliary functions.}\label{fig:auxfunc}
-\end{figure*}
-
-\begin{figure*}[t]
-	\centering
-	\vspace{-1ex}
-	\begin{tabular}{ccc}
-		\includegraphics[width=2cm]{pics/p1.pdf}\hspace{4pt} &
-		\includegraphics[width=2cm]{pics/p2.pdf}\hspace{4pt} &
-		\includegraphics[width=2cm]{pics/p3.pdf}\hspace{4pt} \\
-		(a) $\mbody(m,C,A) = (A,...)$\ \ \  & (b) $\mbody(m,C,A) = (C,...)$\ \ \  & (c) $\mbody(m,C,A) = (C,...)$
-	\end{tabular} \\
-   \begin{tabular}{cc}
-   	\includegraphics[height=3cm]{pics/p4.pdf}\hspace{4pt} &
-   	\includegraphics[height=3cm]{pics/p5.pdf}\hspace{4pt} \\ 
-   	(d) $\mbody(m,D,A) = \keyword{undefined}$\ \ \  & (e) $\mbody(m,D,A) = \keyword{undefined}$
-   \end{tabular}
-	\caption{Examples on $\mbody$. ``$\uparrow$'' stands for partial overrides.}\label{fig:examplesmbody}
-	%\saveSpaceFig
-\end{figure*}
-
-\subsubsection{$\mostSpecific$ and $\mostSpecificOverride$}
-
-$\mostSpecific$ is an auxiliary function that finds the most specific original implementations of a method.
-Let us consider $\mostSpecific(m, I, J)$, what it returns is a set of interfaces, each including its own $m$ as a most specific implementation.
-Such a set may contain several elements, but that implies ambiguity; what we expect is actually a singleton set.
-By the definition of $\mostSpecific$ shown in Figure~\ref{fig:auxfunc}, an interface belongs to the return set if and only if:
-\begin{itemize}
-	\item It has an original definition of $m$;
-	\item It is a supertype of $I$;
-	\item It is along path $J$, meaning that it is either a supertype or a subtype of $J$ (including $J$ itself);
-	\item It does not have a subtype in the same set, because we have used $prune$ to filter out all super types.
-\end{itemize}
-We could have put $set1$ and $set2$ together, but the current
-definition is clearer.
-
-The $\mostSpecific$ function only focuses on original method implementations, all the method updates are omitted during that time.
-On the other hand, another auxiliary function $\mostSpecificOverride(m, I, J)$ has the assumption that $J$ defines an original $m$, and this function tries to find the most specific implementations that partially overrides such an $m$.
-Just as $\mostSpecific$, $\mostSpecificOverride$ also returns the set of interfaces after pruning.
-An interface belongs to the return set if and only if:
-\begin{itemize}
-	\item It is between $I$ and $J$;
-	\item It defines a method update for $J.m$;
-	\item It does not have a subtype in the same set.
-\end{itemize}
-The algorithm for finding the most specific partial overrides is quite similar to that for most specific original method.
-A partial override is not allowed to work on another partial override, and one can hide another if their interfaces has subtyping relations.
-If they do not hide each other, the result implies ambiguity.
-
-\subsubsection{$\mbody$ and $\mtype$}
-
-$\mbody(m, I_d, I_s)$, as defined in Figure~\ref{fig:auxfunc}, denotes a method body lookup function.
-We use $I_d, I_s$, since $\mbody$ is usually invoked by a receiver of a method $m$, with its dynamic
-type $I_d$ and static type $I_s$. Such a function returns the most specific method implementation, more
-accurately, its parameters, returned expression and the types. It considers both originally defined methods and method updates, so $\mostSpecific$ and $\mostSpecificOverride$ are invoked.
-
-To calculate $\mbody(m, I_d, I_s)$:
-\begin{itemize}
-	\item First, it invokes $\mostSpecific(m, I_d, I_s)$ and returns a set.
-	\item If $\mostSpecific$ returns a singleton set $\{I\}$, then it is good, otherwise $\mbody$ is undefined in
-	this case.
-The set $\{I\}$ implies that we will use the $m$ from $I$ without ambiguity.
-Moreover, we have to invoke $\mostSpecificOverride(m, I_d, I)$, to check if there are updated versions of $m$ between $I_d$ and $I$.
-Again we forbid ambiguity, so the expected set after pruning is also a singleton set $\{J\}$.
-	\item Finally, we fetch the implementation of $m$ in interface $J$ and return its related information.
-\end{itemize}
-The definition of $\mtype$ used in typing rules simply relies on $\mbody$. In short,
-$$\mbody(m, I, I) = (J, \overline{I_x}\ \overline{x}, I_e\ e) \ \Longrightarrow\ \mtype(m, I) = \overline{I_x}\rightarrow I_e$$
-
-\begin{comment}
-$mbody(m, I)$ algorithm:
-\begin{itemize}
-	\item If m is defined in I directly, then return I.m()
-	\item Else, let $\overline{I'} = mdefined(fathers(I))$, all ancestors of $I$ that has directly defined $m()$.
-	\item $\overline{I''} = needed(\overline{I'})$, keep only interfaces that are needed, which are not super-interface of others.
-	\item If $\overline{I''}$ is unique, then return this unique one.
-Else if any two I1,I2 in $\overline{I''}$ share a parent in $\overline{I'}$, then diamond conflict is detected, report error.
-Else return multiple $m()$s.
-\end{itemize}
-\end{comment}
-
-\begin{comment}
-\subsubsection{\collectMethods}
-\[ \collectMethods(I) = \left( \bigcup_{I_i \in \overline{I}} \methods(I_i) \right) \bigcup \methods(I) \]
-\[ \methods(I) = \overline{M}, \text{where } IT(I) = \interface{I}{I}{M} \]
-\end{comment}
-
-\subsubsection{Examples}
-
-Examples for $\mbody$ are shown in Figure~\ref{fig:examplesmbody}.
-Note that we use \lstinline|m| to denote an original method, and ``\lstinline|m|$\uparrow$\lstinline|A|'' for a partial override on \lstinline|A|.
-For each small example, the result
-gives the interface to which $m$ is dispatched. (a) is a basic model for unintentional method conflicts; (b) and (c) demonstrate
-that hierarchical dispatch can find the most specific original method and partial override. More interesting are the two bad examples
-(d) and (e), they both fail on $\mbody$. (d) is the well-known diamond inheritance, which our model also forbids, and (e) is similar to
-(d) because the two partial overrides are working on the same operation. Both counter-examples imply that \lstinline|new D().A::m()| will
-lead to ambiguity, and in order for type soundness, both have to be denied by the type checker. This is guaranteed by the interface check
-\textsc{(T-Intf)} in Figure~\ref{fig:typingrules}.
 

### 2017-06-17 Aplas17/sections/Overview.tex
halfway Sec2.3

@@
 
+\bruno{Emphasizing hierarchical dispatch and triangle inheritance.}\haoyuan{Done}
 On the other hand, we also need dynamic dispatch as it is essential and widely used in object-oriented programming.
@@
 
-\subsection{Partial Overrides in \MIM	}\label{subsec:partialoverrides}
+\subsection{Problem 3: Overriding on Individual Branches}\label{subsec:partialoverrides}
 
-Method overriding is commonly supported by many OO languages as a kind of polymorphism.
-We have seen that \MIM{} is able to preserve several conflicted branches simultaneously and let them coexist.
-In that case, a traditional method overriding, like one in Java, will override all the inherited methods, and hence
-hide all those conflicted branches. Besides, \MIM{} also allows partial overrides to offer independent extensibility.
-A partial override will specify one of the branches, and only refine the method from that branch. It ensures that
-other branches are not affected.
+We have seen that hierarchical dispatch can dynamically find the latest implementation of a method from one path (or branch). But when
+several branches are merged by triangle inheritance, there is usually demand for updating them separately. For example, someone plans to
+reuse the other features of \lstinline|DrawableLoggingDeck|, but updates the \lstinline|draw| from \lstinline|Drawable| by setting the canvas
+invisible. Unfortunately in traditional models, the merged branches cannot be separately overridden any longer, since overriding
+will hide all branches and break coexistence. Modifying existing code is again unsatisfactory as it affects modularity.\\
 
-For example, we define an interface \lstinline|DrawableLoggingDeck2|, and in its definition we refine the \lstinline|draw()| from \lstinline|Drawable()| by setting
-the canvas invisible:
+\noindent\textbf{Solution in \name{}:} an additional feature of \name{} is \textit{hierarchical overriding}. It allows conflicting methods
+to be overridden on individual branches, and hence offers independent extensibility. The above example can be easily realized by:
 \vspace{3pt}\begin{lstlisting}
@@
 }
+
+// main program
+new DrawableLoggingDeck2().Drawable::draw()      // calling draw in DrawableLoggingDeck2
 \end{lstlisting}\vspace{3pt}
-Here the partial override specifies \lstinline|Drawable| to be refined.
-The use of it ensures that both branches of \lstinline|draw()| are preserved.
-At the same time, we should notice that the methods we present in previous examples are called ``original methods'', and they are actually created by ``total overrides'', rather than partial overrides.
-Some client code is shown below: \haoyuan{which words should we use instead of "total overrides"?}
-\vspace{3pt}\begin{lstlisting}
-DrawableLoggingDeck2 d2 = new DrawableLoggingDeck2();
-d2.Drawable::draw(); // calling draw() in DrawableLoggingDeck2
-d2.Deck::draw();       // calling draw() in LoggingDeck
-\end{lstlisting}\vspace{3pt}
+\haoyuan{TODO: introduce the concept of original methods.}
 

### 2017-06-18 Aplas17/sections/Introduction.tex
local

--- 2017-06-15 Aplas17/sections/Introduction.tex
@@
 A reason why programming languages have resisted to multiple
-inheritance in the past is that, as Cook~\cite{Cook1987} put it, 
+inheritance in the past is that, as Cook~\cite{Cook1987} puts it, 
 ``\emph{multiple inheritance is good but there is no good way to do it}''.

### 2017-06-18 Aplas17/sections/RelatedWork.tex

@@
 \subsection{Hierarchical Dispatch}
-As we have discussed before, the mix of static and dynamic dispatch is particularly useful under certain circumstances,
-yet there is little attention from related work. In the prototype-based language \self~\cite{Chambers1991}, inheritance is a basic feature.
+As we have discussed before, although the mix of static and dynamic dispatch is 
+particularly useful under certain circumstances, it has received little research attention. 
+In the prototype-based language \self{}~\cite{Chambers1991}, inheritance is a basic feature.
 It does not include classes but instead allow individual objects to inherit from (or delegate to) other objects. 
@@
 language supports multiple (object) inheritance in a clever way. It not only develops the new inheritance
-relation with \emph{prioritized parents}, but also adopts \emph{sender path tiebreaker rule} for method lookup, which is similar with our approach, using hierarchical information in method resolution, but in a prototype-based language setting.\haoyuan{Do they have updates?}
+relation with \emph{prioritized parents}, but also adopts \emph{sender path tiebreaker rule} for method lookup.
+It specifies that ``\emph{if two slots with the same name are defined in equal-priority parents of the receiver, but only 
+one of the parents is an ancestor or descendant of the object containing the method that is sending the message,
+then that parent's slot takes precedence over the over parent's slot}''. 
+Similar to our model, this sender path tiebreaker rule resolves ambiguities between unrelated abstractions. However,
+it is used in a prototype-based language setting and it does not support method hierarchical overriding as \MIM{} does.
 
 \subsection{Formalization Based on Featherweight Java}
-Featherweight Java (FJ)~\cite{Igarashi01FJ} is a minimal core calculus of Java language, proposed by Igarashi et. al\haoyuan{Need cite}. There are
-many models built on
-Featherweight Java, including FeatherTrait~\cite{Liquori08ftj}, Featherweight defenders~\cite{goetz12fdefenders}, Jx~\cite{Nystrom2004}, and so on.
+Featherweight Java (FJ)~\cite{Igarashi01FJ} is a minimal core calculus of Java language, 
+proposed by Igarashi et. al. There are many models built on Featherweight Java, 
+including FeatherTrait~\cite{Liquori08ftj}, Featherweight defenders~\cite{goetz12fdefenders}, Jx~\cite{Nystrom2004}, 
+Featherweight Scala~\cite{Cremet2006}, and so on.
 FJ provides the standard model of formalizing a Java-like object-oriented language, and 
@@
 static types as annotations along with various terms. As far as we
-know, this technique has not appeared in the literature before.
+know, this technique has not appeared in the literature before. The static type annotation is of vital 
+importance in our hierarchical dispatch algorithm.

### 2017-06-18 Aplas17/sections/Auxiliary.tex
fix Aux

--- 2017-05-05 paper/sections/Formalization.tex
@@
-\section{Formalization}
-
-In this section, we present a formalization of our MIM calculus, based on
-a minimal subset of Java 8 interfaces. The syntax, typing rules and small-step
-semantics are included below.
-
-\subsection{Syntax}
-Figure~\ref{fig:syntax} shows the syntax of MIM. The multiple inheritance feature
-of MIM has a basis on Java interfaces. To demonstrate how unintentional method conflicts
-are untangled in MIM, we present the calculus in a straightforward way, hence we only
-focus on a small subset of the interface model. For example, all the methods declared in an
-interface are default methods, that is to say, they always provide default implementations.
-From this point we can view that we are actually modelling a class model that supports multiple
-inheritance. Then it is straightforward to do object creation like ``\new I''. Fields and
-primitive types are not modelled as well.
-
-We use uppercase letters like $I, J, K$ to represent identifiers for interfaces. By multiple inheritance,
-an interface can have a set of super interfaces, where such a set can be empty. Inside an interface are a
-set of method declarations. Each method body holds a return statement. As seen in Figure~\ref{fig:syntax},
-we have introduced the \kwoverride keyword to override an old implementation of the method. If the interface
-that it overrides is exactly the enclosing interface, then such a method is seen as ``originally defined''.
-Again for simplicity, overloading is not modelled for methods, which implies we can uniquely identify a method
-by its name.
-
-An expression can be a variable, a method invocation, an object creation, furthermore, a path-invocation like
-``$e.I::m(\overline{e})$'', meaning that the dynamically binded implementation for method $m$ should be along
-the path $I$. Another case is the super-invocation, enabling a method to access an old implementation from the
-specified super type. Hence a super-invocation can only be used inside an interface definition. Finally an expression
-can also be a value ``$<I> \new J$''. It is exactly an object instance of $J$ with annotated static type $I$.
-Note that values are only intended for the small-step semantics of MIM, hence they are not supposed to appear in the source program.
-
-\begin{figure*}[htbp]
-\begin{displaymath}
-\begin{array}{l}
-\begin{array}{llrl}
-\text{Interfaces}   & IL & \Coloneqq & \interface{I}{I}{M} \\
-\text{Methods}      & M  & \Coloneqq & \method{I}{m}{I_x}{x}{J}{e} \\
-\text{Expressions}  & e  & \Coloneqq & x \mid
-e.m(\overline{e}) \mid
-\new{I} \mid
-e.I::m(\overline{e}) \mid
-\kwsuper.I::m(e) \; \red{\mid} \; \red{v^*} \\
-\text{Context}      & \Gamma & \Coloneqq & \overline{x:I} \\
-\text{\red{Values}}       & v & \Coloneqq & <I>\new{J} \\
-\\
-\text{Interface names} & I, J, K & & \\
-\text{Method names} & m & & \\
-\text{Variable names} & x & &
-\end{array}
-\end{array}
-\end{displaymath}
-\caption{Syntax. \red{*: only intended for semantic rules.}}\label{fig:syntax}
-\end{figure*}
-
-\subsection{Subtyping and Typing Rules}
-The subtyping of MIM consists of only a few rules shown in Figure ?.
-In short, subtyping relations are built from the inheritance in interface
-declarations. They hold both reflexivity and transitivity.
-
-Details of type-checking rules are displayed in Figure ?, including expression
-typing, well-formedness of methods and interfaces. As a convention, an environment
-$\Gamma$ is maintained to store the types of variables, together with ``this'' type, namely
-the enclosing type. The three rules for method invocation, (T-INVK), (T-PATHINVK) and (T-SUPERINVK)
-are very similar, in the sense that they all check the type of the specific method, by using
-an auxiliary function \mtype. \mtype is the function for looking up method types, which we will
-illustrate later. After the method type is obtained, they all check that arguments and the receiver
-have compatible types. Additionally, (T-PATHINVK) requires the receiver to be the subtype of the specified
-path type, and (T-SUPERINVK) checks if the enclosing type directly extends the specified super type.
-
-The method typing rule (T-METHOD) is more interesting, since the method can either be an original implementation or a update.
-Besides static type-checking for the return expression,
-we further use the helper function $\mostSpecific$ to ensure that the method update is legal. The formal definition is available in Section ?
-By that we define the legality of method updating: the updated method must be an original method (not another method update), and method updating cannot cross over method overriding (a method overriding cannot appear between the method update and the updated original method in inheritance hierarchy).
-
-Finally, (T-INTF) defines interface type-checking in a straightforward way.
-
-\begin{figure*}[htbp]
-\begin{mathpar}
-	\framebox{$ I <: J $} \hspace{.5in} \subid \\
-	\subtrans \hspace{.5in} \subextends
-\end{mathpar}
-\caption{Subtyping.}\label{fig:subtyping}
-\end{figure*}
-
-\begin{figure*}[htbp]
-\begin{mathpar}
-	\framebox{$ \judgeewf \Gamma {e:I} $} \hspace{.5in}
-	\tvar \\
-	\tinvk \\
-	\tpathinvk \\
-	\tsuperinvk \\
-	\tnew \\
-	\tmethod \\
-	\tintf
-\end{mathpar}
-\caption{Typing rules.}\label{fig:typingrules}
-\end{figure*}
-
-\subsection{Small-step Semantics and Congruence}
-Figure ? and Figure ? define small-step semantic rules and congruence rules,
-respectively. When evaluating an expression, they are invoked recursively and
-alternately to produce a single value in the end. The small-step semantics (S-INVK), (S-PATHINVK) and (S-SUPERINVK) behave similarly, each corresponds to
-one kind of method invocation.
-They all invoke \mbody for method body lookup.
-Generally, one can understand $\mbody(m, I, J)$ in a way that it finds the most specific body of method $m$, when the receiver has dynamic type $I$ and static type $J$.
-The three rules require that the receiver and the arguments have been evaluated into values, before substitution is applied.
-
-\begin{figure*}[htbp]
-\begin{mathpar}
-	\sinvk \\
-	\spathinvk \\
-	\ssuperinvk
-\end{mathpar}
-\caption{Small-step semantics.}\label{fig:smallstep}
-\end{figure*}
-
-\begin{figure*}[htbp]
-\begin{mathpar}
-	\creceiver \hspace{.5in}
-	\red{\cpathreceiver} \\
-	\red{\cargs} \\
-	\red{\cpathargs} \\
-	\red{\csuperargs} \\
-	\cstatictype \\
-	\cfreduce \\
-	\cannoreduce
-\end{mathpar}
-\caption{Congruence.}\label{fig:congruence}
-\end{figure*}
-
-\subsection{Auxilary Definitions}
-
-To make our formalization concise and expressive, we have defined a list of
-auxiliary functions, collected by Figure~\ref{fig:auxfunc}. To begin with, we
-introduce the basic functions: $\ext, \updateSet$ and $\prune$. $\ext(I, J)$
-simply indicates that interface $I$ directly extends interface $J$. Corresponding
-to this is a more general case $I <: J$, meaning that $I$ is a subtype of $J$.
-$\updateSet(I, J)$ returns a set of methods defined in $I$ that have ``$\kwoverride \; J$''
-in their signatures. Notice that $\updateSet(I, I)$ is a special representative of
+\section{Auxiliary Definitions}\label{subsec:auxdefs}
+In this section we present the auxiliary definitions used in our formalization in 
+Figure~\ref{fig:auxfunc}. To begin with, we
+introduce the basic functions: $\ext, \overrideSet$ and $\prune$. $\ext(I, J)$
+simply indicates that interface $I$ directly extends interface $J$. 
+$\overrideSet(I, J)$ returns a set of methods defined in $I$ that have ``$\kwoverride \; J$''
+in their signatures. Notice that $\overrideSet(I, I)$ is a special representative of
 the ``originally-defined'' method set from $I$. The $\prune$ function takes a set of
@@
 
-\begin{figure*}[htbp]
+\begin{figure*}[t]
     \begin{mathpar}
@@
         {  \mostSpecific(m, I_d, I_s) = \{I\} \\
-			\mostSpecific_2(m, I_d, I) = \{J\} \\
-			\kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_E}{m}{I_X}{x}{I}{e_0}\ldots\}}
-		{\mbody(m, I_d, I_s) = (\overline{I_X} \; \overline{x}, I_E \; e_0)}
+            \mostSpecificOverride(m, I_d, I) = \{J\} \\
+            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_e}{m}{I_x}{x}{I}{e_0}\ldots\}}
+        {\mbody(m, I_d, I_s) = (J, \overline{I_x} \; \overline{x}, I_e \; e_0)}
 
     \inferrule* [left=]
-	{ set1 = \; \{ K <: J \; $and$ \; K >: I \; | \; m \in \updateSet(K, K) \} \\
-		set2 = \; \{ K >: J \; | \; m \in \updateSet(K, K) \} }
+    { set1 = \; \{ K <: J \; $and$ \; K >: I \; | \; m \in \overrideSet(K, K) \} \\
+        set2 = \; \{ K >: J \; | \; m \in \overrideSet(K, K) \} }
     {\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
@@
         { set = \; \{ K <: J \; $and$ \; K >: I \; | \;
-			m \in \updateSet(K, J)  \} }
-		{\mostSpecific_2(m, I, J) = prune(set)}
+            m \in \overrideSet(K, J)  \} }
+        {\mostSpecificOverride(m, I, J) = prune(set)}
 
@@
     \inferrule* [left=]
-	{   \kwinterface \; I \; \kwextends \; \overline{I} \; \{ I_E \; m(\overline{I_X} \; \overline{x}) \;
+    {   \kwinterface \; I \; \kwextends \; \overline{I} \; \{ I_e \; m(\overline{I_x} \; \overline{x}) \;
         \kwoverride \; J \ldots \} }
-	{m \in \updateSet(I, J)}
+    {m \in \overrideSet(I, J)}
     \end{mathpar}
@@
 
-\subsubsection{$\mostSpecific$ and $\mostSpecific_2$}
+\begin{figure*}[t]
+    \centering
+    \vspace{-1ex}
+    \begin{tabular}{ccc}
+        \includegraphics[width=2cm]{pics/p1.pdf}\hspace{4pt} &
+        \includegraphics[width=2cm]{pics/p2.pdf}\hspace{4pt} &
+        \includegraphics[width=2cm]{pics/p3.pdf}\hspace{4pt} \\
+        (a) $\mbody(m,C,A) = (A,...)$\ \ \  & (b) $\mbody(m,C,A) = (C,...)$\ \ \  & (c) $\mbody(m,C,A) = (C,...)$
+    \end{tabular} \\
+   \begin{tabular}{cc}
+    \includegraphics[height=3cm]{pics/p4.pdf}\hspace{4pt} &
+    \includegraphics[height=3cm]{pics/p5.pdf}\hspace{4pt} \\ 
+    (d) $\mbody(m,D,A) = \keyword{undefined}$\ \ \  & (e) $\mbody(m,D,A) = \keyword{undefined}$
+   \end{tabular}
+    \caption{Examples on $\mbody$. ``$\uparrow$'' stands for partial overrides.}\label{fig:examplesmbody}
+    %\saveSpaceFig
+\end{figure*}
+
+\subsection{$\mostSpecific$ and $\mostSpecificOverride$}
 
@@
     \item It is along path $J$, meaning that it is either a supertype or a subtype of $J$ (including $J$ itself);
-	\item It does not have a subtype in the same set, because we have used $prune$ to filter out all super types, as the most specific one is always in the sub-most type.
+    \item It does not have a subtype in the same set, because we have used $prune$ to filter out all super types.
 \end{itemize}
-We could have put $set1$ and $set2$ together, but the current definition leads a clearer illustration.
+We could have put $set1$ and $set2$ together, but the current
+definition is clearer.
 
 The $\mostSpecific$ function only focuses on original method implementations, all the method updates are omitted during that time.
-On the other hand, another auxiliary function $\mostSpecific_2(m, I, J)$ has the assumption that $J$ defines an original $m$, and this function tries to find the most specific implementations that update such an $m$.
-Just as $\mostSpecific$, $\mostSpecific_2$ also returns the set of interfaces after pruning.
+On the other hand, another auxiliary function $\mostSpecificOverride(m, I, J)$ has the assumption that $J$ defines an original $m$, and this function tries to find the most specific implementations that partially overrides such an $m$.
+Just as $\mostSpecific$, $\mostSpecificOverride$ also returns the set of interfaces after pruning.
 An interface belongs to the return set if and only if:
@@
 \end{itemize}
-The algorithm for finding the most specific method update is quite similar to that for most specific original method.
-A method update is not allowed to work on another method update, and one can hide another if their interfaces has subtyping relations.
+The algorithm for finding the most specific partial overrides is quite similar to that for most specific original method.
+A partial override is not allowed to work on another partial override, and one can hide another if their interfaces has subtyping relations.
 If they do not hide each other, the result implies ambiguity.
 
-\subsubsection{$\mbody$ and $\mtype$}
+\subsection{$\mbody$ and $\mtype$}
 
@@
 The set $\{I\}$ implies that we will use the $m$ from $I$ without ambiguity.
-But moreover, we have to invoke $\mostSpecific_2(m, I_d, I)$, to check if there are updated versions of $m$ between $I_d$ and $I$.
+Moreover, we have to invoke $\mostSpecificOverride(m, I_d, I)$, to check if there are updated versions of $m$ between $I_d$ and $I$.
 Again we forbid ambiguity, so the expected set after pruning is also a singleton set $\{J\}$.
@@
 \end{itemize}
-The definition of $\mtype$ simply relies on $\mbody$. In short,
-$$\mbody(m, I, I) = (\overline{I_x}\ \overline{x}, I_E\ e) \ \Longrightarrow\ \mtype(m, I) = \overline{I_x}\rightarrow I_E$$
+The definition of $\mtype$ used in typing rules simply relies on $\mbody$. In short,
+$$\mbody(m, I, I) = (J, \overline{I_x}\ \overline{x}, I_e\ e) \ \Longrightarrow\ \mtype(m, I) = \overline{I_x}\rightarrow I_e$$
 
@@
 
-\begin{itemize}
-	\item Syntax + typing rules + Semantics + Auxiliary definitions
-	\item Implementation: a simple type checker + interpreter in Scala
-\end{itemize}
+\subsection{Examples}
 
-\subsubsection{A Non-Trivial Example}
-
-\[
-\begin{array}{l}
-\kwinterface \; A \; \kwextends \; \{ \\
-\; \; \; \; A \; m() \; \kwoverride \; A \; \{\kwreturn \; \new A;\} \\
-\} \\
-\\
-\kwinterface \; B \; \kwextends \; A \; \{ \\
-\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new B;\} \\
-\} \\
-\\
-\kwinterface \; C \; \kwextends \; A \; \{ \\
-\; \; \; \; A \; m() \; \kwoverride \; C \; \{\kwreturn \; \new C;\} \\
-\} \\
-\\
-\kwinterface \; D \; \kwextends \; B, \; C \; \{ \\
-\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new D;\} \\
-\} \\
-\\
-\kwinterface \; E \; \kwextends \; B \; \{ \\
-\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new E;\} \\
-\} \\
-\\
-\kwinterface \; F \; \kwextends \; D, \; E \; \{ \\
-\; \; \; \; A \; m() \; \kwoverride \; B \; \{\kwreturn \; \new F;\} \\
-\; \; \; \; A \; n(B \; b) \; \kwoverride \; F \; \{\kwreturn \; b.m();\} \\
-\} \\
-\\
-\new F.n(\new F)
-\end{array}
-\]
-
-~\red{Unfortunately I think this example shows that it is hard to reuse
-	$D.m$ on path $B$ and $E.m$ on path $B$ in $F$?}
-
-\red{We can use the $\kwsuper$ keyword to access the originally defined methods
-	in super types, but we cannot access the old updating methods.}
-
-\red{Just like $\kwsuper.I::m()$ is equivalent to $\new I.m()$, maybe we can add
-a degree of freedom to $\kwsuper$, for example, $\kwsuper.D::B::m()$ is equivalent to
-$\new D.B::m()$, so we can use $\kwsuper.D::B::m()$ and $\kwsuper.E::B::m()$ inside interface $F$ for code reuse?}
-
-Interfaces $A,B,C,D,E,F$ OK in type checking.
-
-To type-check $\new F.n(\new F)$:
-\begin{itemize}
-	\item By (T-INVK), we need to calculate $\mtype(n, F)$.
-	\item $\mtype(n, F) = B \to A$. And $\new F : B$.
-	\item $\new F.n(\new F) : A$.
-\end{itemize}
-
-~
-
-To compute \red{$\new F.n(\new F)$}:
-\begin{itemize}
-	\item By (C-RECEIVER), we compute \red{$\new F$}:
-		\begin{itemize}
-			\item By (C-STATICTYPE): \red{$<F> \new F$}.
-		\end{itemize}
-	\item By (C-ARGS), we compute \red{$\new F$}:
-		\begin{itemize}
-			\item By (C-STATICTYPE): \red{$<F> \new F$}.
-		\end{itemize}
-	\item Now we get \red{$(<F> \new F).n(<F> \new F)$}. By (S-INVK):
-		\begin{itemize}
-			\item Compute $\mbody(n, F, F) = \red{(B \; b, A \; b.m())}$.
-			\item Replace \red{$b$} with \red{$<B> \new F$} in \red{$b.m()$}.
-			\item Replace \red{$\kwthis$} with \red{$<F> \new F$} in \red{$b.m()$}.
-		\end{itemize}
-	\item Finally we get \red{$<A>((<B> \new F).m())$}.
-	\item By (C-FREDUCE), we first compute \red{$(<B> \new F).m()$}:
-		\begin{itemize}
-			\item By (S-INVK), we compute \red{$\mbody(m, F, B)$}.
-			\item In $\mbody$, we invoke \red{$\mostSpecific(m, F, B)$}.
-			\item In $\mostSpecific$, \red{$set = \{B\}$, $\prune(set) = \{B\}$}.
-			\item Back to $\mbody$, we invoke \red{$\mostSpecific_3(m, F, B)$}.
-			\item In $\mostSpecific_3$, \red{$set = \{B,D,E,F\}$, $\prune(set) = \{F\}$}.
-			\item Back to $\mbody$, we check \red{$F.m$} and return \red{$(-,A \; (\new F))$}.
-			\item Back to (S-INVK).
-			\item Replace \red{$\kwthis$} with \red{$<B> \new F$} in \red{$\new F$}.
-			\item Finally we get \red{$<A> \new F$}.
-		\end{itemize}
-	\item Now we have \red{$<A>(<A> \new F)$}.
-	\item By (C-ANNOREDUCE): \red{$<A> \new F$}.
-\end{itemize}
-
-\red{TODO: class encapsulation problem: interface A: m; interface B: m update A; interface C: m update B.}
+Examples for $\mbody$ are shown in Figure~\ref{fig:examplesmbody}.
+Note that we use \lstinline|m| to denote an original method, and ``\lstinline|m|$\uparrow$\lstinline|A|'' for a partial override on \lstinline|A|.
+For each small example, the result
+gives the interface to which $m$ is dispatched. (a) is a basic model for unintentional method conflicts; (b) and (c) demonstrate
+that hierarchical dispatch can find the most specific original method and partial override. More interesting are the two bad examples
+(d) and (e), they both fail on $\mbody$. (d) is the well-known diamond inheritance, which our model also forbids, and (e) is similar to
+(d) because the two partial overrides are working on the same operation. Both counter-examples imply that \lstinline|new D().A::m()| will
+lead to ambiguity, and in order for type soundness, both have to be denied by the type checker. This is guaranteed by the interface check
+\textsc{(T-Intf)} in Figure~\ref{fig:typingrules}.

### 2017-06-18 Aplas17/sections/Auxiliary.tex
Done overview and formalization.

@@
    \end{tabular}
-    \caption{Examples on $\mbody$. ``$\uparrow$'' stands for partial overrides.}\label{fig:examplesmbody}
+    \caption{Examples on $\mbody$. ``$\uparrow$'' stands for hierarchical overriding.}\label{fig:examplesmbody}
     %\saveSpaceFig
@@
 
-The $\mostSpecific$ function only focuses on original method implementations, all the method updates are omitted during that time.
-On the other hand, another auxiliary function $\mostSpecificOverride(m, I, J)$ has the assumption that $J$ defines an original $m$, and this function tries to find the most specific implementations that partially overrides such an $m$.
+The $\mostSpecific$ function only focuses on original method implementations, all the hierarchical overriding methods are omitted during that time.
+On the other hand, another auxiliary function $\mostSpecificOverride(m, I, J)$ has the assumption that $J$ defines an original $m$, and this function tries to find the most specific implementations that hierarchically overrides such an $m$.
 Just as $\mostSpecific$, $\mostSpecificOverride$ also returns the set of interfaces after pruning.
@@
     \item It is between $I$ and $J$;
-    \item It defines a method update for $J.m$;
+    \item It hierarchically overrides $J.m$;
     \item It does not have a subtype in the same set.
 \end{itemize}
-The algorithm for finding the most specific partial overrides is quite similar to that for most specific original method.
-A partial override is not allowed to work on another partial override, and one can hide another if their interfaces has subtyping relations.
+The algorithm for finding the most specific hierarchical overriding method is quite similar to that for most specific original method.
+A hierarchical overriding is not allowed to work on another hierarchical overriding, and one can hide another if their interfaces has subtyping relations.
 If they do not hide each other, the result implies ambiguity.
@@
 type $I_d$ and static type $I_s$. Such a function returns the most specific method implementation, more
-accurately, its parameters, returned expression and the types. It considers both originally defined methods and method updates, so $\mostSpecific$ and $\mostSpecificOverride$ are invoked.
+accurately, its parameters, returned expression and the types.
+It considers both originally defined methods and hierarchical overriding methods, so $\mostSpecific$ and $\mostSpecificOverride$ are invoked.
 
@@
 Examples for $\mbody$ are shown in Figure~\ref{fig:examplesmbody}.
-Note that we use \lstinline|m| to denote an original method, and ``\lstinline|m|$\uparrow$\lstinline|A|'' for a partial override on \lstinline|A|.
+Note that we use \lstinline|m| to denote an original method, and ``\lstinline|m|$\uparrow$\lstinline|A|'' for hierarchical overriding on \lstinline|A|.
 For each small example, the result
 gives the interface to which $m$ is dispatched. (a) is a basic model for unintentional method conflicts; (b) and (c) demonstrate
-that hierarchical dispatch can find the most specific original method and partial override. More interesting are the two bad examples
+that hierarchical dispatch can find the most specific original method and hierarchical overriding method. More interesting are the two bad examples
 (d) and (e), they both fail on $\mbody$. (d) is the well-known diamond inheritance, which our model also forbids, and (e) is similar to
-(d) because the two partial overrides are working on the same operation. Both counter-examples imply that \lstinline|new D().A::m()| will
+(d) because the two hierarchical overriding methods are working on the same operation. Both counter-examples imply that \lstinline|new D().A::m()| will
 lead to ambiguity, and in order for type soundness, both have to be denied by the type checker. This is guaranteed by the interface check

### 2017-06-18 Aplas17/sections/Formalization.tex
proof fix
Done overview and formalization.

@@
 
-\bruno{There is quite a bit of teminology that we need to be careful
-  to introduce earlier in the paper. For example: ``original
-  method''. We are also still using terminology such as ``method
-  update'', which I think is now outdated.
-We need to read the paper carefully enough to spot
-  possible uses of terminology which may make sense to us, but 
-we have not introduced properly.}
+\bruno{There is quite a bit of teminology that we need to be careful.}\haoyuan{Done}
 
@@
 interface, then such a method is seen as ``originally defined''; otherwise
-it is a partial override.
+it is hierarchical overriding.
 For simplicity, overloading is not modelled for methods, which
@@
 of $J$ with an annotated static type $I$.
+
+For simplicity \name{} does not formalize statements like assignments and so on, because they are orthogonal features.
+A program consists of a list of interface declarations, plus a single expression.
 
@@
 
-The method typing rule \textsc{(T-Method)} is more interesting, since the method can either be an original implementation or a partial override.
+The method typing rule \textsc{(T-Method)} is more interesting, since the method can either be an original implementation or hierarchical overriding.
 Besides type-checking the return expression,
-we further use the helper function $\mostSpecific$ to ensure that the method update is legal. The formal definition is again in Section~\ref{subsec:auxdefs}.
-By the equation ``$\mostSpecific(m, I, J) = \{J\}$'' we define the legality of method overrides as mentioned in Section~\ref{subsec:partialoverrides}, namely if it is a partial override, it should not overlap a total override, otherwise
-the total override would be returned instead of $J$.
+we further use the helper function $\mostSpecific$, again formally defined in Section~\ref{subsec:auxdefs}.
+By the equation ``$\mostSpecific(m, I, J) = \{J\}$'' we define the legality of method overrides as mentioned in Section~\ref{subsec:partialoverrides}, namely if it is hierarchical overriding, it should not step over original methods, otherwise
+their enclosing types would be returned instead of $J$.
 

### 2017-06-18 Aplas17/sections/Overview.tex
Done overview and formalization.

@@
 \section{A Running Example: DrawableDeck}~\label{sec:overview}
-This section illustrates the features of our \MIM{} model for
+This section illustrates the features of our model for
 resolving unintentional method conflicts. As mentioned before, such a
@@
 \end{itemize}
-Furthermore for simplicity, our formalization does not model state at
+Furthermore for simplicity, our examples and formalization does not deal with state at
 this stage. %%, but that should not block our discussions below.
@@
 
-\noindent\textbf{Solution in \name{}:} below is the pseudo-code that shows the triangle
-inheritance supported by \name{}.
+\noindent\textbf{Our solution:} below is our code that shows the triangle
+inheritance.
 We can define \lstinline|DrawableDeck| by inheriting \lstinline|Drawable| and \lstinline|Deck| together while
-type safety is ensured. It is slightly different from our prototype as we do not model \lstinline|void|, though one can
-define a \lstinline|Void| interface for it.
+type safety is ensured. Again it is slightly different from our prototype as we do not model \lstinline|void| or statements;
+the code is just for illustration.
 \vspace{3pt}\begin{lstlisting}
@@
 // main program
-new DrawableDeck().Drawable::draw()      // calling draw in Drawable
-new Foo().func(new DrawableDeck())       // calling draw in Deck
+DrawableDeck d = new DrawableDeck();
+new DrawableDeck().Drawable::draw();      // calling draw in Drawable
+new Foo().func(new DrawableDeck());       // calling draw in Deck
 \end{lstlisting}\vspace{3pt}
@@
 
+// main program
 DrawableLoggingDeck d = new DrawableLoggingDeck();
@@
 
-\noindent\textbf{Solution in \name{}:} \name{} uses \textit{hierarchical dispatch} for method lookup. A qualified
-method invocation in \name{}, for instance, \lstinline|e.I::m()|, is read as
+\noindent\textbf{Our solution:} we propose \textit{hierarchical dispatch} for method lookup. A qualified
+method invocation in our model, for instance, \lstinline|e.I::m()|, is read as
 ``finding the most specific method \lstinline|m| along the path
@@
 It may still introduce ambiguity when there are multiple paths from the static type to the dynamic type, and those paths cause conflicts.
-\name{} disallows this kind of conflict to ensure unambiguity.
+We disallow this kind of conflict to ensure unambiguity.
 That is to say, we do not allow two methods to override a same base method when they cause conflicts.
@@
 Back to the example, we can write \lstinline|"this.Deck::draw()"| inside the implementation of \lstinline|shuffleAndDraw|, and on \lstinline|d.shuffleAndDraw()| it automatically dispatches to \lstinline|LoggingDeck.draw()|.
-Furthermore, the following code in \name{}
+Furthermore, the following code
 also behaves as expected:
@@
 
-\noindent\textbf{Solution in \name{}:} an additional feature of \name{} is \textit{hierarchical overriding}. It allows conflicting methods
+\noindent\textbf{Our solution:} an additional feature of our model is \textit{hierarchical overriding}. It allows conflicting methods
 to be overridden on individual branches, and hence offers independent extensibility. The above example can be easily realized by:
@@
 // main program
-new DrawableLoggingDeck2().Drawable::draw()      // calling draw in DrawableLoggingDeck2
+DrawableLoggingDeck2 d = new DrawableLoggingDeck2();
+d.Drawable::draw()      // calling draw in DrawableLoggingDeck2
 \end{lstlisting}\vspace{3pt}
-\haoyuan{TODO: introduce the concept of original methods.}
+\textbf{Terminology} The \lstinline|draw| methods we saw before this example are called ``original methods'' in this paper, because they are originally defined in its interface.
+In contrast, \lstinline|DrawableLoggingDeck2| defines a ``hierarchical overriding'' method.
+The difference is that traditional overriding overrides all branches by defining another original method, whereas hierarchical overriding only refines one branch.
 
-In \MIM{}, hierarchical dispatch first finds the most specific original method (branch), then it finds the most specific partial override on that branch.
-A quick counter-example is when there are two partial overrides on \lstinline|Drawable| in \lstinline|DrawableLoggingDeck2|, it leads to ambiguity.
+In our model, triangle inheritance allows several original methods (branches) to coexist, and hierarchical dispatch first finds the most specific original method (branch), then it finds the most specific hierarchical overriding on that branch.
+A quick counter-example is when there are two hierarchical overriding methods on \lstinline|Drawable| in \lstinline|DrawableLoggingDeck2|, it leads to ambiguity.
 The compiler is supposed to forbid that during compile time.
 
-Two rules for partial overrides in \MIM: updates can only refine \textbf{original} methods, and they cannot overlap total overrides.
-For instance, writing \lstinline|"void draw()| \lstinline|override Deck {...}"| is disallowed in \lstinline|DrawableLoggingDeck2|, because existing two branches are \lstinline|Drawable.draw()| and \lstinline|LoggingDeck.draw()|, and \lstinline|Deck.draw()| is already covered.
+Two rules for hierarchical overriding: it can only refine \textbf{original} methods, and cannot jump over original methods with the same signature.
+For instance, writing \lstinline|"void draw()| \lstinline|override Deck {...}"| is disallowed in \lstinline|DrawableLoggingDeck2|, because existing two branches are \lstinline|Drawable.draw| and \lstinline|LoggingDeck.draw|, while \lstinline|Deck.draw| is already covered.
 It does not really make sense to refine an old branch.
 
-Similar to many OO languages, \MIM{} also allows \textit{super method invocation} in a method body.
+Similar to many OO languages, the model also allows \textit{super method invocation} in a method body.
 The invocation \lstinline|super.T::m()| will ignore all the subtypes of \lstinline|T|, and only look at \lstinline|T| together with its super interfaces.
+It should behave the same as \lstinline|new T().m()| in principle.

### 2017-06-18 Aplas17/sections/Introduction.tex
Terminology.

--- 2017-06-17 Aplas17/sections/Introduction.tex
@@
 error happens due to conflicts. However, unlike the diamond problem,
-the conflicted methods have very different meanings and do not share a
+the conflicting methods have very different meanings and do not share a
 common parent. We call such a case ``\textit{triangle inheritance}''.
@@
 are mechanisms available in C++ and C\# that allow for two
-unintentionally conflicted methods to coexist in a class. Among them
+unintentionally conflicting methods to coexist in a class. Among them
 C++ is a representative that accepts the triangle inheritance and

### 2017-06-18 Aplas17/sections/Overview.tex
Terminology.

@@
   they can break the subtyping. Moreover, in
-  contrast with exclusion, renaming can indeed preserve both conflicted
+  contrast with exclusion, renaming can indeed preserve both conflicting
   behaviours, however, it is cumbersome in practice, as introducing new

### 2017-06-18 Aplas17/sections/RelatedWork.tex
Finish one round of review.

@@
 \subsection{Mainstream Multiple Inheritance Models}
-Multiple inheritance is an useful feature in object-oriented
+Multiple inheritance is a useful feature in object-oriented
 programming, although it is difficult to model and can 
@@
   had a presentation with alot of related work on multiple
-  inheritance. Many of those seem to be missing here}
+  inheritance. Many of those seem to be missing here}\yanlin{Done}
 
@@
   something that goes wrong?}
-Furthermore, C++ does not support partial overrides compared to our
+Furthermore, C++ does not support hierarchical overriding compared to our
 model.
@@
 (1) default implementations are not allowed in \csharp{} interfaces; 
-(2) there is only one level of partial overrides (implementations).
+(2) there is only one level of hierarchical overriding to refine conflicting methods individually.
 

### 2017-06-18 Aplas17/sections/Overview.tex
Quick fix.

@@
 \vspace{3pt}\begin{lstlisting}
-interface LoggingDeck {
+interface LoggingDeck extends Deck {
   void draw() { // overriding

### 2017-06-18 Aplas17/paper.tex
Add text for implementaion.
separate Aux defs out to a section
fix Aux
remove example
grammar check Sec1,Sec2

@@
 
-\newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
-\newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
-\newcommand\marco[1]{\authornote{marco}{blue}{#1}}
-\newcommand\haoyuan[1]{\authornote{haoyuan}{cyan}{#1}}
+% \newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
+% \newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
+% \newcommand\marco[1]{\authornote{marco}{blue}{#1}}
+% \newcommand\haoyuan[1]{\authornote{haoyuan}{orange}{#1}}
 
-% \newcommand\bruno[1]{}
-% \newcommand\yanlin[1]{}
-% \newcommand\marco[1]{}
-% \newcommand\haoyuan[1]{}
+\newcommand\bruno[1]{}
+\newcommand\yanlin[1]{}
+\newcommand\marco[1]{}
+\newcommand\haoyuan[1]{}
 
@@
 Multiple inheritance is a valuable feature for Object-Oriented
-Programming. However it is also tricky to get right, as illustrated by
+Programming. However, it is also tricky to get right, as illustrated by
 the extensive literature on the topic. One of the most promising 
-approaches to multiple inheritance are \emph{traits}. Traits offer a
+approaches to multiple inheritance is the \emph{trait} model. Traits offer a
 restricted model of multiple inheritance that is easy to reason and 
@@
 conflicts that arise from method implementations sharing a common 
-ancestor. However the mechanisms of traits are inadequate to deal 
+ancestor. However, the mechanisms of traits are inadequate to deal 
 with \emph{unintentional method conflicts}: conflicts which 
@@
 that deals with unintentional
-method conflicts. In our new model conflicting methods arising
-from unrelated methods can coexist in the same component. Moreover they
+method conflicts. In our new model, conflicting methods arising
+from unrelated methods can coexist in the same component. Moreover, they
 can be \emph{independently overridden}. What ensures unambiguity 
-is the use of information about the class hierarchy. In turn
+is the use of information about the class hierarchy. In turn, 
 hierarchical information is also employed in method dispatching, which 
@@
 \input{sections/Formalization.tex}
+\input{sections/Auxiliary.tex}
 % \input{sections/TypeSafety.tex}

### 2017-06-18 Aplas17/sections/Introduction.tex
grammar check Sec1,Sec2

@@
 inheritance, which is less expressive and flexible than multiple
-inheritance. Nevertheless different flavours of multiple inheritance
+inheritance. Nevertheless, different flavours of multiple inheritance
 have been adopted in some popular OOP languages. C++ has had 
@@
 
-In contrast with the diamond inheritance, a second case of ambiguity
+In contrast with the diamond inheritance, the second case of ambiguity
 is \textit{unintentional method conflicts}~\cite{scharli03traits}. That is conflicting 
@@
 signatures).
-A simple example of this situation are two \lstinline{draw} methods that
+A simple example of this situation is two \lstinline{draw} methods that
 are inherited from a deck of cards and a drawable widget. 
-In such context the two \lstinline{draw} methods have very different meanings, 
+In such context, the two \lstinline{draw} methods have very different meanings, 
 but they happen to share the same name.
@@
 are mechanisms available in C++ and C\# that allow for two
-unintentionally conflicting methods to coexist in a class. Among them
+unintentionally conflicting methods to coexist in a class. Among them, 
 C++ is a representative that accepts the triangle inheritance and
@@
 them for unambiguity, and the dynamic type helps to find the most
-specific implementation. In that case both unambiguity and
+specific implementation. In that case, both unambiguity and
 extensibility are preserved. To present this idea, we introduce a

### 2017-06-18 Aplas17/sections/Overview.tex
grammar check Sec1,Sec2

--- 2017-06-18 Aplas17/sections/Overview.tex
@@
 \end{itemize}
-Furthermore for simplicity, our examples and formalization does not deal with state at
+Furthermore for simplicity, our examples and formalization do not deal with state at
 this stage. %%, but that should not block our discussions below.
@@
 have been developed in a system.  \lstinline|Deck| represents a deck
-of cards, and defines \lstinline|draw| for drawing a card from the
+of cards and defines \lstinline|draw| for drawing a card from the
 deck.  \lstinline|Drawable| is an interface for graphics that
@@
 
-Now one may quickly comes up with a workaround, which is creating a new \lstinline|draw| in \lstinline|DrawableDeck| to
+Now one may quickly come up with a workaround, which is creating a new \lstinline|draw| in \lstinline|DrawableDeck| to
 explicitly overrides the old ones. However, the two conflicting methods have totally different functionalities, merging
@@
 
-In the following text we will see that C++ is still unsatisfactory, as it introduces another problem on code reuse, which motivates
+In the following text, we will see that C++ is still unsatisfactory, as it introduces another problem on code reuse, which motivates
 our work.
@@
 If we try to keep the triangle inheritance, but apply dynamic dispatch, calling \lstinline|shuffleAndDraw| would trigger ambiguity. 
-In principle we want \lstinline|shuffleAndDraw| to invoke \lstinline|LoggingDeck.draw|, because they belong to the same branch, 
+In principle we want \lstinline|shuffleAndDraw| to invoke \lstinline|LoggingDeck.draw| because they belong to the same branch, 
 nonetheless, choosing either static dispatch
@@
 On the other hand, \lstinline|e.m()| where \lstinline|e| has static type \lstinline|I|, simply behaves the same as \lstinline|e.I::m()| in our model.
-Such a dispatch algorithm makes use of both the static type and the dynamic type of the receiver, so it is like a combination of static and dynamic dispatch.
+Such a dispatch algorithm makes use of both the static type and the dynamic type of the receiver, so it is a combination of static and dynamic dispatch.
 Intuitively, the static type specifies one branch to avoid ambiguity, and the dynamic type finds the latest version on that branch.

### 2017-06-18 Aplas17/sections/Formalization.tex
grammar check Sec3

@@
 
-In this section, we present the formal model \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}irarchical \textbf{J}ava}) , based on
-a minimal subset of Java 8 interfaces following Featherweight Java style~\cite{Igarashi01FJ}.
-The syntax, typing rules and small-step semantics are included below.
+In this section, we present the formal model \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}) , based on
+a minimal subset of Java 8 interfaces following Featherweight Java style~\cite{Igarashi01FJ}. We use the same
+conventions as FJ; $\overline{I}$ is shorthand for the (possibly empty)
+list $I_1, ..., I_n$, which may be indexed by $I_i$.
+The syntax, typing rules, and small-step semantics are presented below.
 
@@
 invocation, or object creation. A novel type of expressions are path-invocations like
-``$e.I::m(\overline{e})$'', meaning that the dynamically binded
+``$e.I::m(\overline{e})$'', meaning that the dynamically bound
 implementation for method $m$ should be along the path $I$. Another
@@
 can only be used inside an interface definition.
-Finally an expression can also be annotated with its static type. But \emph{annotated expressions are only intended for the semantic rules},
+Finally, an expression can also be annotated with its static type. But \emph{annotated expressions are only intended for the semantic rules},
 hence they are not supposed to appear in the source program. A value
 ``$\angl{I}\new{J}$''
-is the final result of multple reduction steps evaluating an
+is the final result of multiple reduction steps evaluating an
 expression. Such value represents an object instance
@@
 
-For simplicity \name{} does not formalize statements like assignments and so on, because they are orthogonal features.
+For simplicity, \name{} does not formalize statements like assignments and so on because they are orthogonal features.
 A program consists of a list of interface declarations, plus a single expression.
@@
 
-The method typing rule \textsc{(T-Method)} is more interesting, since the method can either be an original implementation or hierarchical overriding.
+The method typing rule \textsc{(T-Method)} is more interesting since the method can either be an original implementation or hierarchical overriding.
 Besides type-checking the return expression,
@@
 ambiguous during runtime. Therefore the condition says that if an expression type checks, it should not introduce ambiguity during runtime
-in any case. The interface check is responsible to capture ambiguity during compilation.
+in any case. The interface check is responsible for capturing ambiguity during compilation.
 
@@
 the model, which relates typing to computation. The type soundness states that, if an expression is 
-well-typed, then after many reduction steps it must reduce to a value, with its annotation to be subtype of the original expression type.
+well-typed, then after many reduction steps it must reduce to a value, with its annotation to be a subtype of the original expression type.
 Following the Featherweight Java paper~\cite{Igarashi01FJ}, the type-soundness theorem 

### 2017-06-18 Aplas17/sections/Auxiliary.tex
grammar check Sec4,5,6

@@
 \section{Auxiliary Definitions}\label{subsec:auxdefs}
-In this section we present the auxiliary definitions used in our formalization in 
+In this section, we present the auxiliary definitions used in our formalization in 
 Figure~\ref{fig:auxfunc}. To begin with, we
@@
     \item It is along path $J$, meaning that it is either a supertype or a subtype of $J$ (including $J$ itself);
-    \item It does not have a subtype in the same set, because we have used $prune$ to filter out all super types.
+    \item It does not have a subtype in the same set because we have used $prune$ to filter out all super types.
 \end{itemize}
@@
 \end{itemize}
-The algorithm for finding the most specific hierarchical overriding method is quite similar to that for most specific original method.
-A hierarchical overriding is not allowed to work on another hierarchical overriding, and one can hide another if their interfaces has subtyping relations.
+The algorithm for finding the most specific hierarchical overriding method is quite similar to that for finding the most specific original method.
+A hierarchical overriding is not allowed to work on another hierarchical overriding, and one can hide another if their interfaces have subtyping relations.
 If they do not hide each other, the result implies ambiguity.
@@
     \item First, it invokes $\mostSpecific(m, I_d, I_s)$ and returns a set.
-    \item If $\mostSpecific$ returns a singleton set $\{I\}$, then it is good, otherwise $\mbody$ is undefined in
+    \item If $\mostSpecific$ returns a singleton set $\{I\}$, then it is good, otherwise, $\mbody$ is undefined in
     this case.

### 2017-06-18 Aplas17/sections/RelatedWork.tex
grammar check Sec4,5,6

@@
 inheritance models to several specific models (C++ and \csharp) which are closest to our work. Then we 
-discuss similar techniques used in \self. Finally we discuss the foundation and related work of our formalization.
+discuss similar techniques used in \self. Finally, we discuss the foundation and related work of our formalization.
 
@@
 However untangling inheritance also untangles the class structure. In
-CZ, not only the number of classes, but also the class hierarchy
+CZ, not only the number of classes but also the class hierarchy
 complexity increases.
 
-The above mentioned models/languages support multiple inheritance, and
+The above-mentioned models/languages support multiple inheritance, and
 they handle method conflicts in the same way, by simply disallowing
@@
 by setting a linearised composition. This is the common drawback of
-the above mentioned models versus our model.
+the above-mentioned models versus our model.
 
@@
 language supports multiple (object) inheritance in a clever way. It not only develops the new inheritance
-relation with \emph{prioritized parents}, but also adopts \emph{sender path tiebreaker rule} for method lookup.
+relation with \emph{prioritized parents} but also adopts \emph{sender path tiebreaker rule} for method lookup.
 It specifies that ``\emph{if two slots with the same name are defined in equal-priority parents of the receiver, but only 
@@
 Featherweight Scala~\cite{Cremet2006}, and so on.
-FJ provides the standard model of formalizing a Java-like object-oriented language, and 
+FJ provides the standard model of formalizing a Java-like object-oriented language and 
 is easily extensible. In terms of formalization, the key novelty of our model is the use of 

### 2017-06-18 Aplas17/sections/Formalization.tex
revise full

@@
 \section{Formalization}~\label{sec:formalization}
-
-\bruno{There is quite a bit of teminology that we need to be careful.}\haoyuan{Done}
-
 In this section, we present the formal model \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}) , based on
-a minimal subset of Java 8 interfaces following Featherweight Java style~\cite{Igarashi01FJ}. We use the same
+Featherweight Java~\cite{Igarashi01FJ}. We use the same
 conventions as FJ; $\overline{I}$ is shorthand for the (possibly empty)
@@
 inheritance feature of \MIM{} is inspired by Java 8 interfaces, which support
-method implementations via default methods. This feature is quite
-closely related to \emph{traits}~\cite{scharli03traits}.  To demonstrate how
+method implementations via default methods. This feature is 
+closely related to \emph{traits}. To demonstrate how
 unintentional method conflicts are untangled in \MIM{}, we only focus on a small

### 2017-06-18 Aplas17/sections/Introduction.tex
revise full

@@
 have been adopted in some popular OOP languages. C++ has had 
-multiple inheritance from the start. Scala adapts ideas from traits~\cite{scharli03traits} 
+multiple inheritance from the start. Scala adapts the ideas from traits~\cite{scharli03traits} 
 and mixins~\cite{bracha90mixin} to offer a disciplined form of multiple inheritance. Java 8 
@@
 
-A reason why programming languages have resisted to multiple
-inheritance in the past is that, as Cook~\cite{Cook1987} put it, 
-``\emph{multiple inheritance is good but there is no good way to do it}''.
+As Cook~\cite{Cook1987} put it, 
+``\emph{multiple inheritance is good but there is no good way to do it}'', 
+that is one reason why many programming languages refuse to support multiple
+inheritance in the past.
 One of the most sensitive and critical issues is perhaps the ambiguity
@@
 In a nominal system, methods can be designed for different
-functionality, but they just happen to have same names (and
-signatures).
+functionality, but happen to have the same names (and signatures).
 A simple example of this situation is two \lstinline{draw} methods that
@@
 Unintentional method conflicts are less common than the diamond
-problem, nonetheless, they have severe effects in practice. 
+problem, nonetheless, they have severe effects in practice if not handled properly. 
 Unfortunately, such an issue has not received much formal study 
-before. In practice, existing languages also provide limited support for
+before. In practice, existing languages only provide limited support for
 it. In most languages, the mechanisms available to deal with this problem are the same as the diamond
@@
 
-Some other workarounds or approaches include delegation, and
+Some other workarounds or approaches include delegation and
 renaming/exclusion in the trait model. Yet they still have various
@@
 only to one branch of the class hierarchy. Our model can be viewed as
-a generalization of the trait model by providing additional support to
+a generalization of the simplified trait model by providing additional support to
 the triangle inheritance.

### 2017-06-18 Aplas17/sections/Overview.tex
revise full

@@
 \lstinline|DrawableDeck|, which models a drawable deck of cards. 
-Note that we use Java-like syntax
+Note that we use a Java-like syntax
 throughout the paper, and all types are defined with the keyword
@@
 have been developed in a system. \lstinline|Deck| represents a deck
-of cards and defines \lstinline|draw| for drawing a card from the
+of cards and defines a method \lstinline|draw| for drawing a card from the
 deck.  \lstinline|Drawable| is an interface for graphics that
-can be drawn, and also includes a method called \lstinline|draw| for
+can be drawn and also includes a method called \lstinline|draw| for
 visual display. For illustration, the implementation of
@@
 }
-
 interface Drawable {
@@
 Note that both methods have \lstinline|void| return type (we will not formalize
-\lstinline|void| in our calculus afterwards; here is only for illustration). In \lstinline|Deck|, \lstinline|draw| tries to get the cards as a stack, pops
+\lstinline|void| in our calculus afterwards; here it is only for illustration). 
+In \lstinline|Deck|, \lstinline|draw| tries to get the cards as a stack, pops
 out the top card, and so on. While in \lstinline|Drawable|, \lstinline|draw|
@@
 The point of using multiple inheritance is surely for composing the features from various 
-components, and to achieve code reuse, as supported by many mainstream OO
+components and to achieve code reuse, as supported by many mainstream OO
 languages. Nevertheless at this point, languages like Java simply throw a compile
@@
 
-Now one may quickly come up with a workaround, which is creating a new \lstinline|draw| in \lstinline|DrawableDeck| to
-explicitly overrides the old ones. However, the two conflicting methods have totally different functionalities, merging
-them into one does not make any sense. This non-solution will hide the old methods, and break independent extensibility. The
+Now one may quickly come up with a workaround, which is creating a new \lstinline|draw| method in \lstinline|DrawableDeck| to
+explicitly override the old ones. However, the two conflicting methods have totally different functionalities, merging
+them into one does not make any sense. This non-solution will hide the old methods and break independent extensibility. The
 feature we expect is called ``triangle inheritance'', that is to say, when the conflicting methods serve for different behaviours,
@@
   that using delegation makes it hard to correctly maintain
-  self-references \haoyuan{need to cite} in an extensible system [], and also
+  self-references in an extensible system and also
   introduces a lot of boilerplate code.
   \item \textbf{II. Refactor Drawable and/or Deck to rename the methods.} If
-  the code for \lstinline|Drawable| or \lstinline|Deck| are available
+  the source code for \lstinline|Drawable| or \lstinline|Deck| is available
   then it may be possible to rename one of the \lstinline|draw|
@@
   support method exclusion/renaming. Those features
-  provided can eliminate conflicts, although most
+   can eliminate conflicts, although most
   programming languages do not support them. In a traditional OO system,
-  they can break the subtyping. Moreover, in
+  they can break the subtyping relationship. Moreover, in
   contrast with exclusion, renaming can indeed preserve both conflicting
@@
 interface DrawableDeck extends Drawable, Deck {}
-
 interface Foo {
@@
 }
-
 // main program
@@
 \bruno{Emphasizing hierarchical dispatch and triangle inheritance.}\haoyuan{Done}
-On the other hand, we also need dynamic dispatch as it is essential and widely used in object-oriented programming.
+On the other hand, we also need dynamic dispatch as it is essential and widely used in Object-Oriented programming.
 C++ has the flexibility for choosing either way of dispatch by the \kwvirtual{} keyword.
@@
 \lstinline|shuffleAndDraw| is a typical method that invokes \lstinline|draw| in its definition. In principle, we want
-that invocation to use dynamic dispatch, because a programmer may define a subtype of \lstinline|Deck|, and override \lstinline|draw|:
+that invocation to use dynamic dispatch, because a programmer may define a subtype of \lstinline|Deck| and override \lstinline|draw|:
 \vspace{3pt}\begin{lstlisting}
@@
 interface DrawableLoggingDeck extends Drawable, LoggingDeck {...}
-
 // main program
@@
 \end{figure*}
-If we try to keep the triangle inheritance, but apply dynamic dispatch, calling \lstinline|shuffleAndDraw| would trigger ambiguity. 
-In principle we want \lstinline|shuffleAndDraw| to invoke \lstinline|LoggingDeck.draw| because they belong to the same branch, 
+\noindent If we try to keep the triangle inheritance while applying dynamic dispatch, calling \lstinline|shuffleAndDraw| would trigger ambiguity. 
+In principle, we want \lstinline|shuffleAndDraw| to invoke \lstinline|LoggingDeck.draw| because they belong to the same branch, 
 nonetheless, choosing either static dispatch

### 2017-06-18 Aplas17/sections/RelatedWork.tex
revise full

@@
 
+\begin{comment} %C++ related work with code explaination
 \noindent {\bf C++ model.}
@@
   something that goes wrong?}
+Furthermore, C++ does not support hierarchical overriding compared to our
+model.
+\end{comment}
+
+\noindent {\bf C++ model.}
+C++ supports a very flexible inheritance model and allows programmers to choose either static dispatch or dynamic dispatch for method lookup.
+It allows unintentional conflicts and uses static dispatch to resolve them, as discussed in Section~\ref{sec:overview}. 
+With virtual methods, dynamic dispatch is used and 
+method lookup algorithm will find the most specific method definition.
+Although C++ support this flexibility, dynamic dispatching on
+unintentional conflicting methods is problematic.
 Furthermore, C++ does not support hierarchical overriding compared to our

### 2017-06-19 Aplas17/sections/Conclusion.tex
Finish one round of review.

@@
 and type safety, whereas \MIM{} uses a different solution called hierarchical dispatch to obtain both.
-Such an approach not only offers great code reuse like dynamic dispatch, but also ensures unambiguity by
-our algorithm for method resolution. This paper also introduces method updates for refinements on branches individually.
-\MIM{} is formalized with a basis on Featherweight Java, and supported
+Such an approach not only offers great code reuse like dynamic dispatch but also ensures unambiguity by
+our algorithm for method resolution. This paper also introduces hierarchical overriding that refines branches individually.
+\MIM{} is formalized with a basis on Featherweight Java and supported
 by a few theorems. The prototype is implemented in Scala as a simple interpreter.

### 2017-08-10 Aplas17/sections/Auxiliary.tex
revise full
added abstract method
canInstantiate

@@
         {\mbody(m, I_d, I_s) = (J, \overline{I_x} \; \overline{x}, I_e \; e_0)}
+
+    \inferrule* [left=]
+        {  \mostSpecific(m, I_d, I_s) = \{I\} \\
+            \mostSpecificOverride(m, I_d, I) = \{J\} \\
+            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\absmethod{I_e}{m}{I_x}{x}{I}\}}
+        {\mbody(m, I_d, I_s) = (J, \overline{I_x} \; \overline{x}, I_e \; \o)}
 
@@
     \begin{tabular}{ccc}
-        \includegraphics[width=2cm]{pics/p1.pdf}\hspace{4pt} &
-        \includegraphics[width=2cm]{pics/p2.pdf}\hspace{4pt} &
-        \includegraphics[width=2cm]{pics/p3.pdf}\hspace{4pt} \\
+        \includegraphics[width=1.5cm]{pics/p1.pdf}\hspace{4pt} &
+        \includegraphics[width=1.5cm]{pics/p2.pdf}\hspace{4pt} &
+        \includegraphics[width=1.5cm]{pics/p3.pdf}\hspace{4pt} \\
         (a) $\mbody(m,C,A) = (A,...)$\ \ \  & (b) $\mbody(m,C,A) = (C,...)$\ \ \  & (c) $\mbody(m,C,A) = (C,...)$
@@
 
+\subsection{$\canInstantiate$}
+We use the auxilary function $\canInstantiate(I)$ to check whether an interface $I$ can be instantiated or not.
+The algorithm is decribed below:
+\begin{enumerate}
+\item Suppose $\mostSpecific(m, I, I) = \overline{J}$, where $\overline{J}$ is a list of interfaces.
+\item If $\forall J_i \in \overline{J}, if \mostSpecificOverride(m, I, J_i) = \{ K \} $ and $m$ in $K$ is not abstract, 
+then $\canInstantiate(I) = true$, else $\canInstantiate(I) = false$.
+\end{enumerate}
+
 \subsection{$\mbody$ and $\mtype$}
@@
 The definition of $\mtype$ used in typing rules simply relies on $\mbody$. In short,
-$$\mbody(m, I, I) = (J, \overline{I_x}\ \overline{x}, I_e\ e) \ \Longrightarrow\ \mtype(m, I) = \overline{I_x}\rightarrow I_e$$
+$$\mbody(m, I, I) = (J, \overline{I_x}\ \overline{x}, I_e\ ?) \ \Longrightarrow\ \mtype(m, I) = \overline{I_x}\rightarrow I_e$$
 

### 2017-09-04 NewVersion/paper.tex
new

--- 2017-06-18 Aplas17/paper.tex
@@
 
+\newcommand\saveSpaceFig{\vspace{-2ex}}
+
 \lstset{ %
@@
 
+\vspace{-4ex}
+
 \begin{abstract}
@@
 restricted model of multiple inheritance that is easy to reason and 
-has many elegant properties. Traits have good support for method 
+have many elegant properties. Traits have good support for method 
 conflicts which arise from \emph{diamond inheritance}:
@@
 
-This paper presents a new model \name{} 
-(short for \emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}) 
-that deals with unintentional
-method conflicts. In our new model, conflicting methods arising
-from unrelated methods can coexist in the same component. Moreover, they
-can be \emph{independently overridden}. What ensures unambiguity 
-is the use of information about the class hierarchy. In turn, 
-hierarchical information is also employed in method dispatching, which 
-uses a combination of static and dynamic type information to choose 
-the implementation of a method at run-time. We give illustrative 
-examples of our language and features and formalize \name{} as a minimal 
-Featherweight-Java style calculus.
+This paper presents a new model \name{} (short for \emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}) as an extension/variation to the trait model that deals with unintentional method conflicts.
+The method resolution semantics resembles C++, so part of our formalization can be used as a partial C++ method lookup algorithm formalization.
+We discuss the similarities and differences with C++ and also advantages and disadvantages.
+In our new model, conflicting methods arising from unrelated methods can coexist in the same component.
+Moreover, one novel feature we add to our model is hierarchical method overriding: methods can be \emph{independently overridden} along multiple inheritance hierarchy.
+What ensures unambiguity is the use of information about the class hierarchy.
+In turn, hierarchical information is also employed in method dispatching, which uses a combination of static and dynamic type information to choose the implementation of a method at run-time.
+We give illustrative examples of our language and features and formalize \name{} as a minimal Featherweight-Java style calculus.
 

### 2017-09-04 NewVersion/sections/Introduction.tex
new

--- 2017-06-18 Aplas17/sections/Introduction.tex
@@
 
-As Cook~\cite{Cook1987} put it, 
-``\emph{multiple inheritance is good but there is no good way to do it}'', 
-that is one reason why many programming languages refuse to support multiple
-inheritance in the past.
+A reason why programming languages have resisted to multiple
+inheritance in the past is that, as Cook~\cite{Cook1987} puts it, 
+``\emph{multiple inheritance is good but there is no good way to do it}''.
 One of the most sensitive and critical issues is perhaps the ambiguity

### 2017-09-04 NewVersion/sections/TypeSafety.tex
new

\begin{lemma}~\label{lemma0}
% $\textit{If } \mtype(m, I, J) = \overline{D} \rightarrow D, \textit{ and } \mbody(m, I, J) = \overline{x}.e, 
%  \textit{ then for some } J_0 \textit{ with } I <: J_0, \  \exists C <: D, \textit{ such that }  
%  \judgeewf {\overline{x}:\overline{D}, \kwthis:J_0} {e:C} $.
$\textit{If } \mbody(m, I, J) = (J', \overline{I_x} \; \overline{x}, I_e \; e), 
 \textit{ then for some } J_0 \textit{ with } I <: J_0, \  \exists I' <: I_e, \textit{ such that }  
 \judgeewf {\overline{x}:\overline{I_x}, \kwthis:J_0} {e : I'} $.
\end{lemma}

 \begin{proof}~\\
 $\textit{The base case: if } m \textit{ is defined in } I, \textit{ then it is easy since } m 
 \textit{ is defined in } I \textit{ and } 
 \judgeewf {\overline{x}:\overline{I_x}, \kwthis : I} {e : I_e}, \textit{by the rule \textsc{(T-Method)}}.
 \textit{The induction step is also straightforward.} 
 $ 
 \end{proof}

\begin{lemma}[Method Type Preservation]~\label{lemma2}
$\textit{If } \mtype(m, I) = \overline{I_x} \rightarrow I_e, \textit{ then } \mtype(m, J) = \overline{I_x} \rightarrow I_e 
\textit{ for all } J \subtype I.
$
\begin{proof}~\\
Straight induction on the derivation of $J \subtype I$. Whether $m$ is defined in $J$ or not, $\mtype(m, J)$ should 
be the same as $\mtype(m, K)$ where $J \; \kwextends \; K \{...\}$.
\end{proof}
\end{lemma}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{lemma}[Term Substitution Preserves Typing]~\label{lemma1}
$\textit{If } \ \judgeewf {\Gamma, \ \overline{x}:\overline{I_x}} { e : I } \textit{ , and }
\judgeewf {\Gamma} {\overline{y}:\overline{I_y}} \textit{ where } \overline{I_y} \subtype \overline{I_x}
\textit{, then } \judgeewf {\Gamma} {[\overline{y}/\overline{x}]e : I'} \textit{ for some } I' \subtype I.
$

\begin{proof}~\\
\noindent \textbf{Case Var.}
$ e = x \quad I = \Gamma(x) $. \\
If $x \notin \overline{x}$, then the conclusion is immediate, since $[\overline{y}/\overline{x}]x = x$.
On the other hand, if $x = x_i$ and $I = {I_x}_i$, then since $[\overline{y}/\overline{x}]x = [\overline{y}/\overline{x}]x_i = y_i$,
letting $I' = {I_y}_i$ finishes the case.

\noindent \textbf{Case New.}
$e = \new I$ and there are no term for substitution, the conclusion is obvious.

\noindent \textbf{Case Invk.}
$ e = e_0.m(\overline{e}) \quad
  \judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e_0 : I_0} $
$$ mtype(m, I_0) = \overline{I_e} \rightarrow J $$
$$ \judgeewf {\Gamma, \overline{x}:\overline{I_x}} {\overline{e}:\overline{I}} \quad
    \overline{I} \subtype \overline{I_e} $$
By induction hypothesis, there are some $I_0'$ and $\overline{I_e'}$ such that
    $$ \judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0 : I_0'} \quad 
        I_0' \subtype I_0 $$
    $$ \judgeewf {\Gamma} {[\overline{y}/\overline{x}]\overline{e} : \overline{I_e'}} \quad  
        \overline{I_e'} \subtype \overline{I}$$    
By lemma~\ref{lemma2}, 
    $mtype(m, I_0') = \overline{I_e} \rightarrow J$,
then $\overline{I_e'} \subtype \overline{I_e}$ by the transitivity of $\subtype$.
Therefore, by the rule \textsc{(T-Invk)}, 
    $\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0.m([\overline{y}/\overline{x}]\overline{e}) : J}$.

\noindent \textbf{Case PathInvk.}
$ e = e_0.I::m(\overline{e}) $ and proof is similar as case Var.

\noindent \textbf{Case SuperInvk.}
$ e = \kwsuper.I::m(\overline{e}) $ \\
Suppose $\judgeewf {\Gamma} {\kwthis : I_0}$, the following proof should be similar as case Var.
\end{proof}

\end{lemma}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Proof for Theorem~\ref{theorem_subject}}
\begin{proof} ~\\
\noindent \textbf{Case Invk.} 
let \[ e = \angl{J}\new I.m(\overline{\angl{I_e}}\overline{e}) \] 
Suppose \[ \mbody(m, I, J) = (J', \overline{I_x} \; \overline{x}, I_{e_0} \; e_0) \] 
then \[ e' =  [\overline{\angl{I_x}} \overline{e}/\overline{x}, \; \angl{J}\new I/\kwthis ] e_0 \] 
By rules \textsc{(T-New)} and \textsc{(T-Invk)}, 
  \[ \judgeewf \Gamma {\new I:I} \quad 
     \mtype(m, I, J) = \overline{I_x} \rightarrow I_{e_0} \quad 
     \judgeewf \Gamma {\overline{e} : \overline{I_e'}} \quad
     \overline{I_e'} \subtype \overline{I_x} \quad
     \textit{, for some } \; \overline{I_e'}
  \]
By Lemma~\ref{lemma0},
    \[
    \judgeewf {\Gamma, \overline{x}:\overline{I_x}, \kwthis:J_0} {e_0:I_f} \textit{, for some } J \subtype J_0 \textit{ and } I_f \subtype I_{e_0}
    \]
By Lemma~\ref{lemma1},
    \[
    \judgeewf {\Gamma} {[\overline{\angl{I_x}} \overline{e}/\overline{x}, \; \angl{J}\new I/\kwthis ] e_0  :  I_g} \textit{, for some } I_g \subtype I_f 
    \]
So $I_g <: I_{e_0}$, finally just let $I' = I_g$.

\noindent \textbf{Case PathInvk.}
let \[ e = \angl{J}\new I.K::m(\overline{\angl{I_e}} \overline{e}) \]  
Suppose \[ \mbody(m, I, K) = (J', \overline{I_x} \; \overline{x}, I_{e_0} \; e_0) \] 
then \[ e' =  [\overline{\angl{I_x}} \overline{e}/\overline{x}, \; \angl{K}\new I/\kwthis ] e_0 \] 
By rules \textsc{(T-New)} and \textsc{(T-Invk)}, 
  \[ \judgeewf \Gamma {\new I:I} \quad 
     \mtype(m, I, K) = \overline{I_x} \rightarrow I_{e_0} \quad 
     \judgeewf \Gamma {\overline{e} : \overline{I_e'}} \quad
     \overline{I_e'} \subtype \overline{I_x} \quad
     \textit{, for some } \; \overline{I_e'}
  \]
By Lemma~\ref{lemma0},
    \[
    \judgeewf {\Gamma, \overline{x}:\overline{I_x}, \kwthis:J_0} {e_0:I_f} \textit{, for some } K \subtype J_0 \textit{ and } I_f \subtype I_{e_0}
    \]
By Lemma~\ref{lemma1},
    \[
    \judgeewf {\Gamma} {[\overline{\angl{I_x}} \overline{e}/\overline{x}, \; \angl{K}\new I/\kwthis ] e_0  :  I_g} \textit{, for some } I_g \subtype I_f 
    \]
So $I_g <: I_{e_0}$, finally just let $I' = I_g$.

\noindent \textbf{Case Super-Invk.}
let \[ e = \kwsuper.K::m(\overline{\angl{I_e}} \overline{e}) \]   
Suppose \[ \mbody(m, K, K) = (J', \overline{I_x} \; \overline{x}, I_{e_0} \; e_0) \] 
then \[ e' =  [\overline{\angl{I_x}} \overline{e}/\overline{x}] e_0 \] 
By rules \textsc{(T-New)} and \textsc{(T-Invk)}, 
  \[ 
     \mtype(m, K, K) = \overline{I_x} \rightarrow I_{e_0} \quad 
     \judgeewf \Gamma {\overline{e} : \overline{I_e'}} \quad
     \overline{I_e'} \subtype \overline{I_x} \quad
     \textit{, for some } \; \overline{I_e'}
  \]
By Lemma~\ref{lemma0},
    \[
    \judgeewf {\Gamma, \overline{x}:\overline{I_x}, \kwthis:J_0} {e_0:I_f} \textit{, for some } K \subtype J_0 \textit{ and } I_f \subtype I_{e_0}
    \]
By Lemma~\ref{lemma1},
    \[
    \judgeewf {\Gamma} {[\overline{\angl{I_x}} \overline{e}/\overline{x} ] e_0  :  I_g} \textit{, for some } I_g \subtype I_f 
    \]
So $I_g <: I_{e_0}$, finally just let $I' = I_g$.

\end{proof}

\subsubsection{Proof for Theorem~\ref{theorem_progress}}
\begin{proof}~\\
\noindent \textbf{Case 1.}
Given that $e$ is well-typed, by rule \textsc{(T-Invk)}, $\mtype(m, J)$ is defined.
By rule \textsc{(T-Intf)} for interface $I$,
    \[ \forall J >: I, m, \mtype(m, J) \text{ is defined } \Rightarrow \mbody(m, I, J) \text{ is defined } \]
So straightforwardly, we get $ \mbody(m, I, J) = (J', \overline{I_x} \; \overline{x}, I'_E \; e_0) $ and
         $\num{\overline{x}} = \num{\overline{e}}$ for some $J', \overline{I_x}, \overline{x}, I_e'$ and $e_0$

\noindent \textbf{Case 2 and 3.} Proof for case 2 and 3 is similar to case 1, and we omit it here.
\end{proof}

### 2017-09-04 NewVersion/sections/Discussion.tex
change

\section{Discussion}
In this section, we discuss the design space and some reflections of the work. 
\paragraph{Abstract Methods.}
Why we include 
\paragraph{Static Invocation.}
Why we include
\paragraph{Method Resolution Rules.}
Other resolution possibilities and comparison.

### 2017-09-04 NewVersion/sections/Introduction.tex
change

@@
 	\item \textbf{\name:} a formalized model based on Featherweight Java, supporting the above features. Some theorems and their proofs
-	are attached to confirm the type soundness of the model.\bruno{Anything about unambiguity?}
-	\item \textbf{Prototype implementation\footnote{Available in supplementary material attached to the submission.}:} a simple interpreter implemented in Scala that follows our formalization rules, incorporating parsing, type-checking and semantic evaluation.\haoyuan{also mention in formalization.}
+	are attached to confirm the type soundness of the model.
+	\item \textbf{Prototype implementation\footnote{Available in supplementary material attached to the submission.}:} a simple interpreter implemented in Scala that follows our formalization rules, incorporating parsing, type-checking and semantic evaluation.
 \end{itemize}

### 2017-09-05 NewVersion/sections/Formalization.tex
new
filename uppercase

--- 2017-06-18 Aplas17/sections/Formalization.tex
@@
 
+\vspace{-2ex}
 \subsection{Syntax}
@@
 invocation, or object creation. A novel type of expressions are path-invocations like
-``$e.I::m(\overline{e})$'', meaning that the dynamically bound
+``$e.I\pathIvk m(\overline{e})$'', meaning that the dynamically bound
 implementation for method $m$ should be along the path $I$. Another
@@
 \begin{figure*}[t]
+\saveSpaceFig
 \begin{displaymath}
@@
 \text{Interfaces}   & IL & \Coloneqq & \interface{I}{I}{M} \\
-\text{Methods}      & M  & \Coloneqq & \method{I}{m}{I_x}{x}{J}{e} \\
+\text{Methods}      & M  & \Coloneqq & \method{I}{m}{I_x}{x}{J}{e}  \mid
+									   \absmethod{I}{m}{I_x}{x}{J} \\
 \text{Expressions}  & e  & \Coloneqq & x \mid
@@
 \new{I} \mid
-e.I::m(\overline{e}) \mid
-\kwsuper.I::m(e) \; \mid \; \angl{I}e \\
+e.\staAnno{I}{J}m(\overline{e}) \mid
+e.I?m(e) \; \mid \; \angl{I}e \\
 \text{Context}      & \Gamma & \Coloneqq & \overline{x}:\overline{I} \\
@@
 \caption{Syntax of \name{}.}\label{fig:syntax}
+\saveSpaceFig
 \end{figure*}
@@
 \begin{figure*}[t]
+\saveSpaceFig
 \begin{mathpar}
@@
 	\tpathinvk \\
-	\tsuperinvk \\
+	% \tsuperinvk \\
+	\tstaticinvk \\
 	\tnew \\
 	\tmethod \\
+	\tabsmethod \\
 	\tintf
@@
 \caption{Typing and subtyping rules.}\label{fig:typingrules}
+\saveSpaceFig
 \end{figure*}
@@
 	\spathinvk \\
-	\ssuperinvk \\
+	% \ssuperinvk \\
+	\sstaticinvk \\
 	\creceiver \hspace{.5in}
@@
 	\cpathargs \\
-	\csuperargs \\
+	% \csuperargs \\
+	\cstaticargs \\
 	\cstatictype \\
@@
 \caption{Small-step semantics.}\label{fig:smallstep}
+\saveSpaceFig
 \end{figure*}

### 2017-09-06 NewVersion/sections/Auxiliary.tex
new
filename uppercase
more fixing

--- 2017-08-10 Aplas17/sections/Auxiliary.tex
@@
     \inferrule* [left=]
-    { set1 = \; \{ K <: J \; $and$ \; K >: I \; | \; m \in \overrideSet(K, K) \} \\
-        set2 = \; \{ K >: J \; | \; m \in \overrideSet(K, K) \} }
+    { set1 = \; \{K\mid I <: K, \; K <: J\; $and$\; m \in \overrideSet(K, K) \} \\
+        set2 = \; \{K\mid  J <: K \; $and$\; m \in \overrideSet(K, K) \} }
     {\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
@@
     \inferrule* [left=]
-        { set = \; \{ K <: J \; $and$ \; K >: I \; | \;
+        { set = \; \{ K\mid I <: K, \; K <: J\; $and$ \;
             m \in \overrideSet(K, J)  \} }
@@
 
-    prune(set) = \{I \in set \; | \; \nexists J \in set, J <: I, J \neq I \}
+    prune(set) = \{I \in set \; | \; \nexists J \in set\setminus I, J <: I\}
 
@@
         \\ J \in \overline{I} }
-    {\ext(I, J)}
+    {\ext(I, J) \marco{Is this ever used?}}
 
@@
     \begin{tabular}{ccc}
-        \includegraphics[width=1.5cm]{pics/p1.pdf}\hspace{4pt} &
-        \includegraphics[width=1.5cm]{pics/p2.pdf}\hspace{4pt} &
-        \includegraphics[width=1.5cm]{pics/p3.pdf}\hspace{4pt} \\
+        \includegraphics[width=1.5cm]{pics/P1.pdf}\hspace{4pt} &
+        \includegraphics[width=1.5cm]{pics/P2.pdf}\hspace{4pt} &
+        \includegraphics[width=1.5cm]{pics/P3.pdf}\hspace{4pt} \\
         (a) $\mbody(m,C,A) = (A,...)$\ \ \  & (b) $\mbody(m,C,A) = (C,...)$\ \ \  & (c) $\mbody(m,C,A) = (C,...)$
@@
    \begin{tabular}{cc}
-    \includegraphics[height=3cm]{pics/p4.pdf}\hspace{4pt} &
-    \includegraphics[height=3cm]{pics/p5.pdf}\hspace{4pt} \\ 
+    \includegraphics[height=3cm]{pics/P4.pdf}\hspace{4pt} &
+    \includegraphics[height=3cm]{pics/P5.pdf}\hspace{4pt} \\ 
     (d) $\mbody(m,D,A) = \keyword{undefined}$\ \ \  & (e) $\mbody(m,D,A) = \keyword{undefined}$
@@
 \end{enumerate}
+
+\subsection{$\mbodyStatic$}
+The auxilary function $\mbodyStatic$ serves for method loopup for static method invocation. 
+The brief description of the algorithm follows:
+\begin{mathpar}
+    \inferrule* [left=]
+        {  %\mostSpecific(m, I, I) = \{J\} \\
+            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_e}{m}{I_x}{x}{J}{e_0}\ldots\}}
+        {\mbodyStatic(m, J, J') = (J, \overline{I_x} \; \overline{x}, I_e \; e_0)}
+
+    \inferrule* [left=]
+        {  %\mostSpecific(m, I, I) = \{J\} \\
+            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\absmethod{I_e}{m}{I_x}{x}{J}\ldots\}}
+        {\mbodyStatic(m, J, J') = (J, \overline{I_x} \; \overline{x}, I_e \; \o)}
+\end{mathpar}
 

### 2017-09-16 NewVersion/sections/TypeSafety.tex
Fixing proof.

@@
 \end{lemma}
+
+\textcolor{red}{
+\begin{lemma}[Method Type Preservation]~\label{lemma2_new}
+$\textit{If } \mbody(m, I_0, J_0) = (K, \overline{I_x}\ \overline{x}, I_e\ e)$, $\textit{ and }
+\mbody(m, I'_0, J_0) = (K', \overline{I'_x}\ \overline{x'}, I'_e\ e') \textit{ for some }I'_0 \subtype I_0, \textit{ then }
+\overline{I'_x} = \overline{I_x}$ $\textit{and } I'_e = I_e.$
+\end{lemma}}
 
@@
 By lemma~\ref{lemma2}, 
-    $mtype(m, I_0') = \overline{I_e} \rightarrow J$,
-then $\overline{I_e'} \subtype \overline{I_e}$ by the transitivity of $\subtype$.
+    $mtype(m, I_0') = \overline{I_e} \rightarrow J$.
+
+\noindent Then $\overline{I_e'} \subtype \overline{I_e}$ by the transitivity of $\subtype$.
 Therefore, by the rule \textsc{(T-Invk)}, 
@@
 Suppose $\judgeewf {\Gamma} {\kwthis : I_0}$, the following proof should be similar as case Var.
+
+\noindent\textcolor{red}{\textbf{Case PathInvk.} $e = e_0.J_0?m(\overline{e})$. By \textsc{(T-PathInvk)}, suppose}
+	$$\textcolor{red}{\judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e_0 : I_0} \quad I_0 \subtype J_0}$$
+	$$\textcolor{red}{\mbody(m, I_0, J_0) = (\_, \overline{J}\ \_, I\ \_)}$$
+	$$\textcolor{red}{\judgeewf {\Gamma, \overline{x}:\overline{I_x}} {\overline{e} : \overline{I_e}} \quad 
+	  \overline{I_e} \subtype \overline{J} \quad \judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e : I}}$$
+\textcolor{red}{By induction hypothesis, there are some $I'_0$ and some $\overline{I'_e}$ such that}
+	$$\textcolor{red}{\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0 : I_0'} \quad I_0' \subtype I_0 \subtype J_0}$$
+	$$\textcolor{red}{\judgeewf {\Gamma} {[\overline{y}/\overline{x}]\overline{e} : \overline{I_e'}} \quad 
+	  \overline{I_e'} \subtype \overline{I_e} \subtype \overline{J}}$$   
+\textcolor{red}{By lemma~\ref{lemma2_new}, if $[\overline{y}/\overline{x}]e$ is well typed,}
+	$$\textcolor{red}{\mbody(m, I'_0, J_0) = (\_, \overline{J}\ \_, I\ \_)}$$
+\textcolor{red}{Therefore, by the rule \textsc{(T-Invk)}, 
+	$\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0.m([\overline{y}/\overline{x}]\overline{e}) : I}$.}
+
 \end{proof}
@@
 \begin{proof} ~\\
+\noindent\textcolor{red}{\textbf{Case PathInvk.} Let} \haoyuan{where to use lemma 1}
+  $$\textcolor{red}{e = (\angl{J}\new{I}).K?m(\overline{v}) \quad \judgeewf {\Gamma} {e : I_e}}$$
+  $$\textcolor{red}{e' = \angl{I_e}[\overline{\angl{I_x}} \overline{v}/\overline{x}, \angl{I_0}\new{I}/\kwthis]e_0 \quad \judgeewf {\Gamma} {e' : I'_e}}$$
+  $$\textcolor{red}{\mbody(m, I, K) = (I_0, \overline{I_x} \; \overline{x}, I_e \; e_0)}$$
+\textcolor{red}{Since $e$ is well typed, $\angl{J}\new{I}$ is well typed, and}
+  $$\textcolor{red}{\judgeewf {\Gamma} {\angl{J}\new{I} : I}}$$
+\textcolor{red}{By \textsc{(T-Anno)}, we have $I \subtype J$.}
+
+\noindent\textcolor{red}{Suppose that the original form of $(\angl{J}\new{I}).K?m(\overline{v})$ is $e_T.K?m(\overline{e_T})$ by reduction.
+	The original expression should be type-checked already by \textsc{(T-PathInvk)}. Suppose that}
+  $$\textcolor{red}{\judgeewf {\Gamma} {e_T : I_T} \quad \judgeewf {\Gamma} {\overline{e_T} : \overline{I_T}}}$$
+\textcolor{red}{By induction hypothesis, $I \subtype I_T$. By lemma~\ref{lemma2_new},}
+  $$\textcolor{red}{\mbody(m, I_T, K) = (\_, \overline{I_x}\ \_, I_e\ \_)}$$
+\textcolor{red}{Therefore $\overline{I_T} \subtype \overline{I_x}$. By induction hypothesis,}
+  $$\textcolor{red}{\judgeewf {\Gamma} {\overline{v} : \overline{I_v} \subtype \overline{I_T} \subtype \overline{I_x}}}$$
+\textcolor{red}{So the first substitution preserves typing, On the other hand, .... the second one also preserves typing. Hence $I'_e \subtype$ type of $e_0 \subtype I_e$.}
+
 \noindent \textbf{Case Invk.} 

### 2017-09-16 NewVersion/sections/TypeSafety.tex
2nd fix.

@@
   $$\textcolor{red}{\judgeewf {\Gamma} {\angl{J}\new{I} : I}}$$
-\textcolor{red}{By \textsc{(T-Anno)}, we have $I \subtype J$.}
+\textcolor{red}{By \textsc{(T-Anno)}, we have $I \subtype J$. Also, by \textsc{(T-PathInvk)}, $\judgeewf {\Gamma} {\overline{v} : \overline{I_v} \subtype \overline{I_x}}$.}
 
-\noindent\textcolor{red}{Suppose that the original form of $(\angl{J}\new{I}).K?m(\overline{v})$ is $e_T.K?m(\overline{e_T})$ by reduction.
-	The original expression should be type-checked already by \textsc{(T-PathInvk)}. Suppose that}
-  $$\textcolor{red}{\judgeewf {\Gamma} {e_T : I_T} \quad \judgeewf {\Gamma} {\overline{e_T} : \overline{I_T}}}$$
-\textcolor{red}{By induction hypothesis, $I \subtype I_T$. By lemma~\ref{lemma2_new},}
-  $$\textcolor{red}{\mbody(m, I_T, K) = (\_, \overline{I_x}\ \_, I_e\ \_)}$$
-\textcolor{red}{Therefore $\overline{I_T} \subtype \overline{I_x}$. By induction hypothesis,}
-  $$\textcolor{red}{\judgeewf {\Gamma} {\overline{v} : \overline{I_v} \subtype \overline{I_T} \subtype \overline{I_x}}}$$
-\textcolor{red}{So the first substitution preserves typing, On the other hand, .... the second one also preserves typing. Hence $I'_e \subtype$ type of $e_0 \subtype I_e$.}
+\noindent \textcolor{red}{So the first substitution preserves typing, On the other hand, .... the second one also preserves typing. Hence $I'_e \subtype$ type of $e_0 \subtype I_e$.}
 

### 2017-09-18 NewVersion/sections/Formalization.tex
.
reply marco
refine
remove StaticInvocation
More proof.

@@
 \new{I} \mid
-e.\staAnno{I}{J}m(\overline{e}) \mid
 e.I?m(e) \; \mid \; \angl{I}e \\
@@
 	% \tsuperinvk \\
-	\tstaticinvk \\
+	% \tstaticinvk  \\
 	\tnew \\
@@
 	\tabsmethod \\
-	\tintf
+	\tintf \\
+	\tanno
 \end{mathpar}
-\caption{Typing and subtyping rules.}\label{fig:typingrules}
+\label{fig:typingrules}
 \saveSpaceFig
@@
 	% \ssuperinvk \\
-	\sstaticinvk \\
+	% \sstaticinvk \\
 	\creceiver \hspace{.5in}
@@
 	% \csuperargs \\
-	\cstaticargs \\
+	% \cstaticargs \\
 	\cstatictype \\
@@
 \begin{theorem}[Progress]~\label{theorem_progress}
-$\textit{Suppose } e \textit{ is a well-typed expression } $ \\
-\begin{enumerate}
-\item If $e$ includes $\left(\angl{J}\emph{\kwnew}\;I()\right).m(\overline{\angl{I_e}} \; \overline{e})$ as a subexpression,
-    then $ \emph{\mbody}(m, I, J) = (J', \overline{I_x} \; \overline{x}, I'_E \; e_0) $ and
-         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_x}, \overline{x}, I_e'$ and $e_0$.
-\item If $e$ includes $\left(\angl{J}\emph{\kwnew}\;I()\right).K::m(\overline{\angl{I_e}} \overline{e})$ as a subexpression,
-    then $ \emph{\mbody}(m, I, K) = (J', \overline{I_x} \; \overline{x}, I'_E \; e_0) $ and 
-         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_x}, \overline{x}, I_e'$ and $e_0$.
-\item If $e$ includes $\emph{\kwsuper}.K::m(\overline{\angl{I_e}} \overline{e})$ as a subexpression,
-    then $ \emph{\mbody}(m, K, K) = (J', \overline{I_x} \; \overline{x}, I'_E \; e_0) $ and 
-         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_x}, \overline{x}, I_e'$ and $e_0$.
-\end{enumerate}
+$\textit{Suppose } e \textit{ is a well-typed expression, if } e \textit{ includes} $
+
+\noindent $\left(\angl{J}\emph{\kwnew}\;I()\right).K?m(\overline{v}) \textit{ as a subexpression, then } \emph{\mbody}(m, I, K) = (I_0, \overline{I_x} \; \overline{x}, I_e\; e_0) $ $\textit{and } \num{\overline{x}} = \num{\overline{e}} \textit{ for some } \overline{I_x}, \overline{x}, I_e \textit{ and } e_0.$
 \end{theorem}

### 2017-09-18 NewVersion/sections/TypeSafety.tex
More proof.

@@
 
-\begin{lemma}[Method Type Preservation]~\label{lemma2}
-$\textit{If } \mtype(m, I) = \overline{I_x} \rightarrow I_e, \textit{ then } \mtype(m, J) = \overline{I_x} \rightarrow I_e 
-\textit{ for all } J \subtype I.
-$
-\begin{proof}~\\
-Straight induction on the derivation of $J \subtype I$. Whether $m$ is defined in $J$ or not, $\mtype(m, J)$ should 
-be the same as $\mtype(m, K)$ where $J \; \kwextends \; K \{...\}$.
-\end{proof}
-\end{lemma}
-
 \textcolor{red}{
 \begin{lemma}[Method Type Preservation]~\label{lemma2_new}
-$\textit{If } \mbody(m, I_0, J_0) = (K, \overline{I_x}\ \overline{x}, I_e\ e)$, $\textit{ and }
-\mbody(m, I'_0, J_0) = (K', \overline{I'_x}\ \overline{x'}, I'_e\ e') \textit{ for some }I'_0 \subtype I_0, \textit{ then }
+$\textit{If } \mbody(m, I_0, J_0) = (K, \overline{I_x}\ \_, I_e\ \_)$, $\mbody(m, I'_0, J_0) = (K', \overline{I'_x}\ \_, I'_e\ \_) \textit{ for some }I'_0 \subtype I_0, \textit{ then }
 \overline{I'_x} = \overline{I_x}$ $\textit{and } I'_e = I_e.$
 \end{lemma}}
+\begin{proof}
+
+Trivial for the case $I'_0 = I_0$.
+And since the lemma has transitivity on subtyping, it suffices to prove the following cases and rely on induction, where we can suppose that $I'_0$ directly extends $I_0$.
+
+Suppose that $$\mostSpecific(m, I_0, J_0) = \{I\}$$ $$\mostSpecificOverride(m, I_0, I) = \{K\}$$
+
+\textbf{(1) The body of $I'_0$ does not contain $m$.} Trivial because $\mbody(m, I_0, J_0) = \mbody(m, I'_0, J_0)$. \haoyuan{Non-trivial. m may be inherited from other super types. TODO.}
+
+\textbf{(2) $m \in \overrideSet(I'_0, I'_0)$.} In that case $I'_0$ defines an original method $m$.
+ So
+$$\mostSpecific(m, I'_0, J_0) = \{I'_0\}$$ $$\mostSpecificOverride(m, I'_0, I'_0) = \{I'_0\}$$
+Hence $\mbody(m, I'_0, J_0)$ returns the original $m$ from $I'_0$.
+By $\textsc{(T-Intf)}$, we know that $\canOverride(m, I'_0, I)$ holds, which means that $I'_0$ has the same type as $I$ for $m$.
+On the other hand, from $\textsc{(T-Method)}$ and $\textsc{(T-AbsMethod)}$, the type of $m$ is also preserved between $I$ and $K$ (method override needs to keep the type).
+Finally $\mbody(m, I'_0, J_0)$ has the same type as $\mbody(m, I_0, J_0)$.
+
+\textbf{(3) $m \in \overrideSet(I'_0, I)$.} Similar to (2), $I$ and $K$ have the same type for $m$.
+Moreover, $\textsc{(T-Method)}$ and $\textsc{(T-AbsMethod)}$ also ensure that $I'_0$ and $I$ have the same type for $m$.
+\haoyuan{But findOrigin may no longer be I.}
+
+\textbf{(4) $m \in \overrideSet(I'_0, J)$ for some other $J$.} Same as (1). Such an $m$ does not affect the result of $\mbody$.
+%Straight induction on the derivation of $J \subtype I$. Whether $m$ is defined in $J$ or not, $\mtype(m, J)$ should 
+%be the same as $\mtype(m, K)$ where $J \; \kwextends \; K \{...\}$.
+\end{proof}
 
@@
 
+\begin{comment}
 \noindent \textbf{Case Invk.}
@@
 Suppose $\judgeewf {\Gamma} {\kwthis : I_0}$, the following proof should be similar as case Var.
+\end{comment}
 
@@
 \begin{proof} ~\\
-\noindent\textcolor{red}{\textbf{Case PathInvk.} Let} \haoyuan{where to use lemma 1}
+\noindent\textcolor{red}{\textbf{Case Invk.} TODO. By t-invk and t-intf.}
+
+\noindent\textcolor{red}{\textbf{Case PathInvk.} Let}
   $$\textcolor{red}{e = (\angl{J}\new{I}).K?m(\overline{v}) \quad \judgeewf {\Gamma} {e : I_e}}$$
-  $$\textcolor{red}{e' = \angl{I_e}[\overline{\angl{I_x}} \overline{v}/\overline{x}, \angl{I_0}\new{I}/\kwthis]e_0 \quad \judgeewf {\Gamma} {e' : I'_e}}$$
+  $$\textcolor{red}{e' = \angl{I_e}[\overline{\angl{I_x}} \overline{v}/\overline{x}, \angl{I_0}\new{I}/\kwthis]e_0}$$
   $$\textcolor{red}{\mbody(m, I, K) = (I_0, \overline{I_x} \; \overline{x}, I_e \; e_0)}$$
-\textcolor{red}{Since $e$ is well typed, $\angl{J}\new{I}$ is well typed, and}
-  $$\textcolor{red}{\judgeewf {\Gamma} {\angl{J}\new{I} : I}}$$
-\textcolor{red}{By \textsc{(T-Anno)}, we have $I \subtype J$. Also, by \textsc{(T-PathInvk)}, $\judgeewf {\Gamma} {\overline{v} : \overline{I_v} \subtype \overline{I_x}}$.}
+\textcolor{red}{Since $\mbody(m, I, K)$ is defined, the definition of $\mbody$ ensures that $I \subtype I_0$. And since $e$ is well typed, by \textsc{(T-PathInvk)},}
+  $$\textcolor{red}{\judgeewf {\Gamma} {\overline{v} : \overline{I_v} \subtype \overline{I_x}}}$$
 
-\noindent \textcolor{red}{So the first substitution preserves typing, On the other hand, .... the second one also preserves typing. Hence $I'_e \subtype$ type of $e_0 \subtype I_e$.}
+\noindent \textcolor{red}{By \textsc{(T-New)}, \textsc{(T-Anno)} and lemma~\ref{lemma0},}
+  $$\textcolor{red}{\judgeewf {\Gamma} {\angl{I_0}\new{I} : I} \quad \judgeewf {\Gamma, \overline{x} : \overline{I_x}, \kwthis : I_0} {e_0 : I_{e_0} \subtype I_e}}$$
 
+\noindent \textcolor{red}{Hence by lemma~\ref{lemma1}, the substitution preserves typing, thus}
+  $$\textcolor{red}{\judgeewf {\Gamma} {[\overline{\angl{I_x}} \overline{v}/\overline{x}, \angl{I_0}\new{I}/\kwthis]e_0 : I'_{e_0} \subtype I_{e_0} \subtype I_e}}$$
+\noindent \textcolor{red}{By \textsc{(T-Anno)}, $\judgeewf {\Gamma} {e' : I'_{e_0} \subtype I_e}$.}
+
+\begin{comment}
 \noindent \textbf{Case Invk.} 
@@
 
+\end{comment}
 \end{proof}
@@
 \begin{proof}~\\
-\noindent \textbf{Case 1.}
-Given that $e$ is well-typed, by rule \textsc{(T-Invk)}, $\mtype(m, J)$ is defined.
-By rule \textsc{(T-Intf)} for interface $I$,
-    \[ \forall J >: I, m, \mtype(m, J) \text{ is defined } \Rightarrow \mbody(m, I, J) \text{ is defined } \]
-So straightforwardly, we get $ \mbody(m, I, J) = (J', \overline{I_x} \; \overline{x}, I'_E \; e_0) $ and
-         $\num{\overline{x}} = \num{\overline{e}}$ for some $J', \overline{I_x}, \overline{x}, I_e'$ and $e_0$
-
-\noindent \textbf{Case 2 and 3.} Proof for case 2 and 3 is similar to case 1, and we omit it here.
+\noindent \textcolor{red}{TODO. t-pathinvk. t-new. remember canInstantiate() to ensure $e_0$ is not empty.}
 \end{proof}

### 2017-09-19 NewVersion/sections/TypeSafety.tex
more.

@@
 
-\textcolor{red}{
 \begin{lemma}[Method Type Preservation]~\label{lemma2_new}
@@
 \overline{I'_x} = \overline{I_x}$ $\textit{and } I'_e = I_e.$
-\end{lemma}}
+\end{lemma}
 \begin{proof}
 
-Trivial for the case $I'_0 = I_0$.
-And since the lemma has transitivity on subtyping, it suffices to prove the following cases and rely on induction, where we can suppose that $I'_0$ directly extends $I_0$.
+Suppose that $$\mostSpecific(m, I_0, J_0) = \{I\}$$ $$\mostSpecificOverride(m, I_0, I) = \{K\}$$
+$$\mostSpecific(m, I'_0, J_0) = \{I'\}$$ $$\mostSpecificOverride(m, I'_0, I') = \{K'\}$$
 
-Suppose that $$\mostSpecific(m, I_0, J_0) = \{I\}$$ $$\mostSpecificOverride(m, I_0, I) = \{K\}$$
+Below we use $I[m\uparrow J]$ to denote the type of method $m$ defined in $I$ that overrides $J$. We have to prove that $K'[m\uparrow I'] = K[m\uparrow I]$.
+Two facts:
+\begin{itemize}
+	\item A.
+By $\textsc{(T-Intf)}$, $\canOverride$ ensures that an override between any two original methods preserves the method type.
+Formally, $$I_1 \subtype I_2 \ \ \Rightarrow\ \ I_1[m\uparrow I_1] = I_2[m\uparrow I_2]$$
+	\item B. By $\textsc{(T-Method)}$ and $\textsc{(T-AbsMethod)}$, any partial override also preserves method type. Formally,
+	  $$I_1 \subtype I_2\ \ \Rightarrow\ \ I_1[m\uparrow I_2] = I_2[m\uparrow I_2]$$
+\end{itemize}
 
-\textbf{(1) The body of $I'_0$ does not contain $m$.} Trivial because $\mbody(m, I_0, J_0) = \mbody(m, I'_0, J_0)$. \haoyuan{Non-trivial. m may be inherited from other super types. TODO.}
+Since $K \subtype I, K' \subtype I'$, by Fact B, $$K[m\uparrow I] = I[m\uparrow I] \quad K'[m\uparrow I'] = I'[m\uparrow I']$$
 
-\textbf{(2) $m \in \overrideSet(I'_0, I'_0)$.} In that case $I'_0$ defines an original method $m$.
- So
-$$\mostSpecific(m, I'_0, J_0) = \{I'_0\}$$ $$\mostSpecificOverride(m, I'_0, I'_0) = \{I'_0\}$$
-Hence $\mbody(m, I'_0, J_0)$ returns the original $m$ from $I'_0$.
-By $\textsc{(T-Intf)}$, we know that $\canOverride(m, I'_0, I)$ holds, which means that $I'_0$ has the same type as $I$ for $m$.
-On the other hand, from $\textsc{(T-Method)}$ and $\textsc{(T-AbsMethod)}$, the type of $m$ is also preserved between $I$ and $K$ (method override needs to keep the type).
-Finally $\mbody(m, I'_0, J_0)$ has the same type as $\mbody(m, I_0, J_0)$.
-
-\textbf{(3) $m \in \overrideSet(I'_0, I)$.} Similar to (2), $I$ and $K$ have the same type for $m$.
-Moreover, $\textsc{(T-Method)}$ and $\textsc{(T-AbsMethod)}$ also ensure that $I'_0$ and $I$ have the same type for $m$.
-\haoyuan{But findOrigin may no longer be I.}
-
-\textbf{(4) $m \in \overrideSet(I'_0, J)$ for some other $J$.} Same as (1). Such an $m$ does not affect the result of $\mbody$.
-%Straight induction on the derivation of $J \subtype I$. Whether $m$ is defined in $J$ or not, $\mtype(m, J)$ should 
-%be the same as $\mtype(m, K)$ where $J \; \kwextends \; K \{...\}$.
+Hence it suffices to prove that $I'[m\uparrow I'] = I[m\uparrow I]$. Since $I'_0 \subtype I_0$, by the definition of $\mostSpecific$ and $\prune$, $I'$ and $I$
+appear in the same set that is pruned, hence $I' \subtype I$. By Fact A, the proof is done.
 \end{proof}

### 2017-09-19 NewVersion/sections/TypeSafety.tex
Done main part of the proof.

@@
+\haoyuan{For lemma~\ref{lemma1} and Theorem 1, we can have a stricter form. But that is from the design choice that
+we do not accept covariant return types. So we keep it more general at this stage.}
+
 \begin{lemma}~\label{lemma0}
@@
 \begin{lemma}[Method Type Preservation]~\label{lemma2_new}
-$\textit{If } \mbody(m, I_0, J_0) = (K, \overline{I_x}\ \_, I_e\ \_)$, $\mbody(m, I'_0, J_0) = (K', \overline{I'_x}\ \_, I'_e\ \_) \textit{ for some }I'_0 \subtype I_0, \textit{ then }
-\overline{I'_x} = \overline{I_x}$ $\textit{and } I'_e = I_e.$
+$\textit{If } \mbody(m, I_0, J_0) = (K, \overline{I_x}\ \_, I_e\ \_)$, $\textit{Then for any } I'_0 \subtype I_0, \mbody(m, I'_0, J_0) = (K', \overline{I_x}\ \_, I_e\ \_).$
 \end{lemma}
@@
 
+Since $\mbody(m, I_0, J_0)$ is defined, by \textsc{(T-Intf)} we derive that $\mbody(m, I'_0, J_0)$ is also defined.
 Suppose that $$\mostSpecific(m, I_0, J_0) = \{I\}$$ $$\mostSpecificOverride(m, I_0, I) = \{K\}$$
@@
 
-\begin{proof}~\\
+\begin{proof}
+
+\begin{comment}
 \noindent \textbf{Case Var.}
@@
 $e = \new I$ and there are no term for substitution, the conclusion is obvious.
-
-\begin{comment}
 \noindent \textbf{Case Invk.}
@@
 \end{comment}
+~\\
+\indent\textbf{Case PathInvk.} $e = e_0.J_0?m(\overline{e})$. By \textsc{(T-PathInvk)}, suppose
+	$$\judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e_0 : I_0} \quad I_0 \subtype J_0$$
+	$$\mbody(m, I_0, J_0) = (\_, \overline{J}\ \_, I\ \_)$$
+	$$\judgeewf {\Gamma, \overline{x}:\overline{I_x}} {\overline{e} : \overline{I_e}} \quad 
+	  \overline{I_e} \subtype \overline{J} \quad \judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e : I}$$
 
-\noindent\textcolor{red}{\textbf{Case PathInvk.} $e = e_0.J_0?m(\overline{e})$. By \textsc{(T-PathInvk)}, suppose}
-	$$\textcolor{red}{\judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e_0 : I_0} \quad I_0 \subtype J_0}$$
-	$$\textcolor{red}{\mbody(m, I_0, J_0) = (\_, \overline{J}\ \_, I\ \_)}$$
-	$$\textcolor{red}{\judgeewf {\Gamma, \overline{x}:\overline{I_x}} {\overline{e} : \overline{I_e}} \quad 
-	  \overline{I_e} \subtype \overline{J} \quad \judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e : I}}$$
-\textcolor{red}{By induction hypothesis, there are some $I'_0$ and some $\overline{I'_e}$ such that}
-	$$\textcolor{red}{\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0 : I_0'} \quad I_0' \subtype I_0 \subtype J_0}$$
-	$$\textcolor{red}{\judgeewf {\Gamma} {[\overline{y}/\overline{x}]\overline{e} : \overline{I_e'}} \quad 
-	  \overline{I_e'} \subtype \overline{I_e} \subtype \overline{J}}$$   
-\textcolor{red}{By lemma~\ref{lemma2_new}, if $[\overline{y}/\overline{x}]e$ is well typed,}
-	$$\textcolor{red}{\mbody(m, I'_0, J_0) = (\_, \overline{J}\ \_, I\ \_)}$$
-\textcolor{red}{Therefore, by the rule \textsc{(T-Invk)}, 
-	$\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0.m([\overline{y}/\overline{x}]\overline{e}) : I}$.}
+By induction hypothesis, there are some $I'_0$ and some $\overline{I'_e}$ such that
+	$$\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0 : I_0'} \quad I_0' \subtype I_0 \subtype J_0$$
+	$$\judgeewf {\Gamma} {[\overline{y}/\overline{x}]\overline{e} : \overline{I_e'}} \quad 
+	  \overline{I_e'} \subtype \overline{I_e} \subtype \overline{J}$$
+
+By Lemma~\ref{lemma2_new},
+	$$\mbody(m, I'_0, J_0) = (\_, \overline{J}\ \_, I\ \_)$$
+
+Therefore, by the rule \textsc{(T-Invk)}, 
+	$\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0.J_0?m([\overline{y}/\overline{x}]\overline{e}) : I}$.
 
@@
 \begin{proof} ~\\
-\noindent\textcolor{red}{\textbf{Case Invk.} TODO. By t-invk and t-intf.}
+\indent \textbf{Case S-Invk.} Trivial from \textsc{(T-Invk)}, \textsc{(T-PathInvk)} and \textsc{(T-Anno)}, as both $e$ and $e'$ invoke $\mbody(m, J, J)$.
 
-\noindent\textcolor{red}{\textbf{Case PathInvk.} Let}
-  $$\textcolor{red}{e = (\angl{J}\new{I}).K?m(\overline{v}) \quad \judgeewf {\Gamma} {e : I_e}}$$
-  $$\textcolor{red}{e' = \angl{I_e}[\overline{\angl{I_x}} \overline{v}/\overline{x}, \angl{I_0}\new{I}/\kwthis]e_0}$$
-  $$\textcolor{red}{\mbody(m, I, K) = (I_0, \overline{I_x} \; \overline{x}, I_e \; e_0)}$$
-\textcolor{red}{Since $\mbody(m, I, K)$ is defined, the definition of $\mbody$ ensures that $I \subtype I_0$. And since $e$ is well typed, by \textsc{(T-PathInvk)},}
-  $$\textcolor{red}{\judgeewf {\Gamma} {\overline{v} : \overline{I_v} \subtype \overline{I_x}}}$$
+\textbf{Case S-PathInvk.} Let
+  $$e = (\angl{J}\new{I}).K?m(\overline{v}) \quad \judgeewf {\Gamma} {e : I_e}$$
+  $$e' = \angl{I'_e}[\overline{\angl{I_x}} \overline{v}/\overline{x}, \angl{I_0}\new{I}/\kwthis]e_0$$
+  $$\mbody(m, I, K) = (I_0, \overline{I_x} \; \overline{x}, I'_e \; e_0)$$
 
-\noindent \textcolor{red}{By \textsc{(T-New)}, \textsc{(T-Anno)} and lemma~\ref{lemma0},}
-  $$\textcolor{red}{\judgeewf {\Gamma} {\angl{I_0}\new{I} : I} \quad \judgeewf {\Gamma, \overline{x} : \overline{I_x}, \kwthis : I_0} {e_0 : I_{e_0} \subtype I_e}}$$
+Since $\mbody(m, I, K)$ is defined, the definition of $\mbody$ ensures that $I \subtype I_0$. And since $e$ is well typed, by \textsc{(T-PathInvk)},
+  $$\judgeewf {\Gamma} {\overline{v} : \overline{I_v} \subtype \overline{I_x}}$$
 
-\noindent \textcolor{red}{Hence by lemma~\ref{lemma1}, the substitution preserves typing, thus}
-  $$\textcolor{red}{\judgeewf {\Gamma} {[\overline{\angl{I_x}} \overline{v}/\overline{x}, \angl{I_0}\new{I}/\kwthis]e_0 : I'_{e_0} \subtype I_{e_0} \subtype I_e}}$$
-\noindent \textcolor{red}{By \textsc{(T-Anno)}, $\judgeewf {\Gamma} {e' : I'_{e_0} \subtype I_e}$.}
+By \textsc{(T-New)}, \textsc{(T-Anno)} and Lemma~\ref{lemma0},
+  $$\judgeewf {\Gamma} {\angl{I_0}\new{I} : I_0} \quad \judgeewf {\Gamma, \overline{x} : \overline{I_x}, \kwthis : I_0} {e_0 : I_{e_0} \subtype I'_e}$$
+
+Hence by Lemma~\ref{lemma1}, the substitution preserves typing, thus
+  $$\judgeewf {\Gamma} {[\overline{\angl{I_x}} \overline{v}/\overline{x}, \angl{I_0}\new{I}/\kwthis]e_0 : I'_{e_0} \subtype I_{e_0} \subtype I'_e}$$
+
+Hence the conditions of \textsc{(T-Anno)} are satisfied, $\judgeewf {\Gamma} {e' : I'_e}$.
+It suffices to prove that $I'_e \subtype I_e$.
+Since $I'_e$ is from $\mbody(m, I, K)$, whereas $I_e$ is from $\mbody(m, J, K)$, by the rule  \textsc{(T-PathInvk)}.
+By $\textsc{(T-Anno)}$ and the condition that $e$ type-checks, we know that $I \subtype J$.
+By Lemma~\ref{lemma2_new}, $I'_e = I_e$.
 
@@
 \subsubsection{Proof for Theorem~\ref{theorem_progress}}
-\begin{proof}~\\
-\noindent \textcolor{red}{TODO. t-pathinvk. t-new. remember canInstantiate() to ensure $e_0$ is not empty.}
+\begin{proof}
+
+Since $e$ is well typed, by \textsc{(T-PathInvk)} and \textsc{(T-Anno)} we know that
+$$I \subtype J\textrm{, and }\mbody(m, J, K) \textrm{ is defined}$$
+
+By Lemma~\ref{lemma2_new}, $\mbody(m, I, K)$ is also defined, and the type checker ensures the expected number of arguments.
+
+On the other hand, $I \subtype K$. By the definition of $\mostSpecific$, $$\mostSpecific(m, I, K) \subseteq \mostSpecific(m, I, I)$$
+
+By \textsc{(T-New)}, $\canOverride(I)$ should be true. By the definition of $\canOverride$, any $J\in\mostSpecific(m, I, I)$ satisfies that
+$\mostSpecificOverride(m, I, J)$ contains only one interface, in which the $m$ that overrides $J$ is a concrete method.
+Therefore $\mbody(m, I, K)$ also provides a concrete method, which finishes the proof.
 \end{proof}

### 2017-09-19 NewVersion/sections/Formalization.tex
refine formalization text

@@
 \subsection{Syntax}
-Figure~\ref{fig:syntax} shows the syntax of \MIM{}. The multiple
+The abstract syntax of \MIM{} interface declarations, method declarations, and expressions is given at Figure~\ref{fig:syntax}. The multiple
 inheritance feature of \MIM{} is inspired by Java 8 interfaces, which support
@@
 closely related to \emph{traits}. To demonstrate how
-unintentional method conflicts are untangled in \MIM{}, we only focus on a small
-subset of the interface model. For example, all the methods declared
+unintentional method conflicts are untangled in \MIM{}, we only focus on a small subset of the interface model. For example, all the methods declared
 in an interface are default methods, that is to say, they always
@@
 
-We use uppercase letters like $I, J, K$ for interface identifiers. 
-Due to multiple inheritance, an interface can have a set of
-super interfaces, where such a set can be empty. Each interface
+The metavariables $I, J, K$ range over interface names; $x$ ranges over variables; $m$ ranges over method names; $e$ ranges over expressions; and $M$ ranges over method declarations.
+Following Featherweight Java, we assume that the set of variables includes the special variable \kwthis, which cannot be used as the name of an argument to a method.
+In order to achieve multiple inheritance, an interface can have a set of
+parent interfaces, where such a set can be empty. Each interface
 has a set of method declarations. Each method body returns
-an expression. As seen in Figure~\ref{fig:syntax}, we have introduced the
+an expression. As shown in Figure~\ref{fig:syntax}, we have introduced the
 \kwoverride{} keyword to override an old implementation of the

### 2017-09-19 NewVersion/sections/Auxiliary.tex
Last review for today
reply marco
refine
remove StaticInvocation
refine auxiliaries
fix
More proof.

@@
 none of them has a subtyping to one another, since all super types have been removed.
+
+% $\begin{array}{l}
+% \InTextDef{15ex}{
+% \mBody(\m,\C_0)
+% }{
+% \override(\methods(\m),
+% \tops(\m,\Cs))
+% }\\
+% \InTextWith{\metaVar{IT}(\C_0) =
+% \ \ann\ \QM{interface}\ \C_0\ \QM{extends}\ \C_1\ldots\C_n}\\
+% \hspace{1.2in}\oC\methods\ \cC \mbox{ and } \C\in\Cs \mbox{ if } \C_i\subtype\C, i\in 1..n
+
+% \end{array}$
+
+% \noindent The definition of $\mBody$ reconstructs the full set of supertypes $\Cs$ and then delegates the work to two other auxiliary functions:
+%  $\tops(m,\Cs)$ and $\override(\method,\methods)$.
 
@@
     \inferrule* [left=]
-    { set1 = \; \{K\mid I <: K, \; K <: J\; $and$\; m \in \overrideSet(K, K) \} \\
-        set2 = \; \{K\mid  J <: K \; $and$\; m \in \overrideSet(K, K) \} }
-    {\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
-                $prune(set1)$ & if $set1$ is not empty \\ $prune(set2)$ & otherwise
-            \end{tabular}}\right.}
+    { originalIntfs = \; \{K \mid \subt{I}{K}, \; \subt{K}{J} \; \lor \; \subt{J}{K}, \; $and$\; m \in \overrideSet(K, K) \} }
+    {\mostSpecific(m, I, J) = \prune(originalIntfs) }
 
     \inferrule* [left=]
-        { set = \; \{ K\mid I <: K, \; K <: J\; $and$ \;
+        { overrideIntfs = \; \{ K\mid I <: K, \; K <: J\; $and$ \;
             m \in \overrideSet(K, J)  \} }
-        {\mostSpecificOverride(m, I, J) = prune(set)}
+        {\mostSpecificOverride(m, I, J) = \prune(overrideIntfs)}
 
-    prune(set) = \{I \in set \; | \; \nexists J \in set\setminus I, J <: I\}
+    \prune(set) = \{I \in set \; | \; \nexists J \in set\setminus I, J <: I\}
 
-    \inferrule* [left=]
-    {   \interface{I}{I}{M}
-        \\ J \in \overline{I} }
-    {\ext(I, J) \marco{Is this ever used?}}
+    % \inferrule* [left=]
+    % {   \interface{I}{I}{M}
+    %     \\ J \in \overline{I} }
+    % {\ext(I, J) \marco{Is this ever used?} \yanlin{Previously used, new version not used.}}
 
@@
     {m \in \overrideSet(I, J)}
+
+      \inferrule* [left=]
+    {   \kwinterface \; I \; \kwextends \; \overline{I} \; \{ I_e \; m(\overline{I_x} \; \overline{x}) \;
+        	\kwoverride \; I \ldots \} \\
+        \kwinterface \; J \; \kwextends \; \overline{J} \; \{ I_e \; m(\overline{I_x} \; \overline{y}) \;
+      	    \kwoverride \; J \ldots \} \\
+    }
+    {\canOverride(m, I, J)}
     \end{mathpar}
@@
 The algorithm is decribed below:
+
+$$\forall m, \forall J \in \mostSpecific(m, I, I), $$
 \begin{enumerate}
-\item Suppose $\mostSpecific(m, I, I) = \overline{J}$, where $\overline{J}$ is a list of interfaces.
+\item For any $m$, suppose $\mostSpecific(m, I, I) = \overline{J}$, where $\overline{J}$ is a list of interfaces.
 \item If $\forall J_i \in \overline{J}, if \mostSpecificOverride(m, I, J_i) = \{ K \} $ and $m$ in $K$ is not abstract, 
@@
 
+\begin{comment}
 \subsection{$\mbodyStatic$}
@@
         {  %\mostSpecific(m, I, I) = \{J\} \\
-            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_e}{m}{I_x}{x}{J}{e_0}\ldots\}}
+            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_e}{m}{I_x}{x}{J'}{e_0}\ldots\}}
         {\mbodyStatic(m, J, J') = (J, \overline{I_x} \; \overline{x}, I_e \; e_0)}
@@
         {  %\mostSpecific(m, I, I) = \{J\} \\
-            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\absmethod{I_e}{m}{I_x}{x}{J}\ldots\}}
+            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\absmethod{I_e}{m}{I_x}{x}{J'}\ldots\}}
         {\mbodyStatic(m, J, J') = (J, \overline{I_x} \; \overline{x}, I_e \; \o)}
 \end{mathpar}    
+\end{comment}
 

### 2017-09-20 NewVersion/sections/Formalization.tex
refine formalization text

@@
 In this section, we present the formal model \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}) , based on
-Featherweight Java~\cite{Igarashi01FJ}. We use the same
-conventions as FJ; $\overline{I}$ is shorthand for the (possibly empty)
-list $I_1, ..., I_n$, which may be indexed by $I_i$.
-The syntax, typing rules, and small-step semantics are presented below.
+Featherweight Java~\cite{Igarashi01FJ}. The syntax, typing rules, and small-step semantics are presented below.
 
@@
 Following Featherweight Java, we assume that the set of variables includes the special variable \kwthis, which cannot be used as the name of an argument to a method.
+We use the same
+conventions as FJ; we write $\overline{I}$ as shorthand for a possibly empty sequence $I_1, ..., I_n$, which may be indexed by $I_i$; and write $\overline{M}$ as shorthand for $M_1 ..
+M_n$ (with no commas).
+We also abbreviate operations on pairs of sequences in the obvious way, writing $\overline{I} \; \overline{x}$ for $I_1 \; x_1, ..., I_n \; x_n$, where $n$ is the length of $\overline{I}$ and $\overline{x}$.
+
 In order to achieve multiple inheritance, an interface can have a set of 
-parent interfaces, where such a set can be empty. Each interface
-has a set of method declarations. Each method body returns
+parent interfaces, where such a set can be empty.
+The interface declaration $\interface{I}{I}{M}$ introduces an interface named $I$ with parent interfaces $\overline{I}$ and a suite of methods $\overline{M}$.
+The methods of $I$ may either override methods that are already defined in $\overline{I}$ or add new functionality special to $I$, we will illustrate this in more detail later.
+
+Each method body returns
 an expression. As shown in Figure~\ref{fig:syntax}, we have introduced the

### 2017-09-20 NewVersion/sections/Formalization.tex
more refine

@@
 
-Each method body returns
-an expression. As shown in Figure~\ref{fig:syntax}, we have introduced the
+The method declaration $\method{I}{m}{I_x}{x}{J}{e}$ introduces a method named $m$ with result type $I$, parameters $\overline{x}$ of type $\overline{I_x}$ and the overriding target $J$.
+The body of the method is the single statement $ \kwreturn \; e;$.
+We also allow defining abstract methods with $\absmethod{I}{m}{I_x}{x}{J}$, which is similar as normal method but without a method body.
+Notebly, We have introduced the
 \kwoverride{} keyword to override an old implementation of the
@@
 Expressions can be standard constructs such as variables, method
-invocation, or object creation. A novel type of expressions are path-invocations like
-``$e.I\pathIvk m(\overline{e})$'', meaning that the dynamically bound
-implementation for method $m$ should be along the path $I$. Another
-interesting expression are super-invocations, which enable a method to access an old
-implementation from the specified super type. Hence a super-invocation
-can only be used inside an interface definition.
+invocation, or object creation.
+\name{} allows two types of method invocations, one is the normal method invocation $e.m(\overline{e})$ that we are familiar with, another is the novel type of expressions: path-invocations like ``$e.I\pathIvk m(\overline{e})$'', meaning that the dynamically bound
+implementation for method $m$ should be along the path $I$. 
+% Another interesting expression are super-invocations, which enable a method to access an old implementation from the specified super type.
+Hence a super-invocation can only be used inside an interface definition.
 Finally, an expression can also be annotated with its static type. But \emph{annotated expressions are only intended for the semantic rules},

### 2017-09-27 NewVersion/sections/TypeSafety.tex
Done proof. To have explanation in text.

@@
-\haoyuan{For lemma~\ref{lemma1} and Theorem 1, we can have a stricter form. But that is from the design choice that
-we do not accept covariant return types. So we keep it more general at this stage.}
-
-\begin{lemma}~\label{lemma0}
+\begin{lemma}~\label{lemma:return_expr_typing}
 % $\textit{If } \mtype(m, I, J) = \overline{D} \rightarrow D, \textit{ and } \mbody(m, I, J) = \overline{x}.e, 
@@
 %  \judgeewf {\overline{x}:\overline{D}, \kwthis:J_0} {e:C} $.
-$\textit{If } \mbody(m, I, J) = (J', \overline{I_x} \; \overline{x}, I_e \; e), 
- \textit{ then for some } J_0 \textit{ with } I <: J_0, \  \exists I' <: I_e, \textit{ such that }  
- \judgeewf {\overline{x}:\overline{I_x}, \kwthis:J_0} {e : I'} $.
+If $\mbody(m, I_d, I_s) = (J, \overline{I_x} \; \overline{x}, I_e \; e_0)$, then
+ $\judgeewf {\overline{x}:\overline{I_x}, \kwthis:J} {e_0 : I_0}$ for some $I_0 \subtype I_e$.
 \end{lemma}
 
- \begin{proof}~\\
- $\textit{The base case: if } m \textit{ is defined in } I, \textit{ then it is easy since } m 
- \textit{ is defined in } I \textit{ and } 
- \judgeewf {\overline{x}:\overline{I_x}, \kwthis : I} {e : I_e}, \textit{by the rule \textsc{(T-Method)}}.
- \textit{The induction step is also straightforward.} 
- $ 
+\begin{proof}
+By the definition of $\mbody$, the target method $m$ is found in $J$. By the method typing rule \textsc{(T-Method)}, there exists some 
+$I_0 \subtype I_e$ such that $\judgeewf {\overline{x}:\overline{I_x}, \kwthis:J} {e_0 : I_0}$. 
 \end{proof}
 
-\begin{lemma}[Method Type Preservation]~\label{lemma2_new}
-$\textit{If } \mbody(m, I_0, J_0) = (K, \overline{I_x}\ \_, I_e\ \_)$, $\textit{Then for any } I'_0 \subtype I_0, \mbody(m, I'_0, J_0) = (K', \overline{I_x}\ \_, I_e\ \_).$
+\begin{lemma}[Weakening]~\label{lemma:weakening}
+	If $\judgeewf {\Gamma} {e : I}$, then $\judgeewf {\Gamma, x : J} {e : I}$.
+\end{lemma}
+
+\begin{proof}
+Straightforward induction.
+\end{proof}
+
+\begin{lemma}[Method Type Preservation]~\label{lemma:mbody_type_preservation}
+If $\mbody(m, I_0, J_0) = (K, \overline{I_x}\ \_, I_e\ \_)$, then for any $I'_0 \subtype I_0$, $\mbody(m, I'_0, J_0) = (K', \overline{I_x}\ \_, I_e\ \_)$.
 \end{lemma}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{lemma}[Term Substitution Preserves Typing]~\label{lemma1}
-$\textit{If } \ \judgeewf {\Gamma, \ \overline{x}:\overline{I_x}} { e : I } \textit{ , and }
-\judgeewf {\Gamma} {\overline{y}:\overline{I_y}} \textit{ where } \overline{I_y} \subtype \overline{I_x}
-\textit{, then } \judgeewf {\Gamma} {[\overline{y}/\overline{x}]e : I'} \textit{ for some } I' \subtype I.
-$
+\begin{lemma}[Term Substitution Preserves Typing]~\label{lemma:subst_type_preservation}
+If $\judgeewf {\Gamma, \overline{x}:\overline{I_x}} { e : I }$, and
+$\judgeewf {\Gamma} {\overline{y}:\overline{I_x}}$, then
+$\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e : I}$.
 
@@
 \end{comment}
-~\\
-\indent\textbf{Case PathInvk.} $e = e_0.J_0?m(\overline{e})$. By \textsc{(T-PathInvk)}, suppose
+We prove by induction. The expression $e$ has the following cases:
+
+\textbf{Case Var.} Let $e = x$. If $x \notin \overline{x}$, then the substitution does not change anything. Otherwise,
+since $\overline{y}$ have the same types as $\overline{x}$, it immediately finishes the case.
+
+\textbf{Case Invk.} Let $e = e_0.m(\overline{e})$. By \textsc{(T-Invk)} we can suppose that
+	$$\judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e_0 : I_0} \quad \mbody(m, I_0, I_0) = (\_, \overline{J}\ \_, I\ \_)$$
+	$$\judgeewf {\Gamma, \overline{x}:\overline{I_x}} {\overline{e} : \overline{I_e}} \quad 
+	\overline{I_e} \subtype \overline{J} \quad \judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e : I}$$
+
+By induction hypothesis, 
+	$$\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0 : I_0} \quad
+	  \judgeewf {\Gamma} {[\overline{y}/\overline{x}]\overline{e} : \overline{I_e}}$$
+
+Again by \textsc{(T-Invk)}, $\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e : I}$.
+
+\textbf{Case PathInvk.} $e = e_0.J_0?m(\overline{e})$. By \textsc{(T-PathInvk)}, suppose
 	$$\judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e_0 : I_0} \quad I_0 \subtype J_0$$
@@
 
-By induction hypothesis, there are some $I'_0$ and some $\overline{I'_e}$ such that
-	$$\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0 : I_0'} \quad I_0' \subtype I_0 \subtype J_0$$
-	$$\judgeewf {\Gamma} {[\overline{y}/\overline{x}]\overline{e} : \overline{I_e'}} \quad 
-	  \overline{I_e'} \subtype \overline{I_e} \subtype \overline{J}$$
+By induction hypothesis, 
+$$\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0 : I_0} \quad
+\judgeewf {\Gamma} {[\overline{y}/\overline{x}]\overline{e} : \overline{I_e}}$$
 
-By Lemma~\ref{lemma2_new},
-	$$\mbody(m, I'_0, J_0) = (\_, \overline{J}\ \_, I\ \_)$$
+Again by \textsc{(T-PathInvk)}, $\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e : I}$.
 
-Therefore, by the rule \textsc{(T-Invk)}, 
-	$\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0.J_0?m([\overline{y}/\overline{x}]\overline{e}) : I}$.
+\textbf{Case New.} Straightforward.
+
+\textbf{Case Anno.} Straightforward by induction hypothesis and \textsc{(T-Anno)}.
 
@@
 \begin{proof} ~\\
-\indent \textbf{Case S-Invk.} Trivial from \textsc{(T-Invk)}, \textsc{(T-PathInvk)} and \textsc{(T-Anno)}, as both $e$ and $e'$ invoke $\mbody(m, J, J)$.
+\indent \textbf{Case S-Invk.} Let
+   $$e = (\angl{J}\new{I}).m(\overline{v}) \quad \judgeewf {\Gamma} {e : I_e}$$
+   $$e' = (\angl{J}\new{I}).J?m(\overline{v})$$
+
+Since $e$ is well-typed, $\angl{J}\new{I}$ is also well-typed. By \textsc{(T-Anno)},
+  $$\judgeewf {\Gamma} {\angl{J}\new{I} : J} \quad I \subtype J$$
+
+By \textsc{(T-Invk)} on $e$,
+  $$\mbody(m, J, J) = (\_, \overline{I_x}\ \_, I_e\ \_) \quad \judgeewf {\Gamma} {\overline{v} : \overline{I_v}} \quad \overline{I_v}  \subtype \overline{I_x}$$
+
+At this moment, \textsc{(T-PathInvk)} is immediately applicable by the above conditions, including that $e'$ also invokes $\mbody(m, J, J)$. Hence $\judgeewf {\Gamma} {e' : I_e}$.
 
@@
   $$e = (\angl{J}\new{I}).K?m(\overline{v}) \quad \judgeewf {\Gamma} {e : I_e}$$
-  $$e' = \angl{I'_e}[\overline{\angl{I_x}} \overline{v}/\overline{x}, \angl{I_0}\new{I}/\kwthis]e_0$$
-  $$\mbody(m, I, K) = (I_0, \overline{I_x} \; \overline{x}, I'_e \; e_0)$$
+  $$e' = \angl{I_{e_0}}[\overline{\angl{I_x}} \overline{v}/\overline{x}, \angl{I_0}\new{I}/\kwthis]e_0$$
+  $$\mbody(m, I, K) = (I_0, \overline{I_x} \; \overline{x}, I_{e_0} \; e_0)$$
 
-Since $\mbody(m, I, K)$ is defined, the definition of $\mbody$ ensures that $I \subtype I_0$. And since $e$ is well typed, by \textsc{(T-PathInvk)},
-  $$\judgeewf {\Gamma} {\overline{v} : \overline{I_v} \subtype \overline{I_x}}$$
+Since $\mbody(m, I, K)$ is defined, the definition of $\mbody$ ensures that $I \subtype I_0$. And since $e$ is well-typed, by \textsc{(T-PathInvk)},
+  $$\judgeewf {\Gamma} {\overline{v} : \overline{I_v}} \quad \overline{I_v} \subtype \overline{I_x}$$
 
-By \textsc{(T-New)}, \textsc{(T-Anno)} and Lemma~\ref{lemma0},
-  $$\judgeewf {\Gamma} {\angl{I_0}\new{I} : I_0} \quad \judgeewf {\Gamma, \overline{x} : \overline{I_x}, \kwthis : I_0} {e_0 : I_{e_0} \subtype I'_e}$$
+By the rules \textsc{(T-Anno)} and  \textsc{(T-New)},
+  $$\judgeewf {\Gamma} {\overline{\angl{I_x}}\overline{v} : \overline{I_x}} \quad \judgeewf {\Gamma} {\angl{I_0}\new{I} : I_0}$$
 
-Hence by Lemma~\ref{lemma1}, the substitution preserves typing, thus
-  $$\judgeewf {\Gamma} {[\overline{\angl{I_x}} \overline{v}/\overline{x}, \angl{I_0}\new{I}/\kwthis]e_0 : I'_{e_0} \subtype I_{e_0} \subtype I'_e}$$
+On the other hand, by Lemma~\ref{lemma:return_expr_typing},
+  $$\judgeewf {\overline{x} : \overline{I_x}, \kwthis: I_0} {e_0 : I'_{e_0}} \quad I'_{e_0} \subtype I_{e_0}$$
 
-Hence the conditions of \textsc{(T-Anno)} are satisfied, $\judgeewf {\Gamma} {e' : I'_e}$.
-It suffices to prove that $I'_e \subtype I_e$.
-Since $I'_e$ is from $\mbody(m, I, K)$, whereas $I_e$ is from $\mbody(m, J, K)$, by the rule  \textsc{(T-PathInvk)}.
+By Lemma~\ref{lemma:weakening},
+  $$\judgeewf {\Gamma, \overline{x} : \overline{I_x}, \kwthis: I_0} {e_0 : I'_{e_0}}$$
+
+Hence by Lemma~\ref{lemma:subst_type_preservation}, the substitution preserves typing, thus
+  $$\judgeewf {\Gamma} {[\overline{\angl{I_x}} \overline{v}/\overline{x}, \angl{I_0}\new{I}/\kwthis]e_0 : I'_{e_0}}$$
+
+Since $I'_{e_0} \subtype I_{e_0}$, the conditions of \textsc{(T-Anno)} are satisfied, hence $\judgeewf {\Gamma} {e' : I_{e_0}}$.
+Now we only need to prove that $I_{e_0} = I_e$.
+Since $I_{e_0}$ is from $\mbody(m, I, K)$, whereas $I_e$ is from $\mbody(m, J, K)$, by the rule  \textsc{(T-PathInvk)}.
 By $\textsc{(T-Anno)}$ and the condition that $e$ type-checks, we know that $I \subtype J$.
-By Lemma~\ref{lemma2_new}, $I'_e = I_e$.
+By Lemma~\ref{lemma:mbody_type_preservation}, $I_{e_0} = I_e$.
+
+\textbf{Case C-Receiver.} Straightforward induction.
+
+\textbf{Case C-PathReceiver.} Straightforward induction.
+
+\textbf{Case C-Args.} Straightforward induction.
+
+\textbf{Case C-PathArgs.} Straightforward induction.
+
+\textbf{Case C-StaticType.} Immediate by \textsc{(T-Anno)}.
+
+\textbf{Case C-FReduce.} Immediate by \textsc{(T-Anno)} and induction.
+
+\textbf{Case C-AnnoReduce.} Immediate by \textsc{(T-Anno)} and transitivity of $\subtype$.
 
@@
 
-Since $e$ is well typed, by \textsc{(T-PathInvk)} and \textsc{(T-Anno)} we know that
+Since $e$ is well-typed, by \textsc{(T-PathInvk)} and \textsc{(T-Anno)} we know that
 $$I \subtype J\textrm{, and }\mbody(m, J, K) \textrm{ is defined}$$
 
-By Lemma~\ref{lemma2_new}, $\mbody(m, I, K)$ is also defined, and the type checker ensures the expected number of arguments.
+By Lemma~\ref{lemma:mbody_type_preservation}, $\mbody(m, I, K)$ is also defined, and the type checker ensures the expected number of arguments.
 

### 2017-09-27 NewVersion/sections/Formalization.tex
refine s3 text

@@
 invocation, or object creation.
-\name{} allows two types of method invocations, one is the normal method invocation $e.m(\overline{e})$ that we are familiar with, another is the novel type of expressions: path-invocations like ``$e.I\pathIvk m(\overline{e})$'', meaning that the dynamically bound
+\name{} allows two types of method invocations, one is the normal method invocation $e.m(\overline{e})$ that we are familiar with, another is the novel type of method invocation: path-invocations like ``$e.I\pathIvk m(\overline{e})$'', meaning that the dynamically bound
 implementation for method $m$ should be along the path $I$. 
@@
 In short, subtyping relations are built from the inheritance in interface
-declarations. Subtyping is both reflexive and transitive.
+declarations. Subtyping is both symmetric, reflexive and transitive.
 
@@
 
-\begin{figure*}[t]
+\begin{figure}[t]
 \saveSpaceFig
@@
 	\subtrans \hspace{.5in} \subextends \\
+
 	\framebox{$ \judgeewf \Gamma {e:I} $} \hspace{.5in}
@@
 \end{mathpar}
+\caption{Typing Rules of \name{}.}
 \label{fig:typingrules}
 \saveSpaceFig
-\end{figure*}
+\end{figure}
 

### 2017-09-30 NewVersion/paper.tex
change
Marco first commit for formalization
Abstract

--- 2017-06-18 Aplas17/paper.tex
@@
 
-% \newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
-% \newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
-% \newcommand\marco[1]{\authornote{marco}{blue}{#1}}
-% \newcommand\haoyuan[1]{\authornote{haoyuan}{orange}{#1}}
+ \newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
+ \newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
+ \newcommand\marco[1]{\authornote{marco}{blue}{#1}}
+ \newcommand\marcoT[1]{\authorText{blue}{#1}}
+ \newcommand\haoyuan[1]{\authornote{haoyuan}{orange}{#1}}
 
-\newcommand\bruno[1]{}
-\newcommand\yanlin[1]{}
-\newcommand\marco[1]{}
-\newcommand\haoyuan[1]{}
+%\newcommand\bruno[1]{}
+%\newcommand\yanlin[1]{}
+%\newcommand\marco[1]{}
+%\newcommand\haoyuan[1]{}
+
+\newcommand\saveSpaceFig{\vspace{-2ex}}
 
@@
 Programming. However, it is also tricky to get right, as illustrated by
-the extensive literature on the topic. One of the most promising 
+the extensive literature on the topic. A key issue 
+is the \emph{ambiguity} arising from inheriting multiple parents,
+which can have conflicting methods and fields. 
+Numerous existing work provides solutions for 
+conflicts which arise from \emph{diamond inheritance}: i.e.
+conflicts that arise from implementations sharing a common 
+ancestor. However, most mechanisms are inadequate to deal 
+with \emph{unintentional method conflicts}: conflicts which 
+arise from two unrelated methods that happen to share the same name
+and signature.
+
+\begin{comment}
+One of the most promising 
 approaches to multiple inheritance is the \emph{trait} model. Traits offer a
 restricted model of multiple inheritance that is easy to reason and 
-has many elegant properties. Traits have good support for method 
+have many elegant properties. Traits have good support for method 
 conflicts which arise from \emph{diamond inheritance}:
@@
 and signature. 
+\end{comment}
 
-This paper presents a new model \name{} 
-(short for \emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}) 
-that deals with unintentional
-method conflicts. In our new model, conflicting methods arising
-from unrelated methods can coexist in the same component. Moreover, they
-can be \emph{independently overridden}. What ensures unambiguity 
-is the use of information about the class hierarchy. In turn, 
-hierarchical information is also employed in method dispatching, which 
-uses a combination of static and dynamic type information to choose 
-the implementation of a method at run-time. We give illustrative 
-examples of our language and features and formalize \name{} as a minimal 
-Featherweight-Java style calculus.
+This paper presents a new model called \emph{\textbf{F}eatherweight
+  \textbf{H}ierarchical \textbf{J}ava} (\name{}) that deals with
+unintentional method conflicts.
+In our
+new model, conflicting methods arising from unrelated methods can
+coexist in the same component. Furthermore our model supports
+\emph{hierarchical method overriding}: that is, methods can be
+\emph{independently overridden} along the multiple inheritance
+hierarchy. To avoid ambiguity, hierarchical information is 
+employed in method dispatching, which uses a combination of static and
+dynamic type information to choose the implementation of a method at
+run-time. We give illustrative examples of our language and features
+and formalize \name{} as a minimal Featherweight-Java style calculus.
+
+\begin{comment}
+Furthermore we discuss similarities and differences to
+
+What ensures unambiguity is the use of information about
+the class hierarchy.
+
+\name{} is partly inspired by the method resolution semantics
+of C++, but it also incoorporates ideas from the trait model and Java
+8's default methods. We discuss the similarities
+and differences with and also advantages and disadvantages. 
+\end{comment}
 
@@
 \input{sections/Introduction.tex}
-
 \input{sections/Overview.tex}
-
 \input{sections/Formalization.tex}
 \input{sections/Auxiliary.tex}
-% \input{sections/TypeSafety.tex}
-
-% \input{sections/Implementation.tex}
-
-\input{sections/CaseStudy.tex}
-
+\input{sections/Discussion.tex}
 \input{sections/RelatedWork.tex}
-
 \input{sections/Conclusion.tex}

### 2017-09-30 NewVersion/sections/Introduction.tex
Introduction

@@
 and mixins~\cite{bracha90mixin} to offer a disciplined form of multiple inheritance. Java 8 
-offers a simple variant of traits with disguised of interfaces with default methods~\cite{goetz12fdefenders}.
+offers a simple variant of traits, disguised of interfaces with default methods~\cite{goetz12fdefenders}.
 
@@
 \textit{diamond problem}~\cite{Sak89dis,Singh1995} (also known as ``fork-join inheritance''~\cite{Sak89dis}). 
-In the diamond problem, inheritance could allow
+In the diamond problem, inheritance allows
 one feature to be inherited from multiple parent classes that share a
-common ancestor, hence
+common ancestor. Hence
 conflicts arise. The variety of strategies for resolving such conflicts
@@
 including traits, mixins, CZ~\cite{malayeri2009cz}, and many others. Existing
-languages and research have taken care of this case extensively. Other issues
+languages and research have addressed the issue of diamond inheritance extensively. Other issues
 including how multiple inheritance deals with state, 
@@
 
-In contrast with the diamond inheritance, the second case of ambiguity
+In contrast with diamond inheritance, a second case of ambiguity
 is \textit{unintentional method conflicts}~\cite{scharli03traits}. That is conflicting 
@@
 the conflicting methods have very different meanings and do not share a
-common parent. We call such a case ``\textit{triangle inheritance}''.
-\haoyuan{Fine to have a graph with diamond and triangle shapes if we got space.}
+common parent. We call such a case \textit{triangle inheritance}, in
+analogy to diamond inheritance.
 
-Unintentional method conflicts are less common than the diamond
-problem, nonetheless, they have severe effects in practice if not handled properly. 
+%Unintentional method conflicts are perhaps less common than the diamond
+%problem.
+
+When unintentional method conflicts happen, they can have severe
+effects in practice if no
+appropriate mechanisms to deal with them are available. 
 Unfortunately, such an issue has not received much formal study 
 before. In practice, existing languages only provide limited support for
-it. In most languages, the mechanisms available to deal with this problem are the same as the diamond
+the issue. In most languages, the mechanisms available to deal with this problem are the same as the diamond
 inheritance. However, this is often inadequate and can lead 
@@
 when it is necessary to combine two large modules and their features,
-but the inheritance is simply prohibited by a small conflict. As
-a workaround from the diamond inheritance side, it is possible to
+but the inheritance is simply prohibited by a small conflict. 
+As a workaround from the diamond inheritance side, it is possible to
 define a new method in the child class to override those conflicting
-methods. Intuitively using one method to fuse two unrelated features
-is unsatisfactory. Therefore we need a better solution to keep both
+methods. However, using one method to fuse two unrelated features
+is clearly unsatisfactory. Therefore we need a better solution to keep both
 features separately during inheritance, so as not to break
@@
 
-Some other workarounds or approaches include delegation and
-renaming/exclusion in the trait model. Yet they still have various
-drawbacks as we will discuss in Section~\ref{sec:overview}. Closest to our work
-are mechanisms available in C++ and C\# that allow for two
+Closest to our work are mechanisms available in C++ and C\# that allow for two
 unintentionally conflicting methods to coexist in a class. Among them, 
@@
 that programmers can only use either static or dynamic dispatching separately, but dealing
-with unintentional method conflicts seems to require a combination of both.
+with unintentional method conflicts seems to require a combination of
+both. 
+Some other workarounds or approaches include delegation and
+renaming/exclusion in the trait model. Yet they still have various
+drawbacks as we will discuss in Section~\ref{sec:overview}.
+\bruno{The previous paragraph needs to be revised to better discuss the
+  limitations of the C++ approach. Yanlin, Marco can you have a look
+  at this?}
 
@@
 
-This paper proposes \textit{hierarchical dispatch}: a novel approach
+This paper proposes \textit{hierarchical dispatching}: a novel approach
 to method dispatching, which combines static and dynamic
@@
 \textit{hierarchical overriding}, where method overriding can be applied
-only to one branch of the class hierarchy. Our model can be viewed as
-a generalization of the simplified trait model by providing additional support to
-the triangle inheritance.
+only to one branch of the class hierarchy. 
+\name{} is partly inspired by the method resolution semantics
+of C++, but it also incoorporates ideas from the trait model and Java
+8's default methods.
+
+%%Our model can be viewed as
+%%a generalization of the simplified trait model by providing additional support to
+%%the triangle inheritance.
 
@@
           methods to override on individual branches of the class hierarchy.
-	\item \textbf{\name:} a formalized model based on Featherweight Java, supporting the above features. Some theorems and their proofs
-	are attached to confirm the type soundness of the model.
-	\item \textbf{Prototype implementation\footnote{Available in supplementary material attached to the submission.}:} a simple interpreter implemented in Scala that follows our formalization rules, incorporating parsing, type-checking and semantic evaluation.
+	\item \textbf{\name:} a formalized model based on
+          Featherweight Java, supporting the above features. 
+          We provide the static and dynamic semantics, and prove the
+          type soundness of the model.
+	\item \textbf{Prototype implementation\footnote{Available in
+              supplementary material attached to the submission.}:} a
+          simple implementation of \MIM{} implemented in Scala.
+          \bruno{Are the examples in the paper implemented in the interpreter?}
 \end{itemize}

### 2017-09-30 NewVersion/sections/Introduction.tex
Introduction

@@
 multiple inheritance from the start. Scala adapts the ideas from traits~\cite{scharli03traits}
-and mixins~\cite{bracha90mixin} to offer a disciplined form of multiple inheritance. Java 8 
+and mixins~\cite{bracha90mixin}\bruno{please add more references to
+  other work on traits and mixins here} to offer a disciplined form of multiple inheritance. Java 8 
 offers a simple variant of traits, disguised of interfaces with default methods~\cite{goetz12fdefenders}.
@@
 
-In contrast with diamond inheritance, a second case of ambiguity
+In contrast to diamond inheritance, a second case of ambiguity
 is \textit{unintentional method conflicts}~\cite{scharli03traits}. That is conflicting 
@@
 Some other workarounds or approaches include delegation and
-renaming/exclusion in the trait model. Yet they still have various
-drawbacks as we will discuss in Section~\ref{sec:overview}.
+renaming/exclusion in the trait model. However renaming/exclusion 
+can break the subtyping relation between a subclass and its parent.
+This is not adequate for the class model commonly used in mainstream 
+OOP languages, where the subclass is always expected to be a subtype 
+of the parent class.
+
+%%Yet they still have various
+%%drawbacks as we will discuss in Section~\ref{sec:overview}.
 \bruno{The previous paragraph needs to be revised to better discuss the
@@
 to method dispatching, which combines static and dynamic
-information. Using hierarchical dispatch, the method binder will look
+information. Using hierarchical dispatching, the method binder will look
 at both the \emph{static type} and the \emph{dynamic type} of the

### 2017-09-30 NewVersion/sections/Overview.tex
Section 2.1

--- 2017-06-18 Aplas17/sections/Overview.tex
@@
 signature, but with different semantics and functionality. This
-situation is troublesome to programmers that use multiple
+situation is troublesome for programmers that use multiple
 inheritance. Below we illustrate with a running example called
@@
   \item It allows multiple inheritance.
-  \item Every method represents a behaviour and requires a body for its implementation (like Java 8 default methods). There are no abstract methods.
+  \item Every method represents a behaviour and requires a body for
+    its implementation (like Java 8 default methods). 
   \item It can be directly instantiated by the \lstinline|new| keyword.
 \end{itemize}
-Furthermore for simplicity, our examples and formalization do not deal with state at
-this stage. %%, but that should not block our discussions below.
+Furthermore, similarly to traits or Java 8 with default methods,
+interfaces cannot have state.\bruno{I rephrased this sentence}
+
+%%for simplicity, our examples and formalization do not deal with state at
+%%this stage. %%, but that should not block our discussions below.
 
@@
 \end{lstlisting}\vspace{3pt}
+\bruno{The code calls getStack(), but that method is not defined! 
+If you want to present a compelling example, please make sure that 
+the code makes sense! I suppose that getStack() would be an abstract method?
+}
 Note that both methods have \lstinline|void| return type (we will not formalize
@@
 explicitly override the old ones. However, the two conflicting methods have totally different functionalities, merging
-them into one does not make any sense. This non-solution will hide the old methods and break independent extensibility. The
-feature we expect is called ``triangle inheritance'', that is to say, when the conflicting methods serve for different behaviours,
-we can allow them to coexist in the extending interface in a type-safe way.\\
+them into one does not make any sense. This non-solution will hide the
+old methods and break independent extensibility.
 
-\noindent\textbf{Potential Fixes} There are several workarounds that come to our mind:
+\noindent\textbf{Potential Fixes} There are several other workarounds
+that come to our mind. We briefly discuss those potential fixes and
+workarounds next:
 \begin{itemize}
@@
   both preserved, the ambiguity of method call is resolved by static dispatch.
-  Qualified names are used to specify the branch to give the right implementation.
+  Qualified names are used to specify the branch to give the right
+  implementation.\bruno{don't forget to readjust text with what we
+    have learned about C++.}
 \end{itemize}
 
-\noindent\textbf{Our solution:} below is our code that shows the triangle
+\noindent\textbf{Our solution:} 
+The feature we expect is called \emph{triangle inheritance}, that is
+to say, when the conflicting methods serve for different behaviours,
+we can allow them to coexist in the extending interface in a type-safe way.
+Below is our code that shows the triangle
 inheritance.
 We can define \lstinline|DrawableDeck| by inheriting \lstinline|Drawable| and \lstinline|Deck| together while
-type safety is ensured. Again it is slightly different from our prototype as we do not model \lstinline|void| or statements;
-the code is just for illustration.
+type safety is ensured. 
+%%Again it is slightly different from our prototype as we do not model \lstinline|void| or statements;
+%%the code is just for illustration.
 \vspace{3pt}\begin{lstlisting}
@@
 \end{lstlisting}\vspace{3pt}
+\bruno{Please ensure that the syntax we use in the examples, matches 
+up with the syntax in the formalization. In particular make sure that
+the syntax for the various types of method calls are the same.}
+\bruno{You don't actually explain your code! Please explain what the
+  code does, and what are the different types of calls
+  involved. Introduce some terminology here, namely the names for the 
+different types of calls.}
+
+\noindent\textbf{A comparison with C++:} 
 Note that both cases in the above code are valid in C++ for disambiguation. As shown by \lstinline|func|, C++ looks at
@@
 casts in \name{}. C++ further allows explicit casts.
-
 In the following text, we will see that C++ is still unsatisfactory, as it introduces another problem on code reuse, which motivates
-our work.
+our work.\bruno{Please revise.}
 
@@
 \begin{figure*}[t]
+\saveSpaceFig
   \centering
@@
   \caption{UML graph for \lstinline|DrawableLoggingDeck|.}\label{fig:drawableloggingdeck}
+\saveSpaceFig
 \end{figure*}

### 2017-09-30 NewVersion/sections/Overview.tex
Section 2

@@
 \subsection{Problem 2: Dynamic Dispatch for Code Reuse}\label{subsec:problem2}
-
-\bruno{Emphasizing hierarchical dispatch and triangle inheritance.}\haoyuan{Done}
-On the other hand, we also need dynamic dispatch as it is essential and widely used in Object-Oriented programming.
+Dynamic dispatching is essential and widely used in Object-Oriented programming.
 C++ has the flexibility for choosing either way of dispatch by the \kwvirtual{} keyword.
@@
 In that case, \lstinline|shuffleAndDraw| needs to be adapted to the new \lstinline|draw|. But due to static dispatch,
-it still refers to the old \lstinline|draw| in \lstinline|Deck|. Thus programmers have to copy the \lstinline|shuffleAndDraw| code in
+it still refers to the old \lstinline|draw| in
+\lstinline|Deck|\bruno{Is this discussion up-to-date? Please revise
+  the discussion in view of what we know about C++ now.}. Thus programmers have to copy the \lstinline|shuffleAndDraw| code in
 \lstinline|LoggingDeck|. It requires a lot of redundant work if we have to duplicate all such methods. Hence in order for code reuse,

### 2017-09-30 NewVersion/sections/Formalization.tex
Early Sections in Section 3

--- 2017-09-20 NewVersion/sections/Formalization.tex
@@
 \section{Formalization}~\label{sec:formalization}
-In this section, we present the formal model \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}) , based on
-Featherweight Java~\cite{Igarashi01FJ}. The syntax, typing rules, and small-step semantics are presented below.
+In this section, we present the formal model \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), based on
+Featherweight Java~\cite{Igarashi01FJ}. The syntax, typing rules,
+small-step semantics and type soundness proofs are presented.
 
@@
 
-The method declaration $\method{I}{m}{I_x}{x}{J}{e}$ introduces a method named $m$ with result type $I$, parameters $\overline{x}$ of type $\overline{I_x}$ and the overriding target $J$.
-The body of the method is the single statement $ \kwreturn \; e;$.
-We also allow defining abstract methods with $\absmethod{I}{m}{I_x}{x}{J}$, which is similar as normal method but without a method body.
-Notebly, We have introduced the
+The method declaration $\method{I}{m}{I_x}{x}{J}{e}$ introduces a
+method named $m$ with result type $I$, parameters $\overline{x}$ of
+type $\overline{I_x}$ and the overriding target $J$. The body of the
+method is the single statement $ \kwreturn \; e;$. We also allow
+defining abstract methods with $\absmethod{I}{m}{I_x}{x}{J}$, which is
+similar to a normal method but without a method body. Notably, we have introduced the
 \kwoverride{} keyword to override an old implementation of the
@@
 typing, well-formedness of methods and interfaces. As a convention, an environment
-$\Gamma$ is maintained to store the types of variables, together with ``this'' type, namely
+$\Gamma$ is maintained to store the types of variables, together with
+the ``this'' type, namely
 the enclosing type. The three rules for method invocation, \textsc{(T-Invk)}, \textsc{(T-PathInvk)} and \textsc{(T-SuperInvk)}
@@
 an auxiliary function \mtype. \mtype{} is the function for looking up method types, which we will
-illustrate later in Section~\ref{subsec:auxdefs}. After the method type is obtained, they all check that arguments and the receiver
+illustrate later in Section~\ref{subsec:auxdefs}. After the method
+type is obtained, they all check that the arguments and the receiver
 have compatible types. Additionally, \textsc{(T-PathInvk)} requires the receiver to be the subtype of the specified
@@
 
-Finally, \textsc{(T-Invk)} defines interface checking. The condition helps to ensure unambiguity and type soundness of the calculus. We will
+Finally, \textsc{(T-Intf)} defines interface checking. The
+condition\bruno{Well, there are two conditions. I suggest you explain
+  in a bit more detail the 2 conditions, since this rule seems to be
+  the more complex one. Some examples may help.} helps to ensure unambiguity and type soundness of the calculus. We will
 introduce \mbody{} and some counter-examples later. But intuitively, if $\mbody(m,I,J)$ is defined, that means $\new{I}.J::m()$ is not
@@
 
-\begin{figure*}[t]
+\bruno{Explanation for T-Anno is missing}
+
+\begin{figure*}
 \saveSpaceFig
@@
 \saveSpaceFig
+\caption{Typing and subtyping of \name{}.}
 \end{figure*}

### 2017-09-30 NewVersion/sections/Formalization.tex
refine S3

--- 2017-09-27 NewVersion/sections/Formalization.tex
@@
 typing, well-formedness of methods and interfaces. As a convention, an environment
-$\Gamma$ is maintained to store the types of variables, together with ``this'' type, namely
-the enclosing type. The three rules for method invocation, \textsc{(T-Invk)}, \textsc{(T-PathInvk)} and \textsc{(T-SuperInvk)}
-are very similar, in the sense that they all check the type of the specific method, by using
-an auxiliary function \mtype. \mtype{} is the function for looking up method types, which we will
-illustrate later in Section~\ref{subsec:auxdefs}. After the method type is obtained, they all check that arguments and the receiver
-have compatible types. Additionally, \textsc{(T-PathInvk)} requires the receiver to be the subtype of the specified
-path type, and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.
+$\Gamma$ is maintained to store the types of variables, together with the type of \kwthis{}, namely the enclosing type.
+We abbreviate typing judgements on sequences in the obvious way, writing $\judgeewf \Gamma {\overline{e}:\overline{I}}$ as shorthand for $\judgeewf \Gamma {e_1:I_1}, \judgeewf \Gamma {e_2:I_2}, ..., \judgeewf \Gamma {e_n:I_n}$ and writing $\subt{\overline{I}}{\overline{J}}$ as shorthand for $\subt{I_1}{J_1}, \subt{I_2}{J_2}, ..., \subt{I_n}{J_n}$.
+
+There are two typing rules for method invocation: \textsc{(T-Invk)} and \textsc{(T-PathInvk)}.
+\textsc{(T-Invk)} is the typing judgement for a normal method invocation, which is similar to Featherweight Java.
+It checks the type of the specific method, by using an auxiliary function \mbody.
+\mbody is the function for looking up methods, which we will illustrate later in Section~\ref{subsec:auxdefs}.
+After the method type is obtained, we check that arguments and the receiver have compatible types.
+\textsc{(T-PathInvk)} is the typing judgement for a path invocation.
+Besides the conditions of \textsc{(T-PathInvk)}, \textsc{(T-PathInvk)} requires the receiver to be the subtype of the specified
+path type. 
+% and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.
+
+\textsc{(T-New)} is the typing rule for object creation $\new{I}$.
+The auxiliary function $\canInstantiate(I)$ checks whether interface $I$ can be instantiated or not.
+If interface $I$ contains (or inherits) any abstract method that has not been implemented, then interface $I$ cannot be instantiated.
 
@@
 
-Finally, \textsc{(T-Invk)} defines interface checking. The condition helps to ensure unambiguity and type soundness of the calculus. We will
+Finally, \textsc{(T-Invk)} defines interface checking.
+The condition helps to ensure unambiguity and type soundness of the calculus.
+Firstly, we check that all method $\overline{M}$ defined in $I$ type checks.
+
+We will
 introduce \mbody{} and some counter-examples later. But intuitively, if $\mbody(m,I,J)$ is defined, that means $\new{I}.J::m()$ is not

### 2017-09-30 NewVersion/sections/Formalization.tex

--- 2017-09-30 NewVersion/sections/Formalization.tex
@@
 path type, and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.
+
+There are two typing rules for method invocation: \textsc{(T-Invk)} and \textsc{(T-PathInvk)}.
+\textsc{(T-Invk)} is the typing judgement for a normal method invocation, which is similar to Featherweight Java.
+It checks the type of the specific method, by using an auxiliary function \mbody.
+\mbody is the function for looking up methods, which we will illustrate later in Section~\ref{subsec:auxdefs}.
+After the method type is obtained, we check that arguments and the receiver have compatible types.
+\textsc{(T-PathInvk)} is the typing judgement for a path invocation.
+Besides the conditions of \textsc{(T-PathInvk)}, \textsc{(T-PathInvk)} requires the receiver to be the subtype of the specified
+path type. 
+% and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.
+
+\textsc{(T-New)} is the typing rule for object creation $\new{I}$.
+The auxiliary function $\canInstantiate(I)$ checks whether interface $I$ can be instantiated or not.
+If interface $I$ contains (or inherits) any abstract method that has not been implemented, then interface $I$ cannot be instantiated.
 
@@
 \end{mathpar}
+\caption{Typing Rules of \name{}.}
 \label{fig:typingrules}

### 2017-10-02 NewVersion/sections/Overview.tex

--- 2017-06-18 Aplas17/sections/Overview.tex
@@
   \item It allows multiple inheritance.
-  \item Every method represents a behaviour and requires a body for its implementation (like Java 8 default methods). There are no abstract methods.
-  \item It can be directly instantiated by the \lstinline|new| keyword.
+  \item Every method is either abstract or implemented to represent a behavior (like Java 8 default methods). 
+  \item The \lstinline|new| keyword is used to instantiate an interface.
 \end{itemize}
-Furthermore for simplicity, our examples and formalization do not deal with state at
-this stage. %%, but that should not block our discussions below.
+Furthermore, similarly to traits or Java 8 with default methods,
+interfaces cannot have state.
+
+%%for simplicity, our examples and formalization do not deal with state at
+%%this stage. %%, but that should not block our discussions below.
 
@@
 can be drawn and also includes a method called \lstinline|draw| for
-visual display. For illustration, the implementation of
+visual display. For simple illustration, the default implementation of
 \lstinline|draw| in \lstinline|Drawable| only creates a blank canvas
-on the screen, and later some instances (\lstinline|Circle|,
-\lstinline|Square|, or others) that extend \lstinline|Drawable| may
-define their own \lstinline|drawObject| methods and invoke
-\lstinline|draw|.
+on the screen, while the \lstinline|draw| in \lstinline|Deck| simply
+prints out a message.
 
@@
   void draw() { // draws a card from the Deck
-    Stack<Card> cards = this.getStack();
-    if (!cards.isEmpty()) { Card card = cards.pop(); ... }
+    println("Draw a card.");
   }
 }
+
 interface Drawable {
-  void draw() { // draws something on the screen
-    JFrame frame = new JFrame("Canvas");
+  JFrame draw() { // draws something on the screen
+    JFrame frame = new JFrame();
     frame.setVisible(true);
-    ...
+    return frame;
   }
@@
 \end{lstlisting}\vspace{3pt}
-Note that both methods have \lstinline|void| return type (we will not formalize
-\lstinline|void| in our calculus afterwards; here it is only for illustration). 
-In \lstinline|Deck|, \lstinline|draw| tries to get the cards as a stack, pops
-out the top card, and so on. While in \lstinline|Drawable|, \lstinline|draw|
-creates a blank canvas using \lstinline|JFrame|. Now, a programmer is designing a
+Note that the two \lstinline|draw| methods have the same names and parameter types,
+but the return types can be different. In \lstinline|Deck|, \lstinline|println| is a
+library function, loaded by the prelude for example. Since the only operation is messaging,
+the method has \lstinline|void| return type (we could define an interface called \lstinline|Void|
+and return an object of it instead; in many languages it is simply a primitive type). On the other hand, for \lstinline|Drawable|
+the program has to create a blank canvas by \lstinline|JFrame|, again a pre-defined type:
+
+\vspace{3pt}\begin{lstlisting}
+interface JFrame {
+  void setVisible(boolean b) {...}
+  ...
+}
+\end{lstlisting}\vspace{3pt}
+Now, a programmer is designing a
 card game with GUI. He may want to draw a deck on the screen, so he defines a drawable
@@
 components and to achieve code reuse, as supported by many mainstream OO
-languages. Nevertheless at this point, languages like Java simply throw a compile
-error on \lstinline|DrawableDeck|, since the two \lstinline|draw| methods cause a conflict, though accidentally.
+languages. Nevertheless at this point, languages like Java simply treat the two \lstinline|draw| methods
+as the same, and hence throw a compile error on \lstinline|DrawableDeck| about the conflict, though accidentally.
 
@@
 explicitly override the old ones. However, the two conflicting methods have totally different functionalities, merging
-them into one does not make any sense. This non-solution will hide the old methods and break independent extensibility. The
-feature we expect is called ``triangle inheritance'', that is to say, when the conflicting methods serve for different behaviours,
-we can allow them to coexist in the extending interface in a type-safe way.\\
+them into one does not make any sense. This non-solution will hide the
+old methods and break independent extensibility.
 
-\noindent\textbf{Potential Fixes} There are several workarounds that come to our mind:
+\subsection{Potential Fixes}
+
+There are several other workarounds
+that come to our mind. We briefly discuss those potential fixes and
+workarounds next:
 \begin{itemize}
   \item \textbf{I. Delegation.} As an alternative to multiple inheritance,
-  delegation can be used by introducing two fields with
+  delegation can be used by introducing two fields (or field methods) with
   \lstinline|Drawable| type and \lstinline|Deck| type,
@@
   \item \textbf{IV. Static dispatch.} Some other languages like C++ have
-  direct support for the triangle inheritance. While conflicting methods are
-  both preserved, the ambiguity of method call is resolved by static dispatch.
-  Qualified names are used to specify the branch to give the right implementation.
+  direct support for the triangle inheritance. For instance, C++ allows both
+  conflicting methods to coexist, and resolves the ambiguity by static dispatch:
+  \vspace{3pt}\begin{lstlisting}[language=c++]
+  class Deck { public: void draw() {...} };
+  class Drawable { public: JFrame draw() {...} };
+  class DrawableDeck : public Drawable, public Deck {};
+
+  // in main
+  DrawableDeck d;
+  d.Deck::draw(); // prints the message
+  \end{lstlisting}\vspace{3pt}
 \end{itemize}
 
-\noindent\textbf{Our solution:} below is our code that shows the triangle
-inheritance.
-We can define \lstinline|DrawableDeck| by inheriting \lstinline|Drawable| and \lstinline|Deck| together while
-type safety is ensured. Again it is slightly different from our prototype as we do not model \lstinline|void| or statements;
-the code is just for illustration.
-\vspace{3pt}\begin{lstlisting}
-interface DrawableDeck extends Drawable, Deck {}
-interface Foo {
-  void func(Deck obj) { obj.draw(); }
-}
-// main program
-DrawableDeck d = new DrawableDeck();
-new DrawableDeck().Drawable::draw();      // calling draw in Drawable
-new Foo().func(new DrawableDeck());       // calling draw in Deck
-\end{lstlisting}\vspace{3pt}
-Note that both cases in the above code are valid in C++ for disambiguation. As shown by \lstinline|func|, C++ looks at
-the static type of the receiver for static dispatching. Normally we can define such a method \lstinline|func| for ``implicit''
-casts in \name{}. C++ further allows explicit casts.
+So far it seems that static dispatch is the simplest and most straightforward approach,
+as long as the language model accepts unintentionally conflicting methods. However, dynamic
+dipatching appears to be more common in OO programming in order for code reuse. Following the previous example,
+we reimplement \lstinline|Deck| with more features:
 
-In the following text, we will see that C++ is still unsatisfactory, as it introduces another problem on code reuse, which motivates
-our work.
-
-\subsection{Problem 2: Dynamic Dispatch for Code Reuse}\label{subsec:problem2}
-
-\bruno{Emphasizing hierarchical dispatch and triangle inheritance.}\haoyuan{Done}
-On the other hand, we also need dynamic dispatch as it is essential and widely used in Object-Oriented programming.
-C++ has the flexibility for choosing either way of dispatch by the \kwvirtual{} keyword.
-Unfortunately, this approach is still unsatisfactory regarding code reuse. For instance, 
-we redefine \lstinline|Deck| to support
-both \lstinline|draw| and another operation called \lstinline|shuffleAndDraw|:
 \vspace{3pt}\begin{lstlisting}
@@
   void draw() {...}
+  void shuffle() {...}
   void shuffleAndDraw() { shuffle(); draw(); }
-  ...
 }
 \end{lstlisting}\vspace{3pt}
-\lstinline|shuffleAndDraw| is a typical method that invokes \lstinline|draw| in its definition. In principle, we want
-that invocation to use dynamic dispatch, because a programmer may define a subtype of \lstinline|Deck| and override \lstinline|draw|:
+Here \lstinline|shuffleAndDraw| is a typical method that invokes \lstinline|draw| in its definition. Ideally,
+we want that invocation to be dynamically dispatched. This is important, because a programmer may define a subtype
+of \lstinline|Deck| and override the method:
+
 \vspace{3pt}\begin{lstlisting}
-interface LoggingDeck extends Deck {
+interface SafeDeck extends Deck {
+  boolean isEmpty() {...}
   void draw() { // overriding
-    Stack<Card> cards = this.getStack();
-    if (!cards.isEmpty()) {
-      Card card = cards.pop();
-      println("The card is: " + card.toString());
-      ...
-    } else println("Empty deck.");
+    if (isEmpty()) println("The deck is empty.");
+    else println("Draw a card");
   }
@@
 \end{lstlisting}\vspace{3pt}
-In that case, \lstinline|shuffleAndDraw| needs to be adapted to the new \lstinline|draw|. But due to static dispatch,
-it still refers to the old \lstinline|draw| in \lstinline|Deck|. Thus programmers have to copy the \lstinline|shuffleAndDraw| code in
-\lstinline|LoggingDeck|. It requires a lot of redundant work if we have to duplicate all such methods. Hence in order for code reuse,
-we cannot just rely on static dispatch. However, as seen before, dynamic dispatch would take us back to problem 1, for instance, when we
+With static dispatch, it is tedious but we have to copy the \lstinline|shuffleAndDraw| code into \lstinline|SafeDeck|,
+for the adaption to the new \lstinline|draw|. Yet dynamic dispatching immediately saves us from the duplicate work,
+since the method becomes automatically adaptive. Nevertheless, as seen before, dynamic dispatch would take us back to problem
+1, for instance, when we
 have the UML in Figure~\ref{fig:drawableloggingdeck} and the following code:
-\vspace{3pt}\begin{lstlisting}
-interface DrawableLoggingDeck extends Drawable, LoggingDeck {...}
-// main program
-DrawableLoggingDeck d = new DrawableLoggingDeck();
-d.shuffleAndDraw(); // ambiguous draw if dynamically dispatched
-\end{lstlisting}\vspace{3pt}
 
 \begin{figure*}[t]
+	\saveSpaceFig
 	\centering
@@
 	\caption{UML graph for \lstinline|DrawableLoggingDeck|.}\label{fig:drawableloggingdeck}
+	\saveSpaceFig
 \end{figure*}
-\noindent If we try to keep the triangle inheritance while applying dynamic dispatch, calling \lstinline|shuffleAndDraw| would trigger ambiguity. 
-In principle, we want \lstinline|shuffleAndDraw| to invoke \lstinline|LoggingDeck.draw| because they belong to the same branch, 
-nonetheless, choosing either static dispatch
-or dynamic dispatch cannot ensure both the triangle inheritance and code reuse. As far as we know, C++ does not have a solution
-to it. Therefore we need to find another algorithm for method resolution.\\
 
-\noindent\textbf{Our solution:} we propose \textit{hierarchical dispatch} for method lookup. A qualified
-method invocation in our model, for instance, \lstinline|e.I::m()|, is read as
+\vspace{3pt}\begin{lstlisting}
+interface DrawableSafeDeck extends Drawable, SafeDeck {}
+
+// main program
+DrawableSafeDeck d = new DrawableSafeDeck();
+d.shuffleAndDraw(); // ambiguous draw if dynamically dispatched
+\end{lstlisting}\vspace{3pt}
+From \lstinline|DrawableSafeDeck|'s point of view, the \lstinline|draw| method seems ambiguous. But ideally we would
+like \lstinline|shuffleAndDraw| to invoke \lstinline|SafeDeck.draw| because they belong to the same branch. Hence it
+seems that we choose dynamic dispatch but also make use of some static type information. Note that this problem can be
+solved by the C++ code below:
+\vspace{3pt}\begin{lstlisting}
+class Deck { public: virtual void draw() {...} ... };
+class Drawable {...};
+class SafeDeck : public Deck { public: virtual void draw() {...} ... };
+class DrawbaleSafeDeck : public Drawable, public SafeDeck {};
+
+// in main
+DrawableSafeDeck d;
+d.shuffleAndDraw();
+\end{lstlisting}\vspace{3pt}
+By putting ``\lstinline|virtual|'' in front of every method signature, we are enforcing dynamic dispatch in C++.\\
+
+\noindent\textbf{Our solution:} inspired by that, we propose \textit{hierarchical dispatch} in our model
+as the default method lookup algorithm. A \textit{hierarchical invocation}, or \textit{path invocation}, namely
+\lstinline|e.I?m()|, is read as
 ``finding the most specific method \lstinline|m| along the path
-\lstinline|I|''. The meaning of ``along the path \lstinline|I|'' is
-that, if the result of \dispatch{} is \lstinline|J.m()| for some \lstinline|J|, then such a \lstinline|J| must be a super type of \lstinline|e|'s dynamic type, and \lstinline|J| has a subtyping relation with \lstinline|I| (either \lstinline|J <: I| or \lstinline|J >: I|).
-Intuitively, the most specific \lstinline|m()| must be from branch \lstinline|I|, but it can be an updated version after \lstinline|I| because of dynamic dispatch.
+\lstinline|I|''. Formally, the meaning of ``along the path \lstinline|I|'' is
+that, if the result of hierarchical dispatch finds \lstinline|J.m()| for some \lstinline|J|, then such a \lstinline|J| must be a super type of \lstinline|e|'s dynamic type for sure, and \lstinline|J| must have a subtyping relation with \lstinline|I| (either \lstinline|J <: I| or \lstinline|J >: I|).
+Intuitively, the most specific \lstinline|m| must be from branch \lstinline|I|, but it can be an updated version after \lstinline|I| because of dynamic dispatch.
 The formal definition will be introduced later.
 
-On the other hand, \lstinline|e.m()| where \lstinline|e| has static type \lstinline|I|, simply behaves the same as \lstinline|e.I::m()| in our model.
-Such a dispatch algorithm makes use of both the static type and the dynamic type of the receiver, so it is a combination of static and dynamic dispatch.
+On the other hand, \lstinline|e.m()| where \lstinline|e| has static type \lstinline|I|, simply behaves the same as \lstinline|e.I?m()| in our model.
+Such a dispatching algorithm makes use of both the static type and the dynamic type of the receiver, so it is seemingly a combination of static and dynamic dispatch.
 Intuitively, the static type specifies one branch to avoid ambiguity, and the dynamic type finds the latest version on that branch.
@@
 
-Back to the example, we can write \lstinline|"this.Deck::draw()"| inside the implementation of \lstinline|shuffleAndDraw|, and on \lstinline|d.shuffleAndDraw()| it automatically dispatches to \lstinline|LoggingDeck.draw()|.
-Furthermore, the following code
-also behaves as expected:
+Back to the example, our code below just suffices to meet the expectation:
 \vspace{3pt}\begin{lstlisting}
@@
   void draw() {...}
+  void shuffle() {...}
   void shuffleAndDraw() { shuffle(); draw(); }
-  ...
 }
-\end{lstlisting}\vspace{3pt}
-It is because the compiler is able to know that the receiver ``\lstinline|this|'' exactly has static type \lstinline|Deck|. Hence hierarchical dispatch eliminates ambiguity.
+interface Drawable {...}
+interface SafeDeck extends Deck {...}
+interface DrawableSafeDeck extends Drawable, SafeDeck {}
+
+// main program
+new DrawableSafeDeck().shuffleAndDraw() // calls Deck.shuffle, and then SafeDeck.draw
+\end{lstlisting}\vspace{3pt}\haoyuan{mention how the language syntax is different from our formalization. FHJ is only a subset.}
+Note that the \lstinline|draw()| in \lstinline|shuffleAndDraw()| is short for \lstinline|this.draw()|, and is equivalent to \lstinline|this.Deck?draw()|.
+It is because the compiler is able to know that the receiver ``\lstinline|this|'' exactly has static type \lstinline|Deck|.
+Hence hierarchical dispatch eliminates ambiguity in a concise way.\\
+
+\noindent\textbf{Comparison with C++:} as an industrial language, C++ is more practical and flexible to use with lots of features, for example, it handles fields and virtual inheritance, and it allows explicit casts.
+But the compilation is more or less complicated, and sometimes unclear to programmers, which affects its type safety and people's understanding.
+The compilation seems to look into the expressions and the real (runtime) types for ambiguity check in method dispatching, and sometimes the errors are thrown by the linker.
+In contrast, inspired by C++ we formalize the concept of hierarchical dispatch in our model, with type-checking rules and semantics.
+The compilation only cares about the type of the receiver in method invocation, but the rules ensure type soundness so that the evaluation never throws errors on a program that type-checks.
+C++ does not hold type soundness for unintentional method conflicts, it actually accepts the diamond inheritance, and only complains on bad invocations.
+Whereas our model forbids the diamond case, which derives a strong type-safe system, and there are more theoretical aspects in Section~\ref{sec:formalization}.
+\haoyuan{not sure if this paragraph makes sense or is correct.
+Needs refs.}
 

### 2017-10-03 NewVersion/sections/Formalization.tex
Some metarule improvements
tmp

@@
 are invoked recursively and alternately to produce a single value in
-the end. The small-step semantics rules \textsc{(S-Invk)},
-\textsc{(S-PathInvk)} and \textsc{(S-SuperInvk)} behave similarly:
-each corresponds to one kind of method invocation. They all invoke
-\mbody{} for method body lookup. Generally, one can understand
+the end. The small-step semantics rules \textsc{(S-Invk)} and 
+\textsc{(S-PathInvk)} behave similarly: each corresponds to one kind of method invocation.
+\textsc{(S-PathInvk)} invokes \mbody{} for method body lookup.
+The parameters $\overline{x}$ are replaced with arguments $\overline{v}$ with static type annotations $\overline{\angl{I_x}}$, where $\overline{\angl{I_x}}$ is the parameter types coming from method lookup result.
+The rule \textsc{(S-Invk)} simply reduces the problem of normal invocation to path invocation.
+
+Generally, one can understand
 $\mbody(m, I, J)$ in a way that it finds the most specific body of

### 2017-10-03 NewVersion/sections/Auxiliary.tex

@@
 Figure~\ref{fig:auxfunc}. To begin with, we
-introduce the basic functions: $\ext, \overrideSet$ and $\prune$. $\ext(I, J)$
+introduce the basic functions: $\ext, I.m\,\kwoverride\,J$ and $\prune$. $\ext(I, J)$
 simply indicates that interface $I$ directly extends interface $J$. 
 $\overrideSet(I, J)$ returns a set of methods defined in $I$ that have ``$\kwoverride \; J$''
-in their signatures. Notice that $\overrideSet(I, I)$ is a special representative of
+in their signatures. \marco{text need to change since notation is changed.} Notice that $\overrideSet(I, I)$ is a special representative of
 the ``originally-defined'' method set from $I$. The $\prune$ function takes a set of
@@
     \inferrule* [left=]
-    { originalIntfs = \; \{K \mid \subt{I}{K}, \; \subt{K}{J} \; \lor \; \subt{J}{K}, \; $and$\; m \in \overrideSet(K, K) \} }
-    {\mostSpecific(m, I, J) = \prune(originalIntfs) }
+    { origins = \; \{K \mid \subt{I}{K}, \; \subt{K}{J} \; \lor \; \subt{J}{K}, \; $and$\; K.m\,\kwoverride\,K \} }
+    {\mostSpecific(m, I, J) = \prune(origins) }
 
     \inferrule* [left=]
-        { overrideIntfs = \; \{ K\mid I <: K, \; K <: J\; $and$ \;
-            m \in \overrideSet(K, J)  \} }
-        {\mostSpecificOverride(m, I, J) = \prune(overrideIntfs)}
+        { overrides = \; \{ K\mid I <: K, \; K <: J\; $and$ \;
+            K.m\,\kwoverride\,J  \} }
+        {\mostSpecificOverride(m, I, J) = \prune(overrides)}
 
@@
         \kwoverride \; J \ldots \} }
-    {m \in \overrideSet(I, J)}
+    {I.m\,\kwoverride\,J}
 

### 2017-10-03 NewVersion/sections/Overview.tex

@@
 \lstinline|draw| in \lstinline|Drawable| only creates a blank canvas
-on the screen, while the \lstinline|draw| in \lstinline|Deck| simply
+on the screen, while the \lstinline|draw| method in \lstinline|Deck| simply
 prints out a message.
@@
 Note that the two \lstinline|draw| methods have the same names and parameter types,
-but the return types can be different. In \lstinline|Deck|, \lstinline|println| is a
-library function, loaded by the prelude for example. Since the only operation is messaging,
-the method has \lstinline|void| return type (we could define an interface called \lstinline|Void|
-and return an object of it instead; in many languages it is simply a primitive type). On the other hand, for \lstinline|Drawable|
-the program has to create a blank canvas by \lstinline|JFrame|, again a pre-defined type:
-
+but the return types can be different. In \lstinline|Deck|,
+\lstinline|draw| uses \lstinline|println|, which is a
+library function. 
+The method returns \lstinline|void|. Note that \lstinline|void| is
+unsupported in our formalization, but we could have also defined an interface called \lstinline|Void|
+and return an object of that type instead. For the method \lstinline|draw| in
+\lstinline|Drawable|
+the program has to create a blank canvas by \lstinline|JFrame|, which
+is a pre-defined type.
+\begin{comment}
 \vspace{3pt}\begin{lstlisting}
@@
 \end{lstlisting}\vspace{3pt}
+\end{comment}
 Now, a programmer is designing a
@@
 \end{lstlisting}\vspace{3pt}
-The point of using multiple inheritance is surely for composing the features from various 
+The point of using multiple inheritance is for composing the features from various 
 components and to achieve code reuse, as supported by many mainstream OO
 languages. Nevertheless at this point, languages like Java simply treat the two \lstinline|draw| methods
-as the same, and hence throw a compile error on \lstinline|DrawableDeck| about the conflict, though accidentally.
+as the same, and hence they throw a compile error on \lstinline|DrawableDeck| about the conflict, though accidentally.
 
-Now one may quickly come up with a workaround, which is creating a new \lstinline|draw| method in \lstinline|DrawableDeck| to
-explicitly override the old ones. However, the two conflicting methods have totally different functionalities, merging
+Now one may quickly come up with a workaround, which is to create a new \lstinline|draw| method in \lstinline|DrawableDeck| to
+explicitly override the old ones. However, the two conflicting methods
+have totally different functionalities. Therefore merging
 them into one does not make any sense. This non-solution will hide the
@@
 
-\subsection{Potential Fixes}
-
+\paragraph{{\bf Potential Fixes:}}
 There are several other workarounds
@@
 
+\bruno{Why have we eliminated problem 2 and included it in Problem 1?
+Also why are we not showing how to actually solve it with our approach
+now? I what we had previously made more sense. Please finish up this
+section; show our solution, mention that is is quite similar (and
+inspired by C++), but finish it saying that there are other problems
+that C++ does not address.}
+\subsection{Problem 2: Dynamic Dispatching}
 So far it seems that static dispatch is the simplest and most straightforward approach,
 as long as the language model accepts unintentionally conflicting methods. However, dynamic
-dipatching appears to be more common in OO programming in order for code reuse. Following the previous example,
+dispatching appears to be more common in OO programming in order for code reuse. Following the previous example,
 we reimplement \lstinline|Deck| with more features:
@@
 \end{lstlisting}\vspace{3pt}
-With static dispatch, it is tedious but we have to copy the \lstinline|shuffleAndDraw| code into \lstinline|SafeDeck|,
-for the adaption to the new \lstinline|draw|. Yet dynamic dispatching immediately saves us from the duplicate work,
+With static dispatch, we have to copy the \lstinline|shuffleAndDraw| code into \lstinline|SafeDeck|,
+for the adaptation to the new \lstinline|draw|. Yet dynamic dispatching immediately saves us from the duplicate work,
 since the method becomes automatically adaptive. Nevertheless, as seen before, dynamic dispatch would take us back to problem

### 2017-10-03 NewVersion/sections/Auxiliary.tex
Done 4.1 - 4.3/

--- 2017-09-06 NewVersion/sections/Auxiliary.tex
@@
-\section{Auxiliary Definitions}\label{subsec:auxdefs}
-In this section, we present the auxiliary definitions used in our formalization in 
-Figure~\ref{fig:auxfunc}. To begin with, we
-introduce the basic functions: $\ext, \overrideSet$ and $\prune$. $\ext(I, J)$
-simply indicates that interface $I$ directly extends interface $J$. 
-$\overrideSet(I, J)$ returns a set of methods defined in $I$ that have ``$\kwoverride \; J$''
-in their signatures. Notice that $\overrideSet(I, I)$ is a special representative of
-the ``originally-defined'' method set from $I$. The $\prune$ function takes a set of
-types, and filters out those that have subtypes in the same set. Finally in the returned set,
-none of them has a subtyping to one another, since all super types have been removed.
+\section{Fundamental Notations}\label{subsec:auxdefs}
+In this section, we present the fundamental notations used in our formalization.
+Some of them are auxiliary functions, others are however important ones as they
+directly implement our algorithm for method resolution.
+
+\subsection{Auxiliary functions}
+To begin with, we introduce the following basic functions.
+
+\begin{flalign*}
+	& \rhd \textit{Definition of } I[m\ \kwoverride\ J]: & \\
+	& \bullet I[m\ \kwoverride\ J] = \method{I_e}{m}{I_x}{x}{J}{e_0} & \\
+	& \indent\indent \textrm{with: }
+	  \kwinterface \; I \; \kwextends \; \overline{I} \; \{ \method{I_e}{m}{I_x}{x}{J}{e_0} \ldots \} & \\
+	& \bullet I[m\ \kwoverride\ J] = \absmethod{I_e}{m}{I_x}{x}{J} & \\
+	& \indent\indent \textrm{with: }
+	\kwinterface \; I \; \kwextends \; \overline{I} \; \{ \absmethod{I_e}{m}{I_x}{x}{J} \ldots \} & \\
+\end{flalign*}
+Here $I[m\ \kwoverride\ J]$ is basically a directly lookup for method $m$ in the body of $I$, where such a method
+overrides $J$. The method can be either concrete or abstract, and the body of definition is returned. Notice that
+by our syntax, $I[m\ \kwoverride\ I]$ is looking for the originally-defined method $m$ in $I$.
+
+\begin{flalign*}
+	& \rhd \textit{Definition of } \prune(set): & \\
+	& \bullet \prune(set) = \{I \in set \; | \; \nexists J \in set\setminus I, J <: I\} &
+\end{flalign*}
+The $\prune$ function takes a set of
+types, and filters out those that have subtypes in the same set. In the returned set,
+none of them has subtyping relation to one another, since all super types have been removed.
+
+\begin{flalign*}
+	& \rhd \textit{Definition of } \canOverride(m, I, J): & \\
+	& \bullet \canOverride(m, I, J) = True & \\
+	& \indent\indent \textrm{with: } I[m\ \kwoverride\ I] = I_e \; m(\overline{I_x} \; \overline{x}) \; \kwoverride \; I \ldots & \\
+	& \hspace{.77in} J[m\ \kwoverride\ J] = I_e \; m(\overline{I_x} \; \overline{y}) \; \kwoverride \; J \ldots &
+\end{flalign*}
+$\canOverride$ just checks that two original $m$ in $I$ and $J$ have the same type.
 
@@
 
-    \inferrule* [left=]
-    { set1 = \; \{K\mid I <: K, \; K <: J\; $and$\; m \in \overrideSet(K, K) \} \\
-        set2 = \; \{K\mid  J <: K \; $and$\; m \in \overrideSet(K, K) \} }
-    {\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
-                $prune(set1)$ & if $set1$ is not empty \\ $prune(set2)$ & otherwise
-            \end{tabular}}\right.}
-
-    \inferrule* [left=]
-        { set = \; \{ K\mid I <: K, \; K <: J\; $and$ \;
-            m \in \overrideSet(K, J)  \} }
-        {\mostSpecificOverride(m, I, J) = prune(set)}
-
-    prune(set) = \{I \in set \; | \; \nexists J \in set\setminus I, J <: I\}
-
-    \inferrule* [left=]
-    {   \interface{I}{I}{M}
-        \\ J \in \overline{I} }
-    {\ext(I, J) \marco{Is this ever used?}}
-
-    \inferrule* [left=]
-    {   \kwinterface \; I \; \kwextends \; \overline{I} \; \{ I_e \; m(\overline{I_x} \; \overline{x}) \;
-        \kwoverride \; J \ldots \} }
-    {m \in \overrideSet(I, J)}
     \end{mathpar}
@@
 
-$\mostSpecific$ is an auxiliary function that finds the most specific original implementations of a method.
-Let us consider $\mostSpecific(m, I, J)$, what it returns is a set of interfaces, each including its own $m$ as a most specific implementation.
-Such a set may contain several elements, but that implies ambiguity; what we expect is actually a singleton set.
-By the definition of $\mostSpecific$ shown in Figure~\ref{fig:auxfunc}, an interface belongs to the return set if and only if:
+$\mostSpecific$ and $\mostSpecificOverride$ are two core functions for the method lookup algorithm. Generally,
+$\mostSpecific(m, I, J)$ finds the set of most specific interfaces where $m$ is originally defined, they should be above $I$ and
+along path $J$. ``Along path $J$'' means one should be either a subtype or a super type of $J$. Finally with $\prune$
+the overridden interfaces will be filtered out.
+
+\begin{flalign*}
+	& \rhd \textit{Definition of } \mostSpecific(m, I, J): & \\
+	& \bullet \mostSpecific(m, I, J) = \prune(origins) & \\
+	& \indent\indent \textrm{with: } origins = \{K \mid \subt{I}{K}, \textrm{ and } \subt{K}{J} \; \lor \; \subt{J}{K}, &\\
+	& \hspace{1.62in} \textrm{ and } K[m\ \kwoverride\ K] \textrm{ is defined} \} &
+\end{flalign*}
+By the definition, an interface belongs to $\mostSpecific(m, I, J)$ if and only if:
 \begin{itemize}
-    \item It has an original definition of $m$;
-    \item It is a supertype of $I$;
-    \item It is along path $J$, meaning that it is either a supertype or a subtype of $J$ (including $J$ itself);
-    \item It does not have a subtype in the same set because we have used $prune$ to filter out all super types.
+	\item It originally defines $m$;
+	\item It is a super type of $I$;
+	\item It is either a super type or a subtype of $J$ (including $J$ itself);
+	\item Any subtype of it does not belong to the same result set because of $\prune$.
 \end{itemize}
-We could have put $set1$ and $set2$ together, but the current
-definition is clearer.
 
 The $\mostSpecific$ function only focuses on original method implementations, all the hierarchical overriding methods are omitted during that time.
-On the other hand, another auxiliary function $\mostSpecificOverride(m, I, J)$ has the assumption that $J$ defines an original $m$, and this function tries to find the most specific implementations that hierarchically overrides such an $m$.
-Just as $\mostSpecific$, $\mostSpecificOverride$ also returns the set of interfaces after pruning.
-An interface belongs to the return set if and only if:
+On the other hand, $\mostSpecificOverride(m, I, J)$ has the assumption that $J$ defines an original $m$, and this function tries to find the interfaces with most specific implementations that hierarchically overrides such an $m$.
+Formally,
+
+\begin{flalign*}
+	& \rhd \textit{Definition of } \mostSpecificOverride(m, I, J): & \\
+	& \bullet \mostSpecificOverride(m, I, J) = \prune(overrides) & \\
+	& \indent\indent \textrm{with: } overrides = \{K \mid \subt{I}{K}, \; \subt{K}{J} \textrm{ and } K[m\ \kwoverride\ J] \textrm{ is defined} &
+\end{flalign*}
+By the definition, an interface belongs to $\mostSpecific(m, I, J)$ if and only if:
 \begin{itemize}
@@
 	\item It hierarchically overrides $J.m$;
-    \item It does not have a subtype in the same set.
+	\item Any subtype of it does not belong to the same set.
 \end{itemize}
-The algorithm for finding the most specific hierarchical overriding method is quite similar to that for finding the most specific original method.
-A hierarchical overriding is not allowed to work on another hierarchical overriding, and one can hide another if their interfaces have subtyping relations.
-If they do not hide each other, the result implies ambiguity.
 
 \subsection{$\canInstantiate$}
-We use the auxilary function $\canInstantiate(I)$ to check whether an interface $I$ can be instantiated or not.
-The algorithm is decribed below:
-\begin{enumerate}
-\item Suppose $\mostSpecific(m, I, I) = \overline{J}$, where $\overline{J}$ is a list of interfaces.
-\item If $\forall J_i \in \overline{J}, if \mostSpecificOverride(m, I, J_i) = \{ K \} $ and $m$ in $K$ is not abstract, 
-then $\canInstantiate(I) = true$, else $\canInstantiate(I) = false$.
-\end{enumerate}
+$\canInstantiate(I)$ checks whether interface $I$ can be instantiated by the keyword $\kwnew$.
+Below is the algorithm:
 
-\subsection{$\mbodyStatic$}
-The auxilary function $\mbodyStatic$ serves for method loopup for static method invocation. 
-The brief description of the algorithm follows:
-\begin{mathpar}
-    \inferrule* [left=]
-        {  %\mostSpecific(m, I, I) = \{J\} \\
-            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_e}{m}{I_x}{x}{J}{e_0}\ldots\}}
-        {\mbodyStatic(m, J, J') = (J, \overline{I_x} \; \overline{x}, I_e \; e_0)}
-
-    \inferrule* [left=]
-        {  %\mostSpecific(m, I, I) = \{J\} \\
-            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\absmethod{I_e}{m}{I_x}{x}{J}\ldots\}}
-        {\mbodyStatic(m, J, J') = (J, \overline{I_x} \; \overline{x}, I_e \; \o)}
-\end{mathpar}
+\begin{flalign*}
+	& \rhd \textit{Definition of } \canInstantiate(I): & \\
+	& \bullet \canInstantiate(I) = True & \\
+	& \indent\indent \textrm{with: } \forall J \in \mostSpecific(m, I, I), \mostSpecificOverride(m, I, J) = \{K\}, & \\
+	& \hspace{.77in} \textrm{ and } K[m\ \kwoverride\ J] = \method{I_e}{m}{I_x}{x}{J}{e_0} &
+\end{flalign*}
+$\mostSpecific(m, I, I)$ represents the set of branches $I$ inherits on method $m$. $I$ can be instantiated
+if and only if for every branch, the most specific implementation is unambiguous and non-abstract.
 

### 2017-10-03 NewVersion/sections/Formalization.tex

@@
 
-Finally, \textsc{(T-Intf)} defines interface checking. The
+Rule \textsc{(T-Intf)} defines the typing rule for interfaces. The
 condition\bruno{Well, there are two conditions. I suggest you explain
   in a bit more detail the 2 conditions, since this rule seems to be
-  the more complex one. Some examples may help.} helps to ensure unambiguity and type soundness of the calculus. We will
+  the more complex one. Some examples may help.} \yanlin{controversial rule. lets discuss later} helps to ensure unambiguity and type soundness of the calculus. We will
 introduce \mbody{} and some counter-examples later. But intuitively, if $\mbody(m,I,J)$ is defined, that means $\new{I}.J::m()$ is not
@@
 \bruno{Explanation for T-Anno is missing}
+Finally, rule \textsc{(T-Anno)} is the typing rule for an expression with static type annotation.
+The rule says that $\angl{J}e$ type checks to $J$ if the expression $e$ type checks to $I$ and $I \subtype J$.
 
@@
 	\cpathreceiver \\
-	\cargs \\
+	%\cargs \\
 	\cpathargs \\

### 2017-10-03 NewVersion/sections/Auxiliary.tex
Done S4. Proceed to S5.

@@
 $\canOverride$ just checks that two original $m$ in $I$ and $J$ have the same type.
-
-\begin{figure*}[t]
-    \begin{mathpar}
-    \inferrule* [left=]
-        {  \mostSpecific(m, I_d, I_s) = \{I\} \\
-            \mostSpecificOverride(m, I_d, I) = \{J\} \\
-            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_e}{m}{I_x}{x}{I}{e_0}\ldots\}}
-        {\mbody(m, I_d, I_s) = (J, \overline{I_x} \; \overline{x}, I_e \; e_0)}
-
-    \inferrule* [left=]
-        {  \mostSpecific(m, I_d, I_s) = \{I\} \\
-            \mostSpecificOverride(m, I_d, I) = \{J\} \\
-            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\absmethod{I_e}{m}{I_x}{x}{I}\}}
-        {\mbody(m, I_d, I_s) = (J, \overline{I_x} \; \overline{x}, I_e \; \o)}
-
-    \end{mathpar}
-    \caption{Auxiliary functions.}\label{fig:auxfunc}
-\end{figure*}
-
-\begin{figure*}[t]
-    \centering
-    \vspace{-1ex}
-    \begin{tabular}{ccc}
-        \includegraphics[width=1.5cm]{pics/P1.pdf}\hspace{4pt} &
-        \includegraphics[width=1.5cm]{pics/P2.pdf}\hspace{4pt} &
-        \includegraphics[width=1.5cm]{pics/P3.pdf}\hspace{4pt} \\
-        (a) $\mbody(m,C,A) = (A,...)$\ \ \  & (b) $\mbody(m,C,A) = (C,...)$\ \ \  & (c) $\mbody(m,C,A) = (C,...)$
-    \end{tabular} \\
-   \begin{tabular}{cc}
-    \includegraphics[height=3cm]{pics/P4.pdf}\hspace{4pt} &
-    \includegraphics[height=3cm]{pics/P5.pdf}\hspace{4pt} \\ 
-    (d) $\mbody(m,D,A) = \keyword{undefined}$\ \ \  & (e) $\mbody(m,D,A) = \keyword{undefined}$
-   \end{tabular}
-    \caption{Examples on $\mbody$. ``$\uparrow$'' stands for hierarchical overriding.}\label{fig:examplesmbody}
-    %\saveSpaceFig
-\end{figure*}
 
@@
 
-\subsection{$\mbody$ and $\mtype$}
+\subsection{$\mbody$}
 
-$\mbody(m, I_d, I_s)$, as defined in Figure~\ref{fig:auxfunc}, denotes a method body lookup function.
+\begin{flalign*}
+	& \rhd \textit{Definition of } \mbody(m, I_d, I_s): & \\
+	& \bullet \mbody(m, I_d, I_s) = (J, \overline{I_x} \; \overline{x}, I_e \; e_0) & \\
+	& \indent\indent \textrm{with: } \mostSpecific(m, I_d, I_s) = \{I\} & \\
+	& \hspace{.77in} \mostSpecificOverride(m, I_d, I) = \{J\} & \\
+	& \hspace{.77in} J[m\ \kwoverride\ I] = \method{I_e}{m}{I_x}{x}{I}{e_0} & \\
+	& \bullet \mbody(m, I_d, I_s) = (J, \overline{I_x} \; \overline{x}, I_e \; \o) & \\
+	& \indent\indent \textrm{with: } \mostSpecific(m, I_d, I_s) = \{I\} & \\
+	& \hspace{.77in} \mostSpecificOverride(m, I_d, I) = \{J\} & \\
+	& \hspace{.77in} J[m\ \kwoverride\ I] = \absmethod{I_e}{m}{I_x}{x}{I} & \\
+\end{flalign*}
+$\mbody(m, I_d, I_s)$ denotes the method body lookup function.
 We use $I_d, I_s$, since $\mbody$ is usually invoked by a receiver of a method $m$, with its dynamic
 type $I_d$ and static type $I_s$. Such a function returns the most specific method implementation, more
-accurately, its parameters, returned expression and the types.
-It considers both originally defined methods and hierarchical overriding methods, so $\mostSpecific$ and $\mostSpecificOverride$ are invoked.
+accurately, its parameters, returned expression (empty for abstract methods) and the types.
+It considers both originally-defined methods and hierarchical overriding methods, so $\mostSpecific$ and $\mostSpecificOverride$ are invoked.
 
-To calculate $\mbody(m, I_d, I_s)$:
-\begin{itemize}
-    \item First, it invokes $\mostSpecific(m, I_d, I_s)$ and returns a set.
-    \item If $\mostSpecific$ returns a singleton set $\{I\}$, then it is good, otherwise, $\mbody$ is undefined in
-    this case.
-The set $\{I\}$ implies that we will use the $m$ from $I$ without ambiguity.
-Moreover, we have to invoke $\mostSpecificOverride(m, I_d, I)$, to check if there are updated versions of $m$ between $I_d$ and $I$.
-Again we forbid ambiguity, so the expected set after pruning is also a singleton set $\{J\}$.
-    \item Finally, we fetch the implementation of $m$ in interface $J$ and return its related information.
-\end{itemize}
-The definition of $\mtype$ used in typing rules simply relies on $\mbody$. In short,
-$$\mbody(m, I, I) = (J, \overline{I_x}\ \overline{x}, I_e\ ?) \ \Longrightarrow\ \mtype(m, I) = \overline{I_x}\rightarrow I_e$$
-
-\begin{comment}
-$mbody(m, I)$ algorithm:
-\begin{itemize}
-    \item If m is defined in I directly, then return I.m()
-    \item Else, let $\overline{I'} = mdefined(fathers(I))$, all ancestors of $I$ that has directly defined $m()$.
-    \item $\overline{I''} = needed(\overline{I'})$, keep only interfaces that are needed, which are not super-interface of others.
-    \item If $\overline{I''}$ is unique, then return this unique one.
-Else if any two I1,I2 in $\overline{I''}$ share a parent in $\overline{I'}$, then diamond conflict is detected, report error.
-Else return multiple $m()$s.
-\end{itemize}
-\end{comment}
-
-\begin{comment}
-\subsubsection{\collectMethods}
-\[ \collectMethods(I) = \left( \bigcup_{I_i \in \overline{I}} \methods(I_i) \right) \bigcup \methods(I) \]
-\[ \methods(I) = \overline{M}, \text{where } IT(I) = \interface{I}{I}{M} \]
-\end{comment}
+To calculate $\mbody(m, I_d, I_s)$, the invocation of $\mostSpecific$ looks for the most specific original methods and expects a singleton set, so as to avoid unambiguity.
+Furthermore, the invocation of $\mostSpecificOverride$ also expects a unique (unambiguous) most specific hierarchical override.
+And finally the target method is returned.
 
 \subsection{Examples}
+
+\haoyuan{Need more examples?}
+\begin{figure*}[t]
+	\centering
+	\vspace{-1ex}
+	\begin{tabular}{ccc}
+		\includegraphics[width=1.5cm]{pics/P1.pdf}\hspace{4pt} &
+		\includegraphics[width=1.5cm]{pics/P2.pdf}\hspace{4pt} &
+		\includegraphics[width=1.5cm]{pics/P3.pdf}\hspace{4pt} \\
+		(a) $\mbody(m,C,A) = (A,...)$\ \ \  & (b) $\mbody(m,C,A) = (C,...)$\ \ \  & (c) $\mbody(m,C,A) = (C,...)$
+	\end{tabular} \\
+	\begin{tabular}{cc}
+		\includegraphics[height=3cm]{pics/P4.pdf}\hspace{4pt} &
+		\includegraphics[height=3cm]{pics/P5.pdf}\hspace{4pt} \\ 
+		(d) $\mbody(m,D,A) = \keyword{undefined}$\ \ \  & (e) $\mbody(m,D,A) = \keyword{undefined}$
+	\end{tabular}
+	\caption{Examples on $\mbody$. ``$\uparrow$'' stands for hierarchical overriding.}\label{fig:examplesmbody}
+	%\saveSpaceFig
+\end{figure*}
 
@@
 For each small example, the result
-gives the interface to which $m$ is dispatched. (a) is a basic model for unintentional method conflicts; (b) and (c) demonstrate
+gives the interface to which $m$ is dispatched. (a) is a basic model for unintentional method conflicts (triangle inheritance); (b) and (c) demonstrate
 that hierarchical dispatch can find the most specific original method and hierarchical overriding method. More interesting are the two bad examples
-(d) and (e), they both fail on $\mbody$. (d) is the well-known diamond inheritance, which our model also forbids, and (e) is similar to
-(d) because the two hierarchical overriding methods are working on the same operation. Both counter-examples imply that \lstinline|new D().A::m()| will
+(d) and (e), they both fail on $\mbody$.
+(d) is the well-known diamond inheritance, which our model also forbids, and (e) is again a diamond conflict because the two hierarchical overriding methods are working on the same operation.
+Both counter-examples imply that \lstinline|new D().A?m()| will
 lead to ambiguity, and in order for type soundness, both have to be denied by the type checker. This is guaranteed by the interface check

### 2017-10-03 NewVersion/sections/Formalization.tex
more S3

@@
 unintentional method conflicts are untangled in \MIM{}, we only focus on a small subset of the interface model. For example, all the methods declared
-in an interface are default methods, that is to say, they always
-provide default implementations. 
+in an interface are either default methods or abstract methods.
+Default methods provide default implementations for methods, and abstract methods have no method body, which requires future implementation.
 %From this point we can view that we
@@
 Finally, rule \textsc{(T-Anno)} is the typing rule for an expression with static type annotation.
-The rule says that $\angl{J}e$ type checks to $J$ if the expression $e$ type checks to $I$ and $I \subtype J$.
+The rule says that an annotated expression $\angl{J}e$ type checks to $J$ if the expression $e$ type checks and the static annotation $J$ is a subtype of $I$ which is the type of $e$.
 

### 2017-10-04 NewVersion/sections/Formalization.tex
refine s3

@@
 Featherweight Java~\cite{Igarashi01FJ}. The syntax, typing rules,
-small-step semantics and type soundness proofs are presented.
+small-step semantics and theorems for type soundness are presented.
 
@@
 unintentional method conflicts are untangled in \MIM{}, we only focus on a small subset of the interface model. For example, all the methods declared
-in an interface are either default methods or abstract methods.
-Default methods provide default implementations for methods, and abstract methods have no method body, which requires future implementation.
+in an interface are either default methods or abstract methods. Default methods provide default implementations for methods. Abstract methods do not
+have method body, and in fact we are not introducing a different kind of methods, but they are just treated as normal methods that return empty.
+Abstract methods can be overridden with future implementations.
+
 %From this point we can view that we
@@
 %inheritance. 
-Object creation is directly supported via $\new I$. 
+Object creation is represented by $\new I$.
+If any unimplemented abstract methods are defined in interface $I$ (or inherited from parents), then object creation fails.
 Fields and primitive types are not modelled in \MIM{}.
@@
 For simplicity, overloading is not modelled for methods, which
-implies we can uniquely identify a method by its name.
+implies we can uniquely identify a method by its name.\yanlin{the terminology of original methods should have been proposed in Overview.}
 
@@
 $\Gamma$ is maintained to store the types of variables, together with
-the ``this'' type, namely
-the enclosing type. The three rules for method invocation, \textsc{(T-Invk)}, \textsc{(T-PathInvk)} and \textsc{(T-SuperInvk)}
-are very similar, in the sense that they all check the type of the specific method, by using
-an auxiliary function \mtype. \mtype{} is the function for looking up method types, which we will
-illustrate later in Section~\ref{subsec:auxdefs}. After the method
-type is obtained, they all check that the arguments and the receiver
-have compatible types. Additionally, \textsc{(T-PathInvk)} requires the receiver to be the subtype of the specified
-path type, and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.
+the \kwthis type, namely
+the enclosing type. 
+% The three rules for method invocation, \textsc{(T-Invk)}, \textsc{(T-PathInvk)} and \textsc{(T-SuperInvk)}
+% are very similar, in the sense that they all check the type of the specific method, by using
+% an auxiliary function \mtype. \mtype{} is the function for looking up method types, which we will
+% illustrate later in Section~\ref{subsec:auxdefs}. After the method
+% type is obtained, they all check that the arguments and the receiver
+% have compatible types. Additionally, \textsc{(T-PathInvk)} requires the receiver to be the subtype of the specified
+% path type, and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.
 
@@
 \end{mathpar}
-\caption{Typing Rules of \name{}.}
-\label{fig:typingrules}
 \saveSpaceFig
 \caption{Typing and subtyping of \name{}.}
+\label{fig:typingrules}
 \end{figure*}
@@
 the interface to which $m$ is dispatched. Therefore we also keep the
-interface type in the definition of \mbody. This point is consistent
-with the last paragraph in Section~\ref{subsec:problem2}.
+interface type in the definition of \mbody.
 
@@
 similarity between their semantic rules in
-Figure~\ref{fig:smallstep}. For any \lstinline|e.I::m()|, the result
+Figure~\ref{fig:smallstep}. For any \lstinline|e.I?m()|, the result
 of evaluation remains unchanged if we set the static type of
@@
 \subsection{Properties}
-Previously the definitions of our model are given, now we should proceed to prove the type soundness of 
+Previously the definitions of our model are given, now we proceed to prove the type soundness of 
 the model, which relates typing to computation. The type soundness states that, if an expression is 
@@
 (Theorem~\ref{theorem_soundness}) is proved by using the standard technique of subject reduction (Theorem~\ref{theorem_subject})
-and progress (Theorem~\ref{theorem_progress})~\cite{Wright1994}. In Theorem~\ref{theorem_progress} ``$\#(\overline{x})$'' denotes the number of
-elements.
+and progress (Theorem~\ref{theorem_progress})~\cite{Wright1994}. In Theorem~\ref{theorem_progress} ``$\#(\overline{x})$'' denotes the length of
+$\overline{x}$.
 

### 2017-10-05 NewVersion/sections/Formalization.tex
Change formalization.
Done revising formalization.

@@
 e.m(\overline{e}) \mid
-\new{I} \mid
-e.I?m(e) \; \mid \; \angl{I}e \\
+\new{I} \mid \; (I)e \\
 \text{Context}      & \Gamma & \Coloneqq & \overline{x}:\overline{I} \\
-\text{Values}       & v & \Coloneqq & \angl{I} \new{J} \\
+\text{Values}       & v & \Coloneqq & (I) \new{J} \\
 %%\\
@@
 	\tinvk \\
-	\tpathinvk \\
+	% \tpathinvk \\
 	% \tsuperinvk \\
@@
 \begin{mathpar}
-	\sinvk \\
+	% \sinvk \\
 	\spathinvk \\
@@
 	\creceiver \hspace{.5in}
-	\cpathreceiver \\
-	%\cargs \\
-	\cpathargs \\
+	% \cpathreceiver \\
+	\cargs \\
+	% \cpathargs \\
 	% \csuperargs \\
@@
 \begin{theorem}[Subject Reduction]~\label{theorem_subject}
-$\textit{If } \ \judgeewf \Gamma {e : I} \; \textit{ and } \ e \rightarrow e',\ 
-\textit{then } \judgeewf \Gamma {e' : I'} \ \textit{ for some } \ I' <: I.$
+If $\judgeewf \Gamma {e : I}$ and $e \rightarrow e'$, 
+then $\judgeewf \Gamma {e' : I}$.
 \end{theorem}
@@
 \begin{theorem}[Progress]~\label{theorem_progress}
-$\textit{Suppose } e \textit{ is a well-typed expression, if } e \textit{ includes} $
-
-\noindent $\left(\angl{J}\emph{\kwnew}\;I()\right).K?m(\overline{v}) \textit{ as a subexpression, then } \emph{\mbody}(m, I, K) = (I_0, \overline{I_x} \; \overline{x}, I_e\; e_0) $ $\textit{and } \num{\overline{x}} = \num{\overline{e}} \textit{ for some } \overline{I_x}, \overline{x}, I_e \textit{ and } e_0.$
+Suppose $e$ is a well-typed expression, if $e$ includes 
+$\left((J)\emph{\kwnew}\;I()\right).m(\overline{v})$ as a sub-expression, then $\mbody(m, I, J) = (I_0, \overline{I_x} \; \overline{x}, I_e\; e_0)$ and $\num{\overline{x}} = \num{\overline{v}}$ for some $I_0$, $\overline{I_x}$, $\overline{x}$, $I_e$ and $e_0$.
 \end{theorem}
@@
 If $\judgeewf \o {e : I}$ and $e \to^* e'$ with $e'$ a normal form, then $e'$ is 
-a value $v$ with $\judgeewf \o {v:J}$ and $J \subtype I$.
+a value $v$ with $\judgeewf \o {v:I}$.
 \end{theorem}

### 2017-10-05 NewVersion/sections/TypeSafety.tex
Done revising formalization.

@@
 \begin{lemma}[Method Type Preservation]~\label{lemma:mbody_type_preservation}
-If $\mbody(m, I_0, J_0) = (K, \overline{I_x}\ \_, I_e\ \_)$, then for any $I'_0 \subtype I_0$, $\mbody(m, I'_0, J_0) = (K', \overline{I_x}\ \_, I_e\ \_)$.
+If $\mbody(m, J, J) = (K, \overline{I_x}\ \_, I_e\ \_)$, then for any $I \subtype J$, $\mbody(m, I, J) = (K', \overline{I_x}\ \_, I_e\ \_)$.
 \end{lemma}
@@
 
-Since $\mbody(m, I_0, J_0)$ is defined, by \textsc{(T-Intf)} we derive that $\mbody(m, I'_0, J_0)$ is also defined.
-Suppose that $$\mostSpecific(m, I_0, J_0) = \{I\}$$ $$\mostSpecificOverride(m, I_0, I) = \{K\}$$
-$$\mostSpecific(m, I'_0, J_0) = \{I'\}$$ $$\mostSpecificOverride(m, I'_0, I') = \{K'\}$$
+%\begin{comment}	
+Since $\mbody(m, J, J)$ is defined, by \textsc{(T-Intf)} we derive that $\mbody(m, I, J)$ is also defined.
+Suppose that $$\mostSpecific(m, J, J) = \{I_0\}$$ $$\mostSpecificOverride(m, J, I_0) = \{K\}$$
+$$\mostSpecific(m, I, J) = \{I'_0\}$$ $$\mostSpecificOverride(m, I, I'_0) = \{K'\}$$
 
-Below we use $I[m\uparrow J]$ to denote the type of method $m$ defined in $I$ that overrides $J$. We have to prove that $K'[m\uparrow I'] = K[m\uparrow I]$.
+Below we use $I[m\uparrow J]$ to denote the type of method $m$ defined in $I$ that overrides $J$. We have to prove that $K'[m\uparrow I'_0] = K[m\uparrow I_0]$.
 Two facts:
@@
 
-Since $K \subtype I, K' \subtype I'$, by Fact B, $$K[m\uparrow I] = I[m\uparrow I] \quad K'[m\uparrow I'] = I'[m\uparrow I']$$
+By definition of $\mostSpecificOverride$, $K \subtype I_0, K' \subtype I'_0$. By Fact B, $$K[m\uparrow I_0] = I_0[m\uparrow I_0] \quad K'[m\uparrow I'_0] = I'_0[m\uparrow I'_0]$$
 
-Hence it suffices to prove that $I'[m\uparrow I'] = I[m\uparrow I]$. Since $I'_0 \subtype I_0$, by the definition of $\mostSpecific$ and $\prune$, $I'$ and $I$
-appear in the same set that is pruned, hence $I' \subtype I$. By Fact A, the proof is done.
+Hence it suffices to prove that $I'_0[m\uparrow I'_0] = I_0[m\uparrow I_0]$.
+Actually when calculating $\mostSpecific(m, J, J)$, by the definition of $\mostSpecific$ we know that $I_0 \subtype J$ and $I_0[m \; \kwoverride \; I_0]$ is defined.
+So when calculating $\mostSpecific(m, I, J)$ with $I \subtype J$, $I_0$ should also appear in the set before pruned, since the conditions are again satisfied.
+But after pruning, only $I'_0$ is obtained, by definition of $\prune$ it implies $I'_0 \subtype I_0$.
+By Fact A, the proof is done.
+%\end{comment}
+
 \end{proof}
@@
 
+\begin{comment}
 \textbf{Case PathInvk.} $e = e_0.J_0?m(\overline{e})$. By \textsc{(T-PathInvk)}, suppose
@@
 Again by \textsc{(T-PathInvk)}, $\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e : I}$.
+\end{comment}
 
@@
 \indent \textbf{Case S-Invk.} Let
+\begin{comment}
    $$e = (\angl{J}\new{I}).m(\overline{v}) \quad \judgeewf {\Gamma} {e : I_e}$$
@@
 At this moment, \textsc{(T-PathInvk)} is immediately applicable by the above conditions, including that $e'$ also invokes $\mbody(m, J, J)$. Hence $\judgeewf {\Gamma} {e' : I_e}$.
+\textbf{Case S-PathInvk.} Let
+\end{comment}
+  $$e = ((J)\new{I}).m(\overline{v}) \quad \judgeewf {\Gamma} {e : I_e}$$
+  $$e' = (I_{e_0})[\overline{(I_x)v}/\overline{x}, (I_0)\new{I}/\kwthis]e_0$$
+  $$\mbody(m, I, J) = (I_0, \overline{I_x} \; \overline{x}, I_{e_0} \; e_0)$$
 
-\textbf{Case S-PathInvk.} Let
-  $$e = (\angl{J}\new{I}).K?m(\overline{v}) \quad \judgeewf {\Gamma} {e : I_e}$$
-  $$e' = \angl{I_{e_0}}[\overline{\angl{I_x}} \overline{v}/\overline{x}, \angl{I_0}\new{I}/\kwthis]e_0$$
-  $$\mbody(m, I, K) = (I_0, \overline{I_x} \; \overline{x}, I_{e_0} \; e_0)$$
-
-Since $\mbody(m, I, K)$ is defined, the definition of $\mbody$ ensures that $I \subtype I_0$. And since $e$ is well-typed, by \textsc{(T-PathInvk)},
+Since $\mbody(m, I, J)$ is defined, the definition of $\mbody$ ensures that $I \subtype J$. And since $e$ is well-typed, by \textsc{(T-Invk)},
   $$\judgeewf {\Gamma} {\overline{v} : \overline{I_v}} \quad \overline{I_v} \subtype \overline{I_x}$$
@@
 By the rules \textsc{(T-Anno)} and  \textsc{(T-New)},
-  $$\judgeewf {\Gamma} {\overline{\angl{I_x}}\overline{v} : \overline{I_x}} \quad \judgeewf {\Gamma} {\angl{I_0}\new{I} : I_0}$$
+  $$\judgeewf {\Gamma} {\overline{(I_x)v} : \overline{I_x}} \quad \judgeewf {\Gamma} {(I_0)\new{I} : I_0}$$
 
@@
 Hence by Lemma~\ref{lemma:subst_type_preservation}, the substitution preserves typing, thus
-  $$\judgeewf {\Gamma} {[\overline{\angl{I_x}} \overline{v}/\overline{x}, \angl{I_0}\new{I}/\kwthis]e_0 : I'_{e_0}}$$
+  $$\judgeewf {\Gamma} {[\overline{(I_x)v}/\overline{x}, (I_0)\new{I}/\kwthis]e_0 : I'_{e_0}}$$
 
@@
 Now we only need to prove that $I_{e_0} = I_e$.
-Since $I_{e_0}$ is from $\mbody(m, I, K)$, whereas $I_e$ is from $\mbody(m, J, K)$, by the rule  \textsc{(T-PathInvk)}.
-By $\textsc{(T-Anno)}$ and the condition that $e$ type-checks, we know that $I \subtype J$.
-By Lemma~\ref{lemma:mbody_type_preservation}, $I_{e_0} = I_e$.
+Since $I_{e_0}$ is from $\mbody(m, I, J)$, whereas $I_e$ is from $\mbody(m, J, J)$, by the rule \textsc{(T-Invk)} on $e$.
+Since $I \subtype J$, by Lemma~\ref{lemma:mbody_type_preservation}, $I_{e_0} = I_e$.
 
@@
 
-\textbf{Case C-PathReceiver.} Straightforward induction.
+%\textbf{Case C-PathReceiver.} Straightforward induction.
 
@@
 
-\textbf{Case C-PathArgs.} Straightforward induction.
+%\textbf{Case C-PathArgs.} Straightforward induction.
 
@@
 
-Since $e$ is well-typed, by \textsc{(T-PathInvk)} and \textsc{(T-Anno)} we know that
-$$I \subtype J\textrm{, and }\mbody(m, J, K) \textrm{ is defined}$$
+Since $e$ is well-typed, by \textsc{(T-Invk)} and \textsc{(T-Anno)} we know that
+$$I \subtype J\textrm{, and }\mbody(m, J, J) \textrm{ is defined}$$
 
-By Lemma~\ref{lemma:mbody_type_preservation}, $\mbody(m, I, K)$ is also defined, and the type checker ensures the expected number of arguments.
+By \textsc{(T-Intf)}, $\mbody(m, I, J)$ is also defined, and the type checker ensures the expected number of arguments.
 
-On the other hand, $I \subtype K$. By the definition of $\mostSpecific$, $$\mostSpecific(m, I, K) \subseteq \mostSpecific(m, I, I)$$
+On the other hand, since $I \subtype J$, by the definition of $\mostSpecific$, $$\mostSpecific(m, I, J) \subseteq \mostSpecific(m, I, I)$$
 
-By \textsc{(T-New)}, $\canOverride(I)$ should be true. By the definition of $\canOverride$, any $J\in\mostSpecific(m, I, I)$ satisfies that
-$\mostSpecificOverride(m, I, J)$ contains only one interface, in which the $m$ that overrides $J$ is a concrete method.
-Therefore $\mbody(m, I, K)$ also provides a concrete method, which finishes the proof.
+By \textsc{(T-New)}, $\canOverride(I) = True$. By the definition of $\canOverride$, any $J_0\in\mostSpecific(m, I, I)$ satisfies that
+$\mostSpecificOverride(m, I, J_0)$ contains only one interface, in which the $m$ that overrides $J_0$ is a concrete method.
+Therefore $\mbody(m, I, J)$ also provides a concrete method, which finishes the proof.
 \end{proof}

### 2017-10-05 NewVersion/sections/Formalization.tex
refine S3 done

--- 2017-10-04 NewVersion/sections/Formalization.tex
@@
 There are two typing rules for method invocation: \textsc{(T-Invk)} and \textsc{(T-PathInvk)}.
-\textsc{(T-Invk)} is the typing judgement for a normal method invocation, which is similar to Featherweight Java.
-It checks the type of the specific method, by using an auxiliary function \mbody.
-\mbody is the function for looking up methods, which we will illustrate later in Section~\ref{subsec:auxdefs}.
-After the method type is obtained, we check that arguments and the receiver have compatible types.
+\textsc{(T-Invk)} is the typing judgement for a normal method invocation.
+First it ensures that the method receiver $e_0$ type checks to a type $I_0$.
+Then it checks the type of the specific method, by using an auxiliary function $\mbody(m, I_0, I_0)$, which is the function for looking up methods that we will illustrate in more detail in Section~\ref{subsec:auxdefs}.
+The form of \mbody is different to FJ, which has two parameters.
+The first $I_0$ represents the dynamic type and the second, the static type.
+If the result of \mbody is not \Undefined, it means the method exists and the corresponding method parameters and return types are given.
+After the method type is obtained, we check that all arguments $\overline{e}$ type check to $\overline{I}$ which are subtypes of $\overline{J}$.
 \textsc{(T-PathInvk)} is the typing judgement for a path invocation.
-Besides the conditions of \textsc{(T-PathInvk)}, \textsc{(T-PathInvk)} requires the receiver to be the subtype of the specified
-path type. 
+Besides the conditions of \textsc{(T-Invk)}, \textsc{(T-PathInvk)} requires the type of receiver to be the subtype of the specified path type.
 % and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.
@@
 
-Rule \textsc{(T-Intf)} defines the typing rule for interfaces. The
-condition\bruno{Well, there are two conditions. I suggest you explain
+\bruno{Well, there are two conditions. I suggest you explain
   in a bit more detail the 2 conditions, since this rule seems to be
-  the more complex one. Some examples may help.} \yanlin{controversial rule. lets discuss later} helps to ensure unambiguity and type soundness of the calculus. We will
-introduce \mbody{} and some counter-examples later. But intuitively, if $\mbody(m,I,J)$ is defined, that means $\new{I}.J::m()$ is not
-ambiguous during runtime. Therefore the condition says that if an expression type checks, it should not introduce ambiguity during runtime
-in any case. The interface check is responsible for capturing ambiguity during compilation.
+  the more complex one. Some examples may help.} \yanlin{controversial rule. lets discuss later} 
+Rule \textsc{(T-Intf)} defines the typing rule for interfaces.
+Interface $I$ type checks only if the following conditions are satisfied: 1) all methods $\overline{M}$ that are directly defined in $I$ type check; 2) method lookup $\mbody(m, I, J)$ successes as long as the method $m$ is defined in any interface $J$ which is an ancestor of $I$; 3)if an original method $m$ defined in interfaces $I$ overrides another original method defined in an ancestor of $I$, then the method types are compatible.
+These conditions ensure unambiguity and type soundness of the calculus.
+We will introduce \mbody{} and some counter-examples later.
+But intuitively, if $\mbody(m,I,J)$ is defined, that means $\new{I}.J::m()$ is not ambiguous during runtime.
+Therefore the condition says that if an expression type checks, it should not introduce ambiguity during runtime in any case.
+The interface check is responsible for capturing ambiguity during compilation.
 

### 2017-10-05 NewVersion/sections/Discussion.tex
S5 skeleton

@@
 Why we include 
-\paragraph{Static Invocation.}
-Why we include
+\paragraph{Path Invocation}
+
+\paragraph{Static/Super Invocation}
+Extensibly adding rules to the current formalization.
+- can dispatch to any method (both original method and updating method).
+- static dispatch algorithm.
+
+\paragraph{Diamond interface check}
+
+\paragraph{Hierarchical Overriding Restriction.}
+In \MIM{}, hierarchical overriding can only override an interface that defines the original method.
+But in reality, sometimes this condition is too restrict and can be relaxed to allowing overriding a super interface.
+..
+Pros & cons.
+
 \paragraph{Method Resolution Rules.}

### 2017-10-06 NewVersion/sections/RelatedWork.tex
refine S6 related work. + MiddleMan discussion

--- 2017-06-18 Aplas17/sections/RelatedWork.tex
@@
 inheritance~\cite{ellis1990annotated,scala-overview,bracha90mixin,scharli03traits,malayeri2009cz,csharpdoc,Moon1986,Flatt1998,Ancona2003}. 
-The Mixin model~\cite{bracha90mixin} allows naming components 
+The Mixin models~\cite{bracha90mixin,Flatt1998,van1996encapsulation,Ancona2003,Hendler86} allow naming components 
 that can be applied to various classes as reusable functionality units. However, the linearization (total ordering) of mixin 
@@
 the renaming feature helps to solve the unintentional method conflicts problem, however, it breaks structural subtyping.
-\bruno{Should talk
-  about work on traits that support renaming.}\bruno{I remember Yanlin
-  had a presentation with alot of related work on multiple
-  inheritance. Many of those seem to be missing here}\yanlin{Done}
 
@@
 \subsection{Resolving Unintentional Method Conflicts}
-There are a few languages that partly realize the problem of
+There are a few languages that may have realized the problem of
 unintentional conflicts and provide some support for it.
 
+\begin{comment} %C++ related work with code explaination
 \noindent {\bf C++ model.}
@@
 model.
+\end{comment}
+
+\noindent {\bf C++ model.}
+C++ supports a very flexible inheritance model and allows programmers to choose either static dispatch or dynamic dispatch for method lookup.
+It allows the existance of unintentional conflicts and uses static dispatch to resolve them, as discussed in Section~\ref{sec:overview}. 
+With virtual methods, dynamic dispatch is used and 
+method lookup algorithm will find the most specific method definition.\yanlin{to revise: be consistant with introduction}
+Although C++ support this flexibility, it does not support hierarchical overriding compared to our
+model.
+However, there is one workaround we found online that mimicks hierarchical overriding, we call it the "MiddleMan" approach, as shown in Figure~\ref{fig:middleman}.
+In this example, class \texttt{A} and \texttt{B} are two classes that both defines a method \texttt{m} unintentionally.
+
+Class \texttt{MiddleMan}, as its name suggests, acts as a middle man between its class \texttt{C} and its parents \texttt{A, B}.
+\texttt{MiddleMan} defines a virtual method \texttt{m} that overrides a parent method \texttt{m} and delegate the implementation to another method \texttt{m\_impl} that takes \kwthis as parameter.
+C++ supports method overloading, so that multiple \texttt{m\_impl} methods with different parameter types can co-exist.
+When definning class \texttt{C}, we specify the parents to be \texttt{MiddleMan<A>, MiddleMan<B>} instead of \texttt{A, B}.
+This way, programmers may define new versions of \texttt{A.m} and \texttt{B.m} in class \texttt{C} by providing the corresponding \texttt{m\_impl} methods.
+Then in the client code, the method call \texttt{((A*)c)->m()} will print out string \texttt{"MA2"}, as expected.
+Although this workaround can help us defining partial method overrides to a certain extent, the drawbacks are obvious.
+Firsly, the approach is complex and requires the pre-knowledge of the programmer to this approach.
+Moreover, no direct syntax support makes the "MiddleMan" code cumbersome to write.
+Finally, the approach is ad-hoc, meaning that the class \texttt{MiddleMan} shown in Figure~\ref{fig:middleman} is not general enough to be used in other cases, more middle-mans are needed if partial method overrides happens in other classes.
+
+\begin{figure*}
+\begin{lstlisting}
+class A { public: virtual void m() {cout << "MA" << endl;}};
+class B { public: virtual void m() {cout << "MB" << endl;}};
+template<class C>
+class MiddleMan : public C {
+    void m() override final { m_impl(this); }
+  protected:
+    virtual void m_impl(MiddleMan*) { return this->C::m(); }
+};
+class C : public MiddleMan<A>, public MiddleMan<B> { 
+private:
+    void m_impl (MiddleMan<A>*) override {cout << "MA2" << endl;}
+    void m_impl (MiddleMan<B>*) override {cout << "MB2" << endl;}
+};
+int main()
+{
+    C* c = new C();
+    ((A*)c)->m();         //print "MA2"
+    return 0;
+}
+\end{lstlisting}
+\caption{The "MiddleMan" approach.}
+\label{fig:middleman}
+\end{figure*}
 
@@
 only be accessed through an instance of the interface. Explicit
-interface implementation allows the programmer to inherit two
+interface implementation allows an interface to inherit multiple 
 interfaces that share the same member names and give each interface
@@
 
-\subsection{Hierarchical Dispatch}
+\subsection{Hierarchical Dispatch in \self{}}
 As we have discussed before, although the mix of static and dynamic dispatch is 

### 2017-10-06 NewVersion/sections/Auxiliary.tex

@@
 \end{flalign*}
-Here $I[m\ \kwoverride\ J]$ is basically a directly lookup for method $m$ in the body of $I$, where such a method
-overrides $J$. The method can be either concrete or abstract, and the body of definition is returned. Notice that
+Here $I[m\ \kwoverride\ J]$ is basically a direct lookup for method $m$ in the body of $I$, where such a method
+overrides $J$ (like static dispatch). The method can be either concrete or abstract, and the body of definition is returned. Notice that
 by our syntax, $I[m\ \kwoverride\ I]$ is looking for the originally-defined method $m$ in $I$.

### 2017-10-06 NewVersion/sections/Discussion.tex
refine S6 related work. + MiddleMan discussion

--- 2017-09-04 NewVersion/sections/Discussion.tex
@@
 \section{Discussion}
-In this section, we discuss the design space and some reflections of the work. 
-\paragraph{Abstract Methods.}
-Why we include 
-\paragraph{Static Invocation.}
-Why we include
-\paragraph{Method Resolution Rules.}
+In this section, we will discuss the design space and some reflections of the work. There are some relationships we made
+between our language model and traits, Java interfaces as well as other languages. And there are certainly some other ways
+around to improve our model for better code reuse.
+
+\subsection{Abstract Methods}
+
+Abstract methods are one of the key features in most general OO languages. For example, Java interfaces were designed
+to include only method declarations, and those abstract methods can be implemented in a class body, although in the formal
+Featherweight Java model, abstract methods are not involved because of its orthogonality to the core calculus. In traits the
+similar idea is to use keywords like ``\textbf{require}'' for abstract method declarations. Abstract methods provide a way to
+delay the implementations to future subtypes. Using overriding, they also help to ``exclude'' existing implementations.
+
+In our formalized mini-calculus, however, abstract methods are not a completely orthogonal feature. The $\canInstantiate$ function
+has to check whether an interface can be instantiated, by looking at all the inherited branches and seeing if each most specific method
+is abstract or not.
+
+Our formalization has already made abstract methods in a simple way. In other languages they may perform more complicated behaviours.
+For instance, in Java 8 when putting two identical abstract methods together by multiple inheritance, there is no conflict error. We omit
+that case for two reasons. First, our formalization just treats abstract methods as concrete methods with an empty body, and that simplifies
+the rules and the proof a lot.
+Second, our design choice tends to give more sense on those interesting cases, just as we reject the diamond inheritance.
+The triangle inheritance should distinguish and treat differently on the two methods instead of fusing them, for they represent different operations, even if they are abstract.
+
+\subsection{Orthogonal \& Non-Orthogonal Extensions}
+
+Our model is designed as a minimal calculus for focusing only on resolving unintentional conflicts. Therefore, we have omitted a number of
+common orthogonal features including primitive types, assignments, method overloading, covariant method return types, static dispatch, and so on.
+Those features can be modularly added to the model without breaking type soundness \haoyuan{correct?}.
+For example, we present the additional syntax, typing and semantic rules of static invocation below as an extension:
+
+\begin{mathpar}
+	\begin{array}{llrl}
+		\text{Expressions}  & e  & \Coloneqq & \ldots \; \mid \; e.J_0@J_1::m(\overline{e})
+	\end{array} \\
+	\tstaticinvk \\
+	\sstaticinvk
+\end{mathpar}
+A static invocation $e.J_0@J_1::m(\overline{e})$ aims at finding the method $m$ in $J_0$ that hierarchically overrides $J_1$, thus $J_0[m\ \kwoverride\ J_1]$ is invoked.
+As shown in \textsc{(S-StaticInvk)}, static dispatch needs a receiver to involve in the substitution for ``$\kwthis$'' reference, so as to provide the latest implementations.
+In fact, static dispatch is common in OO programming, as it provides a shortcut to the reuse of old implementation easily, and super calls can also rely on this feature.
+For convenience we just make it simple above, whereas in languages like C++ or Java, the static or super invocations are more flexible hence complicated; they can climb the class hierarchy.
+
+Fields as a particular non-orthogonal feature.
+
+\subsection{More}
+
+\paragraph{Diamond interface check, loosen the model}
+
+\paragraph{Hierarchical Overriding Restriction, loosen the model.}
+In \MIM{}, hierarchical overriding can only override an interface that defines the original method.
+But in reality, sometimes this condition is too restrict and can be relaxed to allowing overriding a super interface...
+And an override could be able to go over original methods.
+Pros \& cons.
+
+\paragraph{Path Invocation}
+
+\paragraph{(no example) Method Resolution Rules.}
+
+\paragraph{(no example) better code reuse (more kinds of method invocation)}
 Other resolution possibilities and comparison.

### 2017-10-08 NewVersion/sections/Discussion.tex
S5 done.

@@
 the rules and the proof a lot.
-Second, our design choice tends to give more sense on those interesting cases, just as we reject the diamond inheritance.
+Second, our design choice tends to give more sense on those interesting cases, just as we reject the simple case of diamond inheritance.
 The triangle inheritance should distinguish and treat differently on the two methods instead of fusing them, for they represent different operations, even if they are abstract.
@@
 
-Fields as a particular non-orthogonal feature.
+One typical non-orthogonal extension to our model could be to have fields.
+Having fields in OO multiple inheritance is a non-trivial issue.
+There has been a lot of work on it, such as C++ that uses virtual inheritance.
+The trait model simply disallows state to avoid that issue.
+In our language, however, we can perhaps borrow the idea of \textit{interface-based programming} [], which actually models state with abstract state operations.
+This can be realized by extending our current model with static methods and anonymous classes from Java.
+To directly support fields it requires more discussions and experiments, we leave them as our future work.
 
-\subsection{More}
+\subsection{Loosening the Model}
 
-\paragraph{Diamond interface check, loosen the model}
+For the goal of simplifying the model and type soundness proof, we have added a few constraints in the minimal calculus. Our language simply rejects the diamond inheritance, see the example below:
 
-\paragraph{Hierarchical Overriding Restriction, loosen the model.}
-In \MIM{}, hierarchical overriding can only override an interface that defines the original method.
-But in reality, sometimes this condition is too restrict and can be relaxed to allowing overriding a super interface...
-And an override could be able to go over original methods.
-Pros \& cons.
+\vspace{3pt}\begin{lstlisting}
+interface A { void m() {...} }
+interface B extends A { void m() {...} }
+interface C extends A { void m() {...} }
+interface D extends B, C {}
+\end{lstlisting}\vspace{3pt}
+In the example, both $B.m$ and $C.m$ override $A.m$, so we think they should represent the same operation. In that case, we believe that D inherits
+both conflicting methods without an explicit override, and it is in fact an intention conflict.
+Our calculus rejects these intentional conflicts by rule \textsc{(T-Intf)}, where $D$ is considered to be ill-formed.
+Nonetheless, as a general-purpose language, C++ accepts the definition of $D$, but forbids a cast from $D$ to $A$ because of ambiguity.
+For the conciseness of the proof, our language is more conservative on interfaces.
+But we could also loosen the model and perform ambiguity check on casts and other expressions.
 
-\paragraph{Path Invocation}
+Another case is about the restriction on hierarchical overrides.
+In our language model there are two types of methods (though they share the same syntax): original methods and hierarchical overrides.
+We require that a hierarchical override should only override an original method.
+Yet from the idea of encapsulation and modularity on programs, we could also allow an override to work on another override, which forms a series of overrides.
 
-\paragraph{(no example) Method Resolution Rules.}
-
-\paragraph{(no example) better code reuse (more kinds of method invocation)}
-Other resolution possibilities and comparison.
+\haoyuan{more.
+1) Path Invocation, more generalized diamond inheritance: not clear; other method resolution techniques: no example; better code reuse with other kinds of method invocation: no example.
+}

### 2017-10-08 NewVersion/sections/Introduction.tex
revise S1

@@
 have been adopted in some popular OOP languages. C++ has had 
-multiple inheritance from the start. Scala adapts the ideas from traits~\cite{scharli03traits}
-and mixins~\cite{bracha90mixin}\bruno{please add more references to
-  other work on traits and mixins here} to offer a disciplined form of multiple inheritance. Java 8 
+multiple inheritance from the start. Scala adapts the ideas from traits~\cite{scharli03traits,Ducasse:2006:TMF:1119479.1119483,Liquori08ftj}
+and mixins~\cite{bracha90mixin,Flatt1998,van1996encapsulation,Ancona2003,Hendler86} to offer a disciplined form of multiple inheritance. Java 8 
 offers a simple variant of traits, disguised of interfaces with default methods~\cite{goetz12fdefenders}.
@@
 C++ is a representative that accepts the triangle inheritance and
-resolves the ambiguity by \emph{static dispatching}. However, C++ has
-limited support for virtual methods with unintentional conflicts, and
-it will often throw errors when composing them. This is again
-unsatisfactory because virtual methods are pervasive in OOP and used 
-for code reuse and extensibility. A problem with the C++ approach is
-that programmers can only use either static or dynamic dispatching separately, but dealing
-with unintentional method conflicts seems to require a combination of
-both. 
+resolves the ambiguity by \emph{static dispatching} or cast. But the drawback is that these conflicting methods cannot be further updated. 
+% However, C++ has
+% limited support for virtual methods with unintentional conflicts, and
+% it will often throw errors when composing them. This is again
+% unsatisfactory because virtual methods are pervasive in OOP and used 
+% for code reuse and extensibility. A problem with the C++ approach is
+% that programmers can only use either static or dynamic dispatching separately, but dealing
+% with unintentional method conflicts seems to require a combination of
+% both. 
 Some other workarounds or approaches include delegation and
@@
           \bruno{Are the examples in the paper implemented in the interpreter?}
+          \yanlin{new formalization has not been implemented yet.}
 \end{itemize}

### 2017-10-09 NewVersion/sections/Introduction.tex
Revised Intro

@@
 
-Closest to our work are mechanisms available in C++ and C\# that allow for two
-unintentionally conflicting methods to coexist in a class. Among them, 
-C++ is a representative that accepts the triangle inheritance and
-resolves the ambiguity by \emph{static dispatching} or cast. But the drawback is that these conflicting methods cannot be further updated. 
+C++ and C\# do allow for two
+unintentionally conflicting methods to coexist in a class. 
+C++ accepts the triangle inheritance and
+resolves the ambiguity by \emph{static dispatching} or casts. But the
+drawback is that these conflicting methods cannot be further overriden. 
+\bruno{how about C\#?}
 % However, C++ has
@@
 
-This paper proposes \textit{hierarchical dispatching}: a novel approach
+This paper proposes two mechanisms to deal with unintentional method
+conflicts: \textit{hierarchical dispatching} and \emph{hierarchical
+  overriding}. Hierarchical dispatching is inspired by the mechanisms in C++ and
+provides an approach
 to method dispatching, which combines static and dynamic
@@
 specific implementation. In that case, both unambiguity and
-extensibility are preserved. To present this idea, we introduce a
+extensibility are preserved. 
+\textit{Hierarchical overriding} allows method overriding to be applied
+only to one branch of the class hierarchy. Hierarchical overriding 
+adds expressive power that is not available in languages such as 
+C++ or C\#. To present both ideas, we introduce a
 formalized model \MIM{} in Section~\ref{sec:formalization} based on
 Featherweight Java~\cite{Igarashi01FJ}, together with theorems and
-proofs for type soundness. In the model we also propose
-\textit{hierarchical overriding}, where method overriding can be applied
-only to one branch of the class hierarchy. 
-\name{} is partly inspired by the method resolution semantics
-of C++, but it also incoorporates ideas from the trait model and Java
-8's default methods.
+proofs for type soundness.
 

### 2017-10-09 NewVersion/sections/Discussion.tex
Working on S3.

@@
 Nonetheless, as a general-purpose language, C++ accepts the definition of $D$, but forbids a cast from $D$ to $A$ because of ambiguity.
-For the conciseness of the proof, our language is more conservative on interfaces.
-But we could also loosen the model and perform ambiguity check on casts and other expressions.
+For the conciseness of the proof, our language is more conservative on interfaces, but open on up-casts.
+We could also loosen the model and perform ambiguity check on casts and other expressions.
+We need to handle more cases than C++, for instance, in the above program assume that $B.m$ and $C.m$ are hierarchical overrides on $A$, it is still a diamond.
 

### 2017-10-09 NewVersion/sections/Formalization.tex
Working on S3.

@@
 in an interface are either default methods or abstract methods. Default methods provide default implementations for methods. Abstract methods do not
-have method body, and in fact we are not introducing a different kind of methods, but they are just treated as normal methods that return empty.
-Abstract methods can be overridden with future implementations.
+have method body, and in fact they can be considered as normal methods that return nothing. Abstract methods can be overridden with future implementations.
 
@@
 Expressions can be standard constructs such as variables, method
-invocation, or object creation.
-\name{} allows two types of method invocations, one is the normal method invocation $e.m(\overline{e})$ that we are familiar with, another is the novel type of method invocation: path-invocations like ``$e.I\pathIvk m(\overline{e})$'', meaning that the dynamically bound
-implementation for method $m$ should be along the path $I$. 
-% Another interesting expression are super-invocations, which enable a method to access an old implementation from the specified super type.
-Hence a super-invocation can only be used inside an interface definition.
-Finally, an expression can also be annotated with its static type. But \emph{annotated expressions are only intended for the semantic rules},
-hence they are not supposed to appear in the source program. A value
-``$\angl{I}\new{J}$''
+invocation, or object creation, together with casts.
+Again, to be concise, the casts are merely safe up-casts. Those cast-expressions
+are in fact annotated expressions, where the annotation indicates its static type.
+The coexistence of static and dynamic types is the key to hierarchical dispatch.
+A value
+``$(I)\new{J}$''
 is the final result of multiple reduction steps evaluating an
-expression. Such value represents an object instance
-of $J$ with an annotated static type $I$.
+expression.
 
@@
 $\Gamma$ is maintained to store the types of variables, together with
-the \kwthis type, namely
-the enclosing type. 
+the self-reference $\kwthis$.
 % The three rules for method invocation, \textsc{(T-Invk)}, \textsc{(T-PathInvk)} and \textsc{(T-SuperInvk)}

### 2017-10-09 NewVersion/sections/Auxiliary.tex
Section 4

@@
-\section{Fundamental Notations}\label{subsec:auxdefs}
-In this section, we present the fundamental notations used in our formalization.
+\section{Fundamental Notions}\label{subsec:auxdefs}
+In this section, we present the fundamental notions used in our formalization.
 Some of them are auxiliary functions, others are however important ones as they
 directly implement our algorithm for method resolution.
+\bruno{I felt like there's not enough explanation/context in this
+  section. It is just dumping definitions without connecting them and
+  their purpose properly.}
 
@@
 To begin with, we introduce the following basic functions. 
+\bruno{explain: where are these definitions used and for what purpose?
+  You need similar explanations everywhere you introduce new definitions.}
 
@@
 
+\bruno{do not use the names of the definitions as titles of
+  Sections. Please give a title that states the purpose. 
+For this section in particular it may be something like ``Finding the most
+specific method override''}
 \subsection{$\mostSpecific$ and $\mostSpecificOverride$}
@@
 $\canInstantiate(I)$ checks whether interface $I$ can be instantiated by the keyword $\kwnew$.
-Below is the algorithm:
+Below is the algorithm:\bruno{used for what and where?}
 
@@
 
-\haoyuan{Need more examples?}
+\haoyuan{Need more examples?}\bruno{ask Marco.}
 \begin{figure*}[t]

### 2017-10-09 NewVersion/sections/Formalization.tex
Section 4

--- 2017-10-05 NewVersion/sections/Formalization.tex
@@
 small-step semantics and theorems for type soundness are presented.
+\bruno{In general, please try to use latex paragraphs to add more
+  structure and emphasize contents.}
 
@@
 For simplicity, overloading is not modelled for methods, which
-implies we can uniquely identify a method by its name.\yanlin{the terminology of original methods should have been proposed in Overview.}
+implies that we can uniquely identify a method by its name.\yanlin{the terminology of original methods should have been proposed in Overview.}
+\bruno{Then please do so.}
 
@@
 \subsection{Subtyping and Typing Rules}
+\paragraph{Subtyping}
 The subtyping of \MIM{} consists of only a few rules shown at the top of Figure~\ref{fig:typingrules}.
@@
 
+\paragraph{Type-checking}
 Details of type-checking rules are displayed at the bottom of Figure~\ref{fig:typingrules}, including expression
@@
 
-There are two typing rules for method invocation: \textsc{(T-Invk)} and \textsc{(T-PathInvk)}.
-\textsc{(T-Invk)} is the typing judgement for a normal method invocation.
-First it ensures that the method receiver $e_0$ type checks to a type $I_0$.
-Then it checks the type of the specific method, by using an auxiliary function $\mbody(m, I_0, I_0)$, which is the function for looking up methods that we will illustrate in more detail in Section~\ref{subsec:auxdefs}.
-The form of \mbody is different to FJ, which has two parameters.
-The first $I_0$ represents the dynamic type and the second, the static type.
-If the result of \mbody is not \Undefined, it means the method exists and the corresponding method parameters and return types are given.
+There are two typing rules for method invocation: \textsc{(T-Invk)}
+and \textsc{(T-PathInvk)}. \textsc{(T-Invk)} is the typing judgement
+for a normal method invocation. First it ensures that the method
+receiver $e_0$ type checks to a type $I_0$. Then it checks the type of
+the specific method, by using an auxiliary function $\mbody(m, I_0,
+I_0)$, which is the function for looking up methods that we will
+illustrate in more detail in Section~\ref{subsec:auxdefs}. The form of
+\mbody is different to FJ\bruno{Use xspace to fix the spacing problem
+  of macros like mbody}, which has two parameters. The first $I_0$
+represents the dynamic type and the second, the static type. If the
+result of \mbody is not \Undefined, it means that the method exists and the corresponding method parameters and return types are given.
 After the method type is obtained, we check that all arguments $\overline{e}$ type check to $\overline{I}$ which are subtypes of $\overline{J}$.
@@
 \textsc{(S-PathInvk)} invokes \mbody{} for method body lookup.
-The parameters $\overline{x}$ are replaced with arguments $\overline{v}$ with static type annotations $\overline{\angl{I_x}}$, where $\overline{\angl{I_x}}$ is the parameter types coming from method lookup result.
+The parameters $\overline{x}$ are replaced with arguments $\overline{v}$ with static type annotations $\overline{\angl{I_x}}$, where $\overline{\angl{I_x}}$ are the parameter types coming from method lookup result.
 The rule \textsc{(S-Invk)} simply reduces the problem of normal invocation to path invocation.
@@
 \subsection{Properties}
-Previously the definitions of our model are given, now we proceed to prove the type soundness of 
-the model, which relates typing to computation. The type soundness states that, if an expression is 
+Now we proceed to prove the type soundness of 
+the model, which relates typing to computation. Type soundness states that, if an expression is 
 well-typed, then after many reduction steps it must reduce to a value, with its annotation to be a subtype of the original expression type.
@@
 \end{proof}
+\bruno{Were we not supposed to have some note/comment as to why the
+  type soundness theorem is stricter that FJ?}

### 2017-10-09 NewVersion/sections/Introduction.tex
Section 4

@@
 drawback is that these conflicting methods cannot be further overriden. 
-\bruno{how about C\#?}
+\bruno{how about C\#? Say something about C\# here.}
 % However, C++ has
@@
 specific implementation. In that case, both unambiguity and
-extensibility are preserved. 
-\textit{Hierarchical overriding} allows method overriding to be applied
+extensibility are preserved. The main novelty over existing work is 
+the formalization of the essence of a hierarchical dispatching
+algorithm, which (as far as we know) has not been formalized before. 
+Furthermore, \textit{hierarchical overriding} allows method overriding to be applied
 only to one branch of the class hierarchy. Hierarchical overriding 

### 2017-10-09 NewVersion/sections/Discussion.tex
Start of Section 5

@@
 \section{Discussion}
-In this section, we will discuss the design space and some reflections of the work. There are some relationships we made
-between our language model and traits, Java interfaces as well as other languages. And there are certainly some other ways
-around to improve our model for better code reuse.
+In this section, we will discuss the design space and reflect about some of the design decisions of our work. We relate 
+our language to traits, Java interfaces as well as other languages. Furthermore we discuss
+ways to improve our  work.\bruno{references please!!!}
 
@@
 Abstract methods are one of the key features in most general OO languages. For example, Java interfaces were designed
-to include only method declarations, and those abstract methods can be implemented in a class body, although in the formal
-Featherweight Java model, abstract methods are not involved because of its orthogonality to the core calculus. In traits the
+to include only method declarations, and those abstract methods can be implemented in a class body. 
+The formal Featherweight Java model does not include abstract methods because of its orthogonality to the core calculus. In traits the
 similar idea is to use keywords like ``\textbf{require}'' for abstract method declarations. Abstract methods provide a way to
@@
 
-In our formalized mini-calculus, however, abstract methods are not a completely orthogonal feature. The $\canInstantiate$ function
+In our formalized calculus, however, abstract methods are not a completely orthogonal feature. The $\canInstantiate$ function
 has to check whether an interface can be instantiated, by looking at all the inherited branches and seeing if each most specific method
@@
 
-Our formalization has already made abstract methods in a simple way. In other languages they may perform more complicated behaviours.
+Our formalization has a simple form of abstract methods, which behave similarly to conventional methods with respect to conflicts.
+Other languages support more complicated behaviour.
 For instance, in Java 8 when putting two identical abstract methods together by multiple inheritance, there is no conflict error. We omit
@@
 Second, our design choice tends to give more sense on those interesting cases, just as we reject the simple case of diamond inheritance.
-The triangle inheritance should distinguish and treat differently on the two methods instead of fusing them, for they represent different operations, even if they are abstract.
+The triangle inheritance should distinguish and treat differently on the two methods instead of fusing them, since they represent different operations, even if they are abstract.
+Thus our model adopts a very conservative behaviour rather than automatically merging
+methods, and implicitly assumming diamond inheritance.
 

### 2017-10-09 NewVersion/sections/Introduction.tex
S1

@@
 unintentionally conflicting methods to coexist in a class.
+C\# allows this by interface multiple inheritance and explicit method implementation, but there are people argue that in C\# you cannot do "multiple inheritance" \emph{from} interfaces, you can only \emph{implement} multiple interfaces.
+We will have more detailed discussion on this in Section~\ref{sec:relatedwork}.
 C++ accepts the triangle inheritance and
-resolves the ambiguity by \emph{static dispatching} or casts. But the
+resolves the ambiguity by specifying the expected path by \emph{upcasts}. But the
 drawback is that these conflicting methods cannot be further overriden. 
-\bruno{how about C\#? Say something about C\# here.}
+\bruno{how about C\#? Say something about C\# here.}\yanlin{added C\#}
 % However, C++ has

### 2017-10-09 NewVersion/sections/Formalization.tex
S2. DrawableSafeDeck figure

@@
 illustrate in more detail in Section~\ref{subsec:auxdefs}. The form of
-\mbody is different to FJ\bruno{Use xspace to fix the spacing problem
+\mbody{} is different to FJ\bruno{Use xspace to fix the spacing problem
   of macros like mbody}, which has two parameters. The first $I_0$
@@
   in a bit more detail the 2 conditions, since this rule seems to be
-  the more complex one. Some examples may help.} \yanlin{controversial rule. lets discuss later} 
+  the more complex one. Some examples may help.} \yanlin{added} 
 Rule \textsc{(T-Intf)} defines the typing rule for interfaces.
-Interface $I$ type checks only if the following conditions are satisfied: 1) all methods $\overline{M}$ that are directly defined in $I$ type check; 2) method lookup $\mbody(m, I, J)$ successes as long as the method $m$ is defined in any interface $J$ which is an ancestor of $I$; 3)if an original method $m$ defined in interfaces $I$ overrides another original method defined in an ancestor of $I$, then the method types are compatible.
+Interface $I$ type checks only if the following conditions are satisfied: 1) all methods $\overline{M}$ that are directly defined in $I$ type check; 2) method lookup $\mbody(m, I, J)$ successes as long as the method $m$ is originally defined in any interface $J$ which is an ancestor of $I$; 3)if an original method $m$ defined in interfaces $I$ overrides another original method defined in an ancestor of $I$, then the method types are compatible.
 These conditions ensure unambiguity and type soundness of the calculus.
@@
 
-\bruno{Explanation for T-Anno is missing}
+\bruno{Explanation for T-Anno is missing.}\yanlin{Added.}
 Finally, rule \textsc{(T-Anno)} is the typing rule for an expression with static type annotation.

### 2017-10-09 NewVersion/sections/Overview.tex
Section 4
S2. DrawableSafeDeck figure

@@
 interfaces cannot have state.
+
+%In the remainder of this section we show three problems that arize 
+%from unintentional method conflicts. The first two problems
 
@@
 Now, a programmer is designing a
-card game with GUI. He may want to draw a deck on the screen, so he defines a drawable
+card game with a GUI. He may want to draw a deck on the screen, so he defines a drawable
 deck using multiple inheritance:
@@
 1, for instance, when we
-have the UML in Figure~\ref{fig:drawableloggingdeck} and the following code:
+have the UML in Figure~\ref{fig:drawablesafedeck} and the following code:
 
@@
 	\centering
-	\includegraphics[height=2cm]{pics/DrawableLoggingDeck.pdf}
-	\caption{UML graph for \lstinline|DrawableLoggingDeck|.}\label{fig:drawableloggingdeck}
+	\includegraphics[height=2cm]{pics/DrawableSafeDeck.pdf}
+	\caption{UML graph for \lstinline|DrawableSafeDeck|.}\label{fig:drawablesafedeck}
 	\saveSpaceFig

### 2017-10-09 NewVersion/sections/Overview.tex
S2.3 adding nature workaround in c++

@@
 \subsection{Problem 3: Overriding on Individual Branches}\label{subsec:partialoverrides}
-
 We have seen that hierarchical dispatch can dynamically find the latest implementation of a method from one path (or branch). But when
 several branches are merged by triangle inheritance, there is usually demand for updating them separately. For example, someone plans to
-reuse the other features of \lstinline|DrawableLoggingDeck|, but updates the \lstinline|draw| from \lstinline|Drawable| by setting the canvas
-invisible. Unfortunately in traditional models, the merged branches cannot be separately overridden any longer, since overriding
-will hide all branches and break coexistence. Modifying existing code is again unsatisfactory as it affects modularity.\\
+reuse the other features of \lstinline|DrawableSafeDeck|, but updates the \lstinline|draw| from \lstinline|Drawable| by drawing a rectangle representing deck.
+Unfortunately in traditional models, the merged branches cannot be separately overridden any longer, since overriding
+will hide all branches and break coexistence.
+Modifying existing code is again unsatisfactory as it affects modularity.
+The nature way to work around the problem is to define a new component \lstinline|Drawable2| and change the class hierarchy:
+\begin{lstlisting}
+interface Drawable2 extends Drawable {
+  void draw() {
+    JFrame frame = new JFrame("Canvas");
+    frame.setSize(600, 600);
+    frame.getContentPane().setBackground(Color.red);
+    frame.getContentPane().add(new Square(10,10,100,100));
+    ....
+  }
+}
+interface DrawableSafeDeck extends Drawable2, SafeDeck {}
+\end{lstlisting} 
+The drawabck of the workaround is obvious: it breaks the existing hierarchy and changes the old code.
 
@@
 \vspace{3pt}\begin{lstlisting}
-interface DrawableLoggingDeck2 extends DrawableLoggingDeck {
+interface DrawableSafeDeck extends Drawable, SafeDeck {
   void draw() override Drawable {
     JFrame frame = new JFrame("Canvas");
-    frame.setVisible(false);
+    frame.setSize(600, 600);
+    frame.getContentPane().setBackground(Color.red);
+    frame.getContentPane().add(new Square(10,10,100,100));
     ...
@@
 }
-// main program
-DrawableLoggingDeck2 d = new DrawableLoggingDeck2();
-d.Drawable::draw()      // calling draw in DrawableLoggingDeck2
+// main program, calling draw in DrawableSafeDeck
+((Drawable)new DrawableSafeDeck()).draw(); 
 \end{lstlisting}\vspace{3pt}
+
 \textbf{Terminology} The \lstinline|draw| methods we saw before this example are called ``original methods'' in this paper, because they are originally defined in its interface.
-In contrast, \lstinline|DrawableLoggingDeck2| defines a ``hierarchical overriding'' method.
-The difference is that traditional overriding overrides all branches by defining another original method, whereas hierarchical overriding only refines one branch.
+In contrast, \lstinline|DrawableSafeDeck2| defines a ``hierarchical overriding'' method.
+The difference is that traditional method overriding overrides all branches by defining another original method, whereas hierarchical overriding only refines one branch.
 
 In our model, triangle inheritance allows several original methods (branches) to coexist, and hierarchical dispatch first finds the most specific original method (branch), then it finds the most specific hierarchical overriding on that branch.
-A quick counter-example is when there are two hierarchical overriding methods on \lstinline|Drawable| in \lstinline|DrawableLoggingDeck2|, it leads to ambiguity.
+A quick counter-example is when there are two hierarchical overriding methods on \lstinline|Drawable| in \lstinline|DrawableSafeDeck2|, it leads to ambiguity.
 The compiler is supposed to forbid that during compile time.
@@
 Two rules for hierarchical overriding: it can only refine \textbf{original} methods, and cannot jump over original methods with the same signature.
-For instance, writing \lstinline|"void draw()| \lstinline|override Deck {...}"| is disallowed in \lstinline|DrawableLoggingDeck2|, because existing two branches are \lstinline|Drawable.draw| and \lstinline|LoggingDeck.draw|, while \lstinline|Deck.draw| is already covered.
+For instance, writing \lstinline|"void draw()| \lstinline|override Deck {...}"| is disallowed in \lstinline|DrawableSafeDeck2|, because existing two branches are \lstinline|Drawable.draw| and \lstinline|SafeDeck.draw|, while \lstinline|Deck.draw| is already covered.
 It does not really make sense to refine an old branch.

### 2017-10-09 NewVersion/sections/Overview.tex
fix

@@
 \textbf{Terminology} The \lstinline|draw| methods we saw before this example are called ``original methods'' in this paper, because they are originally defined in its interface.
-In contrast, \lstinline|DrawableSafeDeck2| defines a ``hierarchical overriding'' method.
+In contrast, \lstinline|DrawableSafeDeck| defines a ``hierarchical overriding'' method.
 The difference is that traditional method overriding overrides all branches by defining another original method, whereas hierarchical overriding only refines one branch.
@@
 In our model, triangle inheritance allows several original methods (branches) to coexist, and hierarchical dispatch first finds the most specific original method (branch), then it finds the most specific hierarchical overriding on that branch.
-A quick counter-example is when there are two hierarchical overriding methods on \lstinline|Drawable| in \lstinline|DrawableSafeDeck2|, it leads to ambiguity.
+A quick counter-example is when there are two hierarchical overriding methods on \lstinline|Drawable| in \lstinline|DrawableSafeDeck|, it leads to ambiguity.
 The compiler is supposed to forbid that during compile time.
 
-Two rules for hierarchical overriding: it can only refine \textbf{original} methods, and cannot jump over original methods with the same signature.
-For instance, writing \lstinline|"void draw()| \lstinline|override Deck {...}"| is disallowed in \lstinline|DrawableSafeDeck2|, because existing two branches are \lstinline|Drawable.draw| and \lstinline|SafeDeck.draw|, while \lstinline|Deck.draw| is already covered.
+A special rule for hierarchical overriding is: it can only refine \textbf{original} methods, and cannot jump over original methods with the same signature.
+For instance, writing \lstinline|"void draw()| \lstinline|override Deck {...}"| is disallowed in \lstinline|DrawableSafeDeck|, because existing two branches are \lstinline|Drawable.draw| and \lstinline|SafeDeck.draw|, while \lstinline|Deck.draw| is already covered.
 It does not really make sense to refine an old branch.
 
-Similar to many OO languages, the model also allows \textit{super method invocation} in a method body.
+% Similar to many OO languages, the model also allows \textit{super method invocation} in a method body.
 The invocation \lstinline|super.T::m()| will ignore all the subtypes of \lstinline|T|, and only look at \lstinline|T| together with its super interfaces.

### 2017-10-09 NewVersion/sections/Overview.tex
S2.2 by Haoyuan

@@
   \item It allows multiple inheritance.
-  \item Every method is either abstract or implemented to represent a behavior (like Java 8 default methods). 
+  \item Every method is either abstract or implemented with a body (like Java 8 default methods). 
   \item The \lstinline|new| keyword is used to instantiate an interface.
@@
 
-\bruno{Why have we eliminated problem 2 and included it in Problem 1?
-Also why are we not showing how to actually solve it with our approach
-now? I what we had previously made more sense. Please finish up this
-section; show our solution, mention that is is quite similar (and
-inspired by C++), but finish it saying that there are other problems
-that C++ does not address.}
+%\bruno{Why have we eliminated problem 2 and included it in Problem 1?
+%Also why are we not showing how to actually solve it with our approach
+%now? I what we had previously made more sense. Please finish up this
+%section; show our solution, mention that is is quite similar (and
+%inspired by C++), but finish it saying that there are other problems
+%that C++ does not address.}
+
+\noindent\textbf{Our solution:} our language also supports static dispatch as a straightforward
+way to resolve ambiguity. Both conflicting methods are inherited, as shown below:
+  \vspace{3pt}\begin{lstlisting}
+interface Deck { void draw() {...} }
+interface Drawable { JFrame draw() {...} }
+interface DrawableDeck extends Drawable, Deck {}
+
+// main program
+new DrawableDeck().Deck::draw()
+\end{lstlisting}\vspace{3pt}
+The main program is merely an expression. We will
+present static dispatch as an extension in Section~\ref{sec:orthoext}, but our core calculus
+excludes static dispatch
+since it is an orthogonal feature.
+
 \subsection{Problem 2: Dynamic Dispatching}
@@
 // main program
-DrawableSafeDeck d = new DrawableSafeDeck();
-d.shuffleAndDraw(); // ambiguous draw if dynamically dispatched
+new DrawableSafeDeck().shuffleAndDraw() // ambiguous draw if dynamically dispatched
 \end{lstlisting}\vspace{3pt}
-From \lstinline|DrawableSafeDeck|'s point of view, the \lstinline|draw| method seems ambiguous. But ideally we would
+From the perspective of \lstinline|DrawableSafeDeck|, the \lstinline|draw| method seems ambiguous. But ideally we would
 like \lstinline|shuffleAndDraw| to invoke \lstinline|SafeDeck.draw| because they belong to the same branch. Hence it
-seems that we choose dynamic dispatch but also make use of some static type information. Note that this problem can be
-solved by the C++ code below:
+seems that we choose dynamic dispatch but also make use of static type information, since the enclosing type of \lstinline|shuffleAndDraw|specifies the branch.
+Note that in C++, if we put the \lstinline[language=c++]|virtual| keyword in front of every \lstinline|draw| method, the dynamic dispatch correctly does the disambiguation:
 \vspace{3pt}\begin{lstlisting}
 class Deck { public: virtual void draw() {...} ... };
-class Drawable {...};
+class Drawable { public: virtual JFrame draw() {...} };
 class SafeDeck : public Deck { public: virtual void draw() {...} ... };
@@
 DrawableSafeDeck d;
-d.shuffleAndDraw();
+d.shuffleAndDraw(); // calls SafeDeck.draw during that time
+((Drawable*) &d)->draw(); // calls Drawable.draw
 \end{lstlisting}\vspace{3pt}
-By putting ``\lstinline|virtual|'' in front of every method signature, we are enforcing dynamic dispatch in C++.\\
+As an object of \lstinline|DrawableSafeDeck|, when calling \lstinline|shuffleAndDraw|, it dynamically dispatches to the right method \lstinline|SafeDeck.draw|.
+And in C++ we can use also casts for disambiguation.
+Unfortunately, the C++ language, or rather the feature on triangle inheritance, has not been well formalized. Inspired by C++, we
+have formalised this feature into a minimal core calculus, studied and proved the type soundness. It is concise and can readily be imported to other systems.\\
 
-\noindent\textbf{Our solution:} inspired by that, we propose \textit{hierarchical dispatch} in our model
-as the default method lookup algorithm. A \textit{hierarchical invocation}, or \textit{path invocation}, namely
-\lstinline|e.I?m()|, is read as
-``finding the most specific method \lstinline|m| along the path
-\lstinline|I|''. Formally, the meaning of ``along the path \lstinline|I|'' is
-that, if the result of hierarchical dispatch finds \lstinline|J.m()| for some \lstinline|J|, then such a \lstinline|J| must be a super type of \lstinline|e|'s dynamic type for sure, and \lstinline|J| must have a subtyping relation with \lstinline|I| (either \lstinline|J <: I| or \lstinline|J >: I|).
-Intuitively, the most specific \lstinline|m| must be from branch \lstinline|I|, but it can be an updated version after \lstinline|I| because of dynamic dispatch.
-The formal definition will be introduced later.
-
-On the other hand, \lstinline|e.m()| where \lstinline|e| has static type \lstinline|I|, simply behaves the same as \lstinline|e.I?m()| in our model.
-Such a dispatching algorithm makes use of both the static type and the dynamic type of the receiver, so it is seemingly a combination of static and dynamic dispatch.
-Intuitively, the static type specifies one branch to avoid ambiguity, and the dynamic type finds the latest version on that branch.
-It may still introduce ambiguity when there are multiple paths from the static type to the dynamic type, and those paths cause conflicts.
-We disallow this kind of conflict to ensure unambiguity.
-That is to say, we do not allow two methods to override a same base method when they cause conflicts.
-This is natural, as they are just two versions of the same operation, hence it is no longer an ``unintentional'' conflict, but the diamond problem.
+\noindent\textbf{Our solution:} we propose \textit{hierarchical dispatch} in our model
+as the default method lookup algorithm. During the runtime, the method call \lstinline|e.m()|
+makes use of both the static type and the dynamic type of the receiver, so it is seemingly a
+combination of static and dynamic dispatch. Intuitively, the static type specifies one branch
+to avoid ambiguity, and the dynamic type finds the latest implementation on that branch. The formal algorithm
+will be introduced later.
 
@@
   void shuffle() {...}
-  void shuffleAndDraw() { shuffle(); draw(); }
+  void shuffleAndDraw() { this.shuffle(); this.draw(); }
 }
@@
 // main program
-new DrawableSafeDeck().shuffleAndDraw() // calls Deck.shuffle, and then SafeDeck.draw
-\end{lstlisting}\vspace{3pt}\haoyuan{mention how the language syntax is different from our formalization. FHJ is only a subset.}
-Note that the \lstinline|draw()| in \lstinline|shuffleAndDraw()| is short for \lstinline|this.draw()|, and is equivalent to \lstinline|this.Deck?draw()|.
-It is because the compiler is able to know that the receiver ``\lstinline|this|'' exactly has static type \lstinline|Deck|.
-Hence hierarchical dispatch eliminates ambiguity in a concise way.\\
+new DrawableSafeDeck().shuffleAndDraw() // SafeDeck.draw is called
+\end{lstlisting}\vspace{3pt}
+So in the runtime, when \lstinline|this.draw()| in called,
+the dynamic type of the receiver is \lstinline|DrawableSafeDeck|, but the self-reference actually
+has static type \lstinline|Deck|. The \textit{hierarchical invocation} can be read as 
+``finding the most specific \lstinline|draw| along the path \lstinline|Deck|''. The meaning of ``along path
+\lstinline|Deck|'' not only implies what \lstinline|Deck| inherits, but also the domain of its subtypes up to the
+dynamic type. Finally \lstinline|SafeDeck.draw| is correctly returned.
 
-\noindent\textbf{Comparison with C++:} as an industrial language, C++ is more practical and flexible to use with lots of features, for example, it handles fields and virtual inheritance, and it allows explicit casts.
-But the compilation is more or less complicated, and sometimes unclear to programmers, which affects its type safety and people's understanding.
-The compilation seems to look into the expressions and the real (runtime) types for ambiguity check in method dispatching, and sometimes the errors are thrown by the linker.
-In contrast, inspired by C++ we formalize the concept of hierarchical dispatch in our model, with type-checking rules and semantics.
-The compilation only cares about the type of the receiver in method invocation, but the rules ensure type soundness so that the evaluation never throws errors on a program that type-checks.
-C++ does not hold type soundness for unintentional method conflicts, it actually accepts the diamond inheritance, and only complains on bad invocations.
-Whereas our model forbids the diamond case, which derives a strong type-safe system, and there are more theoretical aspects in Section~\ref{sec:formalization}.
-\haoyuan{not sure if this paragraph makes sense or is correct.
-Needs refs.}
+In our language model, there are two types of casts: implicit casts and explicit upcasts. The implicit casts appear
+when passing arguments and returning expressions, they are also upcasts. Hence all casts are safe, and the difference
+from C++ is that C++ checks ambiguity on casts, whereas our model is open to those safe casts. Unfortunately,
+it introduces ambiguity in what we call ``the diamond inheritance'': when two methods override a same base method
+but then accepted by multiple inheritance. The definition of such interfaces has to be rejected,
+but this is natural as they are just two versions of the same operation, hence it is no longer an ``unintentional'' conflict.
+Our proof demonstrates that it is a sufficient condition for type soundness.
+
+The expression ``\lstinline|((Deck) new DrawableSafeDeck()).draw()|'' in our language also invokes \lstinline|SafeDeck.draw| 
+by an explicit upcast.
+\haoyuan{mention how the language syntax is different from our formalization. FHJ is only a subset.}
 

### 2017-10-09 NewVersion/paper.tex
Introduction
added page number
Abstract and Intro

@@
 \documentclass{llncs}
+\pagestyle{plain}
 
@@
   \textbf{H}ierarchical \textbf{J}ava} (\name{}) that deals with
-unintentional method conflicts.
-In our
-new model, conflicting methods arising from unrelated methods can
-coexist in the same component. Furthermore our model supports
-\emph{hierarchical method overriding}: that is, methods can be
-\emph{independently overridden} along the multiple inheritance
-hierarchy. To avoid ambiguity, hierarchical information is 
-employed in method dispatching, which uses a combination of static and
-dynamic type information to choose the implementation of a method at
-run-time. We give illustrative examples of our language and features
+unintentional method conflicts.  In our new model, which is partly
+inspired by C++, conflicting methods arising from unrelated methods
+can coexist in the same class, and \emph{hierarchical dispatching}
+supports unambigous lookups in the presence of such conflicting
+methods.  To avoid ambiguity, hierarchical information is employed in
+method dispatching, which uses a combination of static and dynamic
+type information to choose the implementation of a method at run-time.
+Furthermore, unlike all existing inheritance models, our model
+supports \emph{hierarchical method overriding}: that is, methods can
+be \emph{independently overridden} along the multiple inheritance
+hierarchy. We give illustrative examples of our language and features
 and formalize \name{} as a minimal Featherweight-Java style calculus.

### 2017-10-09 NewVersion/sections/Introduction.tex
Abstract and Intro

--- 2017-10-09 NewVersion/sections/Introduction.tex
@@
 C++ and C\# do allow for two
-unintentionally conflicting methods to coexist in a class. 
-C++ accepts the triangle inheritance and
-resolves the ambiguity by \emph{static dispatching} or casts. But the
-drawback is that these conflicting methods cannot be further overriden. 
-\bruno{how about C\#? Say something about C\# here.}
+unintentionally conflicting methods to coexist in a class. C\# allows
+this by interface multiple inheritance and explicit method
+implementations. But since C\# is a single inheritance language, 
+it is only possible to \emph{implement} multiple interfaces (but not
+multiple classes). %We will have more detailed discussion on this in Section~\ref{sec:relatedwork}.
+C++ accepts triangle inheritance and
+resolves the ambiguity by specifying the expected path by
+\emph{upcasts}. However
+neither the C\# or C++ approaches allow
+such conflicting methods to be further overriden. 
 % However, C++ has
@@
 \begin{itemize}
-	\item \textbf{Hierarchical dispatch algorithm:} an algorithm that integrates both the static type and dynamic type for method dispatch, and hence
-	ensures unambiguity as well as extensibility.
+	\item \textbf{Formalization of a hierarchical dispatching algorithm} that integrates both the static type and dynamic type for method dispatch, and hence
+	ensures unambiguity as well as extensibility in the presence
+        of unintentional method conflicts.
 	\item \textbf{Hierarchical overriding:} a novel notion that allows

### 2017-10-10 NewVersion/sections/RelatedWork.tex
S1
Related Work

@@
-\section{Related Work}
-Here we describe related work in four parts. We discuss from mainstream popular multiple 
-inheritance models to several specific models (C++ and \csharp) which are closest to our work. Then we 
-discuss similar techniques used in \self. Finally, we discuss the foundation and related work of our formalization.
+\section{Related Work}~\label{sec:relatedwork}
+We describe related work in four parts. We first discuss mainstream popular multiple 
+inheritance models and the specific models (C++ and \csharp) which are closest to our work. Then we 
+discuss related techniques used in \self. Finally, we discuss the foundation and related work of our formalization.
 
@@
 strong line between units of reuse and object factories. Traits act
-as units of reuse, containing functionality code; while classes,
-assembled from traits, act as object factories. Java 8
+as units of reuse, containing functionality code. Classes, on the
+other hand, are
+assembled from traits and act as object factories. Java 8
 interfaces are closely related to traits: concrete method
 implementations are allowed (via the \textbf{\texttt{default}}
-keyword) inside interfaces and there are also proposals such as FeatherTrait Java~\cite{Liquori08ftj} 
-for extending Java with traits. There are extensions~\cite{reppy2006foundation,Reppy:2007:MT:2394758.2394784} to 
-the original trait model with various advanced features such as \emph{renaming}. As discussed in Section~\ref{sec:overview},
-the renaming feature helps to solve the unintentional method conflicts problem, however, it breaks structural subtyping.
+keyword) inside interfaces, thus allowing for a restricted form 
+of multiple inheritance.
+There are also proposals such as FeatherTrait Java~\cite{Liquori08ftj} 
+for extending Java with traits. Extensions~\cite{reppy2006foundation,Reppy:2007:MT:2394758.2394784} to 
+the original trait model exists with various advanced features, such as \emph{renaming}. As discussed in Section~\ref{sec:overview},
+the renaming feature helps to solve the unintentional method conflicts
+problem. However, it breaks structural subtyping.
 
@@
 two methods with the same signature from two different units to
-coexist. The ambiguity is resolved either by programmers explicitly or
-by setting a linearised composition. This is the common drawback of
-the above-mentioned models versus our model.
+coexist. In contrast, our work provides mechanisms that allows 
+methods with the same signatures, but different parents to coexist 
+in a class. Disambiguation is possible in many cases by using both 
+static and dynamic type information during method dispatching.
 
 \subsection{Resolving Unintentional Method Conflicts}
-There are a few languages that may have realized the problem of
+A few language implementations have realized the problem of
 unintentional conflicts and provide some support for it.
@@
 Although C++ support this flexibility, dynamic dispatching on
-unintentional conflicting methods is problematic, as discussed in Section~\ref{sec:overview}.\bruno{why? give example of
-  something that goes wrong?}
-Furthermore, C++ does not support hierarchical overriding compared to our
-model.
+unintentional conflicting methods is problematic, as discussed in
+Section~\ref{sec:overview}.\bruno{where in the overview are we
+  discussing this?}
+Furthermore, compared to our
+model, C++ does not support hierarchical overriding.
 \end{comment}
@@
 C++ supports a very flexible inheritance model and allows programmers to choose either static dispatch or dynamic dispatch for method lookup.
-It allows the existance of unintentional conflicts and uses static dispatch to resolve them, as discussed in Section~\ref{sec:overview}. 
+It allows the existence of unintentional conflicts and uses static
+dispatch to resolve them, as discussed in Section~\ref{sec:overview}. 
+\bruno{if we are dropping the static dispatching discussion this text
+  may be outdated.}
 With virtual methods, dynamic dispatch is used and 
 method lookup algorithm will find the most specific method definition.\yanlin{to revise: be consistant with introduction}
-Although C++ support this flexibility, it does not support hierarchical overriding compared to our
-model.
-However, there is one workaround we found online that mimicks hierarchical overriding, we call it the "MiddleMan" approach, as shown in Figure~\ref{fig:middleman}.
-In this example, class \texttt{A} and \texttt{B} are two classes that both defines a method \texttt{m} unintentionally.
+A contribution of our work is to provide a minimal formal model of
+hierarchical dispatching, whereas C++ can be viewed as a real-world
+implementation. As far as we know there is no any formal model that
+captures this aspect of the C++ method dispatching model. 
+\bruno{The discussion points out further differences. We need to refer
+to that discussion here too.}
+
+Although C++ supports hierarchical dispatching, it does not support
+hierarchical overriding.  However, there is a possible
+workaround\footnote{put the url here} that mimicks hierarchical
+overriding.  We call it the "MiddleMan" approach, as shown in
+Figure~\ref{fig:middleman}. In this example, classes \texttt{A} and
+\texttt{B} are two classes that both define a method with the same
+name \texttt{m}
+unintentionally.
 
@@
 Moreover, no direct syntax support makes the "MiddleMan" code cumbersome to write.
-Finally, the approach is ad-hoc, meaning that the class \texttt{MiddleMan} shown in Figure~\ref{fig:middleman} is not general enough to be used in other cases, more middle-mans are needed if partial method overrides happens in other classes.
+Finally, the approach is ad-hoc, meaning that the class \texttt{MiddleMan} shown in Figure~\ref{fig:middleman} is not general enough to be used in other cases: more middle-mans are needed if partial method overrides happens in other classes.
 
-\begin{figure*}
+\begin{figure*}[t]
 \begin{lstlisting}
@@
 
-\noindent  {\bf \csharp{} Explicit method implementation.}
-Explicit method implementation is a special feature supported by
+\noindent  {\bf \csharp{} Explicit method implementations.}
+Explicit method implementations is a special feature supported by
 \csharp{}. As described in \csharp{} documentation~\cite{csharpdoc}, a
@@
 only be accessed through an instance of the interface. Explicit
-interface implementation allows an interface to inherit multiple 
+interface implementations allows an interface to inherit multiple 
 interfaces that share the same member names and give each interface
@@
 same signature. However, there are two critical differences to \MIM{}:
-(1) default implementations are not allowed in \csharp{} interfaces; 
-(2) there is only one level of hierarchical overriding to refine conflicting methods individually.
+(1) default method implementations are not allowed in \csharp{} interfaces; 
+(2) there is only one level conflicting method implementations at the
+class that implements the multiple parent interfaces. Further
+overriding of those methods is not possible in subclasses.
 
@@
 In the prototype-based language \self{}~\cite{Chambers1991}, inheritance is a basic feature.
-It does not include classes but instead allow individual objects to inherit from (or delegate to) other objects. 
+\self{} does not include classes but instead allows individual objects to inherit from (or delegate to) other objects. 
 Although it is different from class-based languages, the multiple inheritance model is somehow similar. The \self{}
@@
 relation with \emph{prioritized parents} but also adopts \emph{sender path tiebreaker rule} for method lookup.
-It specifies that ``\emph{if two slots with the same name are defined in equal-priority parents of the receiver, but only 
+In \self{} ``\emph{if two slots with the same name are defined in equal-priority parents of the receiver, but only 
 one of the parents is an ancestor or descendant of the object containing the method that is sending the message,
 then that parent's slot takes precedence over the over parent's slot}''. 
-Similar to our model, this sender path tiebreaker rule resolves ambiguities between unrelated abstractions. However,
+Similarly to our model, this sender path tiebreaker rule resolves ambiguities between unrelated slots. However,
 it is used in a prototype-based language setting and it does not support method hierarchical overriding as \MIM{} does.
@@
 Featherweight Scala~\cite{Cremet2006}, and so on.
-FJ provides the standard model of formalizing a Java-like object-oriented language and 
+FJ provides the standard model of formalizing a Java-like object-oriented languages and 
 is easily extensible. In terms of formalization, the key novelty of our model is the use of 
@@
 know, this technique has not appeared in the literature before. The static type annotation is of vital 
-importance in our hierarchical dispatch algorithm.
+importance in our hierarchical dispatch algorithm, and it allows for a
+more precise subject-reduction theorem as discussed in
+Section~\ref{}\bruno{put reference and make sure that we discuss this topic}.

### 2017-10-10 NewVersion/sections/Overview.tex
Done S2 ready for review.

@@
-\section{A Running Example: DrawableDeck}~\label{sec:overview}
-This section illustrates the features of our model for
-resolving unintentional method conflicts. As mentioned before, such a
-case arises when two inherited methods happen to have the same
-signature, but with different semantics and functionality. This
-situation is troublesome for programmers that use multiple
-inheritance. Below we illustrate with a running example called
-\lstinline|DrawableDeck|, which models a drawable deck of cards. 
-Note that we use a Java-like syntax
-throughout the paper, and all types are defined with the keyword
-``\lstinline|interface|''. The concept is closely related to Java 8
-interfaces with default methods~\cite{bono14} and traits. For simplicity, an interface in our model has
-the following characteristics:
+\section{A Running Example: Drawable Deck}~\label{sec:overview}
+This section illustrates the problem of unintentional method conflicts for motivation,
+together with the features of our model on addressing this issue, by
+a simple running example. In the following text we will introduce three
+problems one by one, and lead the discussion on possible workarounds and our solutions.
+Here it is worth clarifying that problem 1 and 2 are the entrance to the general problem,
+and languages like C++ can give nice solutions to both, hence we are not basically proposing
+some novel algorithm on conflict resolution, but inspired to formalize a minimal calculus
+on this feature with type soundness. However, for problem 3 there is no satisfactory approach
+in existing languages, thus we propose our new feature for direct support.
+
+In the rest of the paper, we use a Java-like syntax for programs. All types are defined with the keyword
+``\lstinline|interface|''; the concept is closely related to Java 8
+interfaces with default methods~\cite{bono14} and traits. In short, 
+an interface in our model has the following characteristics:
 \begin{itemize}
@@
 	\item The \lstinline|new| keyword is used to instantiate an interface.
+	\item It cannot have state.
 \end{itemize}
-Furthermore, similarly to traits or Java 8 with default methods,
-interfaces cannot have state.
-
 %In the remainder of this section we show three problems that arize 
@@
 \end{lstlisting}\vspace{3pt}
-Note that the two \lstinline|draw| methods have the same names and parameter types,
-but the return types can be different. In \lstinline|Deck|,
+Note that in \lstinline|Deck|,
 \lstinline|draw| uses \lstinline|println|, which is a
@@
 \end{comment}
-Now, a programmer is designing a
+
+Now, supppose that a programmer is designing a
 card game with a GUI. He may want to draw a deck on the screen, so he defines a drawable
@@
 languages. Nevertheless at this point, languages like Java simply treat the two \lstinline|draw| methods
-as the same, and hence they throw a compile error on \lstinline|DrawableDeck| about the conflict, though accidentally.
+as the same, and hence the compiler throws an error
+on \lstinline|DrawableDeck| about the conflict.
 
-Now one may quickly come up with a workaround, which is to create a new \lstinline|draw| method in \lstinline|DrawableDeck| to
-explicitly override the old ones. However, the two conflicting methods
-have totally different functionalities. Therefore merging
-them into one does not make any sense. This non-solution will hide the
+This case is the so-called \textit{unintentional method conflicts}. It arises when two inherited methods happen have
+the same name and parameter types, but they are totally designed for different functionalities with different semantics.
+Now one may quickly come up with a workaround, which is to manually merge them, by
+creating a new \lstinline|draw| method in \lstinline|DrawableDeck| to
+override the old ones. However, merging two methods with totally different functionalities does not make any sense.
+This non-solution will hide the
 old methods and break independent extensibility.
 
-\paragraph{{\bf Potential Fixes:}}
-There are several other workarounds
+\paragraph{Problem:} How to resolve unintentional method conflicts and invoke the conflicting methods separately without
+ambiguity.
+
+\paragraph{Potential Fixes:} There are several other workarounds
 that come to our mind. We briefly discuss those potential fixes and
@@
 \begin{itemize}
-  \item \textbf{I. Delegation.} As an alternative to multiple inheritance,
+  \item \textit{I. Delegation.} As an alternative to multiple inheritance,
   delegation can be used by introducing two fields (or field methods) with
@@
   introduces a lot of boilerplate code.
-  \item \textbf{II. Refactor Drawable and/or Deck to rename the methods.} If
+  \item \textit{II. Refactor Drawable and/or Deck to rename the methods.} If
   the source code for \lstinline|Drawable| or \lstinline|Deck| is available
@@
   modifying existing code, and may not be possible if code is unavailable.
-  \item \textbf{III. Method exclusion/renaming in traits.} Some trait models
+  \item \textit{III. Method exclusion/renaming in traits.} Some trait models
   support method exclusion/renaming. Those features
@@
   names can affect other code blocks.
-  \item \textbf{IV. Static dispatch.} Some other languages like C++ have
-  direct support for the triangle inheritance. For instance, C++ allows both
-  conflicting methods to coexist, and resolves the ambiguity by static dispatch:
-  \vspace{3pt}\begin{lstlisting}[language=c++]
-  class Deck { public: void draw() {...} };
-  class Drawable { public: JFrame draw() {...} };
-  class DrawableDeck : public Drawable, public Deck {};
-
-  // in main
-  DrawableDeck d;
-  d.Deck::draw(); // prints the message
-  \end{lstlisting}\vspace{3pt}
 \end{itemize}
@@
 
-\noindent\textbf{Our solution:} our language also supports static dispatch as a straightforward
-way to resolve ambiguity. Both conflicting methods are inherited, as shown below:
+\paragraph{Our solution:} It is important to preserve both conflicting methods
+during inheritance instead of explicitly merging them. That is to say, the compiler
+needs to accept \lstinline|DrawableDeck|. And then the disambiguation is done by
+up-casts, so as to specify the branch we would like to call.
+
 \vspace{3pt}\begin{lstlisting}
@@
 // main program
-new DrawableDeck().Deck::draw()
+((Deck) new DrawableDeck()).draw() // calls Deck.draw
 \end{lstlisting}\vspace{3pt}
-The main program is merely an expression. We will
-present static dispatch as an extension in Section~\ref{sec:orthoext}, but our core calculus
-excludes static dispatch
-since it is an orthogonal feature.
+In our language, the main program is merely an expression. The above cast indicates
+that we expect to invoke the \lstinline|draw| from branch \lstinline|Deck|.
+
+We call this case the triangle inheritance, where two unintentionally conflicting methods
+are accepted by multiple inheritance. Note that C++ supports this feature and also addresses the
+ambiguity by up-casts. The code for the above example is similar.
 
 \subsection{Problem 2: Dynamic Dispatching}
-So far it seems that static dispatch is the simplest and most straightforward approach,
-as long as the language model accepts unintentionally conflicting methods. However, dynamic
-dispatching appears to be more common in OO programming in order for code reuse. Following the previous example,
-we reimplement \lstinline|Deck| with more features:
+It seems that the solution to problem 1 is straightforward and easy to achieve, but things can
+become more complicated with dynamic dispatching. Dynamic
+dispatching is very common in OO programming in order for code reuse. Let us expand the previous
+example a bit, by redefining those interfaces with more features:
 
@@
   void shuffle() {...}
-  void shuffleAndDraw() { shuffle(); draw(); }
+  void shuffleAndDraw() { this.shuffle(); this.draw(); }
 }
 \end{lstlisting}\vspace{3pt}
-Here \lstinline|shuffleAndDraw| is a typical method that invokes \lstinline|draw| in its definition. Ideally,
+Here \lstinline|shuffleAndDraw| invokes \lstinline|draw| from its own enclosing type. Ideally,
 we want that invocation to be dynamically dispatched. This is important, because a programmer may define a subtype
@@
 \end{lstlisting}\vspace{3pt}
-With static dispatch, we have to copy the \lstinline|shuffleAndDraw| code into \lstinline|SafeDeck|,
-for the adaptation to the new \lstinline|draw|. Yet dynamic dispatching immediately saves us from the duplicate work,
-since the method becomes automatically adaptive. Nevertheless, as seen before, dynamic dispatch would take us back to problem
-1, for instance, when we
-have the UML in Figure~\ref{fig:drawablesafedeck} and the following code:
+With static dispatching, we may have to copy the \lstinline|shuffleAndDraw| code into \lstinline|SafeDeck|,
+so as to be adaptive to the new \lstinline|draw|. Yet dynamic dispatching immediately saves us from the duplicate work,
+since the method becomes automatically adaptive. Nevertheless, as seen before, dynamic dispatch would potentially introduce ambiguity,
+for instance, when we have the UML in Figure~\ref{fig:drawablesafedeck} and the following code:
 
@@
 // main program
-new DrawableSafeDeck().shuffleAndDraw() // ambiguous draw if dynamically dispatched
+new DrawableSafeDeck().shuffleAndDraw()
 \end{lstlisting}\vspace{3pt}
+When the \lstinline|DrawableSafeDeck| object calls \lstinline|shuffleAndDraw|, the implementation in \lstinline|Deck|
+is surely dispatched. But then \lstinline|shuffleAndDraw| invokes ``\lstinline|this.draw()|'', and at this point, the receiver
+is replaced by the object \lstinline|new DrawableSafeDeck()|.
+
 From the perspective of \lstinline|DrawableSafeDeck|, the \lstinline|draw| method seems ambiguous. But ideally we would
-like \lstinline|shuffleAndDraw| to invoke \lstinline|SafeDeck.draw| because they belong to the same branch. Hence it
-seems that we choose dynamic dispatch but also make use of static type information, since the enclosing type of \lstinline|shuffleAndDraw|specifies the branch.
-Note that in C++, if we put the \lstinline[language=c++]|virtual| keyword in front of every \lstinline|draw| method, the dynamic dispatch correctly does the disambiguation:
-\vspace{3pt}\begin{lstlisting}
-class Deck { public: virtual void draw() {...} ... };
-class Drawable { public: virtual JFrame draw() {...} };
-class SafeDeck : public Deck { public: virtual void draw() {...} ... };
-class DrawbaleSafeDeck : public Drawable, public SafeDeck {};
+like \lstinline|shuffleAndDraw| to invoke \lstinline|SafeDeck.draw| because they belong to the same branch. It
+seems that we choose dynamic dispatch but also make use of static type information, since the type of this-reference (\lstinline|Deck|) specifies the branch.
+Note that in C++, if we put the \lstinline[language=c++]|virtual| keyword in front of every \lstinline|draw| method, that means
+we enforce the dynamic dispatch, and it does the disambiguation correctly.
+Unfortunately, the C++ language, or rather the feature on triangle inheritance, has not been well formalized.
 
-// in main
-DrawableSafeDeck d;
-d.shuffleAndDraw(); // calls SafeDeck.draw during that time
-((Drawable*) &d)->draw(); // calls Drawable.draw
-\end{lstlisting}\vspace{3pt}
-As an object of \lstinline|DrawableSafeDeck|, when calling \lstinline|shuffleAndDraw|, it dynamically dispatches to the right method \lstinline|SafeDeck.draw|.
-And in C++ we can use also casts for disambiguation.
-Unfortunately, the C++ language, or rather the feature on triangle inheritance, has not been well formalized. Inspired by C++, we
-have formalised this feature into a minimal core calculus, studied and proved the type soundness. It is concise and can readily be imported to other systems.\\
+\paragraph{Problem:} How to ensure that the correct method is invoked, by disambiguating conflicting methods in a dynamically dispatched setting, and how to achieve such a formalized language model.
+\\
 
-\noindent\textbf{Our solution:} we propose \textit{hierarchical dispatch} in our model
+\paragraph{Our solution:} Inspired by C++, we have formalized this feature into a minimal core calculus,
+studied and proved the type soundness. It is concise and can readily be imported to other systems. 
+And in the formalization, we propose \textit{hierarchical dispatch} in our model
 as the default method lookup algorithm. During the runtime, the method call \lstinline|e.m()|
@@
 \end{lstlisting}\vspace{3pt}
-So in the runtime, when \lstinline|this.draw()| in called,
-the dynamic type of the receiver is \lstinline|DrawableSafeDeck|, but the self-reference actually
-has static type \lstinline|Deck|. The \textit{hierarchical invocation} can be read as 
+During the runtime, when \lstinline|this.draw()| in called,
+the dynamic type of the receiver is \lstinline|DrawableSafeDeck|, but the static type is actually
+\lstinline|Deck|. Here it is an instance of the \textit{hierarchical invocation}, which can be read as 
 ``finding the most specific \lstinline|draw| along the path \lstinline|Deck|''. The meaning of ``along path
-\lstinline|Deck|'' not only implies what \lstinline|Deck| inherits, but also the domain of its subtypes up to the
+\lstinline|Deck|'' not only implies what \lstinline|Deck| inherits, but also the domain of its subtypes until the
 dynamic type. Finally \lstinline|SafeDeck.draw| is correctly returned.
@@
 
-The expression ``\lstinline|((Deck) new DrawableSafeDeck()).draw()|'' in our language also invokes \lstinline|SafeDeck.draw| 
-by an explicit upcast.
-\haoyuan{mention how the language syntax is different from our formalization. FHJ is only a subset.}
+\subsection{Problem 3: Overriding on Individual Branches}\label{subsec:partialoverrides}
 
-\subsection{Problem 3: Overriding on Individual Branches}\label{subsec:partialoverrides}
-We have seen that hierarchical dispatch can dynamically find the latest implementation of a method from one path (or branch). But when
-several branches are merged by triangle inheritance, there is usually demand for updating them separately. For example, someone plans to
-reuse the other features of \lstinline|DrawableSafeDeck|, but updates the \lstinline|draw| from \lstinline|Drawable| by drawing a rectangle representing deck.
-Unfortunately in traditional models, the merged branches cannot be separately overridden any longer, since overriding
-will hide all branches and break coexistence.
-Modifying existing code is again unsatisfactory as it affects modularity.
-The nature way to work around the problem is to define a new component \lstinline|Drawable2| and change the class hierarchy:
-\begin{lstlisting}
-interface Drawable2 extends Drawable {
+This is not the end of the story, because after the programmer defines \lstinline|DrawableSafeDeck|, he needs to override
+\lstinline|Drawable.draw|, and give the implementation of drawing, so that the deck can indeed be visualized on the canvas.
+
+\paragraph{Problem:} how to update the conflicting methods separately, after the triangle inheritance.
+
+\paragraph{Potential fixes:} Unfortunately as far as we are concerned, the existing approaches are unsatisfactory.
+One direction is to simply avoid this issue, by putting overriding before inheritance. For example, we define a new component
+that extends \lstinline|Drawable|, simply draw the deck as a rectangle, and modifies the hierarchy:
+\vspace{3pt}\begin{lstlisting}
+interface DrawableRect extends Drawable {
   void draw() {
@@
 }
-interface DrawableSafeDeck extends Drawable2, SafeDeck {}
-\end{lstlisting} 
-The drawabck of the workaround is obvious: it breaks the existing hierarchy and changes the old code.
 
-\noindent\textbf{Our solution:} an additional feature of our model is \textit{hierarchical overriding}. It allows conflicting methods
+interface DrawableSafeDeck extends DrawableRect, SafeDeck {}
+\end{lstlisting} \vspace{3pt}
+This workaround seems to work, but there are severe issues:
+\begin{itemize}
+	\item It changes the hierarchy and existing code, hence breaks the modularity.
+	\item The demand for separate overriding after the triangle inheritance comes especially when there is interaction. In the above code we assume
+	that the overriding is unrelated to \lstinline|Deck|. But when the drawing relies on some information of the \lstinline|Deck|
+	object, we have to either introduce field methods for delegation, or change the signature of \lstinline|draw| to take a parameter.
+	Either way introduces unnecessary complexity and affects extensibility.
+\end{itemize}
+Another workaround in C++ adopts templates, but there are still issues and we put the discussion in Section~\ref{subsec:middleman}.
+
+\paragraph{Our solution:} An additional feature of our model is \textit{hierarchical overriding}. It allows conflicting methods
 to be overridden on individual branches, and hence offers independent extensibility. The above example can be easily realized by:
@@
 }
-// main program, calling draw in DrawableSafeDeck
-((Drawable)new DrawableSafeDeck()).draw(); 
+
+// main program
+((Drawable)new DrawableSafeDeck()).draw(); // calls the latest draw
 \end{lstlisting}\vspace{3pt}
+The direct support for individual overriding also works when there is interaction. In our formalization, this feature is necessary
+and also involves in the algorithm of hierarchical dispatch.
 
-\textbf{Terminology} The \lstinline|draw| methods we saw before this example are called ``original methods'' in this paper, because they are originally defined in its interface.
-In contrast, \lstinline|DrawableSafeDeck| defines a ``hierarchical overriding'' method.
+\paragraph{Terminology:} The \lstinline|draw| methods we saw in previous subsections are called \textit{original methods} in this paper, because they are originally defined in its interface.
+In contrast, \lstinline|DrawableSafeDeck| defines a \textit{hierarchical overriding method}.
 The difference is that traditional method overriding overrides all branches by defining another original method, whereas hierarchical overriding only refines one branch.
 
-In our model, triangle inheritance allows several original methods (branches) to coexist, and hierarchical dispatch first finds the most specific original method (branch), then it finds the most specific hierarchical overriding on that branch.
+\paragraph{Overview of hierarchical dispatching algorithm:} In our model, triangle inheritance allows several original methods (branches) to coexist, and hierarchical dispatch first finds the most specific original method (branch), then it finds the most specific hierarchical overriding on that branch.
 A quick counter-example is when there are two hierarchical overriding methods on \lstinline|Drawable| in \lstinline|DrawableSafeDeck|, it leads to ambiguity.
-The compiler is supposed to forbid that during compile time.
+The compiler is supposed to forbid the case.
 

### 2017-10-10 NewVersion/sections/RelatedWork.tex
Done S2 ready for review.

@@
 
-\subsection{Resolving Unintentional Method Conflicts}
+\subsection{Resolving Unintentional Method Conflicts}\label{subsec:middleman}
 A few language implementations have realized the problem of

### 2017-10-10 NewVersion/sections/Formalization.tex
S3

@@
 \section{Formalization}~\label{sec:formalization}
-In this section, we present the formal model \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), based on
+In this section, we present the formal model called \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), following similar style of 
 Featherweight Java~\cite{Igarashi01FJ}. The syntax, typing rules,
 small-step semantics and theorems for type soundness are presented.
-\bruno{In general, please try to use latex paragraphs to add more
-  structure and emphasize contents.}
 
-\vspace{-2ex}
+% \vspace{-2ex}
 \subsection{Syntax}
@@
 
-%From this point we can view that we
-%are actually modelling a class model that supports multiple
-%inheritance. 
-Object creation is represented by $\new I$.
-If any unimplemented abstract methods are defined in interface $I$ (or inherited from parents), then object creation fails.
-Fields and primitive types are not modelled in \MIM{}.
-
-The metavariables $I, J, K$ range over interface names; $x$ ranges over variables; $m$ ranges over method names; $e$ ranges over expressions; and $M$ ranges over method declarations.
+\paragraph{Notations}
+The metavariables $I, J$ range over interface names; $x$ ranges over variables; $m$ ranges over method names; $e$ ranges over expressions; and $M$ ranges over method declarations.
 Following Featherweight Java, we assume that the set of variables includes the special variable \kwthis, which cannot be used as the name of an argument to a method.
@@
 
+\paragraph{Interfaces}
 In order to achieve multiple inheritance, an interface can have a set of 
@@
 
+\paragraph{Methods}
 The method declaration $\method{I}{m}{I_x}{x}{J}{e}$ introduces a
@@
 For simplicity, overloading is not modelled for methods, which
-implies that we can uniquely identify a method by its name.\yanlin{the terminology of original methods should have been proposed in Overview.}
-\bruno{Then please do so.}
+implies that we can uniquely identify a method by its name.
 
+\paragraph{Expressions \& Values}
 Expressions can be standard constructs such as variables, method
 invocation, or object creation, together with casts. 
+Object creation is represented by $\new I$.
+If any unimplemented abstract methods are defined in interface $I$ (or inherited from parents), then object creation fails.
+Fields and primitive types are not modelled in \MIM{}.
 Again, to be concise, the casts are merely safe up-casts. Those cast-expressions
@@
 illustrate in more detail in Section~\ref{subsec:auxdefs}. The form of
-\mbody{} is different to FJ\bruno{Use xspace to fix the spacing problem
-  of macros like mbody}, which has two parameters. The first $I_0$
+\mbody{} is different to FJ, which has two parameters. The first $I_0$
 represents the dynamic type and the second, the static type. If the
@@
 
-\bruno{Explanation for T-Anno is missing.}\yanlin{Added.}
 Finally, rule \textsc{(T-Anno)} is the typing rule for an expression with static type annotation.

### 2017-10-10 NewVersion/sections/Overview.tex
Section 2.1

@@
 \section{A Running Example: Drawable Deck}~\label{sec:overview}
-This section illustrates the problem of unintentional method conflicts for motivation,
+This section illustrates the problem of unintentional method conflicts,
 together with the features of our model on addressing this issue, by
 a simple running example. In the following text we will introduce three
-problems one by one, and lead the discussion on possible workarounds and our solutions.
-Here it is worth clarifying that problem 1 and 2 are the entrance to the general problem,
-and languages like C++ can give nice solutions to both, hence we are not basically proposing
-some novel algorithm on conflict resolution, but inspired to formalize a minimal calculus
-on this feature with type soundness. However, for problem 3 there is no satisfactory approach
-in existing languages, thus we propose our new feature for direct support.
+problems one by one, and have a discussion on possible workarounds and
+our solutions.
+Problems 1 and 2 are related to hierarchical dispatching, and in 
+C++ it is possible to have similar solutions solutions to both
+problems. Hence it is important to emphasize that, with respect to
+hierarchical dispatching, our contribution is not a novel
+mechanism. Instead, 
+inspired by the C++ solution, our contribution is the formalization a minimal calculus
+of this feature together with a proof type soundness. However, for the final problem, there is no satisfactory approach
+in existing languages, thus we propose a new feature (hierarchical
+overriding) with the corresponding formalization of that feature.
 
@@
 \end{lstlisting}\vspace{3pt}
-Note that in \lstinline|Deck|,
+In \lstinline|Deck|,
 \lstinline|draw| uses \lstinline|println|, which is a
 library function. 
-The method returns \lstinline|void|. Note that \lstinline|void| is
-unsupported in our formalization, but we could have also defined an interface called \lstinline|Void|
-and return an object of that type instead. For the method \lstinline|draw| in
+The method returns \lstinline|void|. Note that, similarly to
+Featherweight Java~\cite{}\bruno{reference}, \lstinline|void| is
+unsupported in our formalization. We could have also defined an interface called \lstinline|Void|
+and return an object of that type instead, but for simplicity of
+presentation we use \lstinline|void|. For the method \lstinline|draw| in
 \lstinline|Drawable|
@@
 This case is the so-called \textit{unintentional method conflicts}. It arises when two inherited methods happen have
-the same name and parameter types, but they are totally designed for different functionalities with different semantics.
+the same name and parameter types, but they are designed for different functionalities with different semantics.
 Now one may quickly come up with a workaround, which is to manually merge them, by
@@
 
-\paragraph{Problem:} How to resolve unintentional method conflicts and invoke the conflicting methods separately without
-ambiguity.
-
-\paragraph{Potential Fixes:} There are several other workarounds
+\paragraph{Problem and Possible Workarounds:} The essential problem is
+how to resolve unintentional method conflicts and invoke the
+conflicting methods separately without ambiguity. To this problem, there are several other workarounds
 that come to our mind. We briefly discuss those potential fixes and
@@
   contrast with exclusion, renaming can indeed preserve both conflicting
-  behaviours, however, it is cumbersome in practice, as introducing new
+  behaviours. However, it is cumbersome in practice, as introducing new
   names can affect other code blocks.
@@
 
-\paragraph{Our solution:} It is important to preserve both conflicting methods
-during inheritance instead of explicitly merging them. That is to say, the compiler
-needs to accept \lstinline|DrawableDeck|. And then the disambiguation is done by
-up-casts, so as to specify the branch we would like to call.
+\paragraph{Our solution:} To solve this problem it is important to preserve both conflicting methods
+during inheritance instead of merging them into a single method. That is to say, the compiler
+needs to accept \lstinline|DrawableDeck|. To disambiguite method calls
+we can use \emph{up-casts}, so as to specify the ``branch'' in the
+inheritance hierarchy that should be called. The following code
+illustrates the use of up-casts for disambiguation:
 
@@
 are accepted by multiple inheritance. Note that C++ supports this feature and also addresses the
-ambiguity by up-casts. The code for the above example is similar.
+ambiguity by up-casts. The code for the above example in C++ is similar.
 

### 2017-10-10 NewVersion/sections/Formalization.tex
S3

@@
 In this section, we present the formal model called \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), following similar style of 
-Featherweight Java~\cite{Igarashi01FJ}. The syntax, typing rules,
+Featherweight Java~\cite{Igarashi01FJ}. \MIM{} is a minimal core calculus that formalizes the core concept of hierarchical dispatch and overriding. The syntax, typing rules,
 small-step semantics and theorems for type soundness are presented.
@@
 \paragraph{Methods}
-The method declaration $\method{I}{m}{I_x}{x}{J}{e}$ introduces a
+We allow the definition of two kinds of methods, ``original method'' and ``overriding method'', which share the same syntax. The method declaration $\method{I}{m}{I_x}{x}{J}{e}$ introduces a
 method named $m$ with result type $I$, parameters $\overline{x}$ of
 type $\overline{I_x}$ and the overriding target $J$. The body of the
-method is the single statement $ \kwreturn \; e;$. We also allow
-defining abstract methods with $\absmethod{I}{m}{I_x}{x}{J}$, which is
-similar to a normal method but without a method body. Notably, we have introduced the
+method is the single statement $ \kwreturn \; e;$. Notably, we have introduced the
 \kwoverride{} keyword to override an old implementation of the
 method. If the interface that it overrides is exactly the enclosing
-interface, then such a method is seen as ``originally defined''; otherwise
-it is hierarchical overriding.
+interface, then such a method is seen as ``originally defined'' and called ``original method''; otherwise it is an ``overriding method''. We also allow
+defining abstract methods with $\absmethod{I}{m}{I_x}{x}{J}$, which is
+similar to a normal method but without a method body. 
 For simplicity, overloading is not modelled for methods, which
@@
 
-There are two typing rules for method invocation: \textsc{(T-Invk)}
-and \textsc{(T-PathInvk)}. \textsc{(T-Invk)} is the typing judgement
-for a normal method invocation. First it ensures that the method
+\textsc{(T-Invk)} is the typing rule for method invocation.
+ First it ensures that the method
 receiver $e_0$ type checks to a type $I_0$. Then it checks the type of
@@
 \mbody{} is different to FJ, which has two parameters. The first $I_0$
-represents the dynamic type and the second, the static type. If the
-result of \mbody is not \Undefined, it means that the method exists and the corresponding method parameters and return types are given.
+represents the dynamic type and the second, the path type.
+The path type is the upcast type of $e_0$ (if any), else the path type is the same as its dynamic type.
+If the result of \mbody{} is not \Undefined, it means that the method exists and the corresponding method parameters and return types are given.
 After the method type is obtained, we check that all arguments $\overline{e}$ type check to $\overline{I}$ which are subtypes of $\overline{J}$.
-\textsc{(T-PathInvk)} is the typing judgement for a path invocation.
+% \textsc{(T-PathInvk)} is the typing judgement for a path invocation.
 Besides the conditions of \textsc{(T-Invk)}, \textsc{(T-PathInvk)} requires the type of receiver to be the subtype of the specified path type.

### 2017-10-10 NewVersion/sections/RelatedWork.tex
revised RelatedWork

@@
 \noindent {\bf C++ model.}
-C++ supports a very flexible inheritance model and allows programmers to choose either static dispatch or dynamic dispatch for method lookup.
-It allows the existence of unintentional conflicts and uses static
-dispatch to resolve them, as discussed in Section~\ref{sec:overview}. 
+C++ supports a very flexible inheritance model (normal inheritance and virtual inheritance). 
+It allows the existence of unintentional conflicts and users may specify a hierarchical path via cast for disambiguation, as discussed in Section~\ref{sec:overview}. 
 \bruno{if we are dropping the static dispatching discussion this text
@@
 With virtual methods, dynamic dispatch is used and 
-method lookup algorithm will find the most specific method definition.\yanlin{to revise: be consistant with introduction}
+method lookup algorithm will find the most specific method definition.
 A contribution of our work is to provide a minimal formal model of
@@
 hierarchical overriding.  However, there is a possible
-workaround\footnote{put the url here} that mimicks hierarchical
-overriding.  We call it the "MiddleMan" approach, as shown in
+workaround\footnote{https://stackoverflow.com/questions/44632250/can-i-do-mimic-things-likes-this-partial-override-in-c} that mimicks hierarchical
+overriding.  We call it the \emph{MiddleMan} approach, as shown in
 Figure~\ref{fig:middleman}. In this example, classes \texttt{A} and
@@
 \end{lstlisting}
-\caption{The "MiddleMan" approach.}
+\caption{The \emph{MiddleMan} approach.}
 \label{fig:middleman}
@@
 \subsection{Formalization Based on Featherweight Java}
-Featherweight Java (FJ)~\cite{Igarashi01FJ} is a minimal core calculus of Java language, 
+Featherweight Java (FJ)~\cite{Igarashi01FJ} is a minimal core calculus of the Java language, 
 proposed by Igarashi et. al. There are many models built on Featherweight Java, 
@@
 FJ provides the standard model of formalizing a Java-like object-oriented languages and 
-is easily extensible. In terms of formalization, the key novelty of our model is the use of 
-static types as annotations along with various terms. As far as we
-know, this technique has not appeared in the literature before. The static type annotation is of vital 
-importance in our hierarchical dispatch algorithm, and it allows for a
+is easily extensible.
+In terms of formalization, the key novelty of our model is making use of various types (such as parameter types, method return types, etc) as upcasts along with various terms.
+As far as we know, this technique has not appeared in the literature before.
+This notion is of vital importance in our hierarchical dispatch algorithm, and it allows for a
 more precise subject-reduction theorem as discussed in
-Section~\ref{}\bruno{put reference and make sure that we discuss this topic}.
+Section~\ref{sec:formalization}.\bruno{put reference and make sure that we discuss this topic}

### 2017-10-10 NewVersion/sections/Conclusion.tex
Section 2.1
revised Conclusion

--- 2017-06-19 Aplas17/sections/Conclusion.tex
@@
 
+\bruno{I think that the conclusion is not upto date. Please update it and let me know when ready.}
+\yanlin{done}
 This paper proposes \MIM{} as a new multiple inheritance model for unintentional method conflicts. 
-Existing approaches including static dispatch and dynamic dispatch have to compromise between code reuse
-and type safety, whereas \MIM{} uses a different solution called hierarchical dispatch to obtain both.
-Such an approach not only offers great code reuse like dynamic dispatch but also ensures unambiguity by
-our algorithm for method resolution. This paper also introduces hierarchical overriding that refines branches individually.
-\MIM{} is formalized with a basis on Featherweight Java and supported
-by a few theorems. The prototype is implemented in Scala as a simple interpreter.
+Existing approaches we discussed before either do not support unintentional method conflicts or have to compromise between code reuse and type safety; the closest one (C++) do not support partial method override.
+Two key mechanisms in this paper are hierarchical dispatching and hierarchical overriding.
+For hierarchical dispatching, we mimic the method lookup algorithm as in C++ and provide the formal algorithm in \mbody{} in \MIM{}.
+It makes use of both dynamic type information and path information from either upcasts or parameters' information.
+Such an approach not only offers great code reuse like dynamic dispatch but also ensures unambiguity by our algorithm for method resolution.
+This paper also introduces hierarchical overriding that refines branches individually.
+\MIM{} is formalized following the style of Featherweight Java and a few properties(theorems) of type-soundness are proved on \MIM{}. The prototype is implemented in Scala as a simple interpreter.
 
-Our model can certainly be improved at some aspects. We did not formalize fields as in Featherweight Java for simplicity.
-And we did not formalize other common features including
-method overloading, casts, covariant return types, and so on, some of which are orthogonal in the design space.
+Our model can certainly be improved at some aspects.
+We do not formalize fields as in Featherweight Java for the reason of simplicity.
+And we do not formalize other common features including method overloading, casts, covariant return types, and so on, some of which are orthogonal in the design space.
 Moreover, we restrict that hierarchical overriding can only work on original methods.
-Potentially a looser condition can better support encapsulation and modularity with respect to code design.
+Potentially a looser condition can better support encapsulation and modularity with respect to code design as discussed in Section~\ref{sec:discussion} and could be a good future work.

### 2017-10-10 NewVersion/sections/Discussion.tex
More.
revised Conclusion

@@
-\section{Discussion}
+\section{Discussion}\label{sec:discussion}
 In this section, we will discuss the design space and reflect about some of the design decisions of our work. We relate 
@@
 
-\subsection{Orthogonal \& Non-Orthogonal Extensions}
+\subsection{Orthogonal \& Non-Orthogonal Extensions}\label{sec:orthoext}
 

### 2017-10-11 NewVersion/sections/Overview.tex
Section 2.2

@@
 Problems 1 and 2 are related to hierarchical dispatching, and in 
-C++ it is possible to have similar solutions solutions to both
+C++ it is possible to have similar solutions to both
 problems. Hence it is important to emphasize that, with respect to
@@
 
-\paragraph{Our solution:} To solve this problem it is important to preserve both conflicting methods
-during inheritance instead of merging them into a single method. That is to say, the compiler
-needs to accept \lstinline|DrawableDeck|. To disambiguite method calls
-we can use \emph{up-casts}, so as to specify the ``branch'' in the
+\paragraph{\MIM{}'s solution:} To solve this problem it is important to preserve both conflicting methods
+during inheritance instead of merging them into a single
+method. Therefore \MIM{} accepts the definition of \lstinline|DrawableDeck|. To disambiguite method calls
+we can use \emph{up-casts} in \MIM{}'s, so as to specify the ``branch'' in the
 inheritance hierarchy that should be called. The following code
@@
 ((Deck) new DrawableDeck()).draw()  // calls Deck.draw
+// (new DrawableDeck()).draw()        // this call is ambiguous and rejected
 \end{lstlisting}\vspace{3pt}
 In our language, the main program is merely an expression. The above cast indicates
-that we expect to invoke the \lstinline|draw| from branch \lstinline|Deck|.
+that we expect to invoke the \lstinline|draw| from branch
+\lstinline|Deck|. Similarly we could have used an upcast to \lstinline|Drawable|
+to call the \lstinline|draw| method from \lstinline|Drawable|.
+Without the cast the call would be ambiguous, and
+\MIM{}'s type system would reject that call.
 
-We call this case the triangle inheritance, where two unintentionally conflicting methods
+This example illustrates the basic form of triangle inheritance, where two unintentionally conflicting methods
 are accepted by multiple inheritance. Note that C++ supports this feature and also addresses the
@@
 \subsection{Problem 2: Dynamic Dispatching}
-It seems that the solution to problem 1 is straightforward and easy to achieve, but things can
+Using explicit upcasts for disambiguation helps when making calls to
+classes with conflicting methods, but things
 become more complicated with dynamic dispatching. Dynamic
@@
 \end{lstlisting}\vspace{3pt}
-Here \lstinline|shuffleAndDraw| invokes \lstinline|draw| from its own enclosing type. Ideally,
+Here \lstinline|shuffleAndDraw| \emph{invokes \lstinline|draw| from its own enclosing type}. Ideally,
 we want that invocation to be dynamically dispatched. This is important, because a programmer may define a subtype
@@
 since the method becomes automatically adaptive. Nevertheless, as seen before, dynamic dispatch would potentially introduce ambiguity,
-for instance, when we have the UML in Figure~\ref{fig:drawablesafedeck} and the following code:
+for instance, when we have the class hierarchy structure in Figure~\ref{fig:drawablesafedeck} and the following code:
 
@@
 When the \lstinline|DrawableSafeDeck| object calls \lstinline|shuffleAndDraw|, the implementation in \lstinline|Deck|
-is surely dispatched. But then \lstinline|shuffleAndDraw| invokes ``\lstinline|this.draw()|'', and at this point, the receiver
+is dispatched. But then \lstinline|shuffleAndDraw| invokes ``\lstinline|this.draw()|'', and at this point, the receiver
 is replaced by the object \lstinline|new DrawableSafeDeck()|.
@@
 From the perspective of \lstinline|DrawableSafeDeck|, the \lstinline|draw| method seems ambiguous. But ideally we would
-like \lstinline|shuffleAndDraw| to invoke \lstinline|SafeDeck.draw| because they belong to the same branch. It
-seems that we choose dynamic dispatch but also make use of static type information, since the type of this-reference (\lstinline|Deck|) specifies the branch.
-Note that in C++, if we put the \lstinline[language=c++]|virtual| keyword in front of every \lstinline|draw| method, that means
-we enforce the dynamic dispatch, and it does the disambiguation correctly.
-Unfortunately, the C++ language, or rather the feature on triangle inheritance, has not been well formalized.
+like \lstinline|shuffleAndDraw| to invoke \lstinline|SafeDeck.draw|
+because they belong to the same class hierarchy branch. It
+seems that we choose dynamic dispatch but also make use of static type
+information, since the type of this-reference (\lstinline|Deck|)
+specifies the branch to use unambiguously.
 
-\paragraph{Problem:} How to ensure that the correct method is invoked, by disambiguating conflicting methods in a dynamically dispatched setting, and how to achieve such a formalized language model.
-\\
+%%\paragraph{Problem:} \\
 
-\paragraph{Our solution:} Inspired by C++, we have formalized this feature into a minimal core calculus,
-studied and proved the type soundness. It is concise and can readily be imported to other systems. 
-And in the formalization, we propose \textit{hierarchical dispatch} in our model
-as the default method lookup algorithm. During the runtime, the method call \lstinline|e.m()|
+\paragraph{\MIM's solution:} 
+The essential problem is how to ensure that the correct method is
+invoked. To solve this problem \MIM{} uses a variant of method
+disptaching that we call \textit{hierarchical dispatch}. In
+hierarchical dispatch both the static and dynamic type information 
+ared used to select the right method implementation.
+%Inspired by C++, we have formalized this feature into a minimal core calculus,
+%studied and proved the type soundness. It is concise and can readily be imported to other systems. 
+%And in the formalization, we propose \textit{hierarchical dispatch} in our model
+%as the default method lookup algorithm. 
+During the runtime, the method call \lstinline|e.m()|
 makes use of both the static type and the dynamic type of the receiver, so it is seemingly a
 combination of static and dynamic dispatch. Intuitively, the static type specifies one branch
-to avoid ambiguity, and the dynamic type finds the latest implementation on that branch. The formal algorithm
+to avoid ambiguity, and the dynamic type finds the most specific implementation on that branch. The formal algorithm
 will be introduced later.
 
-Back to the example, our code below just suffices to meet the expectation:
+Using hierarchical dispatching the following code is accepted:
 \vspace{3pt}\begin{lstlisting}
@@
 
-In our language model, there are two types of casts: implicit casts and explicit upcasts. The implicit casts appear
-when passing arguments and returning expressions, they are also upcasts. Hence all casts are safe, and the difference
-from C++ is that C++ checks ambiguity on casts, whereas our model is open to those safe casts. Unfortunately,
+%Note that in C++, if we put the \lstinline[language=c++]|virtual| keyword in front of every \lstinline|draw| method, that means
+%we enforce the dynamic dispatch, and it does the disambiguation correctly.
+%Unfortunately, the C++ language, or rather the feature on triangle inheritance, has not been well formalized.
+
+\paragraph{Implicit and Explicit Upcasts}
+In our language model, there are two types of casts: \emph{implicit casts} and \emph{explicit upcasts}. The implicit casts appear
+when passing arguments and returning expressions, they are also
+upcasts. Hence all casts are safe. C++ implementations also support a
+similar solution. However a notable difference between \MIM{} and C++
+is that C++ checks ambiguity on casts, whereas our model is open to those safe casts. Unfortunately,
 it introduces ambiguity in what we call ``the diamond inheritance'': when two methods override a same base method
@@
 but this is natural as they are just two versions of the same operation, hence it is no longer an ``unintentional'' conflict.
-Our proof demonstrates that it is a sufficient condition for type soundness.
+Our proof demonstrates that it is a sufficient condition for type
+soundness.
+\bruno{I think the difference between C++ and our model is an important discussion, but very confusingly
+  written. I believe that some more detail is needed. Do we have an
+  extended discussion later?}
 

### 2017-10-11 NewVersion/sections/Overview.tex
Section 2

@@
 
-This is not the end of the story, because after the programmer defines \lstinline|DrawableSafeDeck|, he needs to override
-\lstinline|Drawable.draw|, and give the implementation of drawing, so that the deck can indeed be visualized on the canvas.
+Method overriding is common in Object-Oriented Programming. 
+With diamond inheritance where conflicting methods are intended to have 
+the same semantics, method overriding is not a problem. If conflicting
+methods arize from multiple parents, we can override all those methods 
+in a single unified (or merged) method in the subclass. Therefore
+further overriding is simple, because there is only one method that
+can be overriden.
 
-\paragraph{Problem:} how to update the conflicting methods separately, after the triangle inheritance.
+With unintentional method conflicts, however, the situation is more
+complicated because different, separate, conflicting methods can exist
+in a class. Ideally we would like to support overriding for those
+methods too, in exactly the same way that overriding is available for 
+other (non-conflicting) methods. However we need to be able to
+override the individual conflicting methods, rather than overriding all
+conflicting methods into a single merged method.  We illustrate the
+problem and the need for a more refined overrding mechanism with 
+an example.
 
-\paragraph{Potential fixes:} Unfortunately as far as we are concerned, the existing approaches are unsatisfactory.
+Suppose that the programmer defines \lstinline|DrawableSafeDeck|, but he needs to override
+\lstinline|Drawable.draw| and give a new implementation of drawing, so that the deck can indeed be visualized on the canvas.
+
+%\paragraph{Problem:} how to update the conflicting methods separately, after the triangle inheritance.
+
+\paragraph{Potential solutions/workarounds in existing languages:} Unfortunately in all languages we known
+(including C++), the existing approaches are unsatisfactory.
 One direction is to simply avoid this issue, by putting overriding before inheritance. For example, we define a new component
@@
 	\item It changes the hierarchy and existing code, hence breaks the modularity.
-	\item The demand for separate overriding after the triangle inheritance comes especially when there is interaction. In the above code we assume
+	\item The demand for separate overriding after the triangle
+          inheritance comes especially when there is
+          interaction\bruno{what interaction?}. In the above code we assume
 	that the overriding is unrelated to \lstinline|Deck|. But when the drawing relies on some information of the \lstinline|Deck|
@@
 \end{itemize}
-Another workaround in C++ adopts templates, but there are still issues and we put the discussion in Section~\ref{subsec:middleman}.
 
-\paragraph{Our solution:} An additional feature of our model is \textit{hierarchical overriding}. It allows conflicting methods
+There are more involved workarounds in C++ using templates and complex
+patterns, but such patterns are complex to use and there are still issues. A more detailed discussion of
+such an approach is presented in Section~\ref{subsec:middleman}.
+
+\paragraph{\MIM{}'s solution:} An additional feature of our model is \textit{hierarchical overriding}. It allows conflicting methods
 to be overridden on individual branches, and hence offers independent extensibility. The above example can be easily realized by:
@@
 ((Drawable)new DrawableSafeDeck()).draw(); // calls the latest draw
-\end{lstlisting}\vspace{3pt}
+\end{lstlisting}\vspace{3pt}\bruno{make override a keyword in
+  lstlisting.}
+Here the idea is that \emph{only} \lstinline{Drawable.draw} is
+overriden. This is accomplished by specifying, in the method
+definition, that only the method override only overrides the method 
+from \lstinline|Drawable|.  
 The direct support for individual overriding also works when there is interaction. In our formalization, this feature is necessary
-and also involves in the algorithm of hierarchical dispatch.
+and also involves in the algorithm of hierarchical dispatch.\bruno{the
+last two sentences are a bit unclear. I think it is related to ``interaction''.}
 
-\paragraph{Terminology:} The \lstinline|draw| methods we saw in previous subsections are called \textit{original methods} in this paper, because they are originally defined in its interface.
+\paragraph{Terminology:} The \lstinline|draw| methods we saw in
+previous subsections\bruno{by now I saw many methods. Please be more precise.} are called \textit{original methods} in this paper, because they are originally defined in its interface.
 In contrast, \lstinline|DrawableSafeDeck| defines a \textit{hierarchical overriding method}.
@@
 
-\paragraph{Overview of hierarchical dispatching algorithm:} In our model, triangle inheritance allows several original methods (branches) to coexist, and hierarchical dispatch first finds the most specific original method (branch), then it finds the most specific hierarchical overriding on that branch.
-A quick counter-example is when there are two hierarchical overriding methods on \lstinline|Drawable| in \lstinline|DrawableSafeDeck|, it leads to ambiguity.
-The compiler is supposed to forbid the case.
+\paragraph{Overview of hierarchical dispatching algorithm:} In our
+model, triangle inheritance allows several original methods (branches)
+to coexist, and hierarchical dispatch first finds the most specific
+original method (branch), then it finds the most specific hierarchical
+overriding on that branch. A quick counter-example is when there are
+two hierarchical overriding methods on \lstinline|Drawable| in
+\lstinline|DrawableSafeDeck|, it leads to ambiguity. The compiler is
+supposed to forbid the case.\bruno{please show code illustrating this,
+and improve explanation.}
 

### 2017-10-11 NewVersion/sections/Discussion.tex
Added refs.

@@
 our language to traits, Java interfaces as well as other languages. Furthermore we discuss
-ways to improve our  work.\bruno{references please!!!}
+ways to improve our  work.\bruno{references please!!!} \haoyuan{Done}
 
@@
 to include only method declarations, and those abstract methods can be implemented in a class body. 
-The formal Featherweight Java model does not include abstract methods because of its orthogonality to the core calculus. In traits the
-similar idea is to use keywords like ``\textbf{require}'' for abstract method declarations. Abstract methods provide a way to
+The formal Featherweight Java model~\cite{Igarashi01FJ} does not include abstract methods because of its orthogonality
+to the core calculus. In traits the
+similar idea is to use keywords like ``\textbf{require}'' for abstract method declarations~\cite{scharli03traits}.
+Abstract methods provide a way to
 delay the implementations to future subtypes. Using overriding, they also help to ``exclude'' existing implementations.
@@
 Having fields in OO multiple inheritance is a non-trivial issue.
-There has been a lot of work on it, such as C++ that uses virtual inheritance.
+There has been a lot of work on it, such as C++ that uses virtual inheritance~\cite{ellis1990annotated}.
 The trait model simply disallows state to avoid that issue.
-In our language, however, we can perhaps borrow the idea of \textit{interface-based programming} [], which actually models state with abstract state operations.
+In our language, however, we can perhaps borrow the idea of \textit{interface-based programming}~\cite{classless}, which actually models state with abstract state operations.
 This can be realized by extending our current model with static methods and anonymous classes from Java.

### 2017-10-11 NewVersion/sections/Formalization.tex
S3 on the way.

@@
 \paragraph{Methods}
-We allow the definition of two kinds of methods, ``original method'' and ``overriding method'', which share the same syntax. The method declaration $\method{I}{m}{I_x}{x}{J}{e}$ introduces a
+Original methods and hierarchically overriding methods share the same syntax in our model for simplicity.
+The concrete method declaration $\method{I}{m}{I_x}{x}{J}{e}$ introduces a
 method named $m$ with result type $I$, parameters $\overline{x}$ of
 type $\overline{I_x}$ and the overriding target $J$. The body of the
-method is the single statement $ \kwreturn \; e;$. Notably, we have introduced the
+method simply includes the returned expression $e$. Notably, we have introduced the
 \kwoverride{} keyword to override an old implementation of the
 method. If the interface that it overrides is exactly the enclosing
-interface, then such a method is seen as ``originally defined'' and called ``original method''; otherwise it is an ``overriding method''. We also allow
-defining abstract methods with $\absmethod{I}{m}{I_x}{x}{J}$, which is
-similar to a normal method but without a method body. 
+interface, then such a method is seen as originally defined; otherwise it is an overriding method. The definition
+of abstract methods is done with $\absmethod{I}{m}{I_x}{x}{J}$, which is
+similar to a concrete method but without the method body. 
 For simplicity, overloading is not modelled for methods, which
@@
 Expressions can be standard constructs such as variables, method
-invocation, or object creation, together with casts. 
-Object creation is represented by $\new I$.
-If any unimplemented abstract methods are defined in interface $I$ (or inherited from parents), then object creation fails.
-Fields and primitive types are not modelled in \MIM{}.
-Again, to be concise, the casts are merely safe up-casts. Those cast-expressions
-are in fact annotated expressions, where the annotation indicates its static type.
+invocation, or object creation, together with cast expressions. 
+Object creation is represented by $\new I$. Fields and primitive types are not modelled in \MIM{}. 
+The casts are merely safe up-casts, and in fact, they can be viewed as
+annotated expressions, where the annotation indicates its static type.
 The coexistence of static and dynamic types is the key to hierarchical dispatch.
@@
 \textsc{(T-Invk)} is the typing rule for method invocation.
- First it ensures that the method
-receiver $e_0$ type checks to a type $I_0$. Then it checks the type of
-the specific method, by using an auxiliary function $\mbody(m, I_0,
-I_0)$, which is the function for looking up methods that we will
-illustrate in more detail in Section~\ref{subsec:auxdefs}. The form of
-\mbody{} is different to FJ, which has two parameters. The first $I_0$
-represents the dynamic type and the second, the path type.
-The path type is the upcast type of $e_0$ (if any), else the path type is the same as its dynamic type.
-If the result of \mbody{} is not \Undefined, it means that the method exists and the corresponding method parameters and return types are given.
-After the method type is obtained, we check that all arguments $\overline{e}$ type check to $\overline{I}$ which are subtypes of $\overline{J}$.
+Naturally, the receiver and the arguments are required to be type-checked.
+$\mbody$ is our key function for method lookup, based on the
+hierarchical dispatching algorithm. The formal definition will be introduced in
+Section~\ref{subsec:auxdefs}. To overview,
+the hierarchical invocation $\mbody(m, I, J)$ means ``finding most specific $m$
+above $I$ and along path $J$'', and usually $I$ denotes the dynamic type while $J$
+denotes the static type. In \textsc{(T-Invk)}, as the compilation should not be aware
+of the dynamic type, it only requires that invoking $m$ is valid for the static type of the
+receiver. The result of $\mbody$ contains the interface that provides the most specific implementation,
+the parameters and the return type. Note that we accept implicit upcasts on the arguments.
 % \textsc{(T-PathInvk)} is the typing judgement for a path invocation.
@@
 \textsc{(T-New)} is the typing rule for object creation $\new{I}$.
-The auxiliary function $\canInstantiate(I)$ checks whether interface $I$ can be instantiated or not.
-If interface $I$ contains (or inherits) any abstract method that has not been implemented, then interface $I$ cannot be instantiated.
+The auxiliary function $\canInstantiate(I)$ checks whether interface $I$ can be instantiated or not, formalized in Section~\ref{subsec:auxdefs}.
+Since triangle inheritance accepts conflicting branches to coexist, the check requires that the most specific method is concrete for each method on each branch.
 
-The method typing rule \textsc{(T-Method)} is more interesting since the method can either be an original implementation or hierarchical overriding.
-Besides type-checking the return expression,
-we further use the helper function $\mostSpecific$, again formally defined in Section~\ref{subsec:auxdefs}.
-By the equation ``$\mostSpecific(m, I, J) = \{J\}$'' we define the legality of method overrides as mentioned in Section~\ref{subsec:partialoverrides}, namely if it is hierarchical overriding, it should not step over original methods, otherwise
-their enclosing types would be returned instead of $J$.
+\textsc{(T-Method)} is more interesting since a method can either be an original method or a hierarchical overriding, though
+they share the same syntax and method typing rule. $\mostSpecific(m, I, J)$ is a fundamental function from Section~\ref{subsec:auxdefs},
+used to find ``the most specific interfaces that are above $I$ and along path $J$, and originally defines $m$''. By ``most specific interfaces'',
+it implies that the inherited super types are excluded.
+Thus the condition $\mostSpecific(m, I, J) = \{J\}$ indicates the characteristics of a hierarchical overriding: it must override an original method; the overriding is direct and there does not exist any other original $m$ in between.
+Then $\mbody(m, J, J)$ provides the type of the original method, so hierarchical overriding has to preserve the type. Finally the return expression
+needs to be type-checked, and there is also an implicit cast to the declared return type.
+For the definition of an original method, $I = J$ and the rule is straightforward.
+\textsc{(T-AbsMethod)} is a similar rule but works on abstract method declarations.
 
-\bruno{Well, there are two conditions. I suggest you explain
-  in a bit more detail the 2 conditions, since this rule seems to be
-  the more complex one. Some examples may help.} \yanlin{added} 
-Rule \textsc{(T-Intf)} defines the typing rule for interfaces.
-Interface $I$ type checks only if the following conditions are satisfied: 1) all methods $\overline{M}$ that are directly defined in $I$ type check; 2) method lookup $\mbody(m, I, J)$ successes as long as the method $m$ is originally defined in any interface $J$ which is an ancestor of $I$; 3)if an original method $m$ defined in interfaces $I$ overrides another original method defined in an ancestor of $I$, then the method types are compatible.
-These conditions ensure unambiguity and type soundness of the calculus.
-We will introduce \mbody{} and some counter-examples later.
-But intuitively, if $\mbody(m,I,J)$ is defined, that means $\new{I}.J::m()$ is not ambiguous during runtime.
-Therefore the condition says that if an expression type checks, it should not introduce ambiguity during runtime in any case.
-The interface check is responsible for capturing ambiguity during compilation.
+\textsc{(T-Intf)} defines the typing rule on interfaces. The first condition is obvious, namely its methods need to be well checked. The third
+condition checks whether the overriding between original methods preserves typing.
+In the condition we again use some helper functions from Section~\ref{subsec:auxdefs}.
+$I[m\ \kwoverride\ I]$ is defined if $I$ originally defines $m$, and $\canOverride(m, I, J)$ checks whether $I.m$ has the same type as $J.m$.
+Generally the preservation of method type is required for any super type $J$ and any method $m$.
+
+The second condition of \textsc{(T-Intf)} is more complex, and is the key to type soundness. Unlike C++ which rejects on ambiguous calls,
+\MIM{} rejects on the definition of interfaces when they form a diamond. Consider the case when the second condition is broken: $\mbody(m, J, J)$
+is defined but $\mbody(m, I, J)$ is undefined for some $J$ and $m$. It ...
 
@@
 The rule says that an annotated expression $\angl{J}e$ type checks to $J$ if the expression $e$ type checks and the static annotation $J$ is a subtype of $I$ which is the type of $e$.
+
+\paragraph{Examples for mbody: TODO}
 

### 2017-10-11 NewVersion/sections/Overview.tex
small comment
S3 on the way.

@@
 
-\subsection{Problem 2: Dynamic Dispatching}
+\subsection{Problem 2: Dynamic Dispatching}\label{subsec:problem2}
 Using explicit upcasts for disambiguation helps when making calls to
@@
 to avoid ambiguity, and the dynamic type finds the most specific implementation on that branch. The formal algorithm
-will be introduced later.
+will be introduced later.\bruno{avoid using words like ``later'' or
+  ``before''. Instead use references to the actual Sections.}
 

### 2017-10-11 NewVersion/sections/RelatedWork.tex
Related work

@@
 inheritance~\cite{ellis1990annotated,scala-overview,bracha90mixin,scharli03traits,malayeri2009cz,csharpdoc,Moon1986,Flatt1998,Ancona2003}. 
-The Mixin models~\cite{bracha90mixin,Flatt1998,van1996encapsulation,Ancona2003,Hendler86} allow naming components 
+The mixin models~\cite{bracha90mixin,Flatt1998,van1996encapsulation,Ancona2003,Hendler86} allow naming components 
 that can be applied to various classes as reusable functionality units. However, the linearization (total ordering) of mixin 
@@
 
-The above-mentioned models/languages support multiple inheritance, and
-they handle method conflicts in the same way, by simply disallowing
+The above-mentioned models/languages support multiple inheritance, 
+focusing on diamond inheritance.
+They handle method conflicts in the same way, by simply disallowing
 two methods with the same signature from two different units to
@@
 static and dynamic type information during method dispatching.
+In the cases where real ambiguity exists, \MIM{}'s type system can
+reject interface definitions and/or method calls statically.
 
@@
 C++ supports a very flexible inheritance model (normal inheritance and virtual inheritance). 
-It allows the existence of unintentional conflicts and users may specify a hierarchical path via cast for disambiguation, as discussed in Section~\ref{sec:overview}. 
-\bruno{if we are dropping the static dispatching discussion this text
-  may be outdated.}
+It allows the existence of unintentional conflicts and users may specify a hierarchical path via casts for disambiguation, as discussed in Section~\ref{sec:overview}. 
 With virtual methods, dynamic dispatch is used and 

### 2017-10-11 NewVersion/sections/Formalization.tex
Done S3 ready for review.

@@
 \textsc{(T-Invk)} is the typing rule for method invocation.
-Naturally, the receiver and the arguments are required to be type-checked.
+Naturally, the receiver and the arguments are required to be well-typed.
 $\mbody$ is our key function for method lookup, based on the
@@
 receiver. The result of $\mbody$ contains the interface that provides the most specific implementation,
-the parameters and the return type. Note that we accept implicit upcasts on the arguments.
+the parameters and the return type. We use underscore for the return expression, to imply that an empty return expression
+from an abstract method is also acceptable.
+Note that we accept implicit upcasts on the arguments.
 % \textsc{(T-PathInvk)} is the typing judgement for a path invocation.
@@
 needs to be type-checked, and there is also an implicit cast to the declared return type.
-For the definition of an original method, $I = J$ and the rule is straightforward.
+For the definition of an original method, $I$ equals $J$ and the rule is straightforward.
 \textsc{(T-AbsMethod)} is a similar rule but works on abstract method declarations.
@@
 The second condition of \textsc{(T-Intf)} is more complex, and is the key to type soundness. Unlike C++ which rejects on ambiguous calls,
-\MIM{} rejects on the definition of interfaces when they form a diamond. Consider the case when the second condition is broken: $\mbody(m, J, J)$
-is defined but $\mbody(m, I, J)$ is undefined for some $J$ and $m$. It ...
+\MIM{} rejects on the definition of interfaces when they reach a diamond. Consider the case when the second condition is broken: $\mbody(m, J, J)$
+is defined but $\mbody(m, I, J)$ is undefined for some $J$ and $m$. It indicates that $m$ is available and unambiguous from the perspective of $J$,
+but is ambiguous to $I$ on branch $J$. That means there are multiple overriding paths of $m$ from $J$ to $I$, which form a diamond. Hence rejecting
+that case meets our expectation.
 
-Finally, rule \textsc{(T-Anno)} is the typing rule for an expression with static type annotation.
-The rule says that an annotated expression $\angl{J}e$ type checks to $J$ if the expression $e$ type checks and the static annotation $J$ is a subtype of $I$ which is the type of $e$.
+Finally, rule \textsc{(T-Anno)} is the typing rule for a cast expression. By the rule, only upcasts are valid.
 
@@
 \saveSpaceFig
+
 \begin{mathpar}
@@
 Figure~\ref{fig:smallstep} defines the small-step semantic and
-congruence rules, respectively. When evaluating an expression, they
-are invoked recursively and alternately to produce a single value in
-the end. The small-step semantics rules \textsc{(S-Invk)} and 
-\textsc{(S-PathInvk)} behave similarly: each corresponds to one kind of method invocation.
-\textsc{(S-PathInvk)} invokes \mbody{} for method body lookup.
-The parameters $\overline{x}$ are replaced with arguments $\overline{v}$ with static type annotations $\overline{\angl{I_x}}$, where $\overline{\angl{I_x}}$ are the parameter types coming from method lookup result.
-The rule \textsc{(S-Invk)} simply reduces the problem of normal invocation to path invocation.
+congruence rules of \MIM{}. When evaluating an expression, they
+are invoked recursively and alternately, and produce a single value in
+the end. \haoyuan{we need to be consistent on paragraph upper/lower case.}
 
-Generally, one can understand
-$\mbody(m, I, J)$ in a way that it finds the most specific body of
-method $m$, when the receiver has dynamic type $I$ and static type
-$J$.  Notice, for example in \textsc{(S-Invk)}, that when
-``$\new{I}$'' replaces ``\lstinline|this|'', its static type should be
-the interface to which $m$ is dispatched. Therefore we also keep the
-interface type in the definition of \mbody.
+\paragraph{Semantic Rule} \textsc{(S-Invk)} is the only computation rule we need for method invocation.
+As a small-step rule and by congruence, it assumes that the receiver and the arguments are already values.
+Specifically, the receiver $(J)\new{I}$ indicates the dynamic type $I$
+together with the static type $J$. Therefore $\mbody(m, I, J)$ carries out hierarchical dispatch, acquires
+the types, the return expression $e_0$ and the interface $I_0$ which provides the most specific method.
+Here we use $e_0$ to imply that the return expression is forced to be non-empty because it requires a concrete implementation. Now the
+rule reduces method invocation to $e_0$ with substitution.
+Parameters are substituted with arguments, and \lstinline|this| reference is substituted with the receiver,
+and in the meanwhile implicit casts are applied, so that static types are recorded via annotations. Finally
+there is again an annotation from the return type.
 
-On the other hand, there is a relationship between path invocation and
-the regular method invocation, and it can be observed from the
-similarity between their semantic rules in
-Figure~\ref{fig:smallstep}. For any \lstinline|e.I?m()|, the result
-of evaluation remains unchanged if we set the static type of
-\lstinline|e| to be $I$. This can be done by an implicit cast, that
-is, we can define a function with one parameter type $I$, then
-\lstinline|e| is passed to that function and directly returned. This
-is equivalent to writing explicit casts like \lstinline|((I) e).m()|
-in languages like Java.
+\paragraph{Congruence Rules} \textsc{(C-Receiver)}, \textsc{(C-Args)} and \textsc{(C-FReduce)} are natural congruence rules
+on receivers, arguments and cast-expressions, respectively. \textsc{(C-StaticType)} automatically adds an annotation $I$ to the new
+object $\new{I}$. \textsc{(C-AnnoReduce)} merges nested upcasts into a single upcast with the outermost type.
 
@@
 \subsection{Properties}
-Now we proceed to prove the type soundness of 
-the model, which relates typing to computation. Type soundness states that, if an expression is 
-well-typed, then after many reduction steps it must reduce to a value, with its annotation to be a subtype of the original expression type.
-Following the Featherweight Java paper~\cite{Igarashi01FJ}, the type-soundness theorem 
-(Theorem~\ref{theorem_soundness}) is proved by using the standard technique of subject reduction (Theorem~\ref{theorem_subject})
-and progress (Theorem~\ref{theorem_progress})~\cite{Wright1994}. In Theorem~\ref{theorem_progress} ``$\#(\overline{x})$'' denotes the length of
-$\overline{x}$.
+
+We present the type soundness of the model by a few theorems below, following the standard technique of
+subject reduction and progress proposed by~\cite{Wright1994}. The proof, together with some lemmas, are
+in Appendix. The type soundness states that if an expression is well-typed, then after many reduction
+steps it must reduce to a value, and its annotation is the same as the static type of the original expression.
 
@@
 \end{proof}
-\bruno{Were we not supposed to have some note/comment as to why the
-  type soundness theorem is stricter that FJ?}
+Note that in Theorem~\ref{theorem_progress}, ``$\#(\overline{x})$'' denotes the length of
+$\overline{x}$.
+
+Our theorems are stricter than those of Featherweight Java~\cite{Igarashi01FJ}. Specifically, in both term substitution (a lemma in Appendix)
+and subject reduction, the type may go down in FJ, but in \MIM{} it is unchanged. The difference is due to
+subtyping; the parameter or \lstinline|this| reference requires some type $I$, but a value with a more specific type,
+which is subtype of $I$, can be passed. However, as \MIM{} keeps track of the static types, the annotations in the
+substitution actually ensures the type to be unchanged.

### 2017-10-11 NewVersion/sections/Auxiliary.tex
revised S4: Fundamental algorithms and Auxiliary definitions

--- 2017-10-06 NewVersion/sections/Auxiliary.tex
@@
-\section{Fundamental Notations}\label{subsec:auxdefs}
-In this section, we present the fundamental notations used in our formalization.
+\section{Fundamental Algorithms and Auxiliary Definitions}\label{sec:auxdefs}
+In this section, we present the fundamental algorithms and auxiliary definitions used in our formalization.
 Some of them are auxiliary functions, others are however important ones as they
-directly implement our algorithm for method resolution.
+directly implement our algorithm for method lookup.
+\bruno{I felt like there's not enough explanation/context in this
+  section. It is just dumping definitions without connecting them and
+  their purpose properly.}
 
-\subsection{Auxiliary functions}
-To begin with, we introduce the following basic functions.
+\subsection{Method Lookup Algorithm in \mbody{}}
+Before showing the definition of \mbody{}, we start with several examples of method lookup, as shown in Figure~\ref{fig:examplesmbody}.
+Note that we use \lstinline|m| to denote an original method, and ``\lstinline|m|$\uparrow$\lstinline|A|'' for hierarchical overriding on \lstinline|A|.
+For each small example, the result gives the interface to which $m$ is dispatched.
+(a) is our old friend example for unintentional method conflicts (triangle inheritance); (b) and (c) demonstrate
+that hierarchical dispatch can find the most specific original method and hierarchical overriding method.
+More interesting are the two bad examples (d) and (e), they both fail on $\mbody$.
+(d) is the well-known diamond inheritance, where $\mbody(m, D, A)$ is \Undefined; (e) is again a diamond conflict because the two hierarchical overriding methods are overriding the same branch.
+Both counter-examples imply that \lstinline|(A)new D().m()| will
+lead to ambiguity, and in order to ensure type soundness, both of them have to be rejected by the type checker.
+Our model guarantees this by the interface checking rule\textsc{(T-Intf)} in Figure~\ref{fig:typingrules}.
 
-\begin{flalign*}
-	& \rhd \textit{Definition of } I[m\ \kwoverride\ J]: & \\
-	& \bullet I[m\ \kwoverride\ J] = \method{I_e}{m}{I_x}{x}{J}{e_0} & \\
-	& \indent\indent \textrm{with: }
-	  \kwinterface \; I \; \kwextends \; \overline{I} \; \{ \method{I_e}{m}{I_x}{x}{J}{e_0} \ldots \} & \\
-	& \bullet I[m\ \kwoverride\ J] = \absmethod{I_e}{m}{I_x}{x}{J} & \\
-	& \indent\indent \textrm{with: }
-	\kwinterface \; I \; \kwextends \; \overline{I} \; \{ \absmethod{I_e}{m}{I_x}{x}{J} \ldots \} & \\
-\end{flalign*}
-Here $I[m\ \kwoverride\ J]$ is basically a direct lookup for method $m$ in the body of $I$, where such a method
-overrides $J$ (like static dispatch). The method can be either concrete or abstract, and the body of definition is returned. Notice that
-by our syntax, $I[m\ \kwoverride\ I]$ is looking for the originally-defined method $m$ in $I$.
-
-\begin{flalign*}
-	& \rhd \textit{Definition of } \prune(set): & \\
-	& \bullet \prune(set) = \{I \in set \; | \; \nexists J \in set\setminus I, J <: I\} &
-\end{flalign*}
-The $\prune$ function takes a set of
-types, and filters out those that have subtypes in the same set. In the returned set,
-none of them has subtyping relation to one another, since all super types have been removed.
-
-\begin{flalign*}
-	& \rhd \textit{Definition of } \canOverride(m, I, J): & \\
-	& \bullet \canOverride(m, I, J) = True & \\
-	& \indent\indent \textrm{with: } I[m\ \kwoverride\ I] = I_e \; m(\overline{I_x} \; \overline{x}) \; \kwoverride \; I \ldots & \\
-	& \hspace{.77in} J[m\ \kwoverride\ J] = I_e \; m(\overline{I_x} \; \overline{y}) \; \kwoverride \; J \ldots &
-\end{flalign*}
-$\canOverride$ just checks that two original $m$ in $I$ and $J$ have the same type.
-
-\subsection{$\mostSpecific$ and $\mostSpecificOverride$}
-
-$\mostSpecific$ and $\mostSpecificOverride$ are two core functions for the method lookup algorithm. Generally,
-$\mostSpecific(m, I, J)$ finds the set of most specific interfaces where $m$ is originally defined, they should be above $I$ and
-along path $J$. ``Along path $J$'' means one should be either a subtype or a super type of $J$. Finally with $\prune$
-the overridden interfaces will be filtered out.
-
-\begin{flalign*}
-	& \rhd \textit{Definition of } \mostSpecific(m, I, J): & \\
-	& \bullet \mostSpecific(m, I, J) = \prune(origins) & \\
-	& \indent\indent \textrm{with: } origins = \{K \mid \subt{I}{K}, \textrm{ and } \subt{K}{J} \; \lor \; \subt{J}{K}, &\\
-	& \hspace{1.62in} \textrm{ and } K[m\ \kwoverride\ K] \textrm{ is defined} \} &
-\end{flalign*}
-By the definition, an interface belongs to $\mostSpecific(m, I, J)$ if and only if:
-\begin{itemize}
-	\item It originally defines $m$;
-	\item It is a super type of $I$;
-	\item It is either a super type or a subtype of $J$ (including $J$ itself);
-	\item Any subtype of it does not belong to the same result set because of $\prune$.
-\end{itemize}
-
-The $\mostSpecific$ function only focuses on original method implementations, all the hierarchical overriding methods are omitted during that time.
-On the other hand, $\mostSpecificOverride(m, I, J)$ has the assumption that $J$ defines an original $m$, and this function tries to find the interfaces with most specific implementations that hierarchically overrides such an $m$.
-Formally,
-
-\begin{flalign*}
-	& \rhd \textit{Definition of } \mostSpecificOverride(m, I, J): & \\
-	& \bullet \mostSpecificOverride(m, I, J) = \prune(overrides) & \\
-	& \indent\indent \textrm{with: } overrides = \{K \mid \subt{I}{K}, \; \subt{K}{J} \textrm{ and } K[m\ \kwoverride\ J] \textrm{ is defined} &
-\end{flalign*}
-By the definition, an interface belongs to $\mostSpecific(m, I, J)$ if and only if:
-\begin{itemize}
-	\item It is between $I$ and $J$;
-	\item It hierarchically overrides $J.m$;
-	\item Any subtype of it does not belong to the same set.
-\end{itemize}
-
-\subsection{$\canInstantiate$}
-$\canInstantiate(I)$ checks whether interface $I$ can be instantiated by the keyword $\kwnew$.
-Below is the algorithm:
-
-\begin{flalign*}
-	& \rhd \textit{Definition of } \canInstantiate(I): & \\
-	& \bullet \canInstantiate(I) = True & \\
-	& \indent\indent \textrm{with: } \forall J \in \mostSpecific(m, I, I), \mostSpecificOverride(m, I, J) = \{K\}, & \\
-	& \hspace{.77in} \textrm{ and } K[m\ \kwoverride\ J] = \method{I_e}{m}{I_x}{x}{J}{e_0} &
-\end{flalign*}
-$\mostSpecific(m, I, I)$ represents the set of branches $I$ inherits on method $m$. $I$ can be instantiated
-if and only if for every branch, the most specific implementation is unambiguous and non-abstract.
-
-\subsection{$\mbody$}
+Now we present the formal definition of \mbody{} that gives the expected results of the above mentioned examples.
 
@@
 $\mbody(m, I_d, I_s)$ denotes the method body lookup function.
-We use $I_d, I_s$, since $\mbody$ is usually invoked by a receiver of a method $m$, with its dynamic
-type $I_d$ and static type $I_s$. Such a function returns the most specific method implementation, more
+We use $I_d, I_s$, since $\mbody$ is usually invoked by a receiver of a method $m$, with its dynamic type $I_d$ and static type $I_s$.
+Such a function returns the most specific method implementation, more
 accurately, its parameters, returned expression (empty for abstract methods) and the types.
-It considers both originally-defined methods and hierarchical overriding methods, so $\mostSpecific$ and $\mostSpecificOverride$ are invoked.
+It considers both originally-defined methods and hierarchical overriding methods, so $\mostSpecific$ and $\mostSpecificOverride$ (see the definition in Section~\ref{sec:mostSpecific} and Section~\ref{sec:mostSpecificOverride}) are invoked as helper functions.
 
@@
 
-\subsection{Examples}
-
-\haoyuan{Need more examples?}
+\haoyuan{Need more examples?}\bruno{ask Marco.}
 \begin{figure*}[t]
@@
 
-Examples for $\mbody$ are shown in Figure~\ref{fig:examplesmbody}.
-Note that we use \lstinline|m| to denote an original method, and ``\lstinline|m|$\uparrow$\lstinline|A|'' for hierarchical overriding on \lstinline|A|.
-For each small example, the result
-gives the interface to which $m$ is dispatched. (a) is a basic model for unintentional method conflicts (triangle inheritance); (b) and (c) demonstrate
-that hierarchical dispatch can find the most specific original method and hierarchical overriding method. More interesting are the two bad examples
-(d) and (e), they both fail on $\mbody$.
-(d) is the well-known diamond inheritance, which our model also forbids, and (e) is again a diamond conflict because the two hierarchical overriding methods are working on the same operation.
-Both counter-examples imply that \lstinline|new D().A?m()| will
-lead to ambiguity, and in order for type soundness, both have to be denied by the type checker. This is guaranteed by the interface check
-\textsc{(T-Intf)} in Figure~\ref{fig:typingrules}.
+\subsection{Finding the Most Specific Origin: \mostSpecific}\label{sec:mostSpecific}
+We proceed to give the definition of auxiliary functions \mostSpecific{} and \mostSpecificOverride, which are two core functions for the method lookup algorithm. Generally,
+$\mostSpecific(m, I, J)$ finds the set of most specific interfaces where $m$ is originally defined, they should be above $I$ and
+along path $J$. ``Along path $J$'' means one should be either a subtype or a super type of $J$. Finally with $\prune$(defined in Section~\ref{sec:otherdefs})
+the overridden interfaces will be filtered out.
+
+\begin{flalign*}
+	& \rhd \textit{Definition of } \mostSpecific(m, I, J): & \\
+	& \bullet \mostSpecific(m, I, J) = \prune(origins) & \\
+	& \indent\indent \textrm{with: } origins = \{K \mid \subt{I}{K}, \textrm{ and } \subt{K}{J} \; \lor \; \subt{J}{K}, &\\
+	& \hspace{1.62in} \textrm{ and } K[m\ \kwoverride\ K] \textrm{ is defined} \} &
+\end{flalign*}
+By the definition, an interface belongs to $\mostSpecific(m, I, J)$ if and only if:
+\begin{itemize}
+	\item It originally defines $m$;
+	\item It is a super type of $I$;
+	\item It is either a super type or a subtype of $J$ (including $J$ itself);
+	\item Any subtype of it does not belong to the same result set because of $\prune$.
+\end{itemize}
+
+\subsection{Finding the Most Specifc Overriding: \mostSpecificOverride}\label{sec:mostSpecificOverride}
+The $\mostSpecific$ function only focuses on original method implementations, all the hierarchical overriding methods are omitted during that step.
+On the other hand, $\mostSpecificOverride(m, I, J)$ has the assumption that $J$ defines an original $m$, and this function tries to find the interfaces with most specific implementations that hierarchically overrides such an $m$.
+Formally,
+
+\begin{flalign*}
+	& \rhd \textit{Definition of } \mostSpecificOverride(m, I, J): & \\
+	& \bullet \mostSpecificOverride(m, I, J) = \prune(overrides) & \\
+	& \indent\indent \textrm{with: } overrides = \{K \mid \subt{I}{K}, \; \subt{K}{J} \textrm{ and } K[m\ \kwoverride\ J] \textrm{ is defined} &
+\end{flalign*}
+By the definition, an interface belongs to $\mostSpecific(m, I, J)$ if and only if:
+\begin{itemize}
+	\item It is between $I$ and $J$;
+	\item It hierarchically overrides $J.m$;
+	\item Any subtype of it does not belong to the same set.
+\end{itemize}
+
+\subsection{Others}\label{sec:otherdefs}
+Below we give other minor definitions of the auxiliary functions that are used in previous sections
+
+%%%%============================ I[m override J] ================%%%%%%%%
+\begin{flalign*}
+	& \rhd \textit{Definition of } I[m\ \kwoverride\ J]: & \\
+	& \bullet I[m\ \kwoverride\ J] = \method{I_e}{m}{I_x}{x}{J}{e_0} & \\
+	& \indent\indent \textrm{with: }
+	  \kwinterface \; I \; \kwextends \; \overline{I} \; \{ \method{I_e}{m}{I_x}{x}{J}{e_0} \ldots \} & \\
+	& \bullet I[m\ \kwoverride\ J] = \absmethod{I_e}{m}{I_x}{x}{J} & \\
+	& \indent\indent \textrm{with: }
+	\kwinterface \; I \; \kwextends \; \overline{I} \; \{ \absmethod{I_e}{m}{I_x}{x}{J} \ldots \} & \\
+\end{flalign*}
+Here $I[m\ \kwoverride\ J]$ is basically a direct lookup for method $m$ in the body of $I$, where such a method
+overrides $J$ (like static dispatch). The method can be either concrete or abstract, and the body of definition is returned. Notice that
+by our syntax, $I[m\ \kwoverride\ I]$ is looking for the originally-defined method $m$ in $I$.
+%%%%============================ I[m override J] end================%%%%%%%%
+
+%%%%============================ prune(set) ================%%%%%%%%
+\begin{flalign*}
+	& \rhd \textit{Definition of } \prune(set): & \\
+	& \bullet \prune(set) = \{I \in set \; | \; \nexists J \in set\setminus I, J <: I\} &
+\end{flalign*}
+The $\prune$ function takes a set of
+types, and filters out those that have subtypes in the same set. In the returned set,
+none of them has subtyping relation to one another, since all super types have been removed.
+%%%%============================ prune(set) end ================%%%%%%%%
+
+%%%%============================ canOverride ================%%%%%%%%
+\begin{flalign*}
+	& \rhd \textit{Definition of } \canOverride(m, I, J): & \\
+	& \bullet \canOverride(m, I, J) = True & \\
+	& \indent\indent \textrm{with: } I[m\ \kwoverride\ I] = I_e \; m(\overline{I_x} \; \overline{x}) \; \kwoverride \; I \ldots & \\
+	& \hspace{.77in} J[m\ \kwoverride\ J] = I_e \; m(\overline{I_x} \; \overline{y}) \; \kwoverride \; J \ldots &
+\end{flalign*}
+$\canOverride$ just checks that two original $m$ in $I$ and $J$ have the same type.
+%%%%============================ canOverride end ================%%%%%%%%
+
+%%%%============================ canInstantiate ================%%%%%%%%
+$\canInstantiate(I)$ checks whether interface $I$ can be instantiated by the keyword $\kwnew$.
+Below is the algorithm:\bruno{used for what and where?}
+
+\begin{flalign*}
+	& \rhd \textit{Definition of } \canInstantiate(I): & \\
+	& \bullet \canInstantiate(I) = True & \\
+	& \indent\indent \textrm{with: } \forall J \in \mostSpecific(m, I, I), \mostSpecificOverride(m, I, J) = \{K\}, & \\
+	& \hspace{.77in} \textrm{ and } K[m\ \kwoverride\ J] = \method{I_e}{m}{I_x}{x}{J}{e_0} &
+\end{flalign*}
+$\mostSpecific(m, I, I)$ represents the set of branches $I$ inherits on method $m$. $I$ can be instantiated
+if and only if for every branch, the most specific implementation is unambiguous and non-abstract.
+%%%%============================ canInstantiate end ================%%%%%%%%

### 2017-10-11 NewVersion/paper.tex
title
Added a small example. Now S3 is ready.

@@
 	showtabs=false,                 % show tabs within strings adding particular underscores
-	morekeywords={var,updates},
+	morekeywords={var,override},
 	%  frame=single,                   % adds a frame around the code
@@
 % \title{FHJ: A Formal Model for Resolving Unintended Conflicts in Multiple Inheritance}
-\title{Hierarchical Dispatching and Overriding}
+\title{FHJ: A Formal Model for Hierarchical Dispatching and Overriding}
 %\subtitle{\InterfaceBased Programming for the Masses}

### 2017-10-11 NewVersion/sections/Formalization.tex
Added a small example. Now S3 is ready.

@@
 
-\subsection{Subtyping and Typing Rules}
+\subsection{Subtyping and Typing Rules}\label{subsec:typingrules}
 \paragraph{Subtyping}
@@
 hierarchical dispatching algorithm. The formal definition will be introduced in
-Section~\ref{subsec:auxdefs}. To overview,
+Section~\ref{sec:auxdefs}. To overview,
 the hierarchical invocation $\mbody(m, I, J)$ means ``finding most specific $m$
@@
 \textsc{(T-New)} is the typing rule for object creation $\new{I}$.
-The auxiliary function $\canInstantiate(I)$ checks whether interface $I$ can be instantiated or not, formalized in Section~\ref{subsec:auxdefs}.
+The auxiliary function $\canInstantiate(I)$ checks whether interface $I$ can be instantiated or not, formalized in Section~\ref{sec:auxdefs}.
 Since triangle inheritance accepts conflicting branches to coexist, the check requires that the most specific method is concrete for each method on each branch.
@@
 \textsc{(T-Method)} is more interesting since a method can either be an original method or a hierarchical overriding, though
-they share the same syntax and method typing rule. $\mostSpecific(m, I, J)$ is a fundamental function from Section~\ref{subsec:auxdefs},
+they share the same syntax and method typing rule. $\mostSpecific(m, I, J)$ is a fundamental function from Section~\ref{sec:auxdefs},
 used to find ``the most specific interfaces that are above $I$ and along path $J$, and originally defines $m$''. By ``most specific interfaces'',
@@
 condition checks whether the overriding between original methods preserves typing.
-In the condition we again use some helper functions from Section~\ref{subsec:auxdefs}.
+In the condition we again use some helper functions from Section~\ref{sec:auxdefs}.
 $I[m\ \kwoverride\ I]$ is defined if $I$ originally defines $m$, and $\canOverride(m, I, J)$ checks whether $I.m$ has the same type as $J.m$.
@@
 
-\paragraph{Examples for mbody: TODO}
+\paragraph{Counter-Example} Counter-examples can promote understanding on the typing rules. Here we refer to case (e)
+in Figure~\ref{fig:examplesmbody}. To be specific, the entire program in \MIM{} is as follows:
 
-\begin{figure*}
+\vspace{3pt}\begin{lstlisting}
+interface T                 {}
+interface T1 extends T      {}
+interface T2 extends T      {}
+interface A                 { T m() override A { return new T(); } }
+interface B extends A       { T m() override A { return new T1(); } }
+interface C extends A       { T m() override A { return new T2(); } }
+interface D extends B, C {}
+
+((A) new D()).m()
+\end{lstlisting}\vspace{3pt}
+This program does not compile on $D$, because of the second condition in \textsc{(T-Intf)}, where $I$ equals $D$ and $J$ equals $A$.
+By the algorithm, $\mbody(m, A, A)$ will refer to $A.m$, but $\mbody(m, D, A)$ is undefined, since both $B.m$ and $C.m$ are most specific
+to D along path $A$, which forms a diamond. The expression \lstinline|((A) new D()).m()| is one example of triggering ambiguity, but \MIM{}
+simply rejects the definition of $D$. To resolve the issue, the programmer need to have an overriding method in $D$, to explicitly merge
+the conflicting ones.
+
+\begin{figure*}[t]
 \saveSpaceFig
@@
 object $\new{I}$. \textsc{(C-AnnoReduce)} merges nested upcasts into a single upcast with the outermost type.
+
+\begin{comment}
+\paragraph{Example} In contrast with the counter-example in Section~\ref{subsec:typingrules}, it is better to understand semantics by
+well-compiled examples. Here we abstract a variant of the \lstinline|DrawableDeck| example:
+
+\vspace{3pt}\begin{lstlisting}
+interface Void       {}
+interface JFrame     {}
+interface Deck       { Void draw() override Deck { return new Void(); } }
+interface Drawable { JFrame draw() override Drawable; }
+interface DrawableDeck extends Drawable, Deck {
+  JFrame draw() override Drawable {
+    return new JFrame();
+  }
+}
+
+((Drawable) new DrawableDeck()).draw()
+\end{lstlisting}\vspace{3pt}
+We put \lstinline|Drawable.draw| as an abstract method instead, but hierarchically override it in \lstinline|DrawableDeck|.
+By typing rules, the code is well-compiled. And during runtime,
+\begin{align*}
+	& ((Drawable) new DrawableDeck()).draw() \\
+\rightarrow & (JFrame) new JFrame()
+\end{align*}
+\end{comment}
 

### 2017-10-11 NewVersion/sections/Overview.tex
added a UML graph
Added a small example. Now S3 is ready.

@@
 
-\subsection{Problem 1: Unintentional Method Conflicts}
+\subsection{Problem 1: Unintentional Method Conflicts}\label{subsec:problem1}
 Suppose that two components \lstinline|Deck| and \lstinline|Drawable| 
@@
 
+% \begin{figure*}[t]
+% 	\saveSpaceFig
+% 	\centering
+% 	\includegraphics[height=2cm]{pics/DrawableSafeDeck.pdf}
+% 	\caption{UML graph for \lstinline|DrawableSafeDeck|.}\label{fig:drawablesafedeck}
+% 	\saveSpaceFig
+% \end{figure*}
+
 \begin{figure*}[t]
-	\saveSpaceFig
+  % \nocaptionrule
   \centering
-	\includegraphics[height=2cm]{pics/DrawableSafeDeck.pdf}
-	\caption{UML graph for \lstinline|DrawableSafeDeck|.}\label{fig:drawablesafedeck}
-	\saveSpaceFig
+  \begin{minipage}[t]{0.4\textwidth}
+  \includegraphics[height=4cm]{pics/DrawableSafeDeck1.pdf}
+  \end{minipage}
+  \hspace*{2pt}
+  \begin{minipage}[t]{0.5\textwidth}
+  \includegraphics[height=4cm]{pics/DrawableSafeDeck0.pdf}
+  \end{minipage}
+  \caption{UML graphs for \lstinline|DrawableSafeDeck|.}\label{fig:drawablesafedeck}
 \end{figure*}
+\yanlin{todo: change text and add a ref in Introduction}
 

### 2017-10-11 NewVersion/sections/Auxiliary.tex
Quick comments on S4.

@@
 directly implement our algorithm for method lookup.
-\bruno{I felt like there's not enough explanation/context in this
-  section. It is just dumping definitions without connecting them and
-  their purpose properly.}
+%\bruno{I felt like there's not enough explanation/context in this
+ % section. It is just dumping definitions without connecting them and
+ % their purpose properly.}
+
+\bruno{used for what and where?}\haoyuan{todo: used for where}
 
@@
 Our model guarantees this by the interface checking rule\textsc{(T-Intf)} in Figure~\ref{fig:typingrules}.
+\haoyuan{need better explanation on these examples.}
 
@@
 accurately, its parameters, returned expression (empty for abstract methods) and the types.
-It considers both originally-defined methods and hierarchical overriding methods, so $\mostSpecific$ and $\mostSpecificOverride$ (see the definition in Section~\ref{sec:mostSpecific} and Section~\ref{sec:mostSpecificOverride}) are invoked as helper functions.
+It considers both originally-defined methods and hierarchical overriding methods, so $\mostSpecific$ and $\mostSpecificOverride$ (see the definition in Section~\ref{sec:mostSpecific} and Section~\ref{sec:mostSpecificOverride}) are both invoked.
 
-To calculate $\mbody(m, I_d, I_s)$, the invocation of $\mostSpecific$ looks for the most specific original methods and expects a singleton set, so as to avoid unambiguity.
+To calculate $\mbody(m, I_d, I_s)$, the invocation of $\mostSpecific$ looks for the most specific original methods and their interfaces, and expects a singleton set, so as to avoid unambiguity.
 Furthermore, the invocation of $\mostSpecificOverride$ also expects a unique (unambiguous) most specific hierarchical override.
@@
 \subsection{Finding the Most Specific Origin: \mostSpecific}\label{sec:mostSpecific}
-We proceed to give the definition of auxiliary functions \mostSpecific{} and \mostSpecificOverride, which are two core functions for the method lookup algorithm. Generally,
+We proceed to give the definition of two core functions that support method lookup, namely \mostSpecific{} and \mostSpecificOverride. Generally,
 $\mostSpecific(m, I, J)$ finds the set of most specific interfaces where $m$ is originally defined, they should be above $I$ and
-along path $J$. ``Along path $J$'' means one should be either a subtype or a super type of $J$. Finally with $\prune$(defined in Section~\ref{sec:otherdefs})
+along path $J$. ``Along path $J$'' means one should be either a subtype or a super type of $J$. Finally with $\prune$ (defined in Section~\ref{sec:otherdefs})
 the overridden interfaces will be filtered out.
@@
 \subsection{Others}\label{sec:otherdefs}
-Below we give other minor definitions of the auxiliary functions that are used in previous sections
+Below we give other minor definitions of the auxiliary functions that are used in previous sections.
 
@@
 %%%%============================ canInstantiate ================%%%%%%%%
-$\canInstantiate(I)$ checks whether interface $I$ can be instantiated by the keyword $\kwnew$.
-Below is the algorithm:\bruno{used for what and where?}
-
 \begin{flalign*}
@@
 \end{flalign*}
+$\canInstantiate(I)$ checks whether interface $I$ can be instantiated by the keyword $\kwnew$.
 $\mostSpecific(m, I, I)$ represents the set of branches $I$ inherits on method $m$. $I$ can be instantiated

### 2017-10-11 NewVersion/sections/Introduction.tex
typos
revised S2 (need Haoyuan to fix "interaction")

@@
 %%drawbacks as we will discuss in Section~\ref{sec:overview}.
-\bruno{The previous paragraph needs to be revised to better discuss the
-  limitations of the C++ approach. Yanlin, Marco can you have a look
-  at this?}
+% \bruno{The previous paragraph needs to be revised to better discuss the
+%   limitations of the C++ approach. Yanlin, Marco can you have a look
+%   at this?}
 
@@
 	\item \textbf{Hierarchical overriding:} a novel notion that allows
-          methods to override on individual branches of the class hierarchy.
+          methods to override individual branches of the class hierarchy.
 	\item \textbf{\name:} a formalized model based on

### 2017-10-11 NewVersion/sections/Overview.tex
revised S2 (need Haoyuan to fix "interaction")

@@
 Problems 1 and 2 are related to hierarchical dispatching, and in 
-C++ it is possible to have similar solutions to both
+C++ it is possible to have similar solutions as ours to both
 problems. Hence it is important to emphasize that, with respect to
@@
 mechanism. Instead, 
-inspired by the C++ solution, our contribution is the formalization a minimal calculus
-of this feature together with a proof type soundness. However, for the final problem, there is no satisfactory approach
+inspired by the C++ solution, our contribution is formalizing a minimal calculus
+of this feature together with a proof of type soundness. However, for the final problem, there is no satisfactory approach
 in existing languages, thus we propose a new feature (hierarchical
@@
 The method returns \lstinline|void|. Note that, similarly to
-Featherweight Java~\cite{}\bruno{reference}, \lstinline|void| is
+Featherweight Java~\cite{Igarashi01FJ}, \lstinline|void| is
 unsupported in our formalization. We could have also defined an interface called \lstinline|Void|
@@
 
-This case is the so-called \textit{unintentional method conflicts}. It arises when two inherited methods happen have
+This case is the so-called \textit{unintentional method conflicts}. It arises when two inherited methods happen to have
 the same name and parameter types, but they are designed for different functionalities with different semantics.
@@
 method. Therefore \MIM{} accepts the definition of \lstinline|DrawableDeck|. To disambiguite method calls
-we can use \emph{up-casts} in \MIM{}'s, so as to specify the ``branch'' in the
+we can use \emph{up-casts} in \MIM{}, so as to specify the ``branch'' in the
 inheritance hierarchy that should be called. The following code
@@
 With static dispatching, we may have to copy the \lstinline|shuffleAndDraw| code into \lstinline|SafeDeck|,
-so as to be adaptive to the new \lstinline|draw|. Yet dynamic dispatching immediately saves us from the duplicate work,
+so as to be adaptive to the new \lstinline|draw|. Yet dynamic dispatching immediately saves us from the duplicated work,
 since the method becomes automatically adaptive. Nevertheless, as seen before, dynamic dispatch would potentially introduce ambiguity,
-for instance, when we have the class hierarchy structure in Figure~\ref{fig:drawablesafedeck} and the following code:
+for instance, when we have the class hierarchy structure shown in Figure~\ref{fig:drawablesafedeck}(left) and the following code:
 
@@
 combination of static and dynamic dispatch. Intuitively, the static type specifies one branch
-to avoid ambiguity, and the dynamic type finds the most specific implementation on that branch. The formal algorithm
-will be introduced later.\bruno{avoid using words like ``later'' or
-  ``before''. Instead use references to the actual Sections.}
+to avoid ambiguity, and the dynamic type finds the most specific implementation on that branch.
+The formal algorithm will be introduced in Section~\ref{sec:formalization} and Section~\ref{sec:auxdefs}.
 
@@
 override the individual conflicting methods, rather than overriding all
-conflicting methods into a single merged method.  We illustrate the
+conflicting methods into a single merged one. We illustrate the
 problem and the need for a more refined overrding mechanism with 
@@
 (including C++), the existing approaches are unsatisfactory.
-One direction is to simply avoid this issue, by putting overriding before inheritance. For example, we define a new component
-that extends \lstinline|Drawable|, simply draw the deck as a rectangle, and modifies the hierarchy:
+One direction is to simply avoid this issue, by putting overriding before inheritance.
+For example, as shown in Figure~\ref{fig:drawablesafedeck}(right), we define a new component \lstinline|DrawableRect| that extends \lstinline|Drawable|, which simply draws the deck as a rectangle, and modifies the hierarchy:
 \vspace{3pt}\begin{lstlisting}
@@
 ((Drawable)new DrawableSafeDeck()).draw(); // calls the latest draw
-\end{lstlisting}\vspace{3pt}\bruno{make override a keyword in
-  lstlisting.}
+\end{lstlisting}\vspace{3pt}
+
 Here the idea is that \emph{only} \lstinline{Drawable.draw} is
@@
 
-\paragraph{Overview of hierarchical dispatching algorithm:} In our
+\paragraph{A peek of hierarchical dispatching algorithm:} In our
 model, triangle inheritance allows several original methods (branches)

### 2017-10-12 NewVersion/sections/Introduction.tex
Totos listed (meeting summary).

@@
+\yanlin{
+TODOs:
+\begin{itemize}
+\item UML Diagram for full solution in introduction with informal explanation
+\item Move Figure 5 to end of Section 2 together with explanation
+\item Improve Figure 5 with additional mbody calls
+\item Improve Figure 5 with visual information that signals that in examples d) and e) then D does not type-check
+\item Make names of classes more consistent in Figure 5
+\item Add example (f) : A m      B m   C m   D  m  This would compile, note that if it was BArrowA m and/or CArrowA m it would also compile and D would have the same observable behaviour
+\item remove S1 “Unfortunately, such an issue ...”
+\item S2, should remove the discussion about JFrmae. all return type void.
+\item S2, mention DrawableDeck in P2.3 is a new version of DrawableDeck before.
+\item S2, “Ideally, we want that invocation to be dynamically dispatched.” --> “In FHJ, this invocation is dynamically dispatched.“.
+and revise the following paragraph on “we may have to copy the shuffleAndDraw code into SafeDeck, so as to be adaptive to the new draw.
+“.
+\item S2.2 revise paragraph “Implicit and Explicit Upcasts “.
+\item S2.3 (Maybe) put “Potential solutions/workarounds in existing languages” after “FHJ solution”.
+\item S2.3 (Maybe) add “redraw()” method in Drawable. and add another method call similar to shuffleAndDraw()
+\item Talk about Fig5 earlier. Move from S4.1 to S2.3 (a peek of ..)
+\item The keywords in code are barely distinghuishable from other code,  make them bolder/darker
+
+\item in Figure 1, the UML diagram on the right side is not quite right, 
+we want to be able to override draw from Drawable in DrawableSafeDeck, 
+the override (which is *the most important point*) is not in the UML diagram.
+  => Figure 1 on the right is the UML for P3 potential workaround, not for P3 FHJ, we need another UML. 
+\item Submit abstract
+\item Introduction to revise (by Bruno)
+\item Revise overview (Yanlin and Haoyuan)
+\item Section 4, 5 (Haoyuan)
+\item Section 6 (Yanlin)
+\item Section 7 (Yanlin and Haoyuan)
+\end{itemize}
+}
+
 \section{Introduction}
@@
 appropriate mechanisms to deal with them are available. 
-Unfortunately, such an issue has not received much formal study 
-before. In practice, existing languages only provide limited support for
+% Unfortunately, such an issue has not received much formal study 
+% before. 
+In practice, existing languages only provide limited support for
 the issue. In most languages, the mechanisms available to deal with this problem are the same as the diamond

### 2017-10-12 NewVersion/paper.tex
make keywords bold.

@@
 	escapeinside={(*}{*)},          % if you want to add a comment within your code
-	keywordstyle=\ttfamily\bfseries,
+	keywordstyle=\sffamily\bfseries,
 	aboveskip=0pt,

### 2017-10-12 NewVersion/sections/Introduction.tex
make keywords bold.
revised Overview

@@
 \item remove S1 “Unfortunately, such an issue ...”
-\item S2, should remove the discussion about JFrmae. all return type void.
-\item S2, mention DrawableDeck in P2.3 is a new version of DrawableDeck before.
-\item S2, “Ideally, we want that invocation to be dynamically dispatched.” --> “In FHJ, this invocation is dynamically dispatched.“.
+\item (\checkmark)S2, should remove the discussion about JFrmae. all return type void.
+\item (\checkmark)S2, mention DrawableDeck in P2.3 is a new version of DrawableDeck before.
+\item (\checkmark)S2, “Ideally, we want that invocation to be dynamically dispatched.” --> “In FHJ, this invocation is dynamically dispatched.“.
 and revise the following paragraph on “we may have to copy the shuffleAndDraw code into SafeDeck, so as to be adaptive to the new draw.
@@
 \item Talk about Fig5 earlier. Move from S4.1 to S2.3 (a peek of ..)
-\item The keywords in code are barely distinghuishable from other code,  make them bolder/darker
+%\item The keywords in code are barely distinghuishable from other code,  make them bolder/darker
 
-\item in Figure 1, the UML diagram on the right side is not quite right, 
+\item (\checkmark)in Figure 1, the UML diagram on the right side is not quite right, 
 we want to be able to override draw from Drawable in DrawableSafeDeck, 

### 2017-10-12 NewVersion/sections/Overview.tex
added UML for P3 FHJ
revised Overview

@@
 on the screen, while the \lstinline|draw| method in \lstinline|Deck| simply
-prints out a message.
+prints out a message \lstinline|"Draw a card."|.
 
@@
 interface Drawable {
-  JFrame draw() { // draws something on the screen
+  void draw() { // draws something on the screen
     JFrame frame = new JFrame();
     frame.setVisible(true);
-    return frame;
   }
@@
 \lstinline|Drawable|
-the program has to create a blank canvas by \lstinline|JFrame|, which
-is a pre-defined type.
+the program create a blank canvas by \lstinline|JFrame| and set the visibility to \lstinline|true|.
+
 \begin{comment}
@@
 \end{lstlisting}\vspace{3pt}
-Here \lstinline|shuffleAndDraw| \emph{invokes \lstinline|draw| from its own enclosing type}. Ideally,
-we want that invocation to be dynamically dispatched. This is important, because a programmer may define a subtype
-of \lstinline|Deck| and override the method:
+Here \lstinline|shuffleAndDraw| \emph{invokes \lstinline|draw| from its own enclosing type}.
+In \MIM{}, this invocation is dynamically dispatched.
+This is important, because a programmer may define a subtype
+of \lstinline|Deck| and override the method \lstinline|draw|:
 
@@
 \end{lstlisting}\vspace{3pt}
-With static dispatching, we may have to copy the \lstinline|shuffleAndDraw| code into \lstinline|SafeDeck|,
-so as to be adaptive to the new \lstinline|draw|. Yet dynamic dispatching immediately saves us from the duplicated work,
-since the method becomes automatically adaptive. Nevertheless, as seen before, dynamic dispatch would potentially introduce ambiguity,
+Without dynamic dispatching, we may have to copy the \lstinline|shuffleAndDraw| code into \lstinline|SafeDeck|, so that \lstinline|shuffleAndDraw| calls the new \lstinline|draw| defined in \lstinline|SafeDeck|.
+Yet dynamic dispatching immediately saves us from the duplication work,
+since the method becomes automatically dispatched to the most specific one. Nevertheless, as seen before, dynamic dispatch would potentially introduce ambiguity,
 for instance, when we have the class hierarchy structure shown in Figure~\ref{fig:drawablesafedeck}(left) and the following code:
@@
   \centering
-  \begin{minipage}[t]{0.4\textwidth}
+  \begin{minipage}[t]{0.28\textwidth}
   \includegraphics[height=4cm]{pics/DrawableSafeDeck1.pdf}
   \end{minipage}
+  \centering
   \hspace*{2pt}
-  \begin{minipage}[t]{0.5\textwidth}
+  \begin{minipage}[t]{0.4\textwidth}
   \includegraphics[height=4cm]{pics/DrawableSafeDeck0.pdf}
+  \end{minipage}
+  \centering
+  \hspace*{2pt}
+  \begin{minipage}[t]{0.25\textwidth}
+  \includegraphics[height=4cm]{pics/DrawableSafeDeck3.pdf}
   \end{minipage}  
@@
 \end{figure*}
-\yanlin{todo: change text and add a ref in Introduction}
 
@@
 \paragraph{Implicit and Explicit Upcasts}
+\yanlin{todo: Haoyuan.}
 In our language model, there are two types of casts: \emph{implicit casts} and \emph{explicit upcasts}. The implicit casts appear
@@
 \subsection{Problem 3: Overriding on Individual Branches}\label{subsec:partialoverrides}
-
 Method overriding is common in Object-Oriented Programming. 
@@
 
-Suppose that the programmer defines \lstinline|DrawableSafeDeck|, but he needs to override
+Suppose that the programmer defines a new interface \lstinline|DrawableSafeDeck| (based on the code in Section~\ref{subsec:problem2} without the old \lstinline|DrawableSafeDeck|), but he needs to override
 \lstinline|Drawable.draw| and give a new implementation of drawing, so that the deck can indeed be visualized on the canvas.

### 2017-10-12 NewVersion/sections/Conclusion.tex
Example in intro

--- 2017-06-19 Aplas17/sections/Conclusion.tex
@@
 
-This paper proposes \MIM{} as a new multiple inheritance model for unintentional method conflicts.
-Existing approaches including static dispatch and dynamic dispatch have to compromise between code reuse
-and type safety, whereas \MIM{} uses a different solution called hierarchical dispatch to obtain both.
-Such an approach not only offers great code reuse like dynamic dispatch but also ensures unambiguity by
-our algorithm for method resolution. This paper also introduces hierarchical overriding that refines branches individually.
-\MIM{} is formalized with a basis on Featherweight Java and supported
-by a few theorems. The prototype is implemented in Scala as a simple interpreter.
+This paper proposes \MIM{} as a new multiple inheritance model for
+unintentional method conflicts. Previous approaches 
+either do not support unintentional method conflicts, have to
+compromise between code reuse and type safety, or do not fully support
+overriding in the presence of unintentional conflicts. To deal with unintentional method conflicts we
+introduce two key mechanisms: hierarchical dispatching and
+hierarchical overriding. Hierarchical dispatching is inspired by the
+mechanisms in C++. We provide a minimal formal model of hierarchical
+dispatching in \MIM{}. Such algorithm makes use of both dynamic type
+information and path information from either upcasts or parameters'
+information. Such an approach not only offers great code reuse like
+dynamic dispatch but also ensures unambiguity by our algorithm for
+method resolution. Additionally we introduce \emph{hierarchical
+  overriding} to allow conflicting methods in different branches to be
+individually overriden. \MIM{} is formalized following the style of
+Featherweight Java and type-soundness is proved. A prototype language is
+implemented in Scala as a simple interpreter.
 
-Our model can certainly be improved at some aspects. We did not formalize fields as in Featherweight Java for simplicity.
-And we did not formalize other common features including
-method overloading, casts, covariant return types, and so on, some of which are orthogonal in the design space.
-Moreover, we restrict that hierarchical overriding can only work on original methods.
-Potentially a looser condition can better support encapsulation and modularity with respect to code design.
+Our model can certainly be improved at some aspects. We do not
+formalize fields as in Featherweight Java for the reason of
+simplicity\bruno{I'm not sure that simplicity is a good excuse; 
+following the trait model may be a better excuse.}. And we do not formalize other common features including
+method overloading, casts, covariant return types, and so on, some of
+which are orthogonal in the design space. Moreover, we restrict that
+hierarchical overriding can only work on original methods. Potentially
+a looser condition can better support encapsulation and modularity
+with respect to code design as discussed in
+Section~\ref{sec:discussion} and could be a good future work.

### 2017-10-12 NewVersion/sections/Introduction.tex
Example in intro

--- 2017-10-12 NewVersion/sections/Introduction.tex
@@
 \item Talk about Fig5 earlier. Move from S4.1 to S2.3 (a peek of ..)
-\item The keywords in code are barely distinghuishable from other code,  make them bolder/darker
+%\item The keywords in code are barely distinghuishable from other code,  make them bolder/darker
 
@@
 algorithm, which (as far as we know) has not been formalized before.
-Furthermore, \textit{hierarchical overriding} allows method overriding to be applied
+
+\begin{figure}
+\center  \includegraphics[height=4cm]{pics/DrawableSafeDeck3.pdf}
+\caption{\lstinline|DrawableSafeDeck|: an illustration of hierarchical overriding.}
+\label{fig:main}
+\end{figure}
+
+\textit{Hierarchical overriding} is a novel language
+mechanism that allows method overriding to be applied
 only to one branch of the class hierarchy. Hierarchical overriding 
 adds expressive power that is not available in languages such as 
-C++ or C\#. To present both ideas, we introduce a
+C++ or C\#. Hierarchical overriding allows overriding to work 
+for classes with multiple (conflicting) methods sharing the 
+same names and signatures. An example is presented in 
+Figure~\ref{fig:main}. In this example there are 4 classes/interfaces.
+Two classes model a deck of cards (\lstinline|Deck|) and a class for
+drawable widgets (\lstinline|Drawable|). 
+A class \lstinline|SafeDeck| adds functionality to check whether a 
+the deck is empty and to prevent drawing a card from an empty deck. 
+The interesting class is \lstinline|DrawableSafeDeck|, which inherits 
+from both \lstinline|SafeDeck| and \lstinline|Drawable|. Hierchical
+overriding is used in \lstinline|DrawableSafeDeck| to keep two separate \lstinline|draw|
+methods for each parent, but overriding \emph{only} the \lstinline|draw|
+method coming from \lstinline|Drawable|, in order to draw a widget
+with a deck of cards. Note that hierchical overriding is denoted in the UML
+diagram with the notation
+\lstinline|draw()|$\shneg$\lstinline|Drawable|. In this case the
+notation expresses that the \lstinline|draw| method from \lstinline|Drawable|
+is overriden. Although in this example only one of the
+\lstinline|draw| methods is overriden (and the other is simply inherited), hierarchical overriding
+supports multiple conflicting methods to be independently overriden as well.
+
+To present hierarchical overriding and dispatching, we introduce a
 formalized model \MIM{} in Section~\ref{sec:formalization} based on

### 2017-10-12 NewVersion/sections/Discussion.tex
Added bruno's comment on fields.

@@
 
-One typical non-orthogonal extension to our model could be to have fields.
-Having fields in OO multiple inheritance is a non-trivial issue.
-There has been a lot of work on it, such as C++ that uses virtual inheritance~\cite{ellis1990annotated}.
-The trait model simply disallows state to avoid that issue.
-In our language, however, we can perhaps borrow the idea of \textit{interface-based programming}~\cite{classless}, which actually models state with abstract state operations.
+One typical non-orthogonal extension to \MIM{} could be to have fields.
+The design of \MIM{} can be viewed as an extension to Java 8 with default methods which allows for unintentional method conflicts.
+Like Java interfaces and traits, state is forbidden in \MIM{} since having state in OO multiple inheritance is a non-trivial issue.
+There has been some related work on it, such as C++ that uses virtual inheritance~\cite{ellis1990annotated}.
+In our model, however, we can perhaps borrow the idea of \textit{interface-based programming}~\cite{classless}, which models state with abstract state operations.
 This can be realized by extending our current model with static methods and anonymous classes from Java.

### 2017-10-12 NewVersion/sections/Introduction.tex

@@
 
-\item in Figure 1, the UML diagram on the right side is not quite right, 
+\item (\checkmark)in Figure 1, the UML diagram on the right side is not quite right, 
 we want to be able to override draw from Drawable in DrawableSafeDeck, 

### 2017-10-12 NewVersion/sections/Overview.tex

@@
 
+\begin{figure*}[t]
+	\vspace{-1ex}
+	\hspace{-15pt}\begin{tabular}{clclcl}
+		&\multicolumn{1}{c}{\includegraphics[width=1.5cm]{pics/P1.pdf}} & &
+		\multicolumn{1}{c}{\includegraphics[width=1.5cm]{pics/P2.pdf}} & &
+		\multicolumn{1}{c}{\includegraphics[width=1.5cm]{pics/P3.pdf}} \\
+		(a) & $\mbody(m,C,A) = (A,...)$\ \ \  & (b) & $\mbody(m,C,A) = (C,...)$\ \ \  & (c) & $\mbody(m,C,A) = (C,...)$ \\
+		& $\mbody(m,C,B) = (B,...)$ & & $\mbody(m,C,B) = (C,...)$ & & $\mbody(m,C,B) = (B,...)$ \\
+		& $\mbody(m,C,C) = \keyword{undefined}$ & & $\mbody(m,C,C) = (C,...)$ & & $\mbody(m,C,C) = \keyword{undefined}$ \\
+		& & & & & \\
+		& \multicolumn{1}{c}{\includegraphics[height=3cm]{pics/P4.pdf}} & &
+		\multicolumn{1}{c}{\includegraphics[height=3cm]{pics/P5.pdf}} & & 
+		\multicolumn{1}{c}{\includegraphics[height=3cm]{pics/P6.pdf}} \\ 
+		(d) & $\mbody(m,T,T) = (T,...)$\ \ \  & (e) & $\mbody(m,T,T) = (T,...)$\ \ \ & (f) & $\mbody(m,C,T) = (C,...)$ \\
+		& $\mbody(m,C,T) = \keyword{undefined}$ & & $\mbody(m,C,T) = \keyword{undefined}$ & & $\mbody(m,C,A) = (C,...)$ \\
+		& $C\text{ rejected by type-check}$ & & $C\text{ rejected by type-check}$ & & $\mbody(m,C,B) = (C,...)$ \\
+		& & & & & $\mbody(m,C,C) = (C,...)$
+	\end{tabular}
+	\caption{Examples on $\mbody$. ``$\uparrow$'' stands for hierarchical overriding.}\label{fig:examplesmbody}
+	%\saveSpaceFig
+\end{figure*}
+
 % Similar to many OO languages, the model also allows \textit{super method invocation} in a method body.

### 2017-10-12 NewVersion/sections/Auxiliary.tex
Put examples in Overview. To add text.
Changes in S2.

@@
 
-\subsection{Method Lookup Algorithm in \mbody{}}
+\subsection{Method Lookup Algorithm in \mbody{}}\label{subsec:mbodydef}
 Before showing the definition of \mbody{}, we start with several examples of method lookup, as shown in Figure~\ref{fig:examplesmbody}.
@@
 And finally the target method is returned.
-
-\haoyuan{Need more examples?}\bruno{ask Marco.}
-\begin{figure*}[t]
-	\centering
-	\vspace{-1ex}
-	\begin{tabular}{ccc}
-		\includegraphics[width=1.5cm]{pics/P1.pdf}\hspace{4pt} &
-		\includegraphics[width=1.5cm]{pics/P2.pdf}\hspace{4pt} &
-		\includegraphics[width=1.5cm]{pics/P3.pdf}\hspace{4pt} \\
-		(a) $\mbody(m,C,A) = (A,...)$\ \ \  & (b) $\mbody(m,C,A) = (C,...)$\ \ \  & (c) $\mbody(m,C,A) = (C,...)$
-	\end{tabular} \\
-	\begin{tabular}{cc}
-		\includegraphics[height=3cm]{pics/P4.pdf}\hspace{4pt} &
-		\includegraphics[height=3cm]{pics/P5.pdf}\hspace{4pt} \\ 
-		(d) $\mbody(m,D,A) = \keyword{undefined}$\ \ \  & (e) $\mbody(m,D,A) = \keyword{undefined}$
-	\end{tabular}
-	\caption{Examples on $\mbody$. ``$\uparrow$'' stands for hierarchical overriding.}\label{fig:examplesmbody}
-	%\saveSpaceFig
-\end{figure*}
 

### 2017-10-12 NewVersion/sections/Overview.tex
Changes in S2.

@@
 \yanlin{todo: Haoyuan.}
+\haoyuan{To move to S5.}
 In our language model, there are two types of casts: \emph{implicit casts} and \emph{explicit upcasts}. The implicit casts appear
@@
 	\item It changes the hierarchy and existing code, hence breaks the modularity.
-	\item The demand for separate overriding after the triangle
-          inheritance comes especially when there is
-          interaction\bruno{what interaction?}. In the above code we assume
+	\item Separate overriding is required to come after the triangle
+          inheritance, especially when the implementation needs functionality from both parents. In the above code we have assumed
 	that the overriding is unrelated to \lstinline|Deck|. But when the drawing relies on some information of the \lstinline|Deck|
@@
 from \lstinline|Drawable|.  
-The direct support for individual overriding also works when there is interaction. In our formalization, this feature is necessary
-and also involves in the algorithm of hierarchical dispatch.\bruno{the
-last two sentences are a bit unclear. I think it is related to ``interaction''.}
+The individual overriding allows us to make use of the methods from \lstinline|SafeDeck| as well. In the formalization, the 
+hierarchical overriding feature is also an important feature that involves in the algorithm of hierarchical dispatch.
+%\bruno{the last two sentences are a bit unclear. I think it is related to ``interaction''.}
 
-\paragraph{Terminology:} The \lstinline|draw| methods we saw in
-previous subsections\bruno{by now I saw many methods. Please be more precise.} are called \textit{original methods} in this paper, because they are originally defined in its interface.
+\paragraph{Terminology:} In \lstinline|Drawable|, \lstinline|Deck| and \lstinline|SafeDeck|, the \lstinline|draw| methods are called \textit{original methods} in this paper, because they are originally defined by the interfaces.
 In contrast, \lstinline|DrawableSafeDeck| defines a \textit{hierarchical overriding method}.
 The difference is that traditional method overriding overrides all branches by defining another original method, whereas hierarchical overriding only refines one branch.
-
-\paragraph{A peek of hierarchical dispatching algorithm:} In our
-model, triangle inheritance allows several original methods (branches)
-to coexist, and hierarchical dispatch first finds the most specific
-original method (branch), then it finds the most specific hierarchical
-overriding on that branch. A quick counter-example is when there are
-two hierarchical overriding methods on \lstinline|Drawable| in
-\lstinline|DrawableSafeDeck|, it leads to ambiguity. The compiler is
-supposed to forbid the case.\bruno{please show code illustrating this,
-and improve explanation.}
 
@@
 It does not really make sense to refine an old branch.
+\haoyuan{I think we are abusing font styles.
+Maybe put all bold text in italic, except for code.}
 
@@
 	\end{tabular}
-	\caption{Examples on $\mbody$. ``$\uparrow$'' stands for hierarchical overriding.}\label{fig:examplesmbody}
+	\caption{Examples in \MIM{}. ``$m\uparrow A$'' stands for hierarchical overriding ``$m$ \lstinline|override| $A$''.}\label{fig:examplesmbody}
 	%\saveSpaceFig
@@
 
+\paragraph{A peek of hierarchical dispatching algorithm:} In \MIM{}, triangle inheritance allows several original methods (branches)
+to coexist, and hierarchical dispatch first finds the most specific
+original method (branch), then it finds the most specific hierarchical
+overriding on that branch.
+
+Before the formalized algorithm, Figure~\ref{fig:examplesmbody} gives a peek at the behavior by
+some quick examples. The UML diagrams present the hierarchy. In (c) and (e), an up-arrow $\uparrow$ is short for ``\lstinline|override|''.
+In (d) and (e), a cross mark indicates that the interface fails to type-check. Generally, \MIM{} rejects on the definition of an interface
+during compilation, if it reaches a diamond and hence is possible to cause ambiguity. $\mbody$ is the method lookup function for hierarchical
+dispatch, formally defined in Section~\ref{subsec:mbodydef}.
+In general, $\mbody(m, X, Y) = (Z, ...)$ reflects that the source code \lstinline|((X) new Y()).m()| calls \lstinline|Z.m| in the runtime.
+It is undefined when method dispatch is ambiguous.
+
+In  Figure~\ref{fig:examplesmbody}, (a) is the base case for unintentional conflicts, namely the triangle inheritance.
+(b) uses overriding to explicitly merge the conflicting methods.
+(c) represents hierarchical overriding.
+(d) and (e) are two base cases of diamond inheritance in \MIM{}, and the definition of each $C$ is rejected because $T$ is an ambiguous parent to $C$.
+(f) gives a common solution to the diamond as in Java or traits, which is to explicitly override $A.m$ and $B.m$ in $C$.
+In the last three examples, conflicting methods $A.m$ and $B.m$ should be viewed as
+intentional conflicts, as they come from the same source $T$.
 % Similar to many OO languages, the model also allows \textit{super method invocation} in a method body.

### 2017-10-12 NewVersion/sections/Formalization.tex
First revision on S3

@@
 in an interface are either default methods or abstract methods. Default methods provide default implementations for methods. Abstract methods do not
-have method body, and in fact they can be considered as normal methods that return nothing. Abstract methods can be overridden with future implementations.
+have a method body. Abstract methods can be overridden with future implementations.
 
@@
 it implies that the inherited super types are excluded.
-Thus the condition $\mostSpecific(m, I, J) = \{J\}$ indicates the characteristics of a hierarchical overriding: it must override an original method; the overriding is direct and there does not exist any other original $m$ in between.
+Thus the condition $\mostSpecific(m, I, J) = \{J\}$ indicates a characteristic of a hierarchical overriding: it must override an original method; the overriding is direct and there does not exist any other original $m$ in between.
 Then $\mbody(m, J, J)$ provides the type of the original method, so hierarchical overriding has to preserve the type. Finally the return expression
@@
 \MIM{} rejects on the definition of interfaces when they reach a diamond. Consider the case when the second condition is broken: $\mbody(m, J, J)$
-is defined but $\mbody(m, I, J)$ is undefined for some $J$ and $m$. It indicates that $m$ is available and unambiguous from the perspective of $J$,
-but is ambiguous to $I$ on branch $J$. That means there are multiple overriding paths of $m$ from $J$ to $I$, which form a diamond. Hence rejecting
+is defined but $\mbody(m, I, J)$ is undefined for some $J$ and $m$. This indicates that $m$ is available and unambiguous from the perspective of $J$,
+but is ambiguous to $I$ on branch $J$. That means that there are multiple overriding paths of $m$ from $J$ to $I$, which form a diamond. Hence rejecting
 that case meets our expectation.
@@
 
-\paragraph{Counter-Example} Counter-examples can promote understanding on the typing rules. Here we refer to case (e)
+\paragraph{Example} \bruno{what is the purpose of this example:
+  state-it upfront please. Is this example meant to ilustrate T-Inf?
+  Then it's better to have the example together with the text
+  explaining T-inf.}
+Here we refer to case (e)
 in Figure~\ref{fig:examplesmbody}. To be specific, the entire program in \MIM{} is as follows:
@@
 
-\paragraph{Semantic Rule} \textsc{(S-Invk)} is the only computation rule we need for method invocation.
+\paragraph{Semantic Rules} \textsc{(S-Invk)} is the only computation rule we need for method invocation.
 As a small-step rule and by congruence, it assumes that the receiver and the arguments are already values.
@@
 rule reduces method invocation to $e_0$ with substitution.
-Parameters are substituted with arguments, and \lstinline|this| reference is substituted with the receiver,
+Parameters are substituted with arguments, and the \lstinline|this| reference is substituted by the receiver,
 and in the meanwhile implicit casts are applied, so that static types are recorded via annotations. Finally
@@
 We present the type soundness of the model by a few theorems below, following the standard technique of
-subject reduction and progress proposed by~\cite{Wright1994}. The proof, together with some lemmas, are
-in Appendix. The type soundness states that if an expression is well-typed, then after many reduction
+subject reduction and progress proposed by Wright et al.~\cite{Wright1994}. The proof, together with some lemmas, are
+in Appendix. Type soundness states that if an expression is well-typed, then after many reduction
 steps it must reduce to a value, and its annotation is the same as the static type of the original expression.
@@
 Our theorems are stricter than those of Featherweight Java~\cite{Igarashi01FJ}. Specifically, in both term substitution (a lemma in Appendix)
-and subject reduction, the type may go down in FJ, but in \MIM{} it is unchanged. The difference is due to
-subtyping; the parameter or \lstinline|this| reference requires some type $I$, but a value with a more specific type,
-which is subtype of $I$, can be passed. However, as \MIM{} keeps track of the static types, the annotations in the
-substitution actually ensures the type to be unchanged.
+and subject reduction, reduction may lead to a term with a subtype in
+FJ, but in \MIM{} types are unchanged. The difference is due to
+%%subtyping; the parameter or \lstinline|this| reference requires some type $I$, but a value with a more specific type,
+%%which is subtype of $I$, can be passed. However, as 
+the fact that \MIM{} keeps track of the static types during
+reduction. 
+In FJ, the information about the static types is lost.
+
+%the annotations in the
+%substitution actually ensures the type to be unchanged.

### 2017-10-12 NewVersion/sections/Auxiliary.tex
S4 adaped to the changes.

@@
 \subsection{Method Lookup Algorithm in \mbody{}}\label{subsec:mbodydef}
-Before showing the definition of \mbody{}, we start with several examples of method lookup, as shown in Figure~\ref{fig:examplesmbody}.
-Note that we use \lstinline|m| to denote an original method, and ``\lstinline|m|$\uparrow$\lstinline|A|'' for hierarchical overriding on \lstinline|A|.
-For each small example, the result gives the interface to which $m$ is dispatched.
-(a) is our old friend example for unintentional method conflicts (triangle inheritance); (b) and (c) demonstrate
-that hierarchical dispatch can find the most specific original method and hierarchical overriding method.
-More interesting are the two bad examples (d) and (e), they both fail on $\mbody$.
-(d) is the well-known diamond inheritance, where $\mbody(m, D, A)$ is \Undefined; (e) is again a diamond conflict because the two hierarchical overriding methods are overriding the same branch.
-Both counter-examples imply that \lstinline|(A)new D().m()| will
-lead to ambiguity, and in order to ensure type soundness, both of them have to be rejected by the type checker.
-Our model guarantees this by the interface checking rule\textsc{(T-Intf)} in Figure~\ref{fig:typingrules}.
-\haoyuan{need better explanation on these examples.}
 
-Now we present the formal definition of \mbody{} that gives the expected results of the above mentioned examples.
+$\mbody(m, I_d, I_s)$ denotes the method body lookup function.
+We use $I_d, I_s$, since $\mbody$ is usually invoked by a receiver of a method $m$, with its dynamic type $I_d$ and static type $I_s$.
+Such a function returns the most specific method implementation, more
+accurately, its parameters, returned expression (empty for abstract methods) and the types.
+It considers both originally-defined methods and hierarchical overriding methods, so $\mostSpecific$ and $\mostSpecificOverride$ (see the definition in Section~\ref{sec:mostSpecific} and Section~\ref{sec:mostSpecificOverride}) are both invoked.
+ The formal definition gives the expected results
+for the earlier examples in Figure~\ref{fig:examplesmbody}.
 
@@
 \end{flalign*}
-$\mbody(m, I_d, I_s)$ denotes the method body lookup function.
-We use $I_d, I_s$, since $\mbody$ is usually invoked by a receiver of a method $m$, with its dynamic type $I_d$ and static type $I_s$.
-Such a function returns the most specific method implementation, more
-accurately, its parameters, returned expression (empty for abstract methods) and the types.
-It considers both originally-defined methods and hierarchical overriding methods, so $\mostSpecific$ and $\mostSpecificOverride$ (see the definition in Section~\ref{sec:mostSpecific} and Section~\ref{sec:mostSpecificOverride}) are both invoked.
-
 To calculate $\mbody(m, I_d, I_s)$, the invocation of $\mostSpecific$ looks for the most specific original methods and their interfaces, and expects a singleton set, so as to avoid unambiguity.

### 2017-10-12 NewVersion/sections/Formalization.tex
Section 3

@@
 \section{Formalization}~\label{sec:formalization}
-In this section, we present the formal model called \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), following similar style of 
+In this section, we present a formal model called \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), following similar style of 
 Featherweight Java~\cite{Igarashi01FJ}. \MIM{} is a minimal core calculus that formalizes the core concept of hierarchical dispatch and overriding. The syntax, typing rules,
@@
 $\mbody$ is our key function for method lookup, based on the
-hierarchical dispatching algorithm. The formal definition will be introduced in
-Section~\ref{sec:auxdefs}. To overview,
-the hierarchical invocation $\mbody(m, I, J)$ means ``finding most specific $m$
+hierarchical dispatching algorithm. 
+The hierarchical invocation $\mbody(m, I, J)$ means ``finding most specific $m$
 above $I$ and along path $J$'', and usually $I$ denotes the dynamic type while $J$
-denotes the static type. In \textsc{(T-Invk)}, as the compilation should not be aware
+denotes the static type. 
+The formal definition of $\mbody(m, I, J)$ will be introduced in
+Section~\ref{sec:auxdefs}.
+In \textsc{(T-Invk)}, as the compilation should not be aware
 of the dynamic type, it only requires that invoking $m$ is valid for the static type of the
@@
 
-\textsc{(T-New)} is the typing rule for object creation $\new{I}$.
-The auxiliary function $\canInstantiate(I)$ checks whether interface $I$ can be instantiated or not, formalized in Section~\ref{sec:auxdefs}.
+\textsc{(T-New)} is the typing rule for object creation $\new{I}$. The
+auxiliary function $\canInstantiate(I)$ checks whether interface $I$
+can be instantiated or not, and is formalized in Section~\ref{sec:auxdefs}.
 Since triangle inheritance accepts conflicting branches to coexist, the check requires that the most specific method is concrete for each method on each branch.
@@
 \textsc{(T-Method)} is more interesting since a method can either be an original method or a hierarchical overriding, though
-they share the same syntax and method typing rule. $\mostSpecific(m, I, J)$ is a fundamental function from Section~\ref{sec:auxdefs},
-used to find ``the most specific interfaces that are above $I$ and along path $J$, and originally defines $m$''. By ``most specific interfaces'',
+they share the same syntax and method typing rule. $\mostSpecific(m, I, J)$ is a fundamental function,
+used to find ``the most specific interfaces that are above $I$ and
+along path $J$, and originally defines $m$'' (see
+Section~\ref{sec:auxdefs} for full definition).
+By ``most specific interfaces'',
 it implies that the inherited super types are excluded.
@@
 We present the type soundness of the model by a few theorems below, following the standard technique of
-subject reduction and progress proposed by Wright et al.~\cite{Wright1994}. The proof, together with some lemmas, are
+subject reduction and progress proposed by Wright and Felleisen~\cite{Wright1994}. The proof, together with some lemmas, are
 in Appendix. Type soundness states that if an expression is well-typed, then after many reduction

### 2017-10-12 NewVersion/sections/Formalization.tex
small fix S3

@@
 but is ambiguous to $I$ on branch $J$. That means that there are multiple overriding paths of $m$ from $J$ to $I$, which form a diamond. Hence rejecting
-that case meets our expectation.
-
-Finally, rule \textsc{(T-Anno)} is the typing rule for a cast expression. By the rule, only upcasts are valid.
-
-\paragraph{Example} \bruno{what is the purpose of this example:
+that case meets our expectation. Below is an example (Figure~\ref{fig:examplesmbody} (e)) that illustrates the reason why this condition is needed:
+\bruno{what is the purpose of this example:
   state-it upfront please. Is this example meant to ilustrate T-Inf?
   Then it's better to have the example together with the text
-  explaining T-inf.}
-Here we refer to case (e)
-in Figure~\ref{fig:examplesmbody}. To be specific, the entire program in \MIM{} is as follows:
-
+  explaining T-inf.} \yanlin{revised.please check whether you're happy with it.}
 \vspace{3pt}\begin{lstlisting}
@@
 
+Finally, rule \textsc{(T-Anno)} is the typing rule for a cast expression. By the rule, only upcasts are valid.
+
 \begin{figure*}[t]
 \saveSpaceFig
-
 \begin{mathpar}

### 2017-10-13 NewVersion/sections/Conclusion.tex
Slight change on conclusion.

@@
 
-This paper proposes \MIM{} as a new multiple inheritance model for
+This paper proposes \MIM{} as a formalized multiple inheritance model for
 unintentional method conflicts. Previous approaches 
@@
   overriding} to allow conflicting methods in different branches to be
-individually overriden. \MIM{} is formalized following the style of
+individually overriden.
+
+\MIM{} is formalized following the style of
 Featherweight Java and type-soundness is proved. A prototype language is
-implemented in Scala as a simple interpreter.
+implemented in Scala as a simple interpreter. We believe that the formalization of
+hierarchical dispatching features is general and
+can be safely embedded to other OO models, so as to have support for the triangle
+inheritance.
 
-Our model can certainly be improved at some aspects. We do not
-formalize fields as in Featherweight Java for the reason of
-simplicity\bruno{I'm not sure that simplicity is a good excuse; 
-following the trait model may be a better excuse.}. And we do not formalize other common features including
-method overloading, casts, covariant return types, and so on, some of
-which are orthogonal in the design space. Moreover, we restrict that
-hierarchical overriding can only work on original methods. Potentially
-a looser condition can better support encapsulation and modularity
-with respect to code design as discussed in
-Section~\ref{sec:discussion} and could be a good future work.
+Our model can certainly be improved at some aspects. 
+As discussed in Section~\ref{sec:discussion}, there are orthogonal and
+non-orthogonal features that can potentially be added to the design space. 
+The future work relates to loosening the model without giving up its soundness,
+together with more exploration on fields in the multiple inheritance setting.

### 2017-10-13 NewVersion/sections/Formalization.tex
fix Marco email comments

@@
 \vspace{3pt}\begin{lstlisting}
-interface T                 {}
-interface T1 extends T      {}
-interface T2 extends T      {}
-interface A                 { T m() override A { return new T(); } }
-interface B extends A       { T m() override A { return new T1(); } }
-interface C extends A       { T m() override A { return new T2(); } }
-interface D extends B, C {}
+interface T                 { T m() override T { return new T(); } }
+interface A extends T       { T m() override T { return new A(); } }
+interface B extends T       { T m() override T { return new B(); } }
+interface C extends A, B {}
 
-((A) new D()).m()
+((T) new C()).m()
 \end{lstlisting}\vspace{3pt}
-This program does not compile on $D$, because of the second condition in \textsc{(T-Intf)}, where $I$ equals $D$ and $J$ equals $A$.
-By the algorithm, $\mbody(m, A, A)$ will refer to $A.m$, but $\mbody(m, D, A)$ is undefined, since both $B.m$ and $C.m$ are most specific
-to D along path $A$, which forms a diamond. The expression \lstinline|((A) new D()).m()| is one example of triggering ambiguity, but \MIM{}
-simply rejects the definition of $D$. To resolve the issue, the programmer need to have an overriding method in $D$, to explicitly merge
+This program does not compile on interface $C$, because of the second condition in \textsc{(T-Intf)}, where $I$ equals $C$ and $J$ equals $T$.
+By the algorithm, $\mbody(m, T, T)$ will refer to $T.m$, but $\mbody(m, C, T)$ is undefined, since both $A.m$ and $B.m$ are most specific
+to $C$ along path $T$, which forms a diamond. The expression \lstinline|((A) new D()).m()| is one example of triggering ambiguity, but \MIM{}
+simply rejects the definition of $C$. To resolve the issue, the programmer need to have an overriding method in $C$, to explicitly merge
 the conflicting ones.

### 2017-10-15 NewVersion/sections/Auxiliary.tex
fix Marco email comments
Section 4

@@
-\section{Fundamental Algorithms and Auxiliary Definitions}\label{sec:auxdefs}
-In this section, we present the fundamental algorithms and auxiliary definitions used in our formalization.
-Some of them are auxiliary functions, others are however important ones as they
-directly implement our algorithm for method lookup.
-%\bruno{I felt like there's not enough explanation/context in this
- % section. It is just dumping definitions without connecting them and
- % their purpose properly.}
-
-\bruno{used for what and where?}\haoyuan{todo: used for where}
+\section{Method Lookup Algorithm and Auxiliary Definitions}\label{sec:auxdefs}
+In this section, we present the fundamental algorithms and auxiliary
+definitions used in our formalization, and show that the resulting
+calculus is type sound. The functions presented in this section are
+the key components that implement our algorithm for method lookup.
+\bruno{Yes, I agree with Marco: we can move 3.4 to the end of Section
+  4. Don't forget to revise earlier parts of Section 3 to remove
+  mentions of type-soundness there. Or better, in the summary of
+  Section 3 you can point out that type soundness is proved at the 
+end of Section 4.
+}
 
@@
 We use $I_d, I_s$, since $\mbody$ is usually invoked by a receiver of a method $m$, with its dynamic type $I_d$ and static type $I_s$.
-Such a function returns the most specific method implementation, more
-accurately, its parameters, returned expression (empty for abstract methods) and the types.
+Such a function returns the most specific method implementation.
+More
+accurately, $\mbody$ returns the parameters, returned expression
+(empty for abstract methods) and the types for the method.
 It considers both originally-defined methods and hierarchical overriding methods, so $\mostSpecific$ and $\mostSpecificOverride$ (see the definition in Section~\ref{sec:mostSpecific} and Section~\ref{sec:mostSpecificOverride}) are both invoked.
@@
 \subsection{Finding the Most Specifc Overriding: \mostSpecificOverride}\label{sec:mostSpecificOverride}
-The $\mostSpecific$ function only focuses on original method implementations, all the hierarchical overriding methods are omitted during that step.
-On the other hand, $\mostSpecificOverride(m, I, J)$ has the assumption that $J$ defines an original $m$, and this function tries to find the interfaces with most specific implementations that hierarchically overrides such an $m$.
-Formally,
+The $\mostSpecific$ function only focuses on original method
+implementations, all the hierarchical overriding methods are omitted
+during that step. On the other hand, $\mostSpecificOverride(m, I, J)$
+has the assumption that $J$ defines an original $m$, and this function
+tries to find the interfaces with the most specific implementations that hierarchically overrides such an $m$. Formally,
 

### 2017-10-15 NewVersion/sections/Discussion.tex
Discussion

@@
 For instance, in Java 8 when putting two identical abstract methods together by multiple inheritance, there is no conflict error. We omit
-that case for two reasons. First, our formalization just treats abstract methods as concrete methods with an empty body, and that simplifies
-the rules and the proof a lot.
-Second, our design choice tends to give more sense on those interesting cases, just as we reject the simple case of diamond inheritance.
-The triangle inheritance should distinguish and treat differently on the two methods instead of fusing them, since they represent different operations, even if they are abstract.
+that case for two reasons. Firstly, our formalization just treats abstract methods as concrete methods with an empty body, and that simplifies
+the rules and the proof a lot. Secondly, our design choice tends to give more sense on those interesting cases, just as we reject the simple case of diamond inheritance.
+\bruno{don't quite understand the last sentence.} In the presence of triangle inheritance we distinguish and treat differently on the two methods instead of fusing them, since they represent different operations, even if they are abstract.
 Thus our model adopts a very conservative behaviour rather than automatically merging
 methods, and implicitly assumming diamond inheritance. 
+It is possible to change our model to account for other behaviour for abstract methods, but we view this as a mostly 
+orthogonal change to our work, that should not affect the essence of the model presented here.
 
@@
 common orthogonal features including primitive types, assignments, method overloading, covariant method return types, static dispatch, and so on.
-Those features can be modularly added to the model without breaking type soundness \haoyuan{correct?}.
+Those features can, in principle, be modularly added to the model without breaking type soundness.
 For example, we present the additional syntax, typing and semantic rules of static invocation below as an extension:
@@
 A static invocation $e.J_0@J_1::m(\overline{e})$ aims at finding the method $m$ in $J_0$ that hierarchically overrides $J_1$, thus $J_0[m\ \kwoverride\ J_1]$ is invoked.
-As shown in \textsc{(S-StaticInvk)}, static dispatch needs a receiver to involve in the substitution for ``$\kwthis$'' reference, so as to provide the latest implementations.
+As shown in \textsc{(S-StaticInvk)}, static dispatch needs a receiver for the substitution of the ``$\kwthis$'' reference, so as to provide the latest implementations.
 In fact, static dispatch is common in OO programming, as it provides a shortcut to the reuse of old implementation easily, and super calls can also rely on this feature.
-For convenience we just make it simple above, whereas in languages like C++ or Java, the static or super invocations are more flexible hence complicated; they can climb the class hierarchy.
+For convenience we just make it simple above, whereas in languages like C++ or Java, the static or super invocations are more flexible, as they can climb the class hierarchy.
 
 One typical non-orthogonal extension to \MIM{} could be to have fields.
-The design of \MIM{} can be viewed as an extension to Java 8 with default methods which allows for unintentional method conflicts.
+The design of \MIM{} can be viewed as an variant of Java 8 with default methods which allows for unintentional method conflicts.
 Like Java interfaces and traits, state is forbidden in \MIM{} since having state in OO multiple inheritance is a non-trivial issue.
@@
 This can be realized by extending our current model with static methods and anonymous classes from Java.
-To directly support fields it requires more discussions and experiments, we leave them as our future work.
+However such an extension requires more though, so we leave it to future work.
 
-\subsection{Loosening the Model}
+\subsection{Loosening the Model: Reject Early or Reject Later?}
 
-For the goal of simplifying the model and type soundness proof, we have added a few constraints in the minimal calculus. Our language simply rejects the diamond inheritance, see the example below:
+Our language simply rejects the following case of diamond inheritance:
 
@@
 \end{lstlisting}\vspace{3pt}
-In the example, both $B.m$ and $C.m$ override $A.m$, so we think they should represent the same operation. In that case, we believe that D inherits
-both conflicting methods without an explicit override, and it is in fact an intention conflict.
-Our calculus rejects these intentional conflicts by rule \textsc{(T-Intf)}, where $D$ is considered to be ill-formed.
-Nonetheless, as a general-purpose language, C++ accepts the definition of $D$, but forbids a cast from $D$ to $A$ because of ambiguity.
-For the conciseness of the proof, our language is more conservative on interfaces, but open on up-casts.
-We could also loosen the model and perform ambiguity check on casts and other expressions.
-We need to handle more cases than C++, for instance, in the above program assume that $B.m$ and $C.m$ are hierarchical overrides on $A$, it is still a diamond.
+In the example, both $B.m$ and $C.m$ override $A.m$. In the example, D inherits
+both conflicting methods without an explicit override. In this case automatically merging 
+the two methods (to achieve diamond inheritance) is not possible, which is why many 
+models (like traits and Java 8) reject such programs. Moreover, keeping the two 
+method implementations in \lstinline|D| is problematic. 
+In essence, hierarchical information is 
+not helpful to disambiguate later method calls, since the two methods share 
+the same origin (\lstinline|A.m|). 
+Our calculus rejects such conflicts by the \textsc{(T-Intf)} rule, where $D$ is considered to be ill-formed. 
+We believe that rejecting \lstinline|D| follows the principle of models like traits and Java 8 interfaces, 
+where the language/type-system is meant to alert the programmer for a possible conflict.
 
+Nonetheless,
+ C++ accepts the definition of $D$, but forbids later upcasts from $D$ to $A$ because of ambiguity.
+Our language is more conservative on definitions of interfaces compared to C++, but on the upside up-casts are not rejected.
+We could also loosen the model to accept definitions such as \lstinline|D|, and perform ambiguity check on upcasts and other expressions.
+However, we would need to handle more cases than C++.
+For instance, in the above program assume that $B.m$ and $C.m$ are hierarchical overrides on $A$.
+Then such a case is still a diamond.
+
+\begin{comment}
 Another case is about the restriction on hierarchical overrides.
@@
 Yet from the idea of encapsulation and modularity on programs, we could also allow an override to work on another override, which forms a series of overrides.
+\end{comment}
 

### 2017-10-15 Calculus/src/framework/FHJ.scala
Finished impl.

@@ -16,9 +16,9 @@ object FHJ extends StandardTokenParsers with PackratParsers {
       if (t1 == t2) return true
       typeMap.get(t1).get.exists(x => subType(x, t2))
     }
-    def overrideSet(i: String, j: String): Set[String] = {
-      if (!table.contains(i) || !table.contains(j)) throw new Exception("Error: overrideSet.")
-      methodMap.get(i).get.filter(x => x.update == j).map(x => x.name).toSet
+    def dispatch(i: String, m: String, j: String): Option[MethDef] = {
+      if (!table.contains(i) || !table.contains(j)) throw new Exception("Error: dispatch.")
+      methodMap.get(i).get.find(x => x.name == m && x.update == j)
     }
     def prune(set: Set[String]): Set[String] = set.filter(i => !set.exists(j => j != i && subType(j, i)))
     def collectMethods(i: String): Set[String] = {
@@ -27,7 +27,7 @@ object FHJ extends StandardTokenParsers with PackratParsers {
       val op = (s: Set[String], x: String) => s ++ collectMethods(x)
       typeMap.get(i).get.foldLeft(start)(op)
     }
-    def mbody(m: String, id: String, is: String): Option[(String, List[(String, String)], (String, Expr))] = {
+    def mbody(m: String, id: String, is: String): Option[(String, List[(String, String)], (String, Option[Expr]))] = {
       if (!table.contains(id) || !table.contains(is)) throw new Exception("Error: mbody.")
       val set1 = mostSpecific(m, id, is)
       if (set1.size != 1) return None
@@ -45,15 +45,28 @@ object FHJ extends StandardTokenParsers with PackratParsers {
     }
     def mostSpecific(m: String, i: String, j: String): Set[String] = {
       if (!table.contains(i) || !table.contains(j)) throw new Exception("Error: mostSpecific.")
-      val set1 = table.filter(k => subType(k, j) && subType(i, k) && overrideSet(k, k).contains(m)).toSet
-      if (!set1.isEmpty) return prune(set1)
-      val set2 = table.filter(k => subType(j, k) && overrideSet(k, k).contains(m)).toSet
-      prune(set2)
+      val set = table.filter(k => subType(i, k) && (subType(k, j) || subType(j, k)) && dispatch(k, m, k).isDefined).toSet
+      prune(set)
     }
[…]

### 2017-10-16 NewVersion/sections/Auxiliary.tex
move s3.4 to end of s4

@@
-\section{Method Lookup Algorithm and Auxiliary Definitions}\label{sec:auxdefs}
+% \section{Method Lookup Algorithm and Auxiliary Definitions}\label{sec:auxdefs}
+\section{Key Algorithms and Type-Soundness}\label{sec:auxdefs}
+\yanlin{title changed, is this ok?}
 In this section, we present the fundamental algorithms and auxiliary
@@
 end of Section 4.
-}
+}\yanlin{Revised, please check.}
 
@@
 
-\subsection{Others}\label{sec:otherdefs}
+\subsection{Other Auxiliaries}\label{sec:otherdefs}
 Below we give other minor definitions of the auxiliary functions that are used in previous sections.
@@
 %%%%============================ canInstantiate end ================%%%%%%%%
+
+\subsection{Properties}
+
+We present the type soundness of the model by a few theorems below, following the standard technique of
+subject reduction and progress proposed by Wright and Felleisen~\cite{Wright1994}. The proof, together with some lemmas, are
+in Appendix. Type soundness states that if an expression is well-typed, then after many reduction
+steps it must reduce to a value, and its annotation is the same as the static type of the original expression.
+
+\begin{theorem}[Subject Reduction]~\label{theorem_subject}
+If $\judgeewf \Gamma {e : I}$ and $e \rightarrow e'$, 
+then $\judgeewf \Gamma {e' : I}$.
+\end{theorem}
+\begin{proof}
+See Appendix~\ref{appendix_proof}.
+\end{proof}
+
+\begin{theorem}[Progress]~\label{theorem_progress}
+Suppose $e$ is a well-typed expression, if $e$ includes 
+$\left((J)\emph{\kwnew}\;I()\right).m(\overline{v})$ as a sub-expression, then $\mbody(m, I, J) = (I_0, \overline{I_x} \; \overline{x}, I_e\; e_0)$ and $\num{\overline{x}} = \num{\overline{v}}$ for some $I_0$, $\overline{I_x}$, $\overline{x}$, $I_e$ and $e_0$.
+\end{theorem}
+\begin{proof}
+See Appendix~\ref{appendix_proof}.
+\end{proof}
+
+\begin{theorem}[Type Soundness]~\label{theorem_soundness}
+If $\judgeewf \o {e : I}$ and $e \to^* e'$ with $e'$ a normal form, then $e'$ is 
+a value $v$ with $\judgeewf \o {v:I}$.
+\end{theorem}
+\begin{proof}
+Immediate from Theorem~\ref{theorem_subject} and Theroem~\ref{theorem_progress}.
+\end{proof}
+Note that in Theorem~\ref{theorem_progress}, ``$\#(\overline{x})$'' denotes the length of
+$\overline{x}$.
+
+Our theorems are stricter than those of Featherweight Java~\cite{Igarashi01FJ}. Specifically, in both term substitution (a lemma in Appendix)
+and subject reduction, reduction may lead to a term with a subtype in
+FJ, but in \MIM{} types are unchanged. The difference is due to
+%%subtyping; the parameter or \lstinline|this| reference requires some type $I$, but a value with a more specific type,
+%%which is subtype of $I$, can be passed. However, as 
+the fact that \MIM{} keeps track of the static types during
+reduction. 
+In FJ, the information about the static types is lost.
+
+%the annotations in the
+%substitution actually ensures the type to be unchanged.

### 2017-10-16 NewVersion/sections/Formalization.tex
move s3.4 to end of s4

@@
 In this section, we present a formal model called \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), following similar style of 
-Featherweight Java~\cite{Igarashi01FJ}. \MIM{} is a minimal core calculus that formalizes the core concept of hierarchical dispatch and overriding. The syntax, typing rules,
-small-step semantics and theorems for type soundness are presented.
+Featherweight Java~\cite{Igarashi01FJ}. \MIM{} is a minimal core calculus that formalizes the core concept of hierarchical dispatch and overriding. The syntax, typing rules and small-step semantics.
 
@@
 \end{comment}
-
-\subsection{Properties}
-
-We present the type soundness of the model by a few theorems below, following the standard technique of
-subject reduction and progress proposed by Wright and Felleisen~\cite{Wright1994}. The proof, together with some lemmas, are
-in Appendix. Type soundness states that if an expression is well-typed, then after many reduction
-steps it must reduce to a value, and its annotation is the same as the static type of the original expression.
-
-\begin{theorem}[Subject Reduction]~\label{theorem_subject}
-If $\judgeewf \Gamma {e : I}$ and $e \rightarrow e'$, 
-then $\judgeewf \Gamma {e' : I}$.
-\end{theorem}
-\begin{proof}
-See Appendix~\ref{appendix_proof}.
-\end{proof}
-
-\begin{theorem}[Progress]~\label{theorem_progress}
-Suppose $e$ is a well-typed expression, if $e$ includes 
-$\left((J)\emph{\kwnew}\;I()\right).m(\overline{v})$ as a sub-expression, then $\mbody(m, I, J) = (I_0, \overline{I_x} \; \overline{x}, I_e\; e_0)$ and $\num{\overline{x}} = \num{\overline{v}}$ for some $I_0$, $\overline{I_x}$, $\overline{x}$, $I_e$ and $e_0$.
-\end{theorem}
-\begin{proof}
-See Appendix~\ref{appendix_proof}.
-\end{proof}
-
-\begin{theorem}[Type Soundness]~\label{theorem_soundness}
-If $\judgeewf \o {e : I}$ and $e \to^* e'$ with $e'$ a normal form, then $e'$ is 
-a value $v$ with $\judgeewf \o {v:I}$.
-\end{theorem}
-\begin{proof}
-Immediate from Theorem~\ref{theorem_subject} and Theroem~\ref{theorem_progress}.
-\end{proof}
-Note that in Theorem~\ref{theorem_progress}, ``$\#(\overline{x})$'' denotes the length of
-$\overline{x}$.
-
-Our theorems are stricter than those of Featherweight Java~\cite{Igarashi01FJ}. Specifically, in both term substitution (a lemma in Appendix)
-and subject reduction, reduction may lead to a term with a subtype in
-FJ, but in \MIM{} types are unchanged. The difference is due to
-%%subtyping; the parameter or \lstinline|this| reference requires some type $I$, but a value with a more specific type,
-%%which is subtype of $I$, can be passed. However, as 
-the fact that \MIM{} keeps track of the static types during
-reduction. 
-In FJ, the information about the static types is lost.
-
-%the annotations in the
-%substitution actually ensures the type to be unchanged.

### 2017-10-16 NewVersion/paper.tex
Added author info. Move appendix in front of refs (as required?)

@@
 
- \newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
- \newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
- \newcommand\marco[1]{\authornote{marco}{blue}{#1}}
- \newcommand\marcoT[1]{\authorText{blue}{#1}}
- \newcommand\haoyuan[1]{\authornote{haoyuan}{orange}{#1}}
+%\newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
+%\newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
+%\newcommand\marco[1]{\authornote{marco}{blue}{#1}}
+%\newcommand\marcoT[1]{\authorText{blue}{#1}}
+%\newcommand\haoyuan[1]{\authornote{haoyuan}{orange}{#1}}
 
-%\newcommand\bruno[1]{}
-%\newcommand\yanlin[1]{}
-%\newcommand\marco[1]{}
-%\newcommand\haoyuan[1]{}
+\newcommand\bruno[1]{}
+\newcommand\yanlin[1]{}
+\newcommand\marco[1]{}
+\newcommand\haoyuan[1]{}
 
@@
 % %          {marco.servetto@ecs.vuw.ac.nz}
-\author{Authors Omitted}
-
-\institute{}
+\author{Yanlin Wang\inst{1} \and Haoyuan Zhang\inst{1} \and Bruno C.d.S. Oliveira\inst{1} \and Marco Servetto\inst{2}}
+\institute{The University of Hong Kong \and Victoria University of Wellington \\ \email{ylwang@cs.hku.hk, hyzhang@cs.hku.hk, bruno@cs.hku.hk, marco.servetto@ecs.vuw.ac.nz}}
 
@@
 can coexist in the same class, and \emph{hierarchical dispatching}
-supports unambigous lookups in the presence of such conflicting
+supports unambiguous lookups in the presence of such conflicting
 methods.  To avoid ambiguity, hierarchical information is employed in
@@
 % \bibliographystyle{abbrvnat}
-\bibliographystyle{splncs03}
-\bibliography{paper}
 
@@
 
+\newpage
+
+\bibliographystyle{splncs03}
+\bibliography{paper}
+
 \end{document}

### 2017-10-16 NewVersion/sections/Conclusion.tex
Added author info. Move appendix in front of refs (as required?)

@@
 unintentional method conflicts. Previous approaches 
-either do not support unintentional method conflicts, have to
+either do not support unintentional method conflicts, thus have to
 compromise between code reuse and type safety, or do not fully support
@@
 information and path information from either upcasts or parameters'
-information. Such an approach not only offers great code reuse like
+information. It not only offers great code reuse like
 dynamic dispatch but also ensures unambiguity by our algorithm for
@@
   overriding} to allow conflicting methods in different branches to be
-individually overriden.
+individually overridden.
 
 \MIM{} is formalized following the style of
-Featherweight Java and type-soundness is proved. A prototype language is
-implemented in Scala as a simple interpreter. We believe that the formalization of
+Featherweight Java and proved to be sound. A prototype interpreter is
+implemented in Scala. We believe that the formalization of
 hierarchical dispatching features is general and
-can be safely embedded to other OO models, so as to have support for the triangle
+can be safely embedded in other OO models, so as to have support for the triangle
 inheritance.
 
-Our model can certainly be improved at some aspects. 
+Our model can certainly be improved in some aspects. 
 As discussed in Section~\ref{sec:discussion}, there are orthogonal and
@@
 The future work relates to loosening the model without giving up its soundness,
-together with more exploration on fields in the multiple inheritance setting.
+together with more exploration on supporting fields in the multiple inheritance setting.

### 2017-10-16 NewVersion/sections/Discussion.tex
Added author info. Move appendix in front of refs (as required?)

@@
 to include only method declarations, and those abstract methods can be implemented in a class body. 
-The formal Featherweight Java model~\cite{Igarashi01FJ} does not include abstract methods because of its orthogonality
+The formal Featherweight Java model~\cite{Igarashi01FJ} does not include abstract methods because of the orthogonality
 to the core calculus. In traits the
@@
 Our formalization has a simple form of abstract methods, which behave similarly to conventional methods with respect to conflicts.
-Other languages support more complicated behaviour.
+Other languages may support more complicated behaviours.
 For instance, in Java 8 when putting two identical abstract methods together by multiple inheritance, there is no conflict error. We omit
@@
 Thus our model adopts a very conservative behaviour rather than automatically merging
-methods, and implicitly assumming diamond inheritance. 
-It is possible to change our model to account for other behaviour for abstract methods, but we view this as a mostly 
+methods, and implicitly assuming diamond inheritance. 
+It is possible to change our model to account for other behaviours for abstract methods, but we view this as a mostly 
 orthogonal change to our work, that should not affect the essence of the model presented here.
@@
 One typical non-orthogonal extension to \MIM{} could be to have fields.
-The design of \MIM{} can be viewed as an variant of Java 8 with default methods which allows for unintentional method conflicts.
+The design of \MIM{} can be viewed as a variant of Java 8 with default methods which allows for unintentional method conflicts.
 Like Java interfaces and traits, state is forbidden in \MIM{} since having state in OO multiple inheritance is a non-trivial issue.
@@
 This can be realized by extending our current model with static methods and anonymous classes from Java.
-However such an extension requires more though, so we leave it to future work.
+However such an extension requires more thoughts, so we leave it to future work.
 
@@
 \end{lstlisting}\vspace{3pt}
-In the example, both $B.m$ and $C.m$ override $A.m$. In the example, D inherits
+Here both $B.m$ and $C.m$ override $A.m$, and D inherits
 both conflicting methods without an explicit override. In this case automatically merging 

### 2017-10-16 NewVersion/sections/Introduction.tex
typos
Added author info. Move appendix in front of refs (as required?)

@@
+\begin{comment}
 \yanlin{
@@
 }
+\end{comment}
 
@@
 In contrast to diamond inheritance, a second case of ambiguity
-is \textit{unintentional method conflicts}~\cite{scharli03traits}. That is conflicting 
-methods that do not actually refer to the same feature. 
+is \textit{unintentional method conflicts}~\cite{scharli03traits}. It is that the conflicting 
+methods do not actually refer to the same feature. 
 In a nominal system, methods can be designed for different
@@
 neither the C\# or C++ approaches allow
-such conflicting methods to be further overriden. 
+such conflicting methods to be further overridden. 
 % However, C++ has
@@
 drawable widgets (\lstinline|Drawable|). 
-A class \lstinline|SafeDeck| adds functionality to check whether a 
-the deck is empty and to prevent drawing a card from an empty deck. 
+The class \lstinline|SafeDeck| adds functionality to check whether the
+deck is empty and to prevent drawing a card from an empty deck. 
 The interesting class is \lstinline|DrawableSafeDeck|, which inherits 
-from both \lstinline|SafeDeck| and \lstinline|Drawable|. Hierchical
+from both \lstinline|SafeDeck| and \lstinline|Drawable|. Hierarchical
 overriding is used in \lstinline|DrawableSafeDeck| to keep two separate \lstinline|draw|
@@
 method coming from \lstinline|Drawable|, in order to draw a widget
-with a deck of cards. Note that hierchical overriding is denoted in the UML
+with a deck of cards. Note that hierarchical overriding is denoted in the UML
 diagram with the notation
-\lstinline|draw()|$\shneg$\lstinline|Drawable|. In this case the
-notation expresses that the \lstinline|draw| method from \lstinline|Drawable|
-is overriden. Although in this example only one of the
-\lstinline|draw| methods is overriden (and the other is simply inherited), hierarchical overriding
-supports multiple conflicting methods to be independently overriden as well.
+\lstinline|draw()|$\shneg$\lstinline|Drawable|. It expresses that the \lstinline|draw| method from \lstinline|Drawable|
+is overridden. Although in this example only one of the
+\lstinline|draw| methods is overridden (and the other is simply inherited), hierarchical overriding
+supports multiple conflicting methods to be independently overridden as well.
 
@@
 proofs for type soundness. 
-
-%%Our model can be viewed as
-%%a generalization of the simplified trait model by providing additional support to
-%%the triangle inheritance.
-
 In summary, our contributions are:
@@
               supplementary material attached to the submission.}:} a
-          simple implementation of \MIM{} implemented in Scala.
-          \bruno{Are the examples in the paper implemented in the interpreter?}
-          \yanlin{new formalization has not been implemented yet.}
+          simple implementation of \MIM{} interpreter in Scala.
 \end{itemize}

### 2017-10-16 NewVersion/sections/Overview.tex
Added author info. Move appendix in front of refs (as required?)

@@
 library function. 
-The method returns \lstinline|void|. Note that, similarly to
+The two \lstinline|draw| methods can have different return types, but for simplicity
+they both return \lstinline|void| here. Note that, similarly to
 Featherweight Java~\cite{Igarashi01FJ}, \lstinline|void| is
 unsupported in our formalization. We could have also defined an interface called \lstinline|Void|
-and return an object of that type instead, but for simplicity of
-presentation we use \lstinline|void|. For the method \lstinline|draw| in
-\lstinline|Drawable|
-the program create a blank canvas by \lstinline|JFrame| and set the visibility to \lstinline|true|.
+and return an object of that type instead. To be concise, we use \lstinline|void| in this code.
+For \lstinline|Drawable| the \lstinline|draw|
+creates a blank canvas by \lstinline|JFrame| and set the visibility to \lstinline|true|.
 
@@
 Now, supppose that a programmer is designing a
-card game with a GUI. He may want to draw a deck on the screen, so he defines a drawable
+card game with a GUI. He may want to draw a deck on the screen, so he first defines a drawable
 deck using multiple inheritance:
@@
 \vspace{3pt}\begin{lstlisting}
-interface DrawableDeck extends Drawable, Deck {...} 
+interface DrawableDeck extends Drawable, Deck {} 
 \end{lstlisting}\vspace{3pt}
@@
 
-This case is the so-called \textit{unintentional method conflicts}. It arises when two inherited methods happen to have
+This case is the so-called \textit{unintentional method conflict}. It arises when two inherited methods happen to have
 the same name and parameter types, but they are designed for different functionalities with different semantics.
@@
   \centering
-  \begin{minipage}[t]{0.28\textwidth}
+  \begin{minipage}[t]{0.32\textwidth}
   \includegraphics[height=4cm]{pics/DrawableSafeDeck1.pdf}
@@
   \hspace*{2pt}
-  \begin{minipage}[t]{0.4\textwidth}
+  \begin{minipage}[t]{0.38\textwidth}
   \includegraphics[height=4cm]{pics/DrawableSafeDeck0.pdf}
@@
 invoked. To solve this problem \MIM{} uses a variant of method
-disptaching that we call \textit{hierarchical dispatch}. In
+dispatching that we call \textit{hierarchical dispatch}. In
 hierarchical dispatch both the static and dynamic type information 
-ared used to select the right method implementation.
+are used to select the right method implementation.
 %Inspired by C++, we have formalized this feature into a minimal core calculus,
@@
 %Unfortunately, the C++ language, or rather the feature on triangle inheritance, has not been well formalized.
-
-\paragraph{Implicit and Explicit Upcasts}
-\yanlin{todo: Haoyuan.}
-\haoyuan{To move to S5.}
 In our language model, there are two types of casts: \emph{implicit casts} and \emph{explicit upcasts}. The implicit casts appear
 when passing arguments and returning expressions, they are also
-upcasts. Hence all casts are safe. C++ implementations also support a
+upcasts. Hence all casts are safe.
+
+\begin{comment}
+C++ implementations also support a
 similar solution. However a notable difference between \MIM{} and C++
@@
   extended discussion later?}
+\end{comment}
 
@@
 With unintentional method conflicts, however, the situation is more
-complicated because different, separate, conflicting methods can exist
-in a class. Ideally we would like to support overriding for those
+complicated because different, separate, conflicting methods can coexist
+in one class. Ideally we would like to support overriding for those
 methods too, in exactly the same way that overriding is available for 
@@
 
-\paragraph{Potential solutions/workarounds in existing languages:} Unfortunately in all languages we known
+\paragraph{Potential solutions/workarounds in existing languages:} Unfortunately in all languages we have known
 (including C++), the existing approaches are unsatisfactory.
 One direction is to simply avoid this issue, by putting overriding before inheritance.
-For example, as shown in Figure~\ref{fig:drawablesafedeck}(right), we define a new component \lstinline|DrawableRect| that extends \lstinline|Drawable|, which simply draws the deck as a rectangle, and modifies the hierarchy:
+For example, as shown in Figure~\ref{fig:drawablesafedeck}(middle), we define a new component \lstinline|DrawableRect| that extends \lstinline|Drawable|, which simply draws the deck as a rectangle, and modifies the hierarchy:
 \vspace{3pt}\begin{lstlisting}
@@
 
+The UML graph is shown in Figure~\ref{fig:drawablesafedeck}(right), where
+the up-arrow $\uparrow$ is short for ``\lstinline|override|''.
 Here the idea is that \emph{only} \lstinline{Drawable.draw} is
-overriden. This is accomplished by specifying, in the method
-definition, that only the method override only overrides the method 
+overridden. This is accomplished by specifying, in the method
+definition, that the method only overrides the \lstinline|draw| 
 from \lstinline|Drawable|.  
@@
 Before the formalized algorithm, Figure~\ref{fig:examplesmbody} gives a peek at the behavior by
-some quick examples. The UML diagrams present the hierarchy. In (c) and (e), an up-arrow $\uparrow$ is short for ``\lstinline|override|''.
+some quick examples. The UML diagrams present the hierarchy. 
 In (d) and (e), a cross mark indicates that the interface fails to type-check. Generally, \MIM{} rejects on the definition of an interface

### 2017-10-16 NewVersion/sections/RelatedWork.tex
Added author info. Move appendix in front of refs (as required?)

@@
 the original trait model exists with various advanced features, such as \emph{renaming}. As discussed in Section~\ref{sec:overview},
-the renaming feature helps to solve the unintentional method conflicts
+the renaming feature gives a workaround to the unintentional method conflicts
 problem. However, it breaks structural subtyping.
@@
 two methods with the same signature from two different units to
-coexist. In contrast, our work provides mechanisms that allows 
+coexist. In contrast, our work provides mechanisms that allow 
 methods with the same signatures, but different parents to coexist 
@@
 A few language implementations have realized the problem of
-unintentional conflicts and provide some support for it.
+unintentional conflicts and provided some support for it.
 
@@
 Class \texttt{MiddleMan}, as its name suggests, acts as a middle man between its class \texttt{C} and its parents \texttt{A, B}.
-\texttt{MiddleMan} defines a virtual method \texttt{m} that overrides a parent method \texttt{m} and delegate the implementation to another method \texttt{m\_impl} that takes \kwthis as parameter.
-C++ supports method overloading, so that multiple \texttt{m\_impl} methods with different parameter types can co-exist.
-When definning class \texttt{C}, we specify the parents to be \texttt{MiddleMan<A>, MiddleMan<B>} instead of \texttt{A, B}.
-This way, programmers may define new versions of \texttt{A.m} and \texttt{B.m} in class \texttt{C} by providing the corresponding \texttt{m\_impl} methods.
+\texttt{MiddleMan} defines a virtual method \texttt{m} that overrides a parent method \texttt{m} and delegates the implementation to another method \texttt{m\_impl} that takes $\kwthis$ as parameter.
+C++ supports method overloading, so that multiple \texttt{m\_impl} methods with different parameter types can coexist.
+When defining class \texttt{C}, we specify the parents to be \texttt{MiddleMan<A>, MiddleMan<B>} instead of \texttt{A, B}.
+In this way, programmers may define new versions of \texttt{A.m} and \texttt{B.m} in class \texttt{C} by providing the corresponding \texttt{m\_impl} methods.
 Then in the client code, the method call \texttt{((A*)c)->m()} will print out string \texttt{"MA2"}, as expected.
 Although this workaround can help us defining partial method overrides to a certain extent, the drawbacks are obvious.
-Firsly, the approach is complex and requires the pre-knowledge of the programmer to this approach.
-Moreover, no direct syntax support makes the "MiddleMan" code cumbersome to write.
-Finally, the approach is ad-hoc, meaning that the class \texttt{MiddleMan} shown in Figure~\ref{fig:middleman} is not general enough to be used in other cases: more middle-mans are needed if partial method overrides happens in other classes.
+Firstly, the approach is complex and requires the pre-knowledge of the programmer to this approach.
+Moreover, the lack of direct syntax support makes MiddleMan code cumbersome to write.
+Finally, the approach is ad-hoc, meaning that the class \texttt{MiddleMan} shown in Figure~\ref{fig:middleman} is not general enough to be used in other cases: more middle-mans are needed if partial method overrides happens in other classes; and it is even worse when return types differ.
 
@@
 only be accessed through an instance of the interface. Explicit
-interface implementations allows an interface to inherit multiple 
+interface implementations allow an interface to inherit multiple 
 interfaces that share the same member names and give each interface
@@
 (1) default method implementations are not allowed in \csharp{} interfaces; 
-(2) there is only one level conflicting method implementations at the
+(2) there is only one level of conflicting method implementations at the
 class that implements the multiple parent interfaces. Further
@@
 Featherweight Scala~\cite{Cremet2006}, and so on.
-FJ provides the standard model of formalizing a Java-like object-oriented languages and 
+FJ provides the standard model of formalizing Java-like object-oriented languages and 
 is easily extensible.

### 2017-10-17 NewVersion/sections/Auxiliary.tex
S3,S4 typos, grammar

@@
 \subsection{Finding the Most Specific Origin: \mostSpecific}\label{sec:mostSpecific}
-We proceed to give the definition of two core functions that support method lookup, namely \mostSpecific{} and \mostSpecificOverride. Generally,
+We proceed to give the definitions of two core functions that support method lookup, namely \mostSpecific{} and \mostSpecificOverride. Generally,
 $\mostSpecific(m, I, J)$ finds the set of most specific interfaces where $m$ is originally defined, they should be above $I$ and

### 2017-10-17 NewVersion/sections/Formalization.tex
S3,S4 typos, grammar

@@
 In this section, we present a formal model called \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), following similar style of 
-Featherweight Java~\cite{Igarashi01FJ}. \MIM{} is a minimal core calculus that formalizes the core concept of hierarchical dispatch and overriding. The syntax, typing rules and small-step semantics.
+Featherweight Java~\cite{Igarashi01FJ}.
+\MIM{} is a minimal core calculus that formalizes the core concept of hierarchical dispatching and overriding.
+The syntax, typing rules and small-step semantics are presented.
 
@@
 The abstract syntax of \MIM{} interface declarations, method declarations, and expressions is given at Figure~\ref{fig:syntax}. The multiple
-inheritance feature of \MIM{} is inspired by Java 8 interfaces, which support
+inheritance feature of \MIM{} is inspired by Java 8 interfaces, which supports
 method implementations via default methods. This feature is 
 closely related to \emph{traits}. To demonstrate how
-unintentional method conflicts are untangled in \MIM{}, we only focus on a small subset of the interface model. For example, all the methods declared
+unintentional method conflicts are untangled in \MIM{}, we only focus on a small subset of the interface model. For example, all methods declared
 in an interface are either default methods or abstract methods. Default methods provide default implementations for methods. Abstract methods do not
@@
 interface, then such a method is seen as originally defined; otherwise it is an overriding method. The definition
-of abstract methods is done with $\absmethod{I}{m}{I_x}{x}{J}$, which is
+of abstract methods is written as $\absmethod{I}{m}{I_x}{x}{J}$, which is
 similar to a concrete method but without the method body. 
@@
 Expressions can be standard constructs such as variables, method
-invocation, or object creation, together with cast expressions. 
+invocation, object creation, together with cast expressions. 
 Object creation is represented by $\new I$. Fields and primitive types are not modelled in \MIM{}. 
@@
 
-For simplicity, \name{} does not formalize statements like assignments and so on because they are orthogonal features.
-A program consists of a list of interface declarations, plus a single expression.
+For simplicity, \name{} does not formalize statements like assignments and so on because they are orthogonal features to the hierarchical dispatching and overriding feature.
+A program in \name{} consists of a list of interface declarations, plus a single expression.
 
@@
 Naturally, the receiver and the arguments are required to be well-typed.
-$\mbody$ is our key function for method lookup, based on the
+$\mbody$ is our key function for method lookup that implements the
 hierarchical dispatching algorithm. 
-The hierarchical invocation $\mbody(m, I, J)$ means ``finding most specific $m$
+The hierarchical invocation $\mbody(m, I, J)$ means ``finding most specific method $m$
 above $I$ and along path $J$'', and usually $I$ denotes the dynamic type while $J$
@@
 \textsc{(T-New)} is the typing rule for object creation $\new{I}$. The
-auxiliary function $\canInstantiate(I)$ checks whether interface $I$
-can be instantiated or not, and is formalized in Section~\ref{sec:auxdefs}.
-Since triangle inheritance accepts conflicting branches to coexist, the check requires that the most specific method is concrete for each method on each branch.
+auxiliary function $\canInstantiate(I)$ (see definition in Section~\ref{sec:otherdefs}) checks whether an interface $I$ 
+can be instantiated or not. Since triangle inheritance accepts conflicting branches to coexist, the check requires that the most specific method is concrete for each method on each branch.
 
@@
 it implies that the inherited super types are excluded.
-Thus the condition $\mostSpecific(m, I, J) = \{J\}$ indicates a characteristic of a hierarchical overriding: it must override an original method; the overriding is direct and there does not exist any other original $m$ in between.
+Thus the condition $\mostSpecific(m, I, J) = \{J\}$ indicates a characteristic of a hierarchical overriding: it must override an original method; the overriding is direct and there does not exist any other original method $m$ in between.
 Then $\mbody(m, J, J)$ provides the type of the original method, so hierarchical overriding has to preserve the type. Finally the return expression
@@
 condition checks whether the overriding between original methods preserves typing.
-In the condition we again use some helper functions from Section~\ref{sec:auxdefs}.
+In this condition we again use some helper functions defined in  Section~\ref{sec:auxdefs}.
 $I[m\ \kwoverride\ I]$ is defined if $I$ originally defines $m$, and $\canOverride(m, I, J)$ checks whether $I.m$ has the same type as $J.m$.
@@
 The second condition of \textsc{(T-Intf)} is more complex, and is the key to type soundness. Unlike C++ which rejects on ambiguous calls,
-\MIM{} rejects on the definition of interfaces when they reach a diamond. Consider the case when the second condition is broken: $\mbody(m, J, J)$
+\MIM{} rejects on the definition of interfaces when they form a diamond. Consider the case when the second condition is broken: $\mbody(m, J, J)$
 is defined but $\mbody(m, I, J)$ is undefined for some $J$ and $m$. This indicates that $m$ is available and unambiguous from the perspective of $J$,
-but is ambiguous to $I$ on branch $J$. That means that there are multiple overriding paths of $m$ from $J$ to $I$, which form a diamond. Hence rejecting
+but is ambiguous to $I$ on branch $J$. It means that there are multiple overriding paths of $m$ from $J$ to $I$, which forms a diamond. Hence rejecting
 that case meets our expectation. Below is an example (Figure~\ref{fig:examplesmbody} (e)) that illustrates the reason why this condition is needed:
@@
 Specifically, the receiver $(J)\new{I}$ indicates the dynamic type $I$
-together with the static type $J$. Therefore $\mbody(m, I, J)$ carries out hierarchical dispatch, acquires
+together with the static type $J$. Therefore $\mbody(m, I, J)$ carries out hierarchical dispatching, acquires
 the types, the return expression $e_0$ and the interface $I_0$ which provides the most specific method.

### 2017-10-17 NewVersion/sections/Formalization.tex
typos, grammar, S1 to S4

@@
 \section{Formalization}~\label{sec:formalization}
-In this section, we present a formal model called \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), following similar style of 
+In this section, we present a formal model called \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), following the similar style of 
 Featherweight Java~\cite{Igarashi01FJ}.
@@
 \subsection{Syntax}
-The abstract syntax of \MIM{} interface declarations, method declarations, and expressions is given at Figure~\ref{fig:syntax}. The multiple
+The abstract syntax of \MIM{} interface declarations, method declarations, and expressions is given in Figure~\ref{fig:syntax}. The multiple
 inheritance feature of \MIM{} is inspired by Java 8 interfaces, which supports
@@
 M_n$ (with no commas).
-We also abbreviate operations on pairs of sequences in the obvious way, writing $\overline{I} \; \overline{x}$ for $I_1 \; x_1, ..., I_n \; x_n$, where $n$ is the length of $\overline{I}$ and $\overline{x}$.
+We also abbreviate operations on pairs of sequences in an obvious way, writing $\overline{I} \; \overline{x}$ for $I_1 \; x_1, ..., I_n \; x_n$, where $n$ is the length of $\overline{I}$ and $\overline{x}$.
 
@@
 
-The second condition of \textsc{(T-Intf)} is more complex, and is the key to type soundness. Unlike C++ which rejects on ambiguous calls,
+The second condition of \textsc{(T-Intf)} is more complex and is the key to type soundness. Unlike C++ which rejects on ambiguous calls,
 \MIM{} rejects on the definition of interfaces when they form a diamond. Consider the case when the second condition is broken: $\mbody(m, J, J)$
@@
 \paragraph{Congruence Rules} \textsc{(C-Receiver)}, \textsc{(C-Args)} and \textsc{(C-FReduce)} are natural congruence rules
-on receivers, arguments and cast-expressions, respectively. \textsc{(C-StaticType)} automatically adds an annotation $I$ to the new
+on receivers, arguments, and cast-expressions, respectively. \textsc{(C-StaticType)} automatically adds an annotation $I$ to the new
 object $\new{I}$. \textsc{(C-AnnoReduce)} merges nested upcasts into a single upcast with the outermost type.

### 2017-10-17 NewVersion/sections/Introduction.tex
typos, grammar, S1 to S4

@@
 
-In contrast to diamond inheritance, a second case of ambiguity
+In contrast to diamond inheritance, the second case of ambiguity
 is \textit{unintentional method conflicts}~\cite{scharli03traits}. It is that the conflicting 
@@
 resolves the ambiguity by specifying the expected path by
-\emph{upcasts}. However
-neither the C\# or C++ approaches allow
+\emph{upcasts}. However, neither the C\# or C++ approaches allow
 such conflicting methods to be further overridden. 
@@
 same names and signatures. An example is presented in 
-Figure~\ref{fig:main}. In this example there are 4 classes/interfaces.
+Figure~\ref{fig:main}. In this example, there are 4 classes/interfaces.
 Two classes model a deck of cards (\lstinline|Deck|) and a class for
@@
           Featherweight Java, supporting the above features. 
-          We provide the static and dynamic semantics, and prove the
+          We provide the static and dynamic semantics and prove the
           type soundness of the model.

### 2017-10-17 NewVersion/sections/Overview.tex
typos, grammar, S1 to S4

@@
 a simple running example. In the following text we will introduce three
-problems one by one, and have a discussion on possible workarounds and
+problems one by one and have a discussion on possible workarounds and
 our solutions.
@@
 library function. 
-The two \lstinline|draw| methods can have different return types, but for simplicity
+The two \lstinline|draw| methods can have different return types, but for simplicity, 
 they both return \lstinline|void| here. Note that, similarly to
@@
 
-Now, supppose that a programmer is designing a
+Now, suppose that a programmer is designing a
 card game with a GUI. He may want to draw a deck on the screen, so he first defines a drawable
@@
   methods. However this approach is non-modular, as it requires 
-  modifying existing code, and may not be possible if code is unavailable.
+  modifying existing code, and may not be possible if the code is unavailable.
   \item \textit{III. Method exclusion/renaming in traits.} Some trait models
@@
 during inheritance instead of merging them into a single
-method. Therefore \MIM{} accepts the definition of \lstinline|DrawableDeck|. To disambiguite method calls
+method. Therefore \MIM{} accepts the definition of \lstinline|DrawableDeck|. To disambiguate method calls, 
 we can use \emph{up-casts} in \MIM{}, so as to specify the ``branch'' in the
@@
 to call the \lstinline|draw| method from \lstinline|Drawable|.
-Without the cast the call would be ambiguous, and
+Without the cast, the call would be ambiguous and
 \MIM{}'s type system would reject that call.
@@
 the same semantics, method overriding is not a problem. If conflicting
-methods arize from multiple parents, we can override all those methods 
+methods arise from multiple parents, we can override all those methods 
 in a single unified (or merged) method in the subclass. Therefore
 further overriding is simple, because there is only one method that
-can be overriden.
+can be overridden.
 
@@
 conflicting methods into a single merged one. We illustrate the
-problem and the need for a more refined overrding mechanism with 
+problem and the need for a more refined overriding mechanism with 
 an example.

### 2017-10-17 NewVersion/sections/Auxiliary.tex

@@
 
-\subsection{Finding the Most Specifc Overriding: \mostSpecificOverride}\label{sec:mostSpecificOverride}
+\subsection{Finding the Most Specific Overriding: \mostSpecificOverride}\label{sec:mostSpecificOverride}
 The $\mostSpecific$ function only focuses on original method
@@
 \begin{proof}
-Immediate from Theorem~\ref{theorem_subject} and Theroem~\ref{theorem_progress}.
+Immediate from Theorem~\ref{theorem_subject} and Theorem~\ref{theorem_progress}.
 \end{proof}

### 2017-10-17 NewVersion/sections/Discussion.tex

@@
 In this section, we will discuss the design space and reflect about some of the design decisions of our work. We relate 
-our language to traits, Java interfaces as well as other languages. Furthermore we discuss
+our language to traits, Java interfaces as well as other languages. Furthermore, we discuss
 ways to improve our  work.\bruno{references please!!!} \haoyuan{Done}
@@
  C++ accepts the definition of $D$, but forbids later upcasts from $D$ to $A$ because of ambiguity.
-Our language is more conservative on definitions of interfaces compared to C++, but on the upside up-casts are not rejected.
+Our language is more conservative on definitions of interfaces compared to C++, but on the upside, up-casts are not rejected.
 We could also loosen the model to accept definitions such as \lstinline|D|, and perform ambiguity check on upcasts and other expressions.

### 2017-10-17 NewVersion/sections/Overview.tex
small fixes
local

@@
 become more complicated with dynamic dispatching. Dynamic
-dispatching is very common in OO programming in order for code reuse. Let us expand the previous
+dispatching is very common in OO programming for code reuse. Let us expand the previous
 example a bit, by redefining those interfaces with more features:
@@
 ``finding the most specific \lstinline|draw| along the path \lstinline|Deck|''. The meaning of ``along path
-\lstinline|Deck|'' not only implies what \lstinline|Deck| inherits, but also the domain of its subtypes until the
-dynamic type. Finally \lstinline|SafeDeck.draw| is correctly returned.
+\lstinline|Deck|'' not only implies what \lstinline|Deck| inherits, but also the domain of its subtypes up to the
+dynamic type \lstinline|DrawableSafeDeck|. Finally \lstinline|SafeDeck.draw| is correctly returned.
 

### 2017-10-17 NewVersion/sections/Introduction.tex
Abstract intro overview

@@
 In contrast to diamond inheritance, the second case of ambiguity
-is \textit{unintentional method conflicts}~\cite{scharli03traits}. It is that the conflicting 
+is \textit{unintentional method conflicts}~\cite{scharli03traits}. In
+such a case conflicting 
 methods do not actually refer to the same feature. 
@@
 
-\begin{figure}
+\begin{figure}[t]
 \center  \includegraphics[height=4cm]{pics/DrawableSafeDeck3.pdf}
@@
 diagram with the notation
-\lstinline|draw()|$\shneg$\lstinline|Drawable|. It expresses that the \lstinline|draw| method from \lstinline|Drawable|
+\lstinline|draw()|$\shneg$\lstinline|Drawable|, expressing that the \lstinline|draw| method from \lstinline|Drawable|
 is overridden. Although in this example only one of the
@@
 \begin{itemize}
-	\item \textbf{Formalization of a hierarchical dispatching algorithm} that integrates both the static type and dynamic type for method dispatch, and hence
+	\item \textbf{A formalization of a hierarchical dispatching algorithm} that integrates both the static type and dynamic type for method dispatch, and 
 	ensures unambiguity as well as extensibility in the presence
@@
           type soundness of the model.
-	\item \textbf{Prototype implementation\footnote{Available in
-              supplementary material attached to the submission.}:} a
+	\item \textbf{Prototype implementation\footnote{\bruno{URL
+                here} URL}:} a
           simple implementation of \MIM{} interpreter in Scala.

### 2017-10-17 NewVersion/sections/Overview.tex
Abstract intro overview

@@
 Problems 1 and 2 are related to hierarchical dispatching, and in 
-C++ it is possible to have similar solutions as ours to both
+C++ it is possible to have similar solutions to both
 problems. Hence it is important to emphasize that, with respect to
@@
 of this feature together with a proof of type soundness. However, for the final problem, there is no satisfactory approach
-in existing languages, thus we propose a new feature (hierarchical
+in existing languages, thus what we propose is a new feature (hierarchical
 overriding) with the corresponding formalization of that feature.
@@
 unsupported in our formalization. We could have also defined an interface called \lstinline|Void|
-and return an object of that type instead. To be concise, we use \lstinline|void| in this code.
-For \lstinline|Drawable| the \lstinline|draw|
-creates a blank canvas by \lstinline|JFrame| and set the visibility to \lstinline|true|.
+and return an object of that type instead. To be concise, however, we
+use \lstinline|void| in our examples.
+For \lstinline|Drawable| the \lstinline|draw| method
+creates a blank canvas.
 
@@
 components and to achieve code reuse, as supported by many mainstream OO
-languages. Nevertheless at this point, languages like Java simply treat the two \lstinline|draw| methods
+languages. Nevertheless, at this point, languages like Java simply treat the two \lstinline|draw| methods
 as the same, and hence the compiler throws an error
@@
 during inheritance instead of merging them into a single
-method. Therefore \MIM{} accepts the definition of \lstinline|DrawableDeck|. To disambiguate method calls, 
-we can use \emph{up-casts} in \MIM{}, so as to specify the ``branch'' in the
+method. Therefore \MIM{} accepts the definition of
+\lstinline|DrawableDeck|\bruno{Marco complained about this sentence,
+  which is in the todo list. I've then complained that we should have
+  the todos at the places where TODOs were meant. Now, the sentence
+  remains unchanged. PLEASE go over the TODO list, and check whether
+  you've fixed the issue or not, if not move the TODO to the correct
+  location! }. To disambiguate method calls, 
+we can use \emph{up-casts} in \MIM{} to specify the ``branch'' in the
 inheritance hierarchy that should be called. The following code
@@
 Yet dynamic dispatching immediately saves us from the duplication work,
-since the method becomes automatically dispatched to the most specific one. Nevertheless, as seen before, dynamic dispatch would potentially introduce ambiguity,
-for instance, when we have the class hierarchy structure shown in Figure~\ref{fig:drawablesafedeck}(left) and the following code:
+since the method becomes automatically dispatched to the most specific one. Nevertheless, as seen before, dynamic dispatch would potentially introduce ambiguity.
+For instance, when we have the class hierarchy structure shown in Figure~\ref{fig:drawablesafedeck}(left) and the following code:
 
@@
   \end{minipage}  
-  \caption{UML graphs for \lstinline|DrawableSafeDeck|.}\label{fig:drawablesafedeck}
+  \caption{UML diagrams for 3 variants of \lstinline|DrawableSafeDeck|.}\label{fig:drawablesafedeck}
 \end{figure*}
@@
 \end{lstlisting}\vspace{3pt}
+\bruno{Marco complined about this but this was not addressed either!!!}
 During the runtime, when \lstinline|this.draw()| in called,
@@
 when passing arguments and returning expressions, they are also
-upcasts. Hence all casts are safe.
+upcasts. Hence all casts are safe. \bruno{This discussion seems
+  inconplete. Either complete it or remove it.}
 
@@
 The individual overriding allows us to make use of the methods from \lstinline|SafeDeck| as well. In the formalization, the 
-hierarchical overriding feature is also an important feature that involves in the algorithm of hierarchical dispatch.
+hierarchical overriding feature is also an important feature, involved in the algorithm of hierarchical dispatch.
 %\bruno{the last two sentences are a bit unclear. I think it is related to ``interaction''.}
@@
 
-Before the formalized algorithm, Figure~\ref{fig:examplesmbody} gives a peek at the behavior by
-some quick examples. The UML diagrams present the hierarchy. 
+Before the formalized algorithm, Figure~\ref{fig:examplesmbody} gives
+a peek at the behavior 
+using a few examples. The UML diagrams present the hierarchy. 
 In (d) and (e), a cross mark indicates that the interface fails to type-check. Generally, \MIM{} rejects on the definition of an interface

### 2017-10-17 NewVersion/sections/Overview.tex
Small fix.
small fix in S2

@@
 
-From the perspective of \lstinline|DrawableSafeDeck|, the \lstinline|draw| method seems ambiguous. But ideally we would
+From the perspective of \lstinline|DrawableSafeDeck|, the \lstinline|draw| method seems to be ambiguous since \lstinline|DrawableSafeDeck| inherits two \lstinline|draw| method from both \lstinline|SafeDeck| and \lstinline|Drawable|.
+But ideally we would
 like \lstinline|shuffleAndDraw| to invoke \lstinline|SafeDeck.draw|
-because they belong to the same class hierarchy branch. It
-seems that we choose dynamic dispatch but also make use of static type
+because they belong to the same class hierarchy branch. Intuitively, it 
+seems like we need to choose dynamic dispatch but also make use of static type
 information, since the type of this-reference (\lstinline|Deck|)
@@
 The essential problem is how to ensure that the correct method is
-invoked. To solve this problem \MIM{} uses a variant of method
-dispatching that we call \textit{hierarchical dispatch}. In
-hierarchical dispatch both the static and dynamic type information 
+invoked. To solve this problem, \MIM{} uses a variant of method
+dispatching that we call \textit{hierarchical dispatching}. In
+hierarchical dispatching both the static and dynamic type information 
 are used to select the right method implementation.
@@
 %as the default method lookup algorithm. 
-During the runtime, the method call \lstinline|e.m()|
-makes use of both the static type and the dynamic type of the receiver, so it is seemingly a
+During runtime, the method call \lstinline|e.m()|
+makes use of both the static type and the dynamic type of the receiver, so it seems to be a
 combination of static and dynamic dispatch. Intuitively, the static type specifies one branch
@@
 \bruno{Marco complined about this but this was not addressed either!!!}
-During the runtime, when \lstinline|this.draw()| in called,
+During the runtime, when \lstinline|this.draw()| is called,
 the dynamic type of the receiver is \lstinline|DrawableSafeDeck|, but the static type is actually
 \lstinline|Deck|. Here it is an instance of the \textit{hierarchical invocation}, which can be read as 
-``finding the most specific \lstinline|draw| along the path \lstinline|Deck|''. The meaning of ``along path
+``finding the most specific \lstinline|draw| method along path \lstinline|Deck|''. The meaning of ``along path
 \lstinline|Deck|'' not only implies what \lstinline|Deck| inherits, but also the domain of its subtypes up to the

### 2017-10-18 NewVersion/sections/Overview.tex
Overview

@@
 
-This case is the so-called \textit{unintentional method conflict}. It arises when two inherited methods happen to have
+This case is an example of a so-called \textit{unintentional method conflict}. It arises when two inherited methods happen to have
 the same name and parameter types, but they are designed for different functionalities with different semantics.
-Now one may quickly come up with a workaround, which is to manually merge them, by
+Now one may quickly come up with a workaround, which is to manually
+merge the two methods, by
 creating a new \lstinline|draw| method in \lstinline|DrawableDeck| to
@@
 During runtime, the method call \lstinline|e.m()|
-makes use of both the static type and the dynamic type of the receiver, so it seems to be a
+makes use of both the static type and the dynamic type of the
+receiver, so it is a
 combination of static and dynamic dispatch. Intuitively, the static type specifies one branch
@@
 the dynamic type of the receiver is \lstinline|DrawableSafeDeck|, but the static type is actually
-\lstinline|Deck|. Here it is an instance of the \textit{hierarchical invocation}, which can be read as 
+\lstinline|Deck|. This is an instance of \textit{hierarchical invocation}, which can be read as 
 ``finding the most specific \lstinline|draw| method along path \lstinline|Deck|''. The meaning of ``along path
@@
 %Unfortunately, the C++ language, or rather the feature on triangle inheritance, has not been well formalized.
-In our language model, there are two types of casts: \emph{implicit casts} and \emph{explicit upcasts}. The implicit casts appear
-when passing arguments and returning expressions, they are also
-upcasts. Hence all casts are safe. \bruno{This discussion seems
-  inconplete. Either complete it or remove it.}
+%In our language model, there are two types of casts: \emph{implicit casts} and \emph{explicit upcasts}. The implicit casts appear
+%when passing arguments and returning expressions, they are also
+%upcasts. Hence all casts are safe. \bruno{This discussion seems
+%  inconplete. Either complete it or remove it.}
 
@@
 Method overriding is common in Object-Oriented Programming. 
-With diamond inheritance where conflicting methods are intended to have 
+With diamond inheritance, where conflicting methods are intended to have 
 the same semantics, method overriding is not a problem. If conflicting

### 2017-10-18 NewVersion/sections/Discussion.tex
discussion

@@
 the rules and the proof a lot. Secondly, our design choice tends to give more sense on those interesting cases, just as we reject the simple case of diamond inheritance.
-\bruno{don't quite understand the last sentence.} In the presence of triangle inheritance we distinguish and treat differently on the two methods instead of fusing them, since they represent different operations, even if they are abstract.
+\bruno{don't quite understand the last sentence.} In the presence of triangle inheritance we distinguish and treat differently the two methods instead of fusing them, since they represent different operations, even if they are abstract.
 Thus our model adopts a very conservative behaviour rather than automatically merging
@@
 This can be realized by extending our current model with static methods and anonymous classes from Java.
-However such an extension requires more thoughts, so we leave it to future work.
+However such an extension requires more thought, so we leave it to future work.
 

### 2017-10-18 Calculus/src/framework/FHJ.scala
Impl.

@@ -1,122 +1,11 @@
 package framework
 
-import scala.util.parsing.combinator._
-import scala.util.parsing.combinator.syntactical._
-
-object FHJ extends StandardTokenParsers with PackratParsers {
-  
-  case class Info(table: List[String], typeMap: Map[String, List[String]],
-      methodMap: Map[String, List[MethDef]], typeDefMap: Map[String, TypeDef]) {
-    def ext(t1: String, t2: String): Boolean = {
-      if (!table.contains(t1) || !table.contains(t2)) throw new Exception("Error: ext.")
-      typeMap.get(t1).contains(t2)
-    }
-    def subType(t1: String, t2: String): Boolean = {
-      if (!table.contains(t1) || !table.contains(t2)) throw new Exception("Error: subType.")
-      if (t1 == t2) return true
-      typeMap.get(t1).get.exists(x => subType(x, t2))
-    }
-    def dispatch(i: String, m: String, j: String): Option[MethDef] = {
-      if (!table.contains(i) || !table.contains(j)) throw new Exception("Error: dispatch.")
-      methodMap.get(i).get.find(x => x.name == m && x.update == j)
-    }
-    def prune(set: Set[String]): Set[String] = set.filter(i => !set.exists(j => j != i && subType(j, i)))
-    def collectMethods(i: String): Set[String] = {
-      if (!table.contains(i)) throw new Exception("Error: collectMethods.")
-      val start = methodMap.get(i).get.map(x => x.name).toSet
-      val op = (s: Set[String], x: String) => s ++ collectMethods(x)
-      typeMap.get(i).get.foldLeft(start)(op)
-    }
-    def mbody(m: String, id: String, is: String): Option[(String, List[(String, String)], (String, Option[Expr]))] = {
-      if (!table.contains(id) || !table.contains(is)) throw new Exception("Error: mbody.")
-      val set1 = mostSpecific(m, id, is)
-      if (set1.size != 1) return None
-      val i = set1.head
-      val set2 = mostSpecificOverride(m, id, i)
-      if (set2.size != 1) return None
-      val j = set2.head
-      val method = methodMap.get(j).get.find(x => x.name == m && x.update == i)
-      if (method.isEmpty) None else Some(j, method.get.paras, (method.get.returnType, method.get.returnExpr))
-    }
[…]

### 2017-10-18 Calculus/src/framework/Main.scala

@@ -1,0 +1,41 @@
+package framework
+
+import scala.io.Source
+
+object Main {
+  def run(fileName: String): Unit = {
+    val program = Source.fromFile("examples/" + fileName + ".fhj").mkString
+    val parsed = FHJParser.parse(program)
+    if (parsed.isLeft) println(parsed.left.get)
+    else {
+      val pretty = parsed.right.get.toString
+      println(pretty + "\n")
+      val eval = parsed.right.get.run
+      if (eval.isLeft) println("Type-check: " + eval.left.get)
+      else println("==> " + eval.right.get.toString)
+    }
+  }               
+  
+  def main(args : Array[String]) = {
+    println("----------------------------------\nExample (a):\n")
+    run("Example_a")
+    println("----------------------------------\nExample (b):\n")
+    run("Example_b")
+    println("----------------------------------\nExample (c):\n")
+    run("Example_c")
+    println("----------------------------------\nExample (d):\n")
+    run("Example_d")
+    println("----------------------------------\nExample (e):\n")
+    run("Example_e")
+    println("----------------------------------\nExample (f):\n")
+    run("Example_f")
+    println("----------------------------------\nExample (Problem 1):\n")
+    run("Example_p1")
+    println("----------------------------------\nExample (Problem 2):\n")
+    run("Example_p2")
+    println("----------------------------------\nExample (Problem 3):\n")
+    run("Example_p3")
+    println("----------------------------------")
+  }
+  
+}

### 2017-10-18 Calculus/src/framework/Parser.scala

@@ -1,0 +1,37 @@
+package framework
+
+import scala.util.parsing.combinator._
+import scala.util.parsing.combinator.syntactical._
+
+object FHJParser extends StandardTokenParsers with PackratParsers {
+  import FHJ._
+  
+  lexical.reserved += ("interface", "extends", "return", "new", "override", "super")
+  lexical.delimiters += ("(", ")", "{", "}", ",", ".", "::", ";")
+  
+  val lcid = ident ^? { case id if id.charAt(0).isLower => id }
+  val ucid = ident ^? { case id if id.charAt(0).isUpper => id }
+  
+  object Parser {
+    val pP : PackratParser[Program] = rep(pTD) ~ pE ^^ { case l ~ e => new Program(l, e) }
+    val pTD : PackratParser[TypeDef] =
+      ("interface" ~> ucid) ~ ("extends" ~> repsep(ucid, ",") | success(List())) ~ ("{" ~> rep(pMD) <~ "}") ^^
+        { case n ~ sups ~ ms => new TypeDef(n, sups, ms) }
+    val pMD : PackratParser[MethDef] =
+      ucid ~ lcid ~ ("(" ~> repsep(ucid ~ lcid ^^ { case t ~ n => (t, n) }, ",") <~ ")") ~
+        ("override" ~> ucid) ~ ("{" ~> ("return" ~> pE <~ ";") <~ "}" ^^ { case pE => Some(pE) } | ";" ^^^ None) ^^
+          { case t ~ m ~ paras ~ update ~ e => new MethDef(t, m, paras, update, e) }
+    val pE : PackratParser[Expr] =
+      pE ~ ("." ~> lcid) ~ ("(" ~> repsep(pE, ",") <~ ")") ^^
+        { case e ~ m ~ args => Invk(e, m, args) } |||
+      lcid ~ ("(" ~> repsep(pE, ",") <~ ")") ^^
+        { case m ~ args => Invk(Var("this"), m, args) } |||
+      ("(" ~> ucid <~ ")") ~ pE ^^ { case i ~ e => AnnoExpr(i, e) } |||
+      "new" ~> ucid <~ ("(" ~ ")") ^^ New ||| lcid ^^ Var ||| "(" ~> pE <~ ")" 
+  }
+  
+  def parse(in: String): Either[String, Program] = phrase(Parser.pP)(new lexical.Scanner(in)) match {
+      case t if t.successful => Right(t.get)
+      case t                 => Left(t.toString)
+  }
+}

### 2017-10-18 NewVersion/sections/RelatedWork.tex
Final sections

@@
 \noindent {\bf C++ model.}
-C++ supports a very flexible inheritance model (normal inheritance and virtual inheritance). 
-It allows the existence of unintentional conflicts and users may specify a hierarchical path via casts for disambiguation, as discussed in Section~\ref{sec:overview}. 
+C++ supports a very flexible inheritance model (normal inheritance and
+virtual inheritance). \bruno{what is ``normal'' inheritance?}
+C++ allows the existence of unintentional conflicts and users may specify a hierarchical path via casts for disambiguation, as discussed in Section~\ref{sec:overview}. 
 With virtual methods, dynamic dispatch is used and 

### 2017-10-18 NewVersion/sections/Auxiliary.tex
Added all comments (including marcos).

@@
 \section{Key Algorithms and Type-Soundness}\label{sec:auxdefs}
-\yanlin{title changed, is this ok?}
 In this section, we present the fundamental algorithms and auxiliary
@@
 the key components that implement our algorithm for method lookup.
-\bruno{Yes, I agree with Marco: we can move 3.4 to the end of Section
-  4. Don't forget to revise earlier parts of Section 3 to remove
-  mentions of type-soundness there. Or better, in the summary of
-  Section 3 you can point out that type soundness is proved at the 
-end of Section 4.
-}\yanlin{Revised, please check.}
 
@@
 \subsection{Finding the Most Specific Origin: \mostSpecific}\label{sec:mostSpecific}
+\haoyuan{Visualize findorigin and findoverride with some figures.}
 We proceed to give the definitions of two core functions that support method lookup, namely \mostSpecific{} and \mostSpecificOverride. Generally,
@@
 	& \bullet \canInstantiate(I) = True & \\
-	& \indent\indent \textrm{with: } \forall J \in \mostSpecific(m, I, I), \mostSpecificOverride(m, I, J) = \{K\}, & \\
+	& \indent\indent \textrm{with: } \forall m, \forall J \in \mostSpecific(m, I, I), \mostSpecificOverride(m, I, J) = \{K\}, & \\
 	& \hspace{.77in} \textrm{ and } K[m\ \kwoverride\ J] = \method{I_e}{m}{I_x}{x}{J}{e_0} &

### 2017-10-18 NewVersion/sections/Discussion.tex
Added all comments (including marcos).

@@
 our language to traits, Java interfaces as well as other languages. Furthermore, we discuss
-ways to improve our  work.\bruno{references please!!!} \haoyuan{Done}
+ways to improve our work.
 
@@
 
+\haoyuan{Add two figures: triangle inheritance with abstract methods; accepted by both FHJ and Java; but the difference is
+Java automatically merges them, whereas FHJ distinguishes them. Diamond inheritance with abstract methods; accepted by Java
+but rejected by FHJ for some reason.}
 Abstract methods are one of the key features in most general OO languages. For example, Java interfaces were designed
@@
 Other languages may support more complicated behaviours.
-For instance, in Java 8 when putting two identical abstract methods together by multiple inheritance, there is no conflict error. We omit
+For instance, in Java 8 when putting two identical abstract methods together by multiple inheritance, there is no conflict error. We reject
 that case for two reasons. Firstly, our formalization just treats abstract methods as concrete methods with an empty body, and that simplifies
 the rules and the proof a lot. Secondly, our design choice tends to give more sense on those interesting cases, just as we reject the simple case of diamond inheritance.
-\bruno{don't quite understand the last sentence.} In the presence of triangle inheritance we distinguish and treat differently the two methods instead of fusing them, since they represent different operations, even if they are abstract.
+\bruno{don't quite understand the last sentence.} In the presence of triangle inheritance we distinguish and treat differently the two methods instead of fusing them, since they may represent different operations, even if they are abstract.
 Thus our model adopts a very conservative behaviour rather than automatically merging
@@
 
-\haoyuan{more.
+%\haoyuan{more.
 1) Path Invocation, more generalized diamond inheritance: not clear; other method resolution techniques: no example; better code reuse with other kinds of method invocation: no example.

### 2017-10-18 NewVersion/sections/Formalization.tex
Added all comments (including marcos).

@@
 \kwoverride{} keyword to override an old implementation of the
-method. If the interface that it overrides is exactly the enclosing
+method.\haoyuan{Marco: rephrase.} If the interface that it overrides is exactly the enclosing
 interface, then such a method is seen as originally defined; otherwise it is an overriding method. The definition
@@
 invocation, object creation, together with cast expressions. 
-Object creation is represented by $\new I$. Fields and primitive types are not modelled in \MIM{}. 
+Object creation is represented by $\new I$.\haoyuan{add a footnote: $new I()\{\}$ in Java.} Fields and primitive types are not modelled in \MIM{}. 
 The casts are merely safe up-casts, and in fact, they can be viewed as
@@
 The formal definition of $\mbody(m, I, J)$ will be introduced in
-Section~\ref{sec:auxdefs}.
+Section~\ref{sec:auxdefs}.\haoyuan{rephrase. I=J in typing rules and avoid talking about dynamic type.}
 In \textsc{(T-Invk)}, as the compilation should not be aware
@@
 from an abstract method is also acceptable.
-Note that we accept implicit upcasts on the arguments.
+Note that we accept implicit upcasts on the arguments.\haoyuan{Remove the last sentence; it is just subtyping in OO and
+check this in the paper everywhere.}
 % \textsc{(T-PathInvk)} is the typing judgement for a path invocation.
@@
 	\tnew \\
+	\tanno \\
 	\tmethod \\
 	\tabsmethod \\
-	\tintf \\
-	\tanno
+	\tintf
 \end{mathpar}
@@
 Parameters are substituted with arguments, and the \lstinline|this| reference is substituted by the receiver,
-and in the meanwhile implicit casts are applied, so that static types are recorded via annotations. Finally
-there is again an annotation from the return type.
-
+and in the meanwhile implicit casts are applied, so that static types are recorded via annotations. Finally the return type $I_e$ is put in the front as an annotation.
 \paragraph{Congruence Rules} \textsc{(C-Receiver)}, \textsc{(C-Args)} and \textsc{(C-FReduce)} are natural congruence rules

### 2017-10-18 NewVersion/sections/Introduction.tex
Small fix.
Added all comments (including marcos).

@@
 Figure~\ref{fig:main}. In this example, there are 4 classes/interfaces.
-Two classes model a deck of cards (\lstinline|Deck|) and a class for
-drawable widgets (\lstinline|Drawable|). 
+Two classes \lstinline|Deck| and \lstinline|Drawable| model a deck of cards
+ and a drawable widget, respectively. 
 The class \lstinline|SafeDeck| adds functionality to check whether the
@@
           type soundness of the model.
-	\item \textbf{Prototype implementation\footnote{\bruno{URL
-                here} URL}:} a
-          simple implementation of \MIM{} interpreter in Scala.
+	\item \textbf{Prototype implementation\footnote{https://github.com/YanlinWang/MIM/tree/master/Calculus}:} a
+          simple implementation of \MIM{} interpreter in Scala. The implementation can type-check and run the variants
+          of all the examples shown in this paper.
 \end{itemize}

### 2017-10-18 NewVersion/sections/Overview.tex
Added all comments (including marcos).

@@
 method. Therefore \MIM{} accepts the definition of
-\lstinline|DrawableDeck|\bruno{Marco complained about this sentence,
-  which is in the todo list. I've then complained that we should have
-  the todos at the places where TODOs were meant. Now, the sentence
-  remains unchanged. PLEASE go over the TODO list, and check whether
-  you've fixed the issue or not, if not move the TODO to the correct
-  location! }. To disambiguate method calls, 
+\lstinline|DrawableDeck|. To disambiguate method calls, 
 we can use \emph{up-casts} in \MIM{} to specify the ``branch'' in the
@@
 \end{lstlisting}\vspace{3pt}
-\bruno{Marco complined about this but this was not addressed either!!!}
 During the runtime, when \lstinline|this.draw()| is called,
@@
 dynamic type \lstinline|DrawableSafeDeck|. Finally \lstinline|SafeDeck.draw| is correctly returned.
+\haoyuan{Add reduction steps for this example and illustrate it better.}
 
@@
 \haoyuan{I think we are abusing font styles.
-Maybe put all bold text in italic, except for code.}
+TODO: put all bold text in italic, except for code.
+Keep FHJ as bold.}
 

### 2017-10-18 NewVersion/sections/RelatedWork.tex
Added all comments (including marcos).

@@
 more precise subject-reduction theorem as discussed in
-Section~\ref{sec:formalization}.\bruno{put reference and make sure that we discuss this topic}
+Section~\ref{sec:formalization}.

### 2017-10-18 NewVersion/sections/Formalization.tex
Fix.

--- 2017-10-17 NewVersion/sections/Formalization.tex
@@
 method simply includes the returned expression $e$. Notably, we have introduced the
-\kwoverride{} keyword to override an old implementation of the
-method. If the interface that it overrides is exactly the enclosing
-interface, then such a method is seen as originally defined; otherwise it is an overriding method. The definition
+\kwoverride{} keyword for two cases: if the overridden interface is exactly the enclosing
+interface itself, then such a method is seen as originally defined; otherwise it is a hierarchical overriding method. The definition
 of abstract methods is written as $\absmethod{I}{m}{I_x}{x}{J}$, which is
@@
 invocation, object creation, together with cast expressions. 
-Object creation is represented by $\new I$. Fields and primitive types are not modelled in \MIM{}. 
-The casts are merely safe up-casts, and in fact, they can be viewed as
+Object creation is represented by $\new I$\footnote{In Java the corresponding syntax is $\new I\{\}$.}. Fields and primitive types are not modelled in \MIM{}. 
+The casts are merely safe upcasts, and in fact, they can be viewed as
 annotated expressions, where the annotation indicates its static type.
@@
 $\mbody$ is our key function for method lookup that implements the
-hierarchical dispatching algorithm. 
-The hierarchical invocation $\mbody(m, I, J)$ means ``finding most specific method $m$
-above $I$ and along path $J$'', and usually $I$ denotes the dynamic type while $J$
-denotes the static type. 
-The formal definition of $\mbody(m, I, J)$ will be introduced in
-Section~\ref{sec:auxdefs}.
+hierarchical dispatching algorithm. The formal definition will be introduced in Section~\ref{sec:auxdefs}.
+Here $\mbody(m, I_0, I_0)$ finds the most specific $m$ above $I_0$. ``Above $I_0$'' specifies
+the search space: it not only includes the body of $I_0$, but also its super types.
+For the general case, however, the hierarchical invocation $\mbody(m, I, J)$ finds ``the most specific $m$
+above $I$ and along path/branch $J$''.\haoyuan{Make sure we mentioned this in Overview.}
+
 In \textsc{(T-Invk)}, as the compilation should not be aware
@@
 from an abstract method is also acceptable.
-Note that we accept implicit upcasts on the arguments.
 % \textsc{(T-PathInvk)} is the typing judgement for a path invocation.
@@
 Then $\mbody(m, J, J)$ provides the type of the original method, so hierarchical overriding has to preserve the type. Finally the return expression
-needs to be type-checked, and there is also an implicit cast to the declared return type.
+is type-checked to be subtype of the declared return type.
 For the definition of an original method, $I$ equals $J$ and the rule is straightforward.
@@
 that case meets our expectation. Below is an example (Figure~\ref{fig:examplesmbody} (e)) that illustrates the reason why this condition is needed:
-\bruno{what is the purpose of this example:
-  state-it upfront please. Is this example meant to ilustrate T-Inf?
-  Then it's better to have the example together with the text
-  explaining T-inf.} \yanlin{revised.please check whether you're happy with it.}
+%\bruno{what is the purpose of this example:
+%  state-it upfront please. Is this example meant to ilustrate T-Inf?
+%  Then it's better to have the example together with the text
+%  explaining T-inf.} \yanlin{revised.please check whether you're happy with it.}
 \vspace{3pt}\begin{lstlisting}
@@
 are invoked recursively and alternately, and produce a single value in
-the end. \haoyuan{we need to be consistent on paragraph upper/lower case.}
+the end. %\haoyuan{we need to be consistent on paragraph upper/lower case.}
 
@@
 Parameters are substituted with arguments, and the \lstinline|this| reference is substituted by the receiver,
-and in the meanwhile implicit casts are applied, so that static types are recorded via annotations. Finally
-there is again an annotation from the return type.
-
+and in the meanwhile the static types are recorded via annotations. Finally the return type $I_e$ is put in the front as an annotation.
 \paragraph{Congruence Rules} \textsc{(C-Receiver)}, \textsc{(C-Args)} and \textsc{(C-FReduce)} are natural congruence rules

### 2017-10-18 NewVersion/sections/Overview.tex
Fix.

@@
 \lstinline|DrawableDeck|. To disambiguate method calls, 
-we can use \emph{up-casts} in \MIM{} to specify the ``branch'' in the
+we can use \emph{upcasts} in \MIM{} to specify the ``branch'' in the
 inheritance hierarchy that should be called. The following code
-illustrates the use of up-casts for disambiguation:
+illustrates the use of upcasts for disambiguation:
 
@@
 are accepted by multiple inheritance. Note that C++ supports this feature and also addresses the
-ambiguity by up-casts. The code for the above example in C++ is similar.
+ambiguity by upcasts. The code for the above example in C++ is similar.
 
@@
 
-A special rule for hierarchical overriding is: it can only refine \textbf{original} methods, and cannot jump over original methods with the same signature.
+A special rule for hierarchical overriding is: it can only refine \textit{original} methods, and cannot jump over original methods with the same signature.
 For instance, writing \lstinline|"void draw()| \lstinline|override Deck {...}"| is disallowed in \lstinline|DrawableSafeDeck|, because existing two branches are \lstinline|Drawable.draw| and \lstinline|SafeDeck.draw|, while \lstinline|Deck.draw| is already covered.
 It does not really make sense to refine an old branch.
-\haoyuan{I think we are abusing font styles.
-TODO: put all bold text in italic, except for code.
-Keep FHJ as bold.}
 

### 2017-10-19 NewVersion/sections/Auxiliary.tex
section 4.2 added figures and corresponding text

@@
 We proceed to give the definitions of two core functions that support method lookup, namely \mostSpecific{} and \mostSpecificOverride. Generally,
-$\mostSpecific(m, I, J)$ finds the set of most specific interfaces where $m$ is originally defined, they should be above $I$ and
-along path $J$. ``Along path $J$'' means one should be either a subtype or a super type of $J$. Finally with $\prune$ (defined in Section~\ref{sec:otherdefs})
+$\mostSpecific(m, I, J)$ finds the set of most specific interfaces where $m$ is originally defined.
+As shown in Figure~\ref{fig:findOrigin}(left), interfaces in this set should be above interface $I$ and along path $J$.
+``Along path $J$'' means the interface should be either a subtype or a super type of $J$, visually, it should locate between $J$ and $I$ or above $J$.
+Finally with $\prune$ (defined in Section~\ref{sec:otherdefs})
 the overridden interfaces will be filtered out.
@@
 
+\begin{figure*}[t]
+  % \nocaptionrule
+  % \centering
+  \centering
+  \begin{minipage}[t]{0.55\textwidth}
+  \includegraphics[width=1cm]{pics/P10.pdf}
+  \end{minipage}
+  \centering
+  \hspace*{2pt}
+  \begin{minipage}[t]{0.35\textwidth}
+  \includegraphics[width=1cm]{pics/P9.pdf}
+  \end{minipage}  
+  \caption{UMLs illustrating \mostSpecific(left) and \mostSpecificOverride(right)}\label{fig:findOrigin}
+\end{figure*}
+
 \subsection{Finding the Most Specific Overriding: \mostSpecificOverride}\label{sec:mostSpecificOverride}
@@
 \end{flalign*}
-By the definition, an interface belongs to $\mostSpecific(m, I, J)$ if and only if:
+By the definition, as shown in Figure~\ref{fig:findOrigin}, an interface belongs to $\mostSpecific(m, I, J)$ if and only if:
 \begin{itemize}
-	\item It is between $I$ and $J$;
-	\item It hierarchically overrides $J.m$;
-	\item Any subtype of it does not belong to the same set.
+	\item it is between $I$ and $J$;
+	\item it hierarchically overrides $J.m$;
+	\item any subtype of it does not belong to the same set.
 \end{itemize}

### 2017-10-19 NewVersion/sections/Overview.tex
Typos

@@
 interface Deck { void draw() {...} }
-interface Drawable { JFrame draw() {...} }
+interface Drawable { void draw() {...} }
 interface DrawableDeck extends Drawable, Deck {}
@@
 
-\paragraph{A peek of hierarchical dispatching algorithm:} In \MIM{}, triangle inheritance allows several original methods (branches)
+\paragraph{A peek at the hierarchical dispatching algorithm:} In \MIM{}, triangle inheritance allows several original methods (branches)
 to coexist, and hierarchical dispatch first finds the most specific
@@
 using a few examples. The UML diagrams present the hierarchy. 
-In (d) and (e), a cross mark indicates that the interface fails to type-check. Generally, \MIM{} rejects on the definition of an interface
-during compilation, if it reaches a diamond and hence is possible to cause ambiguity. $\mbody$ is the method lookup function for hierarchical
+In (d) and (e), a cross mark indicates that the interface fails to type-check. Generally, \MIM{} rejects the definition of an interface
+during compilation if it reaches a diamond with ambiguity. $\mbody$ is the method lookup function for hierarchical
 dispatch, formally defined in Section~\ref{subsec:mbodydef}.
-In general, $\mbody(m, X, Y) = (Z, ...)$ reflects that the source code \lstinline|((X) new Y()).m()| calls \lstinline|Z.m| in the runtime.
+In general, $\mbody(m, X, Y) = (Z, ...)$ reflects that the source code \lstinline|((Y) new X()).m()| calls \lstinline|Z.m| in the runtime.
 It is undefined when method dispatch is ambiguous.

### 2017-10-19 NewVersion/sections/Overview.tex
added reduction steps in S2.2

@@
 
-Using hierarchical dispatching the following code is accepted:
+\noindent Using hierarchical dispatching the following code is accepted:
 \vspace{3pt}\begin{lstlisting}
@@
 interface DrawableSafeDeck extends Drawable, SafeDeck {}
-
 // main program
@@
 \end{lstlisting}\vspace{3pt}
+
+\noindent We show the rough reductions here (without our techniques):
+\begin{lstlisting}
+new DrawableSafeDeck().shuffleAndDraw() 
+-> [new DrawableSafeDeck().shuffle(), new DrawableSafeDeck().draw()]
+-> [..., ambiguous call!}]
+\end{lstlisting}
+When the \lstinline|DrawableSafeDeck| object calls \lstinline|shuffleAndDraw|, the implementation in \lstinline|Deck| is dispatched.
+But then \lstinline|shuffleAndDraw| invokes ``\lstinline|this.draw()|'', and at this point, the receiver
+is replaced by the object \lstinline|new DrawableSafeDeck()|.
+From the perspective of \lstinline|DrawableSafeDeck|, the \lstinline|draw| method is ambiguous since \lstinline|DrawableSafeDeck| inherits two \lstinline|draw| method from both \lstinline|SafeDeck| and \lstinline|Drawable|.
+But ideally we would
+like \lstinline|shuffleAndDraw| to invoke \lstinline|SafeDeck.draw|
+because they belong to the same class hierarchy branch. Here is the rough reductions in our model that accept this call: 
+\begin{lstlisting}
+new DrawableSafeDeck().shuffleAndDraw() 
+-> [..., (Deck)new DrawableSafeDeck().draw()]
+-> [..., SafeDeck.draw()]
+\end{lstlisting}
+We make use of the branch information by adding the cast \lstinline|Deck|, since the type of this-reference (\lstinline|Deck|) specifies the branch to use unambiguously. 
 During the runtime, when \lstinline|this.draw()| is called,
@@
 \lstinline|Deck|'' not only implies what \lstinline|Deck| inherits, but also the domain of its subtypes up to the
-dynamic type \lstinline|DrawableSafeDeck|. Finally \lstinline|SafeDeck.draw| is correctly returned.
+dynamic type \lstinline|DrawableSafeDeck|. Finally \lstinline|SafeDeck.draw| is correctly returned. The details of how this is done will be explained in Section~\ref{sec:formalization}.
+
 \haoyuan{Add reduction steps for this example and illustrate it better.}
-
+\yanlin{Added, please review}
 %Note that in C++, if we put the \lstinline[language=c++]|virtual| keyword in front of every \lstinline|draw| method, that means

### 2017-10-19 NewVersion/sections/Overview.tex
small fix
Reductions

@@
 is replaced by the object \lstinline|new DrawableSafeDeck()|.
+From the perspective of \lstinline|DrawableSafeDeck|, the
+\lstinline|draw| method seems to be ambiguous since
+\lstinline|DrawableSafeDeck| inherits two \lstinline|draw| method from
+both \lstinline|SafeDeck| and \lstinline|Drawable|. 
+Indeed, using the a reduction model similar to FJ~\cite{} (where static types tracked), the 
+reduction steps would roughly be:
+\begin{lstlisting}
+new DrawableSafeDeck().shuffleAndDraw() 
+-> [new DrawableSafeDeck().shuffle(), new DrawableSafeDeck().draw()]
+-> [..., ambiguous call!}]
+\end{lstlisting}
+When the \lstinline|DrawableSafeDeck| object calls \lstinline|shuffleAndDraw|, the implementation in \lstinline|Deck| is dispatched.
+But then \lstinline|shuffleAndDraw| invokes ``\lstinline|this.draw()|'', and at this point, the receiver
+is replaced by the object \lstinline|new DrawableSafeDeck()|.
+From the perspective of \lstinline|DrawableSafeDeck|, the \lstinline|draw| method is ambiguous since \lstinline|DrawableSafeDeck| inherits two \lstinline|draw| method from both \lstinline|SafeDeck| and \lstinline|Drawable|.
+But ideally we would
+like \lstinline|shuffleAndDraw| to invoke \lstinline|SafeDeck.draw|
+because they belong to the same class hierarchy branch.
 
-From the perspective of \lstinline|DrawableSafeDeck|, the \lstinline|draw| method seems to be ambiguous since \lstinline|DrawableSafeDeck| inherits two \lstinline|draw| method from both \lstinline|SafeDeck| and \lstinline|Drawable|.
+\begin{comment}
 But ideally we would
@@
 specifies the branch to use unambiguously.
+\end{comment}
 
@@
 
-\noindent We show the rough reductions here (without our techniques):
-\begin{lstlisting}
-new DrawableSafeDeck().shuffleAndDraw() 
--> [new DrawableSafeDeck().shuffle(), new DrawableSafeDeck().draw()]
--> [..., ambiguous call!}]
-\end{lstlisting}
-When the \lstinline|DrawableSafeDeck| object calls \lstinline|shuffleAndDraw|, the implementation in \lstinline|Deck| is dispatched.
-But then \lstinline|shuffleAndDraw| invokes ``\lstinline|this.draw()|'', and at this point, the receiver
-is replaced by the object \lstinline|new DrawableSafeDeck()|.
-From the perspective of \lstinline|DrawableSafeDeck|, the \lstinline|draw| method is ambiguous since \lstinline|DrawableSafeDeck| inherits two \lstinline|draw| method from both \lstinline|SafeDeck| and \lstinline|Drawable|.
-But ideally we would
-like \lstinline|shuffleAndDraw| to invoke \lstinline|SafeDeck.draw|
-because they belong to the same class hierarchy branch. Here is the rough reductions in our model that accept this call: 
+Here are the reductions performed in \MIM{} to accept this call: 
 \begin{lstlisting}
@@
 \end{lstlisting}
-We make use of the branch information by adding the cast \lstinline|Deck|, since the type of this-reference (\lstinline|Deck|) specifies the branch to use unambiguously. 
+Notably, we make use of the branch information by adding the cast \lstinline|Deck|, since the type of this-reference (\lstinline|Deck|) specifies the branch to use unambiguously. 
 During the runtime, when \lstinline|this.draw()| is called,

### 2017-10-19 NewVersion/sections/Discussion.tex
Fix.
S6.2 fix comments

@@
 
-\subsection{Loosening the Model: Reject Early or Reject Later?}
+\subsection{Loosening the Model: Reject Early or Reject Later?}\label{subsec:loosen}
 
@@
  C++ accepts the definition of $D$, but forbids later upcasts from $D$ to $A$ because of ambiguity.
-Our language is more conservative on definitions of interfaces compared to C++, but on the upside, up-casts are not rejected.
+Our language is more conservative on definitions of interfaces compared to C++, but on the upside, upcasts are not rejected.
 We could also loosen the model to accept definitions such as \lstinline|D|, and perform ambiguity check on upcasts and other expressions.

### 2017-10-19 NewVersion/sections/RelatedWork.tex
S6.2 fix comments

@@
 \noindent {\bf C++ model.}
-C++ supports a very flexible inheritance model (normal inheritance and
-virtual inheritance). \bruno{what is ``normal'' inheritance?}
+C++ supports a very flexible inheritance model (including basic and
+virtual inheritance). \bruno{what is ``normal'' inheritance?}\yanlin{changed "normal" to "basic", is this ok?}
 C++ allows the existence of unintentional conflicts and users may specify a hierarchical path via casts for disambiguation, as discussed in Section~\ref{sec:overview}. 
@@
 captures this aspect of the C++ method dispatching model.
+Apart from this, as discussed in Section~\ref{subsec:loosen}, \name{} conservatively rejects some interface/class definitions that C++ accepts, and upcasts are never rejected since they are used for ambiguity resolution.
 \bruno{The discussion points out further differences. We need to refer
-to that discussion here too.}
+to that discussion here too.}\yanlin{added.}
 

### 2017-10-19 NewVersion/paper.tex
Abstract intro overview
Added all comments (including marcos).
S2 reduction steps revised

@@
 
-%\newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
-%\newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
-%\newcommand\marco[1]{\authornote{marco}{blue}{#1}}
-%\newcommand\marcoT[1]{\authorText{blue}{#1}}
-%\newcommand\haoyuan[1]{\authornote{haoyuan}{orange}{#1}}
+\newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
+\newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
+\newcommand\marco[1]{\authornote{marco}{blue}{#1}}
+\newcommand\marcoT[1]{\authorText{blue}{#1}}
+\newcommand\haoyuan[1]{\authornote{haoyuan}{orange}{#1}}
 
-\newcommand\bruno[1]{}
-\newcommand\yanlin[1]{}
-\newcommand\marco[1]{}
-\newcommand\haoyuan[1]{}
+%\newcommand\bruno[1]{}
+%\newcommand\yanlin[1]{}
+%\newcommand\marco[1]{}
+%\newcommand\haoyuan[1]{}
 
@@
 
+\lstdefinestyle{reduction}{
+  	language=C,                % choose the language of the code
+	columns=flexible,
+	lineskip=-1pt,
+	basicstyle=\ttfamily\small,       % the size of the fonts that are used for the code
+	numbers=none,                   % where to put the line-numbers
+	numberstyle=\ttfamily\tiny,      % the size of the fonts that are used for the line-numbers
+	stepnumber=1,                   % the step between two line-numbers. If it's 1 each line will be numbered
+	numbersep=5pt,                  % how far the line-numbers are from the code
+	backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
+	showspaces=false,               % show spaces adding particular underscores
+	showstringspaces=false,         % underline spaces within strings
+	showtabs=false,                 % show tabs within strings adding particular underscores
+	morekeywords={var,override},
+	%  frame=single,                   % adds a frame around the code
+	tabsize=2,                  % sets default tabsize to 2 spaces
+	captionpos=none,                   % sets the caption-position to bottom
+	breaklines=true,                % sets automatic line breaking
+	breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
+	title=\lstname,                 % show the filename of files included with \lstinputlisting; also try caption instead of title
+	escapeinside={(*}{*)},          % if you want to add a comment within your code
+	keywordstyle=\sffamily\bfseries,
+	aboveskip=0pt,
+	belowskip=0pt,
+  moredelim=[is][\underbar]{_}{_},
+  keepspaces=true
+	% commentstyle=\color{Gray},
+	% stringstyle=\color{Green}
+}
+
 \begin{document}
@@
 is the \emph{ambiguity} arising from inheriting multiple parents,
-which can have conflicting methods and fields. 
+which can have conflicting methods. 
 Numerous existing work provides solutions for 
@@
 
+\bibliographystyle{splncs03}
+\bibliography{paper}
+
 \newpage
@@
 
-\newpage
-
-\bibliographystyle{splncs03}
-\bibliography{paper}
-
 \end{document}

### 2017-10-19 NewVersion/sections/Overview.tex
S2 reduction steps revised

@@
 Without dynamic dispatching, we may have to copy the \lstinline|shuffleAndDraw| code into \lstinline|SafeDeck|, so that \lstinline|shuffleAndDraw| calls the new \lstinline|draw| defined in \lstinline|SafeDeck|.
-Yet dynamic dispatching immediately saves us from the duplication work,
+Dynamic dispatching immediately saves us from the duplication work,
 since the method becomes automatically dispatched to the most specific one. Nevertheless, as seen before, dynamic dispatch would potentially introduce ambiguity.
-For instance, when we have the class hierarchy structure shown in Figure~\ref{fig:drawablesafedeck}(left) and the following code:
-
-% \begin{figure*}[t]
-% 	\saveSpaceFig
-% 	\centering
-% 	\includegraphics[height=2cm]{pics/DrawableSafeDeck.pdf}
-% 	\caption{UML graph for \lstinline|DrawableSafeDeck|.}\label{fig:drawablesafedeck}
-% 	\saveSpaceFig
-% \end{figure*}
+For instance, when we have the class hierarchy structure shown in Figure~\ref{fig:drawablesafedeck}(left) with the following code:
 
@@
 \end{lstlisting}\vspace{3pt}
-When the \lstinline|DrawableSafeDeck| object calls \lstinline|shuffleAndDraw|, the implementation in \lstinline|Deck|
+
+\noindent Indeed, using the a reduction model similar to FJ~\cite{Igarashi01FJ} (without static types tracked), the reduction steps would roughly be:
+
+% \begin{equation}\label{}
+% \begin{split}
+% A & = \frac{\pi r^2}{2} \\
+%  & = \frac{1}{2} \pi r^2
+% \end{split}
+% \end{equation}
+
+\begin{lstlisting}[style=reduction, escapechar=\%]
+   %\underline{new DrawableSafeDeck()}%.shuffleAndDraw()
+-> %\underline{new DrawableSafeDeck().shuffle()}%, new DrawableSafeDeck().draw()
+-> ..., %\underline{new DrawableSafeDeck().draw()}%
+-> ..., ambiguous call!!!
+\end{lstlisting}
+
+\noindent When the \lstinline|DrawableSafeDeck| object calls \lstinline|shuffleAndDraw|, the implementation in \lstinline|Deck|
 is dispatched. But then \lstinline|shuffleAndDraw| invokes ``\lstinline|this.draw()|'', and at this point, the receiver
@@
 \lstinline|draw| method seems to be ambiguous since
-\lstinline|DrawableSafeDeck| inherits two \lstinline|draw| method from
+\lstinline|DrawableSafeDeck| inherits two \lstinline|draw| methods from
 both \lstinline|SafeDeck| and \lstinline|Drawable|. 
-Indeed, using the a reduction model similar to FJ~\cite{} (where static types tracked), the 
-reduction steps would roughly be:
-\begin{lstlisting}
-new DrawableSafeDeck().shuffleAndDraw() 
--> [new DrawableSafeDeck().shuffle(), new DrawableSafeDeck().draw()]
--> [..., ambiguous call!}]
-\end{lstlisting}
-When the \lstinline|DrawableSafeDeck| object calls \lstinline|shuffleAndDraw|, the implementation in \lstinline|Deck| is dispatched.
-But then \lstinline|shuffleAndDraw| invokes ``\lstinline|this.draw()|'', and at this point, the receiver
-is replaced by the object \lstinline|new DrawableSafeDeck()|.
-From the perspective of \lstinline|DrawableSafeDeck|, the \lstinline|draw| method is ambiguous since \lstinline|DrawableSafeDeck| inherits two \lstinline|draw| method from both \lstinline|SafeDeck| and \lstinline|Drawable|.
 But ideally we would
@@
 
-%%\paragraph{Problem:} \\
-
 \paragraph{\MIM's solution:} 
@@
 %as the default method lookup algorithm. 
-During runtime, the method call \lstinline|e.m()|
+During runtime, a method call \lstinline|e.m()|
 makes use of both the static type and the dynamic type of the
 receiver, so it is a
-combination of static and dynamic dispatch. Intuitively, the static type specifies one branch
+combination of static and dynamic dispatching. Intuitively, the static type specifies one branch
 to avoid ambiguity, and the dynamic type finds the most specific implementation on that branch.
@@
 
-Here are the reductions performed in \MIM{} to accept this call: 
-\begin{lstlisting}
-new DrawableSafeDeck().shuffleAndDraw() 
--> [..., (Deck)new DrawableSafeDeck().draw()]
--> [..., SafeDeck.draw()]
+\noindent Here are the reductions performed in \MIM{}:
+\begin{lstlisting}[style=reduction, escapechar=\%]
+   %\underline{new DrawableSafeDeck()}%.shuffleAndDraw()
+-> %\underline{((DrawableSafeDeck)new DrawableSafeDeck()).shuffleAndDraw()}%
+-> %\underline{((Deck)new DrawableSafeDeck()).shuffle()}%, ((Deck)new DrawableSafeDeck()).draw()
+-> ..., %\underline{((Deck)new DrawableSafeDeck()).draw()}%
+-> ..., ... %//SafeDeck.draw()%
 \end{lstlisting}
+
 Notably, we make use of the branch information by adding the cast \lstinline|Deck|, since the type of this-reference (\lstinline|Deck|) specifies the branch to use unambiguously. 

### 2017-10-19 NewVersion/sections/Discussion.tex
S3,S5 by Haoyuan

@@
 
-\haoyuan{Add two figures: triangle inheritance with abstract methods; accepted by both FHJ and Java; but the difference is
-Java automatically merges them, whereas FHJ distinguishes them. Diamond inheritance with abstract methods; accepted by Java
-but rejected by FHJ for some reason.}
 Abstract methods are one of the key features in most general OO languages. For example, Java interfaces were designed
@@
 Our formalization has a simple form of abstract methods, which behave similarly to conventional methods with respect to conflicts.
-Other languages may support more complicated behaviours.
-For instance, in Java 8 when putting two identical abstract methods together by multiple inheritance, there is no conflict error. We reject
-that case for two reasons. Firstly, our formalization just treats abstract methods as concrete methods with an empty body, and that simplifies
-the rules and the proof a lot. Secondly, our design choice tends to give more sense on those interesting cases, just as we reject the simple case of diamond inheritance.
-\bruno{don't quite understand the last sentence.} In the presence of triangle inheritance we distinguish and treat differently the two methods instead of fusing them, since they may represent different operations, even if they are abstract.
-Thus our model adopts a very conservative behaviour rather than automatically merging
-methods, and implicitly assuming diamond inheritance. 
-It is possible to change our model to account for other behaviours for abstract methods, but we view this as a mostly 
+Other languages may support more complicated behaviors.
+For instance, in Java 8 when putting two identical abstract methods together by multiple inheritance, there is no conflict error.
+In Figure~\ref{fig:abstractdiamond}, we use italic $m$ to denote abstract methods.
+For both cases, the Java compiler automatically merges conflicting $m$ in $C$.
+In contrast, \MIM{} distinguishes $A.m$ and $B.m$ in triangle inheritance (left), and rejects the diamond inheritance (right).
+There are two reasons.
+Firstly, our formalization just treats abstract methods as concrete methods with an empty body, and that simplifies
+the rules and the proof a lot.
+Secondly, we distinguish and treat differently on the conflicting methods, since they may represent different operations, even if they are abstract.
+Thus our model adopts a very conservative behavior rather than automatically merging
+methods. For the diamond case, as we have mentioned, it is actually an intentional conflict due to the same source $T$.
+It is possible to change our model to account for other behaviors for abstract methods, but we view this as a mostly 
 orthogonal change to our work, that should not affect the essence of the model presented here.
+
+\begin{figure*}[t]
+    % \nocaptionrule
+    % \centering
+    \centering
+    \begin{minipage}[t]{0.45\textwidth}
+        \centering
+        \includegraphics[width=2cm]{pics/P7.pdf}
+    \end{minipage}
+    \centering
+    \hspace*{2pt}
+    \begin{minipage}[t]{0.45\textwidth}
+        \centering
+        \includegraphics[width=2cm]{pics/P8.pdf}
+    \end{minipage}  
+    \caption{Triangle inheritance (left) and diamond inheritance (right) on abstract methods.}\label{fig:abstractdiamond}
+\end{figure*}
 

### 2017-10-19 NewVersion/sections/Auxiliary.tex
Fix.

--- 2017-10-18 NewVersion/sections/Auxiliary.tex
@@
 \subsection{Finding the Most Specific Origin: \mostSpecific}\label{sec:mostSpecific}
-\haoyuan{Visualize findorigin and findoverride with some figures.}
 We proceed to give the definitions of two core functions that support method lookup, namely \mostSpecific{} and \mostSpecificOverride. Generally,
-$\mostSpecific(m, I, J)$ finds the set of most specific interfaces where $m$ is originally defined, they should be above $I$ and
-along path $J$. ``Along path $J$'' means one should be either a subtype or a super type of $J$. Finally with $\prune$ (defined in Section~\ref{sec:otherdefs})
+$\mostSpecific(m, I, J)$ finds the set of most specific interfaces where $m$ is originally defined.
+Interfaces in this set should be above interface $I$ and along path $J$.
+Finally with $\prune$ (defined in Section~\ref{sec:otherdefs})
 the overridden interfaces will be filtered out.
@@
 	\item It originally defines $m$;
-	\item It is a super type of $I$;
-	\item It is either a super type or a subtype of $J$ (including $J$ itself);
+	\item It is a super type of $I$ (including $I$);
+	\item It is either a super type or a subtype of $J$ (including $J$);
 	\item Any subtype of it does not belong to the same result set because of $\prune$.
@@
 \end{flalign*}
-By the definition, an interface belongs to $\mostSpecific(m, I, J)$ if and only if:
+By the definition, an interface belongs to $\mostSpecificOverride(m, I, J)$ if and only if:
 \begin{itemize}
-	\item It is between $I$ and $J$;
-	\item It hierarchically overrides $J.m$;
-	\item Any subtype of it does not belong to the same set.
+	\item it is between $I$ and $J$ (including $I$, $J$);
+	\item it hierarchically overrides $J.m$;
+	\item any subtype of it does not belong to the same set.
 \end{itemize}

### 2017-10-19 NewVersion/sections/Overview.tex
Fix.

@@
 
-\begin{lstlisting}[style=reduction, escapechar=\%]
+\vspace{3pt}\begin{lstlisting}[style=reduction, escapechar=\%]
    %\underline{new DrawableSafeDeck()}%.shuffleAndDraw()
@@
 -> ..., ambiguous call!!!
-\end{lstlisting}
+\end{lstlisting}\vspace{3pt}
 
@@
 %as the default method lookup algorithm. 
-During runtime, a method call \lstinline|e.m()|
+During runtime, a method call
 makes use of both the static type and the dynamic type of the
@@
 to avoid ambiguity, and the dynamic type finds the most specific implementation on that branch.
-The formal algorithm will be introduced in Section~\ref{sec:formalization} and Section~\ref{sec:auxdefs}.
 
-\noindent Using hierarchical dispatching the following code is accepted:
+To be specific, the following code is accepted by \MIM{}:
 \vspace{3pt}\begin{lstlisting}
@@
 \end{lstlisting}\vspace{3pt}
+And the computation performed in \MIM{} is as follows:
+\vspace{3pt}\begin{lstlisting}[style=reduction, escapechar=\%]
+   %\underline{new DrawableSafeDeck()}%.shuffleAndDraw()
+-> %\underline{((DrawableSafeDeck) new DrawableSafeDeck()).shuffleAndDraw()}%
+-> %\underline{((Deck) new DrawableSafeDeck()).shuffle()}%, ((Deck) new DrawableSafeDeck()).draw()
+-> ..., %\underline{((Deck) new DrawableSafeDeck()).draw()}%
+-> ..., ... %// SafeDeck.draw%
+\end{lstlisting}\vspace{3pt}
 
-\noindent Here are the reductions performed in \MIM{}:
-\begin{lstlisting}[style=reduction, escapechar=\%]
-   %\underline{new DrawableSafeDeck()}%.shuffleAndDraw()
--> %\underline{((DrawableSafeDeck)new DrawableSafeDeck()).shuffleAndDraw()}%
--> %\underline{((Deck)new DrawableSafeDeck()).shuffle()}%, ((Deck)new DrawableSafeDeck()).draw()
--> ..., %\underline{((Deck)new DrawableSafeDeck()).draw()}%
--> ..., ... %//SafeDeck.draw()%
-\end{lstlisting}
-
-Notably, we make use of the branch information by adding the cast \lstinline|Deck|, since the type of this-reference (\lstinline|Deck|) specifies the branch to use unambiguously. 
-During the runtime, when \lstinline|this.draw()| is called,
-the dynamic type of the receiver is \lstinline|DrawableSafeDeck|, but the static type is actually
-\lstinline|Deck|. This is an instance of \textit{hierarchical invocation}, which can be read as 
-``finding the most specific \lstinline|draw| method along path \lstinline|Deck|''. The meaning of ``along path
-\lstinline|Deck|'' not only implies what \lstinline|Deck| inherits, but also the domain of its subtypes up to the
-dynamic type \lstinline|DrawableSafeDeck|. Finally \lstinline|SafeDeck.draw| is correctly returned. The details of how this is done will be explained in Section~\ref{sec:formalization}.
-
-\haoyuan{Add reduction steps for this example and illustrate it better.}
-\yanlin{Added, please review}
+Notably, we track the static types by adding casts. In the second reduction step, when 
+\lstinline|shuffleAndDraw| is dispatched, the receiver \lstinline|(DrawableSafeDeck) new DrawableSafeDeck()|
+has to replace the special variable \lstinline|this|, but at this point the cast becomes the type of \lstinline|this|,
+namely \lstinline|Deck|. Thus the information is saved for future disambiguation. And later in the fourth step,
+\lstinline|((Deck) new DrawableSafeDeck()).draw()|
+is an instance of \textit{hierarchical invocation}, which can be read as 
+``finding the most specific \lstinline|draw| above \lstinline|DrawableSafeDeck| and along path \lstinline|Deck|''.
+The meaning of ``above \lstinline|DrawableSafeDeck|'' implies its super types, and ``along path
+\lstinline|Deck|'' specifies the branch. It finally finds the most specific version in \lstinline|SafeDeck|.
+The formal procedure will be introduced in Section~\ref{sec:formalization} and Section~\ref{sec:auxdefs}.
 %Note that in C++, if we put the \lstinline[language=c++]|virtual| keyword in front of every \lstinline|draw| method, that means

### 2017-10-19 NewVersion/sections/Overview.tex
s2 tmp

--- 2017-10-19 NewVersion/sections/Overview.tex
@@
 problems. Hence it is important to emphasize that, with respect to
-hierarchical dispatching, our contribution is not a novel
+hierarchical dispatching, our model is not a novel
 mechanism. Instead, 
-inspired by the C++ solution, our contribution is formalizing a minimal calculus
+inspired by the C++ solutions, our contribution is formalizing a minimal calculus
 of this feature together with a proof of type soundness. However, for the final problem, there is no satisfactory approach

### 2017-10-19 NewVersion/sections/Formalization.tex
S3,S5 by Haoyuan

@@
 Here $\mbody(m, I_0, I_0)$ finds the most specific $m$ above $I_0$. ``Above $I_0$'' specifies
-the search space: it not only includes the body of $I_0$, but also its super types.
+the search space, namely the super types of $I_0$ including itself.
 For the general case, however, the hierarchical invocation $\mbody(m, I, J)$ finds ``the most specific $m$
-above $I$ and along path/branch $J$''.\haoyuan{Make sure we mentioned this in Overview.}
+above $I$ and along path/branch $J$''. ``Along path $J$'' additionally requires the result to relate to $J$, that is to say,
+the most specific interface has a subtyping relationship with $J$.
 
@@
 congruence rules of \MIM{}. When evaluating an expression, they
-are invoked recursively and alternately, and produce a single value in
+are invoked recursively and produce a single value in
 the end. %\haoyuan{we need to be consistent on paragraph upper/lower case.}

### 2017-10-19 NewVersion/sections/Overview.tex
small fix. to 25pages

@@
 of this feature together with a proof of type soundness. However, for the final problem, there is no satisfactory approach
-in existing languages, thus what we propose is a new feature (hierarchical
+in existing languages, thus what we propose is a novel feature (hierarchical
 overriding) with the corresponding formalization of that feature.
@@
 The two \lstinline|draw| methods can have different return types, but for simplicity, 
-they both return \lstinline|void| here. Note that, similarly to
+the return types are both \lstinline|void| here. Note that, similarly to
 Featherweight Java~\cite{Igarashi01FJ}, \lstinline|void| is
@@
 use \lstinline|void| in our examples.
-For \lstinline|Drawable| the \lstinline|draw| method
+In interface \lstinline|Drawable|, the \lstinline|draw| method
 creates a blank canvas.

### 2017-10-20 NewVersion/sections/Overview.tex
Explanation

@@
 \vspace{3pt}\begin{lstlisting}[style=reduction, escapechar=\%]
-   %\underline{new DrawableSafeDeck()}%.shuffleAndDraw()
--> %\underline{new DrawableSafeDeck().shuffle()}%, new DrawableSafeDeck().draw()
--> ..., %\underline{new DrawableSafeDeck().draw()}%
--> ..., ambiguous call!!!
+   %new DrawableSafeDeck()%.shuffleAndDraw()
+-> %new DrawableSafeDeck().shuffle()%; new DrawableSafeDeck().draw()
+-> ...
+-> %new DrawableSafeDeck().draw()%
+-> ambiguous call!!!
 \end{lstlisting}\vspace{3pt}
@@
 \vspace{3pt}\begin{lstlisting}[style=reduction, escapechar=\%]
-   %\underline{new DrawableSafeDeck()}%.shuffleAndDraw()
--> %\underline{((DrawableSafeDeck) new DrawableSafeDeck()).shuffleAndDraw()}%
--> %\underline{((Deck) new DrawableSafeDeck()).shuffle()}%, ((Deck) new DrawableSafeDeck()).draw()
--> ..., %\underline{((Deck) new DrawableSafeDeck()).draw()}%
--> ..., ... %// SafeDeck.draw%
+   %new DrawableSafeDeck()%.shuffleAndDraw()
+-> %((DrawableSafeDeck) new DrawableSafeDeck()).shuffleAndDraw()%
+-> %((Deck) new DrawableSafeDeck()).shuffle()%; ((Deck) new DrawableSafeDeck()).draw()
+-> ...
+-> %((Deck) new DrawableSafeDeck()).draw()%
+-> ... %// SafeDeck.draw%
 \end{lstlisting}\vspace{3pt}
 
-Notably, we track the static types by adding casts. In the second reduction step, when 
-\lstinline|shuffleAndDraw| is dispatched, the receiver \lstinline|(DrawableSafeDeck) new DrawableSafeDeck()|
-has to replace the special variable \lstinline|this|, but at this point the cast becomes the type of \lstinline|this|,
-namely \lstinline|Deck|. Thus the information is saved for future disambiguation. And later in the fourth step,
+Notably, we track the static types by adding casts. In contrast to FJ,
+where \lstinline|new C()| is a value, in \MIM{} such expression is not 
+a value. Instead an expression of the form \lstinline|new C()| is reduced to
+\lstinline|(C) new C()|, which is a value in \MIM{}. This rule is
+applied in the first reduction step. 
+In the second reduction step, when 
+\lstinline|shuffleAndDraw| is dispatched, the receiver
+\lstinline|(DrawableSafeDeck) new DrawableSafeDeck()|
+replaces the special variable \lstinline|this| by 
+\lstinline|(Deck) new DrawableSafeDeck()|. Here, the static type used
+in the cast denotes the origin of the \lstinline|shuffleAndDraw|
+method used
+for method dispatching. 
+%The static type information about the origin
+%of the method is helpful for future disambiguation. 
+Later, in the fourth step,
 \lstinline|((Deck) new DrawableSafeDeck()).draw()|
@@
 The meaning of ``above \lstinline|DrawableSafeDeck|'' implies its super types, and ``along path
-\lstinline|Deck|'' specifies the branch. It finally finds the most specific version in \lstinline|SafeDeck|.
+\lstinline|Deck|'' specifies the branch. Finally, in the last
+reduction step, we find the most
+specific version of \lstinline|draw| in \lstinline|SafeDeck|. In this
+reduction, the cast that tracks the origin of
+\lstinline|shuffleAndDraw| is crutial to unambiguously find the
+correct implementation of \lstinline|draw|.
 The formal procedure will be introduced in Section~\ref{sec:formalization} and Section~\ref{sec:auxdefs}.

### 2017-10-20 NewVersion/sections/Overview.tex
added missing figure and small fix

--- 2017-10-19 NewVersion/sections/Overview.tex
@@
 interface Drawable {
-  void draw() { // draws something on the screen
+  void draw() { // create a blank canvas
     JFrame frame = new JFrame();
@@
 \end{lstlisting}\vspace{3pt}
-The point of using multiple inheritance is for composing the features from various 
+The point of using multiple inheritance is to compose the features from various 
 components and to achieve code reuse, as supported by many mainstream OO
@@
 Now one may quickly come up with a workaround, which is to manually
-merge the two methods, by
-creating a new \lstinline|draw| method in \lstinline|DrawableDeck| to
+merge the two methods by creating a new \lstinline|draw| method in \lstinline|DrawableDeck| to
 override the old ones. However, merging two methods with totally different functionalities does not make any sense.
-This non-solution will hide the
+This non-solution would hide the
 old methods and break independent extensibility.
@@
 how to resolve unintentional method conflicts and invoke the
-conflicting methods separately without ambiguity. To this problem, there are several other workarounds
+conflicting methods separately without ambiguity. To tackle this problem, there are several other workarounds
 that come to our mind. We briefly discuss those potential fixes and
@@
   \item \textit{I. Delegation.} As an alternative to multiple inheritance,
-  delegation can be used by introducing two fields (or field methods) with
+  delegation can be used by introducing two fields (or field methods) with the \yanlin{"field methods"?}
   \lstinline|Drawable| type and \lstinline|Deck| type,
-  respectively. This avoids method conflicts. Nevertheless, it is known
+  respectively. Although it avoids method conflicts, it is known
   that using delegation makes it hard to correctly maintain
@@
   introduces a lot of boilerplate code.
-  \item \textit{II. Refactor Drawable and/or Deck to rename the methods.} If
+  \item \textit{II. Refactor \lstinline|Drawable| and/or \lstinline|Deck| to rename the methods.} If
   the source code for \lstinline|Drawable| or \lstinline|Deck| is available
@@
   methods. However this approach is non-modular, as it requires 
-  modifying existing code, and may not be possible if the code is unavailable.
+  modifying existing code and becomes impossible if the code is unavailable.
   \item \textit{III. Method exclusion/renaming in traits.} Some trait models
@@
 -> %\underline{new DrawableSafeDeck().shuffle()}%, new DrawableSafeDeck().draw()
--> ..., %\underline{new DrawableSafeDeck().draw()}%
+-> ... -> (some steps omitted here)
+-> 
 -> ..., ambiguous call!!!

### 2017-10-20 NewVersion/paper.tex
small fix. to 25pages

@@
 
-\newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
-\newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
-\newcommand\marco[1]{\authornote{marco}{blue}{#1}}
-\newcommand\marcoT[1]{\authorText{blue}{#1}}
-\newcommand\haoyuan[1]{\authornote{haoyuan}{orange}{#1}}
+% \newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
+% \newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
+% \newcommand\marco[1]{\authornote{marco}{blue}{#1}}
+% \newcommand\marcoT[1]{\authorText{blue}{#1}}
+% \newcommand\haoyuan[1]{\authornote{haoyuan}{orange}{#1}}
 
-%\newcommand\bruno[1]{}
-%\newcommand\yanlin[1]{}
-%\newcommand\marco[1]{}
-%\newcommand\haoyuan[1]{}
+\newcommand\bruno[1]{}
+\newcommand\yanlin[1]{}
+\newcommand\marco[1]{}
+\newcommand\haoyuan[1]{}
 
@@
 \author{Yanlin Wang\inst{1} \and Haoyuan Zhang\inst{1} \and Bruno C.d.S. Oliveira\inst{1} \and Marco Servetto\inst{2}}
-\institute{The University of Hong Kong \and Victoria University of Wellington \\ \email{ylwang@cs.hku.hk, hyzhang@cs.hku.hk, bruno@cs.hku.hk, marco.servetto@ecs.vuw.ac.nz}}
+\institute{The University of Hong Kong \and Victoria University of Wellington \\ \email{\{ylwang,hyzhang,bruno\}@cs.hku.hk, marco.servetto@ecs.vuw.ac.nz}}
 
@@
 
+\newpage
 \bibliographystyle{splncs03}

### 2017-10-20 NewVersion/sections/Overview.tex

@@
 \vspace{3pt}\begin{lstlisting}[style=reduction, escapechar=\%]
-   %\underline{new DrawableSafeDeck()}%.shuffleAndDraw()
--> %\underline{new DrawableSafeDeck().shuffle()}%, new DrawableSafeDeck().draw()
--> ... -> (some steps omitted here)
--> 
--> ..., ambiguous call!!!
+   %new DrawableSafeDeck()%.shuffleAndDraw()
+-> %new DrawableSafeDeck().shuffle()%; new DrawableSafeDeck().draw()
+-> ...
+-> %new DrawableSafeDeck().draw()%
+-> ambiguous call!!!
 \end{lstlisting}\vspace{3pt}

### 2017-10-20 NewVersion/sections/Overview.tex
Polish

--- 2017-10-20 NewVersion/sections/Overview.tex
@@
 This section illustrates the problem of unintentional method conflicts,
-together with the features of our model on addressing this issue, by
+together with the features of our model for addressing this issue, by
 a simple running example. In the following text we will introduce three
@@
 In our language, the main program is merely an expression. The above cast indicates
-that we expect to invoke the \lstinline|draw| from branch
+that we expect to invoke the \lstinline|draw| from the branch
 \lstinline|Deck|. Similarly we could have used an upcast to \lstinline|Drawable|
@@
 -> %new DrawableSafeDeck().draw()%
--> ambiguous call!!!
+-> <<error: ambiguous call!!!>>
 \end{lstlisting}\vspace{3pt}
@@
 a value. Instead an expression of the form \lstinline|new C()| is reduced to
-\lstinline|(C) new C()|, which is a value in \MIM{}. This rule is
+\lstinline|(C) new C()|, which is a value in \MIM{} and where the type
+in the cast denotes the static type of the expression. This rule is
 applied in the first reduction step. 
@@
 method used
-for method dispatching. 
+for method dispatching, and the static type is changed to that. 
 %The static type information about the origin
@@
 specific version of \lstinline|draw| in \lstinline|SafeDeck|. In this
-reduction, the cast that tracks the origin of
-\lstinline|shuffleAndDraw| is crutial to unambiguously find the
+sequence of
+reduction steps, the cast that tracks the origin of
+\lstinline|shuffleAndDraw| is crucial to unambiguously find the
 correct implementation of \lstinline|draw|.

### 2017-10-20 NewVersion/sections/Discussion.tex
discussion

@@
 Our formalization has a simple form of abstract methods, which behave similarly to conventional methods with respect to conflicts.
-Other languages may support more complicated behaviors.
+Other languages may support different behaviors.
 For instance, in Java 8 when putting two identical abstract methods together by multiple inheritance, there is no conflict error.
-In Figure~\ref{fig:abstractdiamond}, we use italic $m$ to denote abstract methods.
-For both cases, the Java compiler automatically merges conflicting $m$ in $C$.
-In contrast, \MIM{} distinguishes $A.m$ and $B.m$ in triangle inheritance (left), and rejects the diamond inheritance (right).
-There are two reasons.
-Firstly, our formalization just treats abstract methods as concrete methods with an empty body, and that simplifies
-the rules and the proof a lot.
-Secondly, we distinguish and treat differently on the conflicting methods, since they may represent different operations, even if they are abstract.
+In Figure~\ref{fig:abstractdiamond}, we use italic $\emph{m}$ to denote abstract methods.
+In both cases, the Java compiler accepts the definition of $C$ and automatically merges the two inherited methods $m$ into a single one.
+\MIM{} behaves differently from Java in both cases.
+In the triangle inheritance case (left) $C$ will have two distict abstract methods corresponding to $A.m$ and $B.m$. 
+In the diamond inheritance case the definition of $C$ is rejected. 
+There are two reasons for this difference in behaviour. Firstly, our formalization just treats abstract methods as concrete methods with an empty body, and that simplifies
+the rules and proofs a lot.
+Secondly, and more importantly, we distinguish and treat differently conflicting methods, since they may represent different operations, even if they are abstract.
 Thus our model adopts a very conservative behavior rather than automatically merging
-methods. For the diamond case, as we have mentioned, it is actually an intentional conflict due to the same source $T$.
+methods by default (as done in many languages). 
+Arguably, for the diamond case, as we have mentioned, it is actually an intentional conflict due to the same source $T$.
 It is possible to change our model to account for other behaviors for abstract methods, but we view this as a mostly 
@@
 The design of \MIM{} can be viewed as a variant of Java 8 with default methods which allows for unintentional method conflicts.
-Like Java interfaces and traits, state is forbidden in \MIM{} since having state in OO multiple inheritance is a non-trivial issue.
-There has been some related work on it, such as C++ that uses virtual inheritance~\cite{ellis1990annotated}.
+Like Java interfaces and traits, state is forbidden in \MIM{}.
+There are some inheritance models that also account for fields, such as C++ that uses virtual inheritance~\cite{ellis1990annotated}.
 In our model, however, we can perhaps borrow the idea of \textit{interface-based programming}~\cite{classless}, which models state with abstract state operations.
@@
 
-Our language simply rejects the following case of diamond inheritance:
+\MIM{} rejects the following case of diamond inheritance:
 
@@
 We believe that rejecting \lstinline|D| follows the principle of models like traits and Java 8 interfaces, 
-where the language/type-system is meant to alert the programmer for a possible conflict.
+where the language/type-system is meant to alert the programmer for a possible conflict early.
 

### 2017-10-20 NewVersion/sections/Formalization.tex
small fix. to 25pages
discussion

@@
 
+\begin{figure*}[t]
+\saveSpaceFig
+\begin{mathpar}
+	\framebox{$ I <: J $} \hspace{.5in} \subid \\
+	\subtrans \hspace{.5in} \subextends \\
+
+	\framebox{$ \judgeewf \Gamma {e:I} $} \hspace{.5in}
+	\tvar \\
+	\tinvk \\
+	% \tpathinvk \\
+	% \tsuperinvk \\
+	% \tstaticinvk  \\
+	\tnew \\
+	\tanno \\
+	\tmethod \\
+	\tabsmethod \\
+	\tintf
+\end{mathpar}
+\saveSpaceFig
+\caption{Typing and subtyping of \name{}.}
+\label{fig:typingrules}
+\end{figure*}
+
 \subsection{Subtyping and Typing Rules}\label{subsec:typingrules}
@@
 above $I$ and along path/branch $J$''. ``Along path $J$'' additionally requires the result to relate to $J$, that is to say,
-the most specific interface has a subtyping relationship with $J$.
+the most specific interface that has a subtyping relationship with $J$.
 
@@
 
-\begin{figure*}[t]
-\saveSpaceFig
-\begin{mathpar}
-	\framebox{$ I <: J $} \hspace{.5in} \subid \\
-	\subtrans \hspace{.5in} \subextends \\
-
-	\framebox{$ \judgeewf \Gamma {e:I} $} \hspace{.5in}
-	\tvar \\
-	\tinvk \\
-	% \tpathinvk \\
-	% \tsuperinvk \\
-	% \tstaticinvk  \\
-	\tnew \\
-	\tanno \\
-	\tmethod \\
-	\tabsmethod \\
-	\tintf
-\end{mathpar}
-\saveSpaceFig
-\caption{Typing and subtyping of \name{}.}
-\label{fig:typingrules}
-\end{figure*}
-
 \subsection{Small-step Semantics and Congruence}
-Figure~\ref{fig:smallstep} defines the small-step semantic and
+Figure~\ref{fig:smallstep} defines the small-step semantics and
 congruence rules of \MIM{}. When evaluating an expression, they
@@
 \end{comment}
-
-\begin{figure*}[t]
-\saveSpaceFig
-\begin{mathpar}
-	% \sinvk \\
-	\spathinvk \\
-	% \ssuperinvk \\
-	% \sstaticinvk \\
-	\creceiver \hspace{.5in}
-	% \cpathreceiver \\
-	\cargs \\
-	% \cpathargs \\
-	% \csuperargs \\
-	% \cstaticargs \\
-	\cstatictype \\
-	\cfreduce \\
-	\cannoreduce
-\end{mathpar}
-\caption{Small-step semantics.}\label{fig:smallstep}
-\saveSpaceFig
-\end{figure*}
-
-\begin{comment}
-\begin{figure*}[t]
-\begin{mathpar}
-\end{mathpar}
-\caption{Congruence.}\label{fig:congruence}
-\end{figure*}
-\end{comment}

### 2017-10-20 NewVersion/sections/RelatedWork.tex
Polish

@@
 A few language implementations have realized the problem of
-unintentional conflicts and provided some support for it.
+unintentional conflicts and provide some support for it.
 
@@
 \noindent {\bf C++ model.}
-C++ supports a very flexible inheritance model (including basic and
-virtual inheritance). \bruno{what is ``normal'' inheritance?}\yanlin{changed "normal" to "basic", is this ok?}
+C++ supports a very flexible inheritance model.
 C++ allows the existence of unintentional conflicts and users may specify a hierarchical path via casts for disambiguation, as discussed in Section~\ref{sec:overview}. 

### 2017-10-20 NewVersion/sections/RelatedWork.tex
related work, added c++ other formalizations

@@
 hierarchical dispatching, whereas C++ can be viewed as a real-world
-implementation. As far as we know there is no any formal model that
+implementation.
+There are several formalizations~\cite{Wasserrab2006,ramananandro2012mechanized,Ramalingam1997} in the literature modeling C++ various features and give us some inspiration, however, as far as we know, there is no any formal model that
 captures this aspect of the C++ method dispatching model.

### 2017-10-20 NewVersion/sections/RelatedWork.tex
Related

--- 2017-10-20 NewVersion/sections/RelatedWork.tex
@@
 hierarchical dispatching, whereas C++ can be viewed as a real-world
-implementation. As far as we know there is no any formal model that
+implementation. There are several
+formalizations~\cite{Wasserrab2006,ramananandro2012mechanized,Ramalingam1997}
+in the literature modeling various C++ features. However, as far as we know, there is no formal model that
 captures this aspect of the C++ method dispatching model.

### 2017-10-20 NewVersion/sections/Formalization.tex
compress to 25 pages

@@
 receiver. The result of $\mbody$ contains the interface that provides the most specific implementation,
-the parameters and the return type. We use underscore for the return expression, to imply that an empty return expression
-from an abstract method is also acceptable.
+the parameters and the return type. We use underscore for the return expression, implying that an empty return expression
+from an abstract method is acceptable.
 % \textsc{(T-PathInvk)} is the typing judgement for a path invocation.
@@
 %  explaining T-inf.} \yanlin{revised.please check whether you're happy with it.}
-\vspace{3pt}\begin{lstlisting}
+\begin{lstlisting}
 interface T                 { T m() override T { return new T(); } }
@@
 interface C extends A, B {}
-
 ((T) new C()).m()
-\end{lstlisting}\vspace{3pt}
+\end{lstlisting}
 This program does not compile on interface $C$, because of the second condition in \textsc{(T-Intf)}, where $I$ equals $C$ and $J$ equals $T$.
@@
 congruence rules of \MIM{}. When evaluating an expression, they
-are invoked recursively and produce a single value in
+are invoked and produce a single value in
 the end. %\haoyuan{we need to be consistent on paragraph upper/lower case.}

### 2017-10-20 NewVersion/sections/Overview.tex
compress to 25 pages

@@
 
-\vspace{3pt}\begin{lstlisting}
+\begin{lstlisting}
 interface Deck {
@@
 }
-\end{lstlisting}\vspace{3pt}
+\end{lstlisting}
 In \lstinline|Deck|,
@@
 
-\vspace{3pt}\begin{lstlisting}
+\begin{lstlisting}
 interface Deck { void draw() {...} }
@@
 interface DrawableDeck extends Drawable, Deck {}
-
 // main program
@@
 // (new DrawableDeck()).draw()        // this call is ambiguous and rejected
-\end{lstlisting}\vspace{3pt}
+\end{lstlisting}
 In our language, the main program is merely an expression. The above cast indicates
@@
 }
-\end{lstlisting}\vspace{3pt}
+\end{lstlisting}
 Here \lstinline|shuffleAndDraw| \emph{invokes \lstinline|draw| from its own enclosing type}.
@@
 
-\vspace{3pt}\begin{lstlisting}
+\begin{lstlisting}
 interface SafeDeck extends Deck {
@@
 }
-\end{lstlisting}\vspace{3pt}
+\end{lstlisting}
 Without dynamic dispatching, we may have to copy the \lstinline|shuffleAndDraw| code into \lstinline|SafeDeck|, so that \lstinline|shuffleAndDraw| calls the new \lstinline|draw| defined in \lstinline|SafeDeck|.
@@
 
-\vspace{3pt}\begin{lstlisting}
+\begin{lstlisting}
 interface DrawableSafeDeck extends Drawable, SafeDeck {}
@@
 new DrawableSafeDeck().shuffleAndDraw()
-\end{lstlisting}\vspace{3pt}
+\end{lstlisting}
 
@@
 
-\vspace{3pt}\begin{lstlisting}[style=reduction, escapechar=\%]
+\begin{lstlisting}[style=reduction, escapechar=\%]
    %new DrawableSafeDeck()%.shuffleAndDraw()
@@
 -> <<error: ambiguous call!!!>>
-\end{lstlisting}\vspace{3pt}
+\end{lstlisting}
 
@@
 to avoid ambiguity, and the dynamic type finds the most specific implementation on that branch.
-
 To be specific, the following code is accepted by \MIM{}:
-\vspace{3pt}\begin{lstlisting}
+\begin{lstlisting}
 interface Deck {
@@
 new DrawableSafeDeck().shuffleAndDraw() // SafeDeck.draw is called
-\end{lstlisting}\vspace{3pt}
-And the computation performed in \MIM{} is as follows:
-\vspace{3pt}\begin{lstlisting}[style=reduction, escapechar=\%]
+\end{lstlisting}
+
+\noindent The computation performed in \MIM{} is as follows:
+\begin{lstlisting}[style=reduction, escapechar=\%]
    %new DrawableSafeDeck()%.shuffleAndDraw()
@@
 -> ... %// SafeDeck.draw%
-\end{lstlisting}\vspace{3pt}
+\end{lstlisting}
 
@@
 For example, as shown in Figure~\ref{fig:drawablesafedeck}(middle), we define a new component \lstinline|DrawableRect| that extends \lstinline|Drawable|, which simply draws the deck as a rectangle, and modifies the hierarchy:
-\vspace{3pt}\begin{lstlisting}
+\begin{lstlisting}
 interface DrawableRect extends Drawable {
@@
     frame.getContentPane().setBackground(Color.red);
-    frame.getContentPane().add(new Square(10,10,100,100));
-    ....
+    frame.getContentPane().add(new Square(10,10,100,100)); ...
   }
 }
-
 interface DrawableSafeDeck extends DrawableRect, SafeDeck {}
-\end{lstlisting} \vspace{3pt}
+\end{lstlisting}
 This workaround seems to work, but there are severe issues:
@@
 to be overridden on individual branches, and hence offers independent extensibility. The above example can be easily realized by:
-\vspace{3pt}\begin{lstlisting}
+\begin{lstlisting}
 interface DrawableSafeDeck extends Drawable, SafeDeck {
@@
     frame.getContentPane().setBackground(Color.red);
-    frame.getContentPane().add(new Square(10,10,100,100));
-    ...
+    frame.getContentPane().add(new Square(10,10,100,100)); ...
   }
 }
-
 // main program
 ((Drawable)new DrawableSafeDeck()).draw(); // calls the latest draw
-\end{lstlisting}\vspace{3pt}
+\end{lstlisting}
 

### 2017-10-20 NewVersion/sections/RelatedWork.tex
compress to 25 pages

--- 2017-10-20 NewVersion/sections/RelatedWork.tex
@@
 It allows unintentional conflicts and uses static dispatch to resolve them, as discussed in Section~\ref{sec:overview}. For example, given the following code
-\begin{lstlisting}[language=Java]
+\begin{lstlisting}[language=cpp]
 class A { public: void m() {cout << "MA" << endl;} };
@@
 \begin{figure*}[t]
+\saveSpaceFig
 \begin{lstlisting}
@@
 \label{fig:middleman}
+\saveSpaceFig
 \end{figure*}

### 2017-10-20 NewVersion/sections/RelatedWork.tex

@@
 hierarchical dispatching, whereas C++ can be viewed as a real-world
-implementation.
-There are several formalizations~\cite{Wasserrab2006,ramananandro2012mechanized,Ramalingam1997} in the literature modeling C++ various features and give us some inspiration, however, as far as we know, there is no any formal model that
+implementation. There are several
+formalizations~\cite{Wasserrab2006,ramananandro2012mechanized,Ramalingam1997}
+in the literature modeling various C++ features. However, as far as we know, there is no formal model that
 captures this aspect of the C++ method dispatching model.

### 2017-10-20 NewVersion/sections/Overview.tex
Section 2

--- 2017-10-20 NewVersion/sections/Overview.tex
@@
 
-\subsection{Problem 1: Unintentional Method Conflicts}\label{subsec:problem1}
+\subsection{Problem 1: Basic Unintentional Method Conflicts}\label{subsec:problem1}
 Suppose that two components \lstinline|Deck| and \lstinline|Drawable| 
@@
 In our language, the main program is merely an expression. The above cast indicates
-that we expect to invoke the \lstinline|draw| from the branch
+that we expect to invoke the \lstinline|draw| method from the branch
 \lstinline|Deck|. Similarly we could have used an upcast to \lstinline|Drawable|
@@
 
-Notably, we track the static types by adding casts. In contrast to FJ,
+Notably, we track the static types by adding upcasts during reduction. In contrast to FJ,
 where \lstinline|new C()| is a value, in \MIM{} such expression is not 
@@
 in the cast denotes the origin of the \lstinline|shuffleAndDraw|
-method used
+method (discovered during method lookup) used
 for method dispatching, and the static type is changed to that. 

### 2017-10-20 NewVersion/paper.tex

@@
 	keywordstyle=\sffamily\bfseries,
-	aboveskip=0pt,
-	belowskip=0pt
+	aboveskip=3pt,
+	belowskip=3pt
 	% commentstyle=\color{Gray},

### 2017-10-20 NewVersion/sections/Auxiliary.tex
small fix. to 25pages
added missing figure and small fix

@@
 
+\saveSpaceFig
 \begin{flalign*}
@@
 \end{flalign*}
+\saveSpaceFig
+
 To calculate $\mbody(m, I_d, I_s)$, the invocation of $\mostSpecific$ looks for the most specific original methods and their interfaces, and expects a singleton set, so as to avoid unambiguity.
@@
 And finally the target method is returned.
+
+\begin{figure*}[t]
+\saveSpaceFig
+\begin{mathpar}
+	% \sinvk \\
+	\spathinvk \\
+	% \ssuperinvk \\
+	% \sstaticinvk \\
+	\creceiver \hspace{.5in}
+	% \cpathreceiver \\
+	\cargs \\
+	% \cpathargs \\
+	% \csuperargs \\
+	% \cstaticargs \\
+	\cstatictype \\
+	\cfreduce \\
+	\cannoreduce
+\end{mathpar}
+\caption{Small-step semantics.}\label{fig:smallstep}
+\saveSpaceFig
+\end{figure*}
 
@@
 \end{itemize}
+\saveSpaceFig
 
@@
 \end{flalign*}
+\saveSpaceFig
+
 By the definition, an interface belongs to $\mostSpecificOverride(m, I, J)$ if and only if:
@@
 %%%%============================ prune(set) ================%%%%%%%%
+\saveSpaceFig
 \begin{flalign*}
@@
 \end{flalign*}
+
 The $\prune$ function takes a set of
@@
 %%%%============================ canOverride ================%%%%%%%%
+\saveSpaceFig
 \begin{flalign*}
@@
 \end{flalign*}
+\saveSpaceFig
 $\canOverride$ just checks that two original $m$ in $I$ and $J$ have the same type.
@@
 %%%%============================ canInstantiate ================%%%%%%%%
+\saveSpaceFig
 \begin{flalign*}
@@
 \end{flalign*}
+
 $\canInstantiate(I)$ checks whether interface $I$ can be instantiated by the keyword $\kwnew$.

### 2017-10-20 NewVersion/sections/Discussion.tex

@@
 \begin{figure*}[t]
+\saveSpaceFig
     % \nocaptionrule
@@
         \centering
-        \includegraphics[width=2cm]{pics/P7.pdf}
+        \includegraphics[width=1.4cm]{pics/P7.pdf}
     \end{minipage}
@@
         \centering
-        \includegraphics[width=2cm]{pics/P8.pdf}
+        \includegraphics[width=1.2cm]{pics/P8.pdf}
     \end{minipage}  
     \caption{Triangle inheritance (left) and diamond inheritance (right) on abstract methods.}\label{fig:abstractdiamond}
+\saveSpaceFig
 \end{figure*}
@@
 \subsection{Orthogonal \& Non-Orthogonal Extensions}\label{sec:orthoext}
-
 Our model is designed as a minimal calculus for focusing only on resolving unintentional conflicts. Therefore, we have omitted a number of
@@
 \MIM{} rejects the following case of diamond inheritance:
-
-\vspace{3pt}\begin{lstlisting}
+\begin{lstlisting}
 interface A { void m() {...} }
@@
 interface D extends B, C {}
-\end{lstlisting}\vspace{3pt}
+\end{lstlisting}
 Here both $B.m$ and $C.m$ override $A.m$, and D inherits

### 2017-10-20 NewVersion/sections/Overview.tex
Overview

@@
 \lstinline|(Deck) new DrawableSafeDeck()|. Here, the static type used
-in the cast denotes the origin of the \lstinline|shuffleAndDraw|
-method (discovered during method lookup) used
-for method dispatching, and the static type is changed to that. 
+in the cast (\lstinline|Deck|) denotes the origin of the \lstinline|shuffleAndDraw|
+method, which is discovered during method lookup. 
 %The static type information about the origin

### 2017-10-20 NewVersion/sections/Auxiliary.tex
spellcheck, grammar

@@
 In this section, we present the fundamental algorithms and auxiliary
-definitions used in our formalization, and show that the resulting
+definitions used in our formalization and show that the resulting
 calculus is type sound. The functions presented in this section are
@@
 	\item It originally defines $m$;
-	\item It is a super type of $I$ (including $I$);
-	\item It is either a super type or a subtype of $J$ (including $J$);
+	\item It is a supertype of $I$ (including $I$);
+	\item It is either a supertype or a subtype of $J$ (including $J$);
 	\item Any subtype of it does not belong to the same result set because of $\prune$.
@@
 types, and filters out those that have subtypes in the same set. In the returned set,
-none of them has subtyping relation to one another, since all super types have been removed.
+none of them has subtyping relation to one another, since all supertypes have been removed.
 %%%%============================ prune(set) end ================%%%%%%%%

### 2017-10-20 NewVersion/sections/Discussion.tex
spellcheck, grammar

@@
 The formal Featherweight Java model~\cite{Igarashi01FJ} does not include abstract methods because of the orthogonality
-to the core calculus. In traits the
+to the core calculus. In traits, the
 similar idea is to use keywords like ``\textbf{require}'' for abstract method declarations~\cite{scharli03traits}.
@@
 \MIM{} behaves differently from Java in both cases.
-In the triangle inheritance case (left) $C$ will have two distict abstract methods corresponding to $A.m$ and $B.m$. 
-In the diamond inheritance case the definition of $C$ is rejected. 
+In the triangle inheritance case (left) $C$ will have two distinct abstract methods corresponding to $A.m$ and $B.m$. 
+In the diamond inheritance case, the definition of $C$ is rejected. 
 There are two reasons for this difference in behaviour. Firstly, our formalization just treats abstract methods as concrete methods with an empty body, and that simplifies

### 2017-10-20 NewVersion/sections/Formalization.tex
spellcheck, grammar

@@
 Here $\mbody(m, I_0, I_0)$ finds the most specific $m$ above $I_0$. ``Above $I_0$'' specifies
-the search space, namely the super types of $I_0$ including itself.
+the search space, namely the supertypes of $I_0$ including itself.
 For the general case, however, the hierarchical invocation $\mbody(m, I, J)$ finds ``the most specific $m$
@@
 By ``most specific interfaces'',
-it implies that the inherited super types are excluded.
+it implies that the inherited supertypes are excluded.
 Thus the condition $\mostSpecific(m, I, J) = \{J\}$ indicates a characteristic of a hierarchical overriding: it must override an original method; the overriding is direct and there does not exist any other original method $m$ in between.
@@
 $I[m\ \kwoverride\ I]$ is defined if $I$ originally defines $m$, and $\canOverride(m, I, J)$ checks whether $I.m$ has the same type as $J.m$.
-Generally the preservation of method type is required for any super type $J$ and any method $m$.
+Generally the preservation of method type is required for any supertype $J$ and any method $m$.
 
@@
 Parameters are substituted with arguments, and the \lstinline|this| reference is substituted by the receiver,
-and in the meanwhile the static types are recorded via annotations. Finally the return type $I_e$ is put in the front as an annotation.
+and in the meanwhile the static types are recorded via annotations. Finally, the return type $I_e$ is put in the front as an annotation.
 \paragraph{Congruence Rules} \textsc{(C-Receiver)}, \textsc{(C-Args)} and \textsc{(C-FReduce)} are natural congruence rules

### 2017-10-20 NewVersion/sections/Overview.tex
spellcheck, grammar

@@
 that we expect to invoke the \lstinline|draw| method from the branch
-\lstinline|Deck|. Similarly we could have used an upcast to \lstinline|Drawable|
+\lstinline|Deck|. Similarly, we could have used an upcast to \lstinline|Drawable|
 to call the \lstinline|draw| method from \lstinline|Drawable|.
 Without the cast, the call would be ambiguous and
-\MIM{}'s type system would reject that call.
+\MIM{}'s type system would reject it.
 
@@
 
-\noindent Indeed, using the a reduction model similar to FJ~\cite{Igarashi01FJ} (without static types tracked), the reduction steps would roughly be:
+\noindent Indeed, using a reduction model similar to FJ~\cite{Igarashi01FJ} (without static types tracked), the reduction steps would roughly be:
 
@@
 dispatching that we call \textit{hierarchical dispatching}. In
-hierarchical dispatching both the static and dynamic type information 
+hierarchical dispatching, both the static and dynamic type information 
 are used to select the right method implementation.
@@
 where \lstinline|new C()| is a value, in \MIM{} such expression is not 
-a value. Instead an expression of the form \lstinline|new C()| is reduced to
+a value. Instead, an expression of the form \lstinline|new C()| is reduced to
 \lstinline|(C) new C()|, which is a value in \MIM{} and where the type
@@
 ``finding the most specific \lstinline|draw| above \lstinline|DrawableSafeDeck| and along path \lstinline|Deck|''.
-The meaning of ``above \lstinline|DrawableSafeDeck|'' implies its super types, and ``along path
+The meaning of ``above \lstinline|DrawableSafeDeck|'' implies its supertypes, and ``along path
 \lstinline|Deck|'' specifies the branch. Finally, in the last
@@
 complicated because different, separate, conflicting methods can coexist
-in one class. Ideally we would like to support overriding for those
+in one class. Ideally, we would like to support overriding for those
 methods too, in exactly the same way that overriding is available for 
-other (non-conflicting) methods. However we need to be able to
+other (non-conflicting) methods. However, we need to be able to
 override the individual conflicting methods, rather than overriding all
@@
 Suppose that the programmer defines a new interface \lstinline|DrawableSafeDeck| (based on the code in Section~\ref{subsec:problem2} without the old \lstinline|DrawableSafeDeck|), but he needs to override
-\lstinline|Drawable.draw| and give a new implementation of drawing, so that the deck can indeed be visualized on the canvas.
+\lstinline|Drawable.draw| and give a new implementation of drawing so that the deck can indeed be visualized on the canvas.
 
@@
 	\item Separate overriding is required to come after the triangle
-          inheritance, especially when the implementation needs functionality from both parents. In the above code we have assumed
+          inheritance, especially when the implementation needs functionality from both parents. In the above code, we have assumed
 	that the overriding is unrelated to \lstinline|Deck|. But when the drawing relies on some information of the \lstinline|Deck|
-	object, we have to either introduce field methods for delegation, or change the signature of \lstinline|draw| to take a parameter.
+	object, we have to either introduce field methods for delegation or change the signature of \lstinline|draw| to take a parameter.
 	Either way introduces unnecessary complexity and affects extensibility.
@@
 \paragraph{\MIM{}'s solution:} An additional feature of our model is \textit{hierarchical overriding}. It allows conflicting methods
-to be overridden on individual branches, and hence offers independent extensibility. The above example can be easily realized by:
+to be overridden on individual branches, hence offers independent extensibility. The above example can be easily realized by:
 \begin{lstlisting}
@@
 
-\paragraph{Terminology:} In \lstinline|Drawable|, \lstinline|Deck| and \lstinline|SafeDeck|, the \lstinline|draw| methods are called \textit{original methods} in this paper, because they are originally defined by the interfaces.
+\paragraph{Terminology:} In \lstinline|Drawable|, \lstinline|Deck|, and \lstinline|SafeDeck|, the \lstinline|draw| methods are called \textit{original methods} in this paper, because they are originally defined by the interfaces.
 In contrast, \lstinline|DrawableSafeDeck| defines a \textit{hierarchical overriding method}.
@@
 (c) represents hierarchical overriding.
-(d) and (e) are two base cases of diamond inheritance in \MIM{}, and the definition of each $C$ is rejected because $T$ is an ambiguous parent to $C$.
+(d) and (e) are two base cases of diamond inheritance in \MIM{} and the definition of each $C$ is rejected because $T$ is an ambiguous parent to $C$.
 (f) gives a common solution to the diamond as in Java or traits, which is to explicitly override $A.m$ and $B.m$ in $C$.

### 2017-10-20 NewVersion/sections/RelatedWork.tex
spellcheck, grammar

@@
 Class \texttt{MiddleMan}, as its name suggests, acts as a middle man between its class \texttt{C} and its parents \texttt{A, B}.
-\texttt{MiddleMan} defines a virtual method \texttt{m} that overrides a parent method \texttt{m} and delegates the implementation to another method \texttt{m\_impl} that takes $\kwthis$ as parameter.
+\texttt{MiddleMan} defines a virtual method \texttt{m} that overrides a parent method \texttt{m} and delegates the implementation to another method \texttt{m\_impl} that takes $\kwthis$ as a parameter.
 C++ supports method overloading, so that multiple \texttt{m\_impl} methods with different parameter types can coexist.

### 2017-12-07 NewVersion/sections/Auxiliary.tex
uncommitted stuff

@@
 We present the type soundness of the model by a few theorems below, following the standard technique of
-subject reduction and progress proposed by Wright and Felleisen~\cite{Wright1994}. The proof, together with some lemmas, are
+subject reduction and progress proposed by Wright and Felleisen~\cite{Wright1994}. The proof, together with some lemmas, is presented 
 in Appendix. Type soundness states that if an expression is well-typed, then after many reduction
@@
 
-Our theorems are stricter than those of Featherweight Java~\cite{Igarashi01FJ}. Specifically, in both term substitution (a lemma in Appendix)
-and subject reduction, reduction may lead to a term with a subtype in
-FJ, but in \MIM{} types are unchanged. The difference is due to
-%%subtyping; the parameter or \lstinline|this| reference requires some type $I$, but a value with a more specific type,
-%%which is subtype of $I$, can be passed. However, as 
-the fact that \MIM{} keeps track of the static types during
+Our theorems are stricter than those of Featherweight Java~\cite{Igarashi01FJ}. In FJ, the subject reduction theorem states that 
+after a step of reduction, the type of an expression may change to a subtype due to subtyping. However, in \MIM{}, 
+the type remains unchanged because we keep track of the static types and use them for casting during
 reduction.
-In FJ, the information about the static types is lost.
 

### 2017-12-08 NewVersion/response.txt
separate response

We thank the reviewers for the valuable comments. We try to address the reviews one by one.

Reviewer A.
- generalize the method overriding semantics
We think this suggestion is useful and valueble, we didn't think about this before. It does produce a
simpler method overriding semantics and definitely can be a future work.

- "renaming can break the subtyping relation"
Naturally renaming can break the subtyping relation, of course, there might be techniques as you said 
that tracks the rename mapping and keeps the subtyping relation, but that's the special case and we 
didn't discuss it in the paper.

- "you do not mention the more direct way in which C++ allows disambiguating methods by qualification..."
In Section 2.1 we have mentioned the C++ qualified name approach, see Sec 2.1 -> Potential Fixes -> 
Static dispatch.

- "C++ allows both overriding and shadowing ..."
Since FHJ does not support overloading, it's model is much simpler than C++, so there's no concern 
of distinguishing overriding and shadowing of inherited methods. But we agree that it could be interesting
to add this feature.

- "the notion of 'original' method...."
Sorry that we didn't make it clear. The term "original method" is supposed to be relative to
"hierarchical overriding method". It does include overrides and maybe a better name (for example
"own method"?) is needed.

- "abusing override self syntax for non-(hierarchical-)override...can be empty?..."
Yes, `I { m() }` is a syntactic sugar for `I { m() override I ... }`. In a real language, this should be 
supported. But in formlization, for simplicity, we union them into one.

- Footnote 4: “new I()()” — macro fail?
For footnote 4, the version submitted is "In Java the corresponding syntax is new I(){}." Maybe the 
version you have is not updated?

- "Figure 6: The rule C-StaticType renders the reduction relation non-deterministic"
Without (C-FReduce), (C-StaticType) IS infinite. But in (C-FReduce), the condition `e \neq new J()`
prevent the infinite loop.

Reviewer B.
- "Eiffel seems to allow renaming ..."
In Eiffel, programmers still have to rename methods to resolve the conflicts, so I don't think it is a 
different approach and actually you can't keep the method with the SAME name.

> MiddleMan approach, "whether this problem is really worth a language extension..."
The example in "The C++ programming language" and stackoverflow are both similar to the MiddleMan
approach (they have the same spirit, just MiddleMan approach uses parameter types to distinguish
different methods, while the others use separate sets of methods to distinguish).
We agree that this name conflict problem is not quite popular in practice. That's also the reason
why we do not have a big case study in the paper, because we didn't find a senario that
unintentional method conflicts are frequently used in one project.   But once this issue is
encountered, the effect could be severe, and that existing workarounds might not help a lot. And
since the C++ books, the trait paper as well as other papers mentioned this issue, it might be a
sign that this problem is still an interesting issue in certain cases, which worth exploring and
taking into consideration.  Finally our work shows that this feature is lightweight, it does not
complicate the semantics a lot and can be easily added to language models.

- "It would strengthen your paper if you would provide an implementation..."
As mentioned in Section 1, we have a prototype implementation available here: 
https://github.com/YanlinWang/MIM/tree/master/Calculus

- "What has been removed from FJ: just downcasts?"
Also constructors and fields.

- "5.2: static invocation confusing..."
* "the method m in J_0 that hierarchically overrides J_1" means, the method m defined like this:
interface J_0 { K m() override J_1 { ... } }
* "e1.J_0@J_1 :: m(e2)" is different from "((J1) e1.m(e2)". The first is a static call while the
second dynamic. The result would be different when the method m gets overridden in an heir of J_0.
* For the question "whether it should be forbidden", we think it is a design choice. If the user
makes  a normal e.m() call, for sure it wouldn't access the super methods. But the static invocation
here gives users the freedom to directly call super methods.

- "p.22: "It breaks structural subtyping.."

Review C.
- "The proposal seems unnecessarily complex. In NextGen and MixGen ..."

- "what do you mean by 'reduction model similar to FJ'?"
Sorry for the English, what we mean is that the reduction steps follow the reduction rules in FJ-like
languages, where no static types are tracked.

- "you mention for the first time 'origin'..."
On page 8, "origin" means where the method is defined, we avoid using "original methods" because it
it not introduced yet on page 8. "original method" is a relative concept to hierarchical overriding 
methods.

- "Section 3.2: subtyping is ANTIsymmetric."
Yes, it is not symmetric, we will delete it.

### 2017-12-08 NewVersion/response.txt
refined

@@
 - "The proposal seems unnecessarily complex. In NextGen and MixGen ..." 
+Thanks for the references, we need to add them. The models in these references also show that the
+static types can be utilized for method dispatch, which is similar to C++. But the complexity of our
+model mainly comes from the feature of hierarchical overriding, which is not introduced by previous
+papers. We believe that such complexity can simplify the client code written by programmers.
 

### 2017-12-08 NewVersion/response.txt
Some tweaks

@@
 - generalize the method overriding semantics
-We think this suggestion is useful and valueble, we didn't think about this before. It does produce a
+
+We think this suggestion is useful and valuable, we didn't think about this before. It does produce a
 simpler method overriding semantics and definitely can be a future work.
@@
 - "renaming can break the subtyping relation"
-Naturally renaming can break the subtyping relation, of course, there might be techniques as you said 
-that tracks the rename mapping and keeps the subtyping relation, but that's the special case and we 
-didn't discuss it in the paper.
+
+We are curious to know if the reviewer has a reference to some work
+that tracks the name remapping to preserve the subtyping relation.
+It is not obvious to us that this would work smoothly. A reference
+would be highly appreciatted.
 
@@
 - "C++ allows both overriding and shadowing ..."
-Since FHJ does not support overloading, it's model is much simpler than C++, so there's no concern 
+Since FHJ does not support overloading, it's model is simpler than C++, so there's no concern 
 of distinguishing overriding and shadowing of inherited methods. But we agree that it could be interesting
 to add this feature.
-
-- "the notion of 'original' method...."
-Sorry that we didn't make it clear. The term "original method" is supposed to be relative to
-"hierarchical overriding method". It does include overrides and maybe a better name (for example
-"own method"?) is needed.
 
@@
 
-- Footnote 4: “new I()()” — macro fail?
-For footnote 4, the version submitted is "In Java the corresponding syntax is new I(){}." Maybe the 
-version you have is not updated?
-
 - "Figure 6: The rule C-StaticType renders the reduction relation non-deterministic"
 Without (C-FReduce), (C-StaticType) IS infinite. But in (C-FReduce), the condition `e \neq new J()`
-prevent the infinite loop.
+prevents the infinite loop.
 
@@
 different methods, while the others use separate sets of methods to distinguish).
-We agree that this name conflict problem is not quite popular in practice. That's also the reason
-why we do not have a big case study in the paper, because we didn't find a senario that
-unintentional method conflicts are frequently used in one project.   But once this issue is
+We agree that this name conflict problem is not quite popular in practice. But once this issue is
 encountered, the effect could be severe, and that existing workarounds might not help a lot. And
 since the C++ books, the trait paper as well as other papers mentioned this issue, it might be a
-sign that this problem is still an interesting issue in certain cases, which worth exploring and
-taking into consideration.  Finally our work shows that this feature is lightweight, it does not
+sign that this problem is still an interesting issue in certain cases,
+which is worth exploring and taking into consideration.  Finally our work shows that this feature is lightweight, it does not
 complicate the semantics a lot and can be easily added to language models.

### 2017-12-19 NewVersion/response.txt
uncommitted final response

@@
 Reviewer A.
+
 - generalize the method overriding semantics
@@
 - "you do not mention the more direct way in which C++ allows disambiguating methods by qualification..."
+
 In Section 2.1 we have mentioned the C++ qualified name approach, see Sec 2.1 -> Potential Fixes -> 
@@
 - "C++ allows both overriding and shadowing ..."
+
 Since FHJ does not support overloading, it's model is simpler than C++, so there's no concern 
@@
 - "abusing override self syntax for non-(hierarchical-)override...can be empty?..."
+
 Yes, `I { m() }` is a syntactic sugar for `I { m() override I ... }`. In a real language, this should be 
@@
 - "Figure 6: The rule C-StaticType renders the reduction relation non-deterministic"
+
 Without (C-FReduce), (C-StaticType) IS infinite. But in (C-FReduce), the condition `e \neq new J()`
@@
 Reviewer B.
+
 - "Eiffel seems to allow renaming ..."
+
 In Eiffel, programmers still have to rename methods to resolve the conflicts, so I don't think it is a 
@@
 
-> MiddleMan approach, "whether this problem is really worth a language extension..."
+- MiddleMan approach, "whether this problem is really worth a language extension..."
+
 The example in "The C++ programming language" and stackoverflow are both similar to the MiddleMan
@@
 - "It would strengthen your paper if you would provide an implementation..."
+
 As mentioned in Section 1, we have a prototype implementation available here: 
@@
 - "What has been removed from FJ: just downcasts?"
+
 Also constructors and fields.
@@
 - "5.2: static invocation confusing..."
+
 * "the method m in J_0 that hierarchically overrides J_1" means, the method m defined like this:
@@
 
-- "p.22: "It breaks structural subtyping.."
+Review C.
 
-Review C.
 - "The proposal seems unnecessarily complex. In NextGen and MixGen ..."
+
 Thanks for the references, we need to add them. The models in these references also show that the
@@
 - "what do you mean by 'reduction model similar to FJ'?"
+
 Sorry for the English, what we mean is that the reduction steps follow the reduction rules in FJ-like
@@
 - "you mention for the first time 'origin'..."
+
 On page 8, "origin" means where the method is defined, we avoid using "original methods" because it
@@
 - "Section 3.2: subtyping is ANTIsymmetric."
+
 Yes, it is not symmetric, we will delete it.

### 2017-12-19 ECOOP18/lipics-v2016-sample-article.tex
ECOOP format

\documentclass[a4paper,english]{lipics-v2016}
%This is a template for producing LIPIcs articles. 
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
% for section-numbered lemmas etc., use "numberwithinsect"

\usepackage{microtype}%if unwanted, comment out or use option "draft"

%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

\bibliographystyle{plainurl}% the recommended bibstyle

% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{A Sample Article for the LIPIcs series\footnote{This work was partially supported by someone.}\footnote{A full version of the paper is available at \cite{DBLP:journals/cacm/Knuth74}, \url{XXX}}}
\titlerunning{A Sample LIPIcs Article} %optional, in case that the title is too long; the running title should fit into the top page column

%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
\author[1]{John Q. Open}
\author[2]{Joan R. Access}
\affil[1]{Dummy University Computing Laboratory, Address/City, Country\\
  \texttt{open@dummyuniversity.org}}
\affil[2]{Department of Informatics, Dummy College, Address/City, Country\\
  \texttt{access@dummycollege.org}}
\authorrunning{J.\,Q. Open and J.\,R. Access} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

\Copyright{John Q. Open and Joan R. Access}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\subjclass{Dummy classification -- please refer to \url{http://www.acm.org/about/class/ccs98-html}}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
\keywords{Dummy keyword -- please provide 1--5 keywords}% mandatory: Please provide 1-5 keywords
% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Acces}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
% Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

\begin{abstract}

 \end{abstract}

\section{Typesetting instructions -- please read carefully}

%%
%% Bibliography
%%

%% Please use bibtex,

\bibliography{lipics-v2016-sample-article}

\end{document}

### 2017-12-19 ECOOP18/paper.tex
ECOOP format

--- 2017-10-20 NewVersion/paper.tex
@@
-\documentclass{llncs}
-\pagestyle{plain}
+\documentclass[a4paper,english]{lipics-v2016}
+%This is a template for producing LIPIcs articles. 
+%See lipics-manual.pdf for further information.
+%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
+%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
+% for section-numbered lemmas etc., use "numberwithinsect"
 
+\usepackage{mathtools} % For \Coloneqq
+
+\usepackage{microtype}%if unwanted, comment out or use option "draft"
 \usepackage{listings}
@@
 \usepackage{color}
-% \usepackage{amsthm}
-% \usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{amsmath}
 \usepackage{stmaryrd}
@@
 
-\let\proof\relax
-\let\endproof\relax
+% \let\proof\relax
+% \let\endproof\relax
 \let\mathpar\relax
@@
 
+%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
+
+\bibliographystyle{plainurl}% the recommended bibstyle
+
+% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\title{FHJ: A Formal Model for Hierarchical Dispatching and Overriding}
+%\titlerunning{A Sample LIPIcs Article} %optional, in case that the title is too long; the running title should fit into the top page column
+
+%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
+
+\author[1]{John Q. Open}
+\author[2]{Joan R. Access}
+\affil[1]{Dummy University Computing Laboratory, Address/City, Country\\
+  \texttt{open@dummyuniversity.org}}
+\affil[2]{Department of Informatics, Dummy College, Address/City, Country\\
+  \texttt{access@dummycollege.org}}
+\authorrunning{J.\,Q. Open and J.\,R. Access} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'
+
+\Copyright{John Q. Open and Joan R. Access}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+
+\subjclass{Dummy classification -- please refer to \url{http://www.acm.org/about/class/ccs98-html}}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html .
+E.g., cite as "F.1.1 Models of Computation".
+\keywords{Dummy keyword -- please provide 1--5 keywords}% mandatory: Please provide 1-5 keywords
+% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\EventEditors{John Q. Open and Joan R. Acces}
+\EventNoEds{2}
+\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
+\EventShortTitle{CVIT 2016}
+\EventAcronym{CVIT}
+\EventYear{2016}
+\EventDate{December 24--27, 2016}
+\EventLocation{Little Whinging, United Kingdom}
+\EventLogo{}
+\SeriesVolume{42}
+\ArticleNo{23}
+% Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}
 
-% \title{Untangling Unintended Conflicts with Hierarchical Dispatch}
-% \title{FHJ: A Formal Model for Resolving Unintended Conflicts in Multiple Inheritance}
-\title{FHJ: A Formal Model for Hierarchical Dispatching and Overriding}
-%\subtitle{\InterfaceBased Programming for the Masses}
-
-% \authorinfo{NoAuthor}
-%            {The University of Hong Kong, China}
-% %           {\{ylwang,hyzhang,bruno\}@cs.hku.hk}
-% %\authorinfo{Marco Servetto}
-% %          {Victoria University of Wellington, New Zealand}
-% %          {marco.servetto@ecs.vuw.ac.nz}
-\author{Yanlin Wang\inst{1} \and Haoyuan Zhang\inst{1} \and Bruno C.d.S. Oliveira\inst{1} \and Marco Servetto\inst{2}}
-\institute{The University of Hong Kong \and Victoria University of Wellington \\ \email{\{ylwang,hyzhang,bruno\}@cs.hku.hk, marco.servetto@ecs.vuw.ac.nz}}
-
 \maketitle
-
-\vspace{-4ex}
 
@@
 
-\begin{comment}
-\section*{Acknowledgments}\label{sec:Acknowledgments}
+%%
+%% Bibliography
+%%
 
-Authors would like to thank YYYYY.
-\end{comment}
+%% Please use bibtex,
 
-% \newpage
-% \clearpage
-% \bibliographystyle{abbrvnat}
-
-\newpage
-\bibliographystyle{splncs03}
 \bibliography{paper}
-
-\newpage
 \appendix
-\input{sections/Appendix.tex}
-% \input{sections/Appendix_Formalization.tex}
-% \input{sections/Translation.tex}
-% \input{sections/Appendix_Translation.tex}
+%\input{sections/Appendix.tex}
 

### 2017-12-19 ECOOP18/sections/Introduction.tex
ECOOP format

--- 2017-10-18 NewVersion/sections/Introduction.tex
@@
 is \textit{unintentional method conflicts}~\cite{scharli03traits}. In
-such a case conflicting 
+this case, conflicting 
 methods do not actually refer to the same feature. 
@@
 Some other workarounds or approaches include delegation and
-renaming/exclusion in the trait model. However renaming/exclusion 
+renaming/exclusion in the trait model. However, renaming/exclusion 
 can break the subtyping relation between a subclass and its parent.
@@
 diagram with the notation
-\lstinline|draw()|$\shneg$\lstinline|Drawable|, expressing that the \lstinline|draw| method from \lstinline|Drawable|
+\lstinline|draw()|$\uparrow$\lstinline|Drawable|, expressing that the \lstinline|draw| method from \lstinline|Drawable|
 is overridden. Although in this example only one of the
@@
 \begin{itemize}
-	\item \textbf{A formalization of a hierarchical dispatching algorithm} that integrates both the static type and dynamic type for method dispatch, and 
+	\item \textbf{A formalization of the hierarchical dispatching algorithm} that integrates both the static type and dynamic type for method dispatch, and 
 	ensures unambiguity as well as extensibility in the presence
@@
 	\item \textbf{Prototype implementation\footnote{https://github.com/YanlinWang/MIM/tree/master/Calculus}:} a
-          simple implementation of \MIM{} interpreter in Scala. The implementation can type-check and run the variants
+          simple implementation of \MIM{} interpreter in Scala. The implementation can type-check and run variants
           of all the examples shown in this paper.

### 2018-01-09 ECOOP18/sections/Formalization.tex
ECOOP format
Fix review comments

--- 2017-10-20 NewVersion/sections/Formalization.tex
@@
 \kwoverride{} keyword for two cases: if the overridden interface is exactly the enclosing
-interface itself, then such a method is seen as originally defined; otherwise it is a hierarchical overriding method. The definition
+interface itself, then such a method is seen as originally defined; otherwise it is a hierarchical overriding method. 
+Note that in an interface $J$, $\method{I}{m}{I_x}{x}{J}{e} $ is a syntactic sugar for $
+I \; m(\overline{I_x} \; \overline{x}) \; {\{} \kwreturn \; e ; {\}} $, which is the standard way of method definition in Java-like languages. The definition
 of abstract methods is written as $\absmethod{I}{m}{I_x}{x}{J}$, which is
@@
 \saveSpaceFig
-\caption{Typing and subtyping of \name{}.}
+\caption{Subtyping and Typing Rules of \name{}.}
 \label{fig:typingrules}
@@
 In short, subtyping relations are built from the inheritance in interface
-declarations. Subtyping is both symmetric, reflexive and transitive.
+declarations. Subtyping is both reflexive and transitive.
 

### 2018-01-09 ECOOP18/sections/Introduction.tex
Fix review comments

@@
 and mixins~\cite{bracha90mixin,Flatt1998,van1996encapsulation,Ancona2003,Hendler86} to offer a disciplined form of multiple inheritance. Java 8 
-offers a simple variant of traits, disguised of interfaces with default methods~\cite{goetz12fdefenders}.
+offers a simple variant of traits, disguised as interfaces with default methods~\cite{goetz12fdefenders}.
 
@@
 introduced by multiple inheritance. One case is the famous
-\textit{diamond problem}~\cite{Sak89dis,Singh1995} (also known as ``fork-join inheritance''~\cite{Sak89dis}). 
+\textit{diamond problem}~\cite{Sak89dis,Singh1995} (also known as 
+\emph{fork-join inheritance}~\cite{Sak89dis}). 
 In the diamond problem, inheritance allows

### 2018-01-09 ECOOP18/sections/Overview.tex
Fix review comments

--- 2017-10-20 NewVersion/sections/Overview.tex
@@
 In the rest of the paper, we use a Java-like syntax for programs. All types are defined with the keyword
-``\lstinline|interface|''; the concept is closely related to Java 8
+\lstinline|interface|; the concept is closely related to Java 8
 interfaces with default methods~\cite{bono14} and traits. In short, 
@@
 
-\noindent Indeed, using a reduction model similar to FJ~\cite{Igarashi01FJ} (without static types tracked), the reduction steps would roughly be:
+\noindent Indeed, using reduction steps following the reduction rules in FJ~\cite{Igarashi01FJ}-like languages, where no static types are tracked, the reduction steps would roughly be:
 

### 2018-01-09 ECOOP18/sections/RelatedWork.tex
Fix review comments

--- 2017-10-20 NewVersion/sections/RelatedWork.tex
@@
 We describe related work in four parts. We first discuss mainstream popular multiple 
-inheritance models and the specific models (C++ and \csharp) which are closest to our work. Then we 
+inheritance models and then some specific models (e.g., C++ and \csharp) which are closest to our work. Then we 
 discuss related techniques used in \self. Finally, we discuss the foundation and related work of our formalization.
@@
 C++ allows the existence of unintentional conflicts and users may specify a hierarchical path via casts for disambiguation, as discussed in Section~\ref{sec:overview}. 
-With virtual methods, dynamic dispatch is used and 
+With virtual methods, dynamic dispatch is used and the 
 method lookup algorithm will find the most specific method definition. 
@@
 Although C++ supports hierarchical dispatching, it does not support
-hierarchical overriding.  However, there is a possible
-workaround\footnote{https://stackoverflow.com/questions/44632250/can-i-do-mimic-things-likes-this-partial-override-in-c} that mimicks hierarchical
-overriding.  We call it the \emph{MiddleMan} approach, as shown in
+hierarchical overriding.  However, there are some possible
+workarounds that can mimick hierarchical
+overriding, including the \emph{MiddleMan} approach\footnote{\url{https://stackoverflow.com/questions/44632250/can-i-do-mimic-things-likes-this-partial-override-in-c}}, the \emph{interface classes} pattern as described in Section 25.6 of~\cite{stroustrup1995}, the \emph{LotterySimulation} discussion in~\cite{stroustrup1994design}.
+Since these workarounds share the same spirit, we will discuss in detail the \emph{MiddleMan} approach, with code shown in
 Figure~\ref{fig:middleman}. In this example, classes \texttt{A} and
@@
 
-\noindent  {\bf \csharp{} Explicit method implementations.}
+\noindent  {\bf \csharp{} explicit method implementations.}
 Explicit method implementations is a special feature supported by
@@
 overriding of those methods is not possible in subclasses.
+
+\noindent  {\bf Languages using hygienicity.}
+In NextGen/MixGen~\cite{Allen:2003:FAG:949305.949316}, HygJava~\cite{kusmierek2007hygienic} and Magda~\cite{Bono:2012:MNL:2367163.2367198}, \emph{hygienicity} is proposed to deal with unintentional method conflicts, which is basically giving a method a unique identifier by prefixing the name with an unambiguous path.
+The advantage of this approach, compared to ours, is that it does not require additional notion in the method dispatching.
+However, the disadvantage is that conflicting methods from different branches cannot be merged as in our model.
+Moreover, writing programs in these languages is tedious if not supported by an ad-hoc IDE and the path prefix is mandatory even if it is not needed in some scenarios.
 

### 2018-01-09 ECOOP18/sections/Auxiliary.tex
Fix review comments
Proof of Determinacy in latex

--- 2017-12-07 NewVersion/sections/Auxiliary.tex
@@
 
-\subsection{Method Lookup Algorithm in \mbody{}}\label{subsec:mbodydef}
-
+\subsection{The Method Lookup Algorithm in \mbody{}}\label{subsec:mbodydef}
 $\mbody(m, I_d, I_s)$ denotes the method body lookup function.
@@
 \end{proof}
+
+\begin{theorem}[Determinacy of One-Step Evaluation]~\label{theorem_determinacy}
+	If $t \to t'$ and $t \to t''$, then $t' = t''$.
+\end{theorem}
+\begin{proof}
+See Appendix~\ref{appendix_proof}.
+\end{proof}
+
 Note that in Theorem~\ref{theorem_progress}, ``$\#(\overline{x})$'' denotes the length of

### 2018-01-09 ECOOP18/sections/TypeSafety.tex
Proof of Determinacy in latex

--- 2017-10-05 NewVersion/sections/TypeSafety.tex
@@
 \begin{proof}
-
 Since $e$ is well-typed, by \textsc{(T-Invk)} and \textsc{(T-Anno)} we know that
@@
 
-By \textsc{(T-New)}, $\canOverride(I) = True$. By the definition of $\canOverride$, any $J_0\in\mostSpecific(m, I, I)$ satisfies that
+By \textsc{(T-New)}, $\canInstantiate(I) = True$. By the definition of $\canInstantiate$, any $J_0\in\mostSpecific(m, I, I)$ satisfies that
 $\mostSpecificOverride(m, I, J_0)$ contains only one interface, in which the $m$ that overrides $J_0$ is a concrete method.
@@
 \end{proof}
+
+\subsubsection{Proof for Theorem~\ref{theorem_determinacy}}
+\begin{proof}	
+The Proof is done by induction on a derivation of $t \to t'$, following the book  \emph{TAPL}.
+\begin{itemize}
+	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(S-Invk)}, then we know that $t$ has the form $\left((J)\new{I}\right).m(\overline{v})$ with $I, J, m$ determined.
+Now it is obvious that the last rule in the derivation of $t \to t''$ should also be \textsc{(S-Invk)} with the same $I, J, m$.
+Since $\mbody(m, I, J)$ is a \emph{function} that given the same input will calculate the same result, we know the two induction results are the same, thus $t' = t''$ is immediately proved.
+
+	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-Receiver)}, then $t$ has the form $e_0.m(\overline{e})$ and $e_0 \to e_0'$.
+Since $e_0$ is not a value, the last rule used in $t \to t''$ has to be \textsc{(C-Receiver)} (other rules do not match) too.
+Assume in the reduction $t \to t''$, $e_0 \to e_0''$, thus $e_0'.m(\overline{e}) = e_0''.m(\overline{e})$.
+Thus, $t' = t''$ proved.
+
+	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-StaticType)}, then $t$ is fixed to be $\new{I}$.
+The last rule used in $t \to t''$  has to be \textsc{(C-StaticType)}, and obviously, $t' = t'' = (I)\new{I}$.
+
+	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-FReduce)}, then $t$ has the form $(I)e$ and $e \to e'$.
+The last rule used in $t \to t''$ cannot be \textsc{(C-StaticType)} because it requires $t$ to be $\new{I}$; it can neither be \textsc{(C-AnnoReduce)} because it requires $t$ to be $(I)((J)\new{K})$ where $(J)\new{K}$ is already a value.
+So the last rule used in $t \to t''$ can only be \textsc{(C-FReduce)} (other rules do not match).
+Assume in the reduction $t \to t''$, $e \to e''$, and $(I)e \to (I)e''$.
+By induction hypothesis, $e' = e''$, thus $t' = t''$ proved.
+
+	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-AnnoReduce)}, then the form of $t$ is fixed to be $(I)((J)\new{K})$.
+Since $(I)((J)\new{K})$ is not reducible, the rule \textsc{(C-FReduce)} does not apply.
+The only rule applies in $t \to t''$ is \textsc{(C-AnnoReduce)}.
+Thus $t' = t'' = (I)\new{K}$ proved.
+
+	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-Args)}, then $t$ has the form $v.m(..., e, ...)$ and $e \to e'$.
+The last rule used in $t \to t''$ cannot be \textsc{(S-Invk)} because it requires all arguments to be values.
+Thus only \textsc{(C-Args)} applies to $t \to t''$.
+Assume in the reduction $t \to t''$, $e \to e''$.
+By induction hypothesis, $e' = e''$, thus $v.m(..., e', ...) = v.m(..., e'', ...)$, thus $t' = t''$ proved.
+\end{itemize}
+\end{proof}
+
+\begin{comment}
+If the last rule used in the derivation of t  → t′ is E-IfTrue, then we know that t has the form if t1 then t2 else t3, where t1 = true.
+But now it is obvious that the last rule in the derivation of t  → t′′ cannot be E-IfFalse, since we cannot have both t1 = true and t1 = false.
+Moreover, the last rule in the second derivation cannot be E-If either, since the premise of this rule demands that t1  → t′1 for some t′1, but we have already observed that true does not evaluate to anything.
+So the last rule in the second derivation can only be E-IfTrue, and it immediately follows that t′ = t′′.
+\end{comment}

### 2018-01-10 ECOOP18/sections/Formalization.tex
paragraph -> subsubsection

@@
 
-\paragraph{Notations}
+\subsubsection{Notations}
 The metavariables $I, J$ range over interface names; $x$ ranges over variables; $m$ ranges over method names; $e$ ranges over expressions; and $M$ ranges over method declarations.
@@
 
-\paragraph{Interfaces}
+\subsubsection{Interfaces}
 In order to achieve multiple inheritance, an interface can have a set of 
@@
 
-\paragraph{Methods}
+\subsubsection{Methods}
 Original methods and hierarchically overriding methods share the same syntax in our model for simplicity.
@@
 
-\paragraph{Expressions \& Values}
+\subsubsection{Expressions \& Values}
 Expressions can be standard constructs such as variables, method
@@
 \subsection{Subtyping and Typing Rules}\label{subsec:typingrules}
-\paragraph{Subtyping}
+\subsubsection{Subtyping}
 The subtyping of \MIM{} consists of only a few rules shown at the top of Figure~\ref{fig:typingrules}.
@@
 
-\paragraph{Type-checking}
+\subsubsection{Type-checking}
 Details of type-checking rules are displayed at the bottom of Figure~\ref{fig:typingrules}, including expression
@@
 
-\paragraph{Semantic Rules} \textsc{(S-Invk)} is the only computation rule we need for method invocation.
+\subsubsection{Semantic Rules} \textsc{(S-Invk)} is the only computation rule we need for method invocation.
 As a small-step rule and by congruence, it assumes that the receiver and the arguments are already values.
@@
 and in the meanwhile the static types are recorded via annotations. Finally, the return type $I_e$ is put in the front as an annotation.
-\paragraph{Congruence Rules} \textsc{(C-Receiver)}, \textsc{(C-Args)} and \textsc{(C-FReduce)} are natural congruence rules
+\subsubsection{Congruence Rules} \textsc{(C-Receiver)}, \textsc{(C-Args)} and \textsc{(C-FReduce)} are natural congruence rules
 on receivers, arguments, and cast-expressions, respectively. \textsc{(C-StaticType)} automatically adds an annotation $I$ to the new

### 2018-01-10 ECOOP18/sections/Overview.tex
small fix
paragraph -> subsubsection

@@
 
-\paragraph{Problem and Possible Workarounds:} The essential problem is
+\subsubsection{Problem and Possible Workarounds:} The essential problem is
 how to resolve unintentional method conflicts and invoke the
@@
   introduces a lot of boilerplate code.
+
   \item \textit{II. Refactor \lstinline|Drawable| and/or \lstinline|Deck| to rename the methods.} If
@@
   modifying existing code and becomes impossible if the code is unavailable.
-  \item \textit{III. Method exclusion/renaming in traits.} Some trait models
-  support method exclusion/renaming. Those features
+
+  \item \textit{III. Method exclusion/renaming.} Eiffel~\cite{Meyer:1987:EPR:24686.24694} and some trait models support method exclusion/renaming. Those features
    can eliminate conflicts, although most
@@
 
-\paragraph{\MIM{}'s solution:} To solve this problem it is important to preserve both conflicting methods
+\subsubsection{\MIM{}'s solution:} To solve this problem it is important to preserve both conflicting methods
 during inheritance instead of merging them into a single
@@
 
-\paragraph{\MIM's solution:} 
+\subsubsection{\MIM's solution:} 
 The essential problem is how to ensure that the correct method is
@@
 
-\paragraph{Potential solutions/workarounds in existing languages:} Unfortunately in all languages we have known
+\subsubsection{Potential solutions/workarounds in existing languages:} Unfortunately in all languages we have known
 (including C++), the existing approaches are unsatisfactory.
@@
 
-\paragraph{\MIM{}'s solution:} An additional feature of our model is \textit{hierarchical overriding}. It allows conflicting methods
+\subsubsection{\MIM{}'s solution:} An additional feature of our model is \textit{hierarchical overriding}. It allows conflicting methods
 to be overridden on individual branches, hence offers independent extensibility. The above example can be easily realized by:
@@
 
-\paragraph{Terminology:} In \lstinline|Drawable|, \lstinline|Deck|, and \lstinline|SafeDeck|, the \lstinline|draw| methods are called \textit{original methods} in this paper, because they are originally defined by the interfaces.
+\subsubsection{Terminology:} In \lstinline|Drawable|, \lstinline|Deck|, and \lstinline|SafeDeck|, the \lstinline|draw| methods are called \textit{original methods} in this paper, because they are originally defined by the interfaces.
 In contrast, \lstinline|DrawableSafeDeck| defines a \textit{hierarchical overriding method}.
@@
 
-\paragraph{A peek at the hierarchical dispatching algorithm:} In \MIM{}, triangle inheritance allows several original methods (branches)
+\subsubsection{A peek at the hierarchical dispatching algorithm:} In \MIM{}, triangle inheritance allows several original methods (branches)
 to coexist, and hierarchical dispatch first finds the most specific

### 2018-01-11 ECOOP18/sections/Discussion.tex
added the more general model in discussion: allowing multiple overrides

--- 2017-10-20 NewVersion/sections/Discussion.tex
@@
 In our formalized calculus, however, abstract methods are not a completely orthogonal feature. The $\canInstantiate$ function
-has to check whether an interface can be instantiated, by looking at all the inherited branches and seeing if each most specific method
-is abstract or not.
+has to check whether an interface can be instantiated by looking at all the inherited branches and checking if each most specific method is abstract or not.
 
 Our formalization has a simple form of abstract methods, which behave similarly to conventional methods with respect to conflicts.
-Other languages may support different behaviors.
+Other languages may behave differently. 
 For instance, in Java 8 when putting two identical abstract methods together by multiple inheritance, there is no conflict error.
@@
 \MIM{} behaves differently from Java in both cases.
-In the triangle inheritance case (left) $C$ will have two distinct abstract methods corresponding to $A.m$ and $B.m$. 
+In the triangle inheritance case (left), $C$ will have two distinct abstract methods corresponding to $A.m$ and $B.m$. 
 In the diamond inheritance case, the definition of $C$ is rejected. 
@@
         \centering
-        \includegraphics[width=1.4cm]{pics/P7.pdf}
+        \includegraphics[width=1.6cm]{pics/P7.pdf}
     \end{minipage}
@@
         \centering
-        \includegraphics[width=1.2cm]{pics/P8.pdf}
+        \includegraphics[width=1.4cm]{pics/P8.pdf}
     \end{minipage}  
@@
 \subsection{Orthogonal \& Non-Orthogonal Extensions}\label{sec:orthoext}
-Our model is designed as a minimal calculus for focusing only on resolving unintentional conflicts. Therefore, we have omitted a number of
+Our model is designed as a minimal calculus that focuses on resolving unintentional conflicts. Therefore, we have omitted a number of
 common orthogonal features including primitive types, assignments, method overloading, covariant method return types, static dispatch, and so on.
@@
 
-One typical non-orthogonal extension to \MIM{} could be to have fields.
+One non-orthogonal extension to \MIM{} could be to generalize the model to allow multiple hierarchical method overrding, meaning that, we allow overriding methods to update multiple branches instead of only one branch.
+We present the modification of syntax, typing and semantic rules below (abstract methods omitted):
+
+\begin{mathpar}
+	\begin{array}{llrl}
+		    \text{Methods}      & M  & \Coloneqq & \ldots \;   \mid
+       \momethod{I}{m}{I_x}{x}{J}{e}  
+	\end{array} \\
+	\tmomethod 
+\end{mathpar}
+
+Semantic rules themselves remain unchanged, however, we need to change slightly the definition of \mostSpecificOverride in \mbody:
+
+\saveSpaceFig
+\begin{flalign*}
+& \rhd \textit{Definition of } \mostSpecificOverride(m, I, J): & \\
+& \bullet \mostSpecificOverride(m, I, J) = \prune(overrides) & \\
+& \indent\indent \textrm{with: } overrides = \{K \mid \subt{I}{K}, \; \subt{K}{J} \textrm{ and } K[m\ \kwoverride\ \overline{J}] \textrm{ where } J \in \overline{J} 
+\end{flalign*}
+\saveSpaceFig
+
+\noindent This \emph{multiple overriding} non-othogonal extension shows that our model is friendly to different kinds of language extensions.
+
+Other typical non-orthogonal extensions to \MIM{} could be to have fields.
 The design of \MIM{} can be viewed as a variant of Java 8 with default methods which allows for unintentional method conflicts.

### 2018-01-13 ECOOP18/sections/RelatedWork.tex

@@
 The advantage of this approach, compared to ours, is that it does not require additional notion in the method dispatching.
-However, the disadvantage is that conflicting methods from different branches cannot be merged as in our model.
+However, the disadvantage is that these approaches depend on name appending, where conflicting methods from different branches cannot be merged because they are regarded as unrelated method, since they have different paths and the path names are appended in method names.
 Moreover, writing programs in these languages is tedious if not supported by an ad-hoc IDE and the path prefix is mandatory even if it is not needed in some scenarios.

### 2018-01-13 ECOOP18/sections/RelatedWork.tex
magda code

--- 2018-01-09 ECOOP18/sections/RelatedWork.tex
@@
 The advantage of this approach, compared to ours, is that it does not require additional notion in the method dispatching.
-However, the disadvantage is that conflicting methods from different branches cannot be merged as in our model.
+However, the disadvantage is that these approaches depend on name appending.
+As shown in Figure~\ref{fig:magda_code}, two methods \lstinline|m| from different branches \lstinline|A| and \lstinline|B| cannot be overridden by the method \lstinline|m| in \lstinline|C| because they are regarded as unrelated methods, since in these hygienic approaches, path names are used to distinguish different methods.
 Moreover, writing programs in these languages is tedious if not supported by an ad-hoc IDE and the path prefix is mandatory even if it is not needed in some scenarios.
+Finally, the multiple inheritance model in Magda is based on Mixins, whereas \MIM{} is based on traits.
+Thus, Magda inherits all limitations of Mixins (such as the linearization problem, etc).
+
+\begin{figure*}[t]
+	\saveSpaceFig
+\begin{lstlisting}
+mixin A of Object =
+	new String m()
+	begin
+		return "A";
+	end;
+end;
+
+mixin B of Object = 
+	new String m()
+	begin
+		return "B";
+	end;
+end;
+
+mixin C of A, B = 
+	new String m()
+	begin
+		return "C";
+	end;
+end;
+\end{lstlisting}
+	\caption{Code in Magda.}
+	\label{fig:magda_code}
+	\saveSpaceFig
+\end{figure*}
 

### 2018-01-13 ECOOP18/paper.tex
test git
Proof of Determinacy in latex
small fix
triangle->fork

@@
 
-\newcommand\saveSpaceFig{\vspace{-2ex}}
-
+%\newcommand\saveSpaceFig{\vspace{-2ex}}
+\newcommand\saveSpaceFig{\vspace{0ex}}
+\newcommand\wordfork{fork}
+\newcommand\wordFork{Fork}
 \lstset{ %
@@
 \title{FHJ: A Formal Model for Hierarchical Dispatching and Overriding}
-%\titlerunning{A Sample LIPIcs Article} %optional, in case that the title is too long; the running title should fit into the top page column
+% \titlerunning{A Sample LIPIcs Article} %optional, in case that the title is too long; the running title should fit into the top page column
 
 %% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
-
 \author[1]{John Q. Open}
@@
 	\texttt{access@dummycollege.org}}
-\authorrunning{J.\,Q. Open and J.\,R. Access} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'
+\authorrunning{J.\,Q. Open and J.\,R. Access} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus ‘et. al.’
 
-\Copyright{John Q. Open and Joan R. Access}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+\Copyright{John Q. Open and Joan R. Access}%mandatory, please use full first names. LIPIcs license is “CC-BY”;  http://creativecommons.org/licenses/by/3.0/
 
-\subjclass{Dummy classification -- please refer to \url{http://www.acm.org/about/class/ccs98-html}}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html .
-E.g., cite as "F.1.1 Models of Computation".
-\keywords{Dummy keyword -- please provide 1--5 keywords}% mandatory: Please provide 1-5 keywords
+% \subjclass{Dummy classification -- please refer to \url{http://www.acm.org/about/class/ccs98-html}}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html .
+E.g., cite as “F.1.1 Models of Computation”.
+% \keywords{Dummy keyword -- please provide 1--5 keywords}% mandatory: Please provide 1-5 keywords
 % Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \input{sections/RelatedWork.tex}
+
 \input{sections/Conclusion.tex}
@@
 \appendix
-%\input{sections/Appendix.tex}
-
+\input{sections/Appendix.tex}
 \end{document}

### 2018-01-13 ECOOP18/sections/Conclusion.tex
triangle->fork

--- 2017-10-16 NewVersion/sections/Conclusion.tex
@@
 mechanisms in C++. We provide a minimal formal model of hierarchical
-dispatching in \MIM{}. Such algorithm makes use of both dynamic type
-information and path information from either upcasts or parameters'
+dispatching in \MIM{}. Such an algorithm makes use of both dynamic type
+information and static information from either upcasts or parameters'
 information. It not only offers great code reuse like
@@
 hierarchical dispatching features is general and
-can be safely embedded in other OO models, so as to have support for the triangle
+can be safely embedded in other OO models, so as to have support for the \wordfork{}
 inheritance.

### 2018-01-13 ECOOP18/sections/Discussion.tex
triangle->fork

@@
 \MIM{} behaves differently from Java in both cases.
-In the triangle inheritance case (left), $C$ will have two distinct abstract methods corresponding to $A.m$ and $B.m$. 
+In the \wordfork{} inheritance case (left), $C$ will have two distinct abstract methods corresponding to $A.m$ and $B.m$. 
 In the diamond inheritance case, the definition of $C$ is rejected. 
@@
     \end{minipage}  
-    \caption{Triangle inheritance (left) and diamond inheritance (right) on abstract methods.}\label{fig:abstractdiamond}
+    \caption{\wordFork{} inheritance (left) and diamond inheritance (right) on abstract methods.}\label{fig:abstractdiamond}
 \saveSpaceFig

### 2018-01-13 ECOOP18/sections/Formalization.tex
triangle->fork

@@
 auxiliary function $\canInstantiate(I)$ (see definition in Section~\ref{sec:otherdefs}) checks whether an interface $I$ 
-can be instantiated or not. Since triangle inheritance accepts conflicting branches to coexist, the check requires that the most specific method is concrete for each method on each branch.
+can be instantiated or not. Since \wordfork{} inheritance accepts conflicting branches to coexist, the check requires that the most specific method is concrete for each method on each branch.
 

### 2018-01-13 ECOOP18/sections/Introduction.tex
triangle->fork

@@
 the conflicting methods have very different meanings and do not share a
-common parent. We call such a case \textit{triangle inheritance}, in
+common parent. We call such a case \textit{\wordfork{} inheritance}, in
 analogy to diamond inheritance.
@@
 multiple classes). %We will have more detailed discussion on this in Section~\ref{sec:relatedwork}.
-C++ accepts triangle inheritance and
+C++ accepts \wordfork{} inheritance and
 resolves the ambiguity by specifying the expected path by

### 2018-01-13 ECOOP18/sections/Overview.tex
triangle->fork

@@
 
-This example illustrates the basic form of triangle inheritance, where two unintentionally conflicting methods
+This example illustrates the basic form of \wordfork{} inheritance, where two unintentionally conflicting methods
 are accepted by multiple inheritance. Note that C++ supports this feature and also addresses the
@@
 	\item It changes the hierarchy and existing code, hence breaks the modularity.
-	\item Separate overriding is required to come after the triangle
+	\item Separate overriding is required to come after the \wordfork{} 
           inheritance, especially when the implementation needs functionality from both parents. In the above code, we have assumed
@@
 
-\subsubsection{A peek at the hierarchical dispatching algorithm:} In \MIM{}, triangle inheritance allows several original methods (branches)
+\subsubsection{A peek at the hierarchical dispatching algorithm:} In \MIM{}, \wordfork{}  inheritance allows several original methods (branches)
 to coexist, and hierarchical dispatch first finds the most specific
@@
 
-In  Figure~\ref{fig:examplesmbody}, (a) is the base case for unintentional conflicts, namely the triangle inheritance.
+In  Figure~\ref{fig:examplesmbody}, (a) is the base case for unintentional conflicts, namely the \wordfork{} inheritance.
 (b) uses overriding to explicitly merge the conflicting methods.

### 2018-01-13 ECOOP18/sections/Introduction.tex
more fixes

@@
 A simple example of this situation is two \lstinline{draw} methods that
-are inherited from a deck of cards and a drawable widget. 
+are inherited from a deck of cards and a drawable widget, respectively. 
 In such context, the two \lstinline{draw} methods have very different meanings, 
@@
 resolves the ambiguity by specifying the expected path by
-\emph{upcasts}. However, neither the C\# or C++ approaches allow
+\emph{upcasts}. However, neither the C\# nor C++ approaches allow
 such conflicting methods to be further overridden. 
@@
 The class \lstinline|SafeDeck| adds functionality to check whether the
-deck is empty and to prevent drawing a card from an empty deck. 
+deck is empty so as to prevent drawing a card from an empty deck. 
 The interesting class is \lstinline|DrawableSafeDeck|, which inherits 
@@
 overriding is used in \lstinline|DrawableSafeDeck| to keep two separate \lstinline|draw|
-methods for each parent, but overriding \emph{only} the \lstinline|draw|
+methods for each parent, but override \emph{only} the \lstinline|draw|
 method coming from \lstinline|Drawable|, in order to draw a widget

### 2018-01-13 ECOOP18/sections/Overview.tex
more fixes

@@
 
-\subsubsection{Problem and Possible Workarounds:} The essential problem is
+\subsubsection{Problem and Possible Workarounds} The essential problem is
 how to resolve unintentional method conflicts and invoke the
@@
 
-\subsubsection{\MIM{}'s solution:} To solve this problem it is important to preserve both conflicting methods
+\subsubsection{\MIM{}'s solution} To solve this problem it is important to preserve both conflicting methods
 during inheritance instead of merging them into a single
@@
 \end{lstlisting}
-Here \lstinline|shuffleAndDraw| \emph{invokes \lstinline|draw| from its own enclosing type}.
-In \MIM{}, this invocation is dynamically dispatched.
-This is important, because a programmer may define a subtype
+Here \lstinline|shuffleAndDraw| invokes \lstinline|draw| from its own enclosing type. In \MIM{}, this invocation is dynamically dispatched. This is important, because a programmer may define a subtype
 of \lstinline|Deck| and override the method \lstinline|draw|:
@@
 
-\subsubsection{\MIM's solution:} 
+\subsubsection{\MIM's solution} 
 The essential problem is how to ensure that the correct method is
@@
 Notably, we track the static types by adding upcasts during reduction. In contrast to FJ,
-where \lstinline|new C()| is a value, in \MIM{} such expression is not 
+where \lstinline|new C()| is a value, in \MIM{} such an expression is not 
 a value. Instead, an expression of the form \lstinline|new C()| is reduced to
-\lstinline|(C) new C()|, which is a value in \MIM{} and where the type
-in the cast denotes the static type of the expression. This rule is
+\lstinline|(C) new C()|, which is a value in \MIM{} and the cast denotes the static type of the expression. This rule is
 applied in the first reduction step. 
@@
 an example.
-
 Suppose that the programmer defines a new interface \lstinline|DrawableSafeDeck| (based on the code in Section~\ref{subsec:problem2} without the old \lstinline|DrawableSafeDeck|), but he needs to override
@@
 
-\subsubsection{Potential solutions/workarounds in existing languages:} Unfortunately in all languages we have known
+\subsubsection{Potential solutions/workarounds in existing languages} Unfortunately in all languages we have known
 (including C++), the existing approaches are unsatisfactory.
@@
 
-\subsubsection{\MIM{}'s solution:} An additional feature of our model is \textit{hierarchical overriding}. It allows conflicting methods
+\subsubsection{\MIM{}'s solution} An additional feature of our model is \textit{hierarchical overriding}. It allows conflicting methods
 to be overridden on individual branches, hence offers independent extensibility. The above example can be easily realized by:
@@
 
-\subsubsection{Terminology:} In \lstinline|Drawable|, \lstinline|Deck|, and \lstinline|SafeDeck|, the \lstinline|draw| methods are called \textit{original methods} in this paper, because they are originally defined by the interfaces.
+\subsubsection{Terminology} In \lstinline|Drawable|, \lstinline|Deck|, and \lstinline|SafeDeck|, the \lstinline|draw| methods are called \textit{original methods} in this paper, because they are originally defined by the interfaces.
 In contrast, \lstinline|DrawableSafeDeck| defines a \textit{hierarchical overriding method}.
@@
 
-\subsubsection{A peek at the hierarchical dispatching algorithm:} In \MIM{}, \wordfork{}  inheritance allows several original methods (branches)
+\subsubsection{A peek at the hierarchical dispatching algorithm} In \MIM{}, \wordfork{}  inheritance allows several original methods (branches)
 to coexist, and hierarchical dispatch first finds the most specific

### 2018-01-13 ECOOP18/sections/RelatedWork.tex
added code and explaination of Magda

--- 2018-01-09 ECOOP18/sections/RelatedWork.tex
@@
 In NextGen/MixGen~\cite{Allen:2003:FAG:949305.949316}, HygJava~\cite{kusmierek2007hygienic} and Magda~\cite{Bono:2012:MNL:2367163.2367198}, \emph{hygienicity} is proposed to deal with unintentional method conflicts, which is basically giving a method a unique identifier by prefixing the name with an unambiguous path.
+As shown in Figure~\ref{fig:magda_prefix}, the prefix \lstinline|HelloWorld| in method call \lstinline|(new HelloWorld []).HelloWorld.MainMatter()| is mandatory, although it is not necessarily needed.
+So writing programs in these languages is tedious if not supported by an ad-hoc IDEs.
 The advantage of this approach, compared to ours, is that it does not require additional notion in the method dispatching.
-However, the disadvantage is that conflicting methods from different branches cannot be merged as in our model.
-Moreover, writing programs in these languages is tedious if not supported by an ad-hoc IDE and the path prefix is mandatory even if it is not needed in some scenarios.
+However, the disadvantage is that the compilation strategy is simple: generating conventional code with method names attached with prefixes.
+Unfortunatelly this is problematic, as shown in Figure~\ref{fig:magda_code}, two methods \lstinline|m| from different branches \lstinline|A| and \lstinline|B| cannot be overridden by the method \lstinline|m| in \lstinline|C| because they are regarded as unrelated methods, and \lstinline|m| in \lstinline|C| is just another new method that has nothing to do with \lstinline|A.m| or \lstinline|B.m|.
+The reason is that in these hygienic approaches, path names are used to distinguish different methods.
+In contrast, our model can deal with unentential conflicts, as well as merged methods because our semantics is not simply based on prefixing.
+Instead, our direct operational semantics takes static and dynamic type information into account at runtime when doing method selection.Finally, the multiple inheritance model in Magda is based on Mixins, whereas \MIM{} is based on traits.
+Thus, Magda inherits all limitations of Mixins (such as the linearization problem, etc).
+
+\begin{figure}[t]
+	\saveSpaceFig
+	\begin{lstlisting}
+mixin HelloWorld of Object =
+	new Object MainMatter()
+	begin
+		"Hello world".String.print();
+	end;
+end;
+(new HelloWorld []).HelloWorld.MainMatter();
+	\end{lstlisting}
+	\caption{Full-qualified name of method call in Magda.}
+	\label{fig:magda_prefix}
+	\saveSpaceFig
+\end{figure}
+
+\begin{figure*}[t]
+	\saveSpaceFig
+\begin{lstlisting}
+mixin A of Object =
+	new String m()
+	begin
+		return "A";
+	end;
+end;
+
+mixin B of Object = 
+	new String m()
+	begin
+		return "B";
+	end;
+end;
+
+mixin C of A, B = 
+	new String m()
+	begin
+		return "C";
+	end;
+end;
+\end{lstlisting}
+	\caption{Code in Magda.}
+	\label{fig:magda_code}
+	\saveSpaceFig
+\end{figure*}
 

### 2018-01-13 ECOOP18/sections/RelatedWork.tex
Polished text

--- 2018-01-13 ECOOP18/sections/RelatedWork.tex
@@
 \noindent  {\bf Languages using hygienicity.}
-In NextGen/MixGen~\cite{Allen:2003:FAG:949305.949316}, HygJava~\cite{kusmierek2007hygienic} and Magda~\cite{Bono:2012:MNL:2367163.2367198}, \emph{hygienicity} is proposed to deal with unintentional method conflicts, which is basically giving a method a unique identifier by prefixing the name with an unambiguous path.
-The advantage of this approach, compared to ours, is that it does not require additional notion in the method dispatching.
-However, the disadvantage is that these approaches depend on name appending.
-As shown in Figure~\ref{fig:magda_code}, two methods \lstinline|m| from different branches \lstinline|A| and \lstinline|B| cannot be overridden by the method \lstinline|m| in \lstinline|C| because they are regarded as unrelated methods, since in these hygienic approaches, path names are used to distinguish different methods.
-Moreover, writing programs in these languages is tedious if not supported by an ad-hoc IDE and the path prefix is mandatory even if it is not needed in some scenarios.
-Finally, the multiple inheritance model in Magda is based on Mixins, whereas \MIM{} is based on traits.
-Thus, Magda inherits all limitations of Mixins (such as the linearization problem, etc).
+In NextGen/MixGen~\cite{Allen:2003:FAG:949305.949316},
+HygJava~\cite{kusmierek2007hygienic} and
+Magda~\cite{Bono:2012:MNL:2367163.2367198}, \emph{hygienicity} is
+proposed to deal with unintentional method conflicts. The idea is 
+to give a method a unique identifier by prefixing the name
+with an unambiguous path. As shown in Figure~\ref{fig:magda_prefix},
+the prefix \lstinline|HelloWorld| in method call \lstinline|(new HelloWorld []).HelloWorld.MainMatter()| is mandatory. So writing programs in these languages is
+tedious if not supported by a specialized IDE, that aids filling
+prefix/method information.  The advantage of this
+approach, compared to ours, is that it does not require any additional
+notion for method dispatching. Indeed
+the compilation strategy is simple, just by generating conventional code (say
+in Java or C++) with
+method names attached with prefixes. Unfortunatelly the disadvantage
+is that some expressive power is lost. In particular \emph{merging}
+methods arizing from diamond inheritance is not possible because the 
+methods have different prefixes. 
+As shown in Figure~\ref{fig:magda_code}, two methods
+\lstinline|m| from different branches \lstinline|A| and \lstinline|B|
+cannot be overridden by the method \lstinline|m| in \lstinline|C|
+because they are regarded as unrelated methods, and \lstinline|m| in
+\lstinline|C| is just another new method that has nothing to do with
+\lstinline|A.m| or \lstinline|B.m|. The reason is that in these
+hygienic approaches, path names are used to distinguish different
+methods. In contrast, our model can deal with unintentional conflicts,
+as well as merged methods because our semantics is not simply based on
+prefixing. Instead, our model keeps the names of methods unchanged,
+and our direct operational semantics takes static and
+dynamic type information into account at runtime when doing method
+dispatching. Finally, the multiple inheritance model in Magda is based on
+Mixins, whereas \MIM{} is based on traits. Thus, Magda inherits all
+limitations of Mixins (such as the linearization problem, etc).
+
+\begin{figure}[t]
+	\saveSpaceFig
+	\begin{lstlisting}
+mixin HelloWorld of Object =
+	new Object MainMatter()
+	begin
+		"Hello world".String.print();
+	end;
+end;
+(new HelloWorld []).HelloWorld.MainMatter();
+	\end{lstlisting}
+	\caption{Full-qualified name of method call in Magda.}
+	\label{fig:magda_prefix}
+	\saveSpaceFig
+\end{figure}
 

### 2018-01-13 ECOOP18/sections/Auxiliary.tex
text for determinism
polish text

@@
 
-To calculate $\mbody(m, I_d, I_s)$, the invocation of $\mostSpecific$ looks for the most specific original methods and their interfaces, and expects a singleton set, so as to avoid unambiguity.
-Furthermore, the invocation of $\mostSpecificOverride$ also expects a unique (unambiguous) most specific hierarchical override.
+To calculate $\mbody(m, I_d, I_s)$, the invocation of $\mostSpecific$ looks for the most specific original methods and their interfaces, and expects a singleton set, so as to achieve unambiguity.
+Furthermore, the invocation of $\mostSpecificOverride$ also expects a unique and most specific hierarchical override.
 And finally the target method is returned.
@@
 The $\mostSpecific$ function only focuses on original method
-implementations, all the hierarchical overriding methods are omitted
+implementations, where all the hierarchical overriding methods are omitted
 during that step. On the other hand, $\mostSpecificOverride(m, I, J)$
@@
 
-\begin{theorem}[Determinacy of One-Step Evaluation]~\label{theorem_determinacy}
-	If $t \to t'$ and $t \to t''$, then $t' = t''$.
-\end{theorem}
-\begin{proof}
-See Appendix~\ref{appendix_proof}.
-\end{proof}
-
 Note that in Theorem~\ref{theorem_progress}, ``$\#(\overline{x})$'' denotes the length of
@@
 
+Finally we show that one-step evaluation is deterministic. This
+theorem is helpful to show that our model of multiple inheritance is
+not ambiguous (or non-deterministic).
+
+\begin{theorem}[Determinacy of One-Step Evaluation]~\label{theorem_determinacy}
+	If $t \to t'$ and $t \to t''$, then $t' = t''$.
+\end{theorem}
+\begin{proof}
+See Appendix~\ref{appendix_proof}.
+\end{proof}
+
 %the annotations in the

### 2018-01-13 ECOOP18/sections/Discussion.tex
polish text

@@
 It is possible to change our model to account for other behaviors for abstract methods, but we view this as a mostly 
-orthogonal change to our work, that should not affect the essence of the model presented here.
+orthogonal change to our work, which should not affect the essence of the model presented here.
 
@@
 
-Semantic rules themselves remain unchanged, however, we need to change slightly the definition of \mostSpecificOverride in \mbody:
+Semantic rules themselves remain unchanged, however, we need to change slightly the definition of \mostSpecificOverride{} in \mbody:
 
@@
 
-\noindent This \emph{multiple overriding} non-othogonal extension shows that our model is friendly to different kinds of language extensions.
+%\noindent This \emph{multiple overriding} non-othogonal extension shows that our model is friendly to different kinds of language extensions.
 
@@
 Here both $B.m$ and $C.m$ override $A.m$, and D inherits
-both conflicting methods without an explicit override. In this case automatically merging 
+both conflicting methods without an explicit override. In this case, automatically merging 
 the two methods (to achieve diamond inheritance) is not possible, which is why many 
@@
 We could also loosen the model to accept definitions such as \lstinline|D|, and perform ambiguity check on upcasts and other expressions.
-However, we would need to handle more cases than C++.
+Then, we would need to handle more cases than C++.
 For instance, in the above program assume that $B.m$ and $C.m$ are hierarchical overrides on $A$.

### 2018-01-13 ECOOP18/sections/Formalization.tex
polish text

@@
 is defined but $\mbody(m, I, J)$ is undefined for some $J$ and $m$. This indicates that $m$ is available and unambiguous from the perspective of $J$,
-but is ambiguous to $I$ on branch $J$. It means that there are multiple overriding paths of $m$ from $J$ to $I$, which forms a diamond. Hence rejecting
+but is ambiguous to $I$ on branch $J$. It means that there are multiple overriding paths of $m$ from $J$ to $I$, which form a diamond. Hence rejecting
 that case meets our expectation. Below is an example (Figure~\ref{fig:examplesmbody} (e)) that illustrates the reason why this condition is needed:
@@
 to $C$ along path $T$, which forms a diamond. The expression \lstinline|((A) new D()).m()| is one example of triggering ambiguity, but \MIM{}
-simply rejects the definition of $C$. To resolve the issue, the programmer need to have an overriding method in $C$, to explicitly merge
+simply rejects the definition of $C$. To resolve the issue, the programmer needs to have an overriding method in $C$, to explicitly merge
 the conflicting ones.
@@
 rule reduces method invocation to $e_0$ with substitution.
-Parameters are substituted with arguments, and the \lstinline|this| reference is substituted by the receiver,
+Parameters are substituted with arguments, and the \lstinline|this| reference is substituted with the receiver,
 and in the meanwhile the static types are recorded via annotations. Finally, the return type $I_e$ is put in the front as an annotation.

### 2018-01-13 ECOOP18/sections/RelatedWork.tex
polish text

@@
 overriding, including the \emph{MiddleMan} approach\footnote{\url{https://stackoverflow.com/questions/44632250/can-i-do-mimic-things-likes-this-partial-override-in-c}}, the \emph{interface classes} pattern as described in Section 25.6 of~\cite{stroustrup1995}, the \emph{LotterySimulation} discussion in~\cite{stroustrup1994design}.
-Since these workarounds share the same spirit, we will discuss in detail the \emph{MiddleMan} approach, with code shown in
+Since these workarounds share the same spirit, we will discuss in detail the \emph{MiddleMan} approach, with the code shown in
 Figure~\ref{fig:middleman}. In this example, classes \texttt{A} and
@@
 Moreover, the lack of direct syntax support makes MiddleMan code cumbersome to write.
-Finally, the approach is ad-hoc, meaning that the class \texttt{MiddleMan} shown in Figure~\ref{fig:middleman} is not general enough to be used in other cases: more middle-mans are needed if partial method overrides happens in other classes; and it is even worse when return types differ.
+Finally, the approach is ad-hoc, meaning that the class \texttt{MiddleMan} shown in Figure~\ref{fig:middleman} is not general enough to be used in other cases: more middle-mans are needed if partial method overrides happen in other classes; and it is even worse when return types differ.
 
@@
 in Java or C++) with
-method names attached with prefixes. Unfortunatelly the disadvantage
+method names attached with prefixes. Unfortunately, the disadvantage
 is that some expressive power is lost. In particular \emph{merging}
@@
 	\end{lstlisting}
-	\caption{Full-qualified name of method call in Magda.}
+	\caption{Full-qualified name of method calls in Magda.}
 	\label{fig:magda_prefix}

### 2018-01-13 ECOOP18/sections/RelatedWork.tex
submitted

@@
 
-\begin{figure}[t]
+\begin{figure*}[t]
 	\saveSpaceFig
@@
 	\saveSpaceFig
-\end{figure}
+\end{figure*}
 
@@
 end; 
-
 mixin B of Object = 
@@
 end;
-
 mixin C of A, B = 

### 2018-03-20 ECOOP18/sections/Introduction.tex

@@
           type soundness of the model.
-	\item \textbf{Prototype implementation\footnote{https://github.com/YanlinWang/MIM/tree/master/Calculus}:} a
+	\item \textbf{Prototype implementation\footnote{The implementation is included in supplemental material and we will put it online after the review process.}:} a
           simple implementation of \MIM{} interpreter in Scala. The implementation can type-check and run variants

### 2018-03-20 Calculus/src/framework/AST.scala
Impl.

@@ -1,0 +1,111 @@
+package framework
+
+object AST {
+  case class Program(is: List[TypeDef], e: Expr) {
+    def programCheck(info: Info): String = {
+      var checked: Set[String] = Set()
+      for (t <- info.table) {
+        if (!checked(t)) {
+          assert(info.typeMap.contains(t))
+          for (t0 <- info.typeMap(t)) {
+            if (!checked(t0)) {
+              assert(info.typeMap.contains(t0))
+              assert(info.typeDefMap(t0).interfaceCheck(info))
+              checked += t0
+            }
+          }
+          assert(info.typeDefMap(t).interfaceCheck(info))
+          checked += t
+        }
+      }
+      e.checkType(info, Map())
+    }
+  }
+  
+  case class TypeDef(name: String, sups: List[String], methods: List[MethDef]) {
+    def interfaceCheck(info: Info): Boolean = {
+      assert(sups.forall(x => info.table.contains(x)))
+      assert(methods.forall(x => x.methodCheck(info, name)))
+      val collectMethods = info.collectMethods(name)
+      val cond1 = !(collectMethods.exists(m => info.table.exists(j => info.subType(name, j) &&
+          info.mtype(m, j).isDefined && info.mbody(m, name, j).isEmpty)))
+      val cond2 = !(collectMethods.exists(m => info.table.exists(j => info.subType(name, j) &&
+          info.dispatch(name, m, name).isDefined && info.dispatch(j, m, j).isDefined &&
+              !info.canOverride(m, name, j))))
+      assert(cond1, "Type-checker: condition 2 unsatisfied for type " + name + " on interface check.")
+      assert(cond2, "Type-checker: condition 3 unsatisfied for type " + name + " on interface check.")
+      true
+    }
+  }
+  
+  case class MethDef(returnType: String, name: String, paras: List[(String, String)], update: String, returnExpr: Option[Expr]) {
+    def methodCheck(info: Info, thisType: String) = {
+      assert(info.table.contains(returnType))
+      assert(info.table.contains(update))
+      assert(paras.map(p => p._1).forall(x => info.table.contains(x)))
+      assert(info.subType(thisType, update))
+      if (returnExpr.isDefined) {
+        val env: Map[String, String] = paras.map(p => p._2 -> p._1).toMap + ("this" -> thisType)
[…]

### 2018-03-20 Calculus/src/framework/FHJ.scala

@@ -1,237 +1,0 @@
-package framework
-
-object FHJ {
-  /* Environment. */
-  type Env = {val info: Info; val gamma: Map[String, String]}
-  
-  /* Abstract syntax tree. */
-  /* Typing and semantic rules. */
-  case class TypeDef(name: String, sups: List[String], methods: List[MethDef]) {
-    def interfaceCheck(env: Env): Boolean = {
-      if (sups.exists(x => !env.info.table.contains(x))) return false
-      val env2: Env = new {val info = env.info; val gamma = env.gamma + ("this" -> name)}
-      if (methods.exists(x => !x.methodCheck(env2))) return false
-      val collectMethods = env.info.collectMethods(name)
-      val cond1 = !(collectMethods.exists(m => env.info.table.exists(j => env.info.subType(name, j) &&
-          env.info.mtype(m, j).isDefined && env.info.mbody(m, name, j).isEmpty)))
-      val cond2 = !(collectMethods.exists(m => env.info.table.exists(j => env.info.subType(name, j) &&
-          env.info.dispatch(name, m, name).isDefined && env.info.dispatch(j, m, j).isDefined &&
-              !env.info.canOverride(m, name, j))))
-      cond1 && cond2
-    }
-    override def toString = {
-      val supStr = if (sups.isEmpty) "" else " extends " + sups.reduce((a, b) => a + ", " + b)
-      "interface " + name + supStr + " " +
-        (if (methods.size == 0) "{}" else "{\n" + methods.map(x => x.toString).reduce((a, b) => a + "\n" + b) + "\n}")
-    }
-  }
-  
-  case class MethDef(returnType: String, name: String, paras: List[(String, String)], update: String, returnExpr: Option[Expr]) {
-    def methodCheck(env: Env): Boolean = {
-      if (!env.info.table.contains(returnType)) return false
-      if (!env.info.table.contains(update)) return false
-      if (paras.map(p => p._1).exists(x => !env.info.table.contains(x))) return false
-      val thisType = env.gamma.get("this").get
-      if (!env.info.subType(thisType, update)) return false
-      if (returnExpr.isDefined) {
-        val env2: Env = new {val info = env.info; val gamma = env.gamma ++ paras.map(p => p._2 -> p._1).toMap}
-        val mtype = env.info.mtype(name, update)
-        if (mtype.isEmpty || mtype.get._1.size != paras.size) return false
[…]

### 2018-03-20 Calculus/src/framework/Info.scala

@@ -1,0 +1,68 @@
+package framework
+
+import AST._
+
+case class Info(table: List[String], typeMap: Map[String, List[String]],
+    methodMap: Map[String, List[MethDef]], typeDefMap: Map[String, TypeDef]) {
+  def ext(t1: String, t2: String): Boolean = {
+    assert(table.contains(t1) && table.contains(t2), "Bug: ext.")
+    typeMap.get(t1).contains(t2)
+  }
+  def subType(t1: String, t2: String): Boolean = {
+    assert(table.contains(t1) && table.contains(t2), "Bug: subType.")
+    if (t1 == t2) return true
+    typeMap.get(t1).get.exists(x => subType(x, t2))
+  }
+  def dispatch(i: String, m: String, j: String): Option[MethDef] = {
+    assert(table.contains(i) && table.contains(j), "Bug: dispatch.")
+    methodMap.get(i).get.find(x => x.name == m && x.update == j)
+  }
+  def prune(set: Set[String]): Set[String] = set.filter(i => !set.exists(j => j != i && subType(j, i)))
+  def collectMethods(i: String): Set[String] = {
+    assert(table.contains(i), "Bug: collectMethods.")
+    val start = methodMap.get(i).get.map(x => x.name).toSet
+    val op = (s: Set[String], x: String) => s ++ collectMethods(x)
+    typeMap.get(i).get.foldLeft(start)(op)
+  }
+  def mbody(m: String, id: String, is: String): Option[(String, List[(String, String)], (String, Option[Expr]))] = {
+    assert(table.contains(id) && table.contains(is), "Bug: mbody.")
+    val set1 = mostSpecific(m, id, is)
+    if (set1.size != 1) return None
+    val i = set1.head
+    val set2 = mostSpecificOverride(m, id, i)
+    if (set2.size != 1) return None
+    val j = set2.head
+    val method = methodMap.get(j).get.find(x => x.name == m && x.update == i)
+    if (method.isEmpty) None else Some(j, method.get.paras, (method.get.returnType, method.get.returnExpr))
+  }
+  def mtype(m: String, i: String): Option[(List[String], String)] = {
+    assert(table.contains(i), "Bug: mtype.")
+    val body = mbody(m, i, i)
+    if (body.isEmpty) None else Some(body.get._2.map(p => p._1), body.get._3._1)
+  }
+  def mostSpecific(m: String, i: String, j: String): Set[String] = {
[…]

### 2018-03-20 Calculus/src/framework/Main.scala

@@ -1,6 +1,7 @@
 package framework
 
 import scala.io.Source
+import AST._
 
 object Main {
   def run(fileName: String): Unit = {
@@ -8,33 +9,37 @@ object Main {
     val parsed = FHJParser.parse(program)
     if (parsed.isLeft) println(parsed.left.get)
     else {
-      val pretty = parsed.right.get.toString
-      println(pretty + "\n")
-      val eval = parsed.right.get.run
-      if (eval.isLeft) println("Type-check: " + eval.left.get)
-      else println("==> " + eval.right.get.toString)
+      val p: Program = parsed.right.get
+      println(Pretty.pretty(p) + "\n")
+      try {
+        val info = Preprocessor.createInfo(p)
+        val typeCheck = p.programCheck(info)
+        val eval = new Semantics(info, p.e).eval
+      } catch {
+        case _ => println("ERROR")
+      }
     }
   }               
   
   def main(args : Array[String]) = {
     println("----------------------------------\nExample (a):\n")
-    run("Example_a")
+    run("Example_a") // <A> new A()
     println("----------------------------------\nExample (b):\n")
-    run("Example_b")
+    run("Example_b") // <A> new C()
     println("----------------------------------\nExample (c):\n")
-    run("Example_c")
+    run("Example_c") // <A> new C()
     println("----------------------------------\nExample (d):\n")
-    run("Example_d")
+    run("Example_d") // Type-check: Interface check failed
     println("----------------------------------\nExample (e):\n")
-    run("Example_e")
+    run("Example_e") // Type-check: Interface check failed
     println("----------------------------------\nExample (f):\n")
-    run("Example_f")
+    run("Example_f") // <T> new C()
     println("----------------------------------\nExample (Problem 1):\n")
-    run("Example_p1")
+    run("Example_p1") // <Void> new FromDeck()
     println("----------------------------------\nExample (Problem 2):\n")
-    run("Example_p2")
+    run("Example_p2") // <Void> new FromSafeDeck()
     println("----------------------------------\nExample (Problem 3):\n")
-    run("Example_p3")
+    run("Example_p3") // <Void> new FromDrawableSafeDeck()
     println("----------------------------------")
   }
   

### 2018-03-20 Calculus/src/framework/Parser.scala

@@ -2,10 +2,9 @@ package framework
 
 import scala.util.parsing.combinator._
 import scala.util.parsing.combinator.syntactical._
+import AST._
 
 object FHJParser extends StandardTokenParsers with PackratParsers {
-  import FHJ._
-  
   lexical.reserved += ("interface", "extends", "return", "new", "override", "super")
   lexical.delimiters += ("(", ")", "{", "}", ",", ".", "::", ";")
   

### 2018-03-20 Calculus/src/framework/Preprocessor.scala

@@ -1,0 +1,21 @@
+package framework
+
+import AST._
+
+object Preprocessor {
+  def createInfo(program: Program): Info = {
+    val is: List[TypeDef] = program.is
+    val e = program.e
+    val table = is.map(x => x.name)
+    assert(table.distinct.size == table.size, "Pre-processor: class name conflicts.")
+    val typeMap = is.map(x => {
+      assert(x.sups.distinct.size == x.sups.size, "Pre-processor: super types of " + x.name + " conflict.")
+      assert(x.sups.forall(y => table.contains(y)), "Pre-processor: super types of " + x.name + " undefined.")
+      x.name -> x.sups}).toMap
+    val methodMap = is.map(x => {
+      val methods = x.methods.map(y => (y.name, y.update))
+      assert(methods.distinct.size == methods.size, "Pre-processor: methods of " + x.name + " conflict.")
+      x.name -> x.methods}).toMap
+    new Info(table, typeMap, methodMap, is.map(x => x.name -> x).toMap)
+  }
+}

### 2018-03-20 Calculus/src/framework/Pretty.scala

@@ -1,0 +1,29 @@
+package framework
+
+import AST._
+
+object Pretty {
+  def pretty(p: Program): String = {
+    val isStr = if (p.is.isEmpty) "" else p.is.map(pretty(_)).reduce((a, b) => a + "\n" + b) + "\n\n"
+    isStr + pretty(p.e)
+  }
+  def pretty(t: TypeDef): String = {
+    val supStr = if (t.sups.isEmpty) "" else " extends " + t.sups.reduce((a, b) => a + ", " + b)
+    val methodsStr = if (t.methods.size == 0) "{}" else "{\n" + t.methods.map(pretty(_)).reduce((a, b) => a + "\n" + b) + "\n}"
+    "interface " + t.name + supStr + " " + methodsStr
+  }
+  def pretty(m: MethDef): String = {
+      val parasStr = if (m.paras.isEmpty) "" else m.paras.map(p => p._1 + " " + p._2).reduce((a, b) => a + ", " + b)
+      val body = if (m.returnExpr.isEmpty) ";" else " {\n    return " + pretty(m.returnExpr.get) + ";\n  }"
+      "  " + m.returnType + " " + m.name + "(" + parasStr + ") override " + m.update + body
+  }
+  def pretty(e: Expr): String = e match {
+    case Var(n) => n
+    case New(o) => "new "+ o + "()"
+    case Invk(e, m, args) => {
+      val argsStr = if (args.isEmpty) "" else args.map(pretty(_)).reduce((a, b) => a + ", " + b)
+      pretty(e) + "." + m + "(" + argsStr + ")"
+    }
+    case AnnoExpr(i, e) => "((" + i + ") " + pretty(e) + ")"
+  }
+}

### 2018-03-21 Calculus/src/framework/AST.scala
More impl.

@@ -1,20 +1,22 @@
 package framework
 
+import CompilationError._
+
 object AST {
   case class Program(is: List[TypeDef], e: Expr) {
     def programCheck(info: Info): String = {
       var checked: Set[String] = Set()
       for (t <- info.table) {
         if (!checked(t)) {
-          assert(info.typeMap.contains(t))
+          assert(info.typeMap.contains(t), TypeNotFound(t))
           for (t0 <- info.typeMap(t)) {
             if (!checked(t0)) {
-              assert(info.typeMap.contains(t0))
-              assert(info.typeDefMap(t0).interfaceCheck(info))
+              assert(info.typeMap.contains(t0), TypeNotFound(t0))
+              try info.typeDefMap(t0).interfaceCheck(info) catch {case error: Throwable => nextError(error, TypeError(t0))}
               checked += t0
             }
           }
-          assert(info.typeDefMap(t).interfaceCheck(info))
+          try info.typeDefMap(t).interfaceCheck(info) catch {case error: Throwable => nextError(error, TypeError(t))}
           checked += t
         }
       }
@@ -23,38 +25,38 @@ object AST {
   }
   
   case class TypeDef(name: String, sups: List[String], methods: List[MethDef]) {
-    def interfaceCheck(info: Info): Boolean = {
-      assert(sups.forall(x => info.table.contains(x)))
-      assert(methods.forall(x => x.methodCheck(info, name)))
+    def interfaceCheck(info: Info): Unit = {
+      for (x <- sups) assert(info.table.contains(x), TypeNotFound(x))
+      for (x <- methods) try x.methodCheck(info, name) catch {case error: Throwable => nextError(error, MethError(x))}
       val collectMethods = info.collectMethods(name)
       val cond1 = !(collectMethods.exists(m => info.table.exists(j => info.subType(name, j) &&
           info.mtype(m, j).isDefined && info.mbody(m, name, j).isEmpty)))
       val cond2 = !(collectMethods.exists(m => info.table.exists(j => info.subType(name, j) &&
           info.dispatch(name, m, name).isDefined && info.dispatch(j, m, j).isDefined &&
               !info.canOverride(m, name, j))))
-      assert(cond1, "Type-checker: condition 2 unsatisfied for type " + name + " on interface check.")
-      assert(cond2, "Type-checker: condition 3 unsatisfied for type " + name + " on interface check.")
-      true
[…]

### 2018-03-21 Calculus/src/framework/Main.scala

@@ -2,6 +2,7 @@ package framework
 
 import scala.io.Source
 import AST._
+import CompilationError._
 
 object Main {
   def run(fileName: String): Unit = {
@@ -15,9 +16,7 @@ object Main {
         val info = Preprocessor.createInfo(p)
         val typeCheck = p.programCheck(info)
         val eval = new Semantics(info, p.e).eval
-      } catch {
-        case _ => println("ERROR")
-      }
+      } catch {case error: Throwable => printError(error)}
     }
   }               
   

### 2018-03-21 Calculus/src/framework/Preprocessor.scala

@@ -1,20 +1,21 @@
 package framework
 
 import AST._
+import CompilationError._
 
 object Preprocessor {
   def createInfo(program: Program): Info = {
     val is: List[TypeDef] = program.is
     val e = program.e
     val table = is.map(x => x.name)
-    assert(table.distinct.size == table.size, "Pre-processor: class name conflicts.")
+    assert(table.distinct.size == table.size, Message("Pre-processor: interface names conflict."))
     val typeMap = is.map(x => {
-      assert(x.sups.distinct.size == x.sups.size, "Pre-processor: super types of " + x.name + " conflict.")
-      assert(x.sups.forall(y => table.contains(y)), "Pre-processor: super types of " + x.name + " undefined.")
+      assert(x.sups.distinct.size == x.sups.size, Message("Pre-processor: super types of " + x.name + " conflict."))
+      for (y <- x.sups) assert(table.contains(y), TypeNotFound(y))
       x.name -> x.sups}).toMap
     val methodMap = is.map(x => {
       val methods = x.methods.map(y => (y.name, y.update))
-      assert(methods.distinct.size == methods.size, "Pre-processor: methods of " + x.name + " conflict.")
+      assert(methods.distinct.size == methods.size, Message("Pre-processor: methods of " + x.name + " conflict."))
       x.name -> x.methods}).toMap
     new Info(table, typeMap, methodMap, is.map(x => x.name -> x).toMap)
   }

### 2018-03-21 Calculus_Ext/src/framework/AST.scala
Done impl.

@@ -1,0 +1,118 @@
+package framework
+
+import CompilationError._
+
+object AST {
+  case class Program(is: List[TypeDef], e: Expr) {
+    def programCheck(info: Info): String = {
+      var checked: Set[String] = Set()
+      for (t <- info.table) {
+        if (!checked(t)) {
+          assert(info.typeMap.contains(t), TypeNotFound(t))
+          for (t0 <- info.typeMap(t)) {
+            if (!checked(t0)) {
+              assert(info.typeMap.contains(t0), TypeNotFound(t0))
+              try info.typeDefMap(t0).interfaceCheck(info) catch {case error: Throwable => nextError(error, TypeError(t0))}
+              checked += t0
+            }
+          }
+          try info.typeDefMap(t).interfaceCheck(info) catch {case error: Throwable => nextError(error, TypeError(t))}
+          checked += t
+        }
+      }
+      e.checkType(info, Map())
+    }
+  }
+  
+  case class TypeDef(name: String, sups: List[String], methods: List[MethDef]) {
+    def interfaceCheck(info: Info): Unit = {
+      for (x <- sups) assert(info.table.contains(x), TypeNotFound(x))
+      for (x <- methods) try x.methodCheck(info, name) catch {case error: Throwable => nextError(error, MethError(x))}
+      val collectMethods = info.collectMethods(name)
+      val cond1 = !(collectMethods.exists(m => info.table.exists(j => info.subType(name, j) &&
+          info.mtype(m, j).isDefined && info.mbody(m, name, j).isEmpty)))
+      val cond2 = !(collectMethods.exists(m => info.table.exists(j => info.subType(name, j) &&
+          info.dispatch(name, m, name).isDefined && info.dispatch(j, m, j).isDefined &&
+              !info.canOverride(m, name, j))))
+      assert(cond1, Message("Condition 2 unsatisfied for interface " + name + "."))
+      assert(cond2, Message("Condition 3 unsatisfied for interface " + name + "."))
+    }
+  }
+  
+  case class MethDef(returnType: String, name: String, paras: List[(String, String)],
+      update: List[String], returnExpr: Option[Expr]) {
+    def methodCheck(info: Info, thisType: String): Unit = {
+      assert(info.table.contains(returnType), TypeNotFound(returnType))
+      for (x <- update) assert(info.table.contains(x), TypeNotFound(x))
[…]

### 2018-03-21 Calculus_Ext/src/framework/CompilationError.scala

@@ -1,0 +1,21 @@
+package framework
+
+import AST._
+
+object CompilationError {
+  case class TypeError(t: String) extends Throwable
+  case class MethError(m: MethDef) extends Throwable
+  case class TypeNotFound(t: String) extends Throwable
+  case class VarNotInScope(x: String) extends Throwable
+  case class Message(s: String) extends Throwable
+  
+  def assert[A](f: Boolean, exception: Throwable): Unit = if (!f) throw exception
+  def nextError(f: Throwable, g: Throwable): Unit = {printError(f); throw g}
+  def printError(f: Throwable): Unit = f match {
+    case TypeNotFound(t)  => println("Type " + t + " not found.")
+    case VarNotInScope(x) => println("Variable " + x + " not in scope.")
+    case Message(s)       => println("Error: " + s)
+    case MethError(m)     => println("MethCheck failed: " + Pretty.pretty(m))
+    case TypeError(t)     => println("InterfaceCheck failed: " + t)
+  }
+}

### 2018-03-21 Calculus_Ext/src/framework/FHJ.scala

@@ -1,251 +1,0 @@
-package framework
-
-object FHJ {
-  /* Environment. */
-  type Env = {val info: Info; val gamma: Map[String, String]}
-  
-  /* Abstract syntax tree. */
-  /* Typing and semantic rules. */
-  case class TypeDef(name: String, sups: List[String], methods: List[MethDef]) {
-    def interfaceCheck(env: Env): Boolean = {
-      if (sups.exists(x => !env.info.table.contains(x))) return false
-      val env2: Env = new {val info = env.info; val gamma = env.gamma + ("this" -> name)}
-      if (methods.exists(x => !x.methodCheck(env2))) return false
-      val collectMethods = env.info.collectMethods(name)
-      val cond1 = !(collectMethods.exists(m => env.info.table.exists(j => env.info.subType(name, j) &&
-          env.info.mtype(m, j).isDefined && env.info.mbody(m, name, j).isEmpty)))
-      val cond2 = !(collectMethods.exists(m => env.info.table.exists(j => env.info.subType(name, j) &&
-          env.info.dispatch(name, m, name).isDefined && env.info.dispatch(j, m, j).isDefined &&
-              !env.info.canOverride(m, name, j))))
-      cond1 && cond2
-    }
-    override def toString = {
-      val supStr = if (sups.isEmpty) "" else " extends " + sups.reduce((a, b) => a + ", " + b)
-      "interface " + name + supStr + " " +
-        (if (methods.size == 0) "{}" else "{\n" + methods.map(x => x.toString).reduce((a, b) => a + "\n" + b) + "\n}")
-    }
-  }
-  
-  case class MethDef(returnType: String, name: String, paras: List[(String, String)],
-      update: List[String], returnExpr: Option[Expr]) {
-    def methodCheck(env: Env): Boolean = {
-      if (!env.info.table.contains(returnType)) return false
-      if (update.exists(x => !env.info.table.contains(x))) return false
-      if (paras.map(p => p._1).exists(x => !env.info.table.contains(x))) return false
-      val thisType = env.gamma.get("this").get
-      if (update.exists(x => !env.info.subType(thisType, x))) return false
-      if (returnExpr.isDefined) {
-        val env2: Env = new {val info = env.info; val gamma = env.gamma ++ paras.map(p => p._2 -> p._1).toMap}
-        for (x <- update) {
-          val mtype = env.info.mtype(name, x)
[…]

### 2018-03-21 Calculus_Ext/src/framework/Info.scala

@@ -1,0 +1,68 @@
+package framework
+
+import AST._
+
+case class Info(table: List[String], typeMap: Map[String, List[String]],
+    methodMap: Map[String, List[MethDef]], typeDefMap: Map[String, TypeDef]) {
+  def ext(t1: String, t2: String): Boolean = {
+    assert(table.contains(t1) && table.contains(t2), "Bug: ext.")
+    typeMap.get(t1).contains(t2)
+  }
+  def subType(t1: String, t2: String): Boolean = {
+    assert(table.contains(t1) && table.contains(t2), "Bug: subType.")
+    if (t1 == t2) return true
+    typeMap.get(t1).get.exists(x => subType(x, t2))
+  }
+  def dispatch(i: String, m: String, j: String): Option[MethDef] = {
+    assert(table.contains(i) && table.contains(j), "Bug: dispatch.")
+    methodMap.get(i).get.find(x => x.name == m && x.update.contains(j))
+  }
+  def prune(set: Set[String]): Set[String] = set.filter(i => !set.exists(j => j != i && subType(j, i)))
+  def collectMethods(i: String): Set[String] = {
+    assert(table.contains(i), "Bug: collectMethods.")
+    val start = methodMap.get(i).get.map(x => x.name).toSet
+    val op = (s: Set[String], x: String) => s ++ collectMethods(x)
+    typeMap.get(i).get.foldLeft(start)(op)
+  }
+  def mbody(m: String, id: String, is: String): Option[(String, List[(String, String)], (String, Option[Expr]))] = {
+    assert(table.contains(id) && table.contains(is), "Bug: mbody.")
+    val set1 = mostSpecific(m, id, is)
+    if (set1.size != 1) return None
+    val i = set1.head
+    val set2 = mostSpecificOverride(m, id, i)
+    if (set2.size != 1) return None
+    val j = set2.head
+    val method = methodMap.get(j).get.find(x => x.name == m && x.update.contains(i))
+    if (method.isEmpty) None else Some(j, method.get.paras, (method.get.returnType, method.get.returnExpr))
+  }
+  def mtype(m: String, i: String): Option[(List[String], String)] = {
+    assert(table.contains(i), "Bug: mtype.")
+    val body = mbody(m, i, i)
+    if (body.isEmpty) None else Some(body.get._2.map(p => p._1), body.get._3._1)
+  }
[…]

### 2018-03-21 Calculus_Ext/src/framework/Main.scala

@@ -1,6 +1,8 @@
 package framework
 
 import scala.io.Source
+import AST._
+import CompilationError._
 
 object Main {
   def run(fileName: String): Unit = {
@@ -8,35 +10,37 @@ object Main {
     val parsed = FHJParser.parse(program)
     if (parsed.isLeft) println(parsed.left.get)
     else {
-      val pretty = parsed.right.get.toString
-      println(pretty + "\n")
-      val eval = parsed.right.get.run
-      if (eval.isLeft) println("Type-check: " + eval.left.get)
-      else println("==> " + eval.right.get.toString)
+      val p: Program = parsed.right.get
+      println(Pretty.pretty(p) + "\n")
+      try {
+        val info = Preprocessor.createInfo(p)
+        val typeCheck = p.programCheck(info)
+        val eval = new Semantics(info, p.e).eval
+      } catch {case error: Throwable => printError(error)}
     }
   }               
   
   def main(args : Array[String]) = {
     println("----------------------------------\nExample (a):\n")
-    run("Example_a")
+    run("Example_a")  // <A> new A()
     println("----------------------------------\nExample (b):\n")
-    run("Example_b")
+    run("Example_b")  // <A> new C()
     println("----------------------------------\nExample (c):\n")
-    run("Example_c")
+    run("Example_c")  // <A> new C()
     println("----------------------------------\nExample (d):\n")
-    run("Example_d")
+    run("Example_d")  // Type-check: Interface check failed
     println("----------------------------------\nExample (e):\n")
-    run("Example_e")
+    run("Example_e")  // Type-check: Interface check failed
     println("----------------------------------\nExample (f):\n")
-    run("Example_f")
+    run("Example_f")  // <T> new C()
     println("----------------------------------\nExample (Problem 1):\n")
-    run("Example_p1")
+    run("Example_p1") // <Void> new FromDeck()
     println("----------------------------------\nExample (Problem 2):\n")
-    run("Example_p2")
+    run("Example_p2") // <Void> new FromSafeDeck()
     println("----------------------------------\nExample (Problem 3):\n")
-    run("Example_p3")
+    run("Example_p3") // <Void> new FromDrawableSafeDeck()
     println("----------------------------------\nExample (g):\n")
-    run("Example_g")
+    run("Example_g")  // ((T) new FromAB())
     println("----------------------------------")
   }
   

### 2018-03-21 Calculus_Ext/src/framework/Parser.scala

@@ -2,9 +2,9 @@ package framework
 
 import scala.util.parsing.combinator._
 import scala.util.parsing.combinator.syntactical._
+import AST._
 
 object FHJParser extends StandardTokenParsers with PackratParsers {
-  import FHJ._
   
   lexical.reserved += ("interface", "extends", "return", "new", "override", "super")
   lexical.delimiters += ("(", ")", "{", "}", ",", ".", "::", ";")

### 2018-03-21 Calculus_Ext/src/framework/Preprocessor.scala

@@ -14,9 +14,18 @@ object Preprocessor {
       for (y <- x.sups) assert(table.contains(y), TypeNotFound(y))
       x.name -> x.sups}).toMap
     val methodMap = is.map(x => {
-      val methods = x.methods.map(y => (y.name, y.update))
-      assert(methods.distinct.size == methods.size, Message("Pre-processor: methods of " + x.name + " conflict."))
-      x.name -> x.methods}).toMap
+      var updateMap: Map[String, List[String]] = Map()
+      for (eachMethod <- x.methods) {
+        val mName = eachMethod.name
+        val mUpdate = eachMethod.update
+        updateMap += mName -> (updateMap.getOrElse(mName, List()) ++ mUpdate)
+      }
+      for (value <- updateMap.values) {
+        assert(value.distinct.size == value.size, Message("Pre-processor: multiple updates conflict in " + x.name + "."))
+        assert(value.size <= 1 || !value.contains(x.name),
+            Message("Pre-processor: multiple updates of " + x.name + " containing itself."))
+      }
+    x.name -> x.methods}).toMap
     new Info(table, typeMap, methodMap, is.map(x => x.name -> x).toMap)
   }
 }

### 2018-03-21 Calculus_Ext/src/framework/Pretty.scala

@@ -1,0 +1,29 @@
+package framework
+
+import AST._
+
+object Pretty {
+  def pretty(p: Program): String = {
+    val isStr = if (p.is.isEmpty) "" else p.is.map(pretty(_)).reduce((a, b) => a + "\n" + b) + "\n\n"
+    isStr + pretty(p.e)
+  }
+  def pretty(t: TypeDef): String = {
+    val supStr = if (t.sups.isEmpty) "" else " extends " + t.sups.reduce((a, b) => a + ", " + b)
+    val methodsStr = if (t.methods.size == 0) "{}" else "{\n" + t.methods.map(pretty(_)).reduce((a, b) => a + "\n" + b) + "\n}"
+    "interface " + t.name + supStr + " " + methodsStr
+  }
+  def pretty(m: MethDef): String = {
+      val parasStr = if (m.paras.isEmpty) "" else m.paras.map(p => p._1 + " " + p._2).reduce((a, b) => a + ", " + b)
+      val body = if (m.returnExpr.isEmpty) ";" else " {\n    return " + pretty(m.returnExpr.get) + ";\n  }"
+      "  " + m.returnType + " " + m.name + "(" + parasStr + ") override " + m.update.reduce((a, b) => a + ", " + b) + body
+    }
+  def pretty(e: Expr): String = e match {
+    case Var(n) => n
+    case New(o) => "new "+ o + "()"
+    case Invk(e, m, args) => {
+      val argsStr = if (args.isEmpty) "" else args.map(pretty(_)).reduce((a, b) => a + ", " + b)
+      pretty(e) + "." + m + "(" + argsStr + ")"
+    }
+    case AnnoExpr(i, e) => "((" + i + ") " + pretty(e) + ")"
+  }
+}

### 2018-03-21 Calculus_Ext/src/framework/Semantics.scala

@@ -1,0 +1,45 @@
+package framework
+
+import AST._
+
+class Semantics(info: Info, expr: Expr) {
+  val eval: Expr = eval(expr)
+  
+  case object NoRuleApplies extends Throwable
+  case object Buggy extends Throwable
+  
+  def isVal(e: Expr): Boolean = e match {
+    case AnnoExpr(_, New(_)) => true
+    case _                   => false
+  }
+  
+  def eval1(e: Expr): Expr = e match {
+    case New(i) => AnnoExpr(i, New(i))
+    case Invk(AnnoExpr(j, New(i)), m, args) => {
+      for (index <- 0 to args.length - 1) {
+        val arg = args(index)
+        if (!isVal(arg)) return Invk(AnnoExpr(j, New(i)), m, args.updated(index, eval1(arg)))
+      }
+      val mbody = info.mbody(m, i, j).get
+      val i0 = mbody._1
+      val params = mbody._2
+      val ie = mbody._3._1
+      val e0 = mbody._3._2.get
+      val map = params.zip(args).map(p => p._1._2 -> AnnoExpr( p._1._1, p._2)).toMap + ("this" -> AnnoExpr(i0, New(i)))
+      AnnoExpr(ie, e0.subst(map))
+    }
+    case Invk(e0, m, args) => Invk(eval1(e0), m, args)
+    case AnnoExpr(i, AnnoExpr(j, New(k))) => AnnoExpr(i, New(k))
+    case AnnoExpr(_, New(_)) => throw NoRuleApplies
+    case AnnoExpr(i, e0) => AnnoExpr(i, eval1(e0))
+    case Var(_) => throw Buggy
+    case _ => throw NoRuleApplies
+  }
+  
+  def eval(e: Expr): Expr = {
+    try {println("==> " + Pretty.pretty(e)); eval(eval1(e))} catch {
+      case NoRuleApplies => e
+      case Buggy         => throw new Exception("Wrong evaluation.")
+    }
+  }
+}

### 2018-04-21 UnintentionalStateConflict/paper0/paper.tex
merge UnintentionalStateConflict repo to MIM repo

--- 2017-10-20 NewVersion/paper.tex
@@
 \newcommand{\authorText}[2]{{\color{#1}#2}}
-
-% \newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
-% \newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
-% \newcommand\marco[1]{\authornote{marco}{blue}{#1}}
-% \newcommand\marcoT[1]{\authorText{blue}{#1}}
-% \newcommand\haoyuan[1]{\authornote{haoyuan}{orange}{#1}}
-
-\newcommand\bruno[1]{}
-\newcommand\yanlin[1]{}
-\newcommand\marco[1]{}
-\newcommand\haoyuan[1]{}
 
@@
 
+\newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
+\newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
+\newcommand\marco[1]{\authornote{marco}{blue}{#1}}
+\newcommand\marcoT[1]{\authorText{blue}{#1}}
+\newcommand\haoyuan[1]{\authornote{haoyuan}{orange}{#1}}
+
 \begin{document}
 
-% \title{Untangling Unintended Conflicts with Hierarchical Dispatch}
-% \title{FHJ: A Formal Model for Resolving Unintended Conflicts in Multiple Inheritance}
-\title{FHJ: A Formal Model for Hierarchical Dispatching and Overriding}
-%\subtitle{\InterfaceBased Programming for the Masses}
-
-% \authorinfo{NoAuthor}
-%            {The University of Hong Kong, China}
-% %           {\{ylwang,hyzhang,bruno\}@cs.hku.hk}
-% %\authorinfo{Marco Servetto}
-% %          {Victoria University of Wellington, New Zealand}
-% %          {marco.servetto@ecs.vuw.ac.nz}
-\author{Yanlin Wang\inst{1} \and Haoyuan Zhang\inst{1} \and Bruno C.d.S. Oliveira\inst{1} \and Marco Servetto\inst{2}}
-\institute{The University of Hong Kong \and Victoria University of Wellington \\ \email{\{ylwang,hyzhang,bruno\}@cs.hku.hk, marco.servetto@ecs.vuw.ac.nz}}
-
-\maketitle
-
-\vspace{-4ex}
-
-\begin{abstract}
-Multiple inheritance is a valuable feature for Object-Oriented
-Programming. However, it is also tricky to get right, as illustrated by
-the extensive literature on the topic. A key issue 
-is the \emph{ambiguity} arising from inheriting multiple parents,
-which can have conflicting methods. 
-Numerous existing work provides solutions for 
-conflicts which arise from \emph{diamond inheritance}: i.e.
-conflicts that arise from implementations sharing a common 
-ancestor. However, most mechanisms are inadequate to deal 
-with \emph{unintentional method conflicts}: conflicts which 
-arise from two unrelated methods that happen to share the same name
-and signature.
-
-\begin{comment}
-One of the most promising 
-approaches to multiple inheritance is the \emph{trait} model. Traits offer a
-restricted model of multiple inheritance that is easy to reason and 
-have many elegant properties. Traits have good support for method 
-conflicts which arise from \emph{diamond inheritance}:
-conflicts that arise from method implementations sharing a common 
-ancestor. However, the mechanisms of traits are inadequate to deal 
-with \emph{unintentional method conflicts}: conflicts which 
-arise from two unrelated methods that happen to share the same name
-and signature. 
-\end{comment}
-
-This paper presents a new model called \emph{\textbf{F}eatherweight
-  \textbf{H}ierarchical \textbf{J}ava} (\name{}) that deals with
-unintentional method conflicts.  In our new model, which is partly
-inspired by C++, conflicting methods arising from unrelated methods
-can coexist in the same class, and \emph{hierarchical dispatching}
-supports unambiguous lookups in the presence of such conflicting
-methods.  To avoid ambiguity, hierarchical information is employed in
-method dispatching, which uses a combination of static and dynamic
-type information to choose the implementation of a method at run-time.
-Furthermore, unlike all existing inheritance models, our model
-supports \emph{hierarchical method overriding}: that is, methods can
-be \emph{independently overridden} along the multiple inheritance
-hierarchy. We give illustrative examples of our language and features
-and formalize \name{} as a minimal Featherweight-Java style calculus.
-
-\begin{comment}
-Furthermore we discuss similarities and differences to
-
-What ensures unambiguity is the use of information about
-the class hierarchy.
-
-\name{} is partly inspired by the method resolution semantics
-of C++, but it also incoorporates ideas from the trait model and Java
-8's default methods. We discuss the similarities
-and differences with and also advantages and disadvantages. 
-\end{comment}
-
-\end{abstract}
-
-\input{sections/Introduction.tex}
-\input{sections/Overview.tex}
 \input{sections/Formalization.tex}
-\input{sections/Auxiliary.tex}
-\input{sections/Discussion.tex}
-\input{sections/RelatedWork.tex}
-\input{sections/Conclusion.tex}
-
-\begin{comment}
-\section*{Acknowledgments}\label{sec:Acknowledgments}
-
-Authors would like to thank YYYYY.
-\end{comment}
-
-% \newpage
-% \clearpage
-% \bibliographystyle{abbrvnat}
-
-\newpage
-\bibliographystyle{splncs03}
-\bibliography{paper}
-
-\newpage
-\appendix
-\input{sections/Appendix.tex}
-% \input{sections/Appendix_Formalization.tex}
-% \input{sections/Translation.tex}
-% \input{sections/Appendix_Translation.tex}
 

### 2018-04-21 UnintentionalStateConflict/CalculusX/src/framework/FHJ.scala

@@ -1,0 +1,357 @@
+package framework
+
+object FHJ {
+  /* Environment. */
+  type Env = {val info: Info; val gamma: Map[String, String]}
+  
+  /* Abstract syntax tree. */
+  /* Typing and semantic rules. */
+  case class TypeDef(name: String, sups: List[String], methods: List[MethDef], constr: Option[MC]) {
+    def interfaceCheck(env: Env): Boolean = {
+      if (constr.isDefined) { if (!constr.get.mcCheck(env, name)) return false }
+      if (sups.exists(x => !env.info.table.contains(x))) return false
+      val env2: Env = new {val info = env.info; val gamma = env.gamma + ("this" -> name)}
+      if (methods.exists(x => !x.methodCheck(env2))) return false
+      val collectMethods = env.info.collectMethods(name)
+      val cond1 = !(collectMethods.exists(m => env.info.table.exists(j => env.info.subType(name, j) &&
+          env.info.mtype(m, j).isDefined && env.info.mbody(m, name, j).isEmpty)))
+      val cond2 = !(collectMethods.exists(m => env.info.table.exists(j => env.info.subType(name, j) &&
+          env.info.dispatch(name, m, name).isDefined && env.info.dispatch(j, m, j).isDefined &&
+              !env.info.canOverride(m, name, j))))
+      cond1 && cond2 && setterCheck()
+    }
+    def setterCheck(): Boolean = {
+      methods.forall(method => {
+        val s = method.parseSetter()
+        if (s.isEmpty) return true //not a setter format
+        val fieldName = s.get._1
+        val paras = s.get._2
+        val update = s.get._3
+        val returnType = s.get._4
+        if (paras.size != 1) return false
+        val fieldType = paras.head._1;
+        
+//        val getter = findGetter(methods, fieldName
+        throw new Exception("TODO")
+      })
+    }
+     
+    override def toString = {
+      val supStr = if (sups.isEmpty) "" else " extends " + sups.reduce((a, b) => a + ", " + b)
+      val mcStr = if(constr.isEmpty) "" else constr.get.toString() + "\n"
+      val methodsStr = if (methods.size == 0) "" else  methods.map(x => x.toString).reduce((a, b) => a + "\n" + b) 
+      "interface " + name + supStr + " " + "{\n" + mcStr + methodsStr + "\n}"
+    }
+  }
[…]

### 2018-04-21 UnintentionalStateConflict/CalculusX/src/framework/Main.scala

@@ -1,0 +1,43 @@
+package framework
+
+import scala.io.Source
+
+object Main {
+  def run(fileName: String): Unit = {
+    val program = Source.fromFile("examples/" + fileName + ".fhj").mkString
+    val parsed = FHJParser.parse(program)
+    if (parsed.isLeft) println(parsed.left.get)
+    else {
+      val pretty = parsed.right.get.toString
+      println(pretty + "\n")
+      val eval = parsed.right.get.run
+      if (eval.isLeft) println("Type-check: " + eval.left.get)
+      else println("==> " + eval.right.get.toString)
+    }
+  }               
+  
+  def main(args : Array[String]) = {
+//    println("----------------------------------\nExample (a):\n")
+//    run("Example_a")
+//    println("----------------------------------\nExample (b):\n")
+//    run("Example_b")
+//    println("----------------------------------\nExample (c):\n")
+//    run("Example_c")
+//    println("----------------------------------\nExample (d):\n")
+//    run("Example_d")
+//    println("----------------------------------\nExample (e):\n")
+//    run("Example_e")
+//    println("----------------------------------\nExample (f):\n")
+//    run("Example_f")
+//    println("----------------------------------\nExample (Problem 1):\n")
+//    run("Example_p1")
+//    println("----------------------------------\nExample (Problem 2):\n")
+//    run("Example_p2")
+//    println("----------------------------------\nExample (Problem 3):\n")
+//    run("Example_p3")
+//    println("----------------------------------")
+    println("----------------------------------\nExample (x):\n")
+    run("Example_x")
+  }
+  
+}

### 2018-04-21 UnintentionalStateConflict/CalculusX/src/framework/Parser.scala

@@ -1,0 +1,44 @@
+package framework
+
+import scala.util.parsing.combinator._
+import scala.util.parsing.combinator.syntactical._
+
+object FHJParser extends StandardTokenParsers with PackratParsers {
+  import FHJ._
+  
+  lexical.reserved += ("interface", "extends", "return", "override", "super", "static")
+  lexical.delimiters += ("(", ")", "{", "}", ",", ".", "::", ";")
+  
+  val lcid = ident ^? { case id if id.charAt(0).isLower => id }
+  val ucid = ident ^? { case id if id.charAt(0).isUpper => id }
+  
+  object Parser {
+    val pMC: PackratParser[MC] = ("static" ~> ucid) ~ lcid ~ ("(" ~>
+      repsep(ucid ~ ucid ~ ("." ~> lcid) ^^ { case x1 ~ x2 ~ x3 => (x1, x2, x3)}, ",") <~ ")") ~ ";" ^^ {
+      case i ~ m ~ paras ~ j => new MC(i, m, paras)
+    } 
+    
+    val pP : PackratParser[Program] = rep(pTD) ~ pE ^^ { case l ~ e => new Program(l, e) }
+    val pTD : PackratParser[TypeDef] =
+      ("interface" ~> ucid) ~ ("extends" ~> repsep(ucid, ",") | success(List())) ~ ("{" ~> ((pMC ^^ {case x => Some(x)} | success(None)) ~ rep(pMD)) <~ "}") ^^
+        { case n ~ sups ~ (constr ~ ms) => new TypeDef(n, sups, ms, constr) }
+    val pMD : PackratParser[MethDef] =
+      ucid ~ lcid ~ ("(" ~> repsep(ucid ~ lcid ^^ { case t ~ n => (t, n) }, ",") <~ ")") ~
+        ("override" ~> ucid) ~ ("{" ~> ("return" ~> pE <~ ";") <~ "}" ^^ { case pE => Some(pE) } | ";" ^^^ None) ^^
+          { case t ~ m ~ paras ~ update ~ e => new MethDef(t, m, paras, update, e) }
+    val pE : PackratParser[Expr] =
+      pE ~ ("." ~> lcid) ~ ("(" ~> repsep(pE, ",") <~ ")") ^^
+        { case e ~ m ~ args => Invk(e, m, args) } |||
+      lcid ~ ("(" ~> repsep(pE, ",") <~ ")") ^^
[…]

### 2018-04-24 StateMIM-small/src/framework/AST.scala
USC type-checker (unfinished)

@@ -1,5 +1,6 @@
 package framework
 import Configuration._
+import Error._
 
 object AST {
   
@@ -18,7 +19,8 @@ object AST {
             val methods = x.methods.map(y => (y.name, y.update))
             if (methods.distinct.size != methods.size) error = true
             x.name -> x.methods}).toMap
-          if (error) None else Some(Info(table, typeMap, methodMap, is.map(x => x.name -> x).toMap))
+          val constructorMap = is.map(i => i.name -> i.constr).toMap
+          if (error) None else Some(Info(table, typeMap, methodMap, is.map(x => x.name -> x).toMap, constructorMap))
         }
       }
     }
@@ -26,36 +28,153 @@ object AST {
       val init = Config(H(Map(), 1), VS(List(BS(List()))), e, FS(List()))
       Semantics.eval(collectInfo.get, init)
     }
+    
+    def programCheck(info: Info): String = {
+      var checked: Set[String] = Set()
+      for (t <- info.table) {
+        if (!checked(t)) {
+          assert(info.typeMap.contains(t), TypeNotFound(t))
+          for (t0 <- info.typeMap(t)) {
+            if (!checked(t0)) {
+              assert(info.typeMap.contains(t0), TypeNotFound(t0))
+              try info.typeDefMap(t0).interfaceCheck(info) catch {case error: Throwable => nextError(error, TypeError(t0))}
+              checked += t0
+            }
+          }
+          try info.typeDefMap(t).interfaceCheck(info) catch {case error: Throwable => nextError(error, TypeError(t))}
+          checked += t
+        }
+      }
+      e.checkType(info, Map())
+    }
   }
   
-  case class TypeDef(name: String, sups: List[String], methods: List[MethDef], constr: Option[Constructor]) {}
+  case class TypeDef(name: String, sups: List[String], methods: List[MethDef], constr: Option[Constructor]) {
+    def interfaceCheck(info: Info): Unit = {
+      for (x <- sups) assert(info.table.contains(x), TypeNotFound(x))
+      for (x <- methods) try x.methodCheck(info, name) catch {case error: Throwable => nextError(error, MethError(x))}
+      val collectMethods = info.collectMethods(name)
+      val cond1 = !(collectMethods.exists(m => info.table.exists(j => info.subType(name, j) &&
+          info.mtype(m, j).isDefined && info.mbody(m, name, j).isEmpty)))
[…]

### 2018-04-24 StateMIM-small/src/framework/Error.scala

@@ -1,11 +1,25 @@
 package framework
 
 import Configuration._
+import AST._
 
 object Error {
+  case class TypeError(t: String) extends Throwable
+  case class MethError(m: MethDef) extends Throwable
+  case class TypeNotFound(t: String) extends Throwable
+  case class VarNotInScope(x: String) extends Throwable
+  case class Message(s: String) extends Throwable
   
   case object Buggy extends Throwable
   case object TODO extends Throwable
   case class Done(c: Config) extends Throwable
   
+  def nextError(f: Throwable, g: Throwable): Unit = {printError(f); throw g}
+  def printError(f: Throwable): Unit = f match {
+    case TypeNotFound(t)  => println("Type " + t + " not found.")
+    case VarNotInScope(x) => println("Variable " + x + " not in scope.")
+    case Message(s)       => println("Error: " + s)
+    case MethError(m)     => println("MethCheck failed: " + Pretty.pretty(m))
+    case TypeError(t)     => println("InterfaceCheck failed: " + t)
+  }
 }

### 2018-04-24 StateMIM-small/src/framework/Info.scala

@@ -2,7 +2,8 @@ package framework
 import AST._
 
 case class Info(table: List[String], typeMap: Map[String, List[String]],
-      methodMap: Map[String, List[MethDef]], typeDefMap: Map[String, TypeDef]) {
+      methodMap: Map[String, List[MethDef]], typeDefMap: Map[String, TypeDef], 
+      constructorMap: Map[String, Option[Constructor]]) {
   
   def isField(i: String, j: String, m: String): Option[(Int, String)] = {
     // see the of() method in class I.
@@ -31,8 +32,12 @@ case class Info(table: List[String], typeMap: Map[String, List[String]],
       val method = methodMap.get(j).get.find(x => x.name == m && x.update == i)
       //val error = throw new Exception()
       if (method.isEmpty) None else Some(j, method.get.paras, (method.get.returnType, method.get.returnExpr))
-    }
-  
+  }
+  def mtype(m: String, i: String): Option[(List[String], String)] = {
+    assert(table.contains(i), "Bug: mtype.")
+    val body = mbody(m, i, i)
+    if (body.isEmpty) None else Some(body.get._2.map(p => p.paramType), body.get._3._1)
+  }
   def mostSpecific(m: String, i: String, j: String): Set[String] = {
       if (!table.contains(i) || !table.contains(j)) throw new Exception("Error: mostSpecific.")
       val set = table.filter(k => subType(i, k) && (subType(k, j) || subType(j, k)) && dispatch(k, m, k).isDefined).toSet
@@ -57,7 +62,46 @@ case class Info(table: List[String], typeMap: Map[String, List[String]],
   }
   
   def prune(set: Set[String]): Set[String] = set.filter(i => !set.exists(j => j != i && subType(j, i)))
-  
+  def collectMethods(i: String): Set[String] = {
+    assert(table.contains(i), "Bug: collectMethods.")
+    val start = methodMap.get(i).get.map(x => x.name).toSet
+    val op = (s: Set[String], x: String) => s ++ collectMethods(x)
+    typeMap.get(i).get.foldLeft(start)(op)
+  }
+  def canOverride(m: String, i: String, j: String): Boolean = {
+    assert(table.contains(i) && table.contains(j), "Bug: canOverride.")
+    val meth = dispatch(i, m, i)
+    val meth2 = dispatch(j, m, j)
[…]

### 2018-04-24 StateMIM-small/src/framework/Main.scala

@@ -1,6 +1,7 @@
 package framework
 
 import scala.io.Source
+import AST._
 
 object Main {
   def run(fileName: String): Unit = {
@@ -8,10 +9,17 @@ object Main {
     val parsed = StateMIMParser.parse(program)
     if (parsed.isLeft) println(parsed.left.get)
     else {
-      val pretty = parsed.right.get.toString
+      val p: Program = parsed.right.get
+      val pretty = p.toString
       println(pretty + "\n")
-      val eval = parsed.right.get.eval()
-      println(eval)
+        val info: Info = p.collectInfo.get
+      try {
+        val typeCheck = p.programCheck(info)
+        println("Type check: ==> " + typeCheck)
+        val eval = parsed.right.get.eval()
+        println(eval)
+      } catch {case error: Throwable => Error.printError(error)}
+      
     }
   }     
   def main(args : Array[String]) = {    

### 2018-04-24 StateMIM-small/src/framework/Pretty.scala

@@ -1,0 +1,28 @@
+package framework
+
+import AST._
+
+object Pretty {
+  def pretty(p: Program): String = {
+    val isStr = if (p.is.isEmpty) "" else p.is.map(pretty(_)).reduce((a, b) => a + "\n" + b) + "\n\n"
+    isStr + pretty(p.e)
+  }
+  def pretty(t: TypeDef): String = {
+    val supStr = if (t.sups.isEmpty) "" else " extends " + t.sups.reduce((a, b) => a + ", " + b)
+    val methodsStr = if (t.methods.size == 0) "{}" else "{\n" + t.methods.map(pretty(_)).reduce((a, b) => a + "\n" + b) + "\n}"
+    "interface " + t.name + supStr + " " + methodsStr
+  }
+  def pretty(m: MethDef): String = {
+      val parasStr = if (m.paras.isEmpty) "" else m.paras.map(p => p.paramType + " " + p.name).reduce((a, b) => a + ", " + b)
+      val body = if (m.returnExpr.isEmpty) ";" else " {\n    return " + pretty(m.returnExpr.get) + ";\n  }"
+      "  " + m.returnType + " " + m.name + "(" + parasStr + ") override " + m.update + body
+  }
+  def pretty(e: Expr): String = e match {
+    case Var(n) => n
+    case Invk(e, m, args) => {
+      val argsStr = if (args.isEmpty) "" else args.map(pretty(_)).reduce((a, b) => a + ", " + b)
+      pretty(e) + "." + m + "(" + argsStr + ")"
+    }
+    case AnnoExpr(i, e) => "((" + i + ") " + pretty(e) + ")"
+  }
+}

### 2018-04-24 StateMIM-small/src/framework/Configuration.scala
Slight change.

@@ -26,8 +26,8 @@ object Configuration {
   }
   
   case class BS(varTable: List[(String, Value)]) {
-    def addLet(x: String, v: Value) = BS(varTable :+ (x, v))
-    def remLet() = BS(varTable.init)
+    def addLet(x: String, v: Value) = BS((x, v) +: varTable)
+    def remLet() = BS(varTable.tail)
   }
   
   case class VS(scopes: List[BS]) {

### 2018-04-24 StateMIM-small/src/framework/Semantics.scala

@@ -13,7 +13,6 @@ object Semantics {
     config.expr match {
       case Var(x) => Config(h, vs, vs.getVar(x), fs)
       case Invk(e, m, args) => {
-        println("Evaluating: " + config.expr.toString())
         if (!e.isValue) return Config(h, vs, e, fs.addFrame(Invk_E(m, args)))
         for (index <- 0 to args.length - 1) {
           if (!args(index).isValue)
@@ -29,15 +28,13 @@ object Semantics {
         
         val isField = info.isField(i, j2, m)
         if (args.length == 0 && isField.isDefined) { //Getters
-          println("Is getter")
           val resId = obj.fields(isField.get._1)
           Config(h, vs, Value(isField.get._2, resId), fs)
         } else { //Normal invocations
-          println("Is not getter")
           val paramsMap: List[(String, Value)] = mbody._2.zip(args).map(p => {
             val argValueId = p._2 match { case Value(_, vid) => vid }
             (p._1.name, Value(p._1.paramType, argValueId))
-          }) :+ ("this", eValue)
+          }) :+ ("this", Value(mbody._1, eValue.id))
           val newScope = vs.addScope(BS(paramsMap))
           Config(h, newScope, AnnoExpr(mbody._3._1, mbody._3._2.get), fs.addFrame(ReturnExprForInvk()))
         }

### 2018-04-24 StateMIM-small/src/framework/Error.scala
Problematic with fluent setter.

@@ -14,6 +14,7 @@ object Error {
   case object TODO extends Throwable
   case class Done(c: Config) extends Throwable
   
+  def assert[A](f: Boolean, exception: Throwable): Unit = if (!f) throw exception
   def nextError(f: Throwable, g: Throwable): Unit = {printError(f); throw g}
   def printError(f: Throwable): Unit = f match {
     case TypeNotFound(t)  => println("Type " + t + " not found.")
@@ -21,5 +22,6 @@ object Error {
     case Message(s)       => println("Error: " + s)
     case MethError(m)     => println("MethCheck failed: " + Pretty.pretty(m))
     case TypeError(t)     => println("InterfaceCheck failed: " + t)
+    case e => e.printStackTrace()
   }
 }

### 2018-04-24 StateMIM-small/src/framework/Info.scala

@@ -97,11 +97,13 @@ case class Info(table: List[String], typeMap: Map[String, List[String]],
     typeMap(i).foldLeft(res)(op2)
   }
   def isField(info: Info, name: String, t: String) : Option[String] = {
-      if (info.mbody(name, t, t).isEmpty) None
-      if (info.mbody(name, t, t).get._2.size != 0) None
-      if (info.mbody(name, t, t).get._3._2.isDefined) None
-      Some(info.mbody(name, t, t).get._3._1) //return field type
-    }
+    val mbody = info.mbody(name, t, t)
+    println("mbody(" + name + ", " + t + ", " + t + ") = " + mbody)
+    if (mbody.isEmpty) return None
+    if (mbody.get._2.size != 0) return None
+    if (mbody.get._3._2.isDefined) return None
+    Some(mbody.get._3._1) //return field type
+  }
 }
       
      

### 2018-04-24 ECOOP18/sections/Discussion.tex
fixing reviews for FHJ paper (unfinished)

@@
 The formal Featherweight Java model~\cite{Igarashi01FJ} does not include abstract methods because of the orthogonality
-to the core calculus. In traits, the
+to the core calculus. In traits, a
 similar idea is to use keywords like ``\textbf{require}'' for abstract method declarations~\cite{scharli03traits}.
@@
 In our formalized calculus, however, abstract methods are not a completely orthogonal feature. The $\canInstantiate$ function
-has to check whether an interface can be instantiated by looking at all the inherited branches and checking if each most specific method is abstract or not.
+has to check whether an interface can be instantiated by looking at all the inherited branches and checking if each most specific method is concrete or not.
 
@@
 We could also loosen the model to accept definitions such as \lstinline|D|, and perform ambiguity check on upcasts and other expressions.
-Then, we would need to handle more cases than C++.
-For instance, in the above program assume that $B.m$ and $C.m$ are hierarchical overrides on $A$.
-Then such a case is still a diamond.
+Then, we would need to handle more cases than C++ because of the complication caused by the hierarchical overriding feature.
+% For instance, in the above program assume that $B.m$ and $C.m$ are hierarchical overrides on $A$. Then such a case is still a diamond.
 

### 2018-04-24 ECOOP18/sections/Formalization.tex
fixing reviews for FHJ paper (unfinished)

@@
 \section{Formalization}~\label{sec:formalization}
-In this section, we present a formal model called \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), following the similar style of 
+In this section, we present a formal model called \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), following a similar style as  
 Featherweight Java~\cite{Igarashi01FJ}.
@@
 interface itself, then such a method is seen as originally defined; otherwise it is a hierarchical overriding method. 
-Note that in an interface $J$, $\method{I}{m}{I_x}{x}{J}{e} $ is a syntactic sugar for $
-I \; m(\overline{I_x} \; \overline{x}) \; {\{} \kwreturn \; e ; {\}} $, which is the standard way of method definition in Java-like languages. The definition
+Note that in an interface $J$, $
+I \; m(\overline{I_x} \; \overline{x}) \; {\{} \kwreturn \; e ; {\}} $ is syntactic sugar for $\method{I}{m}{I_x}{x}{J}{e}$, which is the standard way of method definition in Java-like languages.
+The definition
 of abstract methods is written as $\absmethod{I}{m}{I_x}{x}{J}$, which is
@@
 By the algorithm, $\mbody(m, T, T)$ will refer to $T.m$, but $\mbody(m, C, T)$ is undefined, since both $A.m$ and $B.m$ are most specific
-to $C$ along path $T$, which forms a diamond. The expression \lstinline|((A) new D()).m()| is one example of triggering ambiguity, but \MIM{}
+to $C$ along path $T$, which forms a diamond. The expression \lstinline|((T) new C()).m()| is one example of triggering ambiguity, but \MIM{}
 simply rejects the definition of $C$. To resolve the issue, the programmer needs to have an overriding method in $C$, to explicitly merge

### 2018-04-24 ECOOP18/sections/Overview.tex
fixing reviews for FHJ paper (unfinished)

@@
 	\item The \lstinline|new| keyword is used to instantiate an interface.
-	\item It cannot have state.
+	\item It cannot have state. But it is possible to support state in future work.
 \end{itemize}
@@
 A special rule for hierarchical overriding is: it can only refine \textit{original} methods, and cannot jump over original methods with the same signature.
-For instance, writing \lstinline|"void draw()| \lstinline|override Deck {...}"| is disallowed in \lstinline|DrawableSafeDeck|, because existing two branches are \lstinline|Drawable.draw| and \lstinline|SafeDeck.draw|, while \lstinline|Deck.draw| is already covered.
+For instance, writing \lstinline|"void draw()| \lstinline|override Deck {...}"| is disallowed in \lstinline|DrawableSafeDeck|, because the existing two branches are \lstinline|Drawable.draw| and \lstinline|SafeDeck.draw|, while \lstinline|Deck.draw| is already covered.
 It does not really make sense to refine an old branch.
@@
 dispatch, formally defined in Section~\ref{subsec:mbodydef}.
-In general, $\mbody(m, X, Y) = (Z, ...)$ reflects that the source code \lstinline|((Y) new X()).m()| calls \lstinline|Z.m| in the runtime.
+In general, $\mbody(m, X, Y) = (Z, ...)$ reflects that the source code \lstinline|((Y) new X()).m()| calls \lstinline|Z.m| at runtime.
 It is undefined when method dispatch is ambiguous.

### 2018-04-24 ECOOP18/sections/RelatedWork.tex
fixing reviews for FHJ paper (unfinished)

@@
 Moreover, the lack of direct syntax support makes MiddleMan code cumbersome to write.
-Finally, the approach is ad-hoc, meaning that the class \texttt{MiddleMan} shown in Figure~\ref{fig:middleman} is not general enough to be used in other cases: more middle-mans are needed if partial method overrides happen in other classes; and it is even worse when return types differ.
+Finally, the approach is ad-hoc, meaning that the class \texttt{MiddleMan} shown in Figure~\ref{fig:middleman} is not general enough to be used in other cases: more middle-men are needed if partial method overrides happen in other classes; and it is even worse when return types differ.
 
@@
 is that some expressive power is lost. In particular \emph{merging}
-methods arizing from diamond inheritance is not possible because the 
+methods arising from diamond inheritance is not possible because the 
 methods have different prefixes. 
@@
 \self{} does not include classes but instead allows individual objects to inherit from (or delegate to) other objects. 
-Although it is different from class-based languages, the multiple inheritance model is somehow similar. The \self{}
+Although it is different from class-based languages, the multiple inheritance model is somewhat similar. The \self{}
 language supports multiple (object) inheritance in a clever way. It not only develops the new inheritance

### 2018-04-25 ECOOP18/sections/Discussion.tex
fix reviews

@@
 \end{lstlisting}
-Here both $B.m$ and $C.m$ override $A.m$, and D inherits
+Here both \lstinline|B.m| and \lstinline|C.m| override \lstinline|A.m|, and \lstinline|D| inherits
 both conflicting methods without an explicit override. In this case, automatically merging 
@@
 the same origin (\lstinline|A.m|). 
-Our calculus rejects such conflicts by the \textsc{(T-Intf)} rule, where $D$ is considered to be ill-formed. 
+Our calculus rejects such conflicts by the \textsc{(T-Intf)} rule, where \lstinline|D| is considered to be ill-formed. 
 We believe that rejecting \lstinline|D| follows the principle of models like traits and Java 8 interfaces, 
@@
 Nonetheless,
- C++ accepts the definition of $D$, but forbids later upcasts from $D$ to $A$ because of ambiguity.
+ C++ accepts the definition of \lstinline|D|, but forbids later upcasts from \lstinline|D| to \lstinline|A| because of ambiguity.
 Our language is more conservative on definitions of interfaces compared to C++, but on the upside, upcasts are not rejected.

### 2018-04-25 ECOOP18/sections/Formalization.tex
fix reviews

@@
 We use the same
-conventions as FJ; we write $\overline{I}$ as shorthand for a possibly empty sequence $I_1, ..., I_n$, which may be indexed by $I_i$; and write $\overline{M}$ as shorthand for $M_1 ..
+conventions as FJ; we write $\overline{I}$ as shorthand for a possibly empty sequence $I_1, ..., I_n$, which may be indexed by $I_i$; and write $\overline{M}$ as shorthand for $M_1 ...
 M_n$ (with no commas).

### 2018-04-25 ECOOP18/sections/Overview.tex
fix reviews

@@
 languages. Nevertheless, at this point, languages like Java simply treat the two \lstinline|draw| methods
-as the same, and hence the compiler throws an error
-on \lstinline|DrawableDeck| about the conflict.
+as the same, hence the compiler fails to compile the program  and reports an error.
 
@@
 
-\subsubsection{Potential solutions/workarounds in existing languages} Unfortunately in all languages we have known
+\subsubsection{Potential solutions/workarounds in existing languages} Unfortunately in all languages we know of 
 (including C++), the existing approaches are unsatisfactory.
@@
 // main program
-((Drawable)new DrawableSafeDeck()).draw(); // calls the latest draw
+((Drawable)new DrawableSafeDeck()).draw(); //calls the draw in DrawableSafeDeck
 \end{lstlisting}
@@
 The individual overriding allows us to make use of the methods from \lstinline|SafeDeck| as well. In the formalization, the 
-hierarchical overriding feature is also an important feature, involved in the algorithm of hierarchical dispatch.
+hierarchical overriding feature is an important feature, involved in the algorithm of hierarchical dispatch.
 %\bruno{the last two sentences are a bit unclear. I think it is related to ``interaction''.}
@@
 For instance, writing \lstinline|"void draw()| \lstinline|override Deck {...}"| is disallowed in \lstinline|DrawableSafeDeck|, because the existing two branches are \lstinline|Drawable.draw| and \lstinline|SafeDeck.draw|, while \lstinline|Deck.draw| is already covered.
-It does not really make sense to refine an old branch.
+It does not really make sense to refine the old branch \lstinline|Deck|.
 

### 2018-04-25 ECOOP18/sections/Discussion.tex
implementation text

@@
-\section{Discussion}\label{sec:discussion}
-In this section, we will discuss the design space and reflect about some of the design decisions of our work. We relate 
-our language to traits, Java interfaces as well as other languages. Furthermore, we discuss
-ways to improve our work.
+\section{Implementation \& Discussion}\label{sec:discussion}
+In this section, we will talk about the prototype implementation and discuss the design space and reflect about some of the design decisions of our work.
+We relate our language to traits, Java interfaces as well as other languages.
+Furthermore, we discuss ways to improve our work.
+
+\subsection{Implementation}
+We have a simple implementation of \name{} interpreter in Scala. The implementation validates all the examples presented in the paper. The implementation is done in 
+Scala, strictly following the type-checking rules and small-step semantics
+presented in the paper. One nice feature of the implementation is that it can
+show the detailed step-by-step evaluation of the program, which is convenient for
+understanding and debugging programs \& semantics. The final model of \name{}
+is actually a bit different from our initial models. This is partly because in
+the process of implementing and proving theorems we found errors and modified
+the earlier models, creating a positive feedback circle.
 

### 2018-04-25 ECOOP18/sections/Formalization.tex
implementation text

@@
-\section{Formalization}~\label{sec:formalization}
+\section{Formalization}\label{sec:formalization}
 In this section, we present a formal model called \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), following a similar style as  

### 2018-04-25 ECOOP18/sections/Introduction.tex
fix reviews
implementation text

--- 2018-01-13 ECOOP18/sections/Introduction.tex
@@
 %%This issue was proposed by the trait paper, so-called
-When inheritance is used to compose these methods, a compilation 
+When inheritance is used to compose these classes, a compilation 
 error happens due to conflicts. However, unlike the diamond problem,
@@
           type soundness of the model.
-	\item \textbf{Prototype implementation\footnote{https://github.com/YanlinWang/MIM/tree/master/Calculus}:} a
+	\item \textbf{Prototype implementation\footnote{The implementation is available at \url{https://github.com/YanlinWang/MIM/tree/master/Calculus}}:} a
           simple implementation of \MIM{} interpreter in Scala. The implementation can type-check and run variants

### 2018-04-25 ECOOP18/sections/Overview.tex
implementation text

@@
-\section{A Running Example: Drawable Deck}~\label{sec:overview}
+\section{A Running Example: Drawable Deck}\label{sec:overview}
 This section illustrates the problem of unintentional method conflicts,

### 2018-04-25 ECOOP18/sections/RelatedWork.tex
fix reviews
implementation text

@@
-\section{Related Work}~\label{sec:relatedwork}
+\section{Related Work}\label{sec:relatedwork}
 We describe related work in four parts. We first discuss mainstream popular multiple 
@@
 Although this workaround can help us defining partial method overrides to a certain extent, the drawbacks are obvious.
-Firstly, the approach is complex and requires the pre-knowledge of the programmer to this approach.
+Firstly, the approach is complex and requires the programmer to fully understand this approach.
 Moreover, the lack of direct syntax support makes MiddleMan code cumbersome to write.

### 2018-05-02 ECOOP18/sections/Discussion.tex
finish fixing reviews. Ready for Bruno to check.

@@
 One non-orthogonal extension to \MIM{} could be to generalize the model to allow multiple hierarchical method overrding, meaning that, we allow overriding methods to update multiple branches instead of only one branch.
+It offers a more fine-grained mechanism for merging, and can be helpful to easily understand the structure of the hierarchy.
+Multiple overriding would be useful in the following situation, for example:
+
+\begin{lstlisting}
+interface A { void m() {...} }
+interface B { void m() {...} }
+interface C { void m() {...} }
+interface D extends A, B, C {
+	void m() override A,B {...}   // overrides branches A and B only
+	void m() override C {...}      // overrides branch C
+}
+\end{lstlisting}
+
+Here \lstinline|D| inherits from three interfaces \lstinline|A, B, C| with
+conflicting methods \lstinline|m|, but only merges two of those methods.
+While we can simulate D without multiple overriding in our calculus
+(by introducing an intermediate class), a better approach would be
+to support multiple overriding natively.
+
 We present the modification of syntax, typing and semantic rules below (abstract methods omitted):
@@
 \saveSpaceFig
+
+With this approach, branches \lstinline|A| and \lstinline|B| are merged in the sense that they share the same code, which can be separately updated in future interfaces.
+Another approach is to deeply merge the branches, with similar effect as introducing an intermediate interface \lstinline|AB| to explicitly merge the two branches.
+However, this approach is problematic because there is no clear mechanism of identifying and further updating the merged branches.
+This could be an interesting future work to explore.
 

### 2018-05-02 ECOOP18/sections/Formalization.tex
finish fixing reviews. Ready for Bruno to check.

@@
 \subsubsection{Interfaces}
-In order to achieve multiple inheritance, an interface can have a set of 
+In order to achieve multiple inheritance, an interface (which is acyclic, by deafault) can have a set of 
 parent interfaces, where such a set can be empty.

### 2018-05-08 ECOOP18/sections/Discussion.tex
temp

@@
-\section{Implementation \& Discussion}\label{sec:discussion}
+\section{Discussion}\label{sec:discussion}
 In this section, we will talk about the prototype implementation and discuss the design space and reflect about some of the design decisions of our work.

### 2018-05-08 ECOOP18/sections/Formalization.tex
temp

--- 2018-04-25 ECOOP18/sections/Formalization.tex
@@
 \subsubsection{Interfaces}
-In order to achieve multiple inheritance, an interface can have a set of 
+\yanlin{Bruno: acyclic, clarified herer.}
+In order to achieve multiple inheritance, an interface (which is acyclic, by deafault) can have a set of 
 parent interfaces, where such a set can be empty.

### 2018-05-08 ECOOP18/sections/Introduction.tex
temp

@@
 proofs for type soundness.
+
+\yanlin{Bruno.}
+In terms of implementation, we have a prototype implementation of \name{} interpreter in Scala. The implementation validates all the examples presented in the paper. The implementation is done in 
+Scala, strictly following the type-checking rules and small-step semantics presented in the paper.
+One nice feature of the implementation is that it can show the detailed step-by-step evaluation of the program, which is convenient for understanding and debugging programs \& semantics.
+The final model of \name{}
+is actually a bit different from our initial models. This is partly because in
+the process of implementing and proving theorems we found errors and modified the earlier models, creating a positive feedback circle.
+
 In summary, our contributions are:

### 2018-05-08 ECOOP18/sections/Overview.tex
temp

@@
   \item \textit{I. Delegation.} As an alternative to multiple inheritance,
-  delegation can be used by introducing two fields (or field methods) with the \yanlin{"field methods"?}
+  delegation can be used by introducing two fields (or field methods) with the 
   \lstinline|Drawable| type and \lstinline|Deck| type,
@@
 
-\subsubsection{Potential solutions/workarounds in existing languages} Unfortunately in all languages we know of 
+\subsubsection{Potential solutions/workarounds in existing languages} 
+\yanlin{Bruno: one reviewer says S2.3.1 is "less clear", could you check again?}Unfortunately in all languages we know of 
 (including C++), the existing approaches are unsatisfactory.

### 2018-05-08 ECOOP18/sections/Discussion.tex
labeled. Ready for Bruno review

@@
 \section{Discussion}\label{sec:discussion}
-In this section, we will talk about the prototype implementation and discuss the design space and reflect about some of the design decisions of our work.
+In this section, we will discuss the design space and reflect about some of the design decisions of our work.
 We relate our language to traits, Java interfaces as well as other languages.
@@
 
-\subsection{Implementation}
-We have a simple implementation of \name{} interpreter in Scala. The implementation validates all the examples presented in the paper. The implementation is done in 
-Scala, strictly following the type-checking rules and small-step semantics
-presented in the paper. One nice feature of the implementation is that it can
-show the detailed step-by-step evaluation of the program, which is convenient for
-understanding and debugging programs \& semantics. The final model of \name{}
-is actually a bit different from our initial models. This is partly because in
-the process of implementing and proving theorems we found errors and modified
-the earlier models, creating a positive feedback circle.
-
 \subsection{Abstract Methods}
-
 Abstract methods are one of the key features in most general OO languages. For example, Java interfaces were designed
@@
 
+\yanlin{Bruno: discussed multiple overriding and the two designs}
 One non-orthogonal extension to \MIM{} could be to generalize the model to allow multiple hierarchical method overrding, meaning that, we allow overriding methods to update multiple branches instead of only one branch.

### 2018-05-08 poster/poster.tex
poster init

\documentclass[portrait,final,a0paper,fontscale=0.277]{baposter}

\usepackage{listings}

\usepackage{calc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{bm}
\usepackage{url}

\usepackage{graphicx}
\usepackage{multicol}

%\usepackage{times}
%\usepackage{helvet}
%\usepackage{bookman}
\usepackage{palatino}

\usepackage{xspace}

\usepackage{listings}

\lstset{ %
language=Java,                % choose the language of the code
columns=flexible,
lineskip=-1pt,
basicstyle=\ttfamily\small,       % the size of the fonts that are used for the code
numbers=none,                   % where to put the line-numbers
numberstyle=\ttfamily\tiny,      % the size of the fonts that are used for the line-numbers
stepnumber=1,                   % the step between two line-numbers. If it's 1 each line will be numbered
numbersep=5pt,                  % how far the line-numbers are from the code
backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
morekeywords={var},
%  frame=single,                   % adds a frame around the code
tabsize=2,                  % sets default tabsize to 2 spaces
captionpos=none,                   % sets the caption-position to bottom
breaklines=true,                % sets automatic line breaking
breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
title=\lstname,                 % show the filename of files included with \lstinputlisting; also try caption instead of title
escapeinside={(*}{*)},          % if you want to add a comment within your code
keywordstyle=\ttfamily\bfseries,
aboveskip=0pt,
belowskip=0pt,
frame=single %border
% commentstyle=\color{Gray},
% stringstyle=\color{Green}
}

\newcommand{\captionfont}{\footnotesize}

\graphicspath{{images/}{../images/}}
\usetikzlibrary{calc}

\newcommand{\SET}[1]  {\ensuremath{\mathcal{#1}}}
\newcommand{\MAT}[1]  {\ensuremath{\boldsymbol{#1}}}
\newcommand{\VEC}[1]  {\ensuremath{\boldsymbol{#1}}}
\newcommand{\Video}{\SET{V}}
\newcommand{\video}{\VEC{f}}
\newcommand{\track}{x}
\newcommand{\Track}{\SET T}
\newcommand{\LMs}{\SET L}
\newcommand{\lm}{l}
\newcommand{\PosE}{\SET P}
\newcommand{\posE}{\VEC p}
\newcommand{\negE}{\VEC n}
\newcommand{\NegE}{\SET N}
\newcommand{\Occluded}{\SET O}
\newcommand{\occluded}{o}
\newcommand\mixin{\textbf{\texttt{@Obj }}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Some math symbols used in the text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Multicol Settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setlength{\columnsep}{1.5em}
\setlength{\columnseprule}{0mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Save space in lists. Use this after the opening of the list
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\compresslist}{%
\setlength{\itemsep}{0pt}%
\setlength{\parskip}{0pt}%
\setlength{\parsep}{0pt}%
}

\input{symbols}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Begin of Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Here starts the poster
%%%---------------------------------------------------------------------------
%%% Format it to your taste with the options
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Define some colors

%\definecolor{lightblue}{cmyk}{0.83,0.24,0,0.12}
\definecolor{lightblue}{rgb}{0.145,0.6666,1}

% Draw a video
\newlength{\FSZ}
\newcommand{\drawvideo}[3]{% [0 0.25 0.5 0.75 1 1.25 1.5]
   \noindent\pgfmathsetlength{\FSZ}{\linewidth/#2}
   \begin{tikzpicture}[outer sep=0pt,inner sep=0pt,x=\FSZ,y=\FSZ]
   \draw[color=lightblue!50!black] (0,0) node[outer sep=0pt,inner sep=0pt,text width=\linewidth,minimum height=0] (video) {\noindent#3};
   \path [fill=lightblue!50!black,line width=0pt]
     (video.north west) rectangle ([yshift=\FSZ] video.north east)
    \foreach \x in {1,2,...,#2} {
      {[rounded corners=0.6] ($(video.north west)+(-0.7,0.8)+(\x,0)$) rectangle +(0.4,-0.6)}
    }
;
   \path [fill=lightblue!50!black,line width=0pt]
     ([yshift=-1\FSZ] video.south west) rectangle (video.south east)
    \foreach \x in {1,2,...,#2} {
      {[rounded corners=0.6] ($(video.south west)+(-0.7,-0.2)+(\x,0)$) rectangle +(0.4,-0.6)}
    }
;
   \foreach \x in {1,...,#1} {
     \draw[color=lightblue!50!black] ([xshift=\x\linewidth/#1] video.north west) -- ([xshift=\x\linewidth/#1] video.south west);
   }
   \foreach \x in {0,#1} {
     \draw[color=lightblue!50!black] ([xshift=\x\linewidth/#1,yshift=1\FSZ] video.north west) -- ([xshift=\x\linewidth/#1,yshift=-1\FSZ] video.south west);
   }
   \end{tikzpicture}
}

\hyphenation{resolution occlusions}
%%
\begin{poster}%
  % Poster Options
  {
  % Show grid to help with alignment
  grid=false,
  % Column spacing
  colspacing=0.5em,
  % Color style
  bgColorOne=white,
  bgColorTwo=white,
  borderColor=lightblue,
  headerColorOne=black,
  headerColorTwo=lightblue,
  headerFontColor=white,
  boxColorOne=white,
  boxColorTwo=lightblue,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=true,
  headerborder=closed,
  headerheight=0.1\textheight,
%  textfont=\sc, An example of changing the text font
  headershape=roundedright,
  headershade=shadelr,
  headerfont=\Large\bf\textsc, %Sans Serif
  textfont={\setlength{\parindent}{1.5em}},
  boxshade=plain,
%  background=shade-tb,
  background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  {\includegraphics[height=7em]{pdfs/hku.png}}
  % Title
  {\bf\textsc{FHJ: A Formal Model for Hierarchical Dispatching and Overriding}\vspace{0.1em}}
  % Authors
  {\text{Yanlin Wang {,} Haoyuan Zhang {,} Bruno C. d. S. Oliveira} {,} Marco Servetto }
  % \text{The University of Hong Kong, China}}
  % \text{The University of Hong Kong, China: \{ylwang,hyzhang,bruno\}@cs.hku.hk}\\
  % \text{Victoria University of Wellington, New Zealand: marco.servetto@ecs.vuw.ac.nz}}
  % University logo
  {% The makebox allows the title to flow into the logo, this is a hack because of the L shaped logo.
    \includegraphics[width=7em,height=7em]{pdfs/vuw.png}
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Now define the boxes that make up the poster
%%%---------------------------------------------------------------------------
%%% Each box has a name and can be placed absolutely or relatively.
%%% The only inconvenience is that you can only specify a relative position
%%% towards an already declared box. So if you have a box attached to the
%%% bottom, one to the top and a third one which should be in between, you
%%% have to specify the top and bottom boxes before you specify the middle
%%% box.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    % A coloured circle useful as a bullet with an adjustably strong filling
    \newcommand{\colouredcircle}{%
      \tikz{\useasboundingbox (-0.2em,-0.32em) rectangle(0.2em,0.32em); \draw[draw=black,fill=lightblue,line width=0.03em] (0,0) circle(0.18em);}}

  \headerbox{Motivation}{name=motivation,column=0,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \noindent \begin{enumerate}\compresslist
	\item In OOP, multiple inheritance is hard due to the ambiguity arising from inheriting multiple parents (with conflicting methods).
	\item Numerous existing work provides solutions for conflicts which arise from \emph{diamond inheritance}.
	\item However, these solutions are inadequate to deal with \emph{unintentional method conflicts}: conflicts which arise from two unrelated methods that happen to share the same signature.
	% \item Other models (traits, mixins, etc) have certain limitations.
	% \item Our approach is related with traits. But we use operations on state to simulate fields 
	% which traits do not support.
\end{enumerate}
 }

  \headerbox{Contributions}{name=contribution,column=0,below=motivation}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \noindent \begin{enumerate}\compresslist
  \item Abstract state operations: 
      \noindent \begin{itemize} \compresslist
          \item a new way to think about state, via operations instead of fields directly
          \item easy to combine with \emph{multiple (trait) inheritance}
          \item supports constructors, co-variant type-refinement of state
      \end{itemize}    
  % \item Classless Java: a Java extension that allows an interface-based programming style
    % \item IB and Object Interfaces: enable powerful programming idioms using multiple-inheritance, type-refinement and abstract state operations.
    \item Classless Java: a practical realization of IB in Java.
    % \item Type-safe covariant mutable state
    % \item Applications and case studies
   \end{enumerate}
   \vspace{0.3em}
  }

  \headerbox{Implementation}{name=implementation,column=0,below=contribution}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Java supports compilation agents, where Java libraries can interact with the Java compilation process,
acting as a man in the middle between the
generation of AST and bytecode.

This process is facilitated by frameworks like Lombok:
a Java library that aims at reducing Java boilerplate code via
annotations. \mixin was created using Lombok.

\noindent{\centering\includegraphics[width=\linewidth]{pdfs/lombok3.png}\\}
\vspace{0.1em}
}

  \headerbox{UML Diagram}{name=uml,column=0,below=implementation}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent{\centering\includegraphics[width=0.8\linewidth]{pdfs/PegasusDetail.pdf}\\}
\vspace{0.1em}
}

  \headerbox{Results (Partial)}{name=result,column=0,below=uml,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the maze game case study, both SLOC and \# of interfaces are greatly reduced:
\noindent{\centering\includegraphics[width=0.81\linewidth]{pdfs/result.png}\\}
\vspace{0.1em}
}

\vspace{-0.5em}
\headerbox{Object Interfaces and Instantiation}{name=Model,column=1,span=2,row=0}{
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lstinputlisting[linerange=6-13]{../UseMixinLombok/src/pegasus/simple/java8/Main.java}% APPLY:linerange=PEGASUS_JAVA
% \lstinputlisting[linerange=17-19]{../UseMixinLombok/src/pegasus/simple/java8/Main.java}% APPLY:linerange=PEGASUS_INST
\lstinputlisting[linerange=8-12]{../UseMixinLombok/src/pegasus/simple/lombok/Main.java}% APPLY:linerange=PEGASUS_LOMBOK
\lstinputlisting[linerange=1-5]{./import_src/src1.txt}
}

\vspace{-0.5em}
\headerbox{Object Interfaces with State (immutable data)}{name=results,column=1,span=2,row=0,below=Model}{
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \begin{multicols}{2}
%  \noindent{\centering\includegraphics[width=1\linewidth]{images/mymodel.pdf}\\}
% The process of generating an academic document is as follows: for each citation in that document, firstly sample a topic $\topic_k$ according to the distribution from paper\_topic distribution $\delta(\topic ; \paper)$ or author\_topic distribution $\zeta(\topic ; \authorvar)$ or venue\_topic distribution $\psi(\topic ; \venue)$  based on the document type. Then, draw a citation $\citationvar$ from the sampled topic distribution $\phi(:;\topic_k)$ in topic\_citation distribution $\phi(\citationvar;\topic)$.
% \end{multicols}

\lstinputlisting[linerange=7-11]{./import_src/src1.txt}
\lstinputlisting[linerange=13-15]{./import_src/src1.txt}
}

\vspace{-0.5em}

\headerbox{with- Methods}{name=with,column=1,span=2,row=0,below=results}{
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lstinputlisting[linerange=1-5]{./import_src/src2.txt}
}

\vspace{-0.5em}
\headerbox{Mutable Data \& Field Type Refinement}{name=refine,column=1,span=2,row=0,below=with}{
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lstinputlisting[linerange=7-10]{./import_src/src2.txt}
}
\vspace{-0.5em}

\headerbox{More in the paper}{name=more,column=1,span=2,row=0,below=refine}{
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent{\centering\includegraphics[width=0.95\linewidth]{table.png}\\}

\begin{multicols}{2}
\noindent{\centering\includegraphics[width=1.15\linewidth]{pdfs/screenshot4.png}\\}
\begin{itemize}\compresslist
\item Techniques for field type refinement.
\item Formalization and proofs.
\item Case studies and applications.
    \small{\newline
    % \begin{itemize}\compresslist
    % \item The Expression Problem
    % \item Embedded DSLs with Fluent Interfaces
    % \item A Maze Game
    % \item Refactoring an Interpreter
    % \end{itemize}
    [The Expression Problem]\newline
    [Embedded DSLs with Fluent Interfaces]\newline
    [A Maze Game]\newline
    [Refactoring an Interpreter] 
    }
\end{itemize}
\end{multicols}
}

  \headerbox{Acknowledgments}{name=acknowledge,column=1, span=2, below=more}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This work is sponsored by the Hong Kong Research Grant Council Early Career 
Scheme project number 27200514. The first and second authors are supported by 
the SIG PAC student travel grant.
  }

  \headerbox{Contacts}{name=acknowledge,column=1,span=2,below=acknowledge,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{The University of Hong Kong} \\
Yanlin Wang, Haoyuan Zhang, Bruno C. d. S. Oliveira: \emph{\{ylwang,hyzhang,bruno\}@cs.hku.hk} \\
\newline
\textbf{Victoria University of Wellington} \\
Marco Servetto: \emph{marco.servetto@ecs.vuw.ac.nz}
}

\end{poster}
\end{document}

### 2018-05-08 UseMixinLombok/src/casestudy/ep/TestExpression.java

@@ -1,0 +1,91 @@
+package casestudy.ep;
+
+import java.util.ArrayList;
+import java.util.List;
+import lombok.Obj;
+
+public class TestExpression {
+    public static String runTest() {
+        String res = "";
+        Lit e1 = Lit.of(3);
+        res += e1.eval() + "\n"; // 3
+        Lit e2 = Lit.of(4);
+        Add e3 = Add.of(e1, e2);
+        res += e3.eval() + "\n"; // 7
+        Sub e4 = Sub.of(e1, e2);
+        res += e4.eval() + "\n"; // -1
+        LitP e5 = LitP.of(3);
+        LitP e6 = LitP.of(4);
+        AddP e7 = AddP.of(e5, e6);
+        res += e5.print() + " = " + e5.eval() + "\n"; // 3 = 3
+        res += e7.print() + " = " + e7.eval() + "\n"; // (3 + 4) = 7
+        return res;
+    }
+    public static void main(String[] args) {
+        System.out.println(runTest());
+        //independent extensibility
+        ExpPC e8 = AddPC.of(LitPC.of(3), LitPC.of(4));
+        System.out.println(e8.print() + " = " + e8.eval() + " Literals: " + e8.collectLit().toString());
+    }
+}
+
+//BEGIN_EXPRESSION_INIT
+interface Exp { int eval(); }
+@Obj interface Lit extends Exp {
+    int x();
+    default int eval() {return x();}
+}
+@Obj interface Add extends Exp {
+    Exp e1(); Exp e2();
+    default int eval() {
+        return e1().eval() + e2().eval();
+    }
+}
+//END_EXPRESSION_INIT
+
+//BEGIN_EXPRESSION_SUB
+@Obj interface Sub extends Exp {
+	Exp e1(); Exp e2();
+	default int eval() {
+		return e1().eval() - e2().eval();} }
+//END_EXPRESSION_SUB
+
+//BEGIN_EXPRESSION_PRINT
+interface ExpP extends Exp {String print();}
+@Obj interface LitP extends Lit, ExpP {
+    default String print() {return "" + x();}
+}
+@Obj interface AddP extends Add, ExpP {
+    ExpP e1(); //return type refined! 
+    ExpP e2(); //return type refined!
+    default String print() {
+        return "(" + e1().print() + " + " 
+                + e2().print() + ")";}
+}
+//END_EXPRESSION_PRINT
+
[…]

### 2018-05-08 UseMixinLombok/src/pegasus/TestAnimal.java

@@ -1,0 +1,114 @@
+package pegasus;
+
+import lombok.Obj;
+import static java.lang.System.out;
+
+public class TestAnimal {
+    
+    public static String runTest() {
+//BEGIN_USINGHORSE
+Point2D p = Point2D.of(0, 0);
+Horse horse = Horse.of(p);
+horse.location(p.withX(42));
+//END_USINGHORSE
+        String res = "";
+        res += "horse initialized at " + print(horse.location()) + "\n";
+        horse.run();
+        res += "horse.run(); now at " + print(horse.location()) + "\n\n";
+        Bird bird = Bird.of(Point3D.of(10, 10, 10));
+        res += "bird initialized at " + print(bird.location()) + "\n";
+        bird.fly();
+        res += "bird.fly(); now at " + print(bird.location()) + "\n\n";
+        Pegasus pegasus = Pegasus.of(Point3D.of(100, 100, 100));
+        res += "pegasus initialized at " + print(pegasus.location()) + "\n";
+        pegasus.run();
+        res += "pegasus.run(); now at " + print(pegasus.location()) + "\n";
+        pegasus.fly();
+        res += "pegasus.fly(); now at " + print(pegasus.location()) + "\n";
+        return res;
+    }
+    
+    static String print(Point2D p) {
+        return p.x() + ", " + p.y();
+    }
+    
+    static String print(Point3D p) {
+        return p.x() + ", " + p.y() + ", " + p.z();
+    }
+    
+}
+
+//BEGIN_POINT2D
+@Obj 
+interface Point2D {
+    int x();
+    int y();
+    Point2D withX(int x);
+    Point2D withY(int y);
+}
+//END_POINT2D
+
+//BEGIN_POINT3D
+@Obj interface Point3D extends Point2D {
+    int z(); 
+    Point3D withZ(int z);
+    Point3D with(Point2D val); }
+//END_POINT3D
+//BEGIN_ANIMAL
+interface Animal {
+	Point2D location();
+	void location(Point2D val); }
+//END_ANIMAL
+
+//BEGIN_HORSE
+@Obj interface Horse extends Animal {
+	default void run() {
+		location(location().withX(location().x()+20));}}
+//END_HORSE
+
+//BEGIN_BIRD
+@Obj interface Bird extends Animal {
+	Point3D location(); void location(Point3D val);
+	default void location(Point2D val) {
+		location(location().with(val));}
[…]

### 2018-05-08 UseMixinLombok/src/pegasus/simple/java8/Main.java

@@ -1,0 +1,28 @@
+package pegasus.simple.java8;
+
+import static java.lang.System.out;
+
+//BEGIN_PEGASUS_JAVA
+interface Animal {} // no points yet!
+interface Horse extends Animal {
+    default void run(){out.println("run!");}
+}
+interface Bird extends Animal {
+    default void fly(){out.println("fly!");}
+}
+interface Pegasus extends Horse, Bird {}
+//END_PEGASUS_JAVA
+
+//BEGIN_PEGASUS_INST
+class HorseImpl implements Horse {}
+class BirdImpl implements Bird {} 
+class PegasusImpl implements Pegasus {}
+//END_PEGASUS_INST
+
+public interface Main {
+    public static void main(String[] args) {
+        Horse h = new HorseImpl();
+        Bird b = new BirdImpl();
+        Pegasus p = new PegasusImpl();	
+    }
+}

### 2018-05-23 poster/poster.tex
poster

@@
 \usepackage{listings}
-
+\usepackage{comment}
 \usepackage{calc}
@@
 \newcommand\mixin{\textbf{\texttt{@Obj }}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%% Some math symbols used in the text
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Multicol Settings
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \setlength{\columnsep}{1.5em}
 \setlength{\columnseprule}{0mm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Save space in lists. Use this after the opening of the list
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newcommand{\compresslist}{%
@@
 }
-
 \input{symbols}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Begin of Document
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \begin{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Here starts the poster
-%%%---------------------------------------------------------------------------
-%%% Format it to your taste with the options
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Define some colors
-
 %\definecolor{lightblue}{cmyk}{0.83,0.24,0,0.12}
 \definecolor{lightblue}{rgb}{0.145,0.6666,1}
-
 % Draw a video
@@
 }
+\hyphenation{resolution occlusions}
 
-\hyphenation{resolution occlusions}
-%%
 \begin{poster}%
@@
   \headerbox{Motivation}{name=motivation,column=0,row=0}{
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
   \noindent \begin{enumerate}\compresslist
@@
   \headerbox{Contributions}{name=contribution,column=0,below=motivation}{
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
   \noindent \begin{enumerate}\compresslist
-  \item Abstract state operations: 
-      \noindent \begin{itemize} \compresslist
-          \item a new way to think about state, via operations instead of fields directly
-          \item easy to combine with \emph{multiple (trait) inheritance}
-          \item supports constructors, co-variant type-refinement of state
-      \end{itemize}    
-  % \item Classless Java: a Java extension that allows an interface-based programming style
-    % \item IB and Object Interfaces: enable powerful programming idioms using multiple-inheritance, type-refinement and abstract state operations.
-    \item Classless Java: a practical realization of IB in Java.
-    % \item Type-safe covariant mutable state
-    % \item Applications and case studies
+		\item A formalization of the hierarchical dispatching algorithm
+		\item Hierarchical overriding: override individual branches of the class hierarchy.
+		\item FHJ: a formalized model based on Featherweight Java
+		\item Prototype implementation: FHJ interpreter in Scala.
    \end{enumerate}
@@
   }
-
+\begin{comment}
   \headerbox{Implementation}{name=implementation,column=0,below=contribution}{

### 2018-05-23 ECOOP18/paper.tex
polish text
ECOOP final version. template

@@
-\documentclass[a4paper,english]{lipics-v2016}
+\documentclass[a4paper,english]{lipics-v2018}
+% \nolinenumbers
 %This is a template for producing LIPIcs articles. 
@@
 \usepackage{mathtools} % For \Coloneqq
-
-\usepackage{microtype}%if unwanted, comment out or use option "draft"
 \usepackage{listings}
@@
 \usepackage{lmodern}
-
 % \let\proof\relax
@@
 % \newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
-% \newcommand\yanlin[1]{\authornote{yanlin}{purple}{#1}}
+ \newcommand\yanlin[1]{\authornote{yanlin}{red}{#1}}
 % \newcommand\marco[1]{\authornote{marco}{blue}{#1}}
@@
 \newcommand\bruno[1]{}
-\newcommand\yanlin[1]{}
+%\newcommand\yanlin[1]{}
 \newcommand\marco[1]{}
@@
 }
-
 %\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
 
-\bibliographystyle{plainurl}% the recommended bibstyle
+\bibliographystyle{plainurl}% the recommnded bibstyle
 
-% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \title{FHJ: A Formal Model for Hierarchical Dispatching and Overriding}
-% \titlerunning{A Sample LIPIcs Article} %optional, in case that the title is too long; the running title should fit into the top page column
 
-%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
-\author[1]{John Q. Open}
-\author[2]{Joan R. Access}
-\affil[1]{Dummy University Computing Laboratory, Address/City, Country\\
-	\texttt{open@dummyuniversity.org}}
-\affil[2]{Department of Informatics, Dummy College, Address/City, Country\\
-	\texttt{access@dummycollege.org}}
-\authorrunning{J.\,Q. Open and J.\,R. Access} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus ‘et. al.’
+% \titlerunning{Dummy short title}%optional, please use if title is longer than one line
 
-\Copyright{John Q. Open and Joan R. Access}%mandatory, please use full first names. LIPIcs license is “CC-BY”;  http://creativecommons.org/licenses/by/3.0/
+\author{Yanlin Wang}
+{The University of Hong Kong, China}
+{ylwang@cs.hku.hk}
+{}{}%mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
+\author{Haoyuan Zhang}
+{The University of Hong Kong, China}
+{hyzhang@cs.hku.hk}
+{}{}
+\author{Bruno C. d. S. Oliveira}
+{The University of Hong Kong, China}
+{bruno@cs.hku.hk}
+{}{}
+\author{Marco Servetto}
+{Victoria University of Wellington, New Zealand}
+{marco.servetto@ecs.vuw.ac.nz}
+{}{}
 
-% \subjclass{Dummy classification -- please refer to \url{http://www.acm.org/about/class/ccs98-html}}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html .
-E.g., cite as “F.1.1 Models of Computation”.
-% \keywords{Dummy keyword -- please provide 1--5 keywords}% mandatory: Please provide 1-5 keywords
-% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\authorrunning{Y. Wang, H. Zhang, B. C. d. S. Oliveira and M. Servetto}%mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
+
+\Copyright{John Q. Public and Joan R. Public}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+
+\subjclass{Dummy classification}% mandatory: Please choose ACM 2012 classifications from https://www.acm.org/publications/class-2012 or https://dl.acm.org/ccs/ccs_flat.cfm .
+E.g., cite as "General and reference $\rightarrow$ General literature" or \ccsdesc[100]{General and reference~General literature}.
+
+\keywords{Dummy keyword}%mandatory
+
+\category{}%optional, e.g. invited paper
+
+\relatedversion{}%optional, e.g. full version hosted on arXiv, HAL, or other respository/website
+
+\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
+
+\funding{}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.
+
+\acknowledgements{I want to thank \dots}%optional
 
 %Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Acces}
-\EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
+\EventEditors{Todd Millstein}
+\EventNoEds{1}
+\EventLongTitle{32nd European Conference on Object-Oriented Programming (ECOOP 2018)}
+\EventShortTitle{ECOOP 2018}
+\EventAcronym{ECOOP}
+\EventYear{2018}
+\EventDate{July 16--21, 2018}
+\EventLocation{Amsterdam, Netherlands}
 \EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
-% Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\SeriesVolume{109}
+\ArticleNo{20} % “New number” (=<article-no>) goes here!
+
+%\nolinenumbers %uncomment to disable line numbering
+%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\begin{comment}
-One of the most promising 
-approaches to multiple inheritance is the \emph{trait} model. Traits offer a
-restricted model of multiple inheritance that is easy to reason and 
-have many elegant properties. Traits have good support for method 
-conflicts which arise from \emph{diamond inheritance}:
-conflicts that arise from method implementations sharing a common 
-ancestor. However, the mechanisms of traits are inadequate to deal 
-with \emph{unintentional method conflicts}: conflicts which 
-arise from two unrelated methods that happen to share the same name
-and signature. 
-\end{comment}
-
 This paper presents a new model called \emph{\textbf{F}eatherweight
@@
 and formalize \name{} as a minimal Featherweight-Java style calculus.
-
-\begin{comment}
-Furthermore we discuss similarities and differences to
-
-What ensures unambiguity is the use of information about
-the class hierarchy.
-
-\name{} is partly inspired by the method resolution semantics
-of C++, but it also incoorporates ideas from the trait model and Java
-8's default methods. We discuss the similarities
-and differences with and also advantages and disadvantages. 
-\end{comment}
-
 \end{abstract}
@@
 \input{sections/RelatedWork.tex}
-
 \input{sections/Conclusion.tex}
 
-%%
-%% Bibliography
-%%
-
-%% Please use bibtex,
-
 \bibliography{paper}
+\newpage
 \appendix

### 2018-05-23 ECOOP18/paper0.tex
ECOOP final version. template

--- 2017-10-20 NewVersion/paper.tex
@@
 
+%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
+
+\bibliographystyle{plainurl}% the recommended bibstyle
+
+% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\title{FHJ: A Formal Model for Hierarchical Dispatching and Overriding}
+% \titlerunning{A Sample LIPIcs Article} %optional, in case that the title is too long; the running title should fit into the top page column
+
+%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
+\author[1]{Yanlin Wang}
+\author[1]{Haoyuan Zhang}
+\author[1]{Bruno C. d. S. Oliveira}
+\affil[1]{The University of Hong Kong, China \\
+	\texttt{\{yanlin,hyzhang,bruno\}@cs.hku.hk}}
+\author[2]{Marco Servetto}
+\affil[2]{Victoria University of Wellington, New Zealand \\
+    \texttt{marco.servetto@ecs.vuw.ac.nz}}
+
+%\author{Yanlin Wang}{The University of Hong Kong}{yanlin@cs.hku.hk}
+%\author{Haoyuan Zhang}{The University of Hong Kong}{hyzhang@cs.hku.hk}
+\authorrunning{} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus ‘et. al.’
+
+\Copyright{}%mandatory, please use full first names. LIPIcs license is “CC-BY”;  http://creativecommons.org/licenses/by/3.0/
+
+% \subjclass{Dummy classification -- please refer to \url{http://www.acm.org/about/class/ccs98-html}}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html .
+E.g., cite as “F.1.1 Models of Computation”.
+% \keywords{Dummy keyword -- please provide 1--5 keywords}% mandatory: Please provide 1-5 keywords
+% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\EventEditors{John Q. Open and Joan R. Acces}
+\EventNoEds{2}
+\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
+\EventShortTitle{CVIT 2016}
+\EventAcronym{CVIT}
+\EventYear{2016}
+\EventDate{December 24--27, 2016}
+\EventLocation{Little Whinging, United Kingdom}
+\EventLogo{}
+\SeriesVolume{42}
+\ArticleNo{23}
+% Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{document}
 
-% \title{Untangling Unintended Conflicts with Hierarchical Dispatch}
-% \title{FHJ: A Formal Model for Resolving Unintended Conflicts in Multiple Inheritance}
-\title{FHJ: A Formal Model for Hierarchical Dispatching and Overriding}
-%\subtitle{\InterfaceBased Programming for the Masses}
-
-% \authorinfo{NoAuthor}
-%            {The University of Hong Kong, China}
-% %           {\{ylwang,hyzhang,bruno\}@cs.hku.hk}
-% %\authorinfo{Marco Servetto}
-% %          {Victoria University of Wellington, New Zealand}
-% %          {marco.servetto@ecs.vuw.ac.nz}
-\author{Yanlin Wang\inst{1} \and Haoyuan Zhang\inst{1} \and Bruno C.d.S. Oliveira\inst{1} \and Marco Servetto\inst{2}}
-\institute{The University of Hong Kong \and Victoria University of Wellington \\ \email{\{ylwang,hyzhang,bruno\}@cs.hku.hk, marco.servetto@ecs.vuw.ac.nz}}
-
 \maketitle
-
-\vspace{-4ex}
 
@@
 \input{sections/RelatedWork.tex}
+
 \input{sections/Conclusion.tex}
 
-\begin{comment}
-\section*{Acknowledgments}\label{sec:Acknowledgments}
+%%
+%% Bibliography
+%%
 
-Authors would like to thank YYYYY.
-\end{comment}
+%% Please use bibtex,
 
-% \newpage
-% \clearpage
-% \bibliographystyle{abbrvnat}
-
-\newpage
-\bibliographystyle{splncs03}
 \bibliography{paper}
-
 \newpage
@@
 \input{sections/Appendix.tex}
-% \input{sections/Appendix_Formalization.tex}
-% \input{sections/Translation.tex}
-% \input{sections/Appendix_Translation.tex}
-
 \end{document}

### 2018-05-28 ECOOP18/sections/Formalization.tex
revision

--- 2018-04-25 ECOOP18/sections/Formalization.tex
@@
 \subsubsection{Interfaces}
+\yanlin{Bruno: acyclic, clarified herer.}
 In order to achieve multiple inheritance, an interface can have a set of 
-parent interfaces, where such a set can be empty.
+parent interfaces, where such a set can be empty. Moreover, as usual
+in class-based languages, the class hierarchy is acyclic.
 The interface declaration $\interface{I}{I}{M}$ introduces an interface named $I$ with parent interfaces $\overline{I}$ and a suite of methods $\overline{M}$.

### 2018-05-28 ECOOP18/sections/Introduction.tex
revision

--- 2018-04-25 ECOOP18/sections/Introduction.tex
@@
 Featherweight Java~\cite{Igarashi01FJ}, together with theorems and
-proofs for type soundness. 
+proofs for type soundness. We also have a prototype implementation of
+a \name{} interpreter written in Scala. The implementation validates
+all the examples presented in the paper. 
+One nice feature of the implementation is that it can show the
+detailed step-by-step evaluation of the program, which is convenient
+for understanding and debugging programs \& semantics. 
+%The final model of \name{}
+%is actually a bit different from our initial models. This is partly because in
+%the process of implementing and proving theorems we found errors and modified the earlier models, creating a positive feedback circle.
+
 In summary, our contributions are:

### 2018-05-28 ECOOP18/sections/Overview.tex
revision

@@
 	\item The \lstinline|new| keyword is used to instantiate an interface.
-	\item It cannot have state. But it is possible to support state in future work.
+	\item It cannot have state. 
 \end{itemize}
@@
 override the individual conflicting methods, rather than overriding all
-conflicting methods into a single merged one. We illustrate the
+conflicting methods into a single merged one.
+
+We illustrate the
 problem and the need for a more refined overriding mechanism with 
@@
 \subsubsection{Potential solutions/workarounds in existing languages} 
-\yanlin{Bruno: one reviewer says S2.3.1 is "less clear", could you check again?}Unfortunately in all languages we know of 
+\yanlin{Bruno: one reviewer says S2.3.1 is "less clear", could you
+  check again?}\bruno{seems ok to me.}
+Unfortunately in all languages we know of 
 (including C++), the existing approaches are unsatisfactory.
@@
 The individual overriding allows us to make use of the methods from \lstinline|SafeDeck| as well. In the formalization, the 
-hierarchical overriding feature is an important feature, involved in the algorithm of hierarchical dispatch.
-%\bruno{the last two sentences are a bit unclear. I think it is related to ``interaction''.}
+hierarchical overriding feature is an important feature, involved in
+the algorithm of hierarchical dispatch.
+
+Note that, although the example here only shows one conflicting method
+being overriden, hierarchical overriding allows (as expected) multiple conflicting
+methods to be overriden in the same class.
 
@@
 intentional conflicts, as they come from the same source $T$.
-% Similar to many OO languages, the model also allows \textit{super method invocation} in a method body.
-The invocation \lstinline|super.T::m()| will ignore all the subtypes of \lstinline|T|, and only look at \lstinline|T| together with its super interfaces.
-It should behave the same as \lstinline|new T().m()| in principle.
+% Similar to many OO languages, the model also allows \textit{super
+% method invocation} in a method body. The invocation
+% \lstinline|super.T::m()| will ignore all the subtypes of
+% \lstinline|T|, and only look at \lstinline|T| together with its
+% super interfaces. It should behave the same as \lstinline|new
+% T().m()| in principle.
+
+\bruno{I remember that a big complain in the reviews was talking about
+diamond inheritance. The Figure does have diamond inheritance but this
+wasn't clear to the reviewers. Please expand the text to emphasize
+diamond inheritance better!}

### 2018-05-29 ECOOP18/sections/Overview.tex
expanded text for discussing diamond problem with figure 3 (d)(e)(f)

@@
 (c) represents hierarchical overriding.
-(d) and (e) are two base cases of diamond inheritance in \MIM{} and the definition of each $C$ is rejected because $T$ is an ambiguous parent to $C$.
+Our model supports diamond inheritance and can deal with diamond problems.
+For example, (d) and (e) are two base cases of diamond inheritance in \MIM{} and the definition of each $C$ is rejected because $T$ is an ambiguous parent to $C$.
+One solution for diamond inheritance is to merge methods coming from different parents.
 (f) gives a common solution to the diamond as in Java or traits, which is to explicitly override $A.m$ and $B.m$ in $C$.
+And our calculus supports this kind of merging methods.
 In the last three examples, conflicting methods $A.m$ and $B.m$ should be viewed as
@@
 wasn't clear to the reviewers. Please expand the text to emphasize
-diamond inheritance better!}
+diamond inheritance better!}\yanlin{expanded.}

### 2018-06-04 ECOOP18/sections/Formalization.tex
address marco's suggestions

@@
 \subsubsection{Notations}
-The metavariables $I, J$ range over interface names; $x$ ranges over variables; $m$ ranges over method names; $e$ ranges over expressions; and $M$ ranges over method declarations.
+The metavariables $I, J, K$ range over interface names; $x$ ranges over variables; $m$ ranges over method names; $e$ ranges over expressions; and $M$ ranges over method declarations.
 Following Featherweight Java, we assume that the set of variables includes the special variable \kwthis, which cannot be used as the name of an argument to a method.
@@
 parent interfaces, where such a set can be empty. Moreover, as usual
-in class-based languages, the class hierarchy is acyclic.
+in class-based languages, \yanlin{refined 'acyclic'} the extension relation over interfaces is acyclic.
 The interface declaration $\interface{I}{I}{M}$ introduces an interface named $I$ with parent interfaces $\overline{I}$ and a suite of methods $\overline{M}$.
@@
 \kwoverride{} keyword for two cases: if the overridden interface is exactly the enclosing
-interface itself, then such a method is seen as originally defined; otherwise it is a hierarchical overriding method. 
+interface itself, then such a method is seen as originally defined \yanlin{added an explanation} (including the case of merging methods from different branches,  which can be viewed as \emph{reborn}); otherwise it is a hierarchical overriding method.
 Note that in an interface $J$, $
@@
 	\framebox{$ I <: J $} \hspace{.5in} \subid \\
-	\subtrans \hspace{.5in} \subextends \\
+	\subtrans \hspace{.5in} \subextendsForall \\
 
@@
 receiver. The result of $\mbody$ contains the interface that provides the most specific implementation,
-the parameters and the return type. We use underscore for the return expression, implying that an empty return expression
-from an abstract method is acceptable.
+the parameters and the return type. We use underscore for the return expression, matching both implemented and abstract methods. \yanlin{refined.}
 % \textsc{(T-PathInvk)} is the typing judgement for a path invocation.
@@
 
-\subsection{Small-step Semantics and Congruence}
+\subsection{Small-step Semantics and \Congruence{}}
 Figure~\ref{fig:smallstep} defines the small-step semantics and
-congruence rules of \MIM{}. When evaluating an expression, they
+\congruence{} rules of \MIM{}. When evaluating an expression, they
 are invoked and produce a single value in
@@
 and in the meanwhile the static types are recorded via annotations. Finally, the return type $I_e$ is put in the front as an annotation.
-\subsubsection{Congruence Rules} \textsc{(C-Receiver)}, \textsc{(C-Args)} and \textsc{(C-FReduce)} are natural congruence rules
+\subsubsection{\Congruence{} Rules} \textsc{(C-Receiver)}, \textsc{(C-Args)} and \textsc{(C-FReduce)} are natural \congruence{} rules
 on receivers, arguments, and cast-expressions, respectively. \textsc{(C-StaticType)} automatically adds an annotation $I$ to the new

### 2018-06-04 ECOOP18/sections/Overview.tex
address marco's suggestions

@@
 ((Deck) new DrawableDeck()).draw()  // calls Deck.draw
-// (new DrawableDeck()).draw()        // this call is ambiguous and rejected
+// new DrawableDeck().draw()        // this call is ambiguous and rejected
 \end{lstlisting}
-In our language, the main program is merely an expression. The above cast indicates
+\yanlin{Refined.}In our language, a program consists of interfaces declarations and a main an expression which produces the final result.
+In the above main expression \lstinline|((Deck) new DrawableDeck()).draw()|, the cast indicates
 that we expect to invoke the \lstinline|draw| method from the branch

### 2018-06-04 ECOOP18/sections/Auxiliary.tex
marco's suggestions

@@
 Such a function returns the most specific method implementation.
-More
-accurately, $\mbody$ returns the parameters, returned expression
-(empty for abstract methods) and the types for the method.
+\yanlin{Refined.}More
+accurately, $\mbody$ returns $(J, \overline{I_x} \; \overline{x}, I_e \; e_0)$ where $J$ is the found interface that contains the desired method; $\overline{I_x} \; \overline{x}$ are the parameters and its types, $e_0$ is the returned expression (empty for abstract methods).
 It considers both originally-defined methods and hierarchical overriding methods, so $\mostSpecific$ and $\mostSpecificOverride$ (see the definition in Section~\ref{sec:mostSpecific} and Section~\ref{sec:mostSpecificOverride}) are both invoked.
@@
 	& \rhd \textit{Definition of } \canOverride(m, I, J): & \\
-	& \bullet \canOverride(m, I, J) = True & \\
-	& \indent\indent \textrm{with: } I[m\ \kwoverride\ I] = I_e \; m(\overline{I_x} \; \overline{x}) \; \kwoverride \; I \ldots & \\
+	& \bullet \canOverride(m, I, J) \textrm{ holds} & \\
+	& \indent\indent \textrm{iff: } I[m\ \kwoverride\ I] = I_e \; m(\overline{I_x} \; \overline{x}) \; \kwoverride \; I \ldots & \\
 	& \hspace{.77in} J[m\ \kwoverride\ J] = I_e \; m(\overline{I_x} \; \overline{y}) \; \kwoverride \; J \ldots &
@@
 	& \rhd \textit{Definition of } \canInstantiate(I): & \\
-	& \bullet \canInstantiate(I) = True & \\
-	& \indent\indent \textrm{with: } \forall m, \forall J \in \mostSpecific(m, I, I), \mostSpecificOverride(m, I, J) = \{K\}, & \\
+	& \bullet \canInstantiate(I) \textrm{ holds} & \\
+	& \indent\indent \textrm{iff: } \forall m, \forall J \in \mostSpecific(m, I, I), \mostSpecificOverride(m, I, J) = \{K\}, & \\
 	& \hspace{.77in} \textrm{ and } K[m\ \kwoverride\ J] = \method{I_e}{m}{I_x}{x}{J}{e_0} &
@@
 $\mostSpecific(m, I, I)$ represents the set of branches $I$ inherits on method $m$. $I$ can be instantiated
-if and only if for every branch, the most specific implementation is unambiguous and non-abstract.
+if and only if for every branch, the most specific implementation is non-abstract. \yanlin{removed 'unambiguous'.}
 %%%%============================ canInstantiate end ================%%%%%%%%

### 2018-06-04 ECOOP18/sections/Discussion.tex
marco's suggestions

@@
 Furthermore, we discuss ways to improve our work.
+
+\yanlin{marco: The whole section 5 may benefit some English proofreading, but I'm too
+	bad at English to really help... may be Bruno can give some more
+	support here?}
 
@@
 methods by default (as done in many languages). 
+\yanlin{717: we could mention that Godez (the guy maintaing java now) would
+	prefer if Java behaved like our formalization but he can not for
+	retrocompatibility.
+	Re: where do you think is the proper place to mention this? }
 Arguably, for the diamond case, as we have mentioned, it is actually an intentional conflict due to the same source $T$.
@@
 With this approach, branches \lstinline|A| and \lstinline|B| are merged in the sense that they share the same code, which can be separately updated in future interfaces.
-Another approach is to deeply merge the branches, with similar effect as introducing an intermediate interface \lstinline|AB| to explicitly merge the two branches.
+Another approach would be to deeply merge the branches, with similar effect as introducing an intermediate interface \lstinline|AB| to explicitly merge the two branches.
 However, this approach is problematic because there is no clear mechanism of identifying and further updating the merged branches.

### 2018-06-04 ECOOP18/sections/RelatedWork.tex
expanded text for discussing diamond problem with figure 3 (d)(e)(f)
marco's suggestions

@@
 captures this aspect of the C++ method dispatching model.
-Apart from this, as discussed in Section~\ref{subsec:loosen}, \name{} conservatively rejects some interface/class definitions that C++ accepts, and upcasts are never rejected since they are used for ambiguity resolution.
-\bruno{The discussion points out further differences. We need to refer
-to that discussion here too.}\yanlin{added.}
+Apart from this, as discussed in Section~\ref{subsec:loosen}, \name{} conservatively rejects some interface/class definitions that C++ accepts, and upcasts are never rejected
+%since they are used for ambiguity resolution.
+since the ambiguity is prevented beforehand.
+\yanlin{fixed.}
 
@@
 workarounds that can mimick hierarchical
-overriding, including the \emph{MiddleMan} approach\footnote{\url{https://stackoverflow.com/questions/44632250/can-i-do-mimic-things-likes-this-partial-override-in-c}}, the \emph{interface classes} pattern as described in Section 25.6 of~\cite{stroustrup1995}, the \emph{LotterySimulation} discussion in~\cite{stroustrup1994design}.
+overriding, including the \emph{MiddleMan} approach\footnote{\url{https://stackoverflow.com/questions/44632250/can-i-do-mimic-things-likes-this-partial-ove}\\\url{rride-in-c}}, the \emph{interface classes} pattern as described in Section 25.6 of~\cite{stroustrup1995}, the \emph{LotterySimulation} discussion in~\cite{stroustrup1994design}.
 Since these workarounds share the same spirit, we will discuss in detail the \emph{MiddleMan} approach, with the code shown in
@@
 is easily extensible.
-In terms of formalization, the key novelty of our model is making use of various types (such as parameter types, method return types, etc) as upcasts along with various terms.
+In terms of formalization, the key novelty of our model is making use of various types (such as parameter types, method return types, etc) \yanlin{fixed} to track the static types as well as the dynamic types during reduction.
 As far as we know, this technique has not appeared in the literature before.

### 2018-06-05 ECOOP18/sections/Formalization.tex
revision in progress

@@
 method simply includes the returned expression $e$. Notably, we have introduced the
-\kwoverride{} keyword for two cases: if the overridden interface is exactly the enclosing
-interface itself, then such a method is seen as originally defined \yanlin{added an explanation} (including the case of merging methods from different branches,  which can be viewed as \emph{reborn}); otherwise it is a hierarchical overriding method.
+\kwoverride{} keyword for two cases. Firstly, if the overridden interface is exactly the enclosing
+interface itself, then such a method is seen as \emph{originally
+defined}. Note that  the case of merging methods from different
+branches,  also counts as originally defined.
+Secondly, for all other cases the method is considered a \emph{hierarchical overriding method}. 
 Note that in an interface $J$, $
-I \; m(\overline{I_x} \; \overline{x}) \; {\{} \kwreturn \; e ; {\}} $ is syntactic sugar for $\method{I}{m}{I_x}{x}{J}{e}$, which is the standard way of method definition in Java-like languages.
-The definition
+I \; m(\overline{I_x} \; \overline{x}) \; {\{} \kwreturn \; e ; {\}} $
+is syntactic sugar for $\method{I}{m}{I_x}{x}{J}{e}$, which is the
+standard way to define methods in Java-like languages. The definition
 of abstract methods is written as $\absmethod{I}{m}{I_x}{x}{J}$, which is

### 2018-06-05 ECOOP18/paper.tex
revision
marco's suggestions

@@
 \usepackage{url}
+%\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
+%\usepackage[hyphens]{url}
 %\usepackage{pstricks,pst-node,pst-tree} -- clash with preamble.tex
@@
 
-% \newcommand\bruno[1]{\authornote{bruno}{red}{#1}}
+\newcommand\bruno[1]{\authornote{bruno}{blue}{#1}}
  \newcommand\yanlin[1]{\authornote{yanlin}{red}{#1}}
@@
 
-\newcommand\bruno[1]{}
+%\newcommand\bruno[1]{}
 %\newcommand\yanlin[1]{}
@@
 
-\author{Yanlin Wang}
+\author{Yanlin Wang$^1$}
 {The University of Hong Kong, China}
@@
 {}{}%mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
-\author{Haoyuan Zhang}
+\author{Haoyuan Zhang$^1$}
 {The University of Hong Kong, China}
@@
 {bruno@cs.hku.hk}
-{}{}
+{}{Funded by Hong Kong Research Grant Council projects number 17210617 and 17258816}
 \author{Marco Servetto}
@@
 
-\Copyright{John Q. Public and Joan R. Public}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+\Copyright{Yanlin Wang, Haoyuan Zhang, Bruno C. d. S. Oliveira and Marco Servetto}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
 
-\subjclass{Dummy classification}% mandatory: Please choose ACM 2012 classifications from https://www.acm.org/publications/class-2012 or https://dl.acm.org/ccs/ccs_flat.cfm .
+\subjclass{Software and its engineering $\rightarrow$ Object oriented languages}% mandatory: Please choose ACM 2012 classifications from https://www.acm.org/publications/class-2012 or https://dl.acm.org/ccs/ccs_flat.cfm .
 E.g., cite as "General and reference $\rightarrow$ General literature" or \ccsdesc[100]{General and reference~General literature}.
 
-\keywords{Dummy keyword}%mandatory
+\keywords{multiple inheritance; hierarchical dispatching; OOP; language design}%mandatory
 
@@
 
-\acknowledgements{I want to thank \dots}%optional
+\acknowledgements{We thank the anonymous reviewers for their valuable comments.}%optional
 

### 2018-06-05 ECOOP18/sections/Discussion.tex
Revised Section 5

@@
 	Re: where do you think is the proper place to mention this? }
-Arguably, for the diamond case, as we have mentioned, it is actually an intentional conflict due to the same source $T$.
+Arguably, the diamond case it is actually an intentional conflict due
+to the same source $T$. Therefore our model conservatively rejects
+this case.
 It is possible to change our model to account for other behaviors for abstract methods, but we view this as a mostly 
-orthogonal change to our work, which should not affect the essence of the model presented here.
+orthogonal change to our work, and should not affect the essence of the model presented here.
 
@@
 \yanlin{Bruno: discussed multiple overriding and the two designs}
-One non-orthogonal extension to \MIM{} could be to generalize the model to allow multiple hierarchical method overrding, meaning that, we allow overriding methods to update multiple branches instead of only one branch.
-It offers a more fine-grained mechanism for merging, and can be helpful to easily understand the structure of the hierarchy.
+One non-orthogonal extension to \MIM{} could be to generalize the
+model to allow multiple hierarchical method overrding, meaning that,
+we allow overriding methods to update multiple branches instead of
+only one branch.
+This feature offers a more fine-grained mechanism for merging, and can be helpful to easily understand the structure of the hierarchy.
 Multiple overriding would be useful in the following situation, for example:

### 2018-06-06 ECOOP18/sections/Discussion.tex
Revision

@@
 \subsection{Abstract Methods}
-Abstract methods are one of the key features in most general OO languages. For example, Java interfaces were designed
+Abstract methods are one of the key features in most general OO
+languages. For example, Java interfaces (prior to Java 8) were designed
 to include only method declarations, and those abstract methods can be implemented in a class body. 
@@
 One non-orthogonal extension to \MIM{} could be to generalize the
-model to allow multiple hierarchical method overrding, meaning that,
+model to allow multiple hierarchical method overriding, meaning that,
 we allow overriding methods to update multiple branches instead of

### 2018-06-06 ECOOP18/sections/RelatedWork.tex
Revision

@@
 Moreover, the lack of direct syntax support makes MiddleMan code cumbersome to write.
-Finally, the approach is ad-hoc, meaning that the class \texttt{MiddleMan} shown in Figure~\ref{fig:middleman} is not general enough to be used in other cases: more middle-men are needed if partial method overrides happen in other classes; and it is even worse when return types differ.
+Finally, the approach is ad-hoc, meaning that the class \texttt{MiddleMan} shown in Figure~\ref{fig:middleman} is not general enough to be used in other cases: more middle-mens are needed if partial method overrides happen in other classes; and it is even worse when return types differ.
 

### 2018-06-11 ECOOP18/sections/Introduction.tex
revision in progress
remove line number, comments, compress to 25pages.

@@
 In a nominal system, methods can be designed for different
-functionality, but happen to have the same names (and signatures).
+functionality but happen to have the same names (and signatures).
 A simple example of this situation is two \lstinline{draw} methods that
@@
 adds expressive power that is not available in languages such as 
-C++ or C\#. Hierarchical overriding allows overriding to work 
+C++ or C\#. In particular, it allows overriding to work 
 for classes with multiple (conflicting) methods sharing the 

### 2018-06-11 ECOOP18/sections/Overview.tex
revision in progress
remove line number, comments, compress to 25pages.

@@
 interface DrawableSafeDeck extends Drawable, SafeDeck {}
-// main program
 new DrawableSafeDeck().shuffleAndDraw()
@@
 % \end{equation}
-
+\vspace{1ex}
 \begin{lstlisting}[style=reduction, escapechar=\%]
@@
 interface DrawableSafeDeck extends Drawable, SafeDeck {}
-// main program
 new DrawableSafeDeck().shuffleAndDraw() // SafeDeck.draw is called
@@
 \noindent The computation performed in \MIM{} is as follows:
+\vspace{1ex}
 \begin{lstlisting}[style=reduction, escapechar=\%]
@@
 }
-// main program
 ((Drawable)new DrawableSafeDeck()).draw(); //calls the draw in DrawableSafeDeck
@@
 
-In  Figure~\ref{fig:examplesmbody}, (a) is the base case for unintentional conflicts, namely the \wordfork{} inheritance.
-(b) uses overriding to explicitly merge the conflicting methods.
-(c) represents hierarchical overriding.
-Our model supports diamond inheritance and can deal with diamond problems.
+In  Figure~\ref{fig:examplesmbody}, (a) is the base case for
+unintentional conflicts, namely the \wordfork{} inheritance. (b) uses
+overriding to explicitly merge the conflicting methods. (c) represents
+hierarchical overriding.
+
+Furthermore, our model supports diamond inheritance and can deal with diamond problems.
 For example, (d) and (e) are two base cases of diamond inheritance in \MIM{} and the definition of each $C$ is rejected because $T$ is an ambiguous parent to $C$.

### 2018-06-11 ECOOP18/sections/Auxiliary.tex
spellcheck

@@
 \subsection{Finding the Most Specific Origin: \mostSpecific}\label{sec:mostSpecific}
-We proceed to give the definitions of two core functions that support method lookup, namely \mostSpecific{} and \mostSpecificOverride. Generally,
+We proceed to give the definitions of two core functions that support method lookup, namely, \mostSpecific{} and \mostSpecificOverride. Generally,
 $\mostSpecific(m, I, J)$ finds the set of most specific interfaces where $m$ is originally defined.
@@
 $\canInstantiate(I)$ checks whether interface $I$ can be instantiated by the keyword $\kwnew$.
-$\mostSpecific(m, I, I)$ represents the set of branches $I$ inherits on method $m$. $I$ can be instantiated
+$\mostSpecific(m, I, I)$ represents the set of branches that $I$ inherits on method $m$. $I$ can be instantiated
 if and only if for every branch, the most specific implementation is non-abstract. \yanlin{removed 'unambiguous'.}

### 2018-06-11 ECOOP18/sections/Formalization.tex
spellcheck

@@
 ``$(I)\new{J}$''
-is the final result of multiple reduction steps evaluating an
+is the final result of multiple reduction steps for evaluating an
 expression.
@@
 Then $\mbody(m, J, J)$ provides the type of the original method, so hierarchical overriding has to preserve the type. Finally the return expression
-is type-checked to be subtype of the declared return type.
+is type-checked to be a subtype of the declared return type.
 For the definition of an original method, $I$ equals $J$ and the rule is straightforward.
@@
 
-\textsc{(T-Intf)} defines the typing rule on interfaces. The first condition is obvious, namely its methods need to be well checked. The third
+\textsc{(T-Intf)} defines the typing rule on interfaces. The first condition is obvious, namely, its methods need to be well checked. The third
 condition checks whether the overriding between original methods preserves typing.

### 2018-06-11 ECOOP18/sections/Overview.tex
spellcheck

@@
 together with the features of our model for addressing this issue, by
-a simple running example. In the following text we will introduce three
+a simple running example. In the following text, we will introduce three
 problems one by one and have a discussion on possible workarounds and
@@
 can be drawn and also includes a method called \lstinline|draw| for
-visual display. For simple illustration, the default implementation of
+visual display. For simple illustration, the default implementation of the 
 \lstinline|draw| in \lstinline|Drawable| only creates a blank canvas
@@
   then it may be possible to rename one of the \lstinline|draw|
-  methods. However this approach is non-modular, as it requires 
+  methods. However, this approach is non-modular, as it requires 
   modifying existing code and becomes impossible if the code is unavailable.
@@
 Note that, although the example here only shows one conflicting method
-being overriden, hierarchical overriding allows (as expected) multiple conflicting
-methods to be overriden in the same class.
+being overridden, hierarchical overriding allows (as expected) multiple conflicting
+methods to be overridden in the same class.
 

### 2018-06-11 ECOOP18/sections/Discussion.tex
spellcheck done

@@
 only one branch.
-This feature offers a more fine-grained mechanism for merging, and can be helpful to easily understand the structure of the hierarchy.
+This feature offers a more fine-grained mechanism for merging and can be helpful to easily understand the structure of the hierarchy.
 Multiple overriding would be useful in the following situation, for example:
@@
 Another approach would be to deeply merge the branches, with similar effect as introducing an intermediate interface \lstinline|AB| to explicitly merge the two branches.
-However, this approach is problematic because there is no clear mechanism of identifying and further updating the merged branches.
+However, this approach is problematic because there is no clear mechanism for identifying and further updating the merged branches.
 This could be an interesting future work to explore.

### 2018-06-11 ECOOP18/sections/RelatedWork.tex
remove line number, comments, compress to 25pages.
spellcheck done

--- 2018-06-04 ECOOP18/sections/RelatedWork.tex
@@
 hierarchical overriding.  However, there are some possible
-workarounds that can mimick hierarchical
+workarounds that can mimic hierarchical
 overriding, including the \emph{MiddleMan} approach\footnote{\url{https://stackoverflow.com/questions/44632250/can-i-do-mimic-things-likes-this-partial-ove}\\\url{rride-in-c}}, the \emph{interface classes} pattern as described in Section 25.6 of~\cite{stroustrup1995}, the \emph{LotterySimulation} discussion in~\cite{stroustrup1994design}.
@@
 
-Class \texttt{MiddleMan}, as its name suggests, acts as a middle man between its class \texttt{C} and its parents \texttt{A, B}.
+Class \texttt{MiddleMan}, as its name suggests, acts as a middleman between its class \texttt{C} and its parents \texttt{A, B}.
 \texttt{MiddleMan} defines a virtual method \texttt{m} that overrides a parent method \texttt{m} and delegates the implementation to another method \texttt{m\_impl} that takes $\kwthis$ as a parameter.
@@
 In this way, programmers may define new versions of \texttt{A.m} and \texttt{B.m} in class \texttt{C} by providing the corresponding \texttt{m\_impl} methods.
-Then in the client code, the method call \texttt{((A*)c)->m()} will print out string \texttt{"MA2"}, as expected.
+Then in the client code, the method call \texttt{((A*)c)->m()} will print out the string \texttt{"MA2"}, as expected.
 Although this workaround can help us defining partial method overrides to a certain extent, the drawbacks are obvious.
@@
 Moreover, the lack of direct syntax support makes MiddleMan code cumbersome to write.
-Finally, the approach is ad-hoc, meaning that the class \texttt{MiddleMan} shown in Figure~\ref{fig:middleman} is not general enough to be used in other cases: more middle-men are needed if partial method overrides happen in other classes; and it is even worse when return types differ.
+Finally, the approach is ad-hoc, meaning that the class \texttt{MiddleMan} shown in Figure~\ref{fig:middleman} is not general enough to be used in other cases: more middlemen are needed if partial method overrides happen in other classes; and it is even worse when return types differ.
 
@@
 with an unambiguous path. As shown in Figure~\ref{fig:magda_prefix},
-the prefix \lstinline|HelloWorld| in method call \lstinline|(new HelloWorld []).HelloWorld.MainMatter()| is mandatory. So writing programs in these languages is
+the prefix \lstinline|HelloWorld| in the method call \lstinline|(new HelloWorld []).HelloWorld.MainMatter()| is mandatory. So writing programs in these languages is
 tedious if not supported by a specialized IDE, that aids filling
@@
 
+% \begin{figure*}[t]
+% 	% \saveSpaceFig
+% 	\begin{lstlisting}
+% mixin HelloWorld of Object =
+% 	new Object MainMatter()
+% 	begin "Hello world".String.print();	end;
+% end;
+% (new HelloWorld []).HelloWorld.MainMatter();
+% 	\end{lstlisting}
+%     \saveSpaceFig
+% 	\caption{Full-qualified name of method calls in Magda.}
+% 	\label{fig:magda_prefix}
+% 	% \saveSpaceFig
+% \end{figure*}
+
 \begin{figure*}[t]
-	\saveSpaceFig
+    % \saveSpaceFig
     \begin{lstlisting}
@@
     \end{lstlisting}
+    \saveSpaceFig
     \caption{Full-qualified name of method calls in Magda.}
     \label{fig:magda_prefix}
-	\saveSpaceFig
+    % \saveSpaceFig
 \end{figure*}
@@
 \begin{figure*}[t]
-	\saveSpaceFig
+	% \saveSpaceFig
 \begin{lstlisting}
@@
 \end{lstlisting}
+    \saveSpaceFig
 	\caption{Code in Magda.}
 	\label{fig:magda_code}
-	\saveSpaceFig
 \end{figure*}
+
+% \begin{figure*}[t]
+%     % \saveSpaceFig
+% \begin{lstlisting}
+% mixin A of Object =
+%     new String m() begin return "A"; end;
+% end; 
+% mixin B of Object = 
+%     new String m() begin return "B"; end;
+% end;
+% mixin C of A, B = 
+%     new String m() begin return "C"; end;
+% end;
+% \end{lstlisting}
+%     \saveSpaceFig
+%     \caption{Code in Magda.}
+%     \label{fig:magda_code}
+%     % \saveSpaceFig
+% \end{figure*}
 

### 2018-06-27 UnintentionalStateConflict/paper3/sections/Formalization.tex
simplified model

\section{Overview}
\subsection{Motivation}
Combine the work of FHJ and ClasslessJava.
\begin{itemize}
	\item Use abstract state operations to mimic state
	\item If two fields conflict from triangle inheritance, keep the two fields
	\item Override and covariant type refine of fields
\end{itemize}

Example of unintentional fields confliction:
\begin{lstlisting}
interface Payment {
	String Check(); // represnets an entity 'check'
}
interface Verify {
	boolean Check(); // represents a flag of whether the verification is checked or not.
}
interface VerifiedPayment extends Payment, Verify {}
\end{lstlisting}

C++ partly support this, just like unintentional method conflicts. However, c++ cannot handle the case where fields need to be refined or two conflicted fields need to be merged.
\begin{lstlisting}
class A {};
class B:A {};
class Payment {
	public:
	A* check;
};
class Verify {
	public:
	bool check;
};
class VerifiedPayment : public Payment, public Verify {
	public:
	B* check;
};

int main()
{
VerifiedPayment* vp = new VerifiedPayment();
vp->check = new B();
vp->Verify::check = true;
vp->check;
cout << vp->Payment::check << endl;
cout << vp->check << endl;
}
\end{lstlisting}

Example program in a desired language:
\begin{lstlisting}
interface A { int x(); int y(); }
interface B { int x(); }
interface C extends A, B {}
new B(B.x = 0).GET_x();   // 0
(A)new C(A.x = 1, A.y = 2, B.x = 3).GET_x();  // 1
\end{lstlisting}

\section{Formalization}~\label{sec:formalization}
This version:
\begin{itemize}
	\item void setters
	\item statements
	\item explicit constructor. (?)
\end{itemize}
\begin{figure*}
	\saveSpaceFig
	\begin{displaymath}
		\begin{array}{l}
			\begin{array}{llrl}
				\text{Program}		& P & \Coloneqq  & \overline{IL} \ e  \\
				\text{Interfaces}   & IL & \Coloneqq & \interfaceMC{I}{I}{MC?}{M} \\
				\text{Constructors} & MC & \Coloneqq & \constructor{I_x}{J.x} \\
				\text{Methods}      & M  & \Coloneqq & \method{I}{m}{I_x}{x}{J}{e}  \mid
													   \absmethod{I}{m}{I_x}{x}{J} \\
				\text{Expressions}  & e  & \Coloneqq & 
				x \mid
				e.m(\overline{e}) \mid
				(I)e \mid 
				\kwnew \; I(\overline{e}) \mid 
				\mylet{I}{x}{e_1}{e_2} \\
				\text{Context}      & \Gamma & \Coloneqq & \overline{x}:\overline{I} \\
				\text{Values}       & v & \Coloneqq & (I)o \\
			\end{array}
		\end{array}
	\end{displaymath}
	\caption{Syntax}\label{fig:syntax}
	\saveSpaceFig
\end{figure*}

%\begin{figure*}[]
%	\saveSpaceFig
%	\begin{mathpar}
%		\framebox{$ I <: J $} \hspace{.5in} \subid \\
%		\subtrans \hspace{.5in} \subextends \\
%		
%		\framebox{$ \judgeewf \Gamma {e:I} $} \hspace{.5in}
%		\tvar \\
%		\tinvk \\
%		% \tpathinvk \\
%		% \tsuperinvk \\
%		% \tstaticinvk  \\
%		\tnew \\
%		\tanno \\
%		\tmethod \\
%		\tabsmethod \\
%		\tintf
%	\end{mathpar}
%	\saveSpaceFig
%	\caption{Subtyping and Typing Rules}
%		\label{fig:typingrules}
%	\end{figure*}

\begin{figure}
	\begin{mathpar}
		\inferrule* [left=(T-Var)]
		{\judgeewf {} {\Delta \; OK} \\ \judgeewf \Delta {\Gamma \; OK} }
		{\judgeewf {\Delta; \Gamma, x:I}{x:I}}

		\inferrule* [left=(T-Invk)]
		{  \judgeewf {\Delta; \Gamma} {e_0:I_0}
			\\ \mbody(m, I_0, I_0) = (K, \overline{I_x} \; \overline{x}, I \; \_) 
			\\ \judgeewf {\Delta; \Gamma} \overline{e}:\overline{I}
			\\ \overline{I} \subtype \overline{I_x}
		}
		{\judgeewf {\Delta, \Gamma} e_0.m(\overline{e}):I}

		\inferrule* [left=(T-Constructor)]
		{  \mconstr(I_0) = \overline{I_x} \; \overline{x} 
			\\ \judgeewf {\Delta; \Gamma} \overline{e}:\overline{I}
			\\ \overline{I} \subtype \overline{I_x}
		}
		{\judgeewf {\Delta, \Gamma} \newI{I_0}{\overline{e}}:I_0}

		\inferrule* [left=(T-Cast)]
		{  \judgeewf {\Delta, \Gamma}\Gamma e:I  \\
			I \subtype J  }
		{ \judgeewf {\Delta, \Gamma} {(J)e : J} }

		\inferrule* [left=(T-Method)]
		{  I <: J \\
				\mostSpecific(m, I, J) = \{J\} \\
				\mbody(m, J, J) = (K, \overline{I_x} \; \overline{x}, I_e \; \_) \\
				\judgeewf {\Delta; \Gamma, \overline{x}:\overline{I_x}, this:I  } {e_0:I_0} \\
				I_0 \subtype I_e
		}
		{\method{I_e}{m}{I_x}{x}{J}{e_0} \text{ OK IN } I}

		\inferrule* [left=(T-AbsMethod)]
		{  I <: J \quad
			\mostSpecific(m, I, J) = \{J\} \\
			\mbody(m, J, J) = (K, \overline{I_x} \; \overline{x}, I_e \; \_)
		}
		{\absmethod{I_e}{m}{I_x}{x}{J} \text{ OK IN } I}

		\inferrule* [left=(T-MC)]
		{  \validMC(I, \overline{I_x}, \overline{J.x}) 
		}
		{\constructor{I_x}{J.x} \text{ OK IN } I}

		\inferrule* [left=(T-Intf)]
		{  MC \text{ OK IN }  I \\
			\overline{M} \text{ OK IN } I \\
			\forall J >: I \text{ and } m, \mbody(m, J, J) \text{ is defined} \Rightarrow \mbody(m, I, J) \text{ is defined} \\ 
			\forall J >: I \text{ and } m, I[m \; \kwoverride \; I] \text{ and } J[m \; \kwoverride \; J] \text{ defined}  \Rightarrow \canOverride(m, I, J)
		}
		{ \interfaceMC{I}{I}{MC?}{M} \text{ OK }}

		\inferrule* [left=(T-Prog)]
		{  \forall I \in \overline{IL}, I \text{ OK} \\
		   \judgeewf {\Delta; \Gamma} {e : T}
		}
		{ \prog{IL}{e} \text{ OK }}

		\inferrule* [left=(T-Let)]
		{  	\judgeewf {\Delta; \Gamma} {e_1:I_1} \\
			I_1 \subtype I \\	
			\judgeewf {\Delta; \Gamma, x:I} {e_2:I_2} 
		}
		{ 	\judgeewf {\Delta; \Gamma} {\mylet{I}{x}{e_1}{e_2}:I_2} }

		\end{mathpar}
	\caption{Typing Rules.}
\end{figure}

\begin{figure}
\begin{flushleft}
	\begin{mathpar}		
		\inferrule* [left=(E-Invk)]
		{ }{\mu \mid (J)o.m(\overline{v}) \to \mu \mid e'} \\
		\mu(o) = \newI{I}{...} \\ 
		\mbody(m, I, J) = \overline{x}, e \\ 
		e' = e[(J)o/\kwthis, \overline{v}/\overline{x}] \\

		\inferrule* [left=(E-New)]
		{ }{\mu \mid \newI{I}{\overline{v}} \to \mu' \mid (I)o} \\
		o \notin dom(\mu) \\
		\mu' = \mu, o \to \newI{I}{\overline{v}} \\

		\inferrule* [left=(E-Getter)] 
		{ }{\mu \mid (J)o.f() \to \mu \mid (I_F)o_i} \\
		\mu(o) = \newI{I}{o_1, ..., o_n} \\
		I_F \; J.f \textit{ is the i-th element of } \newI{I}{...} \\

		\inferrule* [left=(E-Setter)]
		{ }{\mu \mid (J)o.SET\_f((I')o) \to \mu' \mid (I)o} \\
		\mu(o) = \newI{I}{o_1, ..., o_n} \\
		J.f \textit{ is the i-th element of } \newI{I}{...} \\
		\mu = \mu'', o \to \newI{I}{o_1, ..., o_i, ..., o_n} \\
		\mu' = \mu'', o \to \newI{I}{o_1, ..., o', ..., o_n} \\

		\inferrule* [left=(E-Let)]
		{ }{\mu \mid \mylet{I}{x}{o}{e} \to \mu \mid e[(I)o/x]} \\

		\inferrule* [left=(E-Cast)]
		{ }{\mu \mid (J)((I)o) \to \mu \mid (J)o} \\

		\inferrule* [left=(E-CTX)]
		{\mu \mid e \to \mu' \mid e'}
		{\mu \mid \varepsilon\{e\} \to \mu' \mid \varepsilon\{e'\}} \\

		\varepsilon ::= \varepsilon.m(\overline{e}) \mid 
				     (J)o.m(\overline{o}, \varepsilon, \overline{e}) \mid
				     \newI{I}{\overline{o}, \varepsilon, \overline{e}} \mid
				     \mylet{I}{x}{\varepsilon}{e} \mid
				     (I)\varepsilon
		\end{mathpar}
\end{flushleft}
\caption{Reduction Rules.}
\end{figure}

\section{Aux}

\subsection{$\Delta$}

Definition of $\Delta(I)(J.f)$:
$\Delta(I)(J.f) = K$, where $K \; J.f \in \overline{K \; J.f}$, where $static \; I \; of (\overline{K \; J.f});$ is the method constructor of interface $I$.

\subsection{calField}
$ calField(I, J, \overline{K.f=e}, f_i)$
\begin{itemize}
	\item if $I.f_i \in \overline{K.f}$, return $e_i$ where $I.f_i = e_i$
	\item if $J.f_i \in \overline{K.f}$, return $e_i$ where $J.f_i = e_i$ 
\end{itemize}

\subsection{updateField}
similar as $calField$.

\subsection{validMC}
$\validMC(I, \overline{I_x}, \overline{J.x}) $:
\begin{itemize}
	\item If there are no abstract state operations, then empty argument list is valid.
	\item $\forall J.x \in \overline{J.x}, J.x \text{ is a valid field of } I, \text{ and can be seen as abstrate state operations, and the type matches } I_x$.
	\item The interface $I$ can be instantiated, meaning that, every abstrate field appears in the argument list of the constructor method.
\end{itemize}

\subsection{The Method Lookup Algorithm in \mbody{}}\label{subsec:mbodydef}
$\mbody(m, I_d, I_s)$ denotes the method body lookup function.
We use $I_d, I_s$, since $\mbody$ is usually invoked by a receiver of a method $m$, with its dynamic type $I_d$ and static type $I_s$. Such a function returns the most specific method implementation. More
accurately, $\mbody$ returns the parameters, returned expression
(empty for abstract methods) and the types for the method. It considers both originally-defined methods and hierarchical overriding methods, so $\mostSpecific$ and $\mostSpecificOverride$ (see the definition in Section~\ref{sec:mostSpecific} and Section~\ref{sec:mostSpecificOverride}) are both invoked.

\saveSpaceFig
\begin{flalign*}
	& \rhd \textit{Definition of } \mbody(m, I_d, I_s): & \\
	& \bullet \mbody(m, I_d, I_s) = (J, \overline{I_x} \; \overline{x}, I_e \; e_0) & \\
	& \indent\indent \textrm{with: } \mostSpecific(m, I_d, I_s) = \{I\} & \\
	& \hspace{.77in} \mostSpecificOverride(m, I_d, I) = \{J\} & \\
	& \hspace{.77in} J[m\ \kwoverride\ I] = \method{I_e}{m}{I_x}{x}{I}{e_0} & \\
	& \bullet \mbody(m, I_d, I_s) = (J, \overline{I_x} \; \overline{x}, I_e \; \o) & \\
	& \indent\indent \textrm{with: } \mostSpecific(m, I_d, I_s) = \{I\} & \\
	& \hspace{.77in} \mostSpecificOverride(m, I_d, I) = \{J\} & \\
	& \hspace{.77in} J[m\ \kwoverride\ I] = \absmethod{I_e}{m}{I_x}{x}{I} & \\
\end{flalign*}
\saveSpaceFig

To calculate $\mbody(m, I_d, I_s)$, the invocation of $\mostSpecific$ looks for the most specific original methods and their interfaces, and expects a singleton set, so as to achieve unambiguity. Furthermore, the invocation of $\mostSpecificOverride$ also expects a unique and most specific hierarchical override. And finally the target method is returned.

\subsection{\mostSpecific}\label{sec:mostSpecific}
We proceed to give the definitions of two core functions that support method lookup, namely \mostSpecific{} and \mostSpecificOverride. Generally,
$\mostSpecific(m, I, J)$ finds the set of most specific interfaces where $m$ is originally defined. Interfaces in this set should be above interface $I$ and along path $J$. Finally with $\prune$ (defined in Section~\ref{sec:otherdefs})
the overridden interfaces will be filtered out.

\saveSpaceFig
\begin{flalign*}
	& \rhd \textit{Definition of } \mostSpecific(m, I, J): & \\
	& \bullet \mostSpecific(m, I, J) = \prune(origins) & \\
	& \indent\indent \textrm{with: } origins = \{K \mid \subt{I}{K}, \textrm{ and } \subt{K}{J} \; \lor \; \subt{J}{K}, &\\
	& \hspace{1.62in} \textrm{ and } K[m\ \kwoverride\ K] \textrm{ is defined} \} &
\end{flalign*}
By the definition, an interface belongs to $\mostSpecific(m, I, J)$ if and only if:
\begin{itemize}
	\item It originally defines $m$;
	\item It is a supertype of $I$ (including $I$);
	\item It is either a supertype or a subtype of $J$ (including $J$);
	\item Any subtype of it does not belong to the same result set because of $\prune$.
\end{itemize}
\saveSpaceFig

\subsection{\mostSpecificOverride}\label{sec:mostSpecificOverride}
The $\mostSpecific$ function only focuses on original method
implementations, where all the hierarchical overriding methods are omitted
during that step. On the other hand, $\mostSpecificOverride(m, I, J)$
has the assumption that $J$ defines an original $m$, and this function
tries to find the interfaces with the most specific implementations that hierarchically overrides such an $m$. Formally,

\saveSpaceFig
\begin{flalign*}
	& \rhd \textit{Definition of } \mostSpecificOverride(m, I, J): & \\
	& \bullet \mostSpecificOverride(m, I, J) = \prune(overrides) & \\
	& \indent\indent \textrm{with: } overrides = \{K \mid \subt{I}{K}, \; \subt{K}{J} \textrm{ and } K[m\ \kwoverride\ J] \textrm{ is defined} &
\end{flalign*}
\saveSpaceFig

By the definition, an interface belongs to $\mostSpecificOverride(m, I, J)$ if and only if:
\begin{itemize}
	\item it is between $I$ and $J$ (including $I$, $J$);
	\item it hierarchically overrides $J.m$;
	\item any subtype of it does not belong to the same set.
\end{itemize}

\subsection{others}\label{sec:otherdefs}
Below we give other minor definitions of the auxiliary functions that are used in previous sections.

%%%%============================ I[m override J] ================%%%%%%%%
\begin{flalign*}
	& \rhd \textit{Definition of } I[m\ \kwoverride\ J]: & \\
	& \bullet I[m\ \kwoverride\ J] = \method{I_e}{m}{I_x}{x}{J}{e_0} & \\
	& \indent\indent \textrm{with: }
	\kwinterface \; I \; \kwextends \; \overline{I} \; \{ \method{I_e}{m}{I_x}{x}{J}{e_0} \ldots \} & \\
	& \bullet I[m\ \kwoverride\ J] = \absmethod{I_e}{m}{I_x}{x}{J} & \\
	& \indent\indent \textrm{with: }
	\kwinterface \; I \; \kwextends \; \overline{I} \; \{ \absmethod{I_e}{m}{I_x}{x}{J} \ldots \} & \\
\end{flalign*}
Here $I[m\ \kwoverride\ J]$ is basically a direct lookup for method $m$ in the body of $I$, where such a method
overrides $J$ (like static dispatch). The method can be either concrete or abstract, and the body of definition is returned. Notice that
by our syntax, $I[m\ \kwoverride\ I]$ is looking for the originally-defined method $m$ in $I$.
%%%%============================ I[m override J] end================%%%%%%%%

%%%%============================ prune(set) ================%%%%%%%%
\saveSpaceFig
\begin{flalign*}
	& \rhd \textit{Definition of } \prune(set): & \\
	& \bullet \prune(set) = \{I \in set \; | \; \nexists J \in set\setminus I, J <: I\} &
\end{flalign*}

The $\prune$ function takes a set of
types, and filters out those that have subtypes in the same set. In the returned set,
none of them has subtyping relation to one another, since all supertypes have been removed.
%%%%============================ prune(set) end ================%%%%%%%%

\subsection{$\Delta$}
\saveSpaceFig
\begin{flalign*}
	& \rhd \textit{Definition of } \Delta_f(I)(J.f) & \\
	& I', \text{ where } J == I  \text{ and } I' f(); \text{ defined in } I. & \\
	& I'', \text{ where } I'' f(); \text{ defined in } J \text{ and } \forall I \subtype J' 
	\subtype J, \text{ there is no field } f \text{ defined in } J'.   &
\end{flalign*}

\subsection{$\eval(Sc, x)$}
\saveSpaceFig
\begin{flalign*}
	& \rhd \textit{Definition of } \eval(Sc, x): & \\
	& \bullet \eval(Sc, x) = Sc(x), x \in dom(Sc) & 
\end{flalign*}

\subsection{example}
\begin{lstlisting}
interface I {
	int x();
	static I of(int I.x);
}

interface A {
	int x();
}
interface B {
	int x();
}
interface C extends A, B {
	static C of (int A.x, int B.x);
}
C.of(3,2)
\end{lstlisting}

### 2018-06-27 StateMIM-small/src/framework/AST.scala
Impl using scope (can work).

@@ -25,7 +25,7 @@ object AST {
       }
     }
     def eval(): (String, String) = {
-      val init = Config(H(Map(), 1), VS(List(BS(List()))), e, FS(List()))
+      val init = Config(H(Map(), 1), VS(List(BS(List()))), e)
       Semantics.eval(collectInfo.get, init)
     }
     
@@ -133,7 +133,8 @@ object AST {
       assert(constr.get.paras.size == args.size, Message("Wrong arguments on invk of " + t + "." + m + "()."))
       for (i <- 0 to args.size - 1) {
         val argType = args(i).checkType(info, env)
-        assert(argType == constr.get.paras(i).fieldType, Message("Wrong argument type on invk of " + t + "." + m + "()."))
+        assert(info.subType(argType, constr.get.paras(i).fieldType),
+            Message("Wrong argument#" + (i + 1) + " type on invk of " + t + "." + m + "()."))
       }
       t
     }
@@ -158,7 +159,7 @@ object AST {
       assert(fieldType.isDefined, Message(fieldName + " not a field in " + eT))
       // fieldName:efT, check paraT <: efT 
       assert(info.subType(para.checkType(info, env), fieldType.get), Message("para type <: " + fieldType.get + "does not hold"))
-      eT //TODO: should return static type or?
+      "Void"
     }
   }
  
@@ -175,49 +176,17 @@ object AST {
     }
   }
   
-  case class Value(t: String, id: OId) extends Expr {
-    override def isValue = true
+  case class InvkCloseExpr(e: Expr) extends Expr {
     def checkType(info: Info, env: Map[String, String]) = throw Buggy
   }
   
-  abstract class OpenExpr {
-    def fill(v: Value): Expr = throw Error.TODO
-  }
+  case class LetCloseExpr(e: Expr) extends Expr {
+    def checkType(info: Info, env: Map[String, String]) = throw Buggy
+  } 
   
-  case class Invk_E(m: String, args: List[Expr]) extends OpenExpr {
-    override def fill(v: Value) = Invk(v, m, args)
-  }
-  
-  case class Invk_Arg(e: Expr, m: String, args: List[Expr], index: Int) extends OpenExpr {
-    override def fill(v: Value) = Invk(e, m, args.updated(index, v))
-  }
-  
-  case class InvkStatic_Arg(t: String, m: String, args: List[Expr], index: Int) extends OpenExpr {
[…]

### 2018-06-27 StateMIM-small/src/framework/Configuration.scala

@@ -28,31 +28,23 @@ object Configuration {
   case class BS(varTable: List[(String, Value)]) {
     def addLet(x: String, v: Value) = BS((x, v) +: varTable)
     def remLet() = BS(varTable.tail)
+    override def toString() = if (varTable.isEmpty) ""
+      else varTable.map(p => p._1 + " = " + p._2).reduce((a, b) => a + "; " + b)
   }
   
   case class VS(scopes: List[BS]) {
     def addScope(scope: BS) = VS(scope +: scopes)
     def addLet(x: String, v: Value) = VS(scopes.head.addLet(x, v) +: scopes.tail)
-    def remLet() = VS(scopes.head.remLet() +: scopes.tail)
     def remScope() = VS(scopes.tail)
+    def remLet() = VS(scopes.head.remLet() +: scopes.tail)
     def getVar(x: String) = scopes.head.varTable.find(p => p._1 == x).get._2
-//    def addVar(x: String, v: Value) = VS(scopes.head.addVar(x, v) +: scopes.tail)
-//    def addScope(thisValue: (String, Value), argsValue: List[(String, Value)]): VS = {
-//      val bs = BS(Map(thisValue._1 -> thisValue._2) ++ argsValue)
-//      VS(bs +: scopes)
-//    }
+    override def toString() = if (scopes.isEmpty) ""
+      else scopes.map(p => "[" + p.toString + "]").reduce((a, b) => a + "\n\t " + b)
   }
   
-  case class FS(frames: List[Either[Expr, OpenExpr]]) {
-    def addFrame(open: OpenExpr) = FS(Right(open) +: frames)
-  }
-  
-  case class Config(h: H, vs: VS, expr: Expr, frameStack: FS) {
-    override def toString() = {
-      val tab = "\n      "
-      "Config(" + tab + "expr = " + expr.toString() + tab + "fs = " + frameStack.toString() +
-        tab + "vs = " + vs.toString() + tab + "h = " + h.toString() + "\n    )"
-    }
+  case class Config(h: H, vs: VS, e: Expr) {
+    def update(f: Expr => Expr) = Config(h, vs, f(e))
+    override def toString() = "H = " + h + "\n    VS = " + vs + "\n    Expr = " + e
   }
   
 }

### 2018-06-27 StateMIM-small/src/framework/Error.scala

@@ -12,7 +12,7 @@ object Error {
   
   case object Buggy extends Throwable
   case object TODO extends Throwable
-  case class Done(c: Config) extends Throwable
+  case class Done(config: Config) extends Throwable
   
   def assert[A](f: Boolean, exception: Throwable): Unit = if (!f) throw exception
   def nextError(f: Throwable, g: Throwable): Unit = {printError(f); throw g}

### 2018-06-27 StateMIM-small/src/framework/Info.scala

@@ -8,16 +8,14 @@ case class Info(table: List[String], typeMap: Map[String, List[String]],
   def isField(i: String, j: String, m: String): Option[(Int, String)] = {
     // see the of() method in class I.
     // see if argument J.m exists
-    println("Checking isField: i = " + i + " j = " + j + " m = " + m)
     val typeDef = typeDefMap.get(i).get
     val constr = typeDef.constr
-    if (constr.isEmpty) {println("here"); return None}
+    if (constr.isEmpty) return None
     val paras = constr.get.paras
     for (x <- 0 to paras.length - 1) {
       val para = paras(x)
       if (para.path == j && para.name == m) return Some(x, para.fieldType)
     }
-    println("there")
     None
   }
   
@@ -98,7 +96,6 @@ case class Info(table: List[String], typeMap: Map[String, List[String]],
   }
   def isField(info: Info, name: String, t: String) : Option[String] = {
     val mbody = info.mbody(name, t, t)
-    println("mbody(" + name + ", " + t + ", " + t + ") = " + mbody)
     if (mbody.isEmpty) return None
     if (mbody.get._2.size != 0) return None
     if (mbody.get._3._2.isDefined) return None

### 2018-06-27 StateMIM-small/src/framework/Main.scala

@@ -23,18 +23,19 @@ object Main {
     }
   }     
   def main(args : Array[String]) = {    
-//    println("----------------------------------\nTest0:\n")
-//    run("Test0")
-//    println("----------------------------------\nTest1:\n")
-//    run("Test1")
-//    println("----------------------------------\nTest2:\n")
-//    run("Test2")
-//    println("----------------------------------\nTest3:\n")
-//    run("Test3")
-//    println("----------------------------------\nTest4:\n")
-//    run("Test4")
-//    println("----------------------------------\nTest5:\n")
-//    run("Test5")
+    println("----------------------------------\nTest0:\n")
+    run("Test0")
+    println("----------------------------------\nTest1:\n")
+    run("Test1")
+    println("----------------------------------\nTest2:\n")
+    run("Test2")
+    println("----------------------------------\nTest3:\n")
+    run("Test3")
+    println("----------------------------------\nTest4:\n")
+    run("Test4")
+    println("----------------------------------\nTest5:\n")
+    run("Test5")
+    println("----------------------------------\nTest6:\n")
     run("Test6")
   }
 }

### 2018-06-27 StateMIM-small/src/framework/Semantics.scala

@@ -9,14 +9,13 @@ object Semantics {
   def eval1(info: Info, config: Config): Config = {
     val h = config.h
     val vs = config.vs
-    val fs = config.frameStack
-    config.expr match {
-      case Var(x) => Config(h, vs, vs.getVar(x), fs)
+    config.e match {
+      case Var(x) => Config(h, vs, vs.getVar(x))
       case Invk(e, m, args) => {
-        if (!e.isValue) return Config(h, vs, e, fs.addFrame(Invk_E(m, args)))
+        if (!e.isValue) return eval1(info, Config(h, vs, e)).update(Invk(_, m, args))
         for (index <- 0 to args.length - 1) {
           if (!args(index).isValue)
-            return Config(h, vs, args(index), fs.addFrame(Invk_Arg(e, m, args, index)))
+            return eval1(info, Config(h, vs, args(index))).update(x => Invk(e, m, args.updated(index, x)))
         }
         
         val eValue = e match { case v : Value => v } //cast e to value
@@ -29,52 +28,48 @@ object Semantics {
         val isField = info.isField(i, j2, m)
         if (args.length == 0 && isField.isDefined) { //Getters
           val resId = obj.fields(isField.get._1)
-          Config(h, vs, Value(isField.get._2, resId), fs)
+          return Config(h, vs, Value(isField.get._2, resId))
         } else { //Normal invocations
           val paramsMap: List[(String, Value)] = mbody._2.zip(args).map(p => {
             val argValueId = p._2 match { case Value(_, vid) => vid }
             (p._1.name, Value(p._1.paramType, argValueId))
           }) :+ ("this", Value(mbody._1, eValue.id))
           val newScope = vs.addScope(BS(paramsMap))
-          Config(h, newScope, AnnoExpr(mbody._3._1, mbody._3._2.get), fs.addFrame(ReturnExprForInvk()))
+          Config(h, newScope, InvkCloseExpr(AnnoExpr(mbody._3._1, mbody._3._2.get)))
         }
       }
       case InvkStatic(t, m, args) => {
         for (index <- 0 to args.length - 1) {
-          if (!args(index).isValue)
-            return Config(h, vs, args(index), fs.addFrame(InvkStatic_Arg(t, m, args, index)))
+          if (!args(index).isValue) 
[…]

### 2018-06-27 StateMIM-small/src/framework/StateMIMParser.scala

@@ -6,7 +6,7 @@ import scala.util.parsing.combinator.syntactical._
 object StateMIMParser extends StandardTokenParsers with PackratParsers {
   import AST._
   
-  lexical.reserved += ("interface", "extends", "return", "override", "super", "static", "let")
+  lexical.reserved += ("interface", "extends", "return", "override", "super", "static")
   lexical.delimiters += ("(", ")", "{", "}", ",", ".", "::", ";", "=")
   
   val lcid = ident ^? { case id if id.charAt(0).isLower => id }
@@ -31,7 +31,9 @@ object StateMIMParser extends StandardTokenParsers with PackratParsers {
         { case e ~ m ~ args => Invk(e, m, args) } |||
       pE ~ ("." ~> ucid) ~ ("(" ~> pE <~ ")") ^^
         { case e ~ m ~ arg if (m.startsWith("SET_")) => InvkSetter(e, m.substring(4), arg) } |||
-      ("let" ~> ucid) ~ lcid ~ ("=" ~> pE) ~ (";" ~> pE) ^^
+      pE ~ ("." ~> ucid) ~ ("(" ~> pE <~ ")") ~ (";" ~> pE) ^^
+        { case e ~ m ~ arg ~ e2 if (m.startsWith("SET_")) => LetExpr("Void", "TEMP", InvkSetter(e, m.substring(4), arg), e2) } |||
+      ucid ~ lcid ~ ("=" ~> pE) ~ (";" ~> pE) ^^
         { case t ~ x ~ e1 ~ e2 => LetExpr(t, x, e1, e2) } |||
       lcid ~ ("(" ~> repsep(pE, ",") <~ ")") ^^
         { case m ~ args => Invk(Var("this"), m, args) } |||
@@ -41,8 +43,11 @@ object StateMIMParser extends StandardTokenParsers with PackratParsers {
         { case t ~ m ~ args => InvkStatic(t, m, args) }
   }
   
-  def parse(in: String): Either[String, Program] = phrase(Parser.pP)(new lexical.Scanner(in)) match {
+  def parse(in: String): Either[String, Program] = {
+    val prelude = "interface Void {static Void of();}"
+    phrase(Parser.pP)(new lexical.Scanner(prelude + in)) match {
       case t if t.successful => Right(t.get)
       case t                 => Left(t.toString)
+    }
   }
 }

### 2018-07-05 UnintentionalStateConflict/paper3/sections/Formalization.tex
temp

@@
 \begin{itemize}
-	\item void setters
-	\item statements
-	\item explicit constructor. (?)
+	\item does not support fluent setters
+	\item let-expressions
+	\item explicit constructor.
 \end{itemize}
@@
 \end{lstlisting}
+
+\section{Proof}
+\subsection{Properties}
+\begin{theorem}[Subject Reduction]~\label{theorem_subject}
+If $\judgeewf \Gamma {e : I}$ and $e \rightarrow e'$, 
+then $\judgeewf \Gamma {e' : I}$.
+\end{theorem}
+\begin{proof}
+See Appendix~\ref{appendix_proof}.
+\end{proof}
+
+\begin{theorem}[Progress]~\label{theorem_progress}
+Suppose $e$ is a well-typed expression, if $e$ includes 
+$\left((J)\emph{\kwnew}\;I()\right).m(\overline{v})$ as a sub-expression, then $\mbody(m, I, J) = (I_0, \overline{I_x} \; \overline{x}, I_e\; e_0)$ and $\num{\overline{x}} = \num{\overline{v}}$ for some $I_0$, $\overline{I_x}$, $\overline{x}$, $I_e$ and $e_0$.
+\end{theorem}
+\begin{proof}
+See Appendix~\ref{appendix_proof}.
+\end{proof}
+
+\begin{theorem}[Type Soundness]~\label{theorem_soundness}
+If $\judgeewf \o {e : I}$ and $e \to^* e'$ with $e'$ a normal form, then $e'$ is 
+a value $v$ with $\judgeewf \o {v:I}$.
+\end{theorem}
+\begin{proof}
+Immediate from Theorem~\ref{theorem_subject} and Theorem~\ref{theorem_progress}.
+\end{proof}
+
+\begin{theorem}[Determinacy of One-Step Evaluation]~\label{theorem_determinacy}
+	If $t \to t'$ and $t \to t''$, then $t' = t''$.
+\end{theorem}
+\begin{proof}
+See Appendix~\ref{appendix_proof}.
+\end{proof}

### 2018-07-05 StateMIM-small/src/framework/AST.scala
H's implementation for the simple model

@@ -25,7 +25,7 @@ object AST {
       }
     }
     def eval(): (String, String) = {
-      val init = Config(H(Map(), 1), VS(List(BS(List()))), e)
+      val init = Config(H(Map(), 1), e)
       Semantics.eval(collectInfo.get, init)
     }
     
@@ -103,6 +103,8 @@ object AST {
   abstract class Expr {
     def isValue: Boolean = false
     def checkType(info: Info, env: Map[String, String]): String
+    def subst(x: String, v: Value): Expr // warning: trivial subst. not capture avoiding.
+    // override def toString() = Pretty.pretty(this) // TODO
   }
   
   case class Var(x: String) extends Expr {
@@ -110,6 +112,7 @@ object AST {
       case Some(t) => t
       case None    => throw VarNotInScope(x)
     }
+    def subst(s: String, v: Value) = if (s == x) v else Var(x)
   }
   
   case class Invk(e: Expr, m: String, args: List[Expr]) extends Expr {
@@ -122,6 +125,7 @@ object AST {
       assert(mtype.get._1.zip(argsT).forall(p => info.subType(p._2, p._1)), Message("Argument types unexpected."))
       mtype.get._2
     }
+    def subst(x: String, v: Value) = Invk(e.subst(x, v), m, args.map(_.subst(x, v)))
   }
   
   case class InvkStatic(t: String, m: String, args: List[Expr]) extends Expr {
@@ -138,6 +142,7 @@ object AST {
       }
       t
     }
+    def subst(x: String, v: Value) = InvkStatic(t, m, args.map(_.subst(x, v)))
   }
   
   case class AnnoExpr(i: String, e: Expr) extends Expr {
@@ -147,6 +152,7 @@ object AST {
       assert(info.subType(eT, i), Message(eT + " <: " + i + " does not hold."))
       i
     }
+    def subst(x: String, v: Value) = AnnoExpr(i, e.subst(x, v))
   }
   
   case class InvkSetter(e: Expr, fieldName: String, para: Expr) extends Expr {
@@ -161,6 +167,7 @@ object AST {
       assert(info.subType(para.checkType(info, env), fieldType.get), Message("para type <: " + fieldType.get + "does not hold"))
       "Void"
     }
+    def subst(x: String, v: Value) = InvkSetter(e.subst(x, v), fieldName, para.subst(x, v))
   }
  
[…]

### 2018-07-05 StateMIM-small/src/framework/Semantics.scala

@@ -8,14 +8,16 @@ object Semantics {
   
   def eval1(info: Info, config: Config): Config = {
     val h = config.h
-    val vs = config.vs
     config.e match {
-      case Var(x) => Config(h, vs, vs.getVar(x))
+      case Var(x) => {
+        println(x)
+        throw Buggy
+      }
       case Invk(e, m, args) => {
-        if (!e.isValue) return eval1(info, Config(h, vs, e)).update(Invk(_, m, args))
+        if (!e.isValue) return eval1(info, Config(h, e)).update(Invk(_, m, args))
         for (index <- 0 to args.length - 1) {
           if (!args(index).isValue)
-            return eval1(info, Config(h, vs, args(index))).update(x => Invk(e, m, args.updated(index, x)))
+            return eval1(info, Config(h, args(index))).update(x => Invk(e, m, args.updated(index, x)))
         }
         
         val eValue = e match { case v : Value => v } //cast e to value
@@ -28,48 +30,44 @@ object Semantics {
         val isField = info.isField(i, j2, m)
         if (args.length == 0 && isField.isDefined) { //Getters
           val resId = obj.fields(isField.get._1)
-          return Config(h, vs, Value(isField.get._2, resId))
+          return Config(h, Value(isField.get._2, resId))
         } else { //Normal invocations
           val paramsMap: List[(String, Value)] = mbody._2.zip(args).map(p => {
             val argValueId = p._2 match { case Value(_, vid) => vid }
             (p._1.name, Value(p._1.paramType, argValueId))
           }) :+ ("this", Value(mbody._1, eValue.id))
-          val newScope = vs.addScope(BS(paramsMap))
-          Config(h, newScope, InvkCloseExpr(AnnoExpr(mbody._3._1, mbody._3._2.get)))
+          val returnExpr = AnnoExpr(mbody._3._1, mbody._3._2.get)
+          Config(h, paramsMap.foldRight[Expr](returnExpr)((p1: (String, Value), p2: Expr) => p2.subst(p1._1, p1._2)))
         }
       }
       case InvkStatic(t, m, args) => {
         for (index <- 0 to args.length - 1) {
-          if (!args(index).isValue) 
-            return eval1(info, Config(h, vs, args(index))).update(x => InvkStatic(t, m, args.updated(index, x)))
[…]

### 2018-07-13 poster/poster.tex
poster

@@
   }
-\begin{comment}
-  \headerbox{Implementation}{name=implementation,column=0,below=contribution}{
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Java supports compilation agents, where Java libraries can interact with the Java compilation process,
-acting as a man in the middle between the
-generation of AST and bytecode.
+\headerbox{Real Conflicts}{name=implementation,column=0,below=contribution}{
 
-This process is facilitated by frameworks like Lombok:
-a Java library that aims at reducing Java boilerplate code via
-annotations. \mixin was created using Lombok.
+\noindent{\centering\includegraphics[width=5em]{../ECOOP18/pics/P1.pdf}\\}
+\vspace{0.5em}
+\noindent{\centering\includegraphics[width=5em]{../ECOOP18/pics/P4.pdf}\\}
+\vspace{0.1em}
 
-\noindent{\centering\includegraphics[width=\linewidth]{pdfs/lombok3.png}\\}
-\vspace{0.1em}
+\begin{enumerate}
+\item Real conflicts needs to be explicitly resolved by programmers. \\
+\item Existing OOP models have taken care of this case intensively.
+\end{enumerate}
+% \begin{figure*}
+% \begin{tabular}{clcl}
+% &\multicolumn{1}{c}{\includegraphics[width=5em]{../ECOOP18/pics/P1.pdf}} & & 
+% \multicolumn{1}{c}{\includegraphics[width=5em]{../ECOOP18/pics/P4.pdf}}\\
+% \end{tabular}
+% \end{figure*}
 }
 
-  \headerbox{UML Diagram}{name=uml,column=0,below=implementation}{
+  \headerbox{Unintentional Conflicts}{name=uml,column=0,below=implementation,above=bottom}{
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\noindent{\centering\includegraphics[width=0.8\linewidth]{pdfs/PegasusDetail.pdf}\\}
+\noindent{\centering\includegraphics[width=\linewidth]{../ECOOP18/pics/conflicts.png}\\}
 \vspace{0.1em}
+\begin{enumerate}
+\item Conflicting methods have completely different meaning/domain which just share the same name (and parameter types). 
+\item Few existing OOP models support unintentional method conflicts well. 
+\end{enumerate}
 }
 
+\begin{comment}  
   \headerbox{Results (Partial)}{name=result,column=0,below=uml,above=bottom}{
@@
 \vspace{-0.5em}
-\headerbox{Object Interfaces and Instantiation}{name=Model,column=1,span=2,row=0}{
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \lstinputlisting[linerange=6-13]{../UseMixinLombok/src/pegasus/simple/java8/Main.java}% APPLY:linerange=PEGASUS_JAVA
-% \lstinputlisting[linerange=17-19]{../UseMixinLombok/src/pegasus/simple/java8/Main.java}% APPLY:linerange=PEGASUS_INST
-\lstinputlisting[linerange=8-12]{../UseMixinLombok/src/pegasus/simple/lombok/Main.java}% APPLY:linerange=PEGASUS_LOMBOK
-\lstinputlisting[linerange=1-5]{./import_src/src1.txt}
+\headerbox{P1: basic unintentional method conflicts}{name=Model,column=1,span=2,row=0}{
+\lstinputlisting[linerange=1-6]{./src/src1.txt}
 }
@@
 \vspace{-0.5em}
-\headerbox{Object Interfaces with State (immutable data)}{name=results,column=1,span=2,row=0,below=Model}{
+\headerbox{P2: dynamic dispatching}{name=results,column=1,span=2,row=0,below=Model}{
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\lstinputlisting[linerange=7-11]{./import_src/src1.txt}
-\lstinputlisting[linerange=13-15]{./import_src/src1.txt}
+\lstinputlisting[linerange=9-17]{./src/src1.txt}
 }
@@
 
-\headerbox{with- Methods}{name=with,column=1,span=2,row=0,below=results}{
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\lstinputlisting[linerange=1-5]{./import_src/src2.txt}
+\headerbox{P3: overriding on individual branches}{name=with,column=1,span=2,row=0,below=results}{
+
+\lstinputlisting[linerange=20-29]{./src/src1.txt}
 }
@@
 \vspace{-0.5em}
-\headerbox{Mutable Data \& Field Type Refinement}{name=refine,column=1,span=2,row=0,below=with}{
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\lstinputlisting[linerange=7-10]{./import_src/src2.txt}
+\headerbox{Syntax}{name=syntax,column=1,span=2,row=0,below=with}{
+\noindent{\includegraphics[width=0.9\linewidth]{pdfs/syntax.png}}
 }
@@
 
-\headerbox{More in the paper}{name=more,column=1,span=2,row=0,below=refine}{
+\headerbox{The Key Semantics Rule}{name=semantics,column=1,span=2,row=0,below=syntax}{
+\noindent{\includegraphics[width=0.85\linewidth]{pdfs/semantics2.png}}
+}
+\vspace{-0.5em}
+
+\headerbox{More in the paper}{name=more,column=1,span=2,row=0,below=semantics}{
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\noindent{\centering\includegraphics[width=0.95\linewidth]{table.png}\\}
-
 \begin{multicols}{2}
-\noindent{\centering\includegraphics[width=1.15\linewidth]{pdfs/screenshot4.png}\\}
-\begin{itemize}\compresslist
-\item Techniques for field type refinement.
-\item Formalization and proofs.
-\item Case studies and applications.
-    \small{\newline
-    % \begin{itemize}\compresslist
-    % \item The Expression Problem
-    % \item Embedded DSLs with Fluent Interfaces
-    % \item A Maze Game
-    % \item Refactoring an Interpreter
-    % \end{itemize}
-    [The Expression Problem]\newline
-    [Embedded DSLs with Fluent Interfaces]\newline
-    [A Maze Game]\newline
-    [Refactoring an Interpreter] 
-    }
+\begin{itemize}
+\item Intuitive examples
+\item Subtyping, typing and reduction rules
+\item Design choices
+\item Extensions
+\item Properties/Proofs
+\item ...
 \end{itemize}
 \end{multicols}
+% \noindent{\centering\includegraphics[width=0.95\linewidth]{table.png}\\}
+
+% \begin{multicols}{2}
+% \noindent{\centering\includegraphics[width=1.15\linewidth]{pdfs/screenshot4.png}\\}
+% \begin{itemize}\compresslist
+% \item Techniques for field type refinement.
+% \item Formalization and proofs.
+% \item Case studies and applications.
+%     \small{\newline
+%     % \begin{itemize}\compresslist
+%     % \item The Expression Problem
+%     % \item Embedded DSLs with Fluent Interfaces
+%     % \item A Maze Game
+%     % \item Refactoring an Interpreter
+%     % \end{itemize}
+%     [The Expression Problem]\newline
+%     [Embedded DSLs with Fluent Interfaces]\newline
+%     [A Maze Game]\newline
+%     [Refactoring an Interpreter] 
+%     }
+% \end{itemize}
+% \end{multicols}
 }
 
-  \headerbox{Acknowledgments}{name=acknowledge,column=1, span=2, below=more}{
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-This work is sponsored by the Hong Kong Research Grant Council Early Career 
-Scheme project number 27200514. The first and second authors are supported by 
-the SIG PAC student travel grant.
-  }
+%   \headerbox{Acknowledgments}{name=acknowledge,column=1, span=2, below=more}{
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% This work is sponsored by the Hong Kong Research Grant Council Early Career 
+% Scheme project number 27200514. The first and second authors are supported by 
+% the SIG PAC student travel grant.
+%   }
 
-  \headerbox{Contacts}{name=acknowledge,column=1,span=2,below=acknowledge,above=bottom}{
+  \headerbox{Contacts}{name=acknowledge,column=1,span=2,below=more,above=bottom}{
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-08-08 UnintentionalStateConflict/paper3/sections/Formalization.tex
small fix
proof for theorems 1,2,3

--- 2018-06-27 UnintentionalStateConflict/paper3/sections/Formalization.tex
@@
 		\mu(o) = \newI{I}{...} \\ 
-		\mbody(m, I, J) = \overline{x}, e \\ 
-		e' = e[(J)o/\kwthis, \overline{v}/\overline{x}] \\
+		\mbody(m, I, J) = \overline{I_x} \ \overline{x}, e \\ 
+		e' = e[(J)o/\kwthis, (\overline{I_x})\overline{v}/\overline{x}] \\
 
@@
 \end{lstlisting}
+
+\section{Proof}
+\subsection{Properties}
+\begin{theorem}[Subject Reduction]~\label{theorem_subject}
+If $\judgeewf \Gamma {e : I}$ and $\mu | e \rightarrow \mu' | e'$, 
+then $\judgeewf \Gamma {e' : I}$.
+\end{theorem}
+\begin{proof} ~\\
+\indent \textbf{Case E-Invk.} Let
+  $$e = (J)o.m(\overline{v}) \quad \judgeewf {\Gamma} {e : I_e}$$
+  $$e' = (I_{e_0})[\overline{(I_x)v}/\overline{x}, (I_0)o/\kwthis]e_0$$
+  $$\mbody(m, I, J) = (I_0, \overline{I_x} \; \overline{x}, I_{e_0} \; e_0)$$
+
+Since $\mbody(m, I, J)$ is defined, the definition of $\mbody$ ensures that $I \subtype J$. And since $e$ is well-typed, by \textsc{(T-Invk)},
+  $$\judgeewf {\Gamma} {\overline{v} : \overline{I_v}} \quad \overline{I_v} \subtype \overline{I_x}$$
+
+By the rule \textsc{(T-Cast)},
+  $$\judgeewf {\Gamma} {\overline{(I_x)v} : \overline{I_x}} \quad \judgeewf {\Gamma} {(I_0)\new{I} : I_0}$$
+
+On the other hand, by Lemma~\ref{lemma:return_expr_typing},
+  $$\judgeewf {\overline{x} : \overline{I_x}, \kwthis: I_0} {e_0 : I'_{e_0}} \quad I'_{e_0} \subtype I_{e_0}$$
+
+By Lemma~\ref{lemma:weakening},
+  $$\judgeewf {\Gamma, \overline{x} : \overline{I_x}, \kwthis: I_0} {e_0 : I'_{e_0}}$$
+
+Hence by Lemma~\ref{lemma:subst_type_preservation}, the substitution preserves typing, thus
+  $$\judgeewf {\Gamma} {[\overline{(I_x)v}/\overline{x}, (I_0)o/\kwthis]e_0 : I'_{e_0}}$$
+
+Since $I'_{e_0} \subtype I_{e_0}$, the conditions of \textsc{(T-Cast)} are satisfied, hence $\judgeewf {\Gamma} {e' : I_{e_0}}$.
+Now we only need to prove that $I_{e_0} = I_e$.
+Since $I_{e_0}$ is from $\mbody(m, I, J)$, whereas $I_e$ is from $\mbody(m, J, J)$, by the rule \textsc{(T-Invk)} on $e$.
+Since $I \subtype J$, by Lemma~\ref{lemma:mbody_type_preservation}, $I_{e_0} = I_e$.
+
+\indent \textbf{Case E-New} Let   
+$$e = \newI{I}{\overline{v}}$$   
+$$e' = (I)o$$   
+By the rule \textsc{(T-Constructor)}, $\judgeewf \Gamma e:I$. And by the rule \textsc{(T-Cast)}, $\judgeewf \Gamma e':I$. Proved.
+
+\indent \textbf{Case E-Getter} Let
+$$e = (J)o.f()$$
+$$e' = (I_F)o_i$$
+where $f()$ is a getter with the return type $I_F$. And by the rule \textsc{(T-Cast)}, $\judgeewf \Gamma (I_F)o_i:I_F$. Proved.
+
+\indent \textbf{Case E-Setter}
+Similar as \textbf{Case E-Getter}.
+
+\indent \textbf{Case E-Let} Let
+$$e = \mylet{I}{x}{o}{e_1}$$
+$$e' = [(I)o/x]e_1$$
+Assume that $\judgeewf {\Gamma, x : I} e_1 : I_1$, then by the rule \textsc{(T-Let)}, $\judgeewf {\Gamma} \mylet{I}{x}{o}{e_1} : I_1$.
+By Lemma~\ref{lemma:subst_type_preservation}, $\judgeewf \Gamma [(I)o/x]e_1 : I_1$. Proved.
+
+\indent \textbf{Case E-Cast} 
+Let $e = (J)(I)o$ and $e' = (J)o$, then $\judgeewf \Gamma e : J$ and $\judgeewf \Gamma e' : J$ immediately from the rule \textsc{(T-Cast)}.
+
+\indent \textbf{Case E-CTX}
+Let $e = \varepsilon\{e_1\}$ and $e' = \varepsilon\{e_1'\}$.
+By the induction condition $\mu \mid e_1 \to \mu' \mid e_1'$ and the hypothesis:
+if $\judgeewf \Gamma e_1:J$ and $\mu \mid e_1 \to \mu' \mid e_1'$, then 
+$\judgeewf \Gamma e_1' : J$. Assume that $\judgeewf \Gamma {\varepsilon\{e_1\} : I}$, then by Lemma~\ref{lemma:subst_type_preservation}, 
+$\judgeewf \Gamma {\varepsilon\{e_1'\} : I}$. Proved.
+\end{proof}
+
+\begin{theorem}[Progress]~\label{theorem_progress}
+Suppose $e$ is a well-typed expression, if $e$ includes 
+$(J)o.m(\overline{v})$ as a sub-expression, where $\mu(o) = \newI{I}{...}$, then one of the following conditions holds: 
+\begin{enumerate}
+	\item \# $\overline{v} = 0$, validGetter(m, I, J) 
+	\item \# $\overline{v} = 1$, validSetter(m, I, J)
+	\item $\mbody(m, I, J) = (I_0, \overline{I_x} \; \overline{x}, I_e\; e_0)$ and $\num{\overline{x}} = \num{\overline{v}}$ for some $I_0$, $\overline{I_x}$, $\overline{x}$, $I_e$ and $e_0$.
+\end{enumerate}
+\end{theorem}
+\begin{proof} 
+Since $e$ is well-typed and includes $(J)o.m(\overline{v})$ as a sub-expression. 
+Then the sub-expression $(J)o.m(\overline{v})$ can be divided into three cases:
+\begin{enumerate}
+	\item $m$ is a getter, validGetter(m, I, J) and getters contain no parameter.
+And by the rule \textsc{(T-Invk)}, the number of arguments is the same to the number of parameters of the method(getter), which is 0.
+	\item $m$ is a setter, validSetter(m, I, J) and setters contain one and only one parameter.
+By the rule \textsc{(T-Invk)}, the number of arguments is the same to the number of parameters of the method(setter), which is 1.
+	\item $m$ is neither a getter or setter, by the rule \textsc{(T-Invk)} we know that
+	$$I \subtype J\textrm{, and }\mbody(m, J, J) \textrm{ is defined}$$
+
+	By \textsc{(T-Intf)}, $\mbody(m, I, J)$ is also defined, and the type checker ensures the expected number of arguments.
+
+	On the other hand, since $I \subtype J$, by the definition of $\mostSpecific$, $$\mostSpecific(m, I, J) \subseteq \mostSpecific(m, I, I)$$
+
+	By \textsc{(T-New)}, assume $mconstr(I) = \overline{I_x} \; \overline{x}$ and MC OK in interface I.
+$\validMC(I, \overline{I_x} \; \overline{x}) = True$.
+By the definition of $\validMC$, any $J_0\in\mostSpecific(m, I, I)$ satisfies that
+	$\mostSpecificOverride(m, I, J_0)$ contains only one interface, in which the $m$ that overrides $J_0$ is a concrete method.
+Therefore $\mbody(m, I, J)$ also provides a concrete method, which finishes the proof.
+\end{enumerate}
+\end{proof}
+
+% \begin{theorem}[Progress]~\label{theorem_progress}
+% Suppose $e$ is a well-typed expression, if $e$ includes 
+% $(J)o.m(\overline{v})$ as a sub-expression, where $\mu(o) = \newI{I}{...}$, then  
+% $\mbody(m, I, J) = (I_0, \overline{I_x} \; \overline{x}, I_e\; e_0)$ and $\num{\overline{x}} = \num{\overline{v}}$ for some $I_0$, $\overline{I_x}$, $\overline{x}$, $I_e$ and $e_0$.
+% \end{theorem}
+% \begin{proof}
+% See Appendix~\ref{appendix_proof}.
+% \end{proof}
+% \begin{proof} 
+% Since $e$ is well-typed, by \textsc{(T-Invk)} and \textsc{(T-Anno)} we know that
+% $$I \subtype J\textrm{, and }\mbody(m, J, J) \textrm{ is defined}$$
+
+% By \textsc{(T-Intf)}, $\mbody(m, I, J)$ is also defined, and the type checker ensures the expected number of arguments.
+
+% On the other hand, since $I \subtype J$, by the definition of $\mostSpecific$, $$\mostSpecific(m, I, J) \subseteq \mostSpecific(m, I, I)$$
+
+% By \textsc{(T-New)}, $\canInstantiate(I) = True$. By the definition of $\canInstantiate$, any $J_0\in\mostSpecific(m, I, I)$ satisfies that
+% $\mostSpecificOverride(m, I, J_0)$ contains only one interface, in which the $m$ that overrides $J_0$ is a concrete method.
+Therefore $\mbody(m, I, J)$ also provides a concrete method, which finishes the proof.
+% \end{proof}
+
+\begin{theorem}[Type Soundness]~\label{theorem_soundness}
+If $\judgeewf \o {e : I}$ and $\o | e \to^* \mu | e'$ with $e'$ a normal form, then $e'$ is 
+a value $v$ with $\judgeewf \o {v:I}$.
+\end{theorem}
+\begin{proof}
+Immediate from Theorem~\ref{theorem_subject} and Theorem~\ref{theorem_progress}.
+\end{proof}
+
+\begin{theorem}[Determinacy of One-Step Evaluation]~\label{theorem_determinacy}
+	If $\mu | t \to \mu' | t'$ and $\mu | t \to \mu'' | t''$, then $t' = t''$ and $\mu' = \mu''$.
+\end{theorem}
+\begin{proof}	
+The Proof is done by induction on a derivation of $t \to t'$, following the book  \emph{TAPL}.
+\begin{itemize}
+	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(S-Invk)}, then we know that $t$ has the form $\left((J)\new{I}\right).m(\overline{v})$ with $I, J, m$ determined.
+Now it is obvious that the last rule in the derivation of $t \to t''$ should also be \textsc{(S-Invk)} with the same $I, J, m$.
+Since $\mbody(m, I, J)$ is a \emph{function} that given the same input will calculate the same result, we know the two induction results are the same, thus $t' = t''$ is immediately proved.
+
+	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-Receiver)}, then $t$ has the form $e_0.m(\overline{e})$ and $e_0 \to e_0'$.
+Since $e_0$ is not a value, the last rule used in $t \to t''$ has to be \textsc{(C-Receiver)} (other rules do not match) too.
+Assume in the reduction $t \to t''$, $e_0 \to e_0''$, thus $e_0'.m(\overline{e}) = e_0''.m(\overline{e})$.
+Thus, $t' = t''$ proved.
+
+	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-StaticType)}, then $t$ is fixed to be $\new{I}$.
+The last rule used in $t \to t''$  has to be \textsc{(C-StaticType)}, and obviously, $t' = t'' = (I)\new{I}$.
+
+	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-FReduce)}, then $t$ has the form $(I)e$ and $e \to e'$.
+The last rule used in $t \to t''$ cannot be \textsc{(C-StaticType)} because it requires $t$ to be $\new{I}$; it can neither be \textsc{(C-AnnoReduce)} because it requires $t$ to be $(I)((J)\new{K})$ where $(J)\new{K}$ is already a value.
+So the last rule used in $t \to t''$ can only be \textsc{(C-FReduce)} (other rules do not match).
+Assume in the reduction $t \to t''$, $e \to e''$, and $(I)e \to (I)e''$.
+By induction hypothesis, $e' = e''$, thus $t' = t''$ proved.
+
+	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-AnnoReduce)}, then the form of $t$ is fixed to be $(I)((J)\new{K})$.
+Since $(I)((J)\new{K})$ is not reducible, the rule \textsc{(C-FReduce)} does not apply.
+The only rule applies in $t \to t''$ is \textsc{(C-AnnoReduce)}.
+Thus $t' = t'' = (I)\new{K}$ proved.
+
+	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-Args)}, then $t$ has the form $v.m(..., e, ...)$ and $e \to e'$.
+The last rule used in $t \to t''$ cannot be \textsc{(S-Invk)} because it requires all arguments to be values.
+Thus only \textsc{(C-Args)} applies to $t \to t''$.
+Assume in the reduction $t \to t''$, $e \to e''$.
+By induction hypothesis, $e' = e''$, thus $v.m(..., e', ...) = v.m(..., e'', ...)$, thus $t' = t''$ proved.
+\end{itemize}
+\end{proof}
+
+\subsubsection{Proof for Theorem~\ref{theorem_subject}}
+
+\subsubsection{Proof for Theorem~\ref{theorem_progress}}
+
+\subsubsection{Proof for Theorem~\ref{theorem_determinacy}}

### 2018-08-08 UnintentionalStateConflict/paper3/sections/Formalization.tex
Theorem 4 proof (unfinished)

@@
 \begin{theorem}[Determinacy of One-Step Evaluation]~\label{theorem_determinacy}
-	If $\mu | t \to \mu' | t'$ and $\mu | t \to \mu'' | t''$, then $t' = t''$ and $\mu' = \mu''$.
+	If $\mu \mid t \to \mu' \mid t'$ and $\mu \mid t \to \mu'' \mid t''$, then $t' = t''$ and $\mu' = \mu''$.
 \end{theorem}
 \begin{proof}	
-The Proof is done by induction on a derivation of $t \to t'$, following the book  \emph{TAPL}.
+The Proof is done by induction on a derivation of $\mu \mid t \to \mu' \mid t'$, following the book  \emph{TAPL}.
 \begin{itemize}
-	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(S-Invk)}, then we know that $t$ has the form $\left((J)\new{I}\right).m(\overline{v})$ with $I, J, m$ determined.
-Now it is obvious that the last rule in the derivation of $t \to t''$ should also be \textsc{(S-Invk)} with the same $I, J, m$.
+	\item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-Invk)}, then we know that $t$ has the form $(J)o.m(\overline{v})$ with $\mu(o) = \newI{I}{...}$, $I, J, m$ determined.
+Now it is obvious that the last rule in the derivation of $\mu \mid t \to \mu'' \mid t''$ should also be \textsc{(E-Invk)} with the same $I, J, m$.
 Since $\mbody(m, I, J)$ is a \emph{function} that given the same input will calculate the same result, we know the two induction results are the same, thus $t' = t''$ is immediately proved.
+Also from the rule \textsc{(E-Invk)}, we know that $\mu$ is unchanged, thus $\mu' = \mu'' = \mu$ is also proved.
 
-	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-Receiver)}, then $t$ has the form $e_0.m(\overline{e})$ and $e_0 \to e_0'$.
-Since $e_0$ is not a value, the last rule used in $t \to t''$ has to be \textsc{(C-Receiver)} (other rules do not match) too.
-Assume in the reduction $t \to t''$, $e_0 \to e_0''$, thus $e_0'.m(\overline{e}) = e_0''.m(\overline{e})$.
-Thus, $t' = t''$ proved.
+	\item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-New)}, then the form of $t$ is fixed to be $\newI{I}{\overline{v}}$.
+The only rule applies in $\mu \mid t \to \mu'' \mid t''$ is also \textsc{(E-New)}.
+From the rule \textsc{(E-New)} we know that $t' = t'' = (I)o$ and $\mu' = \mu'' = \mu, o \to \newI{I}{\overline{v}}$ proved.
 
-	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-StaticType)}, then $t$ is fixed to be $\new{I}$.
-The last rule used in $t \to t''$  has to be \textsc{(C-StaticType)}, and obviously, $t' = t'' = (I)\new{I}$.
+	\item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-Cast)}, then the form of $t$ is fixed to be $(I)((J)o)$.
+Since $(J)o$ is not reducible, the only rule applies in $\mu \mid t \to \mu'' \mid t''$ is \textsc{(E-Cast)}.
+Also from the rule \textsc{(E-Cast)} we know that $\mu$ is unchanged, thus $t' = t'' = (I)o$ and $\mu' = \mu'' = \mu$ proved.
 
-	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-FReduce)}, then $t$ has the form $(I)e$ and $e \to e'$.
-The last rule used in $t \to t''$ cannot be \textsc{(C-StaticType)} because it requires $t$ to be $\new{I}$; it can neither be \textsc{(C-AnnoReduce)} because it requires $t$ to be $(I)((J)\new{K})$ where $(J)\new{K}$ is already a value.
-So the last rule used in $t \to t''$ can only be \textsc{(C-FReduce)} (other rules do not match).
-Assume in the reduction $t \to t''$, $e \to e''$, and $(I)e \to (I)e''$.
-By induction hypothesis, $e' = e''$, thus $t' = t''$ proved.
+	\item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-Let)}, then the form of $t$ is fixed to be $\mylet{I}{x}{o}{e}$.
+And the only rule applies in $\mu \mid t \to \mu'' \mid t''$ is \textsc{(E-Let)}.
+Also from the rule \textsc{(E-Cast)} we know that $\mu$ is unchanged, thus $t' = t'' = e[(I)o/x]$ and $\mu' = \mu'' = \mu$ proved.
 
-	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-AnnoReduce)}, then the form of $t$ is fixed to be $(I)((J)\new{K})$.
-Since $(I)((J)\new{K})$ is not reducible, the rule \textsc{(C-FReduce)} does not apply.
-The only rule applies in $t \to t''$ is \textsc{(C-AnnoReduce)}.
-Thus $t' = t'' = (I)\new{K}$ proved.
+	\item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-Getter)}, then the form of $t$ is fixed to be $(J)o.f()$.
+For the second reduction $\mu \mid t \to \mu'' \mid t''$, the rule \textsc{(E-Setter)} does not apply because the number of parameters does not match.
+Also the rule \textsc{(E-Invk)} does not match because the precondition $!validGetter(m, I, J)$ is not satisfied.
+The only rule applies  is the rule \textsc{(E-Getter)}.
+Also from the rule \textsc{(E-Getter)} we know that $\mu$ is unchanged, thus $t' = t'' = (I_F)o_i$ and $\mu' = \mu'' = \mu$ proved.
 
-	\item If the last rule used in the derivation of $t \to t'$ is \textsc{(C-Args)}, then $t$ has the form $v.m(..., e, ...)$ and $e \to e'$.
-The last rule used in $t \to t''$ cannot be \textsc{(S-Invk)} because it requires all arguments to be values.
-Thus only \textsc{(C-Args)} applies to $t \to t''$.
-Assume in the reduction $t \to t''$, $e \to e''$.
-By induction hypothesis, $e' = e''$, thus $v.m(..., e', ...) = v.m(..., e'', ...)$, thus $t' = t''$ proved.
+	\item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-Setter)}, then the form of $t$ is fixed to be $(J)o.SET_f((I')o)$.
+Then for the second reduction $\mu \mid t \to \mu'' \mid t''$, the rule \textsc{(E-Getter)} does not apply because the number of parameters does not match.
+Also the rule \textsc{(E-Invk)} does not match because the precondition $!validSetter(m, I, J)$ is not satisfied.
+The only rule applies is the rule \textsc{(E-Setter)}.
+And from the rule \textsc{(E-Setter)}, we know that $t' = t'' = (I)o$.
+Assume in the first derivation $\mu \mid t \to \mu' \mid t'$, $\mu = \mu_0, o \to \newI{I}{o_1,...,o_i,...,o_n}, \mu' = \mu_0, o \to \newI{I}{o_1,...,o',...,o_n}$, then in the second derivation $\mu \mid t \to \mu'' \mid t''$, $\mu = \mu_0, o \to \newI{I}{o_1,...,o_i,...,o_n}, \mu'' = \mu_0, o \to \newI{I}{o_1,...,o',...,o_n} = \mu'$.
+Proved.
+
+	\item \item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-CTX)}, 
 \end{itemize}

### 2018-08-08 UnintentionalStateConflict/paper3/sections/Formalization.tex
Theorem 4 finished

@@
 \subsection{Properties}
+
 \begin{theorem}[Subject Reduction]~\label{theorem_subject}
@@
 
-	\item \item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-CTX)}, 
+    \item If the last rule used in the derivation of $\mu \mid t \to \mu' \mid t'$ is \textsc{(E-CTX)}, then there are 5 cases ($t$ could take 5 forms):
+    \begin{itemize}
+    	\item If $t = \mylet{I}{x}{\varepsilon}{e}$ and the precondition is $\mu \mid e \to \mu' \mid e'$.
+Then $t' = \varepsilon\{e'\}$ .Then for the second reduction $\mu \mid t \to \mu'' \mid t''$, the rule \textsc{(E-Let)} does not apply because $\varepsilon$ is reducible and does not conform to the form of $\mylet{I}{x}{o}{e}$ in \textsc{(E-Let)}.
+Thus the only rule applies is the rule \textsc{(E-CTX)}.
+Assume the precondition is $\mu \mid e \to \mu'' \mid e''$.
+By the induction hypothesis, $\mu'' = \mu'$ and $e'' = e'$.
+Therefore, $t'' = \varepsilon\{e''\} = \varepsilon\{e'\} = t'$.
+Proved.
+    	\item The proof for the other cases, where 
+    		$t = \varepsilon.m(\overline{e}) $, 
+            $t = (J)o.m(\overline{o}, \varepsilon, \overline{e}) $
+            $t = \newI{I}{\overline{o}, \varepsilon, \overline{e}} $
+            or $t = (I)\varepsilon $ takes the same approach as the first case.
+    \end{itemize}
 \end{itemize}
 \end{proof}
-
-\subsubsection{Proof for Theorem~\ref{theorem_subject}}
-
-\subsubsection{Proof for Theorem~\ref{theorem_progress}}
-
-\subsubsection{Proof for Theorem~\ref{theorem_determinacy}}

### 2018-08-08 UnintentionalStateConflict/paper3/sections/TypeSafety.tex
Lemmas. Missing proof.

--- 2017-10-05 NewVersion/sections/TypeSafety.tex
@@
 
-%\begin{comment}	
+\begin{comment}	
 Since $\mbody(m, J, J)$ is defined, by \textsc{(T-Intf)} we derive that $\mbody(m, I, J)$ is also defined.
@@
 By Fact A, the proof is done.
-%\end{comment}
+\end{comment}
 
@@
 \begin{proof}
+% We prove by induction. The expression $e$ has the following cases:
 
-\begin{comment}
-\noindent \textbf{Case Var.}
-$ e = x \quad I = \Gamma(x) $. \\
-If $x \notin \overline{x}$, then the conclusion is immediate, since $[\overline{y}/\overline{x}]x = x$.
-On the other hand, if $x = x_i$ and $I = {I_x}_i$, then since $[\overline{y}/\overline{x}]x = [\overline{y}/\overline{x}]x_i = y_i$,
-letting $I' = {I_y}_i$ finishes the case.
+% \textbf{Case Var.} Let $e = x$. If $x \notin \overline{x}$, then the substitution does not change anything. Otherwise,
+% since $\overline{y}$ have the same types as $\overline{x}$, it immediately finishes the case.
 
-\noindent \textbf{Case New.}
-$e = \new I$ and there are no term for substitution, the conclusion is obvious.
-\noindent \textbf{Case Invk.}
-$ e = e_0.m(\overline{e}) \quad
-  \judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e_0 : I_0} $
-$$ mtype(m, I_0) = \overline{I_e} \rightarrow J $$
-$$ \judgeewf {\Gamma, \overline{x}:\overline{I_x}} {\overline{e}:\overline{I}} \quad
-    \overline{I} \subtype \overline{I_e} $$
-By induction hypothesis, there are some $I_0'$ and $\overline{I_e'}$ such that
-    $$ \judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0 : I_0'} \quad 
-        I_0' \subtype I_0 $$
-    $$ \judgeewf {\Gamma} {[\overline{y}/\overline{x}]\overline{e} : \overline{I_e'}} \quad  
-        \overline{I_e'} \subtype \overline{I}$$    
-By lemma~\ref{lemma2}, 
-    $mtype(m, I_0') = \overline{I_e} \rightarrow J$.
+% \textbf{Case Invk.} Let $e = e_0.m(\overline{e})$. By \textsc{(T-Invk)} we can suppose that
+% 	$$\judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e_0 : I_0} \quad \mbody(m, I_0, I_0) = (\_, \overline{J}\ \_, I\ \_)$$
+% 	$$\judgeewf {\Gamma, \overline{x}:\overline{I_x}} {\overline{e} : \overline{I_e}} \quad 
+% 	\overline{I_e} \subtype \overline{J} \quad \judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e : I}$$
 
-\noindent Then $\overline{I_e'} \subtype \overline{I_e}$ by the transitivity of $\subtype$.
-Therefore, by the rule \textsc{(T-Invk)}, 
-    $\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0.m([\overline{y}/\overline{x}]\overline{e}) : J}$.
+% By induction hypothesis, 
+% 	$$\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0 : I_0} \quad
+% 	  \judgeewf {\Gamma} {[\overline{y}/\overline{x}]\overline{e} : \overline{I_e}}$$
 
-\noindent \textbf{Case PathInvk.}
-$ e = e_0.I::m(\overline{e}) $ and proof is similar as case Var.
+% Again by \textsc{(T-Invk)}, $\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e : I}$.
 
-\noindent \textbf{Case SuperInvk.}
-$ e = \kwsuper.I::m(\overline{e}) $ \\
-Suppose $\judgeewf {\Gamma} {\kwthis : I_0}$, the following proof should be similar as case Var.
-\end{comment}
-We prove by induction. The expression $e$ has the following cases:
+% \textbf{Case New.} Straightforward.
 
-\textbf{Case Var.} Let $e = x$. If $x \notin \overline{x}$, then the substitution does not change anything. Otherwise,
-since $\overline{y}$ have the same types as $\overline{x}$, it immediately finishes the case.
-
-\textbf{Case Invk.} Let $e = e_0.m(\overline{e})$. By \textsc{(T-Invk)} we can suppose that
-	$$\judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e_0 : I_0} \quad \mbody(m, I_0, I_0) = (\_, \overline{J}\ \_, I\ \_)$$
-	$$\judgeewf {\Gamma, \overline{x}:\overline{I_x}} {\overline{e} : \overline{I_e}} \quad 
-	\overline{I_e} \subtype \overline{J} \quad \judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e : I}$$
-
-By induction hypothesis, 
-	$$\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0 : I_0} \quad
-	  \judgeewf {\Gamma} {[\overline{y}/\overline{x}]\overline{e} : \overline{I_e}}$$
-
-Again by \textsc{(T-Invk)}, $\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e : I}$.
-
-\begin{comment}
-\textbf{Case PathInvk.} $e = e_0.J_0?m(\overline{e})$. By \textsc{(T-PathInvk)}, suppose
-	$$\judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e_0 : I_0} \quad I_0 \subtype J_0$$
-	$$\mbody(m, I_0, J_0) = (\_, \overline{J}\ \_, I\ \_)$$
-	$$\judgeewf {\Gamma, \overline{x}:\overline{I_x}} {\overline{e} : \overline{I_e}} \quad 
-	  \overline{I_e} \subtype \overline{J} \quad \judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e : I}$$
-
-By induction hypothesis, 
-$$\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0 : I_0} \quad
-\judgeewf {\Gamma} {[\overline{y}/\overline{x}]\overline{e} : \overline{I_e}}$$
-
-Again by \textsc{(T-PathInvk)}, $\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e : I}$.
-\end{comment}
-
-\textbf{Case New.} Straightforward.
-
-\textbf{Case Anno.} Straightforward by induction hypothesis and \textsc{(T-Anno)}.
-
+% \textbf{Case Anno.} Straightforward by induction hypothesis and \textsc{(T-Anno)}.
 \end{proof}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Proof for Theorem~\ref{theorem_subject}}
-\begin{proof} ~\\
-\indent \textbf{Case S-Invk.} Let
-\begin{comment}
-   $$e = (\angl{J}\new{I}).m(\overline{v}) \quad \judgeewf {\Gamma} {e : I_e}$$
-   $$e' = (\angl{J}\new{I}).J?m(\overline{v})$$
-
-Since $e$ is well-typed, $\angl{J}\new{I}$ is also well-typed. By \textsc{(T-Anno)},
-  $$\judgeewf {\Gamma} {\angl{J}\new{I} : J} \quad I \subtype J$$
-
-By \textsc{(T-Invk)} on $e$,
-  $$\mbody(m, J, J) = (\_, \overline{I_x}\ \_, I_e\ \_) \quad \judgeewf {\Gamma} {\overline{v} : \overline{I_v}} \quad \overline{I_v}  \subtype \overline{I_x}$$
-
-At this moment, \textsc{(T-PathInvk)} is immediately applicable by the above conditions, including that $e'$ also invokes $\mbody(m, J, J)$. Hence $\judgeewf {\Gamma} {e' : I_e}$.
-\textbf{Case S-PathInvk.} Let
-\end{comment}
-  $$e = ((J)\new{I}).m(\overline{v}) \quad \judgeewf {\Gamma} {e : I_e}$$
-  $$e' = (I_{e_0})[\overline{(I_x)v}/\overline{x}, (I_0)\new{I}/\kwthis]e_0$$
-  $$\mbody(m, I, J) = (I_0, \overline{I_x} \; \overline{x}, I_{e_0} \; e_0)$$
-
-Since $\mbody(m, I, J)$ is defined, the definition of $\mbody$ ensures that $I \subtype J$. And since $e$ is well-typed, by \textsc{(T-Invk)},
-  $$\judgeewf {\Gamma} {\overline{v} : \overline{I_v}} \quad \overline{I_v} \subtype \overline{I_x}$$
-
-By the rules \textsc{(T-Anno)} and  \textsc{(T-New)},
-  $$\judgeewf {\Gamma} {\overline{(I_x)v} : \overline{I_x}} \quad \judgeewf {\Gamma} {(I_0)\new{I} : I_0}$$
-
-On the other hand, by Lemma~\ref{lemma:return_expr_typing},
-  $$\judgeewf {\overline{x} : \overline{I_x}, \kwthis: I_0} {e_0 : I'_{e_0}} \quad I'_{e_0} \subtype I_{e_0}$$
-
-By Lemma~\ref{lemma:weakening},
-  $$\judgeewf {\Gamma, \overline{x} : \overline{I_x}, \kwthis: I_0} {e_0 : I'_{e_0}}$$
-
-Hence by Lemma~\ref{lemma:subst_type_preservation}, the substitution preserves typing, thus
-  $$\judgeewf {\Gamma} {[\overline{(I_x)v}/\overline{x}, (I_0)\new{I}/\kwthis]e_0 : I'_{e_0}}$$
-
-Since $I'_{e_0} \subtype I_{e_0}$, the conditions of \textsc{(T-Anno)} are satisfied, hence $\judgeewf {\Gamma} {e' : I_{e_0}}$.
-Now we only need to prove that $I_{e_0} = I_e$.
-Since $I_{e_0}$ is from $\mbody(m, I, J)$, whereas $I_e$ is from $\mbody(m, J, J)$, by the rule \textsc{(T-Invk)} on $e$.
-Since $I \subtype J$, by Lemma~\ref{lemma:mbody_type_preservation}, $I_{e_0} = I_e$.
-
-\textbf{Case C-Receiver.} Straightforward induction.
-
-%\textbf{Case C-PathReceiver.} Straightforward induction.
-
-\textbf{Case C-Args.} Straightforward induction.
-
-%\textbf{Case C-PathArgs.} Straightforward induction.
-
-\textbf{Case C-StaticType.} Immediate by \textsc{(T-Anno)}.
-
-\textbf{Case C-FReduce.} Immediate by \textsc{(T-Anno)} and induction.
-
-\textbf{Case C-AnnoReduce.} Immediate by \textsc{(T-Anno)} and transitivity of $\subtype$.
-
-\begin{comment}
-\noindent \textbf{Case Invk.} 
-let \[ e = \angl{J}\new I.m(\overline{\angl{I_e}}\overline{e}) \] 
-Suppose \[ \mbody(m, I, J) = (J', \overline{I_x} \; \overline{x}, I_{e_0} \; e_0) \] 
-then \[ e' =  [\overline{\angl{I_x}} \overline{e}/\overline{x}, \; \angl{J}\new I/\kwthis ] e_0 \] 
-By rules \textsc{(T-New)} and \textsc{(T-Invk)}, 
-  \[ \judgeewf \Gamma {\new I:I} \quad 
-     \mtype(m, I, J) = \overline{I_x} \rightarrow I_{e_0} \quad 
-     \judgeewf \Gamma {\overline{e} : \overline{I_e'}} \quad
-     \overline{I_e'} \subtype \overline{I_x} \quad
-     \textit{, for some } \; \overline{I_e'}
-  \]
-By Lemma~\ref{lemma0},
-    \[
-    \judgeewf {\Gamma, \overline{x}:\overline{I_x}, \kwthis:J_0} {e_0:I_f} \textit{, for some } J \subtype J_0 \textit{ and } I_f \subtype I_{e_0}
-    \]
-By Lemma~\ref{lemma1},
-    \[
-    \judgeewf {\Gamma} {[\overline{\angl{I_x}} \overline{e}/\overline{x}, \; \angl{J}\new I/\kwthis ] e_0  :  I_g} \textit{, for some } I_g \subtype I_f 
-    \]
-So $I_g <: I_{e_0}$, finally just let $I' = I_g$.
-
-\noindent \textbf{Case PathInvk.}
-let \[ e = \angl{J}\new I.K::m(\overline{\angl{I_e}} \overline{e}) \]  
-Suppose \[ \mbody(m, I, K) = (J', \overline{I_x} \; \overline{x}, I_{e_0} \; e_0) \] 
-then \[ e' =  [\overline{\angl{I_x}} \overline{e}/\overline{x}, \; \angl{K}\new I/\kwthis ] e_0 \] 
-By rules \textsc{(T-New)} and \textsc{(T-Invk)}, 
-  \[ \judgeewf \Gamma {\new I:I} \quad 
-     \mtype(m, I, K) = \overline{I_x} \rightarrow I_{e_0} \quad 
-     \judgeewf \Gamma {\overline{e} : \overline{I_e'}} \quad
-     \overline{I_e'} \subtype \overline{I_x} \quad
-     \textit{, for some } \; \overline{I_e'}
-  \]
-By Lemma~\ref{lemma0},
-    \[
-    \judgeewf {\Gamma, \overline{x}:\overline{I_x}, \kwthis:J_0} {e_0:I_f} \textit{, for some } K \subtype J_0 \textit{ and } I_f \subtype I_{e_0}
-    \]
-By Lemma~\ref{lemma1},
-    \[
-    \judgeewf {\Gamma} {[\overline{\angl{I_x}} \overline{e}/\overline{x}, \; \angl{K}\new I/\kwthis ] e_0  :  I_g} \textit{, for some } I_g \subtype I_f 
-    \]
-So $I_g <: I_{e_0}$, finally just let $I' = I_g$.
-
-\noindent \textbf{Case Super-Invk.}
-let \[ e = \kwsuper.K::m(\overline{\angl{I_e}} \overline{e}) \]   
-Suppose \[ \mbody(m, K, K) = (J', \overline{I_x} \; \overline{x}, I_{e_0} \; e_0) \] 
-then \[ e' =  [\overline{\angl{I_x}} \overline{e}/\overline{x}] e_0 \] 
-By rules \textsc{(T-New)} and \textsc{(T-Invk)}, 
-  \[ 
-     \mtype(m, K, K) = \overline{I_x} \rightarrow I_{e_0} \quad 
-     \judgeewf \Gamma {\overline{e} : \overline{I_e'}} \quad
-     \overline{I_e'} \subtype \overline{I_x} \quad
-     \textit{, for some } \; \overline{I_e'}
-  \]
-By Lemma~\ref{lemma0},
-    \[
-    \judgeewf {\Gamma, \overline{x}:\overline{I_x}, \kwthis:J_0} {e_0:I_f} \textit{, for some } K \subtype J_0 \textit{ and } I_f \subtype I_{e_0}
-    \]
-By Lemma~\ref{lemma1},
-    \[
-    \judgeewf {\Gamma} {[\overline{\angl{I_x}} \overline{e}/\overline{x} ] e_0  :  I_g} \textit{, for some } I_g \subtype I_f 
-    \]
-So $I_g <: I_{e_0}$, finally just let $I' = I_g$.
-
-\end{comment}
-\end{proof}
-
-\subsubsection{Proof for Theorem~\ref{theorem_progress}}
-\begin{proof}
-
-Since $e$ is well-typed, by \textsc{(T-Invk)} and \textsc{(T-Anno)} we know that
-$$I \subtype J\textrm{, and }\mbody(m, J, J) \textrm{ is defined}$$
-
-By \textsc{(T-Intf)}, $\mbody(m, I, J)$ is also defined, and the type checker ensures the expected number of arguments.
-
-On the other hand, since $I \subtype J$, by the definition of $\mostSpecific$, $$\mostSpecific(m, I, J) \subseteq \mostSpecific(m, I, I)$$
-
-By \textsc{(T-New)}, $\canOverride(I) = True$. By the definition of $\canOverride$, any $J_0\in\mostSpecific(m, I, I)$ satisfies that
-$\mostSpecificOverride(m, I, J_0)$ contains only one interface, in which the $m$ that overrides $J_0$ is a concrete method.
-Therefore $\mbody(m, I, J)$ also provides a concrete method, which finishes the proof.
-\end{proof}
